### 2017-06-28 PAPER.tex
first commit of paper: really rough draft of incomplete sections

\documentclass[preprint2,numberedappendix,tighten,twocolappendix]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
%\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
\shorttitle{Data Analysis Methods for the Detection of the Epoch of Reionization}
\shortauthors{Cheng et al.}

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[figuresright]{rotating}
\usepackage{natbib}
\usepackage{ctable}
\citestyle{aa}

%		Math Shortcuts from Adrian
%\def\b{\mathbf{b}}
%\def\k{\mathbf{k}}
%\def\r{\mathbf{r}}
%\def\q{\mathbf{q}}
%\def\b{\mathbf{b}}
%\def\kp{\mathbf{k}^\prime}
%\def\kpp{\mathbf{k}^{\prime\prime}}
%\def\V{\mathbb{V}}
%\def\At{\tilde{A}}
%\def\Vt{\tilde{V}}
%\def\Tt{\tilde{T}}
%\def\tb{\langle T_b\rangle}
%\newcommand{\vis}{\mathbf{v}}
%\newcommand{\x}{\mathbf{x}}
%\newcommand{\xhat}{\hat{\mathbf{x}}}
%\newcommand{\nhat}{\hat{\mathbf{n}}}
%\newcommand{\A}{\mathbf{A}}
%\newcommand{\N}{\mathbf{N}}
%\newcommand{\rhat}{\hat{\mathbf{r}}}
%\newcommand{\khat}{\hat{\mathbf{k}}}
%\newcommand{\btheta}{\boldsymbol \theta}

\newcommand{\cc}[1]{{\color{purple} \textbf{[#1]}}}

\begin{document}
\title{Data Analysis Methods for the Detection of the Epoch of Reionization}

\author{
Carina Cheng\altaffilmark{1},
et al.
}

%		Notes

%Reference section with: \ref{sec:Intro}
%Reference equation with: \eqref{eq:eqtest}
%Reference figure with: \ref{fig:figtest}
%Cite paper inside sentence: \citet{ref}
%Cite paper at end of sentence: \citep{ref}
%Cite paper inside a parenthetical sentence: \citealt{ref}

%To compile with references shown, compile in BibTeX once and LaTeX twice

%		Sample Equation Syntax
%\begin{equation}
%\label{eqtest}
%\langle \widetilde{T} (\mathbf{k}) \widetilde{T}^* (\mathbf{k^\prime}) \rangle = (2 \pi)^3 \delta^D (\mathbf{k} - \mathbf{k}^\prime) P(k),
%\end{equation}

\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
%\altaffiltext{2}{Hubble Fellow}
%\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley, CA}
%\altaffiltext{3}{Berkeley Center for Cosmological Physics, Berkeley, CA}
%\altaffiltext{3}{Dept. of Physics and Astronomy, U. Pennsylvania, Philadelphia, PA}
%\altaffiltext{8}{School of Earth and Space Exploration, Arizona State U., Tempe, AZ}

\begin{abstract}
\end{abstract}

\section{Introduction}
\label{sec:Intro}

By about one billion years after the Big Bang, the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the Universe's early life. This important transition, during which the first luminous structures formed from gravitational collapse and emit intense radiation, transforming the cold neutral gas into a plasma, is known as the epoch of reionization (EoR). The EoR represents an unexplored era in our cosmic dawn, whose history encodes important information regarding the nature of the first galaxies and the process of structure formation. A direct detection of the EoR would unlock powerful information about the intergalactic medium, revealing connections between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured web of galaxies we observe today.

One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted by neutral hydrogen via its spin-flip transition. This technique is powerful because it can be observed as a function of redshift - that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space. The 21 cm line therefore offers a window into following the evolution of ionization, temperature, and density fluctuations on cosmic scales.

Although a detection of the EoR has not currently been made to-date, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen in order to place constraints on the brightness of the EoR. Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are EDGES (\citealt{bowman2010}), the LWA (\citealt{ellingson_et_al2009}), LEDA (\citealt{greenhill_bernardi2012}), DARE (\citealt{burns2012}), SciHi (\citealt{voytek2014}), BIGHORNS (\citealt{sokolowski2015}), and SARAS (\citealt{patra2015}). Major interferometers, which seek to measure statistical power spectra, include the GMRT (\citealt{paciga_et_al2013}), LOFAR (\citealt{van_haarlem_et_al2013}), the MWA (\citealt{tingay_et_al2013}), the 21CMA (\citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that hopes to combine lessons learned from previous experiments and is forecasted to be able to make a successful \cc{?$\sigma$} detection with an eventual \cc{?} elements.

The major challenge that faces all 21 cm experiments is in isolating a small signal that is buried underneath foregrounds and instrumental systematics that are 4-5 orders of magnitude brighter. A clean measurement therefore requires an intimate understanding of the instrument and a very careful, thorough understanding of data analysis choices. With HERA on the horizon and continual progress being made in the field, it is becoming increasingly more important to develop methods that can both reinforce a potential real detection and explain any false ones. In this paper, we present approaches to both of these issues using data from the 64-element configuration of PAPER. We place special emphasis on the accurate injection and recovery of a fake EoR signal in order to assess signal loss associated with different weighting techniques, as well as the importance of using jack-knife tests to investigate sources of bias.

This paper is organized as follows. In section 2 we give a brief overview of the PAPER-64 array and observations. Section 3 presents two key components of any power spectrum analysis pipeline - accurately quantifying signal loss that may result from data analysis choices, and choosing a weighting scheme to maximum foreground down-weighting without amassing large amounts of signal loss. In Section 4 we highlight useful jack-knife tests that can help discriminate between excess detections from foregrounds. We conclude in Section 5.

\section{Observations}
\label{sec:Obs}

The Donald C. Baker Precision Array for Probing the Epoch of Reionization (PAPER) is a dedicated 21 cm experiment located in the Karoo Desert in South Africa. The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements, each 2 m on a side. The antenna layout is formatted in a grid layout (Figure \ref{fig:paper}), with 8 antennas on a side, 30 m spacing between antennas along the East/West direction, and 4 m spacing between antennas along the North/South direction. For the rest of this paper, we focus on data from only the 30 m pure East/West baselines.

\begin{figure*}
	\centering
	\includegraphics[height=0.3\textwidth]{paper_dipole.png}
	\includegraphics[height=0.3\textwidth]{antenna_layout.png}
	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
	\label{fig:paper}
\end{figure*}

PAPER-64 observed for a total of 135 nights between 2012-2013. The correlator processes a bandwidth of 100-200 MHz, corresponding to a redshift range of 6-12. For more information about the backend system of PAPER-64 and its observations, we refer the reader to \cc{??} and \citet{ali_et_al2015}.

Because there is a detailed discussion of the PAPER-64 data reduction pipeline in \citet{ali_et_al2015}, here we will only briefly summarize the data processing steps prior to the power spectrum analysis.

\cc{TO DO: summarize redundant\&absolute calibration, fg-clean, LST-binning, FRF}

\section{Power Spectrum Analysis}
\label{sec:PS}

We use optimal quadratic estimators as explained by \cc{??} in order to form our final power spectrum quantities. For the reader's convenience, we summarize the method here, as well as highlight changes that we have made for our most recent analysis.

\cc{TO DO: summarize OQE formalism and bootstrapping}
\cc{Don't forget to explain new PS channels, like noise and eor, and how they're created}

\subsection{Signal Loss Formalism}
\label{sec:Sigloss}

Based on our analysis pipeline, potential signal loss is a real and significant issue. More specifically, when applying inverse covariance weighting, $\textbf{C}^{-1}$ is empirically estimated from the data itself, which has the consequence of over-fitting the noise in the data, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters. This is especially prevalent when weighting fringe-rate-filtered data, which has so few independent time modes to begin with, leading to a noisier dataset. Being able to accurately quantify this loss is crucial in interpreting and providing credibility to any power spectrum limits.

New to the PAPER-64 analysis is a robust method to estimate signal loss associated with inverse covariance weighting. This method, explained below, is now a standard analysis step for all PAPER analyses and one that will be used for HERA moving forward.

As discussed previously, our power spectrum pipeline runs on a standardized set of channels (pure data, pure noise, pure EoR, and combinations of the three). As part of our signal loss routine, we also compute power spectra with various levels of the created EoR signal, dialing its amplitude from well-below the data level, to well-above. Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}$ to be:

\begin{equation}
\textbf{r} = \textbf{x} + \textbf{e}
\end{equation}

Using our OQE formalism, we are interested in the following two quantities: $P_{in}$ and $P_{out}$. The input power spectrum, $P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal. The output power spectrum, $P_{out}$, is the weighted power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data. Comparing the two quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting. Ignoring normalization, factors:

\begin{equation}
P_{in} \propto \textbf{e}^{\dagger}\textbf{I}^{-1}\textbf{Q}\textbf{I}^{-1}\textbf{e}
\end{equation}

\begin{eqnarray}
\label{eq:sigloss}
P_{out} \equiv \textbf{P}_{e} &=& \textbf{P}_{r}-\textbf{P}_{x} \nonumber \\
&\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} 
\end{eqnarray}

It is noted that the output power spectrum is comprised of two terms: the covariance treated power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.

One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e}$. Expanding Equation \ref{eq:sigloss}:

\begin{eqnarray}
P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} \nonumber \\
&\propto& \textbf{x}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{x} + \textbf{e}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{e} + \textbf{x}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{e} \nonumber \\
&+& \textbf{e}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{x} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} \nonumber 
\end{eqnarray}

And taking the case of very large $\textbf{e}$, so that $\textbf{C}_{r}^{-1} \sim \textbf{C}_{e}^{-1}$ and any terms involving only $\textbf{x}$ are small:

\begin{eqnarray}
P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e} + \textbf{x}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e} \nonumber \\
&+& \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{x}
\end{eqnarray}

We see that our naive expression for $P_{out}$ is the first term, but there also two additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since the two quantities are un-correlated. However, \cc{need explanation about power in cross-terms here}. Therefore, in our investigation of signal loss, we use the full quantity for $P_{out}$ as in Equation \ref{eq:sigloss}.

For the unweighted case ($\textbf{C} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1. For the weighted case, this is not true due to signal loss. In order to quantify the loss, we look at the ratio of $P_{in}$ to $P_{out}$ as the amplitude level of the injected signal \textbf{e} is increased. In the next section, we highlight two methods that yield similar results for the determination of signal loss using $P_{in}$ and $P_{out}$

\subsection{Signal Loss in Practice}
\label{sec:siglossprac}

Recall that fringe-rate-filtered noise, which mimics the level of noise in our actual PAPER-64 dataset, is a channel in our power spectrum pipeline. We can compute signal loss quantities of interest for the noise $\textbf{n}$ similar to the expressions we featured previously for data $\textbf{x}$.

\begin{eqnarray}
P_{in} &\propto& \textbf{e}^{\dagger}\textbf{I}^{-1}\textbf{Q}\textbf{I}^{-1}\textbf{e} \\
\textbf{s} &=& \textbf{n} + \textbf{e} \\
P_{out} &\propto& \textbf{s}^{\dagger}\textbf{C}_{s}^{-1}\textbf{Q}\textbf{C}_{s}^{-1}\textbf{s} - \textbf{n}^{\dagger}\textbf{C}_{n}^{-1}\textbf{Q}\textbf{C}_{n}^{-1}\textbf{n} 
\end{eqnarray}

Using the input and output power spectra for range of EoR amplitudes, we use two methods to determine signal loss associated with the over-fitting of noise during inverse covariance weighting. We first look at signal loss for the pure noise case (no data), to show that we can successfully inject EoR signals, determine signal loss, and then recover the signal.

The first method is very straightforward. Post-bootstrapping, our final power spectra are 1-dimensional and only a function of $k$. For each $k$, we simply look at $P_{out}$ as a function of $P_{in}$, as shown in Figure \ref{fig:sigloss1_noise}. The shape of this function can be explained as follows. At small injection levels (small $\textbf{e}$), $P_{out}$ and $P_{in}$ are equal, and there is no signal loss. As the amplitude of EoR increases, we then move into a regime where the final output power spectrum is lower than the unweighted input one. This is dangerous, because without correcting for this effect one might be led to underestimate the EoR signal. The peculiar tail at very low injection levels (where $P_{out} > P_{in}$) is an unphysical feature, but rather illustrates that there is some non-negligible cross-term power between $\textbf{n}$ and $\textbf{e}$.

For this method, we interpolate the signal loss factor (per $k$), computed as $P_{in}/P_{out}$, at a $P_{out}$ value equal to the $2\sigma$ power spectrum upper limit of noise alone. In other words, we look at $P_{noise} \propto \textbf{n}^{\dagger}\textbf{C}_{n}^{-1}\textbf{Q}\textbf{C}_{n}^{-1}\textbf{n}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value. We therefore end up with one signal loss correction factor per $k$.

\begin{figure*}
	\centering
	\includegraphics[width=1.0\textwidth]{sigloss1_noise.png}
	\caption{$P_{in}$ vs. $P_{out}$ (blue points) for 15 injection levels and 21 $k$'s. The solid cyan line is the $2\sigma$ upper limit for the weighted power spectrum of noise alone, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation. \cc{Maybe re-do this plot with closer-together points}}
	\label{fig:sigloss1_noise}
\end{figure*}

Figure \ref{fig:ps1_noise} shows the power spectrum of our noise simulation, using full inverse covariance weighting, both before and after signal loss correction. Prior to signal loss correction, it is obvious that the power spectrum is unfeasible because it is well below the theoretical noise level prediction. Post-correction, the power spectrum values blow up much higher than both the theory and unweighted power spectrum. This is an effect caused by the steep nature of the eigenspectrum of $\textbf{C}$, and is explained more in Section \ref{sec:Weight}.

\cc{Need a plot that shows our signal loss factors are CORRECT. How to do that??}

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{ps1_noise_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{ps1_noise.png}
	\caption{Full inverse covariance weighted power spectrum of pure noise (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational parameters. \cc{Color negative points grey}}
	\label{fig:ps1_noise}
\end{figure*}

Our second method for estimating signal loss is similar to the first, but more comprehensive in a statistical sense. Instead of looking at input and output power spectra after bootstrapping, we now look at their values for every bootstrap in order to get a sense of their distributions. Figure \ref{fig:sigloss2_noise} plots $P_{in}$ vs. $P_{out}$ for $20$ bootstraps, and as expected, the function now has a spread in the width-direction in comparison to what was plotted in Figure \ref{fig:sigloss1_noise}, but otherwise shows a familiar trend. Similarly, our weighted noise power spectra also has a defined spread due to bootstrapping.

Using these two distributions ($P_{in}/P_{out}$ and $P_{noise}$), we can create bins along the $P_{noise}$ axis to yield histograms of signal loss factors for each bin. We similarly sort the values of $P_{noise}$ into the same bins, and multiply the probability of $P_{noise}$ per bin (the number of values falling into that bin, divided by the total) with the signal loss factors in that bin, essentially computing a weighted average across all bins to obtain a final signal loss factor per $k$. As shown in Figure \ref{fig:ps2_noise}, the results are very similar to the previous method. For future power spectrum results, we choose to use the second method because it computes final signal loss values using our full distributions of measurements.

One thing to note is that for both methods, we have been careful to validate that the computations yield no signal loss (signal loss factors of $1$) for the unweighted power spectrum case, as is expected. This is important in confirming that signal loss is a direct result of the choice for $\textbf{C}$.

\begin{figure*}
	\centering
	\includegraphics[width=1.0\textwidth]{sigloss2_noise.png}
	\caption{$P_{in}$ vs. $P_{out}$ (blue) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent cyan range of pCn values instead of just the max}}
	\label{fig:sigloss2_noise}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{ps2_noise_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{ps2_noise.png}
	\caption{Full inverse covariance weighted power spectrum of pure noise (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right). Black points correspond to positive values, while grey points correspond to originally negative values that have been made positive for plotting. The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational parameters.}
	\label{fig:ps2_noise}
\end{figure*}

\subsection{Data Weighting}
\label{sec:Weight}

With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{C}$. Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss. We have found that the balance between the two is a delicate one and requires \cc{?? finish sentence...}.

We now turn our attention to power spectra using the 30 m East/West baselines of PAPER-64. Our dataset spans $8.5$ hours of LST ($.1$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate-filtered using an optimal fringe-rate-filter. We have two datasets (even days and odd days), and only cross-multiply data from different days and different baselines. We are interested in $21$ frequency channels (channels 95-115), which yields a power spectrum for a redshift of $z=8.4$.

Using full inverse covariance weighting, our results are not too dissimilar to that of pure noise. Signal loss factors (Figure \ref{fig:sigloss2_data}) are of similar order of magnitude, and our power spectrum blows up past the unweighted version after signal loss correction (Figure \ref{fig:ps2_data}).

%\begin{figure*}
%	\centering
%	\includegraphics[width=1.0\textwidth]{sigloss1_data.png}
%	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels and 21 $k$'s. The solid grey line is the $2\sigma$ upper limit for the weighted power spectrum of data alone, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation. \cc{Probably don't need to show this plot at all}}
%	\label{fig:sigloss1_data}
%\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=1.0\textwidth]{sigloss2_data.png}
	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent grey range of pCv values instead of just the max}}
	\label{fig:sigloss2_data}
\end{figure*}

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{ps2_data_nosigloss.png}
	\includegraphics[width=0.4\textwidth]{ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right). Black points correspond to positive values, while grey points correspond to originally negative values that have been made positive for plotting. The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational parameters.}
	\label{fig:ps2_data}
\end{figure*}

Looking into this behavior in more detail, we investigate the shape of the eigenspectrum of $\textbf{C}$ for a typical baseline used in the analysis. Figure \ref{fig:eigenspectrum} shows this spectrum for baseline (1,4). Most obviously, the spectrum is steep, spanning 4 orders of magnitude. Not as obvious is the effect of this shape on our results. When the matrix $\textbf{C}$ is inverted to form $\textbf{C}^{-1}$, the effect of the steepness of the eigenspectrum is to up-weight very few modes of the sky while the rest are drastically down-weighted. More specifically, our fringe-rate-filtered data contains a finite, small number of independent modes, thereby resulting in a covariance matrix that can be described by just a few modes. Beyond the first few modes, the eigenvalues of each additional mode falls of dramatically. When inverting, we end up not only down-weighting those initial modes but severely up-weighting a few insignificant ones. Because of our weighting choice, signal loss blows up as it thinks we only have a couple modes in our data.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{eigenspectrum.png}
	\includegraphics[width=0.4\textwidth]{covariance.png}
	\caption{Eigenspectrum for $\textbf{C}$ for baseline (1,4) for the 21 channels ofs interest (left) and covariance matrix $\textbf{C}$ for the same baseline (right).}
	\label{fig:eigenspectrum}
\end{figure*}

Clearly the full inverse covariance treatment of our data is suboptimal to even the unweighted case, but we would like to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum. There are many choices for determining the covariance matrix $\textbf{C}$, but here we will illustrate \cc{?} promising ones as applied to PAPER-64.

\cc{TO DO: decide on/explain/show different weightings}

\section{Jack-Knives}
\label{sec:Jack}

\section{Conclusion}
\label{sec:Con}

\section{Acknowledgements}
\cc{NSF Graduate Research Fellowship Program (GRFP) Fellowship}
\cc{UC Berkeley Chancellor's Fellowship}
\label{sec:Ack}

\bibliographystyle{apj}
\bibliography{refs}

\end{document}

### 2017-06-28 PAPER.tex
fleshed out observatiosn and PS estimation a bit more

@@
 \begin{abstract}
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of the omnipresent neutral hydrogen.
+This important epoch of our cosmic dawn harbors a wealth of information regarding the environment during this transformative time, including insight into the nature of the first luminous sources and implications about cosmological parameters.
+There are many experiments investigating the EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate.
+As instruments become more sensitive and a statistical power spectrum detection is in our foreseeable future, it has become increasingly important to develop techniques that help ensure that a potential detection isn't washed out or mistaken for something else.
+In this paper, we focus on two crucial ingredients for a power spectrum detection - a method for the accurate injection and recovery of an EoR signal, and jack-knife tests that can tease out foregrounds and systematics that contaminate our signal.
+We describe and apply these methods using data taken by the 64-element configuration of the Donald C.
+Baker Precision Array for Probing the Epoch of Reionization (PAPER).
 \end{abstract}
@@
 In section 2 we give a brief overview of the PAPER-64 array and observations.
-Section 3 presents two key components of any power spectrum analysis pipeline - accurately quantifying signal loss that may result from data analysis choices, and choosing a weighting scheme to maximum foreground down-weighting without amassing large amounts of signal loss.
-In Section 4 we highlight useful jack-knife tests that can help discriminate between excess detections from foregrounds.
-We conclude in Section 5.
+In section 3 we describe our power spectrum estimation pipeline.
+Section 4 presents two key components of any power spectrum analysis pipeline - accurately quantifying signal loss that may result from data analysis choices, and choosing a weighting scheme to maximum foreground down-weighting without amassing large amounts of signal loss.
+In Section 5 we highlight useful jack-knife tests that can help discriminate between excess detections from foregrounds.
+We conclude in Section 6.
 
@@
 	\centering
-	\includegraphics[height=0.3\textwidth]{paper_dipole.png}
-	\includegraphics[height=0.3\textwidth]{antenna_layout.png}
+	\includegraphics[height=0.35\textwidth]{paper_dipole.png}
+	\includegraphics[height=0.35\textwidth]{antenna_layout.png}
 	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
@@
 
-\cc{TO DO: summarize redundant\&absolute calibration, fg-clean, LST-binning, FRF}
+Beginning with compressed data products which have been cleaned of radio frequency interference (RFI) at the $6\sigma$ level and then down-sampled (to $42.9$ s integrations, $203$ frequency channels), we then employ the technique of redundant calibration as a means of calibrating for individual antenna gains without needing to use information about the sky.
+Because PAPER is laid out on a grid, antenna calibration parameters can be found through the use redundancy.
+Namely, baselines of the same length and orientation should measure the same sky signal, but in practice there are differences due to instrumental effects caused by antennas, cables, and receivers.
+Using the basis of redundancy, however, allows us to set up a system of equations to solve for a complex gain per antenna that brings all baseline of a particular type into alignment.
+We do this using the package OMNICAL.
+
+We next solve for the array's overall phase and gain calibration parameters using a standard self calibration method.
+We used radio sources Pictor A, Fornax A, and the Crab Nebula to fit for an overall phase solution, and set our overall flux scale using Pictor A as a calibrator source.
+Although PAPER-64 data exists for all $4$ polarizations, we only use the $xx$ and $yy$ polarization data to form Stokes I as $V_{I} = \frac{1}{2}(V_{XX} + V_{YY})$.
+
+Eliminating bright foregrounds remains a challenging yet crucial component of any 21 cm data analysis.
+There are many techniques to go about foreground removal, including spectral polynomial fitting, principle component analysis, Fourier-mode filtering, non-parametric subtractions, and inverse covariance weighting.
+PAPER uses a delay-spectrum filtering method which was first explained and applied in \citet{parsons_et_al2014}.
+In short, the delay-filtering technique employs the spectrally smooth nature of foregrounds, which are consequently localized in delay-space, the Fourier dual to frequency.
+We subtract all components that fall within the horizon limit for a specific baseline type in delay-space, plus a $15$ ns buffer, thus gaining about $\sim4$ orders of magnitude in sensitivity.
+
+Finally, after removing an additional layer of RFI (values $3\sigma$ above the median), we average together all our data into two datasets: even julian dates and odd julian dates.
+A total of $124$ nights of data comprises this average, and we use these two datasets as a starting point for constructing power spectrum estimates.
 
@@
 
-We use optimal quadratic estimators as explained by \cc{??} in order to form our final power spectrum quantities.
-For the reader's convenience, we summarize the method here, as well as highlight changes that we have made for our most recent analysis.
+\subsection{Fringe-Rate-Filtering}
+\label{sec:FRF}
 
-\cc{TO DO: summarize OQE formalism and bootstrapping}
-\cc{Don't forget to explain new PS channels, like noise and eor, and how they're created}
+As shown in \citet{parsons_et_al2016}, a fringe-rate filter allows us to maximize our sensitivity even further by averaging visibilities in time.
+We apply this filter in the fringe-rate domain, the Fourier-dual to time, and it effectively amounts to increasing our data's integration time.
+Another way to describe the filter is that it weights different parts of the sky (which rotate at different ``fringe-rates") by the antenna beam.
+This allows us to up-weight parts of the sky high in the primary beam, and down-weight those that are less sensitive.
 
-\subsection{Signal Loss Formalism}
+In \citet{ali_et_al2015}, the filter applied was degraded (widened in fringe-rate space) from an optimal one that can be constructed based on the integration time of the data.
+This was chosen to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying optimal quadratic estimators (OQE) on data with too few modes.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{frp.png}
+	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
+	\label{fig:frp}
+\end{figure}
+
+New to our updated PAPER-64 analysis is the use of the optimal fringe-rate filter, which maximizes our sensitivity.
+With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), resulting in an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
+
+In practice, the optimal fringe-rate profile is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
+The filter is implemented on a per baseline basis by convolving the time-domain visibilities with the Fourier transform of the fringe-rate filter, resulting in averaged visibilities yielding $\sim 2$ orders of magnitude in sensitivity.
+
+\subsection{Power Spectrum Estimation}
+\label{sec:PSEst}
+
+To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as described by \cc{??}.
+A summary of the method is as follows.
+We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$) for each baseline and data group (`even' or `odd').
+As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups, where no baselines are repeated within or between groups.
+For the \citet{ali_et_al2015} method, each group is then sampled with replacement to create a new group, of the same size, that can have repeated baselines inside it.
+We discover that in doing so, we are sacrificing some of our sensitivity since this results in there being 3-4 repeated baselines per group.
+In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one.
+For example, if we have $10$ baselines in a group, we use the first $9$, and then fill the last slot randomly out of the $10$.
+We do this for all $5$ groups.
+This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run ($20$).
+
+Taking $\textbf{x}$ to be averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets). We next form the quantity $\hat{q}_{\alpha}$:
+
+\begin{equation}
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{x}-b_{\alpha}
+\end{equation}
+
+where $\textbf{C}$ is the covariance matrix defined to be $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$.
+The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
+A noise bias $b_{\alpha}$ is subtracted off.
+The index $\alpha$ represents each $k_{\parallel}$ bin, where $k_{\parallel}$ is the Fourier-dual to frequency.
+
+Notice that there are two quantities of $\textbf{C}^{-1}\textbf{x}$ in the expression for $\hat{q}$, representing two copies of inverse covariance weighted data.
+We perform all possible cross-multiplications of this quantity, except between the same datasets (`even' with `even', for example) and same groups (`baseline group 1' with `baseline group 1', for example).
+We avoid these computations to prevent auto power shared between the two quantities from introducing biases.
+
+The rest of the OQE formalism is identical to \citet{ali_et_al2015}. We normalize our power spectrum estimates using the matrix $\textbf{M}$:
+
+\begin{equation}
+\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}}
+\end{equation}
+
+where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. $\textbf{M}$ is related to the Fisher matrix $\textbf{F}$ by:
+
+\begin{eqnarray}
+\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{Q}_{\beta}) \\
+\textbf{W} &=& \textbf{MF}
+\end{eqnarray}
+
+Finally, our final power spectrum is:
+
+\begin{equation}
+\hat{\textbf{p}} = \textbf{Wp}
+\end{equation}
+
+Our final power spectrum quantities are 1-dimensional functions of $k$. We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.
+
+\cc{Explain new PS channels, like noise and eor, and how they're created}
+
+\subsection{Power Spectrum Sensitivity}
+\label{sec:PSSense}
+
+\cc{Add info on how we calculate effective inttime and adjust beam factor because of FRF}
+
+\section{Signal Loss}
 \label{sec:Sigloss}
+
+\subsection{Formalism}
+\label{sec:Formalism}
 
@@
 
-\subsection{Signal Loss in Practice}
+\subsection{Application}
 \label{sec:siglossprac}
 
-Recall that fringe-rate-filtered noise, which mimics the level of noise in our actual PAPER-64 dataset, is a channel in our power spectrum pipeline.
+Recall that fringe-rate filtered noise, which mimics the level of noise in our actual PAPER-64 dataset, is a channel in our power spectrum pipeline.
 We can compute signal loss quantities of interest for the noise $\textbf{n}$ similar to the expressions we featured previously for data $\textbf{x}$.
@@
 We now turn our attention to power spectra using the 30 m East/West baselines of PAPER-64.
-Our dataset spans $8.5$ hours of LST ($.1$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate-filtered using an optimal fringe-rate-filter.
+Our dataset spans $8.5$ hours of LST ($.1$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate filtered using an optimal fringe-rate filter.
 We have two datasets (even days and odd days), and only cross-multiply data from different days and different baselines.
@@
 When the matrix $\textbf{C}$ is inverted to form $\textbf{C}^{-1}$, the effect of the steepness of the eigenspectrum is to up-weight very few modes of the sky while the rest are drastically down-weighted.
-More specifically, our fringe-rate-filtered data contains a finite, small number of independent modes, thereby resulting in a covariance matrix that can be described by just a few modes.
+More specifically, our fringe-rate filtered data contains a finite, small number of independent modes, thereby resulting in a covariance matrix that can be described by just a few modes.
 Beyond the first few modes, the eigenvalues of each additional mode falls of dramatically.

### 2017-06-29 PAPER.tex
finished rough draft of power spectrum estimation section

@@
 
-To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as described by \cc{??}.
-A summary of the method is as follows.
+To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as described by \cc{??}. A summary of the method is as follows.
+
 We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$) for each baseline and data group (`even' or `odd').
@@
 In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one.
-For example, if we have $10$ baselines in a group, we use the first $9$, and then fill the last slot randomly out of the $10$.
+For example, if we have $10$ baselines in a group, we use the first $9$ to guarantee at least $9$ independent measurements, and then fill the last slot randomly out of the $10$.
 We do this for all $5$ groups.
-This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run ($20$).
+This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run for this analysis ($nboots = 20$).
 
@@
 We perform all possible cross-multiplications of this quantity, except between the same datasets (`even' with `even', for example) and same groups (`baseline group 1' with `baseline group 1', for example).
-We avoid these computations to prevent auto power shared between the two quantities from introducing biases.
+We avoid these computations to prevent the introduction of biases from shared auto power.
 
@@
 
-where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. $\textbf{M}$ is related to the Fisher matrix $\textbf{F}$ by:
+where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
 
 \begin{eqnarray}
-\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{Q}_{\beta}) \\
-\textbf{W} &=& \textbf{MF}
+\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{Q}_{\beta}). \\
 \end{eqnarray}
+
+We have a choice for $\textbf{M}$, and we choose to compute it by taking the Cholesky decomposition of $\textbf{F}$.
+Namely, we decompose the Fisher matrix such that $\textbf{F} = \textbf{L}\textbf{L}^{\dagger}$, where $\textbf{L}$ is a lower triangular matrix.
+Next, we construct $\textbf{M} = \textbf{D}\textbf{L}^{-1}$, where \textbf{D} is a diagonal matrix.
+Hence, our window function $\textbf{W} = \textbf{MF}$ becomes $\textbf{W} = \textbf{D}\textbf{L}^{\dagger}$ and is an upper triangular matrix.
+This window function was constructed in a way to prevent the leakage of foreground power from low $k$ to high $k$ modes.
+Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
+Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements.
 
@@
 
-Our final power spectrum quantities are 1-dimensional functions of $k$. We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.
+In practice, we end up with a 2-dimensional power spectrum quantity, which is a function of both time and $k$.
+We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.
 
-\cc{Explain new PS channels, like noise and eor, and how they're created}
+In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the bootstrap and time axes simultaneously.
+Random values are sampled with replacement along both axes, drawing as many values as there are number of bootstraps and times.
+Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis.
+
+However, we have found that this method greatly underestimates power spectrum errors, especially for fringe-rate filtered data.
+This can be explained by the fact that fringe-rate filtered data has a dramatically reduced number of independent modes.
+Hence, drawing $100$ samples out of a length-$100$ dataset that only has $5$ independent modes in it, for example, results in a narrower distribution of values that leads to a false error estimation.
+
+To avoid this issue, we instead take a simple average along the time axis. Our final power spectrum limits are computed by taking the mean and standard deviation over our single bootstrap axis.
+
+In summary, our power spectrum pipeline begins with data with four axes (datasets, baselines, times, frequencies), bootstraps over baselines, uses OQE formalism, and produces $1$-dimensional power spectra for both $\textbf{P(k)}$ and the folded version $\Delta^{2}\textbf{(k)}$, defined as:
+
+\begin{equation}
+\Delta^{\textbf{2}}\textbf{(k)} = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)}
+\end{equation}
+
+One critical new component of our power spectrum pipeline is that we have many different power spectrum channels that simultaneously get processed at the same time and are especially useful for signal loss (Section \ref{sec:Sigloss}) and sensitivity (Section \ref{sec:Sense}) verification.
+Two important channels, in addition to our PAPER-64 data, are a noise dataset and an EoR dataset (in addition to these, we do different combinations of all three).
+We will briefly describe each.
+
+We create random noise with a scale determined by the sensitivity of our instrument and parameters of our dataset. We calculate our system temperature for our frequencies of interest as:
+
+\begin{equation}
+T_{sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{rcvr}
+\end{equation}
+
+where $\nu$ are frequencies in GHz.
+We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ at $150$ MHz.
+This is lower than in \citet{ali_et_al2015} because \cc{why?}.
+We convert this temperature into a variance statistic using:
+
+\begin{equation}
+T_{rms} = \frac{T_{sys}}{\sqrt{\Delta\nu \Delta t N_{days} N_{pols}}}
+\end{equation}
+
+where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of data samples for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
+Our simulated noise has the same shape as our data, and we fringe-rate filter it in the same way to best mimic the real noise floor of our data.
+
+A second additional important channel in our pipeline is a simulated EoR signal.
+We again simulate random noise (with a default scale of $1$) with the same shape as our data, and we fringe-rate filter this signal twice.
+The first filter transforms the unattached noise into a signal that's attached to the sky (what our instrument observes).
+The second filter represents the fringe-rate filtering step in our data analysis pipeline.
+As described in Section \ref{sec:Sigloss}, we create an EoR signal at various amplitude levels.
+
+Our multi-channel power spectrum pipeline has been essential in helping us understand the nuances in our pipeline.
+Because there are many different components and countless subtle effects affecting our final limits, it has been imperative to carry all our channels through the analysis to validate each step.
 
@@
 
-\cc{Add info on how we calculate effective inttime and adjust beam factor because of FRF}
+\cc{Add info on sensitivity equation, how we calculate effective inttime and adjust beam factor because of FRF, etc.}
 

### 2017-07-06 PAPER.tex
-Re-organized layout of paper so that themes are discussed first, with PAPER-64 application at the end -Fleshed out themes intro -Fleshed out signal loss toy model section

@@
 \begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of the omnipresent neutral hydrogen.
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of neutral hydrogen.
 This important epoch of our cosmic dawn harbors a wealth of information regarding the environment during this transformative time, including insight into the nature of the first luminous sources and implications about cosmological parameters.
 There are many experiments investigating the EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate.
-As instruments become more sensitive and a statistical power spectrum detection is in our foreseeable future, it has become increasingly important to develop techniques that help ensure that a potential detection isn't washed out or mistaken for something else.
-In this paper, we focus on two crucial ingredients for a power spectrum detection - a method for the accurate injection and recovery of an EoR signal, and jack-knife tests that can tease out foregrounds and systematics that contaminate our signal.
-We describe and apply these methods using data taken by the 64-element configuration of the Donald C.
+With a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to develop techniques that help maximize sensitivity and validate results.
+Additionally, it is imperative to understand the trade-offs between different methods and their effects on common power spectrum themes.
+In this paper, we focus on three major themes - signal loss, power spectrum error bar estimation, and bias in measurements.
+We describe techniques that affect these themes using both a toy model and data taken by the 64-element configuration of the Donald C.
 Baker Precision Array for Probing the Epoch of Reionization (PAPER).
@@
 A clean measurement therefore requires an intimate understanding of the instrument and a very careful, thorough understanding of data analysis choices.
-With HERA on the horizon and continual progress being made in the field, it is becoming increasingly more important to develop methods that can both reinforce a potential real detection and explain any false ones.
-In this paper, we present approaches to both of these issues using data from the 64-element configuration of PAPER.
-We place special emphasis on the accurate injection and recovery of a fake EoR signal in order to assess signal loss associated with different weighting techniques, as well as the importance of using jack-knife tests to investigate sources of bias.
+With HERA on the horizon and continual progress being made in the field, it is becoming increasingly more important to understand how the methods we choose affect each other and any power spectrum results.
+In this paper, we discuss three themes essential to a $21$ cm power spectrum study and how data analysis choices affect each.
+We approach these themes from both a broad perspective, and through a detailed case study using data from the 64-element configuration of PAPER.
 
 This paper is organized as follows.
-In section 2 we give a brief overview of the PAPER-64 array and observations.
-In section 3 we describe our power spectrum estimation pipeline.
-Section 4 presents two key components of any power spectrum analysis pipeline - accurately quantifying signal loss that may result from data analysis choices, and choosing a weighting scheme to maximum foreground down-weighting without amassing large amounts of signal loss.
-In Section 5 we highlight useful jack-knife tests that can help discriminate between excess detections from foregrounds.
-We conclude in Section 6.
+In section 2 we introduce the three themes of our focus, using a toy model to develop intuition into each one.
+Section 3 presents an overview of the PAPER-64 array and observations, highlighting key changes from \citet{ali_et_al2015}.
+Sections 4, 5, and 6 detail how the new PAPER-64 analysis quantifies signal loss, estimates error bars, and eliminates bias, respectively.
+We conclude in Section 7.
 
-\section{Observations}
+\section{Power Spectrum Themes and Techniques}
+\label{sec:Themes}
+
+A typical dataset for a $21$ cm experiment involves many axes.
+Visibility measurements, the standard data product for radio telescopes, are saved for many baselines and baseline-types.
+These visibilities are comprised of many integrations and a spectrum of frequency channels.
+Data collection can span months and years and can involve multiple polarizations.
+The data itself contains not only an EoR signal, but layers of bright foregrounds, radio frequency interference, instrumental noise, and other systematics.
+
+The job for $21$ cm data analysts is to sift through terabytes of data to ultimately make a power spectrum, a statistical result that encodes the variance of a dataset.
+In other words, a power spectrum measures the strength of the $21$ cm signal on various spatial scales of the sky, a powerful measurement that can be used to trace the evolution of neutral hydrogen during the EoR.
+There are, however, many data analysis choices that affect both the variance of the dataset itself and how it is measured.
+
+Simply stated, we desire to maximize the sensitivity of a dataset as much as possible, while being confident about the result and able to account for irregularities.
+There are many choices as a data analyst, such as how to optimally combine time-ordered measurements, how to best and most accurately estimate its variance, and how to weight data in a way that suppresses uninteresting modes while not destroying an EoR signal.
+Common techniques such as averaging data, inverse covariance weighting, bootstrapping, and jack-knife testing each affect data in different ways and reveal different lessons.
+
+There are often tradeoffs between techniques. For example, \cc{cite papers such as Josh's}.
+
+In this paper, we focus on four power spectrum techniques and their affect on three umbrella $21$ cm power spectrum themes.
+We will give brief definitions now, and build intuition for each theme in the sections to follow.
+
+\begin{center}
+Power Spectrum Techniques
+\end{center}
+\begin{itemize}
+\item \textbf{Fringe-rate filtering:} The concept of a fringe-rate filter is similar to averaging data in time.
+We explain our filter in more detail in Section \ref{sec:CaseStudy}, but a broad description is that a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
+\item \textbf{Inverse covariance weighting:} Of the same flavor as inverse variance weighting, inverse covariance weighting weights a dataset by minimizing the covariance between frequency channels.
+This weighting has the effect of down-weighting correlated information and up-weighting noise-like information.
+\item \textbf{Bootstrapping:} This is a useful method for estimating errors of a dataset from itself. By randomly drawing samples of the data, the spread in those numbers gives us our errors.
+\item \textbf{Jack-Knife testing:} A resampling technique useful for estimating bias, jack-knives can be taken along different dimensions of a dataset to cross-validate results.
+\end{itemize}
+
+\begin{center}
+Power Spectrum Themes
+\end{center}
+\begin{itemize}
+\item \textbf{Signal Loss:} As explained in the next session, there are analysis techniques that can lead to the loss of an EoR signal.
+If not corrected for, it could lead to a false non-detection.
+Computing signal loss has subtle challenges but is a crucial component for confidence in any result.
+\item \textbf{Error Bar Estimation:} Errors on a $21$ cm power spectrum result can make the difference between a detection and a noise-like measurement, which have two very different implications.
+Errors can be estimated in a variety of ways, and we will discuss a few of them.
+\item \textbf{Bias:} There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum.
+It is important to identity them in order to interpret results and develop techniques to suppress contamination.
+\end{itemize}
+
+We will now discuss the three themes more in depth and discuss how certain power spectrum techniques affect each.
+
+\subsection{Signal Loss}
+\label{sec:SiglossOverview}
+
+Signal loss refers to the loss of a cosmological signal in a dataset.
+It can arise in a variety of ways at multiple stages in an analysis pipeline.
+Here we focus on signal loss originating from empirically estimating covariance matrices, a method that succeeds in down-weighting foregrounds but can carry the risk of large amounts of signal loss.
+We will develop our intuition and motivate the effect of signal loss using a toy model simulation.
+
+Suppose we have a very simple dataset which contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
+The data is comprised of a sine-wave foreground that varies in time, and a complex, random-noise EoR signal (Figure \ref{fig:toy_sigloss1}, left).
+
+\begin{figure*}
+	\centering
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss1.png}
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss2.png}
+	\caption{Left: Our toy model dataset contains a sine-wave foreground that varies in time and random noise as an EoR signal.
+Real parts are shown here.
+Right: Eigenspectrum of foregrounds only (blue), EoR only (red), and both (green)}
+	\label{fig:toy_sigloss1}
+\end{figure*}
+
+Before we demonstrate how signal loss can arise, we first look at the eigenspectrum of the covariance matrix that describes our data.
+That is, if $\textbf{x}$ is our dataset which contains both the foreground and EoR, its covariance matrix is empirically defined as $\textbf{C} \equiv \textbf{xx}^{\dagger}$.
+The eigenspectrum, which encodes useful information about the strengths of different frequency modes, is shown in the right plot of Figure \ref{fig:toy_sigloss1}.
+It is obvious that there is only 1 eigenmode in the foreground-only dataset (since we used one sine-wave), and therefore most of the information in our combined dataset is contained in the first mode.
+
+We would like to use inverse covariance weighting to down-weight the foregrounds in our dataset.
+To do so, we compute $\textbf{C}^{-1}$ and use optimal quadratic estimators (see Section \ref{sec:PS} for more details) to Fourier-transform our data along the `frequency' axis and form a power spectrum.
+As an explicit check, we use information from only the first eigenmode, and zero out the others.
+We do this because we know that the foregrounds can be perfectly described by only the first mode, so it should be all that we need to down-weight them.
+
+Figure \ref{fig:toy_sigloss3} shows the unweighted (using the identity matrix $\textbf{I}$ instead of $\textbf{C}$) power spectrum for the foreground-only data in blue, the unweighted power spectrum for the EoR-only data in red, and the weighted power spectrum for the combined dataset in green.
+There is one peak in blue from our one foreground mode.
+
+\begin{figure*}
+	\centering
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss4.png}
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss3.png}
+	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the combined dataset (green).
+Contrasted are the effect of using information from the first eigenmode only (left), and full inverse covariance weighting (right).}
+	\label{fig:toy_sigloss3}
+\end{figure*}
+
+From the left plot, we see that by down-weighting the first mode, we can perfectly recover EoR.
+This is in principle the reason why inverse covariance weighting is so attractive for $21$ cm data.
+If we could perfectly model our foregrounds, we could down-weight them without any signal loss.
+However, this is not the case in reality, since we can't distinguish between foreground and EoR modes.
+
+If we did not know that our foreground information is contained in only one mode, a naive approach would be to use full inverse covariance weighting (using information from all eigenmodes).
+Examining this case, our full inverse covariance weighted result (Figure \ref{fig:toy_sigloss3}, right) almost recovers the EoR signal.
+It exhibits the correct shape, but the amplitude level is slightly low.
+This is actually evidence of a small amount of signal loss.
+In this toy model, the amount of signal loss is small, but we can exaggerate the effect and investigate its cause by `fringe-rate filtering' our toy model dataset.
+
+Since fringe-rate filtering is similar in practice to averaging in time, we average every $4$ time integrations together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels (our matrices will be full rank).
+The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss1}, begin to fall for the last few eigenmodes.
+Although a subtle feature, it has large consequences on the resulting power spectra.
+
+\begin{figure*}
+	\centering
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss6.png}
+	\caption{Left: Our `fringe-rate filtered' toy model dataset.
+It contains $25$ independent samples in time.
+Real parts are shown here.
+Right: Eigenspectrum of foregrounds only (blue), EoR only (red), and both (green).}
+	\label{fig:toy_sigloss5}
+\end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss7.png}
+	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the full inverse covariance weighted combined dataset (green) for a time-averaged dataset (fewer independent modes).}
+	\label{fig:toy_sigloss7}
+\end{figure}
+
+Applying full inverse covariance weighting to this dataset results in the power spectra shown in Figure \ref{fig:toy_sigloss7}.
+It is clear that there is a much larger amount of signal loss for this time-averaged dataset.
+The subtle drop-off in the eigenspectrum shape suggests that when the spectrum is inverted, a few modes are up-weighted more strongly than the rest.
+This means that most of our power spectrum information is coming from only the last few modes, and as a result, is a noisier estimate.
+This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} not only exhibits signal loss, but also fails to trace the shape of the unweighted EoR power spectrum.
+
+Using our toy model, we have shown that signal loss can arise from inverse covariance weighting due to unintentionally up-weighting eigenmodes with very small eigenvalues (overfitting the noise).
+We have also shown that this effect is made larger by reducing the total number of independent samples in a dataset.
+In reality, $21$ cm data from PAPER-64 exhibits $\sim3$ orders of magnitude of signal loss when combining the use of an optimal fringe-rate filter and full inverse covariance weighting.
+
+Going back to our time-averaged simulation data, we will now describe several ways to alter the covariance matrix $\textbf{C}$ in order to avoid signal loss.
+Recall that $\textbf{C}$ is computed from the dataset itself, leading to the up-weighting of very noisy, non-existent modes.
+In practice we compute $\textbf{C}$ this way because we do not know how to accurately model the matrix.
+But for our toy model, we know that our simulated, perfectly-noisy EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
+If we model $\textbf{C}_{EoR}$ as such and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting (instead of computing it based on $(\textbf{x}_{FG} + \textbf{x}_{EoR})$), we see that there is no signal loss (Figure \ref{fig:toy_sigloss8}, left).
+
+\begin{figure*}
+	\centering
+	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss10.png}
+	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss8.png}
+	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss9.png}
+	\caption{Power spectra of foregrounds only (blue), EoR only (red), and the weighted combined dataset (green).
+We show three alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (left), regularizing $\textbf{C}$ by adding an identity matrix to it (middle), and using only the first few eigenmodes of $\textbf{C}$ (right).}
+	\label{fig:toy_sigloss8}
+\end{figure*}
+
+\cc{add paragraph about regularization options}
+
+\subsection{Error Estimation}
+\label{sec:ErrorOverview}
+
+\subsection{Bias}
+\label{sec:BiasOverview}
+
+\section{Case Study: PAPER-64}
+\label{sec:CaseStudy}
+
+Now that we have developed our intuition regarding signal loss, error estimation, and bias, we will look at each in more detail as applied to data taken by PAPER.
+We begin with an overview of the telescope array, its observations, and analysis pipeline.
+
+\subsection{Observations}
 \label{sec:Obs}
@@
 	\centering
-	\includegraphics[height=0.35\textwidth]{paper_dipole.png}
-	\includegraphics[height=0.35\textwidth]{antenna_layout.png}
+	\includegraphics[height=0.35\textwidth]{plots/paper_dipole.png}
+	\includegraphics[height=0.35\textwidth]{plots/antenna_layout.png}
 	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
@@
 
-Finally, after removing an additional layer of RFI (values $3\sigma$ above the median), we average together all our data into two datasets: even julian dates and odd julian dates.
-A total of $124$ nights of data comprises this average, and we use these two datasets as a starting point for constructing power spectrum estimates.
+After removing an additional layer of RFI (values $3\sigma$ above the median), we average together all our data into two datasets: even julian dates and odd julian dates.
+A total of $124$ nights of data comprises this average.
 
-\section{Power Spectrum Analysis}
-\label{sec:PS}
-
-\subsection{Fringe-Rate-Filtering}
-\label{sec:FRF}
-
+Finally, our last analysis step before power spectrum estimation is the use of a fringe-rate filter.
 As shown in \citet{parsons_et_al2016}, a fringe-rate filter allows us to maximize our sensitivity even further by averaging visibilities in time.
@@
 This allows us to up-weight parts of the sky high in the primary beam, and down-weight those that are less sensitive.
-
-In \citet{ali_et_al2015}, the filter applied was degraded (widened in fringe-rate space) from an optimal one that can be constructed based on the integration time of the data.
-This was chosen to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying optimal quadratic estimators (OQE) on data with too few modes.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{frp.png}
-	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
-	\label{fig:frp}
-\end{figure}
-
-New to our updated PAPER-64 analysis is the use of the optimal fringe-rate filter, which maximizes our sensitivity.
-With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), resulting in an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
-
 In practice, the optimal fringe-rate profile is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
@@
 \subsection{Power Spectrum Estimation}
-\label{sec:PSEst}
+\label{sec:PS}
 
@@
 We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$) for each baseline and data group (`even' or `odd').
-As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups, where no baselines are repeated within or between groups.
-For the \citet{ali_et_al2015} method, each group is then sampled with replacement to create a new group, of the same size, that can have repeated baselines inside it.
-We discover that in doing so, we are sacrificing some of our sensitivity since this results in there being 3-4 repeated baselines per group.
-In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one.
-For example, if we have $10$ baselines in a group, we use the first $9$ to guarantee at least $9$ independent measurements, and then fill the last slot randomly out of the $10$.
-We do this for all $5$ groups.
-This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run for this analysis ($nboots = 20$).
-
-Taking $\textbf{x}$ to be averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets). We next form the quantity $\hat{q}_{\alpha}$:
+As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups.
+Taking $\textbf{x}$ to be averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets).
+We next form the quantity $\hat{q}_{\alpha}$:
 
@@
 
-The rest of the OQE formalism is identical to \citet{ali_et_al2015}. We normalize our power spectrum estimates using the matrix $\textbf{M}$:
+Finally, we normalize our power spectrum estimates using the matrix $\textbf{M}$:
 
@@
 We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.
-
-In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the bootstrap and time axes simultaneously.
-Random values are sampled with replacement along both axes, drawing as many values as there are number of bootstraps and times.
-Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis.
-
-However, we have found that this method greatly underestimates power spectrum errors, especially for fringe-rate filtered data.
-This can be explained by the fact that fringe-rate filtered data has a dramatically reduced number of independent modes.
-Hence, drawing $100$ samples out of a length-$100$ dataset that only has $5$ independent modes in it, for example, results in a narrower distribution of values that leads to a false error estimation.
-
-To avoid this issue, we instead take a simple average along the time axis. Our final power spectrum limits are computed by taking the mean and standard deviation over our single bootstrap axis.
-
-In summary, our power spectrum pipeline begins with data with four axes (datasets, baselines, times, frequencies), bootstraps over baselines, uses OQE formalism, and produces $1$-dimensional power spectra for both $\textbf{P(k)}$ and the folded version $\Delta^{2}\textbf{(k)}$, defined as:
+We form both the quantity $\textbf{P(k)}$ and the folded version $\Delta^{2}\textbf{(k)}$, defined as:
 
@@
 \end{equation}
+
+\section{Application: Signal Loss}
+\label{sec:Sigloss}
+
+\subsection{Noise and EoR}
 
@@
 
-\subsection{Power Spectrum Sensitivity}
-\label{sec:PSSense}
-
-\cc{Add info on sensitivity equation, how we calculate effective inttime and adjust beam factor because of FRF, etc.}
-
-\section{Signal Loss}
-\label{sec:Sigloss}
-
-\subsection{Formalism}
-\label{sec:Formalism}
+\subsection{Signal Loss Methodology}
 
@@
 
-\subsection{Application}
-\label{sec:siglossprac}
+\subsection{Signal Loss in Practice}
 
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{sigloss1_noise.png}
+	\includegraphics[width=1.0\textwidth]{plots/sigloss1_noise.png}
 	\caption{$P_{in}$ vs.
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{ps1_noise_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{ps1_noise.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_noise.png}
 	\caption{Full inverse covariance weighted power spectrum of pure noise (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{sigloss2_noise.png}
+	\includegraphics[width=1.0\textwidth]{plots/sigloss2_noise.png}
 	\caption{$P_{in}$ vs. $P_{out}$ (blue) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent cyan range of pCn values instead of just the max}}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{ps2_noise_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{ps2_noise.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_noise.png}
 	\caption{Full inverse covariance weighted power spectrum of pure noise (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
@@
 %	\centering
-%	\includegraphics[width=1.0\textwidth]{sigloss1_data.png}
+%	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
 %	\caption{$P_{in}$ vs.
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{sigloss2_data.png}
+	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
 	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent grey range of pCv values instead of just the max}}
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{ps2_data_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{ps2_data.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
 	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{eigenspectrum.png}
-	\includegraphics[width=0.4\textwidth]{covariance.png}
+	\includegraphics[width=0.4\textwidth]{plots/eigenspectrum.png}
+	\includegraphics[width=0.4\textwidth]{plots/covariance.png}
 	\caption{Eigenspectrum for $\textbf{C}$ for baseline (1,4) for the 21 channels ofs interest (left) and covariance matrix $\textbf{C}$ for the same baseline (right).}
@@
 
-\section{Jack-Knives}
-\label{sec:Jack}
+\section{Application: Error Estimation}
+\label{sec:Error}
+
+\subsection{Thermal Noise}
+
+\cc{Add info on sensitivity equation, how we calculate effective inttime and adjust beam factor because of FRF, etc.}
+
+\subsection{Bootstrapping}
+
+\cc{Include info about baseline bootstrapping:}
+For the \citet{ali_et_al2015} method, each group is then sampled with replacement to create a new group, of the same size, that can have repeated baselines inside it.
+We discover that in doing so, we are sacrificing some of our sensitivity since this results in there being 3-4 repeated baselines per group.
+In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one.
+For example, if we have $10$ baselines in a group, we use the first $9$ to guarantee at least $9$ independent measurements, and then fill the last slot randomly out of the $10$.
+We do this for all $5$ groups.
+This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run for this analysis ($nboots = 20$).
+
+\cc{Include info about second round of bootstrapping:}
+In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the bootstrap and time axes simultaneously.
+Random values are sampled with replacement along both axes, drawing as many values as there are number of bootstraps and times.
+Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis.
+
+However, we have found that this method greatly underestimates power spectrum errors, especially for fringe-rate filtered data.
+This can be explained by the fact that fringe-rate filtered data has a dramatically reduced number of independent modes.
+Hence, drawing $100$ samples out of a length-$100$ dataset that only has $5$ independent modes in it, for example, results in a narrower distribution of values that leads to a false error estimation.
+
+To avoid this issue, we instead take a simple average along the time axis. Our final power spectrum limits are computed by taking the mean and standard deviation over our single bootstrap axis.
+
+\section{Application: Bias}
+\label{sec:Bias}
+
+\cc{Include info about optimal FRF:}
+In \citet{ali_et_al2015}, the filter applied was degraded (widened in fringe-rate space) from an optimal one that can be constructed based on the integration time of the data.
+This was chosen to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying optimal quadratic estimators (OQE) on data with too few modes.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/frp.png}
+	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
+	\label{fig:frp}
+\end{figure}
+
+New to our updated PAPER-64 analysis is the use of the optimal fringe-rate filter, which maximizes our sensitivity.
+With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), resulting in an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
 

### 2017-07-06 PAPER.tex
finished section 2.1

@@
 We describe techniques that affect these themes using both a toy model and data taken by the 64-element configuration of the Donald C.
-Baker Precision Array for Probing the Epoch of Reionization (PAPER).
+Backer Precision Array for Probing the Epoch of Reionization (PAPER).
 \end{abstract}
@@
 
-By about one billion years after the Big Bang, the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the Universe's early life.
-This important transition, during which the first luminous structures formed from gravitational collapse and emit intense radiation, transforming the cold neutral gas into a plasma, is known as the epoch of reionization (EoR).
-The EoR represents an unexplored era in our cosmic dawn, whose history encodes important information regarding the nature of the first galaxies and the process of structure formation.
-A direct detection of the EoR would unlock powerful information about the intergalactic medium, revealing connections between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured web of galaxies we observe today.
+By about one billion years after the Big Bang, the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the baryonic matter content in the early Universe.
+This transition period, during which the first luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas into a plasma, is known as the epoch of reionization (EoR).
+The EoR is a relatively unexplored era in our cosmic dawn.
+Its history encodes important information regarding the nature of the first galaxies and the processes of structure formation.
+Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured web of galaxies we observe today.
 
 One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted by neutral hydrogen via its spin-flip transition.
-This technique is powerful because it can be observed as a function of redshift - that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space.
-The 21 cm line therefore offers a window into following the evolution of ionization, temperature, and density fluctuations on cosmic scales.
+This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space.
+The 21 cm line therefore offers a window into the evolution of ionization, temperature, and density fluctuations on cosmic scales.
 
-Although a detection of the EoR has not currently been made to-date, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen in order to place constraints on the brightness of the EoR.
+Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen to place constraints on the brightness of the EoR.
 Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are EDGES (\citealt{bowman2010}), the LWA (\citealt{ellingson_et_al2009}), LEDA (\citealt{greenhill_bernardi2012}), DARE (\citealt{burns2012}), SciHi (\citealt{voytek2014}), BIGHORNS (\citealt{sokolowski2015}), and SARAS (\citealt{patra2015}).
-Major interferometers, which seek to measure statistical power spectra, include the GMRT (\citealt{paciga_et_al2013}), LOFAR (\citealt{van_haarlem_et_al2013}), the MWA (\citealt{tingay_et_al2013}), the 21CMA (\citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
-The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that hopes to combine lessons learned from previous experiments and is forecasted to be able to make a successful \cc{?$\sigma$} detection with an eventual \cc{?} elements.
+Radio interferometers which seek to measure statistical power spectra include the GMRT (\citealt{paciga_et_al2013}), LOFAR (\citealt{van_haarlem_et_al2013}), the MWA (\citealt{tingay_et_al2013}), the 21CMA (\citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
+The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful $23\sigma$ detection with an eventual $350$ elements, using current analysis techniques (\citealt{deboer_et_al2017}, \citealt{pober_et_al2014}).
 
-The major challenge that faces all 21 cm experiments is in isolating a small signal that is buried underneath foregrounds and instrumental systematics that are 4-5 orders of magnitude brighter.
-A clean measurement therefore requires an intimate understanding of the instrument and a very careful, thorough understanding of data analysis choices.
-With HERA on the horizon and continual progress being made in the field, it is becoming increasingly more important to understand how the methods we choose affect each other and any power spectrum results.
-In this paper, we discuss three themes essential to a $21$ cm power spectrum study and how data analysis choices affect each.
-We approach these themes from both a broad perspective, and through a detailed case study using data from the 64-element configuration of PAPER.
+The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and instrumental systematics that are 4-5 orders of magnitude brighter.
+A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
+With continual progress being made in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact with each other to affect power spectrum results.
+In this paper, we discuss three themes essential to a $21$ cm power spectrum analysis and how data analysis choices affect each.
+We approach these themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER.
 
@@
 But for our toy model, we know that our simulated, perfectly-noisy EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting (instead of computing it based on $(\textbf{x}_{FG} + \textbf{x}_{EoR})$), we see that there is no signal loss (Figure \ref{fig:toy_sigloss8}, left).
+If we model $\textbf{C}_{EoR}$ as such and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting (instead of computing it based on $(\textbf{x}_{FG} + \textbf{x}_{EoR})$), we see that there is no signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
 
@@
 	\centering
-	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss10.png}
-	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss8.png}
-	\includegraphics[height=0.21\textwidth]{plots/toy_sigloss9.png}
+	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss10.png}
+	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss8.png}
+	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss9.png}
+	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss11.png}
 	\caption{Power spectra of foregrounds only (blue), EoR only (red), and the weighted combined dataset (green).
-We show three alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (left), regularizing $\textbf{C}$ by adding an identity matrix to it (middle), and using only the first few eigenmodes of $\textbf{C}$ (right).}
+We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first few eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).}
 	\label{fig:toy_sigloss8}
@@
 
-\cc{add paragraph about regularization options}
+The next three panels of Figure \ref{fig:toy_sigloss8} each involve methods that regularize the matrix $\textbf{C}$ after it is computed from the foreground + EoR dataset.
+By regularizing $\textbf{C}$, we are flattening out its eigenspectrum.
+Therefore, some modes will be down-weighted, but the rest will be treated with similar weights.
+In other words, we won't be up-weighting the last few noisy modes.
+
+Regularization schemes that we are highlighting here are adding an identity matrix to $\textbf{C}$ (Figure \ref{fig:toy_sigloss8}, upper right), killing all but the first three eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).
+Each avoids signal loss, but it is clear that two of the methods down-weight foregrounds much better than the third.
+For this toy model, our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
+Therefore, when multiplying $\textbf{C}$ by an identity matrix, we are only preserving correlations between the same frequencies.
+Hence, because we killed off information from all other frequency combinations, we do a poor job suppressing the foreground.
+
+Although this method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may work better than others based on the dataset.
+One may imagine a situation where a particular systematic is contained to an isolated frequency.
+In such a case, preserving only the diagonal elements of $\textbf{C}$ would be an effective way of removing this contamination.
+In Section \ref{sec:Sigloss}, we apply the lessons we've learned about signal loss and its interaction with fringe-rate filtering and inverse covariance weighting to PAPER-64 data.
 
@@
 The Donald C.
-Baker Precision Array for Probing the Epoch of Reionization (PAPER) is a dedicated 21 cm experiment located in the Karoo Desert in South Africa.
+Backer Precision Array for Probing the Epoch of Reionization (PAPER) is a dedicated 21 cm experiment located in the Karoo Desert in South Africa.
 The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements, each 2 m on a side.

### 2017-07-12 PAPER.tex
-Updated plots to minimize white space -Edited structure of Section 2.1 (made it more organized, divided into subsub sections) -Condensed Section 2 overview

@@
 Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen to place constraints on the brightness of the EoR.
-Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are EDGES (\citealt{bowman2010}), the LWA (\citealt{ellingson_et_al2009}), LEDA (\citealt{greenhill_bernardi2012}), DARE (\citealt{burns2012}), SciHi (\citealt{voytek2014}), BIGHORNS (\citealt{sokolowski2015}), and SARAS (\citealt{patra2015}).
-Radio interferometers which seek to measure statistical power spectra include the GMRT (\citealt{paciga_et_al2013}), LOFAR (\citealt{van_haarlem_et_al2013}), the MWA (\citealt{tingay_et_al2013}), the 21CMA (\citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
+Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES, \citealt{bowman2010}), the Long Wavelength Array (LWA, \citealt{ellingson_et_al2009}),  the Large Aperture Experiment to Detect the Dark Ages (LEDA, \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE, \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI, \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS, \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS, \citealt{patra2015}).
+Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT, \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR,\citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA, \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA, \citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
 The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful $23\sigma$ detection with an eventual $350$ elements, using current analysis techniques (\citealt{deboer_et_al2017}, \citealt{pober_et_al2014}).
@@
 
-A typical dataset for a $21$ cm experiment involves many axes.
-Visibility measurements, the standard data product for radio telescopes, are saved for many baselines and baseline-types.
-These visibilities are comprised of many integrations and a spectrum of frequency channels.
-Data collection can span months and years and can involve multiple polarizations.
-The data itself contains not only an EoR signal, but layers of bright foregrounds, radio frequency interference, instrumental noise, and other systematics.
+We seek to measure the statistical $21$ cm power spectrum.
+As such, we require robust methods that determine accurate confidence intervals and rigorous techniques to identify and suppress systematics.
+Additionally, because of the challenge in isolating a faint signal, we desire to maximize our sensitivity through filtering and weighting techniques.
 
-The job for $21$ cm data analysts is to sift through terabytes of data to ultimately make a power spectrum, a statistical result that encodes the variance of a dataset.
-In other words, a power spectrum measures the strength of the $21$ cm signal on various spatial scales of the sky, a powerful measurement that can be used to trace the evolution of neutral hydrogen during the EoR.
-There are, however, many data analysis choices that affect both the variance of the dataset itself and how it is measured.
+There are many choices for a data analyst, such as how to optimally combine time-ordered measurements, how to best and most accurately estimate its variance, and how to weight data in a way that suppresses contaminated modes while not destroying an EoR signal.
+Common techniques such as averaging data, weighting, bootstrapping, and jack-knife testing each affect data in different ways and reveal different lessons.
 
-Simply stated, we desire to maximize the sensitivity of a dataset as much as possible, while being confident about the result and able to account for irregularities.
-There are many choices as a data analyst, such as how to optimally combine time-ordered measurements, how to best and most accurately estimate its variance, and how to weight data in a way that suppresses uninteresting modes while not destroying an EoR signal.
-Common techniques such as averaging data, inverse covariance weighting, bootstrapping, and jack-knife testing each affect data in different ways and reveal different lessons.
+There are tradeoffs between these power spectrum techniques which impact resulting limits.
+For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing the EoR signal.
+A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
 
-There are often tradeoffs between techniques. For example, \cc{cite papers such as Josh's}.
-
-In this paper, we focus on four power spectrum techniques and their affect on three umbrella $21$ cm power spectrum themes.
+In this paper, we focus on four power spectrum techniques and their effect on three overarching $21$ cm power spectrum themes.
 We will give brief definitions now, and build intuition for each theme in the sections to follow.
-
-\begin{center}
-Power Spectrum Techniques
-\end{center}
-\begin{itemize}
-\item \textbf{Fringe-rate filtering:} The concept of a fringe-rate filter is similar to averaging data in time.
-We explain our filter in more detail in Section \ref{sec:CaseStudy}, but a broad description is that a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
-\item \textbf{Inverse covariance weighting:} Of the same flavor as inverse variance weighting, inverse covariance weighting weights a dataset by minimizing the covariance between frequency channels.
-This weighting has the effect of down-weighting correlated information and up-weighting noise-like information.
-\item \textbf{Bootstrapping:} This is a useful method for estimating errors of a dataset from itself. By randomly drawing samples of the data, the spread in those numbers gives us our errors.
-\item \textbf{Jack-Knife testing:} A resampling technique useful for estimating bias, jack-knives can be taken along different dimensions of a dataset to cross-validate results.
-\end{itemize}
 
@@
 
+\begin{center}
+Power Spectrum Techniques
+\end{center}
+\begin{itemize}
+\item \textbf{Fringe-rate filtering:} The concept of a fringe-rate filter is similar to averaging data in time.
+We explain our filter in more detail in Section \ref{sec:CaseStudy}, but a broad description is that a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
+\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others.
+One particular flavor of weighting is inverse covariance weighting, which weights a dataset by minimizing the covariance between frequency channels.
+This weighting has the effect of down-weighting correlated information (i.e.
+foregrounds) and up-weighting noise-like information (i.e.
+EoR).
+\item \textbf{Bootstrapping:} This is a useful method for estimating errors of a dataset from itself. By randomly drawing many samples of the data, we get a sense of its inherent variance.
+\item \textbf{Jack-Knife testing:} A resampling technique useful for estimating bias, jack-knives can be taken along different dimensions of a dataset to cross-validate results.
+\end{itemize}
+
 We will now discuss the three themes more in depth and discuss how certain power spectrum techniques affect each.
@@
 Signal loss refers to the loss of a cosmological signal in a dataset.
-It can arise in a variety of ways at multiple stages in an analysis pipeline.
-Here we focus on signal loss originating from empirically estimating covariance matrices, a method that succeeds in down-weighting foregrounds but can carry the risk of large amounts of signal loss.
-We will develop our intuition and motivate the effect of signal loss using a toy model simulation.
+It can arise through a variety of ways in an analysis pipeline, such as fitting a polynomial during calibration or applying a delay-domain filter.
+Here we focus on signal loss associated with applying a weight matrix to data.
+Driven by sensitivity needs, we would like to use a weighting method that succeeds in down-weighting foregrounds.
+However, as we'll investigate, this can carry the risk of large amounts of signal loss.
 
-Suppose we have a very simple dataset which contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
-The data is comprised of a sine-wave foreground that varies in time, and a complex, random-noise EoR signal (Figure \ref{fig:toy_sigloss1}, left).
+Before we demonstrate how different weighting matrices affect signal loss, we first recap how weights are related to the power spectrum estimation technique of optimal quadratic estimators (OQE, \citealt{liu_et_al2014b}).
+A summary of the method is as follows.
+
+We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$). We form the quantity $\hat{q}_{\alpha}$:
+
+\begin{equation}
+\label{eq:qhat}
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{x}
+\end{equation}
+
+where $\textbf{w}$ is a weighting matrix (for example, inverse covariance weighting would set $\textbf{w} = \textbf{C}^{-1}$).
+The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
+The index $\alpha$ represents each $k_{\parallel}$ bin, where $k_{\parallel}$ is the Fourier-dual to frequency.
+
+We normalize our power spectrum estimates using the matrix $\textbf{M}$:
+
+\begin{equation}
+\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}}
+\end{equation}
+
+where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+
+\begin{eqnarray}
+\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{Q}_{\beta}). 
+\end{eqnarray}
+
+We have a choice for $\textbf{M}$, and for simplicity in this section we set $\textbf{M} = \textbf{I}$, the identity matrix.
+This is not the case for the analysis of PAPER-64 data, which we describe in Section \ref{sec:PS}.
+Together, $\textbf{M}$ and $\textbf{F}$ form our window function:
+
+\begin{eqnarray}
+\textbf{W} = \textbf{MF}.
+\end{eqnarray}
+
+Finally, our final power spectrum is:
+
+\begin{equation}
+\textbf{p} = \textbf{W}\hat{\textbf{p}}.
+\end{equation}
+
+In the next sections, we will experiment with different weighting matrices $\textbf{w}$ and their impact on the resulting power spectra $\textbf{p}$.
+
+\subsubsection{Toy Model: Inverse Covariance Weighting}
+
+One choice for a weight matrix $\textbf{w}$ is an inverse covariance matrix.
+This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds.
+The covariance matrix $\textbf{C}$ is empirically derived from a data vector $\textbf{x}$ and defined as:
+
+\begin{equation}
+\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle,
+\end{equation}
+
+assuming $\langle\textbf{x}\rangle = 0$. The inverse covariance matrix is therefore $\textbf{C}^{-1}$.
+
+Because $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and destroying signal.
+In contrast to $\textbf{C}$, another choice for a weighting matrix is the identity matrix $\textbf{I}$.
+We will refer to this choice as `unweighted', since using the identity does not alter (doesn't upweight or downweight) the data at all, and therefore does not have signal loss.
+
+We will now build our intuition into how inverse covariance weighting can lead to signal loss through the use of a toy model.
+Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
+This model represents realistic dimensions of an $\sim$hour of PAPER data which could be used for a power spectrum analysis.
+We create a fake bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a fake EoR signal, $\textbf{x}_{EoR}$, as complex, random-noise.
+Adding the two together forms our combined dataset, $\textbf{x}$, which we will be applying different weighting schemes to.
+The three data vectors are shown on the left in Figure \ref{fig:toy_sigloss1}, and our ultimate goal is to suppress the foregrounds perfectly without destroying EoR.
 
@@
 	\centering
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss1.png}
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss2.png}
+	\includegraphics[trim={0.3cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss1.png}
+	\includegraphics[trim={0.3cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss2.png}
 	\caption{Left: Our toy model dataset contains a sine-wave foreground that varies in time and random noise as an EoR signal.
@@
 
-Before we demonstrate how signal loss can arise, we first look at the eigenspectrum of the covariance matrix that describes our data.
-That is, if $\textbf{x}$ is our dataset which contains both the foreground and EoR, its covariance matrix is empirically defined as $\textbf{C} \equiv \textbf{xx}^{\dagger}$.
-The eigenspectrum, which encodes useful information about the strengths of different frequency modes, is shown in the right plot of Figure \ref{fig:toy_sigloss1}.
-It is obvious that there is only 1 eigenmode in the foreground-only dataset (since we used one sine-wave), and therefore most of the information in our combined dataset is contained in the first mode.
-
-We would like to use inverse covariance weighting to down-weight the foregrounds in our dataset.
-To do so, we compute $\textbf{C}^{-1}$ and use optimal quadratic estimators (see Section \ref{sec:PS} for more details) to Fourier-transform our data along the `frequency' axis and form a power spectrum.
-As an explicit check, we use information from only the first eigenmode, and zero out the others.
-We do this because we know that the foregrounds can be perfectly described by only the first mode, so it should be all that we need to down-weight them.
-
-Figure \ref{fig:toy_sigloss3} shows the unweighted (using the identity matrix $\textbf{I}$ instead of $\textbf{C}$) power spectrum for the foreground-only data in blue, the unweighted power spectrum for the EoR-only data in red, and the weighted power spectrum for the combined dataset in green.
-There is one peak in blue from our one foreground mode.
+We compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\textbf{C}^{-1}$.
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
+Also plotted in the figure are the unweighted power spectrum of $\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
 
@@
 	\centering
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss4.png}
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss3.png}
+	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
+	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
 	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the combined dataset (green).
-Contrasted are the effect of using information from the first eigenmode only (left), and full inverse covariance weighting (right).}
+Contrasted are the effect of using inverse covariance weighting (left) and information from the first eigenmode only (right).}
 	\label{fig:toy_sigloss3}
@@
 
-From the left plot, we see that by down-weighting the first mode, we can perfectly recover EoR.
+Examining this case, our inverse covariance weighted result successfully suppresses foregrounds.
 This is in principle the reason why inverse covariance weighting is so attractive for $21$ cm data.
-If we could perfectly model our foregrounds, we could down-weight them without any signal loss.
-However, this is not the case in reality, since we can't distinguish between foreground and EoR modes.
+It is also evident that our result almost recovers the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
+This is actually evidence of a small amount of signal loss.
+In order to understand how this occurs, we need to closely study our covariance matrix $\textbf{C}$.
 
-If we did not know that our foreground information is contained in only one mode, a naive approach would be to use full inverse covariance weighting (using information from all eigenmodes).
-Examining this case, our full inverse covariance weighted result (Figure \ref{fig:toy_sigloss3}, right) almost recovers the EoR signal.
-It exhibits the correct shape, but the amplitude level is slightly low.
-This is actually evidence of a small amount of signal loss.
-In this toy model, the amount of signal loss is small, but we can exaggerate the effect and investigate its cause by `fringe-rate filtering' our toy model dataset.
+It turns out that the eigenspectrum of $\textbf{C}$ offers a window into understanding how inverse covariance weighting affects data.
+An eigenspectrum ranks the eigenvalues of $\textbf{C}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
+The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
 
-Since fringe-rate filtering is similar in practice to averaging in time, we average every $4$ time integrations together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
+For our toy model, the eigenspectra of $\textbf{C}_{FG}$, $\textbf{C}_{EoR}$, and $\textbf{C}$ are shown in the right plot of Figure \ref{fig:toy_sigloss1}.
+The blue curve peaks only at the zeroth eigenmode, revealing that the foregrounds can be described by a single eigenmode.
+This is a direct consequence of how it was constructed (only one sinusoid).
+In fact, the blue peak in Figure \ref{fig:toy_sigloss3} is also a direct result of our foreground's construction.
+The eigenspectrum of EoR, however, is fairly flat, signifying that its covariance matrix is similar to an identity matrix.
+This makes sense because the EoR signal consists of random noise, which should only have strong frequency-frequency correlations when two frequencies are the same.
+
+The eigenmodes with the highest eigenvalues will be down-weighted the most (i.e.
+when the spectrum is inverted, they will be given the smallest weights).
+In contrast, the modes with the smallest eigenvalues will be up-weighted the most.
+In other words, if an eigenspectrum is not perfectly flat, all modes will be given different weights and it is possible to up-weight a few modes much more than others.
+The subtle slope of the eigenspectrum in this toy example gives rise to a small amount of signal loss because it is possible to overfit a few modes (the highest weighted ones) ever so slightly.
+We will see in the next section how this effect can be exaggerated as the `steepness' of the spectrum changes.
+
+Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss.
+Namely, we can zero out all eigenmodes except the first one, thereby down-weighting the foregrounds perfectly and nothing else.
+The result is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
+In this case, we perfectly recover EoR, demonstrating that if we can perfectly model our foregrounds, we can down-weight them without signal loss.
+However, this is not the case in reality since we aren't able to distinguish between foreground and EoR modes.
+
+\subsubsection{Toy Model: Fringe-Rate Filtering}
+
+We have shown how signal loss can arise due to unintentionally up-weighting eigenmodes with small eigenvalues (overfitting the noise).
+We will next show how this effect is exaggerated with a reduction of the total number of independent samples in a dataset.
+
+A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
+To mimic this filter, we average every $4$ time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
 We choose these numbers so that the total number of independent samples is similar to the number of frequency channels (our matrices will be full rank).
-The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss1}, begin to fall for the last few eigenmodes.
-Although a subtle feature, it has large consequences on the resulting power spectra.
+The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss1}, fall more steeply for last few eigenmodes.
+This shape has large consequences on the resulting power spectra.
 
@@
 	\centering
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[height=0.3\textwidth]{plots/toy_sigloss6.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
 	\caption{Left: Our `fringe-rate filtered' toy model dataset.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
 	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the full inverse covariance weighted combined dataset (green) for a time-averaged dataset (fewer independent modes).}
@@
 
-Applying full inverse covariance weighting to this dataset results in the power spectra shown in Figure \ref{fig:toy_sigloss7}.
-It is clear that there is a much larger amount of signal loss for this time-averaged dataset.
-The subtle drop-off in the eigenspectrum shape suggests that when the spectrum is inverted, a few modes are up-weighted more strongly than the rest.
-This means that most of our power spectrum information is coming from only the last few modes, and as a result, is a noisier estimate.
-This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} not only exhibits signal loss, but also fails to trace the shape of the unweighted EoR power spectrum.
+Applying inverse covariance weighting to this dataset results in the power spectra shown in Figure \ref{fig:toy_sigloss7}.
+There is a much larger amount of signal loss for this time-averaged dataset.
+To reiterate, the drop-off in the eigenspectrum shape suggests that when the spectrum is inverted, a few modes are up-weighted much more strongly than the rest.
+This dramatic up-weighting drowns out the EoR signal, giving rise to signal loss.
+Additionally, most of our power spectrum information is coming from only the last few modes and as a result, is a noisier estimate.
+This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
 
-Using our toy model, we have shown that signal loss can arise from inverse covariance weighting due to unintentionally up-weighting eigenmodes with very small eigenvalues (overfitting the noise).
-We have also shown that this effect is made larger by reducing the total number of independent samples in a dataset.
-In reality, $21$ cm data from PAPER-64 exhibits $\sim3$ orders of magnitude of signal loss when combining the use of an optimal fringe-rate filter and full inverse covariance weighting.
+Using our toy model, we have seen that a sensitivity driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates.
+Longer integrations increase sensitivity but reduce the number of independent samples, resulting in steep drop-offs in eigenspectra.
+For PAPER-64 data, we see $\sim3$ orders of magnitude of signal loss when combining the use of an optimal fringe-rate filter and inverse covariance weighting.
 
-Going back to our time-averaged simulation data, we will now describe several ways to alter the covariance matrix $\textbf{C}$ in order to avoid signal loss.
-Recall that $\textbf{C}$ is computed from the dataset itself, leading to the up-weighting of very noisy, non-existent modes.
-In practice we compute $\textbf{C}$ this way because we do not know how to accurately model the matrix.
-But for our toy model, we know that our simulated, perfectly-noisy EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting (instead of computing it based on $(\textbf{x}_{FG} + \textbf{x}_{EoR})$), we see that there is no signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+\subsubsection{Toy Model: Other Weighting}
+
+In a previous section we showed how altering an eigenspectrum can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
+We will now use our toy model to describe several other ways to alter a covariance matrix $\textbf{C}$ in order to minimize signal loss.
+
+As a first test, we know that our simulated EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
+If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
 
@@
 	\centering
-	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss10.png}
-	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss8.png}
-	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss9.png}
-	\includegraphics[height=0.25\textwidth]{plots/toy_sigloss11.png}
+	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss10.png}
+	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss8.png}
+	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss9.png}
+	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss11.png}
 	\caption{Power spectra of foregrounds only (blue), EoR only (red), and the weighted combined dataset (green).
@@
 Therefore, some modes will be down-weighted, but the rest will be treated with similar weights.
-In other words, we won't be up-weighting the last few noisy modes.
+Hence, we won't be up-weighting the last few noisy modes.
 
@@
 Therefore, when multiplying $\textbf{C}$ by an identity matrix, we are only preserving correlations between the same frequencies.
-Hence, because we killed off information from all other frequency combinations, we do a poor job suppressing the foreground.
+Because we killed off information from all other frequency combinations, we do a poor job suppressing the foreground.
 
@@
 In such a case, preserving only the diagonal elements of $\textbf{C}$ would be an effective way of removing this contamination.
+
+In summary, we have a choice of how to weight $21$ cm data.
+Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal.
+Inverse covariance weighting is an optimal weighting for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss.
+The application of a fringe-rate filter heightens this effect by reducing the number of independent samples and steepening eigenspectra further.
+Rather than use inverse covariance weighting, there are several alternate ways to regularize covariance matrices and flatten out eigenspectra to minimize signal loss.
 In Section \ref{sec:Sigloss}, we apply the lessons we've learned about signal loss and its interaction with fringe-rate filtering and inverse covariance weighting to PAPER-64 data.
@@
 
+Two ways of estimating errors on a power spectrum measurement are exploring the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
+In a perfect world, both methods would match up.
+However, in practice the two don't always agree due to contaminates in the data that prevent it from being perfectly noise-limited.
+Therefore, it is important to place error bars on our measurements that have been derived from its inherent variance.
+
+A common technique used to estimate the variance in a dataset is bootstrapping.
+Bootstrapping is a metric that relies on sampling with replacement and allows the estimation of a sampling distribution.
+For example, power spectrum measurements of $21$ cm data can be made along many axes, including time and baselines.
+Through the process of bootstrapping, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
+
+Again, we focus on simple toy models to highlight two traps that one can fall into when bootstrapping power spectra.
+Suppose we have a Gaussian random noise dataset of length $1000$ and variance of $1$.
+We are interested in the average of the dataset, and therefore predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples (in this case, $1000$).
+
+We form $100$ bootstraps, each comprised of an array of length $1000$ that is created by random sampling the original data with replacement.
+The standard deviation over the $100$ bootstraps gives an error estimation for our dataset.
+As shown in Figure \ref{fig:toy_error1} (grey star), the error computed from bootstrapping matches our theoretical prediction.
+
+One major caveat of bootstrapping is that the method is no longer valid when working with correlated data.
+In other words, bootstrapping assumes completely independent samples.
+Therefore, the use of a fringe-rate filter, which averages data in time to increase sensitivity, creates a situation in which bootstrapping can under-estimate errors.
+
+Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent samples to $1000/10 = 100$.
+Bootstrapping this time-averaged noise, using the same exact method as described earlier (drawing the same number of samples as the length of the dataset), under-estimates the error by a factor of $\sim3$.
+This occurs because we are drawing more samples than independent ones available.
+In fact, the error derived from bootstrapping is a strong function of the number of samples that are drawn (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
+However, in this case we know that we have $100$ independent samples, and the error associated with drawing $100$ samples with replacement does match the theoretical prediction as expected.
+
+This examples highlights the importance of understanding how analysis techniques (like a fringe-rate filter) can affect a common statistical procedure (like bootstrapping).
+Bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires precise knowledge of the number of independent samples, which is not a trivial task.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
+	\caption{Error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
+The grey star represents the error associated with drawing $1000$ samples from a length $1000$ array of random noise.
+The black points correspond to time-averaged data and illustrate how errors can be underestimated if drawing more samples than independent ones in the data.
+There are $100$ independent samples in the time-averaged data and using this number does indeed match the theoretical error prediction.}
+	\label{fig:toy_error1}
+\end{figure}
+
+We will now discuss a second subtle feature of bootstrapping that can lead to an over-estimation of errors.
+Suppose we have $1000$ baselines (another appropriate axis for bootstrapping power spectra), each an independent measurement of the sky.
+Bootstrap theory requires a bootstrap to comprise of some combination of the $1000$ baselines.
+If all $1000$ spaces are filled randomly, there is in fact a high probability that baselines will be repeated in a sample (sometimes many times).
+Thus, bootstrapping in this way negatively affects power spectrum sensitivity because the number of independent baselines in a sample can be significantly lower than the total number of baselines.
+
+In order to maximize sensitivity, we use a slightly modified bootstrapping method.
+We first shuffle all the baselines for a bootstrap, take the first $999$, and then fill the last slot randomly with replacement.
+There's a small chance it will yield $1000$ independent samples, but even with $999$ our sensitivity is nearly maximized.
+One may wonder whether this change is still a legitimate way of error estimating since the number of possible random samples for a single bootstrap has dramatically decreased.
+However, as long as this number is still much greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
+
+For our toy model, the fraction of independent baselines using this method ($999/1000$) is over $1.5$ times greater than the aforementioned approach.
+These two methods converge for small numbers of samples, when filling a few spots randomly is nearly the same as filling only the last spot randomly.
+The evolution of both of these methods as a function of number of baselines is shown in Figure \ref{fig:toy_error2}.
+In order to reduce the number of baselines, we divide our $1000$ baselines into $N$ groups, where the number of baselines in a group is $1000/N$.
+No baselines are repeated within or between groups, until a bootstrapping method is applied to each (either sampling all elements with replacement, or only the last one).
+
+It is clear that the fraction of independent baselines in a group is always greater using our new sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group).
+An analog for the y-axis in Figure \ref{fig:toy_error2} is the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.
+
+In summary, bootstrapping is still an effective and straightforward way to estimate errors of a dataset.
+However, one must be careful about violating independence assumptions, as it is possible to under-estimate errors by over-sampling data.
+Additionally, small changes in the way datasets are randomly sampled can ensure that the overall sensitivity is maximized.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
+	\caption{Fraction of independent baselines in a baseline group as a function of the number of baselines in a group.
+A fraction of $1.0$ means that all baselines in a group are independent, and therefore sensitivity is maximized (alternatively, this axis can be treated as a power spectrum sensitivity in temperature-squared space).
+Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
+The former over-estimates error bars by not maximizing baseline sensitivity to its full capacity.}
+	\label{fig:toy_error2}
+\end{figure}
+
+We have discussed the interplay between two of our power spectrum techniques --- fringe-rate filtering and bootstrapping --- and how they affect the theme of error bar estimation.
+In addition to these, inverse covariance weighting can also affect error bars.
+Specifically, a power spectrum measurement and its errors are susceptible to blowing up when the number of non-zero eigenmodes are less than the number of independent samples in a dataset (i.e.
+the covariance matrix is not full rank).
+\cc{Not really sure how to explain this or how much detail to get into here...}
+
+Our fourth power spectrum technique, jack-knife testing, is also related to error estimation.
+Splitting data along various axes and performing the same power spectrum analysis on each provides a test of robustness.
+If the same errors are obtained for each data subset, we can have confidence that they are unbiased.
+
 \subsection{Bias}
 \label{sec:BiasOverview}
+
+As alluded to in the previous section, jack-knife testing is a powerful way to tease out biases by studying how power spectrum measurements of different subsets of data vary.
+Biases can arise due to...
 
@@
 
-To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as described by \cc{??}. A summary of the method is as follows.
+To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as summarized in Section \ref{sec:SiglossOverview}.
+Here we will describe its application to PAPER-64 data.
 
-We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$) for each baseline and data group (`even' or `odd').
+We have a $2$-dimensional data vector $\textbf{x}$ for each baseline and data group (`even' or `odd').
 As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups.
 Taking $\textbf{x}$ to be averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets).
-We next form the quantity $\hat{q}_{\alpha}$:
 
-\begin{equation}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{x}-b_{\alpha}
-\end{equation}
+We use a weight matrix of $\textbf{w} = \cc{???}$ in our analysis.
 
-where $\textbf{C}$ is the covariance matrix defined to be $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$.
-The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
-A noise bias $b_{\alpha}$ is subtracted off.
-The index $\alpha$ represents each $k_{\parallel}$ bin, where $k_{\parallel}$ is the Fourier-dual to frequency.
-
-Notice that there are two quantities of $\textbf{C}^{-1}\textbf{x}$ in the expression for $\hat{q}$, representing two copies of inverse covariance weighted data.
+Notice that there are two quantities of $\textbf{w}\textbf{x}$ in the expression for $\hat{\textbf{q}}$ in Equation \ref{eq:qhat}, representing two copies of weighted data.
 We perform all possible cross-multiplications of this quantity, except between the same datasets (`even' with `even', for example) and same groups (`baseline group 1' with `baseline group 1', for example).
@@
 
-Finally, we normalize our power spectrum estimates using the matrix $\textbf{M}$:
-
-\begin{equation}
-\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}}
-\end{equation}
-
-where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
-
-\begin{eqnarray}
-\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{C}^{-1}\textbf{Q}_{\alpha}\textbf{C}^{-1}\textbf{Q}_{\beta}). \\
-\end{eqnarray}
-
-We have a choice for $\textbf{M}$, and we choose to compute it by taking the Cholesky decomposition of $\textbf{F}$.
+As mentioned previously, we have a choice for our normalization matrix $\textbf{M}$.
+For our analysis, we choose to compute it by taking the Cholesky decomposition of $\textbf{F}$.
 Namely, we decompose the Fisher matrix such that $\textbf{F} = \textbf{L}\textbf{L}^{\dagger}$, where $\textbf{L}$ is a lower triangular matrix.
@@
 
-Finally, our final power spectrum is:
-
-\begin{equation}
-\hat{\textbf{p}} = \textbf{Wp}
-\end{equation}
-
-In practice, we end up with a 2-dimensional power spectrum quantity, which is a function of both time and $k$.
+In practice, our final power spectrum result is a $2$-dimensional quantity (a function of both time and $k$).
 We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.

### 2017-07-15 PAPER.tex
-Fleshed out bias overview section -Made edits from Aaron for Section 2 overview and part of Section 2.1

@@
 
-We seek to measure the statistical $21$ cm power spectrum.
-As such, we require robust methods that determine accurate confidence intervals and rigorous techniques to identify and suppress systematics.
-Additionally, because of the challenge in isolating a faint signal, we desire to maximize our sensitivity through filtering and weighting techniques.
-
-There are many choices for a data analyst, such as how to optimally combine time-ordered measurements, how to best and most accurately estimate its variance, and how to weight data in a way that suppresses contaminated modes while not destroying an EoR signal.
-Common techniques such as averaging data, weighting, bootstrapping, and jack-knife testing each affect data in different ways and reveal different lessons.
-
-There are tradeoffs between these power spectrum techniques which impact resulting limits.
-For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing the EoR signal.
+There are many choices for a data analyst, such as how to combine time-ordered measurements, how to estimate its variance, how to weight data in a way that suppresses contaminated modes while not destroying an EoR signal, and how to identify the source of a detection.
+Many common techniques, such as averaging data, weighting, bootstrapping, and jack-knife testing, each address these issues yet harbor additional trade-offs.
+For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing some EoR signal.
 A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
 
-In this paper, we focus on four power spectrum techniques and their effect on three overarching $21$ cm power spectrum themes.
+Measuring the statistical $21$ cm power spectrum requires robust methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.
+Additionally, we desire to maximize our sensitivity with filtering and weighting techniques.
+In this paper, we focus on four techniques and their effects on three overarching themes of $21$ cm power spectrum estimation.
 We will give brief definitions now, and build intuition for each theme in the sections to follow.
@@
 \begin{itemize}
-\item \textbf{Signal Loss:} As explained in the next session, there are analysis techniques that can lead to the loss of an EoR signal.
+\item[] The accuracy and interpretation of a $21$ cm power spectrum can be encompassed in the following three themes.
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): As explained in the next section, certain analysis techniques can lead to the loss of the EoR signal.
 If not corrected for, it could lead to a false non-detection.
-Computing signal loss has subtle challenges but is a crucial component for confidence in any result.
-\item \textbf{Error Bar Estimation:} Errors on a $21$ cm power spectrum result can make the difference between a detection and a noise-like measurement, which have two very different implications.
+Computing signal loss has subtle challenges but is crucial to the accuracy of any result.
+\item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
 Errors can be estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias:} There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum.
-It is important to identity them in order to interpret results and develop techniques to suppress contamination.
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum, such as bias from noise and foregrounds.
+Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR.
+In this paper we will highlight some sources of bias and discuss ways to mitigate its effects.
 \end{itemize}
@@
 \begin{itemize}
-\item \textbf{Fringe-rate filtering:} The concept of a fringe-rate filter is similar to averaging data in time.
-We explain our filter in more detail in Section \ref{sec:CaseStudy}, but a broad description is that a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
-\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others.
+\item[] The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
+However, they also have limitations and circumstances in which there are trade-offs.
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering can be considered an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
+However, it can also affect the presence of foregrounds and systematics.
+\item \textbf{Weighting:} A dataset can be weighted to emphasize certain spectral features and minimize others.
 One particular flavor of weighting is inverse covariance weighting, which weights a dataset by minimizing the covariance between frequency channels.
@@
 EoR).
-\item \textbf{Bootstrapping:} This is a useful method for estimating errors of a dataset from itself. By randomly drawing many samples of the data, we get a sense of its inherent variance.
+However, one challenge of weighting is in accurately determining a covariance matrix that best describes the data.
+\item \textbf{Bootstrapping:} Because applying theoretical errors to a $21$ cm measurement are insufficient \cc{why?}, bootstrapping is a useful method for estimating errors of a dataset from itself.
+By randomly drawing many samples of the data, we get a sense of its inherent variance, though there are subtleties to consider such as bootstrapping sample sizes.
 \item \textbf{Jack-Knife testing:} A resampling technique useful for estimating bias, jack-knives can be taken along different dimensions of a dataset to cross-validate results.
+In particular, null tests can be used to verify whether results are free of systematics (\citealt{keating_et_al2016}).
 \end{itemize}
 
-We will now discuss the three themes more in depth and discuss how certain power spectrum techniques affect each.
+In the next three subsections, we go into each theme in depth, focusing on how power spectrum technique trade-offs affect each.
+We use a toy data model to develop intuition into why certain analysis choices may be appealing and discuss ways in which they are limited.
+We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues.
+Ultimately, \cc{some kind of summarizing sentence here}.
 
@@
 
-Signal loss refers to the loss of a cosmological signal in a dataset.
-It can arise through a variety of ways in an analysis pipeline, such as fitting a polynomial during calibration or applying a delay-domain filter.
-Here we focus on signal loss associated with applying a weight matrix to data.
-Driven by sensitivity needs, we would like to use a weighting method that succeeds in down-weighting foregrounds.
-However, as we'll investigate, this can carry the risk of large amounts of signal loss.
+Signal loss refers to the attenuation of the target cosmological signal in a dataset.
+It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during spectral calibration, applying a delay-domain filter, or by weighting data by itself.
+Here we focus on signal loss associated with applying a weighting matrix to data.
+Driven by the need to mitigate foreground bias, we would like to use a weighting method that succeeds in down-weighting foregrounds.
+However, as we'll investigate, this carries the risk of large amounts of signal loss.
 
@@
 
-We begin with our data vector $\textbf{x}$, which contains our visibilities that have the shape ($times$, $frequencies$). We form the quantity $\hat{q}_{\alpha}$:
+We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in mK that have the shape ($times$, $frequencies$).
+We form the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
 
@@
 
-where $\textbf{w}$ is a weighting matrix (for example, inverse covariance weighting would set $\textbf{w} = \textbf{C}^{-1}$).
+where $\textbf{w}$ \cc{change to capital letter that isn't taken yet!} is a weighting matrix (for example, inverse covariance weighting would set $\textbf{w} = \textbf{C}^{-1}$).
 The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
-The index $\alpha$ represents each $k_{\parallel}$ bin, where $k_{\parallel}$ is the Fourier-dual to frequency.
+The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency.
 
@@
 
-where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum $\textbf{p}$. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum . We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
 
 \begin{eqnarray}
-\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr(\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{Q}_{\beta}). 
+\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr[\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{Q}_{\beta}]. 
 \end{eqnarray}
 
-We have a choice for $\textbf{M}$, and for simplicity in this section we set $\textbf{M} = \textbf{I}$, the identity matrix.
-This is not the case for the analysis of PAPER-64 data, which we describe in Section \ref{sec:PS}.
-Together, $\textbf{M}$ and $\textbf{F}$ form our window function:
+We have a choice for $\textbf{M}$, and for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, the identity matrix.
+This is not the case for the analysis of PAPER-64 data, which we describe in Section \cc{not sure which section to point to yet} as part of the discussion of bias.
 
-\begin{eqnarray}
-\textbf{W} = \textbf{MF}.
-\end{eqnarray}
-
-Finally, our final power spectrum is:
-
-\begin{equation}
-\textbf{p} = \textbf{W}\hat{\textbf{p}}.
-\end{equation}
-
-In the next sections, we will experiment with different weighting matrices $\textbf{w}$ and their impact on the resulting power spectra $\textbf{p}$.
+In the next sections, we will experiment with different weighting matrices $\textbf{w}$ and their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
 
@@
 
+To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss through the use of a toy model.
+Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
+This model represents realistic dimensions of about an hour of PAPER data which could be used for a power spectrum analysis.
+We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a mock EoR signal, $\textbf{x}_{EoR}$, as complex, random Gaussian noise.
+The sum of the two forms our combined data vector, $\textbf{x}$, to which we will be applying different weighting schemes.
+The three data vectors are shown on in Figure \ref{fig:toy_sigloss1}.
+Our ultimate goal in experimenting with weighting is to suppress the foregrounds perfectly without destroying EoR.
+
 One choice for a weight matrix $\textbf{w}$ is an inverse covariance matrix.
 This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds.
-The covariance matrix $\textbf{C}$ is empirically derived from a data vector $\textbf{x}$ and defined as:
+The covariance matrix $\textbf{C}$, which describes covariances between frequency channels, can be estimated in a variety of ways.
+Should we have perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our real data.
+However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the real foregrounds in the data.
+One attractive way to estimate $\textbf{C}$ then is to empirically derive it from the data vector $\textbf{x}$ itself:
 
@@
 
-assuming $\langle\textbf{x}\rangle = 0$. The inverse covariance matrix is therefore $\textbf{C}^{-1}$.
+assuming $\langle\textbf{x}\rangle = 0$. The inverse covariance matrix is therefore $\textbf{w} = \textbf{C}^{-1}$.
 
-Because $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and destroying signal.
-In contrast to $\textbf{C}$, another choice for a weighting matrix is the identity matrix $\textbf{I}$.
-We will refer to this choice as `unweighted', since using the identity does not alter (doesn't upweight or downweight) the data at all, and therefore does not have signal loss.
+If $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal.
+If instead we choose $\textbf{w} = \textbf{I}$, the identity matrix, there will be no signal loss (although it may suffer from foreground or instrumental bias).
+We will refer to this choice as `unweighted', since using the identity does not alter (doesn't upweight or downweight) the data at all.
 
-We will now build our intuition into how inverse covariance weighting can lead to signal loss through the use of a toy model.
-Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
-This model represents realistic dimensions of an $\sim$hour of PAPER data which could be used for a power spectrum analysis.
-We create a fake bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a fake EoR signal, $\textbf{x}_{EoR}$, as complex, random-noise.
-Adding the two together forms our combined dataset, $\textbf{x}$, which we will be applying different weighting schemes to.
-The three data vectors are shown on the left in Figure \ref{fig:toy_sigloss1}, and our ultimate goal is to suppress the foregrounds perfectly without destroying EoR.
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here.}
+	\label{fig:toy_sigloss1}
+\end{figure}
 
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss1.png}
-	\includegraphics[trim={0.3cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss2.png}
-	\caption{Left: Our toy model dataset contains a sine-wave foreground that varies in time and random noise as an EoR signal.
-Real parts are shown here.
-Right: Eigenspectrum of foregrounds only (blue), EoR only (red), and both (green)}
-	\label{fig:toy_sigloss1}
-\end{figure*}
-
-We compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\textbf{C}^{-1}$.
+First, we compute the power spectrum of $\textbf{x}$ using the OQE formalism and a weighting matrix of $\textbf{C}^{-1}$.
 The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
@@
 	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the combined dataset (green).
-Contrasted are the effect of using inverse covariance weighting (left) and information from the first eigenmode only (right).}
+Contrasted are the effect of using inverse covariance weighting (left) and projecting out the first eigenmode only (right).}
 	\label{fig:toy_sigloss3}
@@
 
-Examining this case, our inverse covariance weighted result successfully suppresses foregrounds.
-This is in principle the reason why inverse covariance weighting is so attractive for $21$ cm data.
-It is also evident that our result almost recovers the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-This is actually evidence of a small amount of signal loss.
-In order to understand how this occurs, we need to closely study our covariance matrix $\textbf{C}$.
+As shown in Figure \ref{fig:toy_sigloss3}, our inverse covariance weighted result successfully suppresses foregrounds.
+This illustrates why inverse covariance weighting is attractive for $21$ cm data.
+It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
+This is evidence of signal loss.
+In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$.
 
-It turns out that the eigenspectrum of $\textbf{C}$ offers a window into understanding how inverse covariance weighting affects data.
+It turns out that because we estimated $\textbf{C}$ from our data, its eigenspectrum offers insight into understanding how inverse covariance weighting affects our result.
 An eigenspectrum ranks the eigenvalues of $\textbf{C}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
@@
 
-For our toy model, the eigenspectra of $\textbf{C}_{FG}$, $\textbf{C}_{EoR}$, and $\textbf{C}$ are shown in the right plot of Figure \ref{fig:toy_sigloss1}.
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
+	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green).}
+	\label{fig:toy_sigloss2}
+\end{figure}
+
+For our toy model, the eigenspectra of $\textbf{C}_{FG}$, $\textbf{C}_{EoR}$, and $\textbf{C}$ are shown in Figure \ref{fig:toy_sigloss2}.
 The blue curve peaks only at the zeroth eigenmode, revealing that the foregrounds can be described by a single eigenmode.
@@
 
-As alluded to in the previous section, jack-knife testing is a powerful way to tease out biases by studying how power spectrum measurements of different subsets of data vary.
-Biases can arise due to...
+There are several sources of bias that could leak into a power spectrum measurement, including noise and foreground biases.
+In this section we will describe analysis techniques that help mitigate these effects and how jack-knife tests can tease out biases that are present in data.
+Ultimately, while different weighting and data combination techniques can help identify and remove biases, it is important to remember that a true detection of EoR will be robust to these tests.
+In other words, detections that aren't stable across multiple jack-knives are likely false ones and attributable to systematic errors.
+
+Noise bias can arise in multiple ways.
+Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise.
+We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating longer, using more baselines, etc.
+However, a noise bias can result if the same thermal noise is multiplied by itself.
+This squaring of noise occurs when cross-multiplying visibilities to enter temperature squared space and results in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument.
+One way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days.
+This ensures that the two quantities that go into a measurement have separate noises that don't correlate with each other.
+
+Another way of introducing a noise bias into data is via cross-talk subtraction.
+Cross-talk is caused by the cross-coupling of signals between antennas and shows up as a constant bias in time in visibilities.
+For PAPER-64, cross-talk is removed during redundant calibration, when the deviation from an average visibility (across similar baseline types) is subtracted off of each visibility.
+This type of removal preserves signals common to all baselines, such as the EoR signal, but also has the consequence of introducing a low level bias.
+This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline now has a piece of all the other baseline's (of the same type) noise.
+One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (filter out zero `fringe-rates').
+
+Foreground bias is perhaps one of the main limiting factors pushing up against $21$ cm results.
+Foreground signals lie $\sim4-5$ orders of magnitude above the cosmological signal, and there are many existing techniques to avoid or remove these strong signals.
+Despite current best efforts to do so, however, there remains some foreground leakage that can show up as detections in a power spectrum.
+This leakage is strongest at low $k$ values, corresponding to large spatial scales on the sky.
+
+As with noise bias, there are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from spreading to high $k$ values.
+Narrow window functions can be used to minimize the influence of a particular $k$ value on other ones (\cc{citation?}).
+This in turn compromises power spectrum sensitivity (narrow window functions increases errors for each $k$-mode) as a trade-off for the minimization of foreground leakage.
+Another option is to construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
+The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (Section \ref{sec:PS}).
+
+One last source of foreground bias that we will highlight here is polarization leakage.
+When forming Stokes I from $XX$ and $YY$ polarization visibility data, we ignore the beam asymmetry between the two.
+This mismatch can cause leakage from Stokes Q ($V_{Q} = \frac{1}{2}(V_{XX}-V_{YY})$) into Stokes I ($V_{I} = \frac{1}{2}(V_{XX}+V_{YY})$).
+Another way of describing this leakage is that Faraday Rotation, which causes a rotation of the polarization angle of a signal, can induce spectral structure at certain delays (\citealt{moore_et_al2013}).
+This type of sky bias is dependent on rotation measures, which characterize the amount of polarization rotation.
+If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result would be biased.
+
+One preventative measure for polarization leakage could be tailoring a fringe-rate filter in a way that improves the match between $XX$ and $YY$ polarization beams (\citealt{parsons_et_al2016}).
+There are also multiple ways of tracing a power spectrum detection to a polarization bias.
+One can look at Stokes Q power spectra to estimate the amount of expected leakage (\citealt{moore_et_al2013}).
+In addition, jack-knife tests can be used to investigate whether polarization leakage affects a result.
+For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum detection.
+
+In general, jack-knife tests are helpful in revealing a range of biases, including polarization and foreground biases.
+Slicing data along LST, for example, can determine whether excess detections are traceable to certain foreground sources.
+Slicing along baselines can uncover poorly operating baselines, or baselines whose weighting matrices aren't properly down-weighting foregrounds.
+Jack-knives can be taken along polarization axes, the frequency axis, daily axes, etc., and each can help trace a bias to a physical reason.
+A real $21$ cm signal, however, should exist regardless of these tests, making jack-knives crucial for confidence in a successful EoR detection.
 
@@
 Using the basis of redundancy, however, allows us to set up a system of equations to solve for a complex gain per antenna that brings all baseline of a particular type into alignment.
-We do this using the package OMNICAL.
+We perform these computations using the package OMNICAL \cc{citation needed}.
 
@@
 We used radio sources Pictor A, Fornax A, and the Crab Nebula to fit for an overall phase solution, and set our overall flux scale using Pictor A as a calibrator source.
-Although PAPER-64 data exists for all $4$ polarizations, we only use the $xx$ and $yy$ polarization data to form Stokes I as $V_{I} = \frac{1}{2}(V_{XX} + V_{YY})$.
+Although PAPER-64 data exists for all $4$ polarizations, we only use the $xx$ and $yy$ polarization data to form Stokes I visibilities as $V_{I} = \frac{1}{2}(V_{XX} + V_{YY})$.
 
@@
 This allows us to up-weight parts of the sky high in the primary beam, and down-weight those that are less sensitive.
-In practice, the optimal fringe-rate profile is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
-The filter is implemented on a per baseline basis by convolving the time-domain visibilities with the Fourier transform of the fringe-rate filter, resulting in averaged visibilities yielding $\sim 2$ orders of magnitude in sensitivity.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/frp.png}
+	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
+	\label{fig:frp}
+\end{figure}
+
+New to our updated PAPER-64 analysis is the use of an optimal fringe-rate filter, which maximizes our sensitivity.
+In \citet{ali_et_al2015}, the filter that was applied was degraded by widening it in fringe-rate space.
+This was chosen in order to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying inverse covariance weighting on data with too few modes.
+
+With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), which yields an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
+The filter is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
+It is then implemented on a per baseline basis by convolving the time-domain visibilities with the Fourier transform of the fringe-rate filter, resulting in averaged visibilities yielding $\sim 2$ orders of magnitude in sensitivity.
 
@@
 We have a $2$-dimensional data vector $\textbf{x}$ for each baseline and data group (`even' or `odd').
-As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups.
-Taking $\textbf{x}$ to be averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets).
-
-We use a weight matrix of $\textbf{w} = \cc{???}$ in our analysis.
+As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups (the way we bootstrap baselines into groups is explained in Section \ref{sec:Boot}).
+Taking $\textbf{x}$ to be the averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets).
 
@@
 
+As detailed in Section \ref{sec:SiglossOverview}, signal loss can arise from the interplay between fringe-rate filtering and inverse covariance weighting.
+In this section, we explain a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss.
+Before doing so however, we first explain how noise and EoR are created in our power spectrum pipeline, both of which are used to verify signal loss.
+
 \subsection{Noise and EoR}
 
-One critical new component of our power spectrum pipeline is that we have many different power spectrum channels that simultaneously get processed at the same time and are especially useful for signal loss (Section \ref{sec:Sigloss}) and sensitivity (Section \ref{sec:Sense}) verification.
-Two important channels, in addition to our PAPER-64 data, are a noise dataset and an EoR dataset (in addition to these, we do different combinations of all three).
+One critical new component of our power spectrum pipeline is that we have many different power spectrum channels that simultaneously get processed at the same time and are especially useful for computing signal loss and sensitivity estimations.
+Two important channels, in addition to our PAPER-64 data, are a noise dataset and an EoR dataset (in addition to these, we also look at different combinations of all three).
 We will briefly describe each.
 
-We create random noise with a scale determined by the sensitivity of our instrument and parameters of our dataset. We calculate our system temperature for our frequencies of interest as:
+We create random noise with a variance determined by the sensitivity of our instrument in order to best represent the thermal noise level of our data.
+We calculate our system temperature for our frequencies of interest as:
 
 \begin{equation}
+\label{eq:sys}
 T_{sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{rcvr}
@@
 We again simulate random noise (with a default scale of $1$) with the same shape as our data, and we fringe-rate filter this signal twice.
-The first filter transforms the unattached noise into a signal that's attached to the sky (what our instrument observes).
+The first filter transforms the unattached noise into a signal that's attached to the sky (i.e.
+what our instrument observes).
 The second filter represents the fringe-rate filtering step in our data analysis pipeline.
-As described in Section \ref{sec:Sigloss}, we create an EoR signal at various amplitude levels.
-
-Our multi-channel power spectrum pipeline has been essential in helping us understand the nuances in our pipeline.
-Because there are many different components and countless subtle effects affecting our final limits, it has been imperative to carry all our channels through the analysis to validate each step.
+This fake EoR signal is injected on top of data at various amplitude levels in order to measure its loss.
 
@@
 
-Based on our analysis pipeline, potential signal loss is a real and significant issue.
-More specifically, when applying inverse covariance weighting, $\textbf{C}^{-1}$ is empirically estimated from the data itself, which has the consequence of over-fitting the noise in the data, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters.
+The loss of a cosmological signal when analyzing PAPER-64 data is a real and significant issue.
+To reiterate, when applying inverse covariance weighting, $\textbf{C}^{-1}$ is empirically estimated from the data itself, which has the consequence of over-fitting the noise in the data, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters.
 This is especially prevalent when weighting fringe-rate-filtered data, which has so few independent time modes to begin with, leading to a noisier dataset.
@@
 
-New to the PAPER-64 analysis is a robust method to estimate signal loss associated with inverse covariance weighting.
-This method, explained below, is now a standard analysis step for all PAPER analyses and one that will be used for HERA moving forward.
+New to the PAPER-64 analysis is a robust method to estimate signal loss. This method is now a standard analysis step for all PAPER analyses and one that will be used for HERA moving forward.
 
@@
 
-Using our OQE formalism, we are interested in the following two quantities: $P_{in}$ and $P_{out}$.
+Using OQE formalism, we are interested in the following two quantities: $P_{in}$ and $P_{out}$.
 The input power spectrum, $P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal.
@@
 \begin{equation}
-P_{in} \propto \textbf{e}^{\dagger}\textbf{I}^{-1}\textbf{Q}\textbf{I}^{-1}\textbf{e}
+P_{in} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}\textbf{I}\textbf{e}
 \end{equation}
@@
 P_{out} \equiv \textbf{P}_{e} &=& \textbf{P}_{r}-\textbf{P}_{x} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} 
+&\propto& \textbf{r}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} 
 \end{eqnarray}
 
-It is noted that the output power spectrum is comprised of two terms: the covariance treated power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.
+It is noted that the output power spectrum is comprised of two terms: the power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.
 
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e}$.
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e}$.
 Expanding Equation \ref{eq:sigloss}:
@@
 \begin{eqnarray}
-P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{x} + \textbf{e}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{e} + \textbf{x}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{x} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} \nonumber 
+P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} \nonumber \\
+&\propto& \textbf{x}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} \nonumber 
 \end{eqnarray}
 
-And taking the case of very large $\textbf{e}$, so that $\textbf{C}_{r}^{-1} \sim \textbf{C}_{e}^{-1}$ and any terms involving only $\textbf{x}$ are small:
+And taking the case of very large $\textbf{e}$, so that $\textbf{w}_{r} \sim \textbf{w}_{e}$ and any terms involving only $\textbf{x}$ are small:
 
 \begin{eqnarray}
-P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e} + \textbf{x}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{C}_{e}^{-1}\textbf{Q}\textbf{C}_{e}^{-1}\textbf{x}
+P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{x}
 \end{eqnarray}
@@
 
-For the unweighted case ($\textbf{C} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1.
+For the unweighted case ($\textbf{w} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1.
 For the weighted case, this is not true due to signal loss.
@@
 
-Recall that fringe-rate filtered noise, which mimics the level of noise in our actual PAPER-64 dataset, is a channel in our power spectrum pipeline.
-We can compute signal loss quantities of interest for the noise $\textbf{n}$ similar to the expressions we featured previously for data $\textbf{x}$.
+We now shift our attention towards computing signal loss for fringe-rate filtered PAPER-64 dataset, using inverse covariance weighting ($\textbf{w} = \textbf{C}^{-1}$).
+Our expressions for $P_{in}$ and $P_{out}$ become:
 
 \begin{eqnarray}
-P_{in} &\propto& \textbf{e}^{\dagger}\textbf{I}^{-1}\textbf{Q}\textbf{I}^{-1}\textbf{e} \\
-\textbf{s} &=& \textbf{n} + \textbf{e} \\
-P_{out} &\propto& \textbf{s}^{\dagger}\textbf{C}_{s}^{-1}\textbf{Q}\textbf{C}_{s}^{-1}\textbf{s} - \textbf{n}^{\dagger}\textbf{C}_{n}^{-1}\textbf{Q}\textbf{C}_{n}^{-1}\textbf{n} 
+P_{in} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}\textbf{I}\textbf{e} \\
+P_{out} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 Using the input and output power spectra for range of EoR amplitudes, we use two methods to determine signal loss associated with the over-fitting of noise during inverse covariance weighting.
-We first look at signal loss for the pure noise case (no data), to show that we can successfully inject EoR signals, determine signal loss, and then recover the signal.
+
+\cc{Determine whether we want to show pure noise plots, or just data, or both!!!}
 
@@
 
-With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{C}$.
+With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{w}$.
 Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
-We have found that the balance between the two is a delicate one and requires \cc{??
-finish sentence...}.
+We have found that the balance between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
 
@@
 \subsection{Thermal Noise}
+\label{sec:PSSense}
 
-\cc{Add info on sensitivity equation, how we calculate effective inttime and adjust beam factor because of FRF, etc.}
+One way to estimate errors of a $21$ cm power spectrum estimate is to compute theoretical errors based on instrumental temperature and observational parameters.
+A theoretical noise limit provides a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can achieved by a particular observation and analysis.
+Here we walk through a detailed computation of a theoretical noise estimation as applied to PAPER-64 observations and highlight major changes from \citet{ali_et_al2015}.
+We first give a general formula, and then go into detail about each factor.
+
+The sensitivity prediction for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
+
+\begin{equation}
+p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lsts}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
+\end{equation}
+
+\begin{itemize}
+\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving distances).
+For $z=8.4$, $X^{2}Y = 5 \times 10^{11} [h^{-3} Mpc^{3} / str \, GHz]$.
+\item $\Omega_{eff}$: The primary beam angular size.
+The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-weighted.
+Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate filter.
+\item $T_{sys}$: The system temperature is set by Equation \ref{eq:sys}, for a receiver temperature of $200$ K and center frequency of $0.15$ GHz. 
+\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from only using the real part of power spectrum estimates when plotting and quoting upper limits.
+\item $N_{lsts}$: The number of LST hours that go into power spectrum estimation.
+The sensitivity scales as the square root because we integrate incoherently over time.
+For PAPER-64, $N_{lsts} = 8$ hours.
+\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate.
+For the analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$.
+\item $t_{int}$: The integration time of the data.
+It is crucial to adapt this number if filtering is applied along the time axis (i.e.
+a fringe-rate filter).
+We compute the effective integration time of our fringe-rate filtered data by...
+For PAPER-64, this number is $t_{int} = 3857$ s.
+\item $N_{days}$: The total number of days of data analyzed. 
+\item $N_{bls}$:
+\item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
+\end{itemize}
 
 \subsection{Bootstrapping}
+\label{sec:Boot}
 
+In this section, we highlight two major changes since \citet{ali_et_al2015}, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
 \cc{Include info about baseline bootstrapping:}
@@
 
-\cc{Include info about optimal FRF:}
-In \citet{ali_et_al2015}, the filter applied was degraded (widened in fringe-rate space) from an optimal one that can be constructed based on the integration time of the data.
-This was chosen to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying optimal quadratic estimators (OQE) on data with too few modes.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/frp.png}
-	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
-	\label{fig:frp}
-\end{figure}
-
-New to our updated PAPER-64 analysis is the use of the optimal fringe-rate filter, which maximizes our sensitivity.
-With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), resulting in an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
-
 \section{Conclusion}

### 2017-07-17 PAPER.tex
-Elaborated on captions for Figures in Section 2 -Did a once-over read and edit of Section 2

@@
 Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR.
-In this paper we will highlight some sources of bias and discuss ways to mitigate its effects.
+In this paper we will highlight some sources of bias and discuss ways to mitigate their effects.
 \end{itemize}
@@
 
-where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum . We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
 
@@
 
-To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss through the use of a toy model.
+To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we use a toy model.
 Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
@@
 The sum of the two forms our combined data vector, $\textbf{x}$, to which we will be applying different weighting schemes.
-The three data vectors are shown on in Figure \ref{fig:toy_sigloss1}.
+The three data vectors are shown in Figure \ref{fig:toy_sigloss1}.
 Our ultimate goal in experimenting with weighting is to suppress the foregrounds perfectly without destroying EoR.
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here.}
+	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here. \cc{colorbar?}}
 	\label{fig:toy_sigloss1}
@@
 	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
-	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the combined dataset (green).
-Contrasted are the effect of using inverse covariance weighting (left) and projecting out the first eigenmode only (right).}
+	\caption{Resulting power spectrum estimates for our toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right).
+There is signal loss for the former but not the latter.}
 	\label{fig:toy_sigloss3}
@@
 
-As shown in Figure \ref{fig:toy_sigloss3}, our inverse covariance weighted result successfully suppresses foregrounds.
+As shown in Figure \ref{fig:toy_sigloss3} (left plot), our inverse covariance weighted result successfully suppresses foregrounds.
 This illustrates why inverse covariance weighting is attractive for $21$ cm data.
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
-	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green).}
+	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green).
+The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
+All eigenspectra steepen slightly for the final few eigenmodes, a behavior that results in some modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate (Figure \ref{fig:toy_sigloss3}, left).
+If only the first eigenmode is used, all others get equal weights and hence, there is no signal loss (Figure \ref{fig:toy_sigloss3}, right)}
 	\label{fig:toy_sigloss2}
@@
 Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss.
-Namely, we can zero out all eigenmodes except the first one, thereby down-weighting the foregrounds perfectly and nothing else.
+Namely, we can project out the zeroth eigenmode (i.e.
+zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
 The result is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
@@
 To mimic this filter, we average every $4$ time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels (our matrices will be full rank).
-The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss1}, fall more steeply for last few eigenmodes.
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
+The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply for the last few eigenmodes.
 This shape has large consequences on the resulting power spectra.
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
-	\caption{Left: Our `fringe-rate filtered' toy model dataset.
+	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
 It contains $25$ independent samples in time.
 Real parts are shown here.
-Right: Eigenspectrum of foregrounds only (blue), EoR only (red), and both (green).}
+Right: Eigenspectrum of the covariance matrices of foregrounds only (blue), EoR only (red), and FG + EoR (green).
+The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
+All eigenspectra steepen for the final few eigenmodes, a behavior that results in a few noisy modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate.}
 	\label{fig:toy_sigloss5}
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
-	\caption{Power spectrum of foregrounds only (blue), EoR only (red), and the full inverse covariance weighted combined dataset (green) for a time-averaged dataset (fewer independent modes).}
+	\caption{Resulting power spectrum estimate for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+We use inverse covariance weighting where $\textbf{C}$ is derived from the data.
+There is a larger amount of signal loss than un-fringe-rate filtered data.
+The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
 	\label{fig:toy_sigloss7}
@@
 	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss11.png}
-	\caption{Power spectra of foregrounds only (blue), EoR only (red), and the weighted combined dataset (green).
-We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first few eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).}
+	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).
+There are many regularization options available to minimize signal loss, and some work better than others depending on the dataset.}
 	\label{fig:toy_sigloss8}
@@
 Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal.
-Inverse covariance weighting is an optimal weighting for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss.
+Inverse covariance weighting is an optimal weighting scheme for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss.
 The application of a fringe-rate filter heightens this effect by reducing the number of independent samples and steepening eigenspectra further.
@@
 For example, power spectrum measurements of $21$ cm data can be made along many axes, including time and baselines.
-Through the process of bootstrapping, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
+Through the process of bootstrapping along these axes, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
 
@@
 Therefore, the use of a fringe-rate filter, which averages data in time to increase sensitivity, creates a situation in which bootstrapping can under-estimate errors.
+We will now show this effect using our toy model.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
-	\caption{Error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
+	\caption{Power spectrum error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
 The grey star represents the error associated with drawing $1000$ samples from a length $1000$ array of random noise.
 The black points correspond to time-averaged data and illustrate how errors can be underestimated if drawing more samples than independent ones in the data.
-There are $100$ independent samples in the time-averaged data and using this number does indeed match the theoretical error prediction.}
+There are $100$ independent samples in the time-averaged data --- hence, using this number does indeed match the theoretical error prediction.}
 	\label{fig:toy_error1}
@@
 
-It is clear that the fraction of independent baselines in a group is always greater using our new sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group).
-An analog for the y-axis in Figure \ref{fig:toy_error2} is the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.
+It is clear that the fraction of independent baselines in a group is always greater using our revised sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group).
+The more baselines per group, the more sensitivity we can gain by ensuring that most of the baselines are independent ones.
+An analog for the y-axis in Figure \ref{fig:toy_error2} is therefore the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.
 
@@
 However, one must be careful about violating independence assumptions, as it is possible to under-estimate errors by over-sampling data.
-Additionally, small changes in the way datasets are randomly sampled can ensure that the overall sensitivity is maximized.
+Additionally, small changes in the way a dataset is randomly sampled can ensure that its overall sensitivity is maximized.
 
@@
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
-The former over-estimates error bars by not maximizing baseline sensitivity to its full capacity.}
+The former over-estimates error bars since some baselines end up being repeated due to random sampling.
+Therefore, baseline sensitivity is not maximized to its full capacity.}
 	\label{fig:toy_error2}
@@
 This type of removal preserves signals common to all baselines, such as the EoR signal, but also has the consequence of introducing a low level bias.
-This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline now has a piece of all the other baseline's (of the same type) noise.
-One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (filter out zero `fringe-rates').
+This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline has a piece of all the other baseline's (of the same type) noise.
+One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (i.e.
+filter out zero `fringe-rates').
 
@@
 This type of sky bias is dependent on rotation measures, which characterize the amount of polarization rotation.
-If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result would be biased.
+If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result for that $k$ would be biased.
 
@@
 In addition, jack-knife tests can be used to investigate whether polarization leakage affects a result.
-For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum detection.
+For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum bias.
 

### 2017-07-17 PAPER.tex
fleshed out thermal noise parameter descriptions

@@
 Using the basis of redundancy, however, allows us to set up a system of equations to solve for a complex gain per antenna that brings all baseline of a particular type into alignment.
-We perform these computations using the package OMNICAL \cc{citation needed}.
+We perform these computations using the package OMNICAL (\citealt{zheng_et_al2014}).
 
@@
 We perform all possible cross-multiplications of this quantity, except between the same datasets (`even' with `even', for example) and same groups (`baseline group 1' with `baseline group 1', for example).
-We avoid these computations to prevent the introduction of biases from shared auto power.
+We avoid these computations to prevent the introduction of noise biases from shared auto power.
 
@@
 Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
-Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements.
+Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing foreground bias.
 
@@
 
-One way to estimate errors of a $21$ cm power spectrum estimate is to compute theoretical errors based on instrumental temperature and observational parameters.
-A theoretical noise limit provides a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can achieved by a particular observation and analysis.
+One way to estimate errors on a $21$ cm power spectrum estimate is to compute theoretical errors based on the instrumental temperature and observational parameters.
+A theoretical noise limit provides a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
 Here we walk through a detailed computation of a theoretical noise estimation as applied to PAPER-64 observations and highlight major changes from \citet{ali_et_al2015}.
@@
 \item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving distances).
-For $z=8.4$, $X^{2}Y = 5 \times 10^{11} [h^{-3} Mpc^{3} / str \, GHz]$.
+For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
 \item $\Omega_{eff}$: The primary beam angular size.
@@
 Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate filter.
-\item $T_{sys}$: The system temperature is set by Equation \ref{eq:sys}, for a receiver temperature of $200$ K and center frequency of $0.15$ GHz. 
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from only using the real part of power spectrum estimates when plotting and quoting upper limits.
-\item $N_{lsts}$: The number of LST hours that go into power spectrum estimation.
+\item $T_{sys}$: The system temperature is set by Equation \ref{eq:sys}, for a receiver temperature of $200$ K and center frequency of $0.15$ GHz. \cc{does this differ from prior analysis?}
+\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from only using the real part of power spectrum estimates when plotting and quoting upper limits (imaginary component is discarded).
+\item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation.
 The sensitivity scales as the square root because we integrate incoherently over time.
@@
 a fringe-rate filter).
-We compute the effective integration time of our fringe-rate filtered data by...
+We compute the effective integration time of our fringe-rate filtered data by scaling our original integration time using the following:
+\begin{equation}
+t_{frf} = t_{int} \frac{\int1 \, df}{\int w^{2}(f) \,df},
+\end{equation}
+where $t_{int}=43$ seconds, $t_{frf}$ is our fringe-rate filtered integration time, $w$ is our fringe-rate profile, and the integral is taken over all fringe-rates.
+In other words, we calculate our effective integration time by computing how our beam is altered in fringe-rate space.
 For PAPER-64, this number is $t_{int} = 3857$ s.
 \item $N_{days}$: The total number of days of data analyzed.
-\item $N_{bls}$:
+In \citet{ali_et_al2015}, this number was set to $135$.
+However, because we divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$.
+Additionally, because our $LST$ coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of $N_{days}$ as the RMS of all the daily counts in one dataset (`even', for example).
+For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ days.
+\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate.
+In \citet{ali_et_al2015}, this number was the total number of $30$ m East/West baselines used in the analysis.
+However, using the total number of baselines neglects the fact that we divid baselines into $5$ groups before cross-multiplying data.
+Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where $N_{gps} = 5$.
+This expression arises because $N_{bls}$ must be scaled by the total number of cross-multiplications going into the power spectrum estimate.
+For $5$ groups, there are $25$ total cross-products, minus $5$ cross-products since we avoid multiplying the same group with itself.
+For our PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ baselines.
 \item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.

### 2017-07-18 PAPER.tex
-Fleshed out Section 5.2 (data bootstrapping)

@@
 In this section, we highlight two major changes since \citet{ali_et_al2015}, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
-\cc{Include info about baseline bootstrapping:}
-For the \citet{ali_et_al2015} method, each group is then sampled with replacement to create a new group, of the same size, that can have repeated baselines inside it.
-We discover that in doing so, we are sacrificing some of our sensitivity since this results in there being 3-4 repeated baselines per group.
-In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one.
-For example, if we have $10$ baselines in a group, we use the first $9$ to guarantee at least $9$ independent measurements, and then fill the last slot randomly out of the $10$.
-We do this for all $5$ groups.
-This is still a valid means of bootstrapping because there are many more possibilities of baseline groupings than the number of bootstraps we run for this analysis ($nboots = 20$).
 
-\cc{Include info about second round of bootstrapping:}
-In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the bootstrap and time axes simultaneously.
+As discussed in Section \ref{sec:ErrorOverview}, traditional bootstrapping theory is only a valid way of estimating errors if a dataset is comprised of independent samples.
+Recall that the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
+In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the baseline bootstrap and time axes simultaneously.
 Random values are sampled with replacement along both axes, drawing as many values as there are number of bootstraps and times.
-Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis.
+Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis (which is typically large, on the order of $N_{boot} \sim 400$).
 
-However, we have found that this method greatly underestimates power spectrum errors, especially for fringe-rate filtered data.
-This can be explained by the fact that fringe-rate filtered data has a dramatically reduced number of independent modes.
-Hence, drawing $100$ samples out of a length-$100$ dataset that only has $5$ independent modes in it, for example, results in a narrower distribution of values that leads to a false error estimation.
+Because our dataset is fringe-rate filtered, we have substantially increased our integration time, resulting in fewer independent samples (from $\sim700$ samples to $8$ samples).
+A random draw of $700$ samples from this dataset therefore has many repeated samples, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance.
+Another way of describing this underestimation is that there are fewer ways to randomly sample data with $8$ independent modes versus $700$, so bootstrapping a fringe-rate filtered dataset yields a narrower distribution of values from which we calculate its standard deviation.
 
-To avoid this issue, we instead take a simple average along the time axis. Our final power spectrum limits are computed by taking the mean and standard deviation over our single bootstrap axis.
+To prevent error underestimation, we simply take the average along the time axis in our revised pipeline rather than bootstrapping.
+Hence, our final power spectrum errors are calculated from the standard deviation over the baseline bootstrapping axis only, which is still a valid axis since each baseline makes an independent measurement of the sky.
+
+The second aspect of bootstrapping discussed in Section \ref{sec:ErrorOverview} is in regard to how a dataset is randomly sampled.
+In order to maximize sensitivity (i.e.
+maximize independent samples in a bootstrap), we have revised the method by which we sample baselines when bootstrapping.
+
+First, we speed things up in our pipeline by dividing our total number of baselines into $5$ groups, where there are no repeated baselines within or between groups.
+In \citet{ali_et_al2015}, each group is then sampled with replacement to create a new group of the same size, which can have repeated baselines inside it.
+We discover that in doing so, we are sacrificing some of our sensitivity since there are $3$-$4$ repeated baselines per group.
+In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one, which we fill randomly.
+We use this method for every bootstrap, creating new groups and sampling the last spot randomly each time.
+
+Power spectrum estimates for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
+The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
+We show upper limits ($2\sigma$ error bars) for three different results.
+Our revised error estimation method is in black, where we only bootstrap along the baseline axis and we maximize sensitivity by random sampling only the last baseline in each group.
+The red curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group.
+In blue, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data.
+We under-estimate errors in doing so because we are drawing many more samples than independent ones since the data is fringe-rate filtered.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/data_errors.png}
+	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods.
+The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used, where $\textbf{C}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
+Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.
+It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly).
+The blue result bootstraps over both the baseline and time axes, and illustrates how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
+	\label{fig:data_errors}
+\end{figure}
 

### 2017-08-04 PAPER.tex
-Made Aaron changes for first half of paper

@@
 \begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of neutral hydrogen.
-This important epoch of our cosmic dawn harbors a wealth of information regarding the environment during this transformative time, including insight into the nature of the first luminous sources and implications about cosmological parameters.
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of neutral hydrogen in the intergalactic medium.
 There are many experiments investigating the EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate.
@@
 Additionally, it is imperative to understand the trade-offs between different methods and their effects on common power spectrum themes.
-In this paper, we focus on three major themes - signal loss, power spectrum error bar estimation, and bias in measurements.
+In this paper, we focus on three major themes --- signal loss, power spectrum error bar estimation, and bias in measurements.
 We describe techniques that affect these themes using both a toy model and data taken by the 64-element configuration of the Donald C.
 Backer Precision Array for Probing the Epoch of Reionization (PAPER).
+\cc{motivate a bit more once the paper is complete}
 \end{abstract}
@@
 
-By about one billion years after the Big Bang, the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the baryonic matter content in the early Universe.
+By about one billion years after the Big Bang ($z \sim 6$), the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the baryonic matter content in the Universe.
 This transition period, during which the first luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas into a plasma, is known as the epoch of reionization (EoR).
@@
 This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space.
-The 21 cm line therefore offers a window into the evolution of ionization, temperature, and density fluctuations on cosmic scales.
+The 21 cm line offers a window into the evolution of ionization, temperature, and density fluctuations on cosmic scales.
 
 Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen to place constraints on the brightness of the EoR.
-Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES, \citealt{bowman2010}), the Long Wavelength Array (LWA, \citealt{ellingson_et_al2009}),  the Large Aperture Experiment to Detect the Dark Ages (LEDA, \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE, \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI, \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS, \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS, \citealt{patra2015}).
-Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT, \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR,\citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA, \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA, \citealt{peterson_et_al2004}, \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
-The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful $23\sigma$ detection with an eventual $350$ elements, using current analysis techniques (\citealt{deboer_et_al2017}, \citealt{pober_et_al2014}).
+Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman2010}), the Long Wavelength Array (LWA; \citealt{ellingson_et_al2009}),  the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; \citealt{patra2015}).
+Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR;\citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; \citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
+The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; \citealt{pober_et_al2014}).
 
@@
 With continual progress being made in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact with each other to affect power spectrum results.
-In this paper, we discuss three themes essential to a $21$ cm power spectrum analysis and how data analysis choices affect each.
-We approach these themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER.
+More specifically, it is imperative to develop techniques and tests that ensure the accuracy and reliability of a potential EoR detection.
+In this paper, we discuss three themes that are essential to investigate for a robust $21$ cm power spectrum analysis.
+We also highlight four power spectrum techniques and their trade-offs, traps, and connections to the themes .
+We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER.
 
@@
 In section 2 we introduce the three themes of our focus, using a toy model to develop intuition into each one.
-Section 3 presents an overview of the PAPER-64 array and observations, highlighting key changes from \citet{ali_et_al2015}.
-Sections 4, 5, and 6 detail how the new PAPER-64 analysis quantifies signal loss, estimates error bars, and eliminates bias, respectively.
+Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}.
 We conclude in Section 7.
@@
 
-There are many choices for a data analyst, such as how to combine time-ordered measurements, how to estimate its variance, how to weight data in a way that suppresses contaminated modes while not destroying an EoR signal, and how to identify the source of a detection.
-Many common techniques, such as averaging data, weighting, bootstrapping, and jack-knife testing, each address these issues yet harbor additional trade-offs.
+There are many choices for a data analyst.
+How can time-ordered measurements be combined?
+How can the variance of the data be estimated?
+In what way(s) can the data be weighted to suppress contaminated modes while not destroying an EoR signal?
+How can the source of a detection be properly identified?
+Many common techniques, such as averaging data, weighting, bootstrapping, and jackknife testing, each address these issues yet harbor additional trade-offs.
 For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing some EoR signal.
@@
 
-Measuring the statistical $21$ cm power spectrum requires robust methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.
-Additionally, we desire to maximize our sensitivity with filtering and weighting techniques.
-In this paper, we focus on four techniques and their effects on three overarching themes of $21$ cm power spectrum estimation.
+Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.
+In this paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay with each other and the themes.
 We will give brief definitions now, and build intuition for each theme in the sections to follow.
@@
 \end{center}
+
+A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power spectrum result.
+Stemmed from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for a rigorous power spectrum analysis.
 \begin{itemize}
-\item[] The accuracy and interpretation of a $21$ cm power spectrum can be encompassed in the following three themes.
 \item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): As explained in the next section, certain analysis techniques can lead to the loss of the EoR signal.
@@
 \end{center}
+
+The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
+We focus on these techniques because of their strong appeal for a power spectrum analysis.
+However, they also have limitations, and we will discuss circumstances in which there are trade-offs.
 \begin{itemize}
-\item[] The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
-However, they also have limitations and circumstances in which there are trade-offs.
 \item \textbf{Fringe-rate filtering:} Fringe-rate filtering can be considered an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
@@
 By randomly drawing many samples of the data, we get a sense of its inherent variance, though there are subtleties to consider such as bootstrapping sample sizes.
-\item \textbf{Jack-Knife testing:} A resampling technique useful for estimating bias, jack-knives can be taken along different dimensions of a dataset to cross-validate results.
+\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different dimensions of a dataset to cross-validate results.
 In particular, null tests can be used to verify whether results are free of systematics (\citealt{keating_et_al2016}).
@@
 
-Signal loss refers to the attenuation of the target cosmological signal in a dataset.
+In this section we illustrate how signal loss arises in analysis.
+Signal loss refers to attenuation of the target cosmological signal in a power spectrum estimate.
 It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during spectral calibration, applying a delay-domain filter, or by weighting data by itself.
-Here we focus on signal loss associated with applying a weighting matrix to data.
+Here we focus on signal loss associated with applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously underestimated in the PAPER-64 analysis.
+
 Driven by the need to mitigate foreground bias, we would like to use a weighting method that succeeds in down-weighting foregrounds.
-However, as we'll investigate, this carries the risk of large amounts of signal loss.
-
-Before we demonstrate how different weighting matrices affect signal loss, we first recap how weights are related to the power spectrum estimation technique of optimal quadratic estimators (OQE, \citealt{liu_et_al2014b}).
-A summary of the method is as follows.
-
-We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in mK that have the shape ($times$, $frequencies$).
+We apply this weighting to data and propagate it into a final estimator using the power spectrum estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}).
+Before showing how signal loss can arise when using different weighting matrices, we first summarize OQE as follows.
+
+We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in Jy that have the shape ($times$, $frequencies$).
 We form the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{x}
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{S}\textbf{Q}_{\alpha}\textbf{S}\textbf{x},
 \end{equation}
 
-where $\textbf{w}$ \cc{change to capital letter that isn't taken yet!} is a weighting matrix (for example, inverse covariance weighting would set $\textbf{w} = \textbf{C}^{-1}$).
+\noindent where $\textbf{S}$ is a weighting matrix (we use $\textbf{S}$ since $\textbf{W}$ is reserved for window functions).
+As an example, inverse covariance weighting would set $\textbf{S} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{S} = \textbf{I}$, the identity matrix.
 The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
@@
 \begin{equation}
-\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}}
+\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}},
 \end{equation}
 
-where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
 
 \begin{eqnarray}
-\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr[\textbf{w}\textbf{Q}_{\alpha}\textbf{w}\textbf{Q}_{\beta}]. 
+\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr[\textbf{S}\textbf{Q}_{\alpha}\textbf{S}\textbf{Q}_{\beta}]. 
 \end{eqnarray}
 
-We have a choice for $\textbf{M}$, and for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, the identity matrix.
-This is not the case for the analysis of PAPER-64 data, which we describe in Section \cc{not sure which section to point to yet} as part of the discussion of bias.
-
-In the next sections, we will experiment with different weighting matrices $\textbf{w}$ and their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
+We have a choice for $\textbf{M}$.
+For simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:PS}
+
+In the next sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{S}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
+Our ultimate goal in experimenting with weighting is to suppress foregrounds perfectly without destroying an EoR signal.
 
 \subsubsection{Toy Model: Inverse Covariance Weighting}
+\label{sec:toymodel}
 
 To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we use a toy model.
-Suppose we have a very simple dataset that contains 2-dimensional data (representing $100$ time integrations and $20$ frequency channels).
-This model represents realistic dimensions of about an hour of PAPER data which could be used for a power spectrum analysis.
-We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, as well as a mock EoR signal, $\textbf{x}_{EoR}$, as complex, random Gaussian noise.
-The sum of the two forms our combined data vector, $\textbf{x}$, to which we will be applying different weighting schemes.
+We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time integrations and $20$ frequency channels).
+This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
+We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency (\cc{explain why a sinusoid for FG}), as well as a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
+Our combined data vector is $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
 The three data vectors are shown in Figure \ref{fig:toy_sigloss1}.
-Our ultimate goal in experimenting with weighting is to suppress the foregrounds perfectly without destroying EoR.
-
-One choice for a weight matrix $\textbf{w}$ is an inverse covariance matrix.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and a random Gaussian signal as a mock EoR signal. Real parts are shown here. \cc{colorbar?}}
+	\label{fig:toy_sigloss1}
+\end{figure}
+
+One choice for a weight matrix $\textbf{S}$ is an inverse covariance matrix.
 This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds.
-The covariance matrix $\textbf{C}$, which describes covariances between frequency channels, can be estimated in a variety of ways.
-Should we have perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our real data.
-However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the real foregrounds in the data.
-One attractive way to estimate $\textbf{C}$ then is to empirically derive it from the data vector $\textbf{x}$ itself:
+\cc{math!} The covariance matrix $\textbf{C}$, which in our case describes covariances between frequency channels, can be estimated in a variety of ways.
+Given perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data.
+\cc{math!} However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the foregrounds in the data.
+
+One attractive way to estimate $\textbf{C}$ is to empirically derive it from the data vector $\textbf{x}$ itself:
 
 \begin{equation}
-\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle,
+\hat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle,
 \end{equation}
 
-assuming $\langle\textbf{x}\rangle = 0$. The inverse covariance matrix is therefore $\textbf{w} = \textbf{C}^{-1}$.
-
-If $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal.
-If instead we choose $\textbf{w} = \textbf{I}$, the identity matrix, there will be no signal loss (although it may suffer from foreground or instrumental bias).
-We will refer to this choice as `unweighted', since using the identity does not alter (doesn't upweight or downweight) the data at all.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and random Gaussian noise as a mock EoR signal. Real parts are shown here. \cc{colorbar?}}
-	\label{fig:toy_sigloss1}
-\end{figure}
+\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a time-average \cc{distinguish between ideal ensemble average and finite estimate???}.
+The inverse covariance matrix is therefore $\textbf{S} = \textbf{C}^{-1}$.
+\cc{should I put hat's on all C's that are estimated from the data?
+Need to distinguish it from ideal C.}
 
@@
 	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
-	\caption{Resulting power spectrum estimates for our toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymode} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right).
-There is signal loss for the former but not the latter.}
+There is signal loss for the former but not the latter.
+\cc{elaborate}}
 	\label{fig:toy_sigloss3}
@@
 
-As shown in Figure \ref{fig:toy_sigloss3} (left plot), our inverse covariance weighted result successfully suppresses foregrounds.
+As shown, our inverse covariance-weighted result successfully suppresses foregrounds \cc{explain why}.
 This illustrates why inverse covariance weighting is attractive for $21$ cm data.
@@
 This is evidence of signal loss.
-In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$.
+In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$, which is shown in Figure \ref{fig:toy_sigloss12}.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 2.3cm 0.3cm 2.3cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only, EoR only, and FG + EoR. Real parts are shown here. \cc{colorbar?}}
+	\label{fig:toy_sigloss12}
+\end{figure}
+
+If $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal \cc{elaborate with math!}.
+As a contradictory example, if instead we choose $\textbf{S} = \textbf{I}$, there will be no signal loss (although it may suffer from foreground or instrumental bias).
 
@@
 An eigenspectrum ranks the eigenvalues of $\textbf{C}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
+Each eigenvalue encodes the amount of variance in the dataset for a particular mode.
 The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+\cc{use more rigorous math to supplement this paragraph}
 
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
-	\caption{Eigenspectrum of foregrounds only (blue), EoR only (red), and FG + EoR (green).
-The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
+	\caption{Eigenspectrum of $\textbf{C}_{FG}$ (blue), $\textbf{C}_{EoR}$ (red), and $\textbf{C}_{FG+EoR}$ (green).
+The eigenspectrum of $\textbf{C}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
 All eigenspectra steepen slightly for the final few eigenmodes, a behavior that results in some modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate (Figure \ref{fig:toy_sigloss3}, left).
-If only the first eigenmode is used, all others get equal weights and hence, there is no signal loss (Figure \ref{fig:toy_sigloss3}, right)}
+If only the first eigenmode is used, all others get equal weights and hence, there is no signal loss (Figure \ref{fig:toy_sigloss3}, right).
+\cc{also illustrate first few and last few eigenvalues -- how to best show this?}}
 	\label{fig:toy_sigloss2}
@@
 This is a direct consequence of how it was constructed (only one sinusoid).
-In fact, the blue peak in Figure \ref{fig:toy_sigloss3} is also a direct result of our foreground's construction.
 The eigenspectrum of EoR, however, is fairly flat, signifying that its covariance matrix is similar to an identity matrix.
-This makes sense because the EoR signal consists of random noise, which should only have strong frequency-frequency correlations when two frequencies are the same.
-
-The eigenmodes with the highest eigenvalues will be down-weighted the most (i.e.
-when the spectrum is inverted, they will be given the smallest weights).
+This makes sense because EoR consists of a random signal, which should only have strong frequency-frequency correlations when two frequencies are the same.
+
+The eigenmodes with the highest eigenvalues will be down-weighted the most; when the spectrum is inverted, they will be given the smallest weights.
 In contrast, the modes with the smallest eigenvalues will be up-weighted the most.
 In other words, if an eigenspectrum is not perfectly flat, all modes will be given different weights and it is possible to up-weight a few modes much more than others.
-The subtle slope of the eigenspectrum in this toy example gives rise to a small amount of signal loss because it is possible to overfit a few modes (the highest weighted ones) ever so slightly.
+The subtle slope of the eigenspectrum in this toy example is the result of describing shapes in the data that aren't physically there \cc{reword sentence...
+the shape is there but it's not valid?}.
+This gives rise to a small amount of signal loss because it is possible to overfit a few modes (the highest weighted ones) ever so slightly.
 We will see in the next section how this effect can be exaggerated as the `steepness' of the spectrum changes.
@@
 zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
-The result is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
-In this case, we perfectly recover EoR, demonstrating that if we can perfectly model our foregrounds, we can down-weight them without signal loss.
-However, this is not the case in reality since we aren't able to distinguish between foreground and EoR modes.
+Altering $\textbf{C}$ in this way is one example of a regularization method, in which we are changing $\textbf{C}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
+The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
+In this case we recover EoR, demonstrating that if we can model our foregrounds, we can down-weight them without signal loss.
+There are several other ways to regularize $\textbf{C}$, and we will discuss some in Section \ref{sec:otherweight}.
 
@@
 We have shown how signal loss can arise due to unintentionally up-weighting eigenmodes with small eigenvalues (overfitting the noise).
-We will next show how this effect is exaggerated with a reduction of the total number of independent samples in a dataset.
+We will next show how this effect is exaggerated by reducing the total number of independent samples in a dataset.
 
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-To mimic this filter, we average every $4$ time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
+Rather than a traditional box-car average, a fringe-rate filter can be designed to up-weight parts of the sky that an instrument is most sensitive to, while down-weighting the opposite.
+We apply a fringe-rate filter to PAPER-64 data in order to optimally combine our time-ordered measurements.
+We weight data based on our primary beam sensitivity, yielding a net increase in sensitivity in our measurements.
+
+Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
+To mimic this filter, we average every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
 We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
 The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply for the last few eigenmodes.
-This shape has large consequences on the resulting power spectra.
+This slope is a consequence of reducing the variance of the dataset through averaging.
+More specifically, when numbers are averaged together we are absorbing outliers into the average, resulting in a narrower distribution of the data.
+Hence, the eigenvalues, which rank the strength of variances in the data, decreases more than an un-averaged case.
 
@@
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
-It contains $25$ independent samples in time.
+We averaged every four samples together, yielding $25$ independent samples in time.
 Real parts are shown here.
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
-	\caption{Resulting power spectrum estimate for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data.
-There is a larger amount of signal loss than un-fringe-rate filtered data.
+There is a larger amount of signal loss than for un-fringe-rate filtered data, a consequence of a steeper eigenspectrum slope which results from washing out variances in the data through averaging.
 The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
@@
 
-Applying inverse covariance weighting to this dataset results in the power spectra shown in Figure \ref{fig:toy_sigloss7}.
+The eigenspectrum shape has large consequences on the resulting power spectra, as evidenced by the power spectra shown in Figure \ref{fig:toy_sigloss7}.
 There is a much larger amount of signal loss for this time-averaged dataset.
 To reiterate, the drop-off in the eigenspectrum shape suggests that when the spectrum is inverted, a few modes are up-weighted much more strongly than the rest.
-This dramatic up-weighting drowns out the EoR signal, giving rise to signal loss.
-Additionally, most of our power spectrum information is coming from only the last few modes and as a result, is a noisier estimate.
+\cc{math?} This dramatic up-weighting drowns out the EoR signal, giving rise to signal loss.
+Additionally, most of our power spectrum information is coming from only the last few modes and as a result, it is a noisier estimate.
 This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
 
-Using our toy model, we have seen that a sensitivity driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates.
+Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates.
 Longer integrations increase sensitivity but reduce the number of independent samples, resulting in steep drop-offs in eigenspectra.
-For PAPER-64 data, we see $\sim3$ orders of magnitude of signal loss when combining the use of an optimal fringe-rate filter and inverse covariance weighting.
-
-\subsubsection{Toy Model: Other Weighting}
-
-In a previous section we showed how altering an eigenspectrum can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
-We will now use our toy model to describe several other ways to alter a covariance matrix $\textbf{C}$ in order to minimize signal loss.
+
+\subsubsection{Toy Model: Other Weighting Options}
+\label{sec:otherweight}
+
+In Section \ref{sec:toymodel} we showed how altering $\textbf{C}$ can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
+We will now use our toy model to describe several other ways to tailor $\textbf{C}$ in order to minimize signal loss.
+We illustrate the resulting power spectra and eigenspectra for four different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
 
 As a first test, we know that our simulated EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\textbf{C}_{FG} = \textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}$ to obtain a final $\textbf{C}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\textbf{C}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$ to obtain a final $\textbf{C}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\textbf{C}$ would).
+This is evident when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}.
+We don't see perfect EoR recovery though, as the green and red curves differ at one $k$ value in Figure \ref{fig:toy_sigloss8}.
+This deviation is a consequence of the difference between the true and modeled covariance matrices.
 
@@
 
-The next three panels of Figure \ref{fig:toy_sigloss8} each involve methods that regularize the matrix $\textbf{C}$ after it is computed from the foreground + EoR dataset.
-By regularizing $\textbf{C}$, we are flattening out its eigenspectrum.
-Therefore, some modes will be down-weighted, but the rest will be treated with similar weights.
-Hence, we won't be up-weighting the last few noisy modes.
-
-Regularization schemes that we are highlighting here are adding an identity matrix to $\textbf{C}$ (Figure \ref{fig:toy_sigloss8}, upper right), killing all but the first three eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).
-Each avoids signal loss, but it is clear that two of the methods down-weight foregrounds much better than the third.
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
+	\caption{We compare the eigenspectrum of an empirically calculated $\textbf{C}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\textbf{C}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\textbf{C}$ (yellow), and multiplying an identity matrix to $\textbf{C}$ (magenta).
+}
+	\label{fig:toy_sigloss14}
+\end{figure}
+
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\textbf{C} = \textbf{C} + \textbf{I}$.
+By adding the identity, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum \cc{why?}.
+
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\textbf{C}$ a different way - by zeroing all but the first three eigenmodes.
+This means that the first three eigenmodes will be given weights (the three highest variance modes will be down-weighted), but the rest will be treated with similar weights.
+Hence, we avoid up-weighting the last few noisy modes and have negligible signal loss.
+However, we do not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
+
+The last regularization scheme we are highlighting here is setting $\textbf{C} = \textbf{C} \cdot \textbf{I}$.
+In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
 For this toy model, our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Therefore, when multiplying $\textbf{C}$ by an identity matrix, we are only preserving correlations between the same frequencies.
-Because we killed off information from all other frequency combinations, we do a poor job suppressing the foreground.
-
-Although this method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may work better than others based on the dataset.
-One may imagine a situation where a particular systematic is contained to an isolated frequency.
+Multiplying by the identity results in a diagonal matrix, meaning we are only left with correlation information between the same two frequencies.
+Because we disregard information from all other frequency combinations, we do a poor job suppressing the foreground.
+But because we flattened the eigenspectrum, we also avoid signal loss.
+
+Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may work better than others based on the dataset.
+\cc{how to make this paragraph less hand-wavy?} One may imagine a situation where a particular systematic is contained to an isolated frequency.
 In such a case, preserving only the diagonal elements of $\textbf{C}$ would be an effective way of removing this contamination.
@@
 Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal.
-Inverse covariance weighting is an optimal weighting scheme for dealing with foregrounds, but its aggressiveness results in sloped eigenspectra shapes, the overfitting of noise, and thus signal loss.
-The application of a fringe-rate filter heightens this effect by reducing the number of independent samples and steepening eigenspectra further.
-Rather than use inverse covariance weighting, there are several alternate ways to regularize covariance matrices and flatten out eigenspectra to minimize signal loss.
-In Section \ref{sec:Sigloss}, we apply the lessons we've learned about signal loss and its interaction with fringe-rate filtering and inverse covariance weighting to PAPER-64 data.
+As we investigated however, there are trade-offs between the weighting method used, its foreground-removal effectiveness, and the amount of resulting signal loss.
 
@@
 
-Two ways of estimating errors on a power spectrum measurement are exploring the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
+Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate confidence intervals for our measurements.
+Two ways of estimating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
 In a perfect world, both methods would match up.
-However, in practice the two don't always agree due to contaminates in the data that prevent it from being perfectly noise-limited.
+However, in practice the two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform weightings.
 Therefore, it is important to place error bars on our measurements that have been derived from its inherent variance.
 
-A common technique used to estimate the variance in a dataset is bootstrapping.
-Bootstrapping is a metric that relies on sampling with replacement and allows the estimation of a sampling distribution.
-For example, power spectrum measurements of $21$ cm data can be made along many axes, including time and baselines.
-Through the process of bootstrapping along these axes, we can obtain error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
-
-Again, we focus on simple toy models to highlight two traps that one can fall into when bootstrapping power spectra.
-Suppose we have a Gaussian random noise dataset of length $1000$ and variance of $1$.
-We are interested in the average of the dataset, and therefore predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples (in this case, $1000$).
-
-We form $100$ bootstraps, each comprised of an array of length $1000$ that is created by random sampling the original data with replacement.
+A common technique used to estimate the error in a measurement is bootstrapping.
+Bootstrapping uses sampling with replacement to estimate a posterior distribution.
+For example, power-spectral measurements of $21$ cm data can be made along many axes, including time and baselines.
+Through the process of resampling and averaging along these axes, we can estimate error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
+
+Again, we focus on toy models to highlight traps that one can fall into when bootstrapping power spectra.
+Suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance.
+We are interested in the average of the dataset, and predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+We form $100$ bootstraps, each comprised of an array of length $1000$ that is created by a random resampling of the original data, with replacement.
 The standard deviation over the $100$ bootstraps gives an error estimation for our dataset.
-As shown in Figure \ref{fig:toy_error1} (grey star), the error computed from bootstrapping matches our theoretical prediction.
-
-One major caveat of bootstrapping is that the method is no longer valid when working with correlated data.
-In other words, bootstrapping assumes completely independent samples.
-Therefore, the use of a fringe-rate filter, which averages data in time to increase sensitivity, creates a situation in which bootstrapping can under-estimate errors.
+As shown in Figure \ref{fig:toy_error1}, the error computed from bootstrapping matches our theoretical prediction.
+
+One major caveat of bootstrapping arises when working with correlated data.
+If, for example, a dataset has many repeated values inside it, this would be reflected in each bootstrap.
+The same value would be present multiple times within a bootstrap and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are many of them.
+Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates errors.
+The use of a fringe-rate filter, which averages data in time to increase sensitivity, is one example which leads to a reduction in the number of independent samples, creating a situation in which errors can be under-estimated.
 We will now show this effect using our toy model.
@@
 Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent samples to $1000/10 = 100$.
-Bootstrapping this time-averaged noise, using the same exact method as described earlier (drawing the same number of samples as the length of the dataset), under-estimates the error by a factor of $\sim3$.
-This occurs because we are drawing more samples than independent ones available.
+Bootstrapping this time-averaged noise, using the same method as described earlier (drawing the same number of samples as the length of the dataset), under-estimates the error by a factor of $\sim3$.
+This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
 In fact, the error derived from bootstrapping is a strong function of the number of samples that are drawn (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
-However, in this case we know that we have $100$ independent samples, and the error associated with drawing $100$ samples with replacement does match the theoretical prediction as expected.
-
-This examples highlights the importance of understanding how analysis techniques (like a fringe-rate filter) can affect a common statistical procedure (like bootstrapping).
-Bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires precise knowledge of the number of independent samples, which is not a trivial task.
+However, if we know that we have $100$ independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction.
+
+This examples highlights the importance of understanding how analysis techniques (e.g.
+fringe-rate filtering) can affect a common statistical procedure like bootstrapping.
+Bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
+For example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the number of averages performed.
+Additionally, we can have a non-integer effective number of samples due to the weighting.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
-	\caption{Power spectrum error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
-The grey star represents the error associated with drawing $1000$ samples from a length $1000$ array of random noise.
-The black points correspond to time-averaged data and illustrate how errors can be underestimated if drawing more samples than independent ones in the data.
-There are $100$ independent samples in the time-averaged data --- hence, using this number does indeed match the theoretical error prediction.}
+	\caption{Error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
+The star represents the error associated with drawing $1000$ samples from a length $1000$ array of a Gaussian random signal.
+The black points correspond to time-averaged data which has $100$ independent samples.
+They illustrate how errors can be underestimated if drawing more samples than there are independent samples in the data.
+The estimated errors match up with the theoretical prediction only at $N=100$.}
 	\label{fig:toy_error1}
@@
 We will now discuss a second subtle feature of bootstrapping that can lead to an over-estimation of errors.
-Suppose we have $1000$ baselines (another appropriate axis for bootstrapping power spectra), each an independent measurement of the sky.
-Bootstrap theory requires a bootstrap to comprise of some combination of the $1000$ baselines.
-If all $1000$ spaces are filled randomly, there is in fact a high probability that baselines will be repeated in a sample (sometimes many times).
-Thus, bootstrapping in this way negatively affects power spectrum sensitivity because the number of independent baselines in a sample can be significantly lower than the total number of baselines.
-
-In order to maximize sensitivity, we use a slightly modified bootstrapping method.
-We first shuffle all the baselines for a bootstrap, take the first $999$, and then fill the last slot randomly with replacement.
-There's a small chance it will yield $1000$ independent samples, but even with $999$ our sensitivity is nearly maximized.
-One may wonder whether this change is still a legitimate way of error estimating since the number of possible random samples for a single bootstrap has dramatically decreased.
-However, as long as this number is still much greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
-
-For our toy model, the fraction of independent baselines using this method ($999/1000$) is over $1.5$ times greater than the aforementioned approach.
-These two methods converge for small numbers of samples, when filling a few spots randomly is nearly the same as filling only the last spot randomly.
-The evolution of both of these methods as a function of number of baselines is shown in Figure \ref{fig:toy_error2}.
-In order to reduce the number of baselines, we divide our $1000$ baselines into $N$ groups, where the number of baselines in a group is $1000/N$.
-No baselines are repeated within or between groups, until a bootstrapping method is applied to each (either sampling all elements with replacement, or only the last one).
-
-It is clear that the fraction of independent baselines in a group is always greater using our revised sampling approach, with the greatest discrepancy for small number of groups (large number of baselines per group).
-The more baselines per group, the more sensitivity we can gain by ensuring that most of the baselines are independent ones.
-An analog for the y-axis in Figure \ref{fig:toy_error2} is therefore the final power spectrum sensitivity in temperature-squared space, which decreases as the square root of the number of baselines that are averaged together for a measurement.
-
-In summary, bootstrapping is still an effective and straightforward way to estimate errors of a dataset.
-However, one must be careful about violating independence assumptions, as it is possible to under-estimate errors by over-sampling data.
-Additionally, small changes in the way a dataset is randomly sampled can ensure that its overall sensitivity is maximized.
+Suppose we have $5$ independent measurements of the sky (from $5$ different baselines, for example).
+A bootstrap then consists of $5$ measurements that are drawn randomly with replacement from the original set.
+If all $5$ spaces are filled randomly, there is a high probability that some measurements will be repeated in the bootstrap because they are drawn more than once.
+The bootstrap may therefore consist of only $3$ or $4$ independent measurements --- a number smaller than the total number of samples.
+In fact, the probability of drawing $5$ completely independent measurements is less than $4\%$.
+
+In order to maximize sensitivity, we desire as many independent samples as possible. However, solely using all $5$ independent measurements does not allow variation between bootstraps.
+
+Therefore, we use a slightly modified bootstrapping method.
+For each bootstrap, we first shuffle the data.
+Next, we take the first $4$ samples, and fill the last slot randomly with replacement.
+In doing so there is a small chance a bootstrap will consist of $5$ independent samples, but even with $4$ our sensitivity is nearly maximized.
+One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
+However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset \cc{explain why}.
+
+In Figure \ref{fig:toy_error2} we compare the two methods of bootstrapping: sampling all elements randomly (black points) versus sampling just the final element randomly (grey points).
+The two converge for datasets with small numbers of elements, when filling a few spots randomly is nearly the same as filling only the last spot randomly.
+However, there is also increased scatter in this regime due to small number statistics.
+
+The difference between the two methods is most pronounced for datasets with large numbers of elements.
+As a dataset grows in size, it becomes increasingly rare to draw entirely independent samples, and thus the benefit of ensuring, say, $999$ independent samples out of $1000$ is most noticeable.
+The more elements in our dataset, the more sensitivity we can gain by mandating that most of our measurements are independent ones.
+An analog for the y-axis in Figure \ref{fig:toy_error2} is therefore the sensitivity of a final power spectrum measurement.
+
+In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset.
+However, we have illustrated two situations in which bootstrapping can lead to inaccurate error estimation.
+Trade-offs exist between averaging data and the validity of bootstrapping --- working with correlated data gives rise to questions concerning the effective number of independent samples, how to best calculate it, and whether it is valid to simply use that number when bootstrapping.
+We have also shown a situation in which a naive bootstrapping method can over-estimate errors, thereby compromising measurement sensitivity.
+While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain analysis choices have compromised the method and whether a variation of traditional re-sampling could be preferred instead.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
-	\caption{Fraction of independent baselines in a baseline group as a function of the number of baselines in a group.
-A fraction of $1.0$ means that all baselines in a group are independent, and therefore sensitivity is maximized (alternatively, this axis can be treated as a power spectrum sensitivity in temperature-squared space).
+	\caption{The fraction of independent elements in a bootstrap as a function of the total number of elements in a dataset.
+A fraction of $1.0$ means that all elements in a bootstrap are independent, and therefore sensitivity is maximized (alternatively, this axis can be thought of as power spectrum sensitivity).
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
-The former over-estimates error bars since some baselines end up being repeated due to random sampling.
-Therefore, baseline sensitivity is not maximized to its full capacity.}
+The former over-estimates error bars since some elements end up being repeated due to random sampling.
+Therefore, sensitivity is not maximized to its full capacity.}
 	\label{fig:toy_error2}
 \end{figure}
-
-We have discussed the interplay between two of our power spectrum techniques --- fringe-rate filtering and bootstrapping --- and how they affect the theme of error bar estimation.
-In addition to these, inverse covariance weighting can also affect error bars.
-Specifically, a power spectrum measurement and its errors are susceptible to blowing up when the number of non-zero eigenmodes are less than the number of independent samples in a dataset (i.e.
-the covariance matrix is not full rank).
-\cc{Not really sure how to explain this or how much detail to get into here...}
-
-Our fourth power spectrum technique, jack-knife testing, is also related to error estimation.
-Splitting data along various axes and performing the same power spectrum analysis on each provides a test of robustness.
-If the same errors are obtained for each data subset, we can have confidence that they are unbiased.
 
@@
 
-There are several sources of bias that could leak into a power spectrum measurement, including noise and foreground biases.
-In this section we will describe analysis techniques that help mitigate these effects and how jack-knife tests can tease out biases that are present in data.
-Ultimately, while different weighting and data combination techniques can help identify and remove biases, it is important to remember that a true detection of EoR will be robust to these tests.
-In other words, detections that aren't stable across multiple jack-knives are likely false ones and attributable to systematic errors.
-
-Noise bias can arise in multiple ways.
+A power spectrum detection could be EoR, but it could also be attributed to other sources of bias.
+Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of $21$ cm data analyses.
+In this section we will discuss possible sources of bias in a measurement, as well as techniques that can help mitigate their effects.
+We will also present a series of essential tests that a legitimate EoR detection must pass and highlight how these tests can be used to identify biases.
+These tests serve as a a starting point for the necessary task of verifying a future EoR detection.
+
+\subsubsection{Foreground and Noise Bias}
+
+Foreground bias is perhaps one of the main limiting factors pushing up against $21$ cm results.
+Foreground signals lie $\sim4$-$5$ orders of magnitude above the cosmological signal, and there are many existing techniques to avoid or remove these strong signals.
+Despite current best efforts to do so, however, there remains some foreground leakage that can show up as detections in a power spectrum.
+\cc{how do we know that?}
+
+Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or $k$ modes.
+For a particular baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between the two antennas in the baseline.
+For longer baselines, this value increases, producing what is known as ``the wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; \citealt{thyagarajan_et_al2013}).
+The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is proportional to $k_{\parallel}$).
+Properties of the wedge can be used to isolate and remove foregrounds, as done by \citet{ali_et_al2015}, \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
+
+Despite making power spectrum measurements outside of the wedge in the ``EoR window", foreground detections are still common at low $k$ values.
+This leakage can be attributed to convolution kernels associated with Fourier-transforming visibilities into delay-space.
+In other words, smooth-spectrum foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
+
+There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from spreading to high $k$ values.
+For example, narrow window functions can be used to minimize the covariance of a particular $k$ value with other ones (\citealt{liu_et_al2014b}).
+\cc{math!} In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
+The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (Section \ref{sec:PS}).
+Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode \cc{develop more}.
+
+Confirming foreground detections at higher $k$'s is more difficult. In the next section, we will present some tests that can help distinguish these excesses from that of EoR.
+
+In addition to foreground bias, noise bias can also be responsible for positive power spectrum detections.
+One example is noise bias arising if thermal noise is multiplied by itself.
 Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise.
 We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating longer, using more baselines, etc.
-However, a noise bias can result if the same thermal noise is multiplied by itself.
-This squaring of noise occurs when cross-multiplying visibilities to enter temperature squared space and results in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument.
+However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by the two copies of $\textbf{x}$ in Equation \ref{eq:qhat}.
+If both copies of $\textbf{x}$ come from the same baseline and time, it can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument.
 One way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days.
@@
 
-Another way of introducing a noise bias into data is via cross-talk subtraction.
-Cross-talk is caused by the cross-coupling of signals between antennas and shows up as a constant bias in time in visibilities.
-For PAPER-64, cross-talk is removed during redundant calibration, when the deviation from an average visibility (across similar baseline types) is subtracted off of each visibility.
-This type of removal preserves signals common to all baselines, such as the EoR signal, but also has the consequence of introducing a low level bias.
-This bias term comes from the averaged cross-talk across a redundant baseline group and hence every baseline has a piece of all the other baseline's (of the same type) noise.
-One way to remove this noise bias is with the use of a fringe-rate filter, which can be chosen to filter out static signals (i.e.
-filter out zero `fringe-rates').
-
-Foreground bias is perhaps one of the main limiting factors pushing up against $21$ cm results.
-Foreground signals lie $\sim4-5$ orders of magnitude above the cosmological signal, and there are many existing techniques to avoid or remove these strong signals.
-Despite current best efforts to do so, however, there remains some foreground leakage that can show up as detections in a power spectrum.
-This leakage is strongest at low $k$ values, corresponding to large spatial scales on the sky.
-
-As with noise bias, there are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from spreading to high $k$ values.
-Narrow window functions can be used to minimize the influence of a particular $k$ value on other ones (\cc{citation?}).
-This in turn compromises power spectrum sensitivity (narrow window functions increases errors for each $k$-mode) as a trade-off for the minimization of foreground leakage.
-Another option is to construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
-The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (Section \ref{sec:PS}).
-
-One last source of foreground bias that we will highlight here is polarization leakage.
-When forming Stokes I from $XX$ and $YY$ polarization visibility data, we ignore the beam asymmetry between the two.
-This mismatch can cause leakage from Stokes Q ($V_{Q} = \frac{1}{2}(V_{XX}-V_{YY})$) into Stokes I ($V_{I} = \frac{1}{2}(V_{XX}+V_{YY})$).
-Another way of describing this leakage is that Faraday Rotation, which causes a rotation of the polarization angle of a signal, can induce spectral structure at certain delays (\citealt{moore_et_al2013}).
-This type of sky bias is dependent on rotation measures, which characterize the amount of polarization rotation.
-If a particular rotation measure is such that a Stokes Q signal ends up falling at a power spectrum delay of interest, the Stokes I result for that $k$ would be biased.
-
-One preventative measure for polarization leakage could be tailoring a fringe-rate filter in a way that improves the match between $XX$ and $YY$ polarization beams (\citealt{parsons_et_al2016}).
-There are also multiple ways of tracing a power spectrum detection to a polarization bias.
-One can look at Stokes Q power spectra to estimate the amount of expected leakage (\citealt{moore_et_al2013}).
-In addition, jack-knife tests can be used to investigate whether polarization leakage affects a result.
-For example, rotation measures are highest when observing into the Galactic plane due to increased Faraday rotation (\cc{citation?}), so one could imagine looking at different rotation measure bins along the Galactic latitude axis in order to identify whether a strong rotation measure coincides with a particular power spectrum bias.
-
-In general, jack-knife tests are helpful in revealing a range of biases, including polarization and foreground biases.
-Slicing data along LST, for example, can determine whether excess detections are traceable to certain foreground sources.
-Slicing along baselines can uncover poorly operating baselines, or baselines whose weighting matrices aren't properly down-weighting foregrounds.
-Jack-knives can be taken along polarization axes, the frequency axis, daily axes, etc., and each can help trace a bias to a physical reason.
-A real $21$ cm signal, however, should exist regardless of these tests, making jack-knives crucial for confidence in a successful EoR detection.
+Another type of noise bias can stem from the spurious cross-coupling of signals between antennas.
+This excess is known as instrumental crosstalk and is an inadvertent correlation between two independent measurements via a coupled signal path.
+Crosstalk appears as a constant phase bias in time in visibilities, and it varies slowly compared to the typical fringe-rates of sources.
+Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters.
+However, there remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any suppression techniques.
+
+In the next section, we approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful jackknife tests.
+
+\subsubsection{Jackknife Tests}
+
+The jackknife is a resampling technique in which a statistic (i.e.
+power spectrum) is computed multiple times using subsets of the data.
+In this section we define two main tests --- the null test and the traditional jackknife --- and explain how a power spectrum detection must pass each.
+We then highlight how these tests can be used to help distinguish between different sources of bias.
+
+\begin{itemize}
+\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to investigate underlying systematics.
+A clean measurement should be noise-like (a `null' result) if it is not dominated by systematics.
+There are several ways to perform null tests on data, as implemented in \citet{keating_et_al2016}.
+For example, one can divide data into two subsets by separating odd and even julian dates, or the first half of the observing season from the second.
+Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR.
+The resulting power spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs from one of the data subsets to the other (i.e.
+doesn't get subtracted perfectly).
+\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill confidence in a final result, since a stable result should be consistent through all of them.
+A successful EoR detection must be steadfast throughout all jackknives no matter how the data is sliced, while other sources of bias may come and go depending on the jackknife performed.
+Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a power spectrum each time as a day of data is removed, or a baseline is removed.
+This type of jackknife would reveal bias present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
+\end{itemize}
+
+While the null test hunts for deviations from thermal noise and the jackknife tests for deviations in subsamples, they are both closely related.
+We can highlight the connection between the two using a toy model dataset.
+
+Suppose we divide the toy model dataset into two subsets, $\textbf{x}_{1}$ and $\textbf{x}_{2}$, which represent jackknives of the complete dataset $\textbf{x}$.
+Both subsets have dimensions of $100$ time integrations and $20$ frequency channels, similar to the toy model used in Section \ref{sec:toymodel}.
+They also have the same level of thermal noise, constructed as a Gaussian random signal for each.
+Identical EoR signals, also constructed as a Gaussian random signal, are in both subsets.
+
+The subsets differ in that only one of them contains a foreground signal (a single complex sinusoid) on top of the noise and EoR, representing a bias that only appears for half the data.
+Mathematically,
+
+\begin{eqnarray}
+\textbf{x}_{1} &=& \textbf{n}_{1} + \textbf{e} + \textbf{fg} \\
+\textbf{x}_{2} &=& \textbf{n}_{2} + \textbf{e}
+\end{eqnarray}
+
+\noindent where $\textbf{n}$ is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal.
+
+We do not perform a time-average or apply a fringe-rate filter to this toy model, since we are interested only in what jackknife tests can tell us about biases.
+For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to avoid signal loss.
+We form $5$ different power spectrum estimates: $\hat{\textbf{p}}$ (full dataset), $\hat{\textbf{p}}_{1}$ (subset $1$), $\hat{\textbf{p}}_{2}$ (subset $2$), $\hat{\textbf{p}}_{noise}$ (noise only), and $\hat{\textbf{p}}_{null}$, which is the result of our differenced dataset $\textbf{x}_{null}$, defined as:
+
+\begin{equation}
+\textbf{x}_{null} = \textbf{x}_{1} - \textbf{x}_{2}. 
+\end{equation}
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
+	\caption{Power spectrum estimates for the full toy model dataset $\textbf{x}$ (green), the differenced dataset $\textbf{x}_{1}-\textbf{x}_{2}$, which represents a null jackknife test (black), and noise alone (red).
+Because $\hat{\textbf{p}}_{null}$ is not consistent with noise, it suggests the presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
+Null tests of clean measurements should be consistent with thermal noise.}
+	\label{fig:toy_bias1}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
+	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model.
+They suggest the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses.
+Clean measurements should remain consistent despite the jackknife taken.}
+	\label{fig:toy_bias2}
+\end{figure}
+
+In Figure \ref{fig:toy_bias1}, we compare $\hat{\textbf{p}}_{null}$, $\hat{\textbf{p}}_{noise}$, and $\hat{\textbf{p}}$.
+Our goal is to determine whether the excess we see in $\hat{\textbf{p}}$ (the power spectrum peak) is due to the EoR signal, something we would not know for a real dataset.
+The null test reveals that there is also an excess in $\hat{\textbf{p}}_{null}$ --- hence, we can rule out EoR.
+Because this is a toy model, we know that the excess is attributable to the foreground signal that did not get subtracted off for the null test.
+
+Additionally, we look at the jackknife results, namely $\hat{\textbf{p}}_{1}$ and $\hat{\textbf{p}}_{2}$.
+The results are shown in Figure \ref{fig:toy_bias2}.
+Again, we see a clear difference between the two, signifying a non-EoR bias that is only present in one subset.
+
+While the null test is useful for ruling out EoR, jackknives are useful in pinpointing which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $\hat{\textbf{p}}_{1}$.
+If foreground or noise biases exist in a dataset, jackknives can tease them out and provide insight into possible sources.
+For example, if jackknives along the time-axis reveal a bias present at a certain LST, a likely explanation would be excess foreground emission from a radio source in the sky at that time.
+A jackknife test involving data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed with the filter, or if similar-shaped detections in both power spectras suggest otherwise.
+There are many other jackknife axes of which we will not go into detail here, including baseline, frequency, and polarization.
+Ultimately, an EoR detection should persist through them all and a clean measurement should pass all null tests.
+
+In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum detection.
+In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data.
 
@@
 
-Now that we have developed our intuition regarding signal loss, error estimation, and bias, we will look at each in more detail as applied to data taken by PAPER.
-We begin with an overview of the telescope array, its observations, and analysis pipeline.
-
-\subsection{Observations}
-\label{sec:Obs}
-
-The Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER) is a dedicated 21 cm experiment located in the Karoo Desert in South Africa.
-The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements, each 2 m on a side.
-The antenna layout is formatted in a grid layout (Figure \ref{fig:paper}), with 8 antennas on a side, 30 m spacing between antennas along the East/West direction, and 4 m spacing between antennas along the North/South direction.
-For the rest of this paper, we focus on data from only the 30 m pure East/West baselines.
-
-\begin{figure*}
-	\centering
-	\includegraphics[height=0.35\textwidth]{plots/paper_dipole.png}
-	\includegraphics[height=0.35\textwidth]{plots/antenna_layout.png}
-	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
+In the previous sections we have discussed three overarching $21$ cm power spectrum themes --- signal loss, error estimation, and bias.
+Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of a power spectrum result.
+
+We now present a case study of these same three themes using data from the PAPER experiment.
+We use the intuition we've developed through our toy model simulations in order to make smartly-motivated data analysis choices for PAPER.
+In light of our new understandings, we also highlight major changes since \citet{ali_et_al2015}.
+
+As a brief review, PAPER is a dedicated $21$ cm experiment located in the Karoo Desert in South Africa.
+The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements (Figure \ref{fig:paper}) that are arranged in a grid layout.
+For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines, of which there are a total of $56$.
+For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and \citet{ali_et_al2015}.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/paper_dipole.png}
+	\caption{PAPER dipole in South Africa.}
 	\label{fig:paper}
-\end{figure*}
-
-PAPER-64 observed for a total of 135 nights between 2012-2013.
-The correlator processes a bandwidth of 100-200 MHz, corresponding to a redshift range of 6-12.
-For more information about the backend system of PAPER-64 and its observations, we refer the reader to \cc{??} and \citet{ali_et_al2015}.
-
-Because there is a detailed discussion of the PAPER-64 data reduction pipeline in \citet{ali_et_al2015}, here we will only briefly summarize the data processing steps prior to the power spectrum analysis.
-
-Beginning with compressed data products which have been cleaned of radio frequency interference (RFI) at the $6\sigma$ level and then down-sampled (to $42.9$ s integrations, $203$ frequency channels), we then employ the technique of redundant calibration as a means of calibrating for individual antenna gains without needing to use information about the sky.
-Because PAPER is laid out on a grid, antenna calibration parameters can be found through the use redundancy.
-Namely, baselines of the same length and orientation should measure the same sky signal, but in practice there are differences due to instrumental effects caused by antennas, cables, and receivers.
-Using the basis of redundancy, however, allows us to set up a system of equations to solve for a complex gain per antenna that brings all baseline of a particular type into alignment.
-We perform these computations using the package OMNICAL (\citealt{zheng_et_al2014}).
-
-We next solve for the array's overall phase and gain calibration parameters using a standard self calibration method.
-We used radio sources Pictor A, Fornax A, and the Crab Nebula to fit for an overall phase solution, and set our overall flux scale using Pictor A as a calibrator source.
-Although PAPER-64 data exists for all $4$ polarizations, we only use the $xx$ and $yy$ polarization data to form Stokes I visibilities as $V_{I} = \frac{1}{2}(V_{XX} + V_{YY})$.
-
-Eliminating bright foregrounds remains a challenging yet crucial component of any 21 cm data analysis.
-There are many techniques to go about foreground removal, including spectral polynomial fitting, principle component analysis, Fourier-mode filtering, non-parametric subtractions, and inverse covariance weighting.
-PAPER uses a delay-spectrum filtering method which was first explained and applied in \citet{parsons_et_al2014}.
-In short, the delay-filtering technique employs the spectrally smooth nature of foregrounds, which are consequently localized in delay-space, the Fourier dual to frequency.
-We subtract all components that fall within the horizon limit for a specific baseline type in delay-space, plus a $15$ ns buffer, thus gaining about $\sim4$ orders of magnitude in sensitivity.
-
-After removing an additional layer of RFI (values $3\sigma$ above the median), we average together all our data into two datasets: even julian dates and odd julian dates.
-A total of $124$ nights of data comprises this average.
-
-Finally, our last analysis step before power spectrum estimation is the use of a fringe-rate filter.
-As shown in \citet{parsons_et_al2016}, a fringe-rate filter allows us to maximize our sensitivity even further by averaging visibilities in time.
-We apply this filter in the fringe-rate domain, the Fourier-dual to time, and it effectively amounts to increasing our data's integration time.
-Another way to describe the filter is that it weights different parts of the sky (which rotate at different ``fringe-rates") by the antenna beam.
-This allows us to up-weight parts of the sky high in the primary beam, and down-weight those that are less sensitive.
+\end{figure}
+
+%\begin{figure*}
+%	\centering
+%	\includegraphics[height=0.35\textwidth]{plots/paper_dipole.png}
+%	\includegraphics[height=0.35\textwidth]{plots/antenna_layout.png}
+%	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
+%	\label{fig:paper}
+%\end{figure*}
+
+The previously best published $21$ cm upper limit result from (\citealt{ali_et_al2015}) uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
+
+\begin{equation}
+\Delta^{\textbf{2}}\textbf{(k)} = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)},
+\end{equation}
+
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
+The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the case study.
+
+We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} only by the fringe-rate filter.
+In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
+This was chosen in order to increase the number of independent modes and reduce signal loss.
+With the development of a robust method for assessing signal loss, we feel comfortable using a narrow filter --- the optimal fringe-rate filter --- in order to maximize sensitivity.
+This filter is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
+The filter in both the fringe-rate domain and time domain is shown in Figure \ref{fig:frp}.
 
@@
 	\includegraphics[width=\columnwidth]{plots/frp.png}
-	\caption{The optimal fringe-rate filter used in the analysis, normalized to $1$.}
+	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and Stokes I polarization beam.
+Bottom: the time-domain convolution kernel corresponding to the top panel.
+Real and imaginary components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black.
+The fringe-rate filter acts as an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
 	\label{fig:frp}
@@
 
-New to our updated PAPER-64 analysis is the use of an optimal fringe-rate filter, which maximizes our sensitivity.
-In \citet{ali_et_al2015}, the filter that was applied was degraded by widening it in fringe-rate space.
-This was chosen in order to decrease the resulting integration time, therefore increasing the number of independent modes and reducing signal loss associated with applying inverse covariance weighting on data with too few modes.
-
-With the development of a robust method for assessing signal loss (see Section \ref{sec:Sigloss}), we feel comfortable using a narrow filter (Figure \ref{fig:frp}), which yields an effective integration time of $3857$ s (see Section \ref{sec:PSSense} for calculation) and $8$ total independent modes for our $8.5$ hours of LST.
-The filter is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
-It is then implemented on a per baseline basis by convolving the time-domain visibilities with the Fourier transform of the fringe-rate filter, resulting in averaged visibilities yielding $\sim 2$ orders of magnitude in sensitivity.
-
-\subsection{Power Spectrum Estimation}
-\label{sec:PS}
-
-To form power spectrum quantities using our two fringe-rate filtered, LST-binned datasets, we use OQE methods as summarized in Section \ref{sec:SiglossOverview}.
-Here we will describe its application to PAPER-64 data.
-
-We have a $2$-dimensional data vector $\textbf{x}$ for each baseline and data group (`even' or `odd').
-As part of our bootstrapping routine (and to speed things up), we divide up our total number of baselines into $5$ random, equal-sized groups (the way we bootstrap baselines into groups is explained in Section \ref{sec:Boot}).
-Taking $\textbf{x}$ to be the averaged data from all baselines within a group, we now have $10$ possible data vectors (for $5$ groups and $2$ datasets).
-
-Notice that there are two quantities of $\textbf{w}\textbf{x}$ in the expression for $\hat{\textbf{q}}$ in Equation \ref{eq:qhat}, representing two copies of weighted data.
-We perform all possible cross-multiplications of this quantity, except between the same datasets (`even' with `even', for example) and same groups (`baseline group 1' with `baseline group 1', for example).
-We avoid these computations to prevent the introduction of noise biases from shared auto power.
-
-As mentioned previously, we have a choice for our normalization matrix $\textbf{M}$.
-For our analysis, we choose to compute it by taking the Cholesky decomposition of $\textbf{F}$.
-Namely, we decompose the Fisher matrix such that $\textbf{F} = \textbf{L}\textbf{L}^{\dagger}$, where $\textbf{L}$ is a lower triangular matrix.
-Next, we construct $\textbf{M} = \textbf{D}\textbf{L}^{-1}$, where \textbf{D} is a diagonal matrix.
-Hence, our window function $\textbf{W} = \textbf{MF}$ becomes $\textbf{W} = \textbf{D}\textbf{L}^{\dagger}$ and is an upper triangular matrix.
-This window function was constructed in a way to prevent the leakage of foreground power from low $k$ to high $k$ modes.
-Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
-Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing foreground bias.
-
-In practice, our final power spectrum result is a $2$-dimensional quantity (a function of both time and $k$).
-We compute $20$ bootstraps of these quantities, where each bootstrap creates baseline groups randomly.
-We form both the quantity $\textbf{P(k)}$ and the folded version $\Delta^{2}\textbf{(k)}$, defined as:
-
-\begin{equation}
-\Delta^{\textbf{2}}\textbf{(k)} = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)}
-\end{equation}
-
-\section{Application: Signal Loss}
+\subsection{Case Study: Signal Loss}
 \label{sec:Sigloss}
 
-As detailed in Section \ref{sec:SiglossOverview}, signal loss can arise from the interplay between fringe-rate filtering and inverse covariance weighting.
-In this section, we explain a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss.
-Before doing so however, we first explain how noise and EoR are created in our power spectrum pipeline, both of which are used to verify signal loss.
-
-\subsection{Noise and EoR}
+As illustrated in Section \ref{sec:SiglossOverview}, signal loss can arise when data is weighted using information from itself.
+There are some weighting schemes which succeed at suppressing systematics but result in the loss of the cosmological signal, while others may preserve the signal along with contaminating ones.
+The data analyst has a choice for how to weight data, but it is crucial to be able to quantify the amount of signal loss associated with any lossy analysis step.
+In this section, we explain a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
+Before doing so however, we first explain how two additional channels --- noise and EoR --- are created in our power spectrum pipeline, both of which are used to verify signal loss.
+
+\subsection{Simulated Noise and EoR}
+\label{sec:simulations}
 
 One critical new component of our power spectrum pipeline is that we have many different power spectrum channels that simultaneously get processed at the same time and are especially useful for computing signal loss and sensitivity estimations.
-Two important channels, in addition to our PAPER-64 data, are a noise dataset and an EoR dataset (in addition to these, we also look at different combinations of all three).
+Two important channels, in addition to our PAPER-64 data, are a simulated noise dataset and an EoR dataset (along with different combinations of all three).
 We will briefly describe each.
 
-We create random noise with a variance determined by the sensitivity of our instrument in order to best represent the thermal noise level of our data.
+We simulate random Gaussian noise with a variance determined by the sensitivity of our instrument in order to best represent the thermal noise level of our data.
 We calculate our system temperature for our frequencies of interest as:
@@
 
-where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of data samples for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
-Our simulated noise has the same shape as our data, and we fringe-rate filter it in the same way to best mimic the real noise floor of our data.
+where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
+Our simulated noise has the same shape as our data, and we fringe-rate filter it using an identical optimal fringe-rate filter to best mimic the real noise floor of our data.
 
 A second additional important channel in our pipeline is a simulated EoR signal.
-We again simulate random noise (with a default scale of $1$) with the same shape as our data, and we fringe-rate filter this signal twice.
+We again simulate random Gaussian noise (with a default variance of $1$) with the same shape as our data, and we fringe-rate filter this signal twice using the optimal filter.
 The first filter transforms the unattached noise into a signal that's attached to the sky (i.e.
@@
 The second filter represents the fringe-rate filtering step in our data analysis pipeline.
-This fake EoR signal is injected on top of data at various amplitude levels in order to measure its loss.
+This mock EoR signal is injected on top of either data or noise at various amplitude levels in order to measure its loss.
 
@@
 
-The loss of a cosmological signal when analyzing PAPER-64 data is a real and significant issue.
-To reiterate, when applying inverse covariance weighting, $\textbf{C}^{-1}$ is empirically estimated from the data itself, which has the consequence of over-fitting the noise in the data, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters.
-This is especially prevalent when weighting fringe-rate-filtered data, which has so few independent time modes to begin with, leading to a noisier dataset.
+The potential loss of a cosmological signal when weighting PAPER-64 data is a real and significant issue.
+To reiterate, when applying a weighting matrix $\textbf{S}$ to data, which has been empirically estimated from the data itself, it has the consequence of over-fitting the noise, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters.
+This is especially prevalent when weighting fringe-rate filtered data, which has so few independent time modes to begin with, leading to a noisier dataset.
 Being able to accurately quantify this loss is crucial in interpreting and providing credibility to any power spectrum limits.
@@
 \begin{equation}
-\textbf{r} = \textbf{x} + \textbf{e}
+\textbf{r} = \textbf{x} + \textbf{e}.
 \end{equation}
@@
 Comparing the two quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
-Ignoring normalization, factors:
+Ignoring normalization factors:
 
@@
 \label{eq:sigloss}
-P_{out} \equiv \textbf{P}_{e} &=& \textbf{P}_{r}-\textbf{P}_{x} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} 
+P_{out} \equiv \hat{\textbf{p}}_{e} &=& \hat{\textbf{p}}_{r}-\hat{\textbf{p}}_{x} \nonumber \\
+&\propto& \textbf{r}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} 
 \end{eqnarray}
 
-It is noted that the output power spectrum is comprised of two terms: the power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.
-
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e}$.
-Expanding Equation \ref{eq:sigloss}:
+It is noted that the output power spectrum is comprised of two terms: the weighted power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.
+
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e}$.
+Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is made up of multiple terms:
 
 \begin{eqnarray}
-P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{w}_{r}\textbf{Q}\textbf{w}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{w}_{x}\textbf{Q}\textbf{w}_{x}\textbf{x} \nonumber 
+\label{eq:crossterm}
+P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} \nonumber \\
+&\propto& \textbf{x}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} 
 \end{eqnarray}
 
-And taking the case of very large $\textbf{e}$, so that $\textbf{w}_{r} \sim \textbf{w}_{e}$ and any terms involving only $\textbf{x}$ are small:
+Taking the case of very large $\textbf{e}$, so that $\textbf{S}_{r} \sim \textbf{S}_{e}$ and any terms involving only $\textbf{x}$ are small:
 
 \begin{eqnarray}
-P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{w}_{e}\textbf{Q}\textbf{w}_{e}\textbf{x}
+P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{x}
 \end{eqnarray}
@@
 An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since the two quantities are un-correlated.
-However, \cc{need explanation about power in cross-terms here}.
-Therefore, in our investigation of signal loss, we use the full quantity for $P_{out}$ as in Equation \ref{eq:sigloss}.
-
-For the unweighted case ($\textbf{w} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1.
-For the weighted case, this is not true due to signal loss.
+However, deeper investigations of these terms reveal that they contain non-negligible power.
+This power is negative, thereby reducing $P_{out}$ and increasing the amount of signal loss.
+In \citet{ali_et_al2015}, the cross-term power was ignored, resulting in an under-estimated signal loss.
+Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \ref{eq:sigloss}.
+
+For the unweighted case ($\textbf{S} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1.
+For the weighted case, this may not be true due to signal loss.
 In order to quantify the loss, we look at the ratio of $P_{in}$ to $P_{out}$ as the amplitude level of the injected signal \textbf{e} is increased.
-In the next section, we highlight two methods that yield similar results for the determination of signal loss using $P_{in}$ and $P_{out}$
+In the next section, we highlight two methods that yield similar results for the determination of signal loss using $P_{in}$ and $P_{out}$.
 
@@
 
-We now shift our attention towards computing signal loss for fringe-rate filtered PAPER-64 dataset, using inverse covariance weighting ($\textbf{w} = \textbf{C}^{-1}$).
-Our expressions for $P_{in}$ and $P_{out}$ become:
+We now shift our attention towards computing signal loss for our fringe-rate filtered PAPER-64 dataset.
+To recap, we use 30 m East/West baselines of PAPER-64.
+Our dataset spans $8$ hours of LST ($.5$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate filtered using an optimal fringe-rate filter.
+We have two datasets (even days and odd days), and only cross-multiply data from different days and different baselines.
+We are interested in $21$ frequency channels (channels 95-115), which yields a power spectrum for a redshift of $z=8.4$.
+
+While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{S} = \textbf{C}^{-1}$), which leads to substantial loss.
+With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
 
@@
 
-Using the input and output power spectra for range of EoR amplitudes, we use two methods to determine signal loss associated with the over-fitting of noise during inverse covariance weighting.
-
-\cc{Determine whether we want to show pure noise plots, or just data, or both!!!}
+Using the input and output power spectrum estimates for a range of EoR amplitudes, we next describe two methods to determine signal loss associated with the over-fitting of noise from inverse covariance weighting of PAPER-64 data.
+\cc{describing both methods may be overkill?}
 
 The first method is very straightforward.
-Post-bootstrapping, our final power spectra are 1-dimensional and only a function of $k$.
-For each $k$, we simply look at $P_{out}$ as a function of $P_{in}$, as shown in Figure \ref{fig:sigloss1_noise}.
+Post-bootstrapping, our final power spectrum estimates are 1-dimensional and only a function of $k$.
+For each $k$, we simply look at $P_{out}$ as a function of $P_{in}$, as shown in Figure \ref{fig:sigloss1_data}.
 The shape of this function can be explained as follows.
@@
 This is dangerous, because without correcting for this effect one might be led to underestimate the EoR signal.
-The peculiar tail at very low injection levels (where $P_{out} > P_{in}$) is an unphysical feature, but rather illustrates that there is some non-negligible cross-term power between $\textbf{n}$ and $\textbf{e}$.
-
-For this method, we interpolate the signal loss factor (per $k$), computed as $P_{in}/P_{out}$, at a $P_{out}$ value equal to the $2\sigma$ power spectrum upper limit of noise alone.
-In other words, we look at $P_{noise} \propto \textbf{n}^{\dagger}\textbf{C}_{n}^{-1}\textbf{Q}\textbf{C}_{n}^{-1}\textbf{n}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value.
+The peculiar tail at very low injection levels (where $P_{out} > P_{in}$) is not a physical feature, but rather illustrates that there is some non-negligible power in the cross-terms of Equation \ref{eq:crossterm} when $\textbf{e}$ is very small.
+
+For this method, we interpolate the signal loss factor (per $k$), computed as $P_{in}/P_{out}$, at a $P_{out}$ value equal to the $2\sigma$ power spectrum upper limit of our data.
+In other words, we look at $\hat{\textbf{p}} \propto \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value.
 We therefore end up with one signal loss correction factor per $k$.
@@
 	\centering
-	\includegraphics[width=1.0\textwidth]{plots/sigloss1_noise.png}
+	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
 	\caption{$P_{in}$ vs.
-$P_{out}$ (blue points) for 15 injection levels and 21 $k$'s.
-The solid cyan line is the $2\sigma$ upper limit for the weighted power spectrum of noise alone, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation.
+$P_{out}$ (black points) for 15 injection levels and 21 $k$'s.
+The solid grey line is the $2\sigma$ upper limit for the weighted power spectrum of PAPER-64 data, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation.
 \cc{Maybe re-do this plot with closer-together points}}
-	\label{fig:sigloss1_noise}
-\end{figure*}
-
-Figure \ref{fig:ps1_noise} shows the power spectrum of our noise simulation, using full inverse covariance weighting, both before and after signal loss correction.
-Prior to signal loss correction, it is obvious that the power spectrum is unfeasible because it is well below the theoretical noise level prediction.
-Post-correction, the power spectrum values blow up much higher than both the theory and unweighted power spectrum.
-This is an effect caused by the steep nature of the eigenspectrum of $\textbf{C}$, and is explained more in Section \ref{sec:Weight}.
-
-\cc{Need a plot that shows our signal loss factors are CORRECT. How to do that??}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise.png}
-	\caption{Full inverse covariance weighted power spectrum of pure noise (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
-The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction based on observational parameters.
-\cc{Color negative points grey}}
-	\label{fig:ps1_noise}
+	\label{fig:sigloss1_data}
 \end{figure*}
@@
 Instead of looking at input and output power spectra after bootstrapping, we now look at their values for every bootstrap in order to get a sense of their distributions.
-Figure \ref{fig:sigloss2_noise} plots $P_{in}$ vs.
-$P_{out}$ for $20$ bootstraps, and as expected, the function now has a spread in the width-direction in comparison to what was plotted in Figure \ref{fig:sigloss1_noise}, but otherwise shows a familiar trend.
-Similarly, our weighted noise power spectra also has a defined spread due to bootstrapping.
-
-Using these two distributions ($P_{in}/P_{out}$ and $P_{noise}$), we can create bins along the $P_{noise}$ axis to yield histograms of signal loss factors for each bin.
-We similarly sort the values of $P_{noise}$ into the same bins, and multiply the probability of $P_{noise}$ per bin (the number of values falling into that bin, divided by the total) with the signal loss factors in that bin, essentially computing a weighted average across all bins to obtain a final signal loss factor per $k$.
-As shown in Figure \ref{fig:ps2_noise}, the results are very similar to the previous method.
+Figure \ref{fig:sigloss2_data} plots $P_{in}$ vs.
+$P_{out}$ for $20$ bootstraps, and as expected, the function now has a spread in the width-direction in comparison to what was plotted in Figure \ref{fig:sigloss1_data}, but otherwise shows a familiar trend.
+Similarly, our weighted power spectra also has a defined spread due to bootstrapping.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
+	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. The transparent grey region represents all PAPER-64 bootstrapped estimates.}
+	\label{fig:sigloss2_data}
+\end{figure*}
+
+Using these two distributions ($P_{in}/P_{out}$ and $\hat{\textbf{p}}$), we can create bins along the $\hat{\textbf{p}}$ axis to yield histograms of signal loss factors for each bin.
+We similarly sort the values of $\hat{\textbf{p}}$ into the same bins, and multiply the probability of $\hat{\textbf{p}}$ per bin (the number of values falling into that bin, divided by the total) with the signal loss factors in that bin, essentially computing a weighted average across all bins to obtain a final signal loss factor per $k$.
+The signal loss results for this method are very similar to the previous method.
 For future power spectrum results, we choose to use the second method because it computes final signal loss values using our full distributions of measurements.
+
+\cc{This next paragraph needs to be worked on.
+What I'm going for is a plot that `proves' our signal loss method is correct, but it's hard to show since the combination of inverse covariance weighting + signal loss correction produces results that are HIGHER than the unweighted level.
+The plot shown below uses PS points instead of error bars, which brings them into closer agreement...}
+To verify our signal loss computations, we compare the unweighted power spectrum estimate of EoR (`true' EoR) with the signal loss corrected weighted power spectrum estimate of EoR + data in a regime where the injected EoR is very large (since there is minimal signal loss for small EoR).
+We compare these two quantities because we must ensure that our weighted combined dataset, after signal loss correction, does not lie below the level of EoR.
+From Figure \ref{fig:sigloss_beforeafter}, we see over $3$ orders of magnitude of signal loss associated with the inverse covariance weighting of fringe-rate filtered PAPER-64 data.
+The power spectrum, post-correction, lies just above the EoR-only power spectrum.
+However, it exhibits a different shape due to \cc{??}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/sigloss_beforeafter.png}
+	\caption{Power spectrum estimates of the combined EoR + PAPER-64 dataset, pre (squares) and post (circles) signal loss correction.
+The dashed blue line is the unweighted power spectrum estimate of EoR alone.}
+	\label{fig:sigloss_beforeafter}
+\end{figure}
 
@@
 This is important in confirming that signal loss is a direct result of the choice for $\textbf{C}$.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{plots/sigloss2_noise.png}
-	\caption{$P_{in}$ vs. $P_{out}$ (blue) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent cyan range of pCn values instead of just the max}}
-	\label{fig:sigloss2_noise}
-\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise.png}
-	\caption{Full inverse covariance weighted power spectrum of pure noise (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
+Similarly, we can compute signal loss for intermediate cases as well, such as a regularized $\textbf{C}$ which exhibits some lossiness, but not as much as inverse covariance weighting.
+
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=1.0\textwidth]{plots/sigloss2_noise.png}
+%	\caption{$P_{in}$ vs. $P_{out}$ (blue) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent cyan range of pCn values instead of just the max}}
+%	\label{fig:sigloss2_noise}
+%\end{figure*}
+
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_nosigloss.png}
+%	\includegraphics[width=0.4\textwidth]{plots/ps2_noise.png}
+%	\caption{Full inverse covariance weighted power spectrum of pure noise (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
 Black points correspond to positive values, while grey points correspond to originally negative values that have been made positive for plotting.
@@
 The solid green line is the theoretical noise level prediction based on observational parameters.}
-	\label{fig:ps2_noise}
-\end{figure*}
+%	\label{fig:ps2_noise}
+%\end{figure*}
 
@@
 
-With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{w}$.
+With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{S}$.
 Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
@@
 
-We now turn our attention to power spectra using the 30 m East/West baselines of PAPER-64.
-Our dataset spans $8.5$ hours of LST ($.1$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate filtered using an optimal fringe-rate filter.
-We have two datasets (even days and odd days), and only cross-multiply data from different days and different baselines.
-We are interested in $21$ frequency channels (channels 95-115), which yields a power spectrum for a redshift of $z=8.4$.
-
-Using full inverse covariance weighting, our results are not too dissimilar to that of pure noise.
-Signal loss factors (Figure \ref{fig:sigloss2_data}) are of similar order of magnitude, and our power spectrum blows up past the unweighted version after signal loss correction (Figure \ref{fig:ps2_data}).
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
-%	\caption{$P_{in}$ vs.
-$P_{out}$ (black) for 15 injection levels and 21 $k$'s.
-The solid grey line is the $2\sigma$ upper limit for the weighted power spectrum of data alone, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation.
-\cc{Probably don't need to show this plot at all}}
-%	\label{fig:sigloss1_data}
-%\end{figure*}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
-	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent grey range of pCv values instead of just the max}}
-	\label{fig:sigloss2_data}
-\end{figure*}
+Using full inverse covariance weighting, our power spectrum results before and after signal loss correction is shown in Figure \ref{fig:ps2_data}.
+Prior to signal loss correction, it is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction.
+Post-correction, the power spectrum values blow up much higher than both the theory and unweighted power spectrum.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
-Black points correspond to positive values, while grey points correspond to originally negative values that have been made positive for plotting.
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
 The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
@@
 
-Looking into this behavior in more detail, we investigate the shape of the eigenspectrum of $\textbf{C}$ for a typical baseline used in the analysis.
+Following our toy model investigation in Section \ref{sec:SiglossOverview}, we investigate the shape of the eigenspectrum of $\textbf{C}$ for a typical baseline used in the analysis.
 Figure \ref{fig:eigenspectrum} shows this spectrum for baseline (1,4).
-Most obviously, the spectrum is steep, spanning 4 orders of magnitude.
-Not as obvious is the effect of this shape on our results.
-When the matrix $\textbf{C}$ is inverted to form $\textbf{C}^{-1}$, the effect of the steepness of the eigenspectrum is to up-weight very few modes of the sky while the rest are drastically down-weighted.
-More specifically, our fringe-rate filtered data contains a finite, small number of independent modes, thereby resulting in a covariance matrix that can be described by just a few modes.
-Beyond the first few modes, the eigenvalues of each additional mode falls of dramatically.
-When inverting, we end up not only down-weighting those initial modes but severely up-weighting a few insignificant ones.
-Because of our weighting choice, signal loss blows up as it thinks we only have a couple modes in our data.
+The spectrum is very steep, spanning 4 orders of magnitude, implying that a couple modes are weighted much more than the rest.
+In fact, this behavior is much more extreme than we saw in the toy model, whose eigenspectrum (for the `fringe-rate filtered' case) only started to vividly steepen for the last few eigenmodes.
+The consequence of assigning individual weights to many more modes than are present in the data is significant --- to the point of resulting in power spectrum values that are higher than if no weighting scheme was used at all.
 
@@
 
-Clearly the full inverse covariance treatment of our data is suboptimal to even the unweighted case, but we would like to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum.
-There are many choices for determining the covariance matrix $\textbf{C}$, but here we will illustrate \cc{?} promising ones as applied to PAPER-64.
-
-\cc{TO DO: decide on/explain/show different weightings}
-
-\section{Application: Error Estimation}
+The full inverse covariance treatment of our data is suboptimal to the unweighted case, meaning that choosing such a weighting does not help suppress systematics as we intended.
+Now we would like to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum.
+There are many choices for determining the covariance matrix $\textbf{C}$, as described in Section \ref{sec:SiglossOverview}, but here we will illustrate \cc{?} promising ones as applied to PAPER-64.
+
+\cc{Should I just show the identity multiplication scheme that seems to be the best? Show lots of options? Mention different options but not show the results?}
+
+\subsection{Case Study: Error Estimation}
 \label{sec:Error}
+
+In this section we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview}.
+We first walk through a derivation for a theoretical error estimation, and then revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
 
@@
 \begin{equation}
+\label{eq:sense}
 p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lsts}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
@@
 
+Equation \ref{eq:sense} represents the most sensitive estimate for $\hat{\textbf{p}}(k)$ given our observing parameters.
+An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging together positive and negative $k$'s.
+
+To verify our thermal noise prediction (and the reason we were led to revise certain factors), we form power spectra estimates using a pure noise simulation as described in Section \ref{sec:simulations}.
+To reiterate, we create Gaussian noise using our system temperature and the same integration time and number of baselines, LSTs, and days that went into our PAPER-64 dataset.
+We also fringe-rate filter the noise in the same way.
+Doing so results in the power spectrum estimate shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and $\textbf{C} = \textbf{C} * \textbf{I}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
+All three are in agreement, validating our analytical thermal noise calculation.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.4\textwidth]{plots/ps_noise_pk.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps_noise_delta.png}
+	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data.
+The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we regularize $\textbf{C}$ by setting $\textbf{C} = \textbf{C} * \textbf{I}$ to minimize signal loss.
+The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper limit).
+The solid green line is the theoretical noise level prediction as calculated by Equation \ref{eq:sense}.
+All three estimates agree.}
+	\label{fig:ps_noise}
+\end{figure*}
+
 \subsection{Bootstrapping}
@@
 
-\section{Application: Bias}
+\subsection{Case Study: Bias}
 \label{sec:Bias}
+
+\cc{Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing} \\
+
+\cc{Need to explain positive bias still... not sure where it comes from yet!}
 

### 2017-08-08 PAPER.tex
Added appendix with analytic derivation of signal loss for toy model

@@
-\documentclass[preprint2,numberedappendix,tighten,twocolappendix]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
+\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
 %\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
@@
 %\newcommand{\vis}{\mathbf{v}}
-%\newcommand{\x}{\mathbf{x}}
+\newcommand{\x}{\mathbf{x}}
+\newcommand{\C}{\mathbf{C}}
+\newcommand{\Chat}{\mathbf{\hat{C}}}
+\newcommand{\F}{\mathbf{F}}
+\newcommand{\Fhat}{\mathbf{\hat{F}}}
+\newcommand{\Q}{\mathbf{Q}}
+\newcommand{\I}{\mathbf{I}}
 %\newcommand{\xhat}{\hat{\mathbf{x}}}
@@
 
-\newcommand{\cc}[1]{{\color{purple} \textbf{[#1]}}}
+\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
+\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
 
@@
 
+\appendix
+\section{A toy model for signal loss}
+\label{sec:SigLossToy}
+
+In this Appendix, we examine a toy model for signal loss.
+Our goal is to build intuition by deriving an analytic formula for power spectrum signal loss.
+We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum estimate.
+
+The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by \acl{We need to decide whether the Q matrices have their Greek indices as upper or lower indices.} \acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
+\begin{equation}
+\hat{p}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
+\end{equation}
+where
+\begin{equation}
+F_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \right)
+\end{equation}
+is the $\alpha$th diagonal element of the Fisher matrix.
+In our case, however, we do not have \emph{a priori} knowledge of the covariance matrix.
+Thus, we replace $\C$ with $\Chat$, its data-derived approximation.
+Our estimator then becomes
+\begin{equation}
+\label{eq:phatloss}
+\hat{p}_\alpha^\textrm{loss} = \frac{1} {2 \F_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
+\end{equation}
+where
+\begin{equation}
+\hat{F}_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
+\end{equation}
+with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than unity).
+We will now provide an explicit demonstration of this by modeling the estimated covariance as
+\begin{equation}
+\label{eq:ChatDef}
+\Chat = (1-\eta) \C + \eta \x \x^t,
+\end{equation}
+where $\eta$ is parameter quantifying our success at estimating the true covariance matrix.
+If $\eta = 1$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
+On the other hand, if $\eta =0$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
+
+Our strategy for computing the signal loss will be to insert Eq.
+\eqref{eq:ChatDef} \acl{Make sure we're consistent w.r.t.
+``Equation" vs.
+``Eq."} into Eq.
+\eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
+We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
+\begin{equation}
+\Chat^{-1}\x = \frac{\C^{-1}\x}{1-\eta} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right],
+\end{equation}
+where we have defined $g \equiv \x^t \C^{-1} \x$. Inserting this into our Fisher estimate we have
+\begin{equation}
+\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta g}{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta g}{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
+\end{equation}
+where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
+Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$.
+Inserting these expressions into our estimator gives
+\begin{eqnarray}
+\label{eq:phatlossexpanded}
+\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta g}{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta g}{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
+&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} \left( \frac{\beta h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\beta^2 h_\alpha^2}{F_{\alpha \alpha}}\right)^{n-k},
+\end{eqnarray}
+where $\beta \equiv \eta g/[1+ \eta (g-1)]$.
+To proceed, we take the ensemble average of $\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties.
+Inspecting Eq.
+\eqref{eq:phatlossexpanded}, we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, where $a$, $b$, and $c$ are integers.
+Expanding $\beta$ in powers of $g$, we have
+\begin{equation}
+\label{eq:betahh}
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_a = 1}^\infty \frac{(-\eta)^{m_1 + \dots + m_a}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle.
+\end{equation}
+Writing out the ensemble averaged quantity on the right hand side and defining $M \equiv m_1 + \dots + m_a$ yields
+\begin{eqnarray}
+\langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha \C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
+&=& \sum_{i_1}^N \sum_{j_1}^N \cdots  \sum_{k_1}^N \sum_{l_1}^N \cdots  \sum_{p_1}^N \sum_{q_1}^N \cdots  ( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} )_{p_1 q_1} \dots (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1})_{p_c q_c}  \nonumber \\
+&&  \times ( \C^{-1} \Q^\alpha \C^{-1})_{k_1 l_1} \dots ( \C^{-1} \Q^\alpha \C^{-1})_{k_b l_b} \C^{-1}_{i_1 j_1}\dots \C^{-1}_{i_M j_M} \langle x_{i_1} x_{j_1} \dots   x_{k_1} x_{l_1} \dots  x_{p_1} x_{q_1} \dots \rangle, \quad
+\end{eqnarray}
+where $N$ is the length of vector $\x$, i.e., the number of data points.
+To further simplify this expression, we assume that the data are Gaussian distributed.
+The expectation value on the right hand side can then be reduced to a sum of product of covariances, where each term in the sum is comprised of a particular way to partition the copies of $x$ into pairs.
+However, in the limit of large $N$ one particular partitioning dominates, and the result can be approximated as \acl{Should probably explain this more fully}
+\begin{equation}
+\langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_a} \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
+\end{equation}
+and re-inserting this into Eq. \eqref{eq:betahh} yields
+\begin{equation}
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
+\end{equation}
+With this result, taking the ensemble average of Eq.
+\eqref{eq:phatlossexpanded} is relatively straightforward.
+One simply replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha \alpha}$ with $2F_{\alpha \alpha}$.
+Performing these substitutions and recalling \acl{make sure the reader will indeed be recalling at this point} that $\langle \hat{p}_\alpha \rangle = \langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
+\begin{equation}
+\frac{\langle \hat{p}_\alpha^\textrm{loss} \rangle}{\langle \hat{p}_\alpha \rangle} = \frac{(1-\beta_N)^2}{1- 2\beta_N + \beta_N^2 \left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / F_{\alpha \alpha}}.
+\end{equation}
+This quantity is in general less than unity, and quantifies the signal loss relative to the ideal estimator $\hat{p}_\alpha$ where we know the true covariance $\C$.
+As an illustrative example, for cases where $\C \propto \I$, this reduces to
+\begin{equation}
+\frac{\langle \hat{p}_\alpha^\textrm{loss} \rangle}{\langle \hat{p}_\alpha \rangle} \Bigg{|}_{\C \propto \I} = \frac{(1-\beta_N)^2}{(1-\beta_N)^2 + \beta_N^2} = \frac{(1-\eta)^2}{(1-\eta)^2 + N^2 \eta^2}.
+\end{equation}
+This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta$ (perfect estimation of $\C$) and goes to zero as $\eta$ approaches $1$.
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\columnwidth]{plots/analytic_sig_loss.pdf}
+	\caption{Power spectrum signal loss for $N=20$ for a toy model where $\Chat = (1-\eta) \C + \eta \x \x^t$.}
+	\label{fig:analytic_sig_loss}
+\end{figure}
+
+In general, one's estimate of the covariance will not be expressible in the form given by Eq.
+\eqref{eq:ChatDef}.
+However, the qualitative point here is that the signal loss can be expressed as a multiplicative factor.
+Even if $\Chat$ is more complicated than the form used for this toy model, the same mathematical technique of expressing the estimator as a series of higher-point functions, reducing these functions (assuming Gaussianity) to two-point functions, and re-summing any power series will show that the signal loss is a multiplicative factor.
+\acl{I can express this last bit more eloquently, but it's late and I'm tired and need to eat dinner.}
+
 \bibliographystyle{apj}

### 2017-08-08 PAPER.tex
edited signal loss methodology

--- 2017-08-04 PAPER.tex
@@
 This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space.
-The 21 cm line offers a window into the evolution of ionization, temperature, and density fluctuations on cosmic scales.
+Tracing the 21 cm line as a function of redshift offers a window into the evolution of ionization, temperature, and density fluctuations during this transformative era.
 
@@
 
-The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and instrumental systematics that are 4-5 orders of magnitude brighter.
+The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and instrumental systematics that are, when combined, 4-5 orders of magnitude brighter.
 A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
@@
 This paper is organized as follows.
-In section 2 we introduce the three themes of our focus, using a toy model to develop intuition into each one.
+In section 2 we introduce the three themes of our focus, using a toy model to develop intuition for each one.
 Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}.
@@
 How can the source of a detection be properly identified?
-Many common techniques, such as averaging data, weighting, bootstrapping, and jackknife testing, each address these issues yet harbor additional trade-offs.
+Many common techniques, such as averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs.
 For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing some EoR signal.
@@
 Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.
-In this paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay with each other and the themes.
+In this paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay with each other and impact the themes.
 We will give brief definitions now, and build intuition for each theme in the sections to follow.
@@
 Errors can be estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can leak its way into a power spectrum, such as bias from noise and foregrounds.
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds.
+A successful EoR detection would also imitate a bias.
 Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR.
@@
 The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
-We focus on these techniques because of their strong appeal for a power spectrum analysis.
-However, they also have limitations, and we will discuss circumstances in which there are trade-offs.
+We focus on these techniques because \cc{??}.
+However, some have limitations, and we will discuss circumstances in which there are trade-offs.
 \begin{itemize}
-\item \textbf{Fringe-rate filtering:} Fringe-rate filtering can be considered an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is considered an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
 Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
@@
 \item \textbf{Weighting:} A dataset can be weighted to emphasize certain spectral features and minimize others.
-One particular flavor of weighting is inverse covariance weighting, which weights a dataset by minimizing the covariance between frequency channels.
+One particular flavor of weighting is inverse covariance weighting, which is a generalized version of inverse variance weighting that also takes into account data correlations.
 This weighting has the effect of down-weighting correlated information (i.e.
@@
 EoR).
-However, one challenge of weighting is in accurately determining a covariance matrix that best describes the data.
-\item \textbf{Bootstrapping:} Because applying theoretical errors to a $21$ cm measurement are insufficient \cc{why?}, bootstrapping is a useful method for estimating errors of a dataset from itself.
-By randomly drawing many samples of the data, we get a sense of its inherent variance, though there are subtleties to consider such as bootstrapping sample sizes.
+However, a challenge of inverse covariance weighting is in accurately describing a covariance matrix that best describes the data.
+\item \textbf{Bootstrapping:} Because theoretical models for covariance matrices are questionable and theoretical error estimation methods rely on assumptions that can be violated by data, applying theoretical errors to a $21$ cm measurement is often avoided.
+Hence, bootstrapping is a useful method for estimating errors of a dataset from itself.
+By randomly drawing many samples of the data, we get a sense of its inherent variance, though there are subtleties to consider such as the independence of values in a dataset.
 \item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different dimensions of a dataset to cross-validate results.
@@
 
-Driven by the need to mitigate foreground bias, we would like to use a weighting method that succeeds in down-weighting foregrounds.
+Driven by the need to mitigate foreground bias, we use a weighting method that succeeds in down-weighting foregrounds.
 We apply this weighting to data and propagate it into a final estimator using the power spectrum estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}).
@@
 
-We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in Jy that have the shape ($times$, $frequencies$).
-We form the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
+We begin with our data vector, $\textbf{x}$ which contains our measured visibilities in Jy.
+It has length ($N_{t}, N_{f}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
+Visibilities are measurements of the Fourier transform of the sky along spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes we only need to take one Fourier transform along the line-of-sight dimension.
+We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
 
@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{S}\textbf{Q}_{\alpha}\textbf{S}\textbf{x},
-\end{equation}
-
-\noindent where $\textbf{S}$ is a weighting matrix (we use $\textbf{S}$ since $\textbf{W}$ is reserved for window functions).
-As an example, inverse covariance weighting would set $\textbf{S} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{S} = \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space.
-The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency.
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{x},
+\end{equation}
+
+\noindent where $\textbf{R}$ is a weighting matrix.
+As an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{R} = \textbf{I}$, the identity matrix.
+The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin.
+The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}).
 
@@
 \begin{equation}
+\label{eq:phat}
 \hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}},
@@
 
-\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. We compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
-
-\begin{eqnarray}
-\textbf{F}_{\alpha\beta} &=& \frac{1}{2}tr[\textbf{S}\textbf{Q}_{\alpha}\textbf{S}\textbf{Q}_{\beta}]. 
-\end{eqnarray}
-
+\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum.
 We have a choice for $\textbf{M}$.
-For simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:PS}
-
-In the next sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{S}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
+For simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}
+
+In the next sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
 Our ultimate goal in experimenting with weighting is to suppress foregrounds perfectly without destroying an EoR signal.
@@
 
-One choice for a weight matrix $\textbf{S}$ is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds.
-\cc{math!} The covariance matrix $\textbf{C}$, which in our case describes covariances between frequency channels, can be estimated in a variety of ways.
+One choice for a weight matrix $\textbf{R}$ is an inverse covariance matrix.
+This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on the measurements (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
+The covariance matrix $\textbf{C}$, which in our case describes covariances between frequency channels, can be estimated in a variety of ways.
 Given perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data.
-\cc{math!} However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the foregrounds in the data.
+However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the foregrounds in the data.
 
@@
 \begin{equation}
-\hat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle,
-\end{equation}
-
-\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a time-average \cc{distinguish between ideal ensemble average and finite estimate???}.
-The inverse covariance matrix is therefore $\textbf{S} = \textbf{C}^{-1}$.
-\cc{should I put hat's on all C's that are estimated from the data?
-Need to distinguish it from ideal C.}
-
-First, we compute the power spectrum of $\textbf{x}$ using the OQE formalism and a weighting matrix of $\textbf{C}^{-1}$.
+\hat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
+\end{equation}
+
+\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a finite time-average. The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
+
+First, we compute the power spectrum of $\textbf{x}$ using the OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$.
 The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
@@
 	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymode} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right).
@@
 As shown, our inverse covariance-weighted result successfully suppresses foregrounds \cc{explain why}.
-This illustrates why inverse covariance weighting is attractive for $21$ cm data.
 It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
 This is evidence of signal loss.
-In order to understand how this occurs, we need to closely study our covariance matrix, $\textbf{C}$, which is shown in Figure \ref{fig:toy_sigloss12}.
+In order to understand how this occurs, we need to closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
 
@@
 If $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal \cc{elaborate with math!}.
-As a contradictory example, if instead we choose $\textbf{S} = \textbf{I}$, there will be no signal loss (although it may suffer from foreground or instrumental bias).
+As a contrasting example, if instead we choose $\textbf{R} = \textbf{I}$, there will be no signal loss (although it may suffer from foreground or instrumental bias).
 
 It turns out that because we estimated $\textbf{C}$ from our data, its eigenspectrum offers insight into understanding how inverse covariance weighting affects our result.
-An eigenspectrum ranks the eigenvalues of $\textbf{C}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
+An eigenspectrum ranks the eigenvalues of $\hat{\textbf{C}}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
 Each eigenvalue encodes the amount of variance in the dataset for a particular mode.
 The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-\cc{use more rigorous math to supplement this paragraph}
 
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
-	\caption{Eigenspectrum of $\textbf{C}_{FG}$ (blue), $\textbf{C}_{EoR}$ (red), and $\textbf{C}_{FG+EoR}$ (green).
-The eigenspectrum of $\textbf{C}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
+	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
+The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
 All eigenspectra steepen slightly for the final few eigenmodes, a behavior that results in some modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate (Figure \ref{fig:toy_sigloss3}, left).
@@
 
-For our toy model, the eigenspectra of $\textbf{C}_{FG}$, $\textbf{C}_{EoR}$, and $\textbf{C}$ are shown in Figure \ref{fig:toy_sigloss2}.
+For our toy model, the eigenspectra of $\hat{\textbf{C}}_{FG}$, $\hat{\textbf{C}}_{EoR}$, and $\hat{\textbf{C}}$ are shown in Figure \ref{fig:toy_sigloss2}.
 The blue curve peaks only at the zeroth eigenmode, revealing that the foregrounds can be described by a single eigenmode.
@@
 zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
-Altering $\textbf{C}$ in this way is one example of a regularization method, in which we are changing $\textbf{C}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
+Altering $\hat{\textbf{C}}$ in this way is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
 The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
 In this case we recover EoR, demonstrating that if we can model our foregrounds, we can down-weight them without signal loss.
-There are several other ways to regularize $\textbf{C}$, and we will discuss some in Section \ref{sec:otherweight}.
+There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section \ref{sec:otherweight}.
 
@@
 
-In Section \ref{sec:toymodel} we showed how altering $\textbf{C}$ can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
-We will now use our toy model to describe several other ways to tailor $\textbf{C}$ in order to minimize signal loss.
+In Section \ref{sec:toymodel} we showed how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
+We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ in order to minimize signal loss.
 We illustrate the resulting power spectra and eigenspectra for four different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
@@
 As a first test, we know that our simulated EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\textbf{C}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$ to obtain a final $\textbf{C}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\textbf{C}$ would).
+If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$ to obtain a final $\hat{\textbf{C}}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
 This is evident when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}.
@@
 	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\textbf{C}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\textbf{C}$ (lower left), and multiplying an identity matrix to $\textbf{C}$ (lower right).
+We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and multiplying an identity matrix to $\hat{\textbf{C}}$ (lower right).
 There are many regularization options available to minimize signal loss, and some work better than others depending on the dataset.}
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
-	\caption{We compare the eigenspectrum of an empirically calculated $\textbf{C}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\textbf{C}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\textbf{C}$ (yellow), and multiplying an identity matrix to $\textbf{C}$ (magenta).
+	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix to $\textbf{C}$ (magenta).
 }
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\textbf{C} = \textbf{C} + \textbf{I}$.
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}} + \textbf{I}$.
 By adding the identity, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum \cc{why?}.
 
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\textbf{C}$ a different way - by zeroing all but the first three eigenmodes.
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by zeroing all but the first three eigenmodes.
 This means that the first three eigenmodes will be given weights (the three highest variance modes will be down-weighted), but the rest will be treated with similar weights.
@@
 
-The last regularization scheme we are highlighting here is setting $\textbf{C} = \textbf{C} \cdot \textbf{I}$.
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \cdot \textbf{I}$.
 In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
@@
 \cc{how to make this paragraph less hand-wavy?} One may imagine a situation where a particular systematic is contained to an isolated frequency.
-In such a case, preserving only the diagonal elements of $\textbf{C}$ would be an effective way of removing this contamination.
+In such a case, preserving only the diagonal elements of $\hat{\textbf{C}}$ would be an effective way of removing this contamination.
 
@@
 \subsubsection{Foreground and Noise Bias}
+\label{sec:BiasTypes}
 
@@
 \cc{math!} In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
-The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (Section \ref{sec:PS}).
-Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode \cc{develop more}.
+The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
+Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode \cc{develop more or cite?}.
 
@@
 
-As illustrated in Section \ref{sec:SiglossOverview}, signal loss can arise when data is weighted using information from itself.
-There are some weighting schemes which succeed at suppressing systematics but result in the loss of the cosmological signal, while others may preserve the signal along with contaminating ones.
-The data analyst has a choice for how to weight data, but it is crucial to be able to quantify the amount of signal loss associated with any lossy analysis step.
-In this section, we explain a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
-Before doing so however, we first explain how two additional channels --- noise and EoR --- are created in our power spectrum pipeline, both of which are used to verify signal loss.
-
-\subsection{Simulated Noise and EoR}
-\label{sec:simulations}
-
-One critical new component of our power spectrum pipeline is that we have many different power spectrum channels that simultaneously get processed at the same time and are especially useful for computing signal loss and sensitivity estimations.
-Two important channels, in addition to our PAPER-64 data, are a simulated noise dataset and an EoR dataset (along with different combinations of all three).
-We will briefly describe each.
-
-We simulate random Gaussian noise with a variance determined by the sensitivity of our instrument in order to best represent the thermal noise level of our data.
-We calculate our system temperature for our frequencies of interest as:
-
-\begin{equation}
-\label{eq:sys}
-T_{sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{rcvr}
-\end{equation}
-
-where $\nu$ are frequencies in GHz.
-We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ at $150$ MHz.
-This is lower than in \citet{ali_et_al2015} because \cc{why?}.
-We convert this temperature into a variance statistic using:
-
-\begin{equation}
-T_{rms} = \frac{T_{sys}}{\sqrt{\Delta\nu \Delta t N_{days} N_{pols}}}
-\end{equation}
-
-where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
-Our simulated noise has the same shape as our data, and we fringe-rate filter it using an identical optimal fringe-rate filter to best mimic the real noise floor of our data.
-
-A second additional important channel in our pipeline is a simulated EoR signal.
-We again simulate random Gaussian noise (with a default variance of $1$) with the same shape as our data, and we fringe-rate filter this signal twice using the optimal filter.
-The first filter transforms the unattached noise into a signal that's attached to the sky (i.e.
+In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from itself.
+Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
+In particular, we highlight major differences from the signal loss computation used in \citet{ali_et_al2015}, which previously underestimated losses.
+
+\subsubsection{Signal Loss Methodology}
+
+We simulate an EoR signal by creating a random Gaussian signal (with a default variance of $1$) with the same shape as our data, and we fringe-rate filter this signal twice using the optimal filter.
+The first filter transforms the white noise into a signal that's attached to the sky (i.e.
 what our instrument observes).
 The second filter represents the fringe-rate filtering step in our data analysis pipeline.
-This mock EoR signal is injected on top of either data or noise at various amplitude levels in order to measure its loss.
-
-\subsection{Signal Loss Methodology}
-
-The potential loss of a cosmological signal when weighting PAPER-64 data is a real and significant issue.
-To reiterate, when applying a weighting matrix $\textbf{S}$ to data, which has been empirically estimated from the data itself, it has the consequence of over-fitting the noise, producing power spectra values well below the thermal noise limit that is predicted based on observation parameters.
-This is especially prevalent when weighting fringe-rate filtered data, which has so few independent time modes to begin with, leading to a noisier dataset.
-Being able to accurately quantify this loss is crucial in interpreting and providing credibility to any power spectrum limits.
-
-New to the PAPER-64 analysis is a robust method to estimate signal loss. This method is now a standard analysis step for all PAPER analyses and one that will be used for HERA moving forward.
-
-As discussed previously, our power spectrum pipeline runs on a standardized set of channels (pure data, pure noise, pure EoR, and combinations of the three).
-As part of our signal loss routine, we also compute power spectra with various levels of the created EoR signal, dialing its amplitude from well-below the data level, to well-above.
-Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector.
-We define $\textbf{r}$ to be:
+This mock EoR signal is injected on top of fringe-rate filtered PAPER-64 data at a range of amplitude levels, ranging from well-below the data level, to well-above.
+
+Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}$ to be the data plus the EoR signal:
 
@@
 
-Using OQE formalism, we are interested in the following two quantities: $P_{in}$ and $P_{out}$.
-The input power spectrum, $P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal.
-The output power spectrum, $P_{out}$, is the weighted power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data.
+We are interested in quantifying how much $\textbf{e}$ is lost after weighting $\textbf{r}$ and applying OQE formalism.
+We investigate this by comparing two quantities we define as the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$.
+$P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal.
+$P_{out}$ is the weighted power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data.
 Comparing the two quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
-Ignoring normalization factors:
-
-\begin{equation}
-P_{in} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}\textbf{I}\textbf{e}
-\end{equation}
+Ignoring normalization factors, these two quantities can be written as:
+
+\begin{equation}
+P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}_{\alpha}\textbf{I}\textbf{e}
+\end{equation}
+
+\noindent and
 
@@
 \label{eq:sigloss}
-P_{out} \equiv \hat{\textbf{p}}_{e} &=& \hat{\textbf{p}}_{r}-\hat{\textbf{p}}_{x} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} 
+P_{out,\alpha} \equiv \hat{\textbf{p}}_{e,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
+&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
@@
 
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out} \propto \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e}$.
-Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is made up of multiple terms:
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e}$.
+Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:
 
@@
 \label{eq:crossterm}
-P_{out} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{S}_{r}\textbf{Q}\textbf{S}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{S}_{x}\textbf{Q}\textbf{S}_{x}\textbf{x} 
+P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
 
-Taking the case of very large $\textbf{e}$, so that $\textbf{S}_{r} \sim \textbf{S}_{e}$ and any terms involving only $\textbf{x}$ are small:
+Taking the case of very large $\textbf{e}$, so that $\textbf{R}_{r} \sim \textbf{R}_{e}$ and any terms involving only $\textbf{x}$ are small, yields:
 
 \begin{eqnarray}
-P_{out, \textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{S}_{e}\textbf{Q}\textbf{S}_{e}\textbf{x}
+\label{eq:pout_expand}
+P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{x}.
 \end{eqnarray}
 
-We see that our naive expression for $P_{out}$ is the first term, but there also two additional terms.
-An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since the two quantities are un-correlated.
+We see that our naive expression for $P_{out}$ is the first term in Equation \ref{eq:pout_expand}, but there are also two additional terms.
+An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are physically unrelated.
+In \citet{ali_et_al2015}, this assumption is used, and the first term in Equation \ref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
+
 However, deeper investigations of these terms reveal that they contain non-negligible power.
-This power is negative, thereby reducing $P_{out}$ and increasing the amount of signal loss.
-In \citet{ali_et_al2015}, the cross-term power was ignored, resulting in an under-estimated signal loss.
-Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \ref{eq:sigloss}.
-
-For the unweighted case ($\textbf{S} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio of $P_{in} / P_{out}$ to be 1.
+In fact, foreground modes and signal modes are anti-correlated on average, as derived and explained in \citet{switzer_et_al2015}.
+The spurious correlation of the two means that we cannot compute signal loss using a signal-only simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss.
+Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \ref{eq:sigloss}, which subtracts the weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
+
+For the unweighted case ($\textbf{R} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio $P_{in} / P_{out} = 1$.
 For the weighted case, this may not be true due to signal loss.
-In order to quantify the loss, we look at the ratio of $P_{in}$ to $P_{out}$ as the amplitude level of the injected signal \textbf{e} is increased.
-In the next section, we highlight two methods that yield similar results for the determination of signal loss using $P_{in}$ and $P_{out}$.
-
-\subsection{Signal Loss in Practice}
+To quantify the loss, we look at the ratio $P_{in}/P_{out}$ as the amplitude level of the injected signal \textbf{e} is increased.
+In the next section, we describe our signal loss transfer function ($P_{in}$ vs.
+$P_{out}$) for PAPER-64 data and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
+
+\subsubsection{Signal Loss in Practice}
 
@@
 
-While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{S} = \textbf{C}^{-1}$), which leads to substantial loss.
+While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), which leads to substantial loss.
 With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
@@
 \begin{eqnarray}
-P_{in} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}\textbf{I}\textbf{e} \\
-P_{out} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x} 
+P_{in,\alpha} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}_{\alpha}\textbf{I}\textbf{e} \\
+P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{x}^{-1}\textbf{x}
 \end{eqnarray}
@@
 For this method, we interpolate the signal loss factor (per $k$), computed as $P_{in}/P_{out}$, at a $P_{out}$ value equal to the $2\sigma$ power spectrum upper limit of our data.
-In other words, we look at $\hat{\textbf{p}} \propto \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}\textbf{C}_{x}^{-1}\textbf{x}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value.
+In other words, we look at $\hat{\textbf{p}}_{\alpha} \propto \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{x}^{-1}\textbf{x}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value.
 We therefore end up with one signal loss correction factor per $k$.
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
-	\caption{$P_{in}$ vs.
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
+%	\caption{$P_{in}$ vs.
 $P_{out}$ (black points) for 15 injection levels and 21 $k$'s.
@@
 \cc{Maybe re-do this plot with closer-together points}}
-	\label{fig:sigloss1_data}
-\end{figure*}
+%	\label{fig:sigloss1_data}
+%\end{figure*}
 
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
-	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. The transparent grey region represents all PAPER-64 bootstrapped estimates.}
-	\label{fig:sigloss2_data}
-\end{figure*}
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
+%	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. The transparent grey region represents all PAPER-64 bootstrapped estimates.}
+%	\label{fig:sigloss2_data}
+%\end{figure*}
 
@@
 
-\subsection{Data Weighting}
+\subsubsection{Data Weighting}
 \label{sec:Weight}
 
-With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{S}$.
+With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{R}$.
 Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
@@
 
-In this section we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview}.
-We first walk through a derivation for a theoretical error estimation, and then revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
-
-\subsection{Thermal Noise}
+In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
+We first walk through a derivation for a theoretical error estimation based on observational parameters.
+Although a theoretical model often differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors that affect its sensitivity.
+We also highlight major changes in our calculation from \citet{ali_et_al2015}, which in total decrease the estimated power spectrum sensitivity of PAPER-64 by a factor of \cc{fill in when ready}.
+Finally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
+
+\subsubsection{Theoretical Error Estimation}
 \label{sec:PSSense}
 
-One way to estimate errors on a $21$ cm power spectrum estimate is to compute theoretical errors based on the instrumental temperature and observational parameters.
-A theoretical noise limit provides a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
+Theoretical errors, computed from the instrumental temperature and observational parameters, provide a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
 Here we walk through a detailed computation of a theoretical noise estimation as applied to PAPER-64 observations and highlight major changes from \citet{ali_et_al2015}.
@@
 Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate filter.
-\item $T_{sys}$: The system temperature is set by Equation \ref{eq:sys}, for a receiver temperature of $200$ K and center frequency of $0.15$ GHz. \cc{does this differ from prior analysis?}
+\item $T_{sys}$: The system temperature is set by:
+
+\begin{equation}
+\label{eq:sys}
+T_{sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{rcvr},
+\end{equation}
+
+where $\nu$ are frequencies in GHz. We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ at $150$ MHz. This is lower than in \citet{ali_et_al2015} because \cc{why?}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from only using the real part of power spectrum estimates when plotting and quoting upper limits (imaginary component is discarded).
@@
 a fringe-rate filter).
-We compute the effective integration time of our fringe-rate filtered data by scaling our original integration time using the following:
+We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time using the following:
 \begin{equation}
@@
 \end{equation}
-where $t_{int}=43$ seconds, $t_{frf}$ is our fringe-rate filtered integration time, $w$ is our fringe-rate profile, and the integral is taken over all fringe-rates.
-In other words, we calculate our effective integration time by computing how our beam is altered in fringe-rate space.
+where $t_{int}=43$ seconds, $t_{frf}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is taken over all fringe-rates.
+In other words, we calculate the effective integration time by computing how our beam is altered in fringe-rate space.
 For PAPER-64, this number is $t_{int} = 3857$ s.
@@
 
-To verify our thermal noise prediction (and the reason we were led to revise certain factors), we form power spectra estimates using a pure noise simulation as described in Section \ref{sec:simulations}.
-To reiterate, we create Gaussian noise using our system temperature and the same integration time and number of baselines, LSTs, and days that went into our PAPER-64 dataset.
-We also fringe-rate filter the noise in the same way.
-Doing so results in the power spectrum estimate shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and $\textbf{C} = \textbf{C} * \textbf{I}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
+To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation.
+We create Gaussian random noise and use $T_{sys}$ in order to best represent the thermal noise level of PAPER-64 data.
+We convert $T_{sys}$ into a variance statistic using:
+
+\begin{equation}
+T_{rms} = \frac{T_{sys}}{\sqrt{\Delta\nu \Delta t N_{days} N_{pols}}},
+\end{equation}
+
+where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
+This rms temperature sets the variance of the Gaussian random noise.
+
+We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter.
+Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and $\hat{\textbf{C}} = \hat{\textbf{C}} * \textbf{I}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
 All three are in agreement, validating our analytical thermal noise calculation.
@@
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data.
-The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we regularize $\textbf{C}$ by setting $\textbf{C} = \textbf{C} * \textbf{I}$ to minimize signal loss.
+The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we regularize $\hat{\textbf{C}}$ by setting $\hat{\textbf{C}} = \hat{\textbf{C}} * \textbf{I}$ to minimize signal loss.
 The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper limit).
@@
 
-\subsection{Bootstrapping}
+\subsubsection{Bootstrapping}
 \label{sec:Boot}
 
-In this section, we highlight two major changes since \citet{ali_et_al2015}, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
-
-As discussed in Section \ref{sec:ErrorOverview}, traditional bootstrapping theory is only a valid way of estimating errors if a dataset is comprised of independent samples.
-Recall that the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
+We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results.
+In this section, we highlight two major changes in the way we estimate errors since \citet{ali_et_al2015}, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
+
+As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised of independent samples.
+The PAPER-64 pipeline outputs $N$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
 In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the baseline bootstrap and time axes simultaneously.
@@
 Because our dataset is fringe-rate filtered, we have substantially increased our integration time, resulting in fewer independent samples (from $\sim700$ samples to $8$ samples).
-A random draw of $700$ samples from this dataset therefore has many repeated samples, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance.
+A random draw of $700$ samples from this dataset therefore has many repeated samples, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
 Another way of describing this underestimation is that there are fewer ways to randomly sample data with $8$ independent modes versus $700$, so bootstrapping a fringe-rate filtered dataset yields a narrower distribution of values from which we calculate its standard deviation.
@@
 
-The second aspect of bootstrapping discussed in Section \ref{sec:ErrorOverview} is in regard to how a dataset is randomly sampled.
-In order to maximize sensitivity (i.e.
-maximize independent samples in a bootstrap), we have revised the method by which we sample baselines when bootstrapping.
-
-First, we speed things up in our pipeline by dividing our total number of baselines into $5$ groups, where there are no repeated baselines within or between groups.
+The second aspect of bootstrapping discussed in Section \ref{sec:ErrorOverview} is the overestimation of errors which arises from repeated values in a randomly sampled bootstrap.
+In order to maximize sensitivity, we have revised the method by which we sample baselines when bootstrapping to ensure mostly independent samples.
+
+First, we speed things up in our pipeline by separating our total number of baselines into $5$ groups (yielding $10$ baselines per group), where there are no repeated baselines within or between groups.
 In \citet{ali_et_al2015}, each group is then sampled with replacement to create a new group of the same size, which can have repeated baselines inside it.
-We discover that in doing so, we are sacrificing some of our sensitivity since there are $3$-$4$ repeated baselines per group.
+In doing so, we are sacrificing some of our sensitivity since there ends up being $3$-$4$ repeated baselines per group (Figure \ref{fig:toy_error2} shows a fraction of independent samples of $\sim55\%$ for $10$ total independent samples) .
 In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one, which we fill randomly.
@@
 Power spectrum estimates for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
-The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
+The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \hat{\textbf{C}}*\textbf{I}$, in order to minimize signal loss.
 We show upper limits ($2\sigma$ error bars) for three different results.
@@
 In blue, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data.
-We under-estimate errors in doing so because we are drawing many more samples than independent ones since the data is fringe-rate filtered.
+We under-estimate errors in doing so because we are drawing many more samples than independent ones.
 
@@
 
+In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as a power spectrum detection and imitate EoR.
+We discussed the importance of using jackknife and null tests for instilling confidence in an EoR detection, as well as identifying other sources of biases.
+Here we demonstrate methods used by PAPER-64 to mitigate foreground and noise bias and we perform jackknife and null tests in order to characterize the stability and implications of our results.
+
+\subsubsection{Mitigating Bias}
+
+We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we suppress noise biases.
+These methods are not novel to this analysis but here we frame them in the context of minimizing false (non-EoR) detections.
+
+Tailoring window functions is one way to suppress foreground biases.
+As alluded to in Section \ref{sec:SiglossOverview}, we have a choice for the normalization matrix $\textbf{M}$ in Equation \ref{eq:phat}.
+For the analysis of PAPER-64 data, we compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+
+\begin{equation}
+\textbf{F}_{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{Q}_{\beta} ]
+\end{equation}
+
+\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$.
+We take the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices:
+
+\begin{equation}
+\textbf{F} = \textbf{LL}^{\dagger}.
+\end{equation}
+
+\noindent Next, we construct $\textbf{M}$:
+
+\begin{equation}
+\textbf{M} = \textbf{DL}^{-1}
+\end{equation}
+
+\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MF}$, becomes:
+
+\begin{equation}
+\textbf{W} = \textbf{DL}^{\dagger}.
+\end{equation}
+
+\noindent Because of the lower triangular matrix, this window function has the property of preventing the leakage of foreground power from low $k$ to high $k$ modes.
+Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
+Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing foreground bias.
+
+In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk.
+In order to avoid the former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \ref{eq:qhat}.
+Namely, the PAPER-64 dataset is divided into two halves: even julian dates and odd julian dates.
+Our data vectors are then $\textbf{x}_{even, 1}$ for the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc.
+We only form $\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `'even', for example, in order to prevent the squaring of the same thermal noise.
+
+To mitigate crosstalk bias, we apply a fringe-rate filter that suppresses fringe-rates of zero... \cc{why don't we filter out fringe-rates of zero completely?}
+
+\subsubsection{Jack-Knife Tests}
+
 \cc{Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing} \\
-
 \cc{Need to explain positive bias still... not sure where it comes from yet!}

### 2017-08-10 PAPER.tex
-Re-wrote signalloss explanation in toy model section

@@
 This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency (\cc{explain why a sinusoid for FG}), as well as a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
+We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, a simplistic but realistic representation of a single bright source.
+We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
 Our combined data vector is $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
@@
 One choice for a weight matrix $\textbf{R}$ is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on the measurements (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
+This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
 The covariance matrix $\textbf{C}$, which in our case describes covariances between frequency channels, can be estimated in a variety of ways.
 Given perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data.
-However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting the foregrounds in the data.
+However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
 
@@
 
-\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a finite time-average. The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
+\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
 
@@
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right).
-There is signal loss for the former but not the latter.
-\cc{elaborate}}
+In the former case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$.
+Because $\hat{\textbf{C}}$ is empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization but may not exist in the true covariance.
+Consequently, these modes are over-fitted and down-weighted, leading to signal loss.
+There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes which $\hat{\textbf{C}}$ does not describe accurately.}
 	\label{fig:toy_sigloss3}
@@
 
-As shown, our inverse covariance-weighted result successfully suppresses foregrounds \cc{explain why}.
+As shown, our inverse covariance-weighted result successfully suppresses foregrounds.
 It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
 This is evidence of signal loss.
-In order to understand how this occurs, we need to closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
+In order to understand the behavior of this result, we need to closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
 
@@
 
-If $\textbf{C}$ is computed from the data itself and its inverse is then applied to the data, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal \cc{elaborate with math!}.
-As a contrasting example, if instead we choose $\textbf{R} = \textbf{I}$, there will be no signal loss (although it may suffer from foreground or instrumental bias).
+If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal.
+For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
+Here we will describe the origin of this signal loss intuitively.
 
 It turns out that because we estimated $\textbf{C}$ from our data, its eigenspectrum offers insight into understanding how inverse covariance weighting affects our result.
-An eigenspectrum ranks the eigenvalues of $\hat{\textbf{C}}$ from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
-Each eigenvalue encodes the amount of variance in the dataset for a particular mode.
+An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
+In other words, the eigenvalues encode the strength of different shapes in the dataset.
 The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+This is usually not the case for a covariance matrix, in which a sloped eigenspectrum means that modes are given different weights.
+When weighting data by an inverse covariance matrix, the modes with the highest eigenvalues are down-weighted the most.
 
@@
 	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
-The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-All eigenspectra steepen slightly for the final few eigenmodes, a behavior that results in some modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate (Figure \ref{fig:toy_sigloss3}, left).
-If only the first eigenmode is used, all others get equal weights and hence, there is no signal loss (Figure \ref{fig:toy_sigloss3}, right).
-\cc{also illustrate first few and last few eigenvalues -- how to best show this?}}
+The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.}
 	\label{fig:toy_sigloss2}
@@
 
-For our toy model, the eigenspectra of $\hat{\textbf{C}}_{FG}$, $\hat{\textbf{C}}_{EoR}$, and $\hat{\textbf{C}}$ are shown in Figure \ref{fig:toy_sigloss2}.
-The blue curve peaks only at the zeroth eigenmode, revealing that the foregrounds can be described by a single eigenmode.
-This is a direct consequence of how it was constructed (only one sinusoid).
-The eigenspectrum of EoR, however, is fairly flat, signifying that its covariance matrix is similar to an identity matrix.
-This makes sense because EoR consists of a random signal, which should only have strong frequency-frequency correlations when two frequencies are the same.
-
-The eigenmodes with the highest eigenvalues will be down-weighted the most; when the spectrum is inverted, they will be given the smallest weights.
-In contrast, the modes with the smallest eigenvalues will be up-weighted the most.
-In other words, if an eigenspectrum is not perfectly flat, all modes will be given different weights and it is possible to up-weight a few modes much more than others.
-The subtle slope of the eigenspectrum in this toy example is the result of describing shapes in the data that aren't physically there \cc{reword sentence...
-the shape is there but it's not valid?}.
-This gives rise to a small amount of signal loss because it is possible to overfit a few modes (the highest weighted ones) ever so slightly.
-We will see in the next section how this effect can be exaggerated as the `steepness' of the spectrum changes.
+If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue of $\textbf{C}$ would be representative of real fluctuations in the data.
+However, when using an estimated $\hat{\textbf{C}}$ that is derived from one particular data realization, some of its eigenvalues may be describing random fluctuations that just happen to exist in the data realization.
+Said differently, shapes that may not exist (or have a weaker existence) in a true covariance may appear stronger in the estimated covariance.
+Hence, they will be down-weighted more than they should be.
+
+In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are more trustworthy than the weakest modes.
+Bright foregrounds usually dominate and would therefore exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
+This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid and assigns it the highest eigenvalue (the peak in Figure \ref{toy_sigloss2}.
+
+The danger of an empirically estimated covariance matrix comes from not being able to describe weak eigenmodes accurately.
+The weak eigenmodes of $\hat{\textbf{C}}$ may characterize random noise fluctuations which will be down-weighted.
+This is what we call the `overfitting' of noise, which leads to signal loss.
 
@@
 zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
+Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing fluctuations that may not exist in the true covariance.
 Altering $\hat{\textbf{C}}$ in this way is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
@@
 
-We have shown how signal loss can arise due to unintentionally up-weighting eigenmodes with small eigenvalues (overfitting the noise).
+We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes with a data-estimated covariance.
 We will next show how this effect is exaggerated by reducing the total number of independent samples in a dataset.
@@
 We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
-The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply for the last few eigenmodes.
-This slope is a consequence of reducing the variance of the dataset through averaging.
-More specifically, when numbers are averaged together we are absorbing outliers into the average, resulting in a narrower distribution of the data.
-Hence, the eigenvalues, which rank the strength of variances in the data, decreases more than an un-averaged case.
+
+The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply, especially for the last few eigenmodes.
+This is because we have fewer independent modes --- fewer shapes in the data --- so we do a worse job characterizing the weak eigenmodes.
+Therefore, there is a more dramatic difference in weighting between the modes and we end up down-weighting random noise-like fluctuations more severely than for the un-fringe-rate filtered case.
 
@@
 The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
-All eigenspectra steepen for the final few eigenmodes, a behavior that results in a few noisy modes being upweighted more strongly than others, thereby overfitting noise and causing signal loss in the final power spectrum estimate.}
+This spectrum is steeper than that in Figure \ref{fig:toy_sigloss2}, resulting in more dramatic difference in weighting between eigenmodes.
+Consequently, if all eigenmodes are used in weighting it is possible to down-weight random noisy modes more severely than for the un-fringe-rate filtered case.}
 	\label{fig:toy_sigloss5}
@@
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data.
-There is a larger amount of signal loss than for un-fringe-rate filtered data, a consequence of a steeper eigenspectrum slope which results from washing out variances in the data through averaging.
+There is a larger amount of signal loss than for un-fringe-rate filtered data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
+This example shows that it is possible to down-weight modes more severely for the un-fringe-rate filtered since there is a more dramatic difference in weighting between modes.
 The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
@@
 
-The eigenspectrum shape has large consequences on the resulting power spectra, as evidenced by the power spectra shown in Figure \ref{fig:toy_sigloss7}.
-There is a much larger amount of signal loss for this time-averaged dataset.
-To reiterate, the drop-off in the eigenspectrum shape suggests that when the spectrum is inverted, a few modes are up-weighted much more strongly than the rest.
-\cc{math?} This dramatic up-weighting drowns out the EoR signal, giving rise to signal loss.
-Additionally, most of our power spectrum information is coming from only the last few modes and as a result, it is a noisier estimate.
+The power spectrum results for inverse covariance weighted fringe-rate filtered data is shown in Figure \ref{fig:toy_sigloss7}.
+As expected, there is a much larger amount of signal loss for this time-averaged dataset.
+Additionally, because of the steepened eigenspectrum, most of our power spectrum information is coming from only the last few modes and as a result, it is a noisier estimate.
 This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
 
-Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates.
-Longer integrations increase sensitivity but reduce the number of independent samples, resulting in steep drop-offs in eigenspectra.
+Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates when using data-estimated covariance matrices.
+Longer integrations increase sensitivity but reduce the number of independent samples, resulting in weakly characterized, steep eigenspectra that can overfit noise greatly.
 
@@
 
-In Section \ref{sec:toymodel} we showed how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between foreground eigenmodes and EoR eigenmodes.
+In Section \ref{sec:toymodel} we showed one example of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from random fluctuation-induced eigenmodes in an estimated one.
 We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ in order to minimize signal loss.
@@
 The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}} + \textbf{I}$.
-By adding the identity, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum \cc{why?}.
+By adding the identity, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
+If all modes are given similar weights, we avoid down-weighting artificial modes more than others.
 
 The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by zeroing all but the first three eigenmodes.
-This means that the first three eigenmodes will be given weights (the three highest variance modes will be down-weighted), but the rest will be treated with similar weights.
-Hence, we avoid up-weighting the last few noisy modes and have negligible signal loss.
+This means that the first three eigenmodes will be given weights, but the rest will be treated with similar weights.
+Again, flattening the eigenspectrum results in negligible signal loss.
 However, we do not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
@@
 	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods.
-The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used, where $\textbf{C}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
+The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used, where $\hat{\textbf{C}}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
 Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.
@@
 
-\noindent Because of the lower triangular matrix, this window function has the property of preventing the leakage of foreground power from low $k$ to high $k$ modes.
+\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage of foreground power from low $k$ to high $k$ modes.
 Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
-Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing foreground bias.
+Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the contamination of foreground bias.
 
@@
 
-To mitigate crosstalk bias, we apply a fringe-rate filter that suppresses fringe-rates of zero... \cc{why don't we filter out fringe-rates of zero completely?}
+To mitigate crosstalk bias, which appears as a static bias in time, we apply a fringe-rate filter that suppresses fringe-rates of zero.
+Figure \ref{fig:frp} shows that the filter response is zero for such static signals.
+The effect of filtering out zero fringe-rates on power spectrum results is shown in \citet{ali_et_al2015}.
+Most notably, power spectrum detections exist at all $k$'s without crosstalk removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
 
@@
 \section{A toy model for signal loss}
-\label{sec:SigLossToy}
+\label{sec:sigloss_appendix}
 
@@
 where $\eta$ is parameter quantifying our success at estimating the true covariance matrix.
-If $\eta = 1$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
-On the other hand, if $\eta =0$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
+If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
+On the other hand, if $\eta =1$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
 
@@
 \end{equation}
-This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta$ (perfect estimation of $\C$) and goes to zero as $\eta$ approaches $1$.
+This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect estimation of $\C$) and goes to zero as $\eta$ approaches $1$.
 \begin{figure}

### 2017-08-24 PAPER.tex
status of paper before going on hold for qual studying

@@
 In this paper, we discuss three themes that are essential to investigate for a robust $21$ cm power spectrum analysis.
-We also highlight four power spectrum techniques and their trade-offs, traps, and connections to the themes .
+We also highlight four power spectrum techniques and their trade-offs, traps, and connections to the themes.
 We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER.
@@
 In section 2 we introduce the three themes of our focus, using a toy model to develop intuition for each one.
-Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}.
-We conclude in Section 7.
+Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum limit.
+We conclude in Section 4.
 
@@
 For example, narrow window functions can be used to minimize the covariance of a particular $k$ value with other ones (\citealt{liu_et_al2014b}).
-\cc{math!} In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
+In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
 The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
@@
 The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements (Figure \ref{fig:paper}) that are arranged in a grid layout.
-For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines, of which there are a total of $56$.
+For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines.
 For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and \citet{ali_et_al2015}.
@@
 
-We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} only by the fringe-rate filter.
+For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines.
+All power spectrum results are produced using channels $95$-$115$, corresponding to a center redshift of $z=8.4$.
+We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} mainly by the fringe-rate filter.
 In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
@@
 
+\cc{This section needs to be filled in once our method is finalized...}
+
 We now shift our attention towards computing signal loss for our fringe-rate filtered PAPER-64 dataset.
-To recap, we use 30 m East/West baselines of PAPER-64.
-Our dataset spans $8$ hours of LST ($.5$-$8.6$ hrs), includes a total of $51$ baselines, and is fringe-rate filtered using an optimal fringe-rate filter.
-We have two datasets (even days and odd days), and only cross-multiply data from different days and different baselines.
-We are interested in $21$ frequency channels (channels 95-115), which yields a power spectrum for a redshift of $z=8.4$.
-
 While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), which leads to substantial loss.
@@
 \end{eqnarray}
-
-Using the input and output power spectrum estimates for a range of EoR amplitudes, we next describe two methods to determine signal loss associated with the over-fitting of noise from inverse covariance weighting of PAPER-64 data.
-\cc{describing both methods may be overkill?}
-
-The first method is very straightforward.
-Post-bootstrapping, our final power spectrum estimates are 1-dimensional and only a function of $k$.
-For each $k$, we simply look at $P_{out}$ as a function of $P_{in}$, as shown in Figure \ref{fig:sigloss1_data}.
-The shape of this function can be explained as follows.
-At small injection levels (small $\textbf{e}$), $P_{out}$ and $P_{in}$ are equal, and there is no signal loss.
-As the amplitude of EoR increases, we then move into a regime where the final output power spectrum is lower than the unweighted input one.
-This is dangerous, because without correcting for this effect one might be led to underestimate the EoR signal.
-The peculiar tail at very low injection levels (where $P_{out} > P_{in}$) is not a physical feature, but rather illustrates that there is some non-negligible power in the cross-terms of Equation \ref{eq:crossterm} when $\textbf{e}$ is very small.
-
-For this method, we interpolate the signal loss factor (per $k$), computed as $P_{in}/P_{out}$, at a $P_{out}$ value equal to the $2\sigma$ power spectrum upper limit of our data.
-In other words, we look at $\hat{\textbf{p}}_{\alpha} \propto \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{x}^{-1}\textbf{x}$, compute its $2\sigma$ upper limit (mean over bootstraps + $2 \times $standard deviation over bootstraps), and interpolate the value of $P_{in}/P_{out}$ at this value.
-We therefore end up with one signal loss correction factor per $k$.
 
@@
 
-Our second method for estimating signal loss is similar to the first, but more comprehensive in a statistical sense.
-Instead of looking at input and output power spectra after bootstrapping, we now look at their values for every bootstrap in order to get a sense of their distributions.
-Figure \ref{fig:sigloss2_data} plots $P_{in}$ vs.
-$P_{out}$ for $20$ bootstraps, and as expected, the function now has a spread in the width-direction in comparison to what was plotted in Figure \ref{fig:sigloss1_data}, but otherwise shows a familiar trend.
-Similarly, our weighted power spectra also has a defined spread due to bootstrapping.
-
 %\begin{figure*}
@@
 
-Using these two distributions ($P_{in}/P_{out}$ and $\hat{\textbf{p}}$), we can create bins along the $\hat{\textbf{p}}$ axis to yield histograms of signal loss factors for each bin.
-We similarly sort the values of $\hat{\textbf{p}}$ into the same bins, and multiply the probability of $\hat{\textbf{p}}$ per bin (the number of values falling into that bin, divided by the total) with the signal loss factors in that bin, essentially computing a weighted average across all bins to obtain a final signal loss factor per $k$.
-The signal loss results for this method are very similar to the previous method.
-For future power spectrum results, we choose to use the second method because it computes final signal loss values using our full distributions of measurements.
-
-\cc{This next paragraph needs to be worked on.
-What I'm going for is a plot that `proves' our signal loss method is correct, but it's hard to show since the combination of inverse covariance weighting + signal loss correction produces results that are HIGHER than the unweighted level.
-The plot shown below uses PS points instead of error bars, which brings them into closer agreement...}
-To verify our signal loss computations, we compare the unweighted power spectrum estimate of EoR (`true' EoR) with the signal loss corrected weighted power spectrum estimate of EoR + data in a regime where the injected EoR is very large (since there is minimal signal loss for small EoR).
-We compare these two quantities because we must ensure that our weighted combined dataset, after signal loss correction, does not lie below the level of EoR.
-From Figure \ref{fig:sigloss_beforeafter}, we see over $3$ orders of magnitude of signal loss associated with the inverse covariance weighting of fringe-rate filtered PAPER-64 data.
-The power spectrum, post-correction, lies just above the EoR-only power spectrum.
-However, it exhibits a different shape due to \cc{??}.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/sigloss_beforeafter.png}
-	\caption{Power spectrum estimates of the combined EoR + PAPER-64 dataset, pre (squares) and post (circles) signal loss correction.
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\columnwidth]{plots/sigloss_beforeafter.png}
+%	\caption{Power spectrum estimates of the combined EoR + PAPER-64 dataset, pre (squares) and post (circles) signal loss correction.
 The dashed blue line is the unweighted power spectrum estimate of EoR alone.}
-	\label{fig:sigloss_beforeafter}
-\end{figure}
-
-One thing to note is that for both methods, we have been careful to validate that the computations yield no signal loss (signal loss factors of $1$) for the unweighted power spectrum case, as is expected.
-This is important in confirming that signal loss is a direct result of the choice for $\textbf{C}$.
-Similarly, we can compute signal loss for intermediate cases as well, such as a regularized $\textbf{C}$ which exhibits some lossiness, but not as much as inverse covariance weighting.
+%	\label{fig:sigloss_beforeafter}
+%\end{figure}
 
@@
 
+\cc{This section is under construction...}
+
 With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{R}$.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
+%	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
+%	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
 The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
 The solid green line is the theoretical noise level prediction based on observational parameters.}
-	\label{fig:ps2_data}
-\end{figure*}
+%	\label{fig:ps2_data}
+%\end{figure*}
 
@@
 Figure \ref{fig:eigenspectrum} shows this spectrum for baseline (1,4).
-The spectrum is very steep, spanning 4 orders of magnitude, implying that a couple modes are weighted much more than the rest.
+The spectrum is very steep, spanning 4 orders of magnitude, implying that different modes are given dramatically different weights.
 In fact, this behavior is much more extreme than we saw in the toy model, whose eigenspectrum (for the `fringe-rate filtered' case) only started to vividly steepen for the last few eigenmodes.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/eigenspectrum.png}
-	\includegraphics[width=0.4\textwidth]{plots/covariance.png}
-	\caption{Eigenspectrum for $\textbf{C}$ for baseline (1,4) for the 21 channels ofs interest (left) and covariance matrix $\textbf{C}$ for the same baseline (right).}
-	\label{fig:eigenspectrum}
-\end{figure*}
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=0.4\textwidth]{plots/eigenspectrum.png}
+%	\includegraphics[width=0.4\textwidth]{plots/covariance.png}
+%	\caption{Eigenspectrum for $\textbf{C}$ for baseline (1,4) for the 21 channels ofs interest (left) and covariance matrix $\textbf{C}$ for the same baseline (right).}
+%	\label{fig:eigenspectrum}
+%\end{figure*}
 
@@
 \cc{Should I just show the identity multiplication scheme that seems to be the best? Show lots of options? Mention different options but not show the results?}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
+	\caption{Highest sensitivity power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff} = \hat{\textbf{C}} * \textbf{I}$ (minimal signal loss).
+Black and grey points correspond to positive and negative power spectrum values, respectively, with $2\sigma$ error bars also plotted.
+The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
+The solid green line is the theoretical noise level prediction based on observational parameters.
+This power spectrum result differs from \citet{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
+Additionally, an optimal fringe-rate filter was used instead of a degraded one.
+Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.}
+	\label{fig:ps1_data}
+\end{figure*}
 
@@
 
+The highest sensitivity power spectrum results using PAPER-64 data, shown in Figure \ref{fig:ps1_data}, have positive biases.
+As discussed in Section \ref{sec:BiasTypes}, the detections that appear at low $k$ values are most likely attributable to foreground leakage.
+However, the positive biases at higher $k$ values require further investigation.
+
 \cc{Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing} \\

### 2017-10-05 PAPER.tex
Fixed algebra mistake in Appendix

@@
 \begin{equation}
-\Chat^{-1}\x = \frac{\C^{-1}\x}{1-\eta} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right],
+\Chat^{-1} = \frac{\C^{-1}}{1-\eta} \left[ \I - \frac{\eta \x \x^t \C^{-1}}{1+ \eta (g-1)}\right],
 \end{equation}
@@
 \begin{equation}
-\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta g}{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta g}{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
+\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
 \end{equation}
@@
 \label{eq:phatlossexpanded}
-\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta g}{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta g}{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
-&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} \left( \frac{\beta h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\beta^2 h_\alpha^2}{F_{\alpha \alpha}}\right)^{n-k},
+\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
+&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} \left( \frac{\varepsilon h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\varepsilon^2 h_\alpha^2}{2 F_{\alpha \alpha}}\right)^{n-k},
 \end{eqnarray}
-where $\beta \equiv \eta g/[1+ \eta (g-1)]$.
+where $\beta \equiv \eta g/[1+ \eta (g-1)]$ and $\varepsilon \equiv \beta / g$.
 To proceed, we take the ensemble average of $\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties.
@@
 \label{eq:betahh}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_a = 1}^\infty \frac{(-\eta)^{m_1 + \dots + m_a}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle.
-\end{equation}
-Writing out the ensemble averaged quantity on the right hand side and defining $M \equiv m_1 + \dots + m_a$ yields
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_{a+d} = 1}^\infty \frac{(-\eta)^{m_1 + \dots + m_{a+d}}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_{a+d}-d} h_\alpha^b h_{\alpha \alpha}^c \rangle.
+\end{equation}
+Writing out the ensemble averaged quantity on the right hand side and defining $M \equiv m_1 + \dots + m_{a+d}$ yields
 \begin{eqnarray}
-\langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha \C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
+\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha \C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
 &=& \sum_{i_1}^N \sum_{j_1}^N \cdots  \sum_{k_1}^N \sum_{l_1}^N \cdots  \sum_{p_1}^N \sum_{q_1}^N \cdots  ( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} )_{p_1 q_1} \dots (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1})_{p_c q_c}  \nonumber \\
@@
 \begin{equation}
-\langle g^{m_1 + \dots + m_a} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_a} \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
+\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_{a+d}} \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
 \end{equation}
@@
 \begin{equation}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a \left[ \frac{\eta }{1+\eta (N-1)} \right]^d \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
 \end{equation}
@@
 \eqref{eq:phatlossexpanded} is relatively straightforward.
-One simply replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha \alpha}$ with $2F_{\alpha \alpha}$.
+One simply replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $\varepsilon$ with $\varepsilon_N \equiv  \eta  / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha \alpha}$ with $2F_{\alpha \alpha}$.
 Performing these substitutions and recalling \acl{make sure the reader will indeed be recalling at this point} that $\langle \hat{p}_\alpha \rangle = \langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
 \begin{equation}
-\frac{\langle \hat{p}_\alpha^\textrm{loss} \rangle}{\langle \hat{p}_\alpha \rangle} = \frac{(1-\beta_N)^2}{1- 2\beta_N + \beta_N^2 \left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / F_{\alpha \alpha}}.
+\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle} = \frac{1- 2\varepsilon_N + \varepsilon_N^2 \left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / 2F_{\alpha \alpha}}{(1-\beta_N)^2}.
 \end{equation}
@@
 \begin{equation}
-\frac{\langle \hat{p}_\alpha^\textrm{loss} \rangle}{\langle \hat{p}_\alpha \rangle} \Bigg{|}_{\C \propto \I} = \frac{(1-\beta_N)^2}{(1-\beta_N)^2 + \beta_N^2} = \frac{(1-\eta)^2}{(1-\eta)^2 + N^2 \eta^2}.
-\end{equation}
-This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect estimation of $\C$) and goes to zero as $\eta$ approaches $1$.
+\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle}  \Bigg{|}_{\C \propto \I} = \left( \frac{1-\varepsilon_N}{1-\beta_N} \right)^2 = \left[\frac{1+ \eta(N-2)}{1- \eta}\right]^2.
+\end{equation}
+This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect estimation of $\C$) and goes to infinity as $\eta$ approaches $1$.
 \begin{figure}

### 2017-10-05 PAPER.tex
corrected some sigloss math

--- 2017-08-24 PAPER.tex
@@
 
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e}$.
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e}$.
 Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:
@@
 
-Taking the case of very large $\textbf{e}$, so that $\textbf{R}_{r} \sim \textbf{R}_{e}$ and any terms involving only $\textbf{x}$ are small, yields:
+Taking the case of very large $\textbf{e}$ so that any terms involving only $\textbf{x}$ are small, yields:
 
@@
 \label{eq:pout_expand}
-P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{e}\textbf{Q}_{\alpha}\textbf{R}_{e}\textbf{x}.
+P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x}.
 \end{eqnarray}

### 2017-10-14 PAPER.tex
-Made small changes -- skimmed for the first time post-qual -Status of paper going into HERA Oct 2017 meeting

@@
 Backer Precision Array for Probing the Epoch of Reionization (PAPER).
+We also highlight how detailed investigations of these themes have led to a revised $21$ cm power spectrum upper limit from PAPER.
 \cc{motivate a bit more once the paper is complete}
@@
 Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman2010}), the Long Wavelength Array (LWA; \citealt{ellingson_et_al2009}),  the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; \citealt{patra2015}).
-Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR;\citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; \citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
+Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; \citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
 The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; \citealt{pober_et_al2014}).
@@
 In section 2 we introduce the three themes of our focus, using a toy model to develop intuition for each one.
-Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum limit.
+Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction paper}).
 We conclude in Section 4.
@@
 
-There are many choices for a data analyst.
+There are many choices a data analyst must consider.
 How can time-ordered measurements be combined?
@@
 If not corrected for, it could lead to a false non-detection.
-Computing signal loss has subtle challenges but is crucial to the accuracy of any result.
+Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
 \item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
@@
 \item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds.
-A successful EoR detection would also imitate a bias.
+In particular, a successful EoR detection would also imitate a bias.
 Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR.
-In this paper we will highlight some sources of bias and discuss ways to mitigate their effects.
+In this paper we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must pass.
 \end{itemize}
@@
 The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
-We focus on these techniques because \cc{??}.
 However, some have limitations, and we will discuss circumstances in which there are trade-offs.
+We choose to focus on these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also being standard steps in general $21$ cm analyses.
 \begin{itemize}
@@
 Hence, bootstrapping is a useful method for estimating errors of a dataset from itself.
-By randomly drawing many samples of the data, we get a sense of its inherent variance, though there are subtleties to consider such as the independence of values in a dataset.
+By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to consider such as the independence of values in a dataset.
 \item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different dimensions of a dataset to cross-validate results.
 In particular, null tests can be used to verify whether results are free of systematics (\citealt{keating_et_al2016}).
+An EoR detection must pass jack-knife and null tests.
 \end{itemize}
 
-In the next three subsections, we go into each theme in depth, focusing on how power spectrum technique trade-offs affect each.
+In the next three subsections, we study each theme in depth, focusing on how power spectrum technique trade-offs affect each.
 We use a toy data model to develop intuition into why certain analysis choices may be appealing and discuss ways in which they are limited.
 We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues.
-Ultimately, \cc{some kind of summarizing sentence here}.
+Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be considered for robust $21$ cm results.
 
@@
 It has length ($N_{t}, N_{f}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
-Visibilities are measurements of the Fourier transform of the sky along spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes we only need to take one Fourier transform along the line-of-sight dimension.
+Visibilities are measurements of the Fourier transform of the sky along $2$ spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes we only need to take one Fourier transform of our data along the line-of-sight dimension.
 We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{x},
-\end{equation}
-
-\noindent where $\textbf{R}$ is a weighting matrix.
-As an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{R} = \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin.
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{x}
+\end{equation}
+
+\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin.
 The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}).
+$\textbf{R}$ is a weighting matrix --- as an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{R} = \textbf{I}$, the identity matrix.
 
@@
 \noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum.
-We have a choice for $\textbf{M}$.
+The data analyst has a choice for $\textbf{M}$.
 For simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}
@@
 We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, a simplistic but realistic representation of a single bright source.
-We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
+We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal \cc{need to motivate why, since real EoR does have correlations}.
 Our combined data vector is $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and a random Gaussian signal as a mock EoR signal. Real parts are shown here. \cc{colorbar?}}
+	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and a random Gaussian signal as a mock EoR signal. Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 
-One choice for a weight matrix $\textbf{R}$ is an inverse covariance matrix.
+One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix.
 This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
@@
 However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
-
-One attractive way to estimate $\textbf{C}$ is to empirically derive it from the data vector $\textbf{x}$ itself:
+For PAPER, we are mostly limited from being able to estimate a true $\textbf{C}$ due to our instrumental models.
+
+Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data vector $\textbf{x}$ itself:
 
@@
 
-First, we compute the power spectrum of $\textbf{x}$ using the OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$.
+First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$.
 The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
-Also plotted in the figure are the unweighted power spectrum of $\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
+Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
 
@@
 This is evidence of signal loss.
-In order to understand the behavior of this result, we need to closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 2.3cm 0.3cm 2.3cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
-	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only, EoR only, and FG + EoR. Real parts are shown here. \cc{colorbar?}}
+In order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only (middle), and FG + EoR (right). Real parts are shown here.}
 	\label{fig:toy_sigloss12}
@@
 
-It turns out that because we estimated $\textbf{C}$ from our data, its eigenspectrum offers insight into understanding how inverse covariance weighting affects our result.
+It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our true $\textbf{C}$, and this difference has consequences on our result.
 An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
@@
 	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
-The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.}
+The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
+These empirically estimated covariance matrices yield eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.}
 	\label{fig:toy_sigloss2}
@@
 Bright foregrounds usually dominate and would therefore exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
-This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid and assigns it the highest eigenvalue (the peak in Figure \ref{toy_sigloss2}.
+This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
 
@@
 Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing fluctuations that may not exist in the true covariance.
-Altering $\hat{\textbf{C}}$ in this way is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
+Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
 The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
-In this case we recover EoR, demonstrating that if we can model our foregrounds, we can down-weight them without signal loss.
+In this case we recover EoR, demonstrating that if we can model our foregrounds perfectly (and disentangle them from other modes), we can down-weight them without signal loss.
 There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section \ref{sec:otherweight}.
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
-We averaged every four samples together, yielding $25$ independent samples in time.
+We average every four samples together, yielding $25$ independent samples in time.
 Real parts are shown here.
-Right: Eigenspectrum of the covariance matrices of foregrounds only (blue), EoR only (red), and FG + EoR (green).
+Right: Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
 The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
-This spectrum is steeper than that in Figure \ref{fig:toy_sigloss2}, resulting in more dramatic difference in weighting between eigenmodes.
+This spectrum is steeper than that in Figure \ref{fig:toy_sigloss2}, resulting in more dramatic differences in weighting between eigenmodes.
 Consequently, if all eigenmodes are used in weighting it is possible to down-weight random noisy modes more severely than for the un-fringe-rate filtered case.}
@@
 
-In Section \ref{sec:toymodel} we showed one example of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from random fluctuation-induced eigenmodes in an estimated one.
+In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from random fluctuation-induced eigenmodes in an estimated one.
 We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ in order to minimize signal loss.
@@
 	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and multiplying an identity matrix to $\hat{\textbf{C}}$ (lower right).
-There are many regularization options available to minimize signal loss, and some work better than others depending on the dataset.}
+We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and multiplying an identity matrix with $\hat{\textbf{C}}$ (lower right).}
 	\label{fig:toy_sigloss8}
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
-	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix to $\textbf{C}$ (magenta).
+	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $\textbf{C}$ (magenta).
 }
@@
 Multiplying by the identity results in a diagonal matrix, meaning we are only left with correlation information between the same two frequencies.
-Because we disregard information from all other frequency combinations, we do a poor job suppressing the foreground.
+Because we disregard information from all other frequency combinations in this case, we do a poor job suppressing the foreground.
 But because we flattened the eigenspectrum, we also avoid signal loss.
 
-Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may work better than others based on the dataset.
-\cc{how to make this paragraph less hand-wavy?} One may imagine a situation where a particular systematic is contained to an isolated frequency.
+Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may be more effective than others based on the spectral nature of the components in a dataset.
+One may imagine a situation where a particular systematic is contained to an isolated frequency (such as radio frequency interference or crosstalk).
 In such a case, preserving only the diagonal elements of $\hat{\textbf{C}}$ would be an effective way of removing this contamination.
@@
 Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate confidence intervals for our measurements.
-Two ways of estimating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
+Two popular ways of estimating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
 In a perfect world, both methods would match up.
@@
 
-We form $100$ bootstraps, each comprised of an array of length $1000$ that is created by a random resampling of the original data, with replacement.
-The standard deviation over the $100$ bootstraps gives an error estimation for our dataset.
-As shown in Figure \ref{fig:toy_error1}, the error computed from bootstrapping matches our theoretical prediction.
+We form $100$ bootstraps, each comprised of an array of length $N$ that is created by a random resampling of the original data, with replacement.
+The standard deviation over the $100$ bootstraps gives an error estimate for our dataset.
+As shown in Figure \ref{fig:toy_error1} by the grey star, the error computed from bootstrapping matches our theoretical prediction.
 
@@
 If, for example, a dataset has many repeated values inside it, this would be reflected in each bootstrap.
-The same value would be present multiple times within a bootstrap and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are many of them.
+The same value would be present multiple times within a bootstrap and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of itself.
 Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates errors.
@@
 
-Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent samples to $1000/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing the same number of samples as the length of the dataset), under-estimates the error by a factor of $\sim3$.
+Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent samples to $N/10 = 100$.
+Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ samples), under-estimates the error by a factor of $\sim3$.
 This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
 In fact, the error derived from bootstrapping is a strong function of the number of samples that are drawn (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
-However, if we know that we have $100$ independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction.
+However, if we know that we have $100$ independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction as expected.
 
@@
 For example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the number of averages performed.
-Additionally, we can have a non-integer effective number of samples due to the weighting.
+We can also have a non-integer effective number of samples due to the weighting.
+Hence, we do not recommend bootstrapping unless the number of independent samples along the axis that is being re-sampled is well-determined.
 
@@
 One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
-However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset \cc{explain why}.
+However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
 
@@
 
-A power spectrum detection could be EoR, but it could also be attributed to other sources of bias.
-Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of $21$ cm data analyses.
+In a $21$ cm power spectrum, detections could be the EoR signal (the holy grail for experiments like PAPER), but they could also (and unfortunately more likely) be attributed to other sources of bias.
+Connecting a detection to EoR as opposed to noise or foreground bias will be a key challenge of future $21$ cm data analyses.
 In this section we will discuss possible sources of bias in a measurement, as well as techniques that can help mitigate their effects.
 We will also present a series of essential tests that a legitimate EoR detection must pass and highlight how these tests can be used to identify biases.
-These tests serve as a a starting point for the necessary task of verifying a future EoR detection.
+These tests serve as a starting point for the necessary task of verifying a future EoR detection.
 
@@
 Despite current best efforts to do so, however, there remains some foreground leakage that can show up as detections in a power spectrum.
-\cc{how do we know that?}
 
@@
 The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
-Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode \cc{develop more or cite?}.
+Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
 
@@
 However, there remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any suppression techniques.
+This crosstalk bias could potentially be identified by comparing the shapes of excesses in power spectra from cross-talk containing data and cross-talk removed data.
 
@@
 In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum detection.
-In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data.
+In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to prove that our excesses are not EoR and to identify their likely cause.
 
@@
 We now present a case study of these same three themes using data from the PAPER experiment.
-We use the intuition we've developed through our toy model simulations in order to make smartly-motivated data analysis choices for PAPER.
-In light of our new understandings, we also highlight major changes since \citet{ali_et_al2015}.
+We use the intuition we've developed through our toy model simulations in order to make educated data analysis choices for PAPER.
+In light of our new understandings, we also highlight major changes since \citet{ali_et_al2015} which have contributed to a revised power spectrum upper limit result.
 
@@
 
-The previously best published $21$ cm upper limit result from (\citealt{ali_et_al2015}) uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
+The previously best published $21$ cm upper limit result from \citet{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
 
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the case study.
-
-For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines.
-All power spectrum results are produced using channels $95$-$115$, corresponding to a center redshift of $z=8.4$.
+The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the following sections.
+
+For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citet{ali_et_al2015} uses an RA range of $0$-$8.6$ hours).
+All power spectrum results are produced using channels $95$-$115$, corresponding to a center redshift of $z=8.4$, identical to the analysis in \citet{ali_et_al2015}.
 We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} mainly by the fringe-rate filter.
@@
 
-\cc{This section needs to be filled in once our method is finalized...}
+\cc{THIS SECTION IS LARGELY INCOMPLETE.}
+
+\cc{Goal of this section is to showcase our signal loss transfer function for PAPER-64 and describe how we compute our signal loss factors.}
+
+\cc{The signal loss methodology is still being worked on but is almost done - it should be straightforward to type it up after.}
+
+\cc{Also include text describing Figure \ref{fig:sigloss_modeloop} which is an interesting one}
 
@@
 \end{eqnarray}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/sigloss_modeloop.png}
+	\caption{\cc{fill out caption}}
+	\label{fig:sigloss_modeloop}
+\end{figure}
 
@@
 
-\cc{This section is under construction...}
+\cc{THIS SECTION IS ALSO LARGELY INCOMPLETE.}
 
@@
 
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
-%	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-%	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
 The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
 The solid green line is the theoretical noise level prediction based on observational parameters.}
-%	\label{fig:ps2_data}
-%\end{figure*}
+	\label{fig:ps2_data}
+\end{figure*}
 
@@
 Figure \ref{fig:eigenspectrum} shows this spectrum for baseline (1,4).
+\cc{need to make this figure still}.
 The spectrum is very steep, spanning 4 orders of magnitude, implying that different modes are given dramatically different weights.
@@
 The full inverse covariance treatment of our data is suboptimal to the unweighted case, meaning that choosing such a weighting does not help suppress systematics as we intended.
-Now we would like to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum.
-There are many choices for determining the covariance matrix $\textbf{C}$, as described in Section \ref{sec:SiglossOverview}, but here we will illustrate \cc{?} promising ones as applied to PAPER-64.
-
-\cc{Should I just show the identity multiplication scheme that seems to be the best? Show lots of options? Mention different options but not show the results?}
+Our ultimate goal is to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum.
+There are many choices for determining the covariance matrix $\textbf{C}$, as described in Section \ref{sec:SiglossOverview}, but here we will illustrate \cc{some number?} promising ones as applied to PAPER-64.
+
+\cc{To Do: Insert PS results here that show different regularization schemes}
+
+\cc{ALSO: this is where our final revised limit will likely be! (Fig \ref{fig:ps1_data})}
 
@@
 In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
-We first walk through a derivation for a theoretical error estimation based on observational parameters.
+We first walk through a derivation for a theoretical error estimation (of thermal noise) based on observational parameters.
 Although a theoretical model often differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-We also highlight major changes in our calculation from \citet{ali_et_al2015}, which in total decrease the estimated power spectrum sensitivity of PAPER-64 by a factor of \cc{fill in when ready}.
+We also highlight major changes in our calculation from \citet{ali_et_al2015}, which in total decreases the estimated power spectrum sensitivity of PAPER-64 by a factor of \cc{fill in when ready}.
 Finally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
@@
 
-Theoretical errors, computed from the instrumental temperature and observational parameters, provide a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
+Theoretical errors of noise, computed from the instrumental temperature and observational parameters, provide a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
 Here we walk through a detailed computation of a theoretical noise estimation as applied to PAPER-64 observations and highlight major changes from \citet{ali_et_al2015}.
@@
 where $\nu$ are frequencies in GHz. We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ at $150$ MHz. This is lower than in \citet{ali_et_al2015} because \cc{why?}.
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from only using the real part of power spectrum estimates when plotting and quoting upper limits (imaginary component is discarded).
+\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum estimates after squaring visibility measurements.
+In \citet{ali_et_al2015}, a factor of $2$ was mistakenly used, which would imply that that real parts were obtained prior to squaring.
 \item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation.
@@
 For the analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$.
+The revised limit in \cc{cite retraction paper} uses three separation types.
 \item $t_{int}$: The integration time of the data.
@@
 In \citet{ali_et_al2015}, this number was the total number of $30$ m East/West baselines used in the analysis.
-However, using the total number of baselines neglects the fact that we divid baselines into $5$ groups before cross-multiplying data.
+However, using the total number of baselines neglects the fact that we divide baselines into $5$ groups before cross-multiplying data.
 Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where $N_{gps} = 5$.
@@
 For $5$ groups, there are $25$ total cross-products, minus $5$ cross-products since we avoid multiplying the same group with itself.
-For our PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ baselines.
+For our PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$.
 \item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
@@
 
-where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
+\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
 This rms temperature sets the variance of the Gaussian random noise.
@@
 As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised of independent samples.
-The PAPER-64 pipeline outputs $N$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
+The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
 In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the baseline bootstrap and time axes simultaneously.
@@
 In \citet{ali_et_al2015}, each group is then sampled with replacement to create a new group of the same size, which can have repeated baselines inside it.
-In doing so, we are sacrificing some of our sensitivity since there ends up being $3$-$4$ repeated baselines per group (Figure \ref{fig:toy_error2} shows a fraction of independent samples of $\sim55\%$ for $10$ total independent samples) .
+In doing so, we are sacrificing some of our sensitivity since there ends up being $3$-$4$ repeated baselines per group (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim55\%$ for $10$ total independent samples) .
 In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one, which we fill randomly.
@@
 
-Power spectrum estimates for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
+Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
 The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \hat{\textbf{C}}*\textbf{I}$, in order to minimize signal loss.
@@
 
-The highest sensitivity power spectrum results using PAPER-64 data, shown in Figure \ref{fig:ps1_data}, have positive biases.
+The highest sensitivity power spectrum result using PAPER-64 data and all revised methods, shown in Figure \ref{fig:ps1_data}, has positive biases.
 As discussed in Section \ref{sec:BiasTypes}, the detections that appear at low $k$ values are most likely attributable to foreground leakage.
@@
 
-\cc{Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing} \\
-\cc{Need to explain positive bias still... not sure where it comes from yet!}
+\cc{THIS NEXT PART IS INCOMPLETE.}
+
+\cc{To Do: Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing}
+
+\cc{To Do: Describe null tests that PAPER-64 fails... for example, it fails null tests in LST, which implies that our excesses are likely residual foregrounds}
 

### 2017-11-10 PAPER.tex
-Fleshed out case study signal loss section (3.1) -Updated signal loss plots -Wrote in some acknowledgements -Added author list

@@
 \documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
-%\documentclass[twocolumn,apj,numberedappendix]{emulateapj}
+%\documentclass[twocolumn,numberedappendix]{emulateapj}
 \shorttitle{Data Analysis Methods for the Detection of the Epoch of Reionization}
@@
 Carina Cheng\altaffilmark{1},
-et al.
+Aaron R. Parsons\altaffilmark{1,2},
+Matthew Kolopanis \altaffilmark{3},
+Daniel C. Jacobs\altaffilmark{3}, 
+Saul A. Kohn\altaffilmark{4},
+Adrian Liu\altaffilmark{1,5}, 
+James E. Aguirre\altaffilmark{5},
+Zaki S. Ali\altaffilmark{1}, 
+Richard F. Bradley\altaffilmark{6,7,8},
+Gianni Bernardi\altaffilmark{9,10,11}, 
+Chris L. Carilli\altaffilmark{12,13},
+David R. DeBoer\altaffilmark{2}, 
+Matthew R. Dexter\altaffilmark{2},
+Joshua S. Dillon\altaffilmark{1},
+Pat Klima\altaffilmark{7},
+David H. E. MacMahon\altaffilmark{2},
+David F. Moore\altaffilmark{5},
+Chuneeta D. Nunhokee\altaffilmark{14},
+Jonathan C. Pober\altaffilmark{15}, 
+William P. Walbrugh\altaffilmark{9},
+Andre Walker\altaffilmark{9}
 }
+
+\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
+\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
+\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
+\altaffiltext{4}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
+\altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
+\altaffiltext{6}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
+\altaffiltext{7}{National Radio Astronomy Obs., Charlottesville VA}
+\altaffiltext{8}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
+\altaffiltext{9}{Square Kilometer Array, S. Africa, Cape Town South Africa}
+\altaffiltext{10}{Dept. of Physics and Electronics, Rhodes University}
+\altaffiltext{11}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
+\altaffiltext{12}{National Radio Astronomy Obs., Socorro NM}
+\altaffiltext{13}{Cavendish Lab., Cambridge UK}
+\altaffiltext{14}{Dept. of Physics and Electronics, Rhodes University, Grahamstown South Africa}
+\altaffiltext{15}{Dept. of Physics, Brown University, Providence RI}
 
@@
 
-\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
-%\altaffiltext{2}{Hubble Fellow}
-%\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley, CA}
-%\altaffiltext{3}{Berkeley Center for Cosmological Physics, Berkeley, CA}
-%\altaffiltext{3}{Dept. of Physics and Astronomy, U. Pennsylvania, Philadelphia, PA}
-%\altaffiltext{8}{School of Earth and Space Exploration, Arizona State U., Tempe, AZ}
+% ABSTRACT ---------------------------------------------------------------------------------
 
@@
 Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-We also highlight how detailed investigations of these themes have led to a revised $21$ cm power spectrum upper limit from PAPER.
-\cc{motivate a bit more once the paper is complete}
+In particular, we highlight how detailed investigations of these themes have led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64.
 \end{abstract}
+
+% INTRO ---------------------------------------------------------------------------------
 
@@
 
-This paper is organized as follows.
-In section 2 we introduce the three themes of our focus, using a toy model to develop intuition for each one.
-Section 3 presents a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction paper}).
-We conclude in Section 4.
+This paper is organized into two main sections.
+In Section \ref{sec:Themes} we introduce the three themes of our focus, using a toy model to develop intuition for each one.
+In Section \ref{sec:CaseStudy} we present a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}).
+We conclude in Section \ref{sec:Con}.
+
+% SECTION 2 INTRO ---------------------------------------------------------------------------------
 
@@
 
+% SECTION 2 SIGLOSS ---------------------------------------------------------------------------------
+
 \subsection{Signal Loss}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}} + \textbf{I}$.
-By adding the identity, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies).
+By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
 If all modes are given similar weights, we avoid down-weighting artificial modes more than others.
@@
 
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \cdot \textbf{I}$.
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting.
 In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
 For this toy model, our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by the identity results in a diagonal matrix, meaning we are only left with correlation information between the same two frequencies.
+Multiplying by the identity, element-wise, results in a diagonal matrix, meaning we are only left with correlation information between the same two frequencies.
 Because we disregard information from all other frequency combinations in this case, we do a poor job suppressing the foreground.
@@
 As we investigated however, there are trade-offs between the weighting method used, its foreground-removal effectiveness, and the amount of resulting signal loss.
+
+% SECTION 2 ERROR ESTIMATION ---------------------------------------------------------------------------------
 
@@
 	\caption{The fraction of independent elements in a bootstrap as a function of the total number of elements in a dataset.
-A fraction of $1.0$ means that all elements in a bootstrap are independent, and therefore sensitivity is maximized (alternatively, this axis can be thought of as power spectrum sensitivity).
+A fraction of $1.0$ means that all elements in a bootstrap are independent, and therefore sensitivity is maximized (alternately, this axis can be thought of as power spectrum sensitivity).
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
@@
 \end{figure}
+
+% SECTION 2 BIAS ---------------------------------------------------------------------------------
 
@@
 
+% SECTION 3  ---------------------------------------------------------------------------------
+
 \section{Case Study: PAPER-64}
@@
 \end{figure}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[height=0.35\textwidth]{plots/paper_dipole.png}
-%	\includegraphics[height=0.35\textwidth]{plots/antenna_layout.png}
-%	\caption{PAPER dipole in South Africa (left) and PAPER-64 antenna layout (right).}
-%	\label{fig:paper}
-%\end{figure*}
 
@@
 
+% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
+
 \subsection{Case Study: Signal Loss}
@@
 The second filter represents the fringe-rate filtering step in our data analysis pipeline.
-This mock EoR signal is injected on top of fringe-rate filtered PAPER-64 data at a range of amplitude levels, ranging from well-below the data level, to well-above.
+This mock EoR signal is injected on top of fringe-rate filtered PAPER-64 data at a range of amplitude levels that spans the data level.
 
@@
 \begin{equation}
+\label{eq:Pin}
 P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}_{\alpha}\textbf{I}\textbf{e}
@@
 
-For the unweighted case ($\textbf{R} \equiv \textbf{I}$), we expect $P_{out}$ and $P_{in}$ to be equal, and hence the ratio $P_{in} / P_{out} = 1$.
-For the weighted case, this may not be true due to signal loss.
-To quantify the loss, we look at the ratio $P_{in}/P_{out}$ as the amplitude level of the injected signal \textbf{e} is increased.
-In the next section, we describe our signal loss transfer function ($P_{in}$ vs.
-$P_{out}$) for PAPER-64 data and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
+The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function that maps an output power spectrum distribution into an input distribution.
+By viewing data through this signal loss lens, we are asking the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe our signal loss transfer function for PAPER-64 data and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
 
@@
 
-\cc{THIS SECTION IS LARGELY INCOMPLETE.}
-
-\cc{Goal of this section is to showcase our signal loss transfer function for PAPER-64 and describe how we compute our signal loss factors.}
-
-\cc{The signal loss methodology is still being worked on but is almost done - it should be straightforward to type it up after.}
-
-\cc{Also include text describing Figure \ref{fig:sigloss_modeloop} which is an interesting one}
-
 We now shift our attention towards computing signal loss for our fringe-rate filtered PAPER-64 dataset.
-While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), which leads to substantial loss.
+While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in \citet{ali_et_al2015} which leads to substantial loss.
 With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/sigloss_modeloop.png}
-	\caption{\cc{fill out caption}}
-	\label{fig:sigloss_modeloop}
-\end{figure}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1.0\textwidth]{plots/sigloss1_data.png}
-%	\caption{$P_{in}$ vs.
-$P_{out}$ (black points) for 15 injection levels and 21 $k$'s.
-The solid grey line is the $2\sigma$ upper limit for the weighted power spectrum of PAPER-64 data, and it is at this level where the signal loss factor $P_{in}/P_{out}$ is computed by interpolation.
-\cc{Maybe re-do this plot with closer-together points}}
-%	\label{fig:sigloss1_data}
-%\end{figure*}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1.0\textwidth]{plots/sigloss2_data.png}
-%	\caption{$P_{in}$ vs. $P_{out}$ (black) for 15 injection levels, 20 bootstraps, and 21 $k$'s. The transparent grey region represents all PAPER-64 bootstrapped estimates.}
-%	\label{fig:sigloss2_data}
-%\end{figure*}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\columnwidth]{plots/sigloss_beforeafter.png}
-%	\caption{Power spectrum estimates of the combined EoR + PAPER-64 dataset, pre (squares) and post (circles) signal loss correction.
-The dashed blue line is the unweighted power spectrum estimate of EoR alone.}
-%	\label{fig:sigloss_beforeafter}
-%\end{figure}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1.0\textwidth]{plots/sigloss2_noise.png}
-%	\caption{$P_{in}$ vs. $P_{out}$ (blue) for 15 injection levels, 20 bootstraps, and 21 $k$'s. \cc{Plot a semi-transparent cyan range of pCn values instead of just the max}}
-%	\label{fig:sigloss2_noise}
-%\end{figure*}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_nosigloss.png}
-%	\includegraphics[width=0.4\textwidth]{plots/ps2_noise.png}
-%	\caption{Full inverse covariance weighted power spectrum of pure noise (black and grey points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
-Black points correspond to positive values, while grey points correspond to originally negative values that have been made positive for plotting.
-The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction based on observational parameters.}
-%	\label{fig:ps2_noise}
-%\end{figure*}
-
-\subsubsection{Data Weighting}
-\label{sec:Weight}
-
-\cc{THIS SECTION IS ALSO LARGELY INCOMPLETE.}
-
-With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{R}$.
-Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
-We have found that the balance between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
-
-Using full inverse covariance weighting, our power spectrum results before and after signal loss correction is shown in Figure \ref{fig:ps2_data}.
-Prior to signal loss correction, it is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction.
-Post-correction, the power spectrum values blow up much higher than both the theory and unweighted power spectrum.
+Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with an unweighted case ($\textbf{R} = \textbf{I}$, right plot).
+The figures depict a smoothed-out distribution (via kernel density estimators) of our input and output power spectra.
+To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (where one copy of \textbf{e} in Equation \ref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
+For each injection, we perform $20$ bootstraps (over baselines, as explained in Section \ref{sec:Boot}), resulting in a total of $800$ data points on our $P_{in}$ vs.
+$P_{out}$ grid.
+It is noted that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
+
+The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, or a perfect mapping from $P_{out}$ to $P_{in}$ (which we expect to occur for the unweighted case).
+The solid grey horizontal lines mark the peak of the data distribution $\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted cases.
+One can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$ using the transfer curve for the inverse covariance weighted case, implying a signal loss factor of $\sim1000$.
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
+	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \ref{eq:Pin} and \ref{eq:sigloss}.
+Smoothed out distributions (via kernel density estimators) are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
+The solid black diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data distribution.
+From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss whereas the unweighted case does not exhibit loss.}
+	\label{fig:sigloss_transfercurve}
+\end{figure*}
+
+One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have signal gain ($P_{out} > P_{in}$).
+This is unphysical in nature but caused due to the cross-terms dominating in Equation \ref{eq:pout_expand} once $\textbf{e}$ becomes small.
+As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to destroyed if weighting the data using itself.
+Although we only show figures for one $k$ value, we note that the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
+
+Finally, it is worth thinking about the spread, or scatter, in our transfer curves in more detail.
+One might imagine that there should be one true $P_{out}$ value for every $P_{in}$, implying one well-determined signal loss factor for every data value.
+In practice we have found that this is not the case, as evidenced by the colored `heat-map' in Figure \ref{fig:sigloss_transfercurve}.
+The cause of this scatter can be thought of as comprised of two components.
+
+The first component is merely the fact that the values of the cross-terms in Equation \ref{eq:pout_expand} change for different EoR signals, $\textbf{e}$.
+Since we draw different random $\textbf{e}$'s for every bootstrap, there is a (small) range of $P_{out}$ values that could result for the same $P_{in}$.
+This randomness is what causes the spread seen in the unweighted case (right plot of Figure \ref{fig:sigloss_transfercurve}), as well as most of the spread in the weighted case (left plot).
+
+The second component of scatter is less intuitive and only applies (at a low level) to the weighted case.
+The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$.
+For example, if we are extremely unlucky, $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
+If weighting using empirically-derived covariances, this entire EoR signal would be destroyed.
+On the contrary, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
+This range of how `unlucky' we can get is not that dramatic in real life, but it is important to correct for the fact that a particular $P_{out}$ value could in principle stem from a range of $P_{in}$ values.
+
+We now explain how we use the transfer curves to map our data (a distribution along $P_{out}$) to a signal-loss corrected distribution (along $P_{in}$) that takes into account the range of signal loss that can be associated for a particular $P_{out}$ value.
+
+Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), we fit a polynomial to each, representing mean signal loss functions.
+We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for every $P_{in}$ value.
+In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
+
+Equipped with our new signal loss curves (a one-to-one mapping function for the unweighted case, and a somewhat smeared out function for the weighted case), we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ columns, treating positive and negative halves of the data distribution separately.
+We note that for PAPER-64, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power), and sometimes centered around 0, representing noise-like measurements.
+
+Finally, we sum up all rows of $P_{out}$ where each row is a $P_{in}$ probability distribution allowed by our measurements.
+This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens.
+We show these final distributions in Figure \ref{fig:sigloss_datadist_inversecovariance} for every $k$.
+We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
+
+\begin{figure*}
+	\centering
+	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
+	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on PAPER-64 data after signal loss correction.
+Power spectrum points are computed from the peak of the distributions.
+Errors are computed using $95\%$ confidence intervals.}
+	\label{fig:sigloss_datadist_inversecovariance}
+\end{figure*}
+
+To summarize this section, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
+The blue dashed line represents the unweighted power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case).
+The black and grey points are positive and negative power spectrum values plotted with $2\sigma$ error bars.
+Prior to signal loss correction, it is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve).
+Post-correction, the power spectrum values blow up to be higher than both the thEoRy and unweighted power spectrum.
+
+Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of independent samples in PAPER-64.
+PAPER-64 has $\sim 8$ independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
+Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first $8$.
+Hence, there is a substantial down-weighting of many random modes, a large loss that the signal loss transfer function captures and corrects for.
+\cc{elaborate?} In the next section, we investigate alternate weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (black points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
 The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
@@
 
-Following our toy model investigation in Section \ref{sec:SiglossOverview}, we investigate the shape of the eigenspectrum of $\textbf{C}$ for a typical baseline used in the analysis.
-Figure \ref{fig:eigenspectrum} shows this spectrum for baseline (1,4).
-\cc{need to make this figure still}.
-The spectrum is very steep, spanning 4 orders of magnitude, implying that different modes are given dramatically different weights.
-In fact, this behavior is much more extreme than we saw in the toy model, whose eigenspectrum (for the `fringe-rate filtered' case) only started to vividly steepen for the last few eigenmodes.
-The consequence of assigning individual weights to many more modes than are present in the data is significant --- to the point of resulting in power spectrum values that are higher than if no weighting scheme was used at all.
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=0.4\textwidth]{plots/eigenspectrum.png}
-%	\includegraphics[width=0.4\textwidth]{plots/covariance.png}
-%	\caption{Eigenspectrum for $\textbf{C}$ for baseline (1,4) for the 21 channels ofs interest (left) and covariance matrix $\textbf{C}$ for the same baseline (right).}
-%	\label{fig:eigenspectrum}
-%\end{figure*}
-
-The full inverse covariance treatment of our data is suboptimal to the unweighted case, meaning that choosing such a weighting does not help suppress systematics as we intended.
-Our ultimate goal is to find a weighting method that does successfully down-weight contaminants in our data and make some improvement over the unweighted power spectrum.
-There are many choices for determining the covariance matrix $\textbf{C}$, as described in Section \ref{sec:SiglossOverview}, but here we will illustrate \cc{some number?} promising ones as applied to PAPER-64.
-
-\cc{To Do: Insert PS results here that show different regularization schemes}
-
-\cc{ALSO: this is where our final revised limit will likely be! (Fig \ref{fig:ps1_data})}
+\subsubsection{Minimizing Signal Loss}
+\label{sec:Weight}
+
+With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{R}$.
+Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
+We have found that the balance between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
+
+We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e.
+flattening out part of the eigenspectrum) can help minimize signal loss.
+We experiment with this idea on PAPER-64 data, dialing the number of modes down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse covariance weighting of our $21$ channels).
+The power spectrum results for one $k$ value, both before and after signal loss correction, are shown in Figure \ref{fig:sigloss_modeloop}.
+We see that the amount of signal loss increases as weighting becomes more aggressive (grey curve).
+In other words, more random fluctuations are being overfit and subtracted as more modes are down-weighted.
+We also find that the power spectrum upper limit, post signal loss correction, increases with the number of down-weighted modes (black curve).
+As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ samples that we have in fringe-rate filtered PAPER-64 data.
+
+Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting is beneficial compared to not weighting (blue dashed line).
+We see in Figure \ref{fig:sigloss_modeloop} that this occurs when only the strongest $\sim3-4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not significant.
 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_nosigloss.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
-	\caption{Highest sensitivity power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff} = \hat{\textbf{C}} * \textbf{I}$ (minimal signal loss).
+	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
+	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ for fringe-rate filtered PAPER-64 data.
+Values are shown before (grey) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that are down-weighted.
+This regularization knob is tuned from $0$ modes (i.e.
+unweighted) to $21$ modes (i.e.
+full inverse covariance weighting).
+Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting.
+Also plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance weighted case (red), and added-identity case (cyan).
+All three regularizations shown (black, red, cyan) perform similarly at their best.}
+	\label{fig:sigloss_modeloop}
+\end{figure*}
+
+Two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} which denote power spectrum values, post-signal loss correction, for two other regularization schemes.
+We multiply an identity matrix element-wise to $\hat{\textbf{C}}$ (i.e.
+inverse variance weighting, shown in red), and also add an arbitrary level of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan).
+We see that all three regularization schemes (black, red, cyan) perform similarly.
+
+We choose to use $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting, for the remainder of this paper, which we will denote as $\hat{\textbf{C}}_{eff}$.
+We choose this weighting scheme due to its simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
+
+Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure \ref{fig:ps1_data}.
+Again, black and grey points correspond to positive and negative power spectrum values respectively, with $2\sigma$ errors bars.
+Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of noise (solid green).
+From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$ (though we only use one baseline type in our analysis as opposed to $3$).
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
+	\caption{Highest sensitivity power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$.
 Black and grey points correspond to positive and negative power spectrum values, respectively, with $2\sigma$ error bars also plotted.
@@
 This power spectrum result differs from \citet{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
-Additionally, an optimal fringe-rate filter was used instead of a degraded one.
-Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.}
+Additionally, an optimal fringe-rate filter was used instead of a degraded one, resulting in an increase in sensitivity but also an increase in signal loss.
+Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.
+We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$.}
 	\label{fig:ps1_data}
 \end{figure*}
+
+In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 data.
+There are many other weighting schemes that we leave for consideration in future work.
+For example, one could estimate $\hat{\textbf{C}}$ using information from different subsets of baselines.
+For redundant arrays this could mean calculating $\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$m diagonal PAPER baselines (instead of the horizontal E/W ones).
+Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied when forming a power spectrum estimate.
+This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation, unlike PAPER-64.
+
+Another possible way to regularize $\hat{\textbf{C}}$ is to use different ranges of LST.
+For example, one could calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to down-weight.
+Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from data that is similar but not exactly the same as the data that is being down-weighted.
+Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting modes in the power spectrum dataset itself.
+
+% SECTION 3 ERROR ESTIMATION ---------------------------------------------------------------------------------
 
@@
 Although a theoretical model often differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-We also highlight major changes in our calculation from \citet{ali_et_al2015}, which in total decreases the estimated power spectrum sensitivity of PAPER-64 by a factor of \cc{fill in when ready}.
-Finally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
+Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
+
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the \citet{ali_et_al2015} analysis of PAPER-64.
+While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
 
@@
 For the analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$.
-The revised limit in \cc{cite retraction paper} uses three separation types.
+The revised limit in \cc{cite kolopanis paper} uses three separation types.
 \item $t_{int}$: The integration time of the data.
@@
 
+Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of \citet{ali_et_al2015} in Figure \ref{fig:sense_check}.
+Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$.
+This is consistent with
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/sense_check.png}
+	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously published sensitivity limits (grey).
+Both sensitivity analyses plotted assume only one baseline type (an additional factor of $\sqrt{3}$ for 3 baseline types is needed to match \citet{ali_et_al2015} exactly).
+Major factors that contribute to the discrepancy are $\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our sensitivity (higher noise floor) by a factor of $\sim7$.}
+	\label{fig:sense_check}
+\end{figure}
+
 To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation.
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps_noise_pk.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps_noise_delta.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_reg.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_reg.png}
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data.
@@
 
+% SECTION 3 BIAS ---------------------------------------------------------------------------------
+
 \subsection{Case Study: Bias}
@@
 
+% CONCLUSION ---------------------------------------------------------------------------------
+
 \section{Conclusion}
@@
 
+We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$
+
 \section{Acknowledgements}
-\cc{NSF Graduate Research Fellowship Program (GRFP) Fellowship}
-\cc{UC Berkeley Chancellor's Fellowship}
+The author would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (grant \cc{fill in}), and thank Eric Switzer for helpful discussions.
+PAPER is supported by grants from the National Science Foundation (awards 0804508, 1129258, and 1125558).
+ARP, JCP, and DCJ would also like to acknowledge NSF support (awards 1352519, 1302774, and 1401708, respectively).
+JEA would like to acknowledge a generous grant from the Mount Cuba Astronomical Association for computing resources.
+We also graciously thank SKA-SA for site infrastructure and observing support.
 \label{sec:Ack}

### 2017-11-10 PAPER.tex
fairly complete draft minus jackknive section and cocnlusion

@@
 We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter.
-Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and $\hat{\textbf{C}} = \hat{\textbf{C}} * \textbf{I}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
+Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
 All three are in agreement, validating our analytical thermal noise calculation.
@@
 Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
-The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$, where $\textbf{C}_{eff} = \hat{\textbf{C}}*\textbf{I}$, in order to minimize signal loss.
+The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$ in order to minimize signal loss.
 We show upper limits ($2\sigma$ error bars) for three different results.
@@
 	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods.
-The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used, where $\hat{\textbf{C}}_{eff} = \textbf{C}*\textbf{I}$, in order to minimize signal loss.
+The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used in order to minimize signal loss.
 Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.

### 2017-11-10 PAPER.tex
-Standardized eqref across whole paper -Standardized superscript alpha's and beta's on Q's instead of subscripts

@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{x}
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
 \end{equation}
@@
 We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating longer, using more baselines, etc.
-However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by the two copies of $\textbf{x}$ in Equation \ref{eq:qhat}.
+However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}.
 If both copies of $\textbf{x}$ come from the same baseline and time, it can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument.
@@
 \label{eq:Pin}
-P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}_{\alpha}\textbf{I}\textbf{e}
+P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 P_{out,\alpha} \equiv \hat{\textbf{p}}_{e,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x}.
+&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
@@
 
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e}$.
-Expanding Equation \ref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$.
+Expanding Equation \eqref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:
 
@@
 \label{eq:crossterm}
-P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}_{\alpha}\textbf{R}_{x}\textbf{x}.
+P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
@@
 \label{eq:pout_expand}
-P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}_{\alpha}\textbf{R}_{r}\textbf{x}.
+P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
 \end{eqnarray}
 
-We see that our naive expression for $P_{out}$ is the first term in Equation \ref{eq:pout_expand}, but there are also two additional terms.
+We see that our naive expression for $P_{out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two additional terms.
 An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are physically unrelated.
-In \citet{ali_et_al2015}, this assumption is used, and the first term in Equation \ref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
+In \citet{ali_et_al2015}, this assumption is used, and the first term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
 
@@
 The spurious correlation of the two means that we cannot compute signal loss using a signal-only simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss.
-Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \ref{eq:sigloss}, which subtracts the weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
+Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 
@@
 \begin{eqnarray}
-P_{in,\alpha} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}_{\alpha}\textbf{I}\textbf{e} \\
-P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}_{\alpha}\textbf{C}_{x}^{-1}\textbf{x}
+P_{in,\alpha} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x}
 \end{eqnarray}
@@
 The figures depict a smoothed-out distribution (via kernel density estimators) of our input and output power spectra.
-To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (where one copy of \textbf{e} in Equation \ref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
+To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (where one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
 For each injection, we perform $20$ bootstraps (over baselines, as explained in Section \ref{sec:Boot}), resulting in a total of $800$ data points on our $P_{in}$ vs.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \ref{eq:Pin} and \ref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Smoothed out distributions (via kernel density estimators) are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
@@
 One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have signal gain ($P_{out} > P_{in}$).
-This is unphysical in nature but caused due to the cross-terms dominating in Equation \ref{eq:pout_expand} once $\textbf{e}$ becomes small.
+This is unphysical in nature but caused due to the cross-terms dominating in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
 As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to destroyed if weighting the data using itself.
@@
 
-The first component is merely the fact that the values of the cross-terms in Equation \ref{eq:pout_expand} change for different EoR signals, $\textbf{e}$.
+The first component is merely the fact that the values of the cross-terms in Equation \eqref{eq:pout_expand} change for different EoR signals, $\textbf{e}$.
 Since we draw different random $\textbf{e}$'s for every bootstrap, there is a (small) range of $P_{out}$ values that could result for the same $P_{in}$.
@@
 
-Equation \ref{eq:sense} represents the most sensitive estimate for $\hat{\textbf{p}}(k)$ given our observing parameters.
+Equation \eqref{eq:sense} represents the most sensitive estimate for $\hat{\textbf{p}}(k)$ given our observing parameters.
 An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging together positive and negative $k$'s.
@@
 We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter.
-Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \ref{eq:sense}.
+Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \eqref{eq:sense}.
 All three are in agreement, validating our analytical thermal noise calculation.
@@
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data.
-The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we regularize $\hat{\textbf{C}}$ by setting $\hat{\textbf{C}} = \hat{\textbf{C}} * \textbf{I}$ to minimize signal loss.
+The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we use $\hat{\textbf{C}}_{eff}$ to minimize signal loss.
 The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction as calculated by Equation \ref{eq:sense}.
+The solid green line is the theoretical noise level prediction as calculated by Equation \eqref{eq:sense}.
 All three estimates agree.}
@@
 Tailoring window functions is one way to suppress foreground biases.
-As alluded to in Section \ref{sec:SiglossOverview}, we have a choice for the normalization matrix $\textbf{M}$ in Equation \ref{eq:phat}.
+As alluded to in Section \ref{sec:SiglossOverview}, we have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}.
 For the analysis of PAPER-64 data, we compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
@@
 \begin{equation}
-\textbf{F}_{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}_{\alpha}\textbf{R}\textbf{Q}_{\beta} ]
+\textbf{F}_{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
 \end{equation}
@@
 In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk.
-In order to avoid the former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \ref{eq:qhat}.
+In order to avoid the former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \eqref{eq:qhat}.
 Namely, the PAPER-64 dataset is divided into two halves: even julian dates and odd julian dates.
@@
 
+% APPENDIX ---------------------------------------------------------------------------------
+
 \appendix
@@
 
-The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by \acl{We need to decide whether the Q matrices have their Greek indices as upper or lower indices.} \acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
+The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by \acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
 \begin{equation}
@@
 
-Our strategy for computing the signal loss will be to insert Eq.
-\eqref{eq:ChatDef} \acl{Make sure we're consistent w.r.t.
-``Equation" vs.
-``Eq."} into Eq.
-\eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
 We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
@@
 To proceed, we take the ensemble average of $\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties.
-Inspecting Eq.
-\eqref{eq:phatlossexpanded}, we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, where $a$, $b$, and $c$ are integers.
+Inspecting Equation \eqref{eq:phatlossexpanded}, we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, where $a$, $b$, and $c$ are integers.
 Expanding $\beta$ in powers of $g$, we have
@@
 \end{equation}
-and re-inserting this into Eq. \eqref{eq:betahh} yields
+and re-inserting this into Equation \eqref{eq:betahh} yields
 \begin{equation}
@@
 \end{equation}
-With this result, taking the ensemble average of Eq.
-\eqref{eq:phatlossexpanded} is relatively straightforward.
+With this result, taking the ensemble average of Equation \eqref{eq:phatlossexpanded} is relatively straightforward.
 One simply replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $\varepsilon$ with $\varepsilon_N \equiv  \eta  / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha \alpha}$ with $2F_{\alpha \alpha}$.
@@
 
-In general, one's estimate of the covariance will not be expressible in the form given by Eq.
-\eqref{eq:ChatDef}.
+In general, one's estimate of the covariance will not be expressible in the form given by Equation \eqref{eq:ChatDef}.
 However, the qualitative point here is that the signal loss can be expressed as a multiplicative factor.

### 2017-11-14 PAPER.tex
-Wrote first draft of PSA64 jackknives -Wrote first draft of conclusion

@@
 Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
-The estimates use a weighting matrix of $\textbf{C}_{eff}^{-1}$ in order to minimize signal loss.
+The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss.
 We show upper limits ($2\sigma$ error bars) for three different results.
 Our revised error estimation method is in black, where we only bootstrap along the baseline axis and we maximize sensitivity by random sampling only the last baseline in each group.
-The red curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group.
-In blue, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data.
+The blue curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group.
+In red, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data.
 We under-estimate errors in doing so because we are drawing many more samples than independent ones.
@@
 	\includegraphics[width=\columnwidth]{plots/data_errors.png}
-	\caption{$2\sigma$ upper limit power spectrum estimates using PAPER-64 data and three different bootstrapping methods.
-The data is fringe-rate filtered and a weighting matrix of $\textbf{C}_{eff}^{-1}$ is used in order to minimize signal loss.
-Three different bootstrapping methods are shown: the black and red use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.
-It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly).
-The blue result bootstraps over both the baseline and time axes, and illustrates how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
+	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping methods.
+The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the effects of bootstrapping from signal loss.
+Three different bootstrapping methods are shown: the blue and black use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.
+It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly), as shown by the black curve.
+In red, bootstrapping occurs over both the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
 	\label{fig:data_errors}
@@
 
-\subsubsection{Jack-Knife Tests}
-
-The highest sensitivity power spectrum result using PAPER-64 data and all revised methods, shown in Figure \ref{fig:ps1_data}, has positive biases.
-As discussed in Section \ref{sec:BiasTypes}, the detections that appear at low $k$ values are most likely attributable to foreground leakage.
-However, the positive biases at higher $k$ values require further investigation.
-
-\cc{THIS NEXT PART IS INCOMPLETE.}
-
-\cc{To Do: Describe some jackknife tests done on PAPER-64 data, such as random signs to baselines and even/odd summing and differencing}
-
-\cc{To Do: Describe null tests that PAPER-64 fails... for example, it fails null tests in LST, which implies that our excesses are likely residual foregrounds}
+\subsubsection{Jackknife Tests}
+
+The highest sensitivity power spectrum result using PAPER-64 data and all revised methods, shown in Figure \ref{fig:ps1_data}, has positive biases at low $k$ values.
+As discussed in Section \ref{sec:BiasTypes}, these detections are most likely attributable to foreground leakage.
+Here we demonstrate $3$ null tests performed on PAPER-64 data that verify that the positive detections are indeed due to foreground variation and not attributable to EoR.
+
+The $3$ null test results are shown in Figure \ref{fig:null}, with each test described as the following:
+
+\begin{itemize}
+\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised PAPER-64 power spectrum (one baseline type only) with weighting matrix $\textbf{C}_{eff}$.
+There are clear detections at low $k$'s.
+\item Even/Odd (blue): We split our dataset into even (e) and odd (o) days, where $\textbf{x}_{1} = e + o$ and $\textbf{x}_{2} = e - o$.
+We form datasets in this way to ensure that we use the full sensitivity of our data.
+When cross-multiplied, we obtain:
+\begin{equation}
+\textbf{x}_{1}\textbf{x}_{2}^{\dagger} = ee^{\dagger} - eo^{\dagger} + oe^{\dagger} - oo^{\dagger}
+\end{equation}
+If the same sky signal is in both the even and odd datasets, we expect it to cancel out.
+\item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the analysis.
+Again, we form $\textbf{x}_{1} = b_{1} + b_{2}$ and $\textbf{x}_{2} = b_{1} - b_{2}$, where $b_{1}$ is the first baseline group and $b_{2}$ is the second baseline group.
+\item LST (purple): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 4.6-8.6 hours).
+We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$
+\end{itemize}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/null.png}
+	\caption{Results of $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ errors (grey shaded region).
+For each, we took jackknives along different axes of the dataset - by julian days (separating even and odd days; blue), by baselines (green), and by LST (purple).
+We expect the sky signal to disappear for a `passing' null test.
+We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to particular baselines or days of data.}
+	\label{fig:null}
+\end{figure}
+
+Investigating Figure \ref{fig:null}, we find that both the baselines and even/odd null tests are consistent with noise.
+We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+The null test in LST (purple) is much more illuminating.
+The fact that there are many power spectrum points outside the estimated error region signifies that the bias we see is likely from foregrounds that vary in LST.
+In other words, $t_{1}$ and $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+The errors on this null test are also large, also reflective of residual foregrounds.
+
+We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s.
+This would illuminate the particular LST range that introduces the foreground bias (or whether the bias is constant in LST), and could potentially be traced to a individual bright radio source.
+This type of detailed analysis will be critical at EoR sensitivities, however, for the purpose of this paper we are not surprised that the bias we see comes from foregrounds in regions where we expect leakage.
 
@@
 
-We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$
+Although current $21$cm published power spectrum upper limits lie a $\sim$couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, expect to continue to push towards EoR sensitivities.
+As the field progresses towards a coveted detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknive and null tests.
+
+In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$cm power spectrum techniques on signal loss, error estimation, and bias, which can be summarized as follows:
+
+\begin{itemize}
+\item Substantial signal loss can result when weighting data using empirically estimated covariances.
+Loss of the $21$cm signal is especially significant if more eigenmodes are down-weighted than exist in the data (having an under-constrained covariance matrix).
+Hence, there exists a trade-off between sensitivity driven time-averaging techniques such as fringe-rate filtering and signal loss.
+\item Signal injection and recovery simulations can be used to quantify signal loss.
+However, a signal-only simulation can underestimate loss by failing to account for spurious correlations between the data and signal.
+\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are correlated.
+If the number of independent samples in a dataset is well-determined, bootstrapping is a simple and accurate way of estimating errors.
+\item An EoR detection must pass all null tests.
+Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in a true EoR detection, and can also be used to tease out systematics.
+\end{itemize}
+
+As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
+For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$.
+The reasons for a previously underestimated limit and ways in which our new analysis differs can be summarized by the following:
+
+\begin{itemize}
+\item Signal loss, previously found to be $<2\%$ in \citet{ali_et_al2015}, was underestimated by a factor of $\sim$$1000$.
+Because PAPER-64 is limited by its number of samples, we use a regularized covariance weighting in our revised analysis to minimize loss, thereby increasing the original PAPER-64 limit in mK$^{2}$ by a factor of $\sim$$50$ instead of $1000$.
+Underestimated signal loss represents the bulk of our revision.
+\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data with a reduced number of independent samples from fringe-rate filtering.
+They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra.
+Hence, the net change for our error estimation is negligible, though the intuition behind the previous estimation was incorrect.
+\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding an increase in predicted sensitivity level by a factor of $\sim$$7$.
+We have verified our revised prediction extensively using pure noise simulations.
+\end{itemize}
+
+The $21$cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand instruments.
+On the power spectrum analysis side, we recognize that there is still much work to do.
+Even with robust signal loss simulations and precise error calculations, we are currently limited by data volume and foreground suppression strategies.
+However, the future promises to bring higher sensitivity $21$ cm measurements, better foreground and instrumental models, more effective and less lossy weighting techniques --- and with all that, an improved understanding of reionization and our early Universe.
+
+% ACKNOWLEDGEMENTS ---------------------------------------------------------------------------------
 
 \section{Acknowledgements}
-The author would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (grant \cc{fill in}), and thank Eric Switzer for helpful discussions.
+The author would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
 PAPER is supported by grants from the National Science Foundation (awards 0804508, 1129258, and 1125558).
@@
 \label{sec:sigloss_appendix}
+
+\cc{Note to Adrian: I standardized all Q indices to be superscripts instead of subscripts. Also standardized equations to be ``Equation eqref" (spell out Equation, and use eqref for references)}
 

### 2017-11-14 PAPER.tex
-Made Danny's edits for first half of paper

@@
 In particular, we highlight how detailed investigations of these themes have led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64.
+This revised result mostly stems from an updated signal loss calculation for loss associated with empirically estimated covariances, and we consider this limit to supersede previously published PAPER-64 and PAPER-32 results.
 \end{abstract}
@@
 We also highlight four power spectrum techniques and their trade-offs, traps, and connections to the themes.
-We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER.
+We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum from the lessons learned.
 
@@
 Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
+PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
 \item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
 Errors can be estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of bias in a visibility measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds.
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds.
 In particular, a successful EoR detection would also imitate a bias.
@@
 \begin{itemize}
-\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is considered an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
 Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
@@
 EoR).
-However, a challenge of inverse covariance weighting is in accurately describing a covariance matrix that best describes the data.
+However, a challenge of inverse covariance weighting is in accurately defining a covariance matrix that best describes the data.
 \item \textbf{Bootstrapping:} Because theoretical models for covariance matrices are questionable and theoretical error estimation methods rely on assumptions that can be violated by data, applying theoretical errors to a $21$ cm measurement is often avoided.
@@
 In the next sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
-Our ultimate goal in experimenting with weighting is to suppress foregrounds perfectly without destroying an EoR signal.
+Our ultimate goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
 
@@
 This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies in time and frequency, a simplistic but realistic representation of a single bright source.
+For PAPER-64 we use $\sim$$8$ hours of data for our analysis, but here we scale it down for this toy model with no loss of generality.
+We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid with a fixed frequency and a smoothly varying offset in time, a simplistic but realistic representation of a single bright source.
 We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal \cc{need to motivate why, since real EoR does have correlations}.
@@
 However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
-For PAPER, we are mostly limited from being able to estimate a true $\textbf{C}$ due to our instrumental models.
 
@@
 It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our true $\textbf{C}$, and this difference has consequences on our result.
-An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each frequency mode in the data.
+An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
 In other words, the eigenvalues encode the strength of different shapes in the dataset.
@@
 
-In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are more trustworthy than the weakest modes.
-Bright foregrounds usually dominate and would therefore exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
+In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are more trustworthy than the weakest modes, since that's where we expect bright foregrounds --- the most prominent shapes --- to be.
+If bright foregrounds dominate, these highest eigenvalue modes therefore exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
 This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
 
-The danger of an empirically estimated covariance matrix comes from not being able to describe weak eigenmodes accurately.
-The weak eigenmodes of $\hat{\textbf{C}}$ may characterize random noise fluctuations which will be down-weighted.
-This is what we call the `overfitting' of noise, which leads to signal loss.
+The danger of an empirically estimated covariance matrix comes from not being able to describe weak eigenmodes of $\textbf{C}$ accurately.
+Instead, the weak eigenmodes of $\hat{\textbf{C}}$ may characterize noise-like fluctuations which will be down-weighted.
+These noise fluctuations could be the signal itself, since $\hat{\textbf{C}}$ is constructed using data that contains the signal.
+This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.
 
@@
 Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing fluctuations that may not exist in the true covariance.
-Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more identical to that of $\textbf{I}$.
+Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$.
 The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average, a fringe-rate filter can be designed to up-weight parts of the sky that an instrument is most sensitive to, while down-weighting the opposite.
-We apply a fringe-rate filter to PAPER-64 data in order to optimally combine our time-ordered measurements.
-We weight data based on our primary beam sensitivity, yielding a net increase in sensitivity in our measurements.
+Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes relevant to things that move as expected for the sidereal motion on the sky, while down-weighting modes which are noise-like.
 
@@
 
-The resulting eigenspectra (Figure \ref{fig:toy_sigloss5}, right), as compared to those in Figure \ref{fig:toy_sigloss2}, fall more steeply, especially for the last few eigenmodes.
-This is because we have fewer independent modes --- fewer shapes in the data --- so we do a worse job characterizing the weak eigenmodes.
-Therefore, there is a more dramatic difference in weighting between the modes and we end up down-weighting random noise-like fluctuations more severely than for the un-fringe-rate filtered case.
+The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss5} (right plot).
+The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for the last few eigenmodes.
+This is because we have fewer independent modes --- \cc{need help filling out the rest here...
+and also citing galaxy lit}.
 
@@
 	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss6.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss15.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
@@
 Real parts are shown here.
-Right: Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
-The eigenspectrum of foregrounds only peaks at the zeroth eigenmode, a consequence of the presence of only one sinusoid.
-This spectrum is steeper than that in Figure \ref{fig:toy_sigloss2}, resulting in more dramatic differences in weighting between eigenmodes.
-Consequently, if all eigenmodes are used in weighting it is possible to down-weight random noisy modes more severely than for the un-fringe-rate filtered case.}
+Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
+The dashed spectrum is steeper, resulting in more dramatic differences in weighting between eigenmodes.
+Consequently, if all eigenmodes are used in weighting it is possible to down-weight random noisy modes more severely than for the non-averaged case.}
 	\label{fig:toy_sigloss5}
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
 	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
 We use inverse covariance weighting where $\textbf{C}$ is derived from the data.
-There is a larger amount of signal loss than for un-fringe-rate filtered data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
-This example shows that it is possible to down-weight modes more severely for the un-fringe-rate filtered since there is a more dramatic difference in weighting between modes.
+There is a larger amount of signal loss than for the non-averaged data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
 The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
@@
 Longer integrations increase sensitivity but reduce the number of independent samples, resulting in weakly characterized, steep eigenspectra that can overfit noise greatly.
+\cc{help me fix explanation}
 
@@
 As a first test, we know that our simulated EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$ to obtain a final $\hat{\textbf{C}}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\hat{\textbf{C}}_{FG}$ (defined as $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
 This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
@@
 	\centering
-	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss10.png}
-	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss8.png}
-	\includegraphics[trim={0.4cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss9.png}
-	\includegraphics[trim={1cm 0.8cm 1.3cm 1cm},clip,height=0.25\textwidth]{plots/toy_sigloss11.png}
+	\includegraphics[trim={0.4cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.png}
+	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.png}
+	\includegraphics[trim={0.4cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.png}
+	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
 	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and multiplying an identity matrix with $\hat{\textbf{C}}$ (lower right).}
+We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\hat{\textbf{C}}$ (lower right).}
 	\label{fig:toy_sigloss8}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies).
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \gamma\textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I} for the purpose of this toy model$).
 By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
@@
 
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by zeroing all but the first three eigenmodes.
-This means that the first three eigenmodes will be given weights, but the rest will be treated with similar weights.
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by only using the first three eigenmodes.
+This means that all but the three highest weights will be replaced with $1$'s (equal weights).
 Again, flattening the eigenspectrum results in negligible signal loss.
@@
 
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting.
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
 In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
@@
 However, in practice the two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform weightings.
-Therefore, it is important to place error bars on our measurements that have been derived from its inherent variance.
+Since modeling errors for a complex instrument is only approximate, we choose to compute error bars on our measurements that have been derived from its inherent variance.
 
@@
 For example, power-spectral measurements of $21$ cm data can be made along many axes, including time and baselines.
-Through the process of resampling and averaging along these axes, we can estimate error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
+Averaging each sample set gives us a realization of the power spectrum answer.
+Realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
+Hence, through the process of resampling and averaging along these axes, we can estimate error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
 
@@
 
-This examples highlights the importance of understanding how analysis techniques (e.g.
+This example highlights the importance of understanding how analysis techniques (e.g.
 fringe-rate filtering) can affect a common statistical procedure like bootstrapping.
@@
 For example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the number of averages performed.
-We can also have a non-integer effective number of samples due to the weighting.
+Down-sampling a fringe-rate filtered signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
 Hence, we do not recommend bootstrapping unless the number of independent samples along the axis that is being re-sampled is well-determined.
@@
 The star represents the error associated with drawing $1000$ samples from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data which has $100$ independent samples.
+The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
 They illustrate how errors can be underestimated if drawing more samples than there are independent samples in the data.
@@
 Therefore, we use a slightly modified bootstrapping method.
-For each bootstrap, we first shuffle the data.
-Next, we take the first $4$ samples, and fill the last slot randomly with replacement.
+For each bootstrap, we draw $N-1=4$ samples without replacement and draw the last slot randomly with replacement.
 In doing so there is a small chance a bootstrap will consist of $5$ independent samples, but even with $4$ our sensitivity is nearly maximized.
@@
 In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset.
-However, we have illustrated two situations in which bootstrapping can lead to inaccurate error estimation.
-Trade-offs exist between averaging data and the validity of bootstrapping --- working with correlated data gives rise to questions concerning the effective number of independent samples, how to best calculate it, and whether it is valid to simply use that number when bootstrapping.
-We have also shown a situation in which a naive bootstrapping method can over-estimate errors, thereby compromising measurement sensitivity.
+However, we have illustrated two situations in which bootstrapping can lead to under-estimated errors and sensitivities.
+First, we have shown that bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample.
+Estimated errors can drop to arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements.
+We have also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible.
 While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain analysis choices have compromised the method and whether a variation of traditional re-sampling could be preferred instead.
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
-	\caption{The fraction of independent elements in a bootstrap as a function of the total number of elements in a dataset.
-A fraction of $1.0$ means that all elements in a bootstrap are independent, and therefore sensitivity is maximized (alternately, this axis can be thought of as power spectrum sensitivity).
+	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a dataset (i.e.
+$4$ out of $5$ elements are independent would yield a fraction of $0.8$).
+A fraction of $1.0$ means that all elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
-The former over-estimates error bars since some elements end up being repeated due to random sampling.
-Therefore, sensitivity is not maximized to its full capacity.}
+The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.
+The `outlier' points lying at a fraction of $1.0$ occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
 	\label{fig:toy_error2}
@@
 
-In a $21$ cm power spectrum, detections could be the EoR signal (the holy grail for experiments like PAPER), but they could also (and unfortunately more likely) be attributed to other sources of bias.
-Connecting a detection to EoR as opposed to noise or foreground bias will be a key challenge of future $21$ cm data analyses.
+In a $21$ cm power spectrum, detections could be the EoR signal, but they could also (and unfortunately more likely) be attributed to other sources of bias.
+Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of future $21$ cm data analyses.
 In this section we will discuss possible sources of bias in a measurement, as well as techniques that can help mitigate their effects.
-We will also present a series of essential tests that a legitimate EoR detection must pass and highlight how these tests can be used to identify biases.
-These tests serve as a starting point for the necessary task of verifying a future EoR detection.
+We will also present a series of tests which we suggest be used to help evaluate deep limits and/or detections.
 
@@
 
-Foreground bias is perhaps one of the main limiting factors pushing up against $21$ cm results.
-Foreground signals lie $\sim4$-$5$ orders of magnitude above the cosmological signal, and there are many existing techniques to avoid or remove these strong signals.
-Despite current best efforts to do so, however, there remains some foreground leakage that can show up as detections in a power spectrum.
+Foreground bias is perhaps one of the main factors limiting $21$ cm results.
+Foreground signals lie $\sim4$-$5$ orders of magnitude above the cosmological signal.
+Though there are many techniques proposed for removing foregrounds, most experiments remain ultimately limited by residuals rather than noise.
 
@@
 For a particular baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between the two antennas in the baseline.
-For longer baselines, this value increases, producing what is known as ``the wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; \citealt{thyagarajan_et_al2013}).
+For longer baselines, this value increases, producing what is known as ``the wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; \citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}).
 The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is proportional to $k_{\parallel}$).
@@
 
-Despite making power spectrum measurements outside of the wedge in the ``EoR window", foreground detections are still common at low $k$ values.
+However, this isolation is not perfect.
+In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond the length of a baseline are often still contaminated at a low level.
 This leakage can be attributed to convolution kernels associated with Fourier-transforming visibilities into delay-space.
@@
 In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
-The PAPER-64 window function is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
+The window function used in \citet{ali_et_al2015} is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
 Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
@@
 
-In addition to foreground bias, noise bias can also be responsible for positive power spectrum detections.
-One example is noise bias arising if thermal noise is multiplied by itself.
+In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is multiplied by itself.
 Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise.
@@
 However, there remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any suppression techniques.
-This crosstalk bias could potentially be identified by comparing the shapes of excesses in power spectra from cross-talk containing data and cross-talk removed data.
 
@@
 The jackknife is a resampling technique in which a statistic (i.e.
-power spectrum) is computed multiple times using subsets of the data.
+power spectrum) is computed in subsets of the data.
+These subsets are then compared to reveal systematics.
 In this section we define two main tests --- the null test and the traditional jackknife --- and explain how a power spectrum detection must pass each.
@@
 \item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to investigate underlying systematics.
-A clean measurement should be noise-like (a `null' result) if it is not dominated by systematics.
-There are several ways to perform null tests on data, as implemented in \citet{keating_et_al2016}.
+Several null tests on data are described in \citet{keating_et_al2016}.
 For example, one can divide data into two subsets by separating odd and even julian dates, or the first half of the observing season from the second.
@@
 \item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill confidence in a final result, since a stable result should be consistent through all of them.
-A successful EoR detection must be steadfast throughout all jackknives no matter how the data is sliced, while other sources of bias may come and go depending on the jackknife performed.
+A result must be steadfast throughout all jackknives no matter how the data is sliced.
 Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a power spectrum each time as a day of data is removed, or a baseline is removed.
@@
 
-Suppose we divide the toy model dataset into two subsets, $\textbf{x}_{1}$ and $\textbf{x}_{2}$, which represent jackknives of the complete dataset $\textbf{x}$.
-Both subsets have dimensions of $100$ time integrations and $20$ frequency channels, similar to the toy model used in Section \ref{sec:toymodel}.
-They also have the same level of thermal noise, constructed as a Gaussian random signal for each.
-Identical EoR signals, also constructed as a Gaussian random signal, are in both subsets.
-
-The subsets differ in that only one of them contains a foreground signal (a single complex sinusoid) on top of the noise and EoR, representing a bias that only appears for half the data.
-Mathematically,
+Suppose we have two measurements (for example, from two baselines), $\textbf{x}_{a}$ and $\textbf{x}_{b}$.
+The measurements have dimensions of $200$ time integrations and $20$ frequency channels.
+They each have separate thermal noises constructed as a Gaussian random signal for each, and identical EoR signals.
+
+To mimic the presence of a systematic in part of the measurement, we add a toy sinusoid foreground, similar to the one used in Section \ref{sec:toymodel}, to the first $100$ time integrations of both measurements.
+This represents a foreground signal present in, for example, the first half of the LST range used for analysis, but not the second half.
+Mathematically, if  $\textbf{n}$ is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
 
 \begin{eqnarray}
-\textbf{x}_{1} &=& \textbf{n}_{1} + \textbf{e} + \textbf{fg} \\
-\textbf{x}_{2} &=& \textbf{n}_{2} + \textbf{e}
+\label{eq:bias1}
+\textbf{x}_{a} &=& \textbf{n}_{a} + \textbf{e} + \textbf{fg} \\
+\label{eq:bias2}
+\textbf{x}_{b} &=& \textbf{n}_{b} + \textbf{e} + \textbf{fg},
 \end{eqnarray}
 
-\noindent where $\textbf{n}$ is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal.
+\noindent where the two jackknife samples (for both $a$ and $b$) are:
+
+\begin{eqnarray}
+\textbf{x}_{1} &=& \textbf{n} + \textbf{e} + \textbf{fg} \\
+\textbf{x}_{2} &=& \textbf{n} + \textbf{e} 
+\end{eqnarray}
+
+\noindent For example, $\textbf{x}_{1a}$ represents a jackknife sample (first half of the data) for the first measurement.
+Similarly, $\textbf{x}_{2b}$ represents a jackknife sample (second half of the data) for the second measurement.
 
@@
 For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to avoid signal loss.
-We form $5$ different power spectrum estimates: $\hat{\textbf{p}}$ (full dataset), $\hat{\textbf{p}}_{1}$ (subset $1$), $\hat{\textbf{p}}_{2}$ (subset $2$), $\hat{\textbf{p}}_{noise}$ (noise only), and $\hat{\textbf{p}}_{null}$, which is the result of our differenced dataset $\textbf{x}_{null}$, defined as:
-
-\begin{equation}
-\textbf{x}_{null} = \textbf{x}_{1} - \textbf{x}_{2}. 
-\end{equation}
+
+We form $3$ different power spectrum estimates shown in Figure \ref{fig:toy_bias1}.
+The first is a null test where we subtract $\textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$.
+This is equivalent to splitting up a full dataset along an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
+We cross-multiply measurements $a$ and $b$ to form an un-biased (noise-wise) estimate (blue curve).
+The second estimate, shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{fg}$ in Equations \ref{eq:bias1} and \ref{eq:bias2}).
+Finally, we also show the noise power spectrum (green).
+
+From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of noise.
+This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
-	\caption{Power spectrum estimates for the full toy model dataset $\textbf{x}$ (green), the differenced dataset $\textbf{x}_{1}-\textbf{x}_{2}$, which represents a null jackknife test (black), and noise alone (red).
-Because $\hat{\textbf{p}}_{null}$ is not consistent with noise, it suggests the presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
+	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without the foreground systematic (red), and noise alone (green).
+Because the first null test is not consistent with noise, it suggests the presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
 Null tests of clean measurements should be consistent with thermal noise.}
@@
 
-In Figure \ref{fig:toy_bias1}, we compare $\hat{\textbf{p}}_{null}$, $\hat{\textbf{p}}_{noise}$, and $\hat{\textbf{p}}$.
-Our goal is to determine whether the excess we see in $\hat{\textbf{p}}$ (the power spectrum peak) is due to the EoR signal, something we would not know for a real dataset.
-The null test reveals that there is also an excess in $\hat{\textbf{p}}_{null}$ --- hence, we can rule out EoR.
-Because this is a toy model, we know that the excess is attributable to the foreground signal that did not get subtracted off for the null test.
-
-Additionally, we look at the jackknife results, namely $\hat{\textbf{p}}_{1}$ and $\hat{\textbf{p}}_{2}$.
-The results are shown in Figure \ref{fig:toy_bias2}.
-Again, we see a clear difference between the two, signifying a non-EoR bias that is only present in one subset.
-
-While the null test is useful for ruling out EoR, jackknives are useful in pinpointing which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $\hat{\textbf{p}}_{1}$.
+While the null test is useful for testing noise properties and the uniformity of a dataset, jackknives are useful in pinpointing which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $\textbf{x}_{1}$ (Figure \ref{fig:toy_bias2}).
 If foreground or noise biases exist in a dataset, jackknives can tease them out and provide insight into possible sources.
@@
 There are many other jackknife axes of which we will not go into detail here, including baseline, frequency, and polarization.
-Ultimately, an EoR detection should persist through them all and a clean measurement should pass all null tests.
+Ultimately, an EoR detection should persist through them all and a clean measurement should exhibit noise-like null spectra.
 
@@
 
-\section{Case Study: PAPER-64}
+\section{Demonstration in PAPER-64 Data}
 \label{sec:CaseStudy}

### 2017-11-15 PAPER.tex
made more edits from Danny up until Section 3.3

@@
 We now present a case study of these same three themes using data from the PAPER experiment.
-We use the intuition we've developed through our toy model simulations in order to make educated data analysis choices for PAPER.
-In light of our new understandings, we also highlight major changes since \citet{ali_et_al2015} which have contributed to a revised power spectrum upper limit result.
+We use the intuition developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in \citet{ali_et_al2015} and obtain a revised power spectrum estimate.
 
 As a brief review, PAPER is a dedicated $21$ cm experiment located in the Karoo Desert in South Africa.
-The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements (Figure \ref{fig:paper}) that are arranged in a grid layout.
+The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout.
 For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/paper_dipole.png}
-	\caption{PAPER dipole in South Africa.}
-	\label{fig:paper}
-\end{figure}
-
 The previously best published $21$ cm upper limit result from \citet{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the following sections.
+%The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the following sections.
 
 For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citet{ali_et_al2015} uses an RA range of $0$-$8.6$ hours).
-All power spectrum results are produced using channels $95$-$115$, corresponding to a center redshift of $z=8.4$, identical to the analysis in \citet{ali_et_al2015}.
+All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in \citet{ali_et_al2015}.
 We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} mainly by the fringe-rate filter.
-In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
+\cc{Danny says the next part is wrong...
+} In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
 This was chosen in order to increase the number of independent modes and reduce signal loss.
@@
 
-\subsection{Case Study: Signal Loss}
+\subsection{PAPER-64: Signal Loss}
 \label{sec:Sigloss}
 
-In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from itself.
+In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data itself.
 Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
@@
 
-We simulate an EoR signal by creating a random Gaussian signal (with a default variance of $1$) with the same shape as our data, and we fringe-rate filter this signal twice using the optimal filter.
-The first filter transforms the white noise into a signal that's attached to the sky (i.e.
-what our instrument observes).
-The second filter represents the fringe-rate filtering step in our data analysis pipeline.
-This mock EoR signal is injected on top of fringe-rate filtered PAPER-64 data at a range of amplitude levels that spans the data level.
+To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
+Here we use the same method used in \citet{ali_et_al2015}, where gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
+This signal is then added to the data.
+\footnote{One specific change from \citet{ali_et_al2015} is that we add this simulated signal into the chain before the final fringe-rate filter is applied to the data.
+Previously, the addition was done after that final fringe-rate filter step.
+This change results in an increased estimate of signal loss, likely due to the use of the fringe-rate filter as a simulator.
+Whether the loss would be estimated at the same level if different $21$ cm simulations were used remains an open question.}
 
@@
 
-The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function that maps an output power spectrum distribution into an input distribution.
+The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an output power spectrum distribution into an input distribution.
 By viewing data through this signal loss lens, we are asking the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe our signal loss transfer function for PAPER-64 data and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
@@
 
-We now shift our attention towards computing signal loss for our fringe-rate filtered PAPER-64 dataset.
+We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset.
 While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in \citet{ali_et_al2015} which leads to substantial loss.
@@
 This is unphysical in nature but caused due to the cross-terms dominating in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
-As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to destroyed if weighting the data using itself.
+As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to be destroyed if weighting the data using itself.
 Although we only show figures for one $k$ value, we note that the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
@@
 Prior to signal loss correction, it is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve).
-Post-correction, the power spectrum values blow up to be higher than both the thEoRy and unweighted power spectrum.
+Post-correction, the power spectrum values blow up to be higher than both the theory and unweighted power spectrum.
 
@@
 We also find that the power spectrum upper limit, post signal loss correction, increases with the number of down-weighted modes (black curve).
-As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ samples that we have in fringe-rate filtered PAPER-64 data.
+As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data.
 
 Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting is beneficial compared to not weighting (blue dashed line).
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs when only the strongest $\sim3-4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not significant.
+We see in Figure \ref{fig:sigloss_modeloop} that this occurs when only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not significant.
 
@@
 For example, one could estimate $\hat{\textbf{C}}$ using information from different subsets of baselines.
-For redundant arrays this could mean calculating $\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$m diagonal PAPER baselines (instead of the horizontal E/W ones).
+For redundant arrays this could mean calculating $\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the horizontal E/W ones).
 Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied when forming a power spectrum estimate.
-This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation, unlike PAPER-64.
-
-Another possible way to regularize $\hat{\textbf{C}}$ is to use different ranges of LST.
+This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation because of this very reason.
+
+Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST.
 For example, one could calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to down-weight.
@@
 
-\subsection{Case Study: Error Estimation}
+\subsection{PAPER-64: Error Estimation}
 \label{sec:Error}
@@
 
-Theoretical errors of noise, computed from the instrumental temperature and observational parameters, provide a useful cross-check for bootstrapped errors and is a helpful predictor of the maximum sensitivity that can be achieved by a particular observation and analysis.
-Here we walk through a detailed computation of a theoretical noise estimation as applied to PAPER-64 observations and highlight major changes from \citet{ali_et_al2015}.
-We first give a general formula, and then go into detail about each factor.
-
-The sensitivity prediction for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
+Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations.
+What we found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations.
+The analytic calculation is only an approximation, however the differences were large enough (factors of $10$ in some cases) to warrant a careful investigation.
+The analytic calculation attempts to combine a large number of pieces of information in an approximate way, and when re-considering some of the approximations we have found there to be large effects.
+What follows here is an accounting of the differences which have been discovered.
+
+The sensitivity prediction \cc{need refs} for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
 
@@
 For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
-\item $\Omega_{eff}$: The primary beam angular size.
+\item $\Omega_{eff}$: The effective primary beam area in steradians \footnote{\cc{ref equation}}.
 The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-weighted.
@@
 
-where $\nu$ are frequencies in GHz. We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ at $150$ MHz. This is lower than in \citet{ali_et_al2015} because \cc{why?}.
+where $\nu$ are frequencies in GHz.
+We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ K at $150$ MHz.
+This is lower than in \citet{ali_et_al2015} because of previous failure to correct for using a median statistic.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum estimates after squaring visibility measurements.
-In \citet{ali_et_al2015}, a factor of $2$ was mistakenly used, which would imply that that real parts were obtained prior to squaring.
+In \citet{ali_et_al2015}, a factor of $2$ was mistakenly used.
 \item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation.
@@
 where $t_{int}=43$ seconds, $t_{frf}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is taken over all fringe-rates.
-In other words, we calculate the effective integration time by computing how our beam is altered in fringe-rate space.
 For PAPER-64, this number is $t_{int} = 3857$ s.
@@
 However, because we divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$.
-Additionally, because our $LST$ coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of $N_{days}$ as the RMS of all the daily counts in one dataset (`even', for example).
-For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ days.
+Additionally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of $N_{days}$ as:
+\begin{equation}
+ \frac{1}{N_{days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
+ \end{equation}
+\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ days.
 \item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate.
 In \citet{ali_et_al2015}, this number was the total number of $30$ m East/West baselines used in the analysis.
-However, using the total number of baselines neglects the fact that we divide baselines into $5$ groups before cross-multiplying data.
-Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where $N_{gps} = 5$.
-This expression arises because $N_{bls}$ must be scaled by the total number of cross-multiplications going into the power spectrum estimate.
-For $5$ groups, there are $25$ total cross-products, minus $5$ cross-products since we avoid multiplying the same group with itself.
-For our PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$.
+However, using the total number of baselines neglects the fact that baselines are averaged into groups before cross-multiplying data.
+Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where, for the \citet{ali_et_al2015} analysis, $N_{gps} = 5$.
+Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as square root of the number of cross multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
+For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$.
 \item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
@@
 
-Equation \eqref{eq:sense} represents the most sensitive estimate for $\hat{\textbf{p}}(k)$ given our observing parameters.
 An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging together positive and negative $k$'s.
@@
 To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation.
-We create Gaussian random noise and use $T_{sys}$ in order to best represent the thermal noise level of PAPER-64 data.
+We create Gaussian random noise assuming a constant $T_{sys}$ (neglecting sky variation) but accounting for the true $N_{days}$ as determined by LST sampling counts for each time and frequency in the LST-binned data.
 We convert $T_{sys}$ into a variance statistic using:
@@
 \noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
-This rms temperature sets the variance of the Gaussian random noise.
-
-We fringe-rate filter the noise in the same way as PAPER-64 data, using an optimal fringe-rate filter.
+This RMS temperature sets the variance of the Gaussian random noise.
+
 Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \eqref{eq:sense}.
@@
 The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
-In \citet{ali_et_al2015}, a second round of bootstrapping occurs over the baseline bootstrap and time axes simultaneously.
-Random values are sampled with replacement along both axes, drawing as many values as there are number of bootstraps and times.
-Final power spectrum limits are then computed by taking the mean and standard deviation over this second bootstrap axis (which is typically large, on the order of $N_{boot} \sim 400$).
+In \citet{ali_et_al2015}, a second round of bootstrapping occurred over the baseline bootstrap and time axes simultaneously.
+Random values were sampled with replacement along both axes, drawing as many values as there are number of time integrations.
+Final power spectrum limits were then computed by taking the mean and standard deviation over this second bootstrap axis (which is typically large, on the order of $N_{boot} \sim 400$).
+We emphasize that in this previous version, the number of elements sampled per bootstrap (number of times $\sim$ $700$) greatly exceeds the number of independent LST samples, under-estimating errors.
 
@@
 A random draw of $700$ samples from this dataset therefore has many repeated samples, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
-Another way of describing this underestimation is that there are fewer ways to randomly sample data with $8$ independent modes versus $700$, so bootstrapping a fringe-rate filtered dataset yields a narrower distribution of values from which we calculate its standard deviation.
-
-To prevent error underestimation, we simply take the average along the time axis in our revised pipeline rather than bootstrapping.
-Hence, our final power spectrum errors are calculated from the standard deviation over the baseline bootstrapping axis only, which is still a valid axis since each baseline makes an independent measurement of the sky.
-
-The second aspect of bootstrapping discussed in Section \ref{sec:ErrorOverview} is the overestimation of errors which arises from repeated values in a randomly sampled bootstrap.
-In order to maximize sensitivity, we have revised the method by which we sample baselines when bootstrapping to ensure mostly independent samples.
-
-First, we speed things up in our pipeline by separating our total number of baselines into $5$ groups (yielding $10$ baselines per group), where there are no repeated baselines within or between groups.
-In \citet{ali_et_al2015}, each group is then sampled with replacement to create a new group of the same size, which can have repeated baselines inside it.
-In doing so, we are sacrificing some of our sensitivity since there ends up being $3$-$4$ repeated baselines per group (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim55\%$ for $10$ total independent samples) .
-In order to maximize our sensitivity but still apply random sampling for use in error estimation, we instead form new groups using all independent baselines except the very last one, which we fill randomly.
-We use this method for every bootstrap, creating new groups and sampling the last spot randomly each time.
-
-Power spectrum estimates showcasing these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
+
+Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second step entirely and now simply bootstrap over baselines with the ``single replacement" strategy described in Section \ref{sec:ErrorOverview}.
+
+The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each group.
+In \citet{ali_et_al2015}, baselines were chosen for groups randomly with replacement.
+In doing so, $\sim$$3$-$4$ baselines per group were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total independent samples) which sacrificed some sensitivity.
+
+Power spectrum estimates with these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
 The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss.
-We show upper limits ($2\sigma$ error bars) for three different results.
-Our revised error estimation method is in black, where we only bootstrap along the baseline axis and we maximize sensitivity by random sampling only the last baseline in each group.
-The blue curve uses a similar method except all baselines are randomly sampled, leading to a higher power spectrum estimate because some baselines are repeated per group.
-In red, we bootstrap along both the baseline and time axes, drawing as many samples as there are in the data.
-We under-estimate errors in doing so because we are drawing many more samples than independent ones.
+As shown in the figure, when the baseline average includes many repeated samples the error is over-estimated, while when only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ modes converges to the theoretical noise level.
+However, if more elements are drawn for each bootstrap than the number of independent samples (by drawing many times along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level.
 
@@
 
-\subsection{Case Study: Bias}
+\subsection{PAPER-64: Bias}
 \label{sec:Bias}
@@
 
-Although current $21$cm published power spectrum upper limits lie a $\sim$couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, expect to continue to push towards EoR sensitivities.
+Although current $21$ cm published power spectrum upper limits lie a $\sim$couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, expect to continue to push towards EoR sensitivities.
 As the field progresses towards a coveted detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknive and null tests.
 
-In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$cm power spectrum techniques on signal loss, error estimation, and bias, which can be summarized as follows:
+In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$ cm power spectrum techniques on signal loss, error estimation, and bias, which can be summarized as follows:
 
@@
 \item Substantial signal loss can result when weighting data using empirically estimated covariances.
-Loss of the $21$cm signal is especially significant if more eigenmodes are down-weighted than exist in the data (having an under-constrained covariance matrix).
+Loss of the $21$ cm signal is especially significant if more eigenmodes are down-weighted than exist in the data (having an under-constrained covariance matrix).
 Hence, there exists a trade-off between sensitivity driven time-averaging techniques such as fringe-rate filtering and signal loss.
@@
 
-The $21$cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand instruments.
+The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand instruments.
 On the power spectrum analysis side, we recognize that there is still much work to do.

### 2017-11-15 PAPER.tex
-Finished Danny's smaller edits throughout paper
made some of Aaron's edits for signal loss methods/practice sections

@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
-Here we use the same method used in \citet{ali_et_al2015}, where gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
+Here we use the same method used in \citet{ali_et_al2015}, where mock gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
 This signal is then added to the data.
@@
 
-We are interested in quantifying how much $\textbf{e}$ is lost after weighting $\textbf{r}$ and applying OQE formalism.
-We investigate this by comparing two quantities we define as the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$.
+We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power spectrum according to OQE formalism.
+We investigate this by comparing two quantities we define as the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
+
+\begin{equation}
+\label{eq:Pin}
+P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+\end{equation}
+
+\noindent and
+
+\begin{eqnarray}
+\label{eq:sigloss}
+P_{out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
+&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
+\end{eqnarray}
+
 $P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal.
@@
 Comparing the two quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
-Ignoring normalization factors, these two quantities can be written as:
-
-\begin{equation}
-\label{eq:Pin}
-P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
-\end{equation}
-
-\noindent and
-
-\begin{eqnarray}
-\label{eq:sigloss}
-P_{out,\alpha} \equiv \hat{\textbf{p}}_{e,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
 
@@
 One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$.
-Expanding Equation \eqref{eq:sigloss}, we see that $P_{out}$ is comprised of multiple terms:
+In short, this naive expression fails to include correlations between the EoR signal and data, which emerges as statistical noise that is added to the estimate, decreasing the value of $P_{out}$.
+Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
 
@@
 
-Taking the case of very large $\textbf{e}$ so that any terms involving only $\textbf{x}$ are small, yields:
+We see that $P_{out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only $\textbf{x}$ are small, yields:
 
@@
 We see that our naive expression for $P_{out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two additional terms.
-An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are physically unrelated.
+An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are statistically unrelated.
 In \citet{ali_et_al2015}, this assumption is used, and the first term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
@@
 However, deeper investigations of these terms reveal that they contain non-negligible power.
-In fact, foreground modes and signal modes are anti-correlated on average, as derived and explained in \citet{switzer_et_al2015}.
-The spurious correlation of the two means that we cannot compute signal loss using a signal-only simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss.
+In fact, foreground modes and signal modes are anti-correlated on average.
+This negative cross-term power arises from inverting a covariance matrix with a strong diagonal and small off-diagonal terms, as we expect to be the form for $\textbf{C}_{r}$.
+Through the inversion process, the off-diagonal terms become negative and ...
+This effect is derived mathematically and explained more in depth in \citet{switzer_et_al2015}.
+
+The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss.
 Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 
-The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an output power spectrum distribution into an input distribution.
-By viewing data through this signal loss lens, we are asking the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe our signal loss transfer function for PAPER-64 data and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
+The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an input power spectrum distribution into an output distribution.
+By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss transfer function and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
 
@@
 We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset.
-While our methodology outlined below is robust to any weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in \citet{ali_et_al2015} which leads to substantial loss.
+While our methodology outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in \citet{ali_et_al2015} which leads to substantial loss.
 With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
@@
 Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with an unweighted case ($\textbf{R} = \textbf{I}$, right plot).
-The figures depict a smoothed-out distribution (via kernel density estimators) of our input and output power spectra.
-To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (where one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
-For each injection, we perform $20$ bootstraps (over baselines, as explained in Section \ref{sec:Boot}), resulting in a total of $800$ data points on our $P_{in}$ vs.
+The figures depict a kernel density estimation of our input to output power spectra.
+To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
+For each injection, we perform $20$ bootstraps over baselines, as explained in Section \ref{sec:Boot}, resulting in a total of $800$ data points on our $P_{in}$ vs.
 $P_{out}$ grid.
-It is noted that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
-
-The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, or a perfect mapping from $P_{out}$ to $P_{in}$ (which we expect to occur for the unweighted case).
+We have verified that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
+
+The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the unweighted case ($\textbf{R} = \textbf{I}$).
 The solid grey horizontal lines mark the peak of the data distribution $\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted cases.
@@
 	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Smoothed out distributions (via kernel density estimators) are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
+Kernel density estimations of the transfer functions are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
 The solid black diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data distribution.
-From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss whereas the unweighted case does not exhibit loss.}
+From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does not exhibit loss.}
 	\label{fig:sigloss_transfercurve}
@@
 
-The first component is merely the fact that the values of the cross-terms in Equation \eqref{eq:pout_expand} change for different EoR signals, $\textbf{e}$.
-Since we draw different random $\textbf{e}$'s for every bootstrap, there is a (small) range of $P_{out}$ values that could result for the same $P_{in}$.
-This randomness is what causes the spread seen in the unweighted case (right plot of Figure \ref{fig:sigloss_transfercurve}), as well as most of the spread in the weighted case (left plot).
-
-The second component of scatter is less intuitive and only applies (at a low level) to the weighted case.
+The first component arises from the fact that the values of the cross-terms in Equation \eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$.
+Since we draw different random $\textbf{e}$'s for every bootstrap, there is a range of $P_{out}$ values that results from the same $P_{in}$.
+This randomness causes the spread seen in the unweighted case (right plot of Figure \ref{fig:sigloss_transfercurve}), as well as most of the spread in the weighted case (left plot).
+
+The second component of scatter is less intuitive and only applies (at a low level) to the weighted case, but represents intrinsic scatter in signal loss.
 The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$.
-For example, if we are extremely unlucky, $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
+For example, if we are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
 If weighting using empirically-derived covariances, this entire EoR signal would be destroyed.
-On the contrary, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-This range of how `unlucky' we can get is not that dramatic in real life, but it is important to correct for the fact that a particular $P_{out}$ value could in principle stem from a range of $P_{in}$ values.
+On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of $P_{in}$ values.
 
@@
 Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), we fit a polynomial to each, representing mean signal loss functions.
-We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for every $P_{in}$ value.
+We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each $P_{in}$ value.
 In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
@@
 Equipped with our new signal loss curves (a one-to-one mapping function for the unweighted case, and a somewhat smeared out function for the weighted case), we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ columns, treating positive and negative halves of the data distribution separately.
-We note that for PAPER-64, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power), and sometimes centered around 0, representing noise-like measurements.
+We note that for PAPER-64, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power), and sometimes centered around zero, representing measurements that are consistent with zero.
 
@@
 
-To summarize this section, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
+To conclude this section, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
 The blue dashed line represents the unweighted power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case).
@@
 Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of independent samples in PAPER-64.
-PAPER-64 has $\sim 8$ independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
+PAPER-64 has eight independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
 Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first $8$.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/data_errors.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
 	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping methods.
@@
 \subsubsection{Mitigating Bias}
+
+\cc{Should we even include this next section? I included it to follow-up on Section 2.3.1, but it's not saying anything new...}
 
@@
 PAPER is supported by grants from the National Science Foundation (awards 0804508, 1129258, and 1125558).
-ARP, JCP, and DCJ would also like to acknowledge NSF support (awards 1352519, 1302774, and 1401708, respectively).
-JEA would like to acknowledge a generous grant from the Mount Cuba Astronomical Association for computing resources.
+ARP, JCP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1302774, 1401708, and 1455151, respectively).
 We also graciously thank SKA-SA for site infrastructure and observing support.

### 2017-11-15 PAPER.tex
-Made Aaron's edits to Section 3.1.1 and 3.1.2

@@
 We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} mainly by the fringe-rate filter.
-\cc{Danny says the next part is wrong...
+\cc{Danny says the next part is wrong, but that's what's in Zaki's paper...
 } In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
@@
 We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power spectrum according to OQE formalism.
-We investigate this by comparing two quantities we define as the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
+We investigate this by comparing two quantities we call the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
 
@@
 However, deeper investigations of these terms reveal that they contain non-negligible power.
-In fact, foreground modes and signal modes are anti-correlated on average.
-This negative cross-term power arises from inverting a covariance matrix with a strong diagonal and small off-diagonal terms, as we expect to be the form for $\textbf{C}_{r}$.
-Through the inversion process, the off-diagonal terms become negative and ...
-This effect is derived mathematically and explained more in depth in \citet{switzer_et_al2015}.
+In fact, foreground modes and signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $\textbf{C}_{r}$.
+Mathematically,
+
+\begin{eqnarray}
+\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle \\
+&=& \langle \textbf{xx}^{\dagger} \rangle + \langle \textbf{xe}^{\dagger} \rangle + \langle \textbf{ex}^{\dagger} \rangle + \langle \textbf{ee}^{\dagger} \rangle,
+\end{eqnarray}
+
+\noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices.
+The middle two terms, however, have a larger amount of power in their off-diagonal terms relative to the diagonal elements, since $\textbf{e}$ and $\textbf{x}$ are statistically unrelated.
+Upon inversion, these off-diagonal terms become negative, driving the cross-terms in Equation \ref{eq:pout_expand} to have negative power.
+This effect is explained in more depth in \citet{switzer_et_al2015}.
 
@@
 
-Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with an unweighted case ($\textbf{R} = \textbf{I}$, right plot).
-The figures depict a kernel density estimation of our input to output power spectra.
-To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments in log-space and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
+Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with the unweighted case ($\textbf{R} = \textbf{I}$, right plot).
+The figures depict a kernel density estimation of our input to output power spectrum transfer function.
+To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments on a lin-log grid and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
 For each injection, we perform $20$ bootstraps over baselines, as explained in Section \ref{sec:Boot}, resulting in a total of $800$ data points on our $P_{in}$ vs.
@@
 The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the unweighted case ($\textbf{R} = \textbf{I}$).
-The solid grey horizontal lines mark the peak of the data distribution $\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted cases.
+Therefore, it is worth thinking about the spread, or scatter, around this black line that we see in the right plot (the colored `heat-map').
+One might imagine that there should be one true $P_{out}$ value for every $P_{in}$, implying one well-determined signal loss factor for every data value.
+Focusing on the unweighted case alone, the scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$.
+Since we draw different random $\textbf{e}$'s for every bootstrap, there is a range of $P_{out}$ values that results from the same $P_{in}$.
+This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of the spread in the weighted case (left plot).
+
+There is a second component of scatter that is less intuitive, only applies (at a low level) to the weighted case, and represents intrinsic scatter in signal loss.
+The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$.
+For example, if we are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
+An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
+On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of $P_{in}$ values.
+We correct for this as explained in the next section.
+
+Finally, the solid grey horizontal lines in Figure \ref{fig:sigloss_transfercurve} mark the peak of the data distribution $\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted cases.
 One can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$ using the transfer curve for the inverse covariance weighted case, implying a signal loss factor of $\sim1000$.
@@
 	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Kernel density estimations of the transfer functions are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
+Kernel density estimations of the power spectrum transfer functions are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
 The solid black diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data distribution.
@@
 One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have signal gain ($P_{out} > P_{in}$).
-This is unphysical in nature but caused due to the cross-terms dominating in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
+This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
 As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to be destroyed if weighting the data using itself.
@@
 
-Finally, it is worth thinking about the spread, or scatter, in our transfer curves in more detail.
-One might imagine that there should be one true $P_{out}$ value for every $P_{in}$, implying one well-determined signal loss factor for every data value.
-In practice we have found that this is not the case, as evidenced by the colored `heat-map' in Figure \ref{fig:sigloss_transfercurve}.
-The cause of this scatter can be thought of as comprised of two components.
-
-The first component arises from the fact that the values of the cross-terms in Equation \eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$.
-Since we draw different random $\textbf{e}$'s for every bootstrap, there is a range of $P_{out}$ values that results from the same $P_{in}$.
-This randomness causes the spread seen in the unweighted case (right plot of Figure \ref{fig:sigloss_transfercurve}), as well as most of the spread in the weighted case (left plot).
-
-The second component of scatter is less intuitive and only applies (at a low level) to the weighted case, but represents intrinsic scatter in signal loss.
-The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$.
-For example, if we are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
-If weighting using empirically-derived covariances, this entire EoR signal would be destroyed.
-On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of $P_{in}$ values.
-
 We now explain how we use the transfer curves to map our data (a distribution along $P_{out}$) to a signal-loss corrected distribution (along $P_{in}$) that takes into account the range of signal loss that can be associated for a particular $P_{out}$ value.
 
-Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), we fit a polynomial to each, representing mean signal loss functions.
-We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each $P_{in}$ value.
+\cc{can someone help me supplement the next 3 paragraphs with math?}
+
+Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), defined as:
+
+\begin{equation}
+\cc{fill in},
+\end{equation}
+
+\noindent we fit a polynomial to each, representing mean signal loss functions.
+We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each $P_{in}$ value:
+
+\begin{equation}
+\cc{fill in}.
+\end{equation}
+
 In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
 
-Equipped with our new signal loss curves (a one-to-one mapping function for the unweighted case, and a somewhat smeared out function for the weighted case), we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ columns, treating positive and negative halves of the data distribution separately.
+Equipped with our new signal loss curves, we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ columns, treating positive and negative halves of the data distribution separately:
+
+\begin{equation}
+\cc{fill in}.
+\end{equation}
+
 We note that for PAPER-64, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power), and sometimes centered around zero, representing measurements that are consistent with zero.
 
-Finally, we sum up all rows of $P_{out}$ where each row is a $P_{in}$ probability distribution allowed by our measurements.
+Finally, we sum up all rows of $P_{out}$ where each row is a $P_{in}$ probability distribution allowed by our measurements:
+
+\begin{equation}
+\cc{fill in}.
+\end{equation}
+
 This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We show these final distributions in Figure \ref{fig:sigloss_datadist_inversecovariance} for every $k$.
 We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
 
-\begin{figure*}
-	\centering
-	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
-	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on PAPER-64 data after signal loss correction.
+%\begin{figure*}
+%	\centering
+%	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
+%	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on %PAPER-64 data after signal loss correction.
 Power spectrum points are computed from the peak of the distributions.
 Errors are computed using $95\%$ confidence intervals.}
-	\label{fig:sigloss_datadist_inversecovariance}
-\end{figure*}
+%	\label{fig:sigloss_datadist_inversecovariance}
+%\end{figure*}
 
@@
 Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of independent samples in PAPER-64.
-PAPER-64 has eight independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
-Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first $8$.
+PAPER-64 only has $\sim$$8$ independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
+Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first eight.
 Hence, there is a substantial down-weighting of many random modes, a large loss that the signal loss transfer function captures and corrects for.
-\cc{elaborate?} In the next section, we investigate alternate weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
+We elaborate on this point in the next section, as well as investigate alternate weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
 
@@
 We also find that the power spectrum upper limit, post signal loss correction, increases with the number of down-weighted modes (black curve).
-As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data.
+As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data \cc{elaborate?}.
 
@@
 The author would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
-PAPER is supported by grants from the National Science Foundation (awards 0804508, 1129258, and 1125558).
+PAPER and HERA are supported by grants from the National Science Foundation (awards 0804508, 1129258, 1125558, 1440343, and 1636646).
 ARP, JCP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1302774, 1401708, and 1455151, respectively).

### 2017-11-16 PAPER.tex
revised conclusion based on aaron's edits

@@
 \subsubsection{Jackknife Tests}
+\label{sec:JackknifeOverview}
 
@@
 Also plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance weighted case (red), and added-identity case (cyan).
-All three regularizations shown (black, red, cyan) perform similarly at their best.}
+All three regularizations shown (black, red, cyan) perform similarly at their best.
+Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted as solid green.}
 	\label{fig:sigloss_modeloop}
@@
 Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of noise (solid green).
-From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$ (though we only use one baseline type in our analysis as opposed to $3$).
+From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$).
+\cc{ref kolopanis limit instead later}
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Highest sensitivity power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$.
+	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$.
 Black and grey points correspond to positive and negative power spectrum values, respectively, with $2\sigma$ error bars also plotted.
@@
 This power spectrum result differs from \citet{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
-Additionally, an optimal fringe-rate filter was used instead of a degraded one, resulting in an increase in sensitivity but also an increase in signal loss.
 Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.
-We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$.}
+We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
 	\label{fig:ps1_data}
@@
 
-Although current $21$ cm published power spectrum upper limits lie a $\sim$couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, expect to continue to push towards EoR sensitivities.
-As the field progresses towards a coveted detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknive and null tests.
+Although current $21$ cm published power spectrum upper limits lie a couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities.
+As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknive and null tests.
 
@@
 \begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances.
+\item Substantial signal loss can result when weighting data using empirically estimated covariances (Section \ref{sec:SiglossOverview}).
 Loss of the $21$ cm signal is especially significant if more eigenmodes are down-weighted than exist in the data (having an under-constrained covariance matrix).
 Hence, there exists a trade-off between sensitivity driven time-averaging techniques such as fringe-rate filtering and signal loss.
-\item Signal injection and recovery simulations can be used to quantify signal loss.
-However, a signal-only simulation can underestimate loss by failing to account for spurious correlations between the data and signal.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are correlated.
+\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}).
+However, a signal-only simulation (i.e.
+comparing an unweighted vs.
+weighted power spectrum of EoR) can underestimate loss by failing to account for spurious correlations between the data and signal.
+\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated (Section \ref{sec:ErrorOverview}).
 If the number of independent samples in a dataset is well-determined, bootstrapping is a simple and accurate way of estimating errors.
-\item An EoR detection must pass all null tests.
-Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in a true EoR detection, and can also be used to tease out systematics.
+\item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}).
+Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection, and can also be used to tease out systematics.
 \end{itemize}
@@
 As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
-For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim50$ in mK$^{2}$.
+For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.
 The reasons for a previously underestimated limit and ways in which our new analysis differs can be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citet{ali_et_al2015}, was underestimated by a factor of $\sim$$1000$.
-Because PAPER-64 is limited by its number of samples, we use a regularized covariance weighting in our revised analysis to minimize loss, thereby increasing the original PAPER-64 limit in mK$^{2}$ by a factor of $\sim$$50$ instead of $1000$.
-Underestimated signal loss represents the bulk of our revision.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data with a reduced number of independent samples from fringe-rate filtering.
-They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra.
-Hence, the net change for our error estimation is negligible, though the intuition behind the previous estimation was incorrect.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding an increase in predicted sensitivity level by a factor of $\sim$$7$.
+\item Signal loss, previously found to be $<2\%$ in \citet{ali_et_al2015}, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting.
+For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}).
+However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ in mK higher than previous limits.
+Underestimated signal loss therefore represents the bulk of our revision.
+\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering.
+They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra (Section \ref{sec:Boot}).
+Hence, the net change for our error estimation is negligible, though the rationale behind the previous estimation was incorrect.
+\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$7$ (Section \ref{sec:PSSense}).
 We have verified our revised prediction extensively using pure noise simulations.
+We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that the theoretical prediction for noise in \citet{ali_et_al2015} was too high for its data points.
 \end{itemize}
@@
 The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand instruments.
-On the power spectrum analysis side, we recognize that there is still much work to do.
-Even with robust signal loss simulations and precise error calculations, we are currently limited by data volume and foreground suppression strategies.
-However, the future promises to bring higher sensitivity $21$ cm measurements, better foreground and instrumental models, more effective and less lossy weighting techniques --- and with all that, an improved understanding of reionization and our early Universe.
+On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and comprehensive jackknife tests will play critical roles in accurate $21$ cm results.
+Looking ahead, the future promises to bring higher sensitivity measurements, better foreground and instrumental models, more effective and less lossy weighting techniques --- and with all that, an improved understanding of reionization and our early Universe.
 
@@
 \section{Acknowledgements}
-The author would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
-PAPER and HERA are supported by grants from the National Science Foundation (awards 0804508, 1129258, 1125558, 1440343, and 1636646).
+CC would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
+PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646).
 ARP, JCP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1302774, 1401708, and 1455151, respectively).

### 2017-11-20 PAPER.tex
-Read-through for typos/clarifcations (intro and sigloss toy model)

@@
 Adrian Liu\altaffilmark{1,5}, 
-James E. Aguirre\altaffilmark{5},
+James E. Aguirre\altaffilmark{4},
 Zaki S. Ali\altaffilmark{1}, 
@@
 David H. E. MacMahon\altaffilmark{2},
-David F. Moore\altaffilmark{5},
-Chuneeta D. Nunhokee\altaffilmark{14},
-Jonathan C. Pober\altaffilmark{15}, 
+David F. Moore\altaffilmark{4},
+Chuneeta D. Nunhokee\altaffilmark{10},
+Jonathan C. Pober\altaffilmark{14}, 
 William P. Walbrugh\altaffilmark{9},
@@
 \altaffiltext{9}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{10}{Dept. of Physics and Electronics, Rhodes University}
+\altaffiltext{10}{Dept. of Physics and Electronics, Rhodes University, South Africa}
 \altaffiltext{11}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
@@
 \altaffiltext{13}{Cavendish Lab., Cambridge UK}
-\altaffiltext{14}{Dept. of Physics and Electronics, Rhodes University, Grahamstown South Africa}
-\altaffiltext{15}{Dept. of Physics, Brown University, Providence RI}
+\altaffiltext{14}{Dept. of Physics, Brown University, Providence RI}
 
@@
 In this paper, we focus on three major themes --- signal loss, power spectrum error bar estimation, and bias in measurements.
-We describe techniques that affect these themes using both a toy model and data taken by the 64-element configuration of the Donald C.
+We describe techniques that affect these themes using both toy models and data taken by the 64-element configuration of the Donald C.
 Backer Precision Array for Probing the Epoch of Reionization (PAPER).
 In particular, we highlight how detailed investigations of these themes have led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64.
-This revised result mostly stems from an updated signal loss calculation for loss associated with empirically estimated covariances, and we consider this limit to supersede previously published PAPER-64 and PAPER-32 results.
+This revised result mostly stems from an updated signal loss calculation for loss associated with empirically estimated covariances and supersedes results from previously published PAPER analyses.
 \end{abstract}
@@
 In Section \ref{sec:Themes} we introduce the three themes of our focus, using a toy model to develop intuition for each one.
-In Section \ref{sec:CaseStudy} we present a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015} which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}).
+In Section \ref{sec:CaseStudy} we present a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}).
 We conclude in Section \ref{sec:Con}.
@@
 \begin{itemize}
-\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}), and we explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}).
 Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
 However, it can also affect the presence of foregrounds and systematics.
+We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
 \item \textbf{Weighting:} A dataset can be weighted to emphasize certain spectral features and minimize others.
@@
 It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during spectral calibration, applying a delay-domain filter, or by weighting data by itself.
-Here we focus on signal loss associated with applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously underestimated in the PAPER-64 analysis.
+Here we focus on signal loss associated with applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously underestimated in the P64 analysis
 
@@
 
-We begin with our data vector, $\textbf{x}$ which contains our measured visibilities in Jy.
+We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in Jy.
 It has length ($N_{t}, N_{f}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
+\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
 \end{equation}
@@
 \noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum.
-The data analyst has a choice for $\textbf{M}$.
-For simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}
-
-In the next sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
+The data analyst has a choice for $\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}
+
+In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
 Our ultimate goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
@@
 We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid with a fixed frequency and a smoothly varying offset in time, a simplistic but realistic representation of a single bright source.
-We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal \cc{need to motivate why, since real EoR does have correlations}.
-Our combined data vector is $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
+We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
+A more realistic EoR signal would have a sloped power spectrum in $\hat{\textbf{p}}$(k) (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
+However, in this paper we treat all $k$'s separately, so a simplistic white noise approximation can be used.
+Our combined data vector is then $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
 The three data vectors are shown in Figure \ref{fig:toy_sigloss1}.
@@
 	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset contains a sinusoid foreground that varies in time and frequency and a random Gaussian signal as a mock EoR signal. Real parts are shown here.}
+	\caption{Our toy model dataset contains a sinusoid foreground that varies smoothly in time and a random Gaussian signal as a mock EoR signal. Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 	\centering
-	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
 	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only (middle), and FG + EoR (right). Real parts are shown here.}
@@
 The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-This is usually not the case for a covariance matrix, in which a sloped eigenspectrum means that modes are given different weights.
-When weighting data by an inverse covariance matrix, the modes with the highest eigenvalues are down-weighted the most.
+This is usually not the case for a covariance matrix, for which a sloped eigenspectrum means that modes are given different weights.
+The modes with the highest eigenvalues are down-weighted the most.
 
@@
 The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices yield eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.}
+These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.}
 	\label{fig:toy_sigloss2}
@@
 In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are more trustworthy than the weakest modes, since that's where we expect bright foregrounds --- the most prominent shapes --- to be.
-If bright foregrounds dominate, these highest eigenvalue modes therefore exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
-This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
+If bright foregrounds dominate, these highest eigenvalue modes would exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
+This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
 
@@
 	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We use inverse covariance weighting where $\textbf{C}$ is derived from the data.
+We use inverse covariance weighting where $\textbf{C}$ is computed from the data.
 There is a larger amount of signal loss than for the non-averaged data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
@@
 
-As a first test, we know that our simulated EoR should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
+As a first test, we know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
 If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\hat{\textbf{C}}_{FG}$ (defined as $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
@@
 This is evident when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}.
-We don't see perfect EoR recovery though, as the green and red curves differ at one $k$ value in Figure \ref{fig:toy_sigloss8}.
+We don't see perfect EoR recovery though, as the green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}.
 This deviation is a consequence of the difference between the true and modeled covariance matrices.
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
-	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $\textbf{C}$ (magenta).
-}
+	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $\hat{\textbf{C}}$ (magenta).
+All eigenspectra (except the green) are relatively flat and don't exhibit signal loss.}
 	\label{fig:toy_sigloss14}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \gamma\textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I} for the purpose of this toy model$).
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \gamma\textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I}$ for the purpose of this toy model).
 By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
@@
 The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is proportional to $k_{\parallel}$).
-Properties of the wedge can be used to isolate and remove foregrounds, as done by \citet{ali_et_al2015}, \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
+Properties of the wedge can be used to isolate and remove foregrounds, as done by P64, \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
 
@@
 In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
-The window function used in \citet{ali_et_al2015} is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
+The window function used in P64 is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
 Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
@@
 We now present a case study of these same three themes using data from the PAPER experiment.
-We use the intuition developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in \citet{ali_et_al2015} and obtain a revised power spectrum estimate.
+We use the intuition developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in P64 and obtain a revised power spectrum estimate.
 
@@
 For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines.
-For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and \citet{ali_et_al2015}.
-
-The previously best published $21$ cm upper limit result from \citet{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
+For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and P64.
+
+The previously best published $21$ cm upper limit result from P64 uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
 
@@
 
-For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citet{ali_et_al2015} uses an RA range of $0$-$8.6$ hours).
-All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in \citet{ali_et_al2015}.
-We note that the PAPER-64 dataset that we use in this case study differs from that in \citet{ali_et_al2015} mainly by the fringe-rate filter.
+For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses an RA range of $0$-$8.6$ hours).
+All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in P64.
+We note that the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter.
 \cc{Danny says the next part is wrong, but that's what's in Zaki's paper...
-} In \citet{ali_et_al2015}, the applied filter was degraded by widening it in fringe-rate space.
+} In P64, the applied filter was degraded by widening it in fringe-rate space.
 This was chosen in order to increase the number of independent modes and reduce signal loss.
@@
 Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
-In particular, we highlight major differences from the signal loss computation used in \citet{ali_et_al2015}, which previously underestimated losses.
+In particular, we highlight major differences from the signal loss computation used in P64, which previously underestimated losses.
 
@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
-Here we use the same method used in \citet{ali_et_al2015}, where mock gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
+Here we use the same method used in P64, where mock gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
 This signal is then added to the data.
-\footnote{One specific change from \citet{ali_et_al2015} is that we add this simulated signal into the chain before the final fringe-rate filter is applied to the data.
+\footnote{One specific change from P64 is that we add this simulated signal into the chain before the final fringe-rate filter is applied to the data.
 Previously, the addition was done after that final fringe-rate filter step.
@@
 An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are statistically unrelated.
-In \citet{ali_et_al2015}, this assumption is used, and the first term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
+In P64, this assumption is used, and the first term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
 
@@
 We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset.
-While our methodology outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in \citet{ali_et_al2015} which leads to substantial loss.
+While our methodology outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss.
 With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
@@
 Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of noise (solid green).
-From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$).
+From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$).
 \cc{ref kolopanis limit instead later}
@@
 The solid green line is the theoretical noise level prediction based on observational parameters.
-This power spectrum result differs from \citet{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
+This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
 Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.
-We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
+We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
 	\label{fig:ps1_data}
@@
 
-In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the \citet{ali_et_al2015} analysis of PAPER-64.
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the P64 analysis of PAPER-64.
 While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
@@
 We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ K at $150$ MHz.
-This is lower than in \citet{ali_et_al2015} because of previous failure to correct for using a median statistic.
+This is lower than in P64 because of previous failure to correct for using a median statistic.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum estimates after squaring visibility measurements.
-In \citet{ali_et_al2015}, a factor of $2$ was mistakenly used.
+In P64, a factor of $2$ was mistakenly used.
 \item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation.
@@
 \item $N_{days}$: The total number of days of data analyzed.
-In \citet{ali_et_al2015}, this number was set to $135$.
+In P64, this number was set to $135$.
 However, because we divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$.
@@
 \item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate.
-In \citet{ali_et_al2015}, this number was the total number of $30$ m East/West baselines used in the analysis.
+In P64, this number was the total number of $30$ m East/West baselines used in the analysis.
 However, using the total number of baselines neglects the fact that baselines are averaged into groups before cross-multiplying data.
-Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where, for the \citet{ali_et_al2015} analysis, $N_{gps} = 5$.
+Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where, for the P64 analysis, $N_{gps} = 5$.
 Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as square root of the number of cross multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
@@
 
-Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of \citet{ali_et_al2015} in Figure \ref{fig:sense_check}.
+Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of P64 in Figure \ref{fig:sense_check}.
 Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$.
@@
 	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously published sensitivity limits (grey).
-Both sensitivity analyses plotted assume only one baseline type (an additional factor of $\sqrt{3}$ for 3 baseline types is needed to match \citet{ali_et_al2015} exactly).
+Both sensitivity analyses plotted assume only one baseline type (an additional factor of $\sqrt{3}$ for 3 baseline types is needed to match P64 exactly).
 Major factors that contribute to the discrepancy are $\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our sensitivity (higher noise floor) by a factor of $\sim7$.}
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results.
-In this section, we highlight two major changes in the way we estimate errors since \citet{ali_et_al2015}, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
+In this section, we highlight two major changes in the way we estimate errors since P64, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
 
@@
 The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
-In \citet{ali_et_al2015}, a second round of bootstrapping occurred over the baseline bootstrap and time axes simultaneously.
+In P64, a second round of bootstrapping occurred over the baseline bootstrap and time axes simultaneously.
 Random values were sampled with replacement along both axes, drawing as many values as there are number of time integrations.
@@
 The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each group.
-In \citet{ali_et_al2015}, baselines were chosen for groups randomly with replacement.
+In P64, baselines were chosen for groups randomly with replacement.
 In doing so, $\sim$$3$-$4$ baselines per group were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total independent samples) which sacrificed some sensitivity.
@@
 Figure \ref{fig:frp} shows that the filter response is zero for such static signals.
-The effect of filtering out zero fringe-rates on power spectrum results is shown in \citet{ali_et_al2015}.
+The effect of filtering out zero fringe-rates on power spectrum results is shown in P64.
 Most notably, power spectrum detections exist at all $k$'s without crosstalk removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
@@
 As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
-For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citet{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.
+For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.
 The reasons for a previously underestimated limit and ways in which our new analysis differs can be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citet{ali_et_al2015}, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting.
+\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting.
 For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}).
@@
 We have verified our revised prediction extensively using pure noise simulations.
-We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that the theoretical prediction for noise in \citet{ali_et_al2015} was too high for its data points.
+We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that the theoretical prediction for noise in P64 was too high for its data points.
 \end{itemize}

### 2017-11-20 PAPER.tex
-went through whole paper for typos and small changes

@@
 The standard deviation over the $100$ bootstraps gives an error estimate for our dataset.
-As shown in Figure \ref{fig:toy_error1} by the grey star, the error computed from bootstrapping matches our theoretical prediction.
+As shown in Figure \ref{fig:toy_error1} by the grey star, the error computed from bootstrapping matches our theoretical prediction (green).
 
@@
 
-Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ samples), under-estimates the error by a factor of $\sim3$.
+Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent data samples to $N/10 = 100$.
+Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$.
 This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of samples that are drawn (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
+In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
 However, if we know that we have $100$ independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction as expected.
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
-	\caption{Error estimation produced by bootstrapping as a function of the number of samples drawn when sampling with replacement.
-The star represents the error associated with drawing $1000$ samples from a length $1000$ array of a Gaussian random signal.
+	\caption{Error estimation produced by bootstrapping as a function of the number of elements drawn per bootstrap when sampling with replacement.
+The star represents the error associated with drawing $1000$ elements from a length $1000$ array of a Gaussian random signal.
 The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more samples than there are independent samples in the data.
+They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
 The estimated errors match up with the theoretical prediction only at $N=100$.}
@@
 For each bootstrap, we draw $N-1=4$ samples without replacement and draw the last slot randomly with replacement.
-In doing so there is a small chance a bootstrap will consist of $5$ independent samples, but even with $4$ our sensitivity is nearly maximized.
+In doing so there is a small chance a bootstrap will consist of $5$ independent measurements, but even with $4$ our sensitivity is nearly maximized.
 One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
@@
 	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a dataset (i.e.
-$4$ out of $5$ elements are independent would yield a fraction of $0.8$).
+if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$).
 A fraction of $1.0$ means that all elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
@@
 The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.
-The `outlier' points lying at a fraction of $1.0$ occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
+The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
 	\label{fig:toy_error2}
@@
 Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or $k$ modes.
-For a particular baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between the two antennas in the baseline.
+For a particular baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between two antennas in a baseline.
 For longer baselines, this value increases, producing what is known as ``the wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; \citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}).
@@
 doesn't get subtracted perfectly).
-\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill confidence in a final result, since a stable result should be consistent through all of them.
-A result must be steadfast throughout all jackknives no matter how the data is sliced.
-Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a power spectrum each time as a day of data is removed, or a baseline is removed.
+\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill confidence in a final result.
+A stable result must be steadfast throughout all jackknives no matter how the data is sliced.
+Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new power spectrum every time as a day of data is removed, or a baseline is removed.
 This type of jackknife would reveal bias present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
@@
 This is equivalent to splitting up a full dataset along an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
-We cross-multiply measurements $a$ and $b$ to form an un-biased (noise-wise) estimate (blue curve).
+We cross-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve).
 The second estimate, shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{fg}$ in Equations \ref{eq:bias1} and \ref{eq:bias2}).
@@
 From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of noise.
-This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
+This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
 
@@
 
-For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses an RA range of $0$-$8.6$ hours).
+For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA range of $0$-$8.6$ hours).
 All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in P64.
@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
-Here we use the same method used in P64, where mock gaussian noise visibilities are filtered in fringe-rate space to retain only ``sky-like" time-modes.
+Here we use the same method used in P64, where mock gaussian noise visibilities (mock EoR signals) are filtered in fringe-rate space to retain only ``sky-like" time-modes.
 This signal is then added to the data.
@@
 In fact, foreground modes and signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $\textbf{C}_{r}$.
-Mathematically,
+Mathematically, the covariance of the data plus EoR is:
 
@@
 \noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices.
-The middle two terms, however, have a larger amount of power in their off-diagonal terms relative to the diagonal elements, since $\textbf{e}$ and $\textbf{x}$ are statistically unrelated.
+The middle two terms, however, have a larger amount of power in their off-diagonal terms relative to their diagonal elements, since $\textbf{e}$ and $\textbf{x}$ are statistically unrelated.
 Upon inversion, these off-diagonal terms become negative, driving the cross-terms in Equation \ref{eq:pout_expand} to have negative power.
@@
 The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of $P_{in}$ values.
-We correct for this as explained in the next section.
+We correct for this, as explained later in this section.
 
@@
 
-Two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} which denote power spectrum values, post-signal loss correction, for two other regularization schemes.
+In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} which denote power spectrum values, post-signal loss correction, for two other regularization schemes.
 We multiply an identity matrix element-wise to $\hat{\textbf{C}}$ (i.e.
-inverse variance weighting, shown in red), and also add an arbitrary level of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan).
-We see that all three regularization schemes (black, red, cyan) perform similarly.
+inverse variance weighting, shown in red), and also add an arbitrarily chosen level of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan).
+We see that all three regularization schemes (black, red, cyan) perform similarly at their best.
 
@@
 The analytic calculation is only an approximation, however the differences were large enough (factors of $10$ in some cases) to warrant a careful investigation.
-The analytic calculation attempts to combine a large number of pieces of information in an approximate way, and when re-considering some of the approximations we have found there to be large effects.
+The analytic calculation attempts to combine a large number of pieces of information in an approximate way, and when re-considering some of the approximations, we have found there to be large effects.
 What follows here is an accounting of the differences which have been discovered.
 
-The sensitivity prediction \cc{need refs} for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
+The sensitivity prediction (\citealt{parsons_et_al2012a}) for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
 
@@
 For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
-\item $\Omega_{eff}$: The effective primary beam area in steradians \footnote{\cc{ref equation}}.
+\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}, \citealt{pober_et_al2012}).
 The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-weighted.
@@
 For the analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$.
-The revised limit in \cc{cite kolopanis paper} uses three separation types.
+The updated limits in \cc{cite kolopanis paper} use three separation types.
 \item $t_{int}$: The integration time of the data.
@@
 However, using the total number of baselines neglects the fact that baselines are averaged into groups before cross-multiplying data.
-Our revised estimate for the parameter is $N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}}$, where, for the P64 analysis, $N_{gps} = 5$.
-Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as square root of the number of cross multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
+Our revised estimate for the parameter is:
+\begin{equation}
+N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
+\end{equation}
+\noindent where, for the P64 analysis, $N_{gps} = 5$.
+Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
 For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$.
@@
 Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$.
-This is consistent with
 
@@
 
-\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
+\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST-binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
 This RMS temperature sets the variance of the Gaussian random noise.
@@
 Final power spectrum limits were then computed by taking the mean and standard deviation over this second bootstrap axis (which is typically large, on the order of $N_{boot} \sim 400$).
-We emphasize that in this previous version, the number of elements sampled per bootstrap (number of times $\sim$ $700$) greatly exceeds the number of independent LST samples, under-estimating errors.
+We emphasize that in this previous version, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly exceeds the number of independent LST samples ($\sim$$8$), under-estimating errors.
 
 Because our dataset is fringe-rate filtered, we have substantially increased our integration time, resulting in fewer independent samples (from $\sim700$ samples to $8$ samples).
-A random draw of $700$ samples from this dataset therefore has many repeated samples, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
+A random draw of $700$ measurements from this dataset therefore has many repeated values, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
 
@@
 As shown in the figure, when the baseline average includes many repeated samples the error is over-estimated, while when only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ modes converges to the theoretical noise level.
-However, if more elements are drawn for each bootstrap than the number of independent samples (by drawing many times along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level.
+However, if more elements are drawn for each bootstrap than the number of independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level.
 
@@
 It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly), as shown by the black curve.
-In red, bootstrapping occurs over both the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).}
+In red, bootstrapping occurs over both the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).
+We use the method illustrated by the black curve in our updated analysis, which is shown to agree with the analytic prediction for noise (green).}
 	\label{fig:data_errors}
@@
 
-In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as a power spectrum detection and imitate EoR.
+In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum detections and imitate EoR.
 We discussed the importance of using jackknife and null tests for instilling confidence in an EoR detection, as well as identifying other sources of biases.
-Here we demonstrate methods used by PAPER-64 to mitigate foreground and noise bias and we perform jackknife and null tests in order to characterize the stability and implications of our results.
+Here we demonstrate methods used by PAPER-64 to mitigate foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.
 
@@
 Our data vectors are then $\textbf{x}_{even, 1}$ for the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc.
-We only form $\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `'even', for example, in order to prevent the squaring of the same thermal noise.
+We only form $\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for example, in order to prevent the squaring of the same thermal noise.
 
@@
 
-The highest sensitivity power spectrum result using PAPER-64 data and all revised methods, shown in Figure \ref{fig:ps1_data}, has positive biases at low $k$ values.
+The highest sensitivity power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in Figure \ref{fig:ps1_data}, has positive biases at low $k$ values.
 As discussed in Section \ref{sec:BiasTypes}, these detections are most likely attributable to foreground leakage.
@@
 \begin{itemize}
-\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised PAPER-64 power spectrum (one baseline type only) with weighting matrix $\textbf{C}_{eff}$.
+\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised PAPER-64 power spectrum (one baseline type only) with weighting matrix $\hat{\textbf{C}}_{eff}$.
 There are clear detections at low $k$'s.
@@
 \item LST (purple): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 4.6-8.6 hours).
-We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$
+We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$.
 \end{itemize}
@@
 	\includegraphics[width=\columnwidth]{plots/null.png}
-	\caption{Results of $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ errors (grey shaded region).
+	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ errors (grey shaded region).
 For each, we took jackknives along different axes of the dataset - by julian days (separating even and odd days; blue), by baselines (green), and by LST (purple).
@@
 In other words, $t_{1}$ and $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-The errors on this null test are also large, also reflective of residual foregrounds.
+The errors for this null test are also large, also reflective of residual foregrounds.
 
 We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s.
-This would illuminate the particular LST range that introduces the foreground bias (or whether the bias is constant in LST), and could potentially be traced to a individual bright radio source.
-This type of detailed analysis will be critical at EoR sensitivities, however, for the purpose of this paper we are not surprised that the bias we see comes from foregrounds in regions where we expect leakage.
+This would illuminate the particular LST range that introduces the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source.
+This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the bias we see comes from foregrounds in regions where we expect leakage.
 
@@
 Although current $21$ cm published power spectrum upper limits lie a couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities.
-As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknive and null tests.
+As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife and null tests.
 
@@
 comparing an unweighted vs.
-weighted power spectrum of EoR) can underestimate loss by failing to account for spurious correlations between the data and signal.
+weighted power spectrum of EoR only) can underestimate loss by failing to account for spurious correlations between the data and signal.
 \item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated (Section \ref{sec:ErrorOverview}).
@@
 \item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}).
-Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection, and can also be used to tease out systematics.
+Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection and can also be used to tease out systematics.
 \end{itemize}
@@
 For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}).
-However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ in mK higher than previous limits.
+However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ mK higher than previous limits.
 Underestimated signal loss therefore represents the bulk of our revision.
@@
 Hence, the net change for our error estimation is negligible, though the rationale behind the previous estimation was incorrect.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$7$ (Section \ref{sec:PSSense}).
+\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$3$ in mK (Section \ref{sec:PSSense}).
 We have verified our revised prediction extensively using pure noise simulations.
@@
 \section{Acknowledgements}
-CC would like acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
+CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
 PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646).

### 2017-11-21 PAPER.tex
made jonnie edits until 2.1.1

@@
 Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen to place constraints on the brightness of the EoR.
-Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman2010}), the Long Wavelength Array (LWA; \citealt{ellingson_et_al2009}),  the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; \citealt{patra2015}).
+Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; \citealt{patra2015}).
 Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; \citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
@@
 In this paper, we discuss three themes that are essential to investigate for a robust $21$ cm power spectrum analysis.
-We also highlight four power spectrum techniques and their trade-offs, traps, and connections to the themes.
+We also highlight four power spectrum techniques and their trade-offs, potential pitfalls, and connections to the themes.
 We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum from the lessons learned.
@@
 A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power spectrum result.
-Stemmed from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for a rigorous power spectrum analysis.
+Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for a rigorous power spectrum analysis.
 \begin{itemize}
-\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): As explained in the next section, certain analysis techniques can lead to the loss of the EoR signal.
-If not corrected for, it could lead to a false non-detection.
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Certain analysis techniques can lead to the loss of the EoR signal.
+If not corrected for, this loss could lead to a false non-detection.
 Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
-PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item \textbf{Error Bar Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
+\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
 Errors can be estimated in a variety of ways, and we will discuss a few of them.
@@
 We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
-\item \textbf{Weighting:} A dataset can be weighted to emphasize certain spectral features and minimize others.
-One particular flavor of weighting is inverse covariance weighting, which is a generalized version of inverse variance weighting that also takes into account data correlations.
+\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others.
+One particular flavor of weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations.
 This weighting has the effect of down-weighting correlated information (i.e.
@@
 However, a challenge of inverse covariance weighting is in accurately defining a covariance matrix that best describes the data.
-\item \textbf{Bootstrapping:} Because theoretical models for covariance matrices are questionable and theoretical error estimation methods rely on assumptions that can be violated by data, applying theoretical errors to a $21$ cm measurement is often avoided.
-Hence, bootstrapping is a useful method for estimating errors of a dataset from itself.
+\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation methods, bootstrapping is one way to estimate errors.
+Bootstrapping is a useful method for estimating errors of a dataset from itself.
 By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to consider such as the independence of values in a dataset.
@@
 
-Driven by the need to mitigate foreground bias, we use a weighting method that succeeds in down-weighting foregrounds.
-We apply this weighting to data and propagate it into a final estimator using the power spectrum estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}).
-Before showing how signal loss can arise when using different weighting matrices, we first summarize OQE as follows.
-
-We begin with our data vector, $\textbf{x}$, which contains our measured visibilities in Jy.
+Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
+This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}).
+Before showing how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER analysis.
+
+We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities in Jy.
 It has length ($N_{t}, N_{f}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
@@
 
-\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin.
+\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin, as well as cosmological scalings.
 The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}).
@@
 \noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum.
-The data analyst has a choice for $\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}
+The data analyst has a choice for $\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}.
 
@@
 	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset contains a sinusoid foreground that varies smoothly in time and a random Gaussian signal as a mock EoR signal. Real parts are shown here.}
+	\caption{Our toy model dataset.
+We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in time and frequency.
+We model a mock EoR signal as a random Gaussian signal.
+Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 	\centering
-	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss15.png}
+	\includegraphics[trim={1.5cm 0.2cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
@@
 Underestimated signal loss therefore represents the bulk of our revision.
+We note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
 \item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering.

### 2017-11-21 PAPER.tex
Made jonnie edits until 2.1

@@
 This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-For PAPER-64 we use $\sim$$8$ hours of data for our analysis, but here we scale it down for this toy model with no loss of generality.
-We create a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid with a fixed frequency and a smoothly varying offset in time, a simplistic but realistic representation of a single bright source.
+For PAPER-64 we use $\sim$$8$ hours of data for our analysis (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of generality.
+
+We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation.
+Hence, flat spectrum sources (away from zenith) oscillate in time and frequency in our measurements.
+We therefore form a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
 We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
@@
 Given perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data.
-However, if our foreground model is flawed for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
+However, if our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
 
@@
 
-\noindent assuming $\langle\textbf{x}\rangle = 0$, where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
+\noindent assuming $\langle\textbf{x}\rangle = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient amount of time), where $\langle \rangle$ denotes a finite average over time $t$.
+The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
 
 First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$.
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3} (the right plot shows an alternate weighting approach and will be discussed further below).
 Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
@@
 This is evidence of signal loss.
-In order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$, which is shown in Figure \ref{fig:toy_sigloss12}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
-	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only (middle), and FG + EoR (right). Real parts are shown here.}
-	\label{fig:toy_sigloss12}
-\end{figure}
-
-If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias to estimates of the signal.
+In order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$.
+%, which is shown in Figure \ref{fig:toy_sigloss12}.
+
+If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.
 For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
@@
 
-In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are more trustworthy than the weakest modes, since that's where we expect bright foregrounds --- the most prominent shapes --- to be.
-If bright foregrounds dominate, these highest eigenvalue modes would exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
+In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds --- the most prominent shapes in the data.
+If bright foregrounds dominate a dataset, these highest eigenvalue modes would exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
 This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
+In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.
+The foreground sinusoid is clearly visible in $\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only (middle), and FG + EoR (right). Real parts are shown here.}
+	\label{fig:toy_sigloss12}
+\end{figure}
 
@@
 Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss.
-Namely, we can project out the zeroth eigenmode (i.e.
+Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode.
+We can project out the zeroth eigenmode (i.e.
 zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes relevant to things that move as expected for the sidereal motion on the sky, while down-weighting modes which are noise-like.
+Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes corresponding to the sidereal motion on the sky, while down-weighting modes which are noise-like.
 
@@
 To mimic this filter, we average every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix.
+In this case...
+\cc{fill in}}
 
@@
 As expected, there is a much larger amount of signal loss for this time-averaged dataset.
-Additionally, because of the steepened eigenspectrum, most of our power spectrum information is coming from only the last few modes and as a result, it is a noisier estimate.
+Additionally, because of the steepened eigenspectrum, the last few eigenmodes receive more weight relative to the others.
+Therefore, most of our power spectrum information is coming from only these last few modes and as a result, it is a noisier estimate.
 This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
@@
 Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates when using data-estimated covariance matrices.
-Longer integrations increase sensitivity but reduce the number of independent samples, resulting in weakly characterized, steep eigenspectra that can overfit noise greatly.
-\cc{help me fix explanation}
+Longer integrations increase sensitivity but reduce the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit noise greatly.
+We note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be advantageous to use one despite the trade-offs.
 
@@
 
-As a first test, we know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-If we model $\textbf{C}_{EoR}$ as such, instead of computing it based on the dataset itself, and add it to $\hat{\textbf{C}}_{FG}$ (defined as $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting, we see that there is negligible signal loss (Figure \ref{fig:toy_sigloss8}, upper left).
+As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be avoided.
+We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
+We model $\textbf{C}_{EoR}$ as such, instead of computing it based on $\textbf{x}_{EoR}$ itself.
+Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting.
+In Figure \ref{fig:toy_sigloss8} (upper left), we see that there is negligible signal loss.
 This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
@@
 This deviation is a consequence of the difference between the true and modeled covariance matrices.
+In practice such a weighting option is not feasible, as we do not know $\textbf{C}_{EoR}$.
 
@@
 	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $\hat{\textbf{C}}$ (magenta).
-All eigenspectra (except the green) are relatively flat and don't exhibit signal loss.}
+All eigenspectra (except the green) are relatively flat and don't exhibit signal loss.
+All were computed for the fringe-rate filtered toy model case.}
 	\label{fig:toy_sigloss14}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij} + \gamma\textbf{I}_{ij}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I}$ for the purpose of this toy model).
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}} + \gamma\textbf{I}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I}$ for the purpose of this toy model).
 By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
@@
 The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by only using the first three eigenmodes.
-This means that all but the three highest weights will be replaced with $1$'s (equal weights).
+Recalling that the foregrounds can be described entirely by the first eigenmode, this method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the eigenspectrum with $1$'s (equal weights).
 Again, flattening the eigenspectrum results in negligible signal loss.
@@
 
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
 In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
@@
 Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate confidence intervals for our measurements.
-Two popular ways of estimating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
+Two popular ways of empirically calculating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
 In a perfect world, both methods would match up.
 However, in practice the two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform weightings.
-Since modeling errors for a complex instrument is only approximate, we choose to compute error bars on our measurements that have been derived from its inherent variance.
+For PAPER's analysis, we choose to compute error bars on our measurements that have been derived from its inherent variance.
 
@@
 Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, power-spectral measurements of $21$ cm data can be made along many axes, including time and baselines.
+For example, power-spectral measurements of $21$ cm data can be made from different samples of data (i.e.
+data can be sliced along time, baselines, etc.
+and a power spectrum measurement can be made for each).
 Averaging each sample set gives us a realization of the power spectrum answer.
@@
 
-Again, we focus on toy models to highlight traps that one can fall into when bootstrapping power spectra.
+Again, we focus on toy models to highlight pitfalls that one can fall into when bootstrapping power spectra.
 Suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance.
@@
 
-We choose to use $\hat{\textbf{C}} = \hat{\textbf{C}}_{ij}\textbf{I}_{ij}$, or inverse variance weighting, for the remainder of this paper, which we will denote as $\hat{\textbf{C}}_{eff}$.
+We choose to use $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or inverse variance weighting, for the remainder of this paper, which we will denote as $\hat{\textbf{C}}_{eff}$.
 We choose this weighting scheme due to its simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.

### 2017-11-22 PAPER.tex
made jonnie changes until Section 3

@@
 Our ultimate goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
+We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for the sake of completeness.
+The specifics of how signal loss crops up in PAPER's analysis is later described in Section \ref{sec:Sigloss}.
 
@@
 The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.}
+These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.
+Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to loss.}
 	\label{fig:toy_sigloss2}
@@
 If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue of $\textbf{C}$ would be representative of real fluctuations in the data.
-However, when using an estimated $\hat{\textbf{C}}$ that is derived from one particular data realization, some of its eigenvalues may be describing random fluctuations that just happen to exist in the data realization.
+However, when using an estimated $\hat{\textbf{C}}$ that is derived from one particular data realization, its eigenvalues may differ from the truth.
 Said differently, shapes that may not exist (or have a weaker existence) in a true covariance may appear stronger in the estimated covariance.
@@
 In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds --- the most prominent shapes in the data.
-If bright foregrounds dominate a dataset, these highest eigenvalue modes would exist in both $\textbf{C}$ and $\hat{\textbf{C}}$.
+For these `strong' modes, where foregrounds outshine the EoR signal, $\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial.
 This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
@@
 
-The danger of an empirically estimated covariance matrix comes from not being able to describe weak eigenmodes of $\textbf{C}$ accurately.
-Instead, the weak eigenmodes of $\hat{\textbf{C}}$ may characterize noise-like fluctuations which will be down-weighted.
-These noise fluctuations could be the signal itself, since $\hat{\textbf{C}}$ is constructed using data that contains the signal.
+The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
+If these weak eigenmodes of $\hat{\textbf{C}}$ characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted).
 This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.
@@
 zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
-Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing fluctuations that may not exist in the true covariance.
+Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing EoR fluctuations.
 Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$.
@@
 
-We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes with a data-estimated covariance.
+We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes (EoR dominated modes) with a data-estimated covariance.
 We will next show how this effect is exaggerated by reducing the total number of independent samples in a dataset.
@@
 The dashed spectrum is steeper, resulting in more dramatic differences in weighting between eigenmodes.
-Consequently, if all eigenmodes are used in weighting it is possible to down-weight random noisy modes more severely than for the non-averaged case.}
+Consequently, if all eigenmodes are used in weighting it is possible to down-weight EoR modes more severely than for the non-averaged case.}
 	\label{fig:toy_sigloss5}
@@
 There is a larger amount of signal loss than for the non-averaged data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
-The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes.}
+The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the weakest, EoR-dominated modes, which are down-weighted the least).}
 	\label{fig:toy_sigloss7}
@@
 Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates when using data-estimated covariance matrices.
-Longer integrations increase sensitivity but reduce the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit noise greatly.
+Longer integrations increase sensitivity but reduce the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit signal greatly.
 We note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be advantageous to use one despite the trade-offs.
@@
 
-In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from random fluctuation-induced eigenmodes in an estimated one.
+In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from those in an estimated one.
 We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ in order to minimize signal loss.
-We illustrate the resulting power spectra and eigenspectra for four different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
+We choose four independent regularization methods to highlight in this section, which have been chosen due to their simplicity in implementation and straightforward interpretations.
+We illustrate the resulting power spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
 
@@
 In Figure \ref{fig:toy_sigloss8} (upper left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting small fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
 This is evident when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}.
@@
 By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
-If all modes are given similar weights, we avoid down-weighting artificial modes more than others.
+If all modes are given similar weights, we avoid down-weighting EoR modes more than others.
 
@@
 However, in practice the two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform weightings.
+
 For PAPER's analysis, we choose to compute error bars on our measurements that have been derived from its inherent variance.
-
-A common technique used to estimate the error in a measurement is bootstrapping.
+A common technique used to do this is bootstrapping.
+For pedagogical purposes, we first define the technique of bootstrapping and then illustrate some of its pitfalls through toy models.
+
 Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, power-spectral measurements of $21$ cm data can be made from different samples of data (i.e.
-data can be sliced along time, baselines, etc.
-and a power spectrum measurement can be made for each).
-Averaging each sample set gives us a realization of the power spectrum answer.
+For example, measurements (like power spectra) can be made from different samples of data.
+Averaging each sample set gives us a realization of the (power spectrum) answer.
 Realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Hence, through the process of resampling and averaging along these axes, we can estimate error bars for our results which represent the underlying distribution of power spectra values that are allowed by our measurements.
-
-Again, we focus on toy models to highlight pitfalls that one can fall into when bootstrapping power spectra.
-Suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance.
-We are interested in the average of the dataset, and predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-We form $100$ bootstraps, each comprised of an array of length $N$ that is created by a random resampling of the original data, with replacement.
-The standard deviation over the $100$ bootstraps gives an error estimate for our dataset.
-As shown in Figure \ref{fig:toy_error1} by the grey star, the error computed from bootstrapping matches our theoretical prediction (green).
+Hence, through the process of resampling and averaging along different axes, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements.
+
+Suppose we have $N$ different measurements targeting the same quantity ($N$ power spectrum measurements).
+Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
+Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (every $N$th slot is filled randomly for each bootstrap).
+Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
+The error (on the mean) is then computed as the standard deviation across all bootstraps.
+
+We must be careful in distinguishing $N_{boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
+In the toy models presented in this section, $N_{boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{boot}$.
+It is the value of $N$ that we must be careful in setting, as described in the rest of this section.
+
+For our toy model, suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
+This could represent $1000$ power spectrum measurements, for which we are interested in its error.
+We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+We next form $500$ bootstraps ($N_{boot} = 500$).
+To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
+The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
+This error is indicated by the grey star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
 
@@
 For example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the number of averages performed.
-Down-sampling a fringe-rate filtered signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
+Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
 Hence, we do not recommend bootstrapping unless the number of independent samples along the axis that is being re-sampled is well-determined.
@@
 	\caption{Error estimation produced by bootstrapping as a function of the number of elements drawn per bootstrap when sampling with replacement.
-The star represents the error associated with drawing $1000$ elements from a length $1000$ array of a Gaussian random signal.
+The star represents the standard deviation of $500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
 The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
@@
 
-We will now discuss a second subtle feature of bootstrapping that can lead to an over-estimation of errors.
+We will now discuss a second subtle feature of bootstrapping that fails to maximize the sensitivity of a dataset.
 Suppose we have $5$ independent measurements of the sky (from $5$ different baselines, for example).
@@
 In doing so there is a small chance a bootstrap will consist of $5$ independent measurements, but even with $4$ our sensitivity is nearly maximized.
-One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
+%One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
 However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
@@
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
-The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.
-The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
+The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.} %The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
 	\label{fig:toy_error2}
@@
 In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond the length of a baseline are often still contaminated at a low level.
-This leakage can be attributed to convolution kernels associated with Fourier-transforming visibilities into delay-space.
+This leakage, especially at low $k$'s, can be attributed to convolution kernels associated with Fourier-transforming visibilities into delay-space.
 In other words, smooth-spectrum foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
@@
 
-Confirming foreground detections at higher $k$'s is more difficult. In the next section, we will present some tests that can help distinguish these excesses from that of EoR.
+Confirming foreground detections at higher $k$'s is more difficult.
+In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
 
@@
 
-In the next section, we approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful jackknife tests.
-
 \subsubsection{Jackknife Tests}
@@
 
+We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful jackknife tests.
 The jackknife is a resampling technique in which a statistic (i.e.
@@
 Several null tests on data are described in \citet{keating_et_al2016}.
-For example, one can divide data into two subsets by separating odd and even julian dates, or the first half of the observing season from the second.
+For example, one can divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second.
 Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR.
@@
 
-\begin{eqnarray}
+\begin{equation}
 \label{eq:bias1}
-\textbf{x}_{a} &=& \textbf{n}_{a} + \textbf{e} + \textbf{fg} \\
+\textbf{x}_{a} = \textbf{n}_{a} + \textbf{e} + \textbf{fg}
+\end{equation}
+
+\noindent and
+
+\begin{equation}
 \label{eq:bias2}
-\textbf{x}_{b} &=& \textbf{n}_{b} + \textbf{e} + \textbf{fg},
-\end{eqnarray}
-
-\noindent where the two jackknife samples (for both $a$ and $b$) are:
+\textbf{x}_{b} = \textbf{n}_{b} + \textbf{e} + \textbf{fg}.
+\end{equation}
+
+\noindent The two jackknife samples are $\textbf{x}_{1}$ and $\textbf{x}_{2}$, representing jackknives in time. These can be written (for both measurements $a$ and $b$) as:
 
@@
 For example, if jackknives along the time-axis reveal a bias present at a certain LST, a likely explanation would be excess foreground emission from a radio source in the sky at that time.
-A jackknife test involving data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed with the filter, or if similar-shaped detections in both power spectras suggest otherwise.
+A jackknife test involving data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed with the filter, or if similar-shaped detections in both power spectra suggest otherwise.
 There are many other jackknife axes of which we will not go into detail here, including baseline, frequency, and polarization.

### 2017-11-22 PAPER.tex
made jonnie edits until section 3.1

@@
 The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout.
-For our case study, we focus solely on Stokes I data from PAPER's $30$ m East/West baselines.
+For our case study, we focus solely on Stokes I estimated data (\citealt{moore_et_al2013}) from PAPER's $30$ m East/West baselines (Figure \ref{fig:ant_layout}).
 For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and P64.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/ant_layout.png}
+	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this paper (such as baseline 49\_41).}
+	\label{fig:ant_layout}
+\end{figure}
 
@@
 All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in P64.
-We note that the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter.
-\cc{Danny says the next part is wrong, but that's what's in Zaki's paper...
-} In P64, the applied filter was degraded by widening it in fringe-rate space.
-This was chosen in order to increase the number of independent modes and reduce signal loss.
-With the development of a robust method for assessing signal loss, we feel comfortable using a narrow filter --- the optimal fringe-rate filter --- in order to maximize sensitivity.
+We note that, besides using only $1$ baseline type instead of the $3$ in P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter.
+In P64, the applied filter was degraded by widening it in fringe-rate space.
+This was chosen in order to increase the number of independent modes and reduce signal loss, though as we will see this signal loss was still under-estimated.
+With the development of a new, robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity.
 This filter is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.

### 2017-11-22 PAPER.tex
made jonnie edits until section 3.2

@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
-Here we use the same method used in P64, where mock gaussian noise visibilities (mock EoR signals) are filtered in fringe-rate space to retain only ``sky-like" time-modes.
+Here we use the same method used in P64, where mock Gaussian noise visibilities (mock EoR signals) are filtered in fringe-rate space to retain only ``sky-like" time-modes.
 This signal is then added to the data.
-\footnote{One specific change from P64 is that we add this simulated signal into the chain before the final fringe-rate filter is applied to the data.
+\footnote{One specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is applied to the data.
 Previously, the addition was done after that final fringe-rate filter step.
@@
 Upon inversion, these off-diagonal terms become negative, driving the cross-terms in Equation \ref{eq:pout_expand} to have negative power.
-This effect is explained in more depth in \citet{switzer_et_al2015}.
+\cc{someone help me write this more elegantly...}This effect is explained in more depth in \citet{switzer_et_al2015}.
 
@@
 The solid black diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data distribution.
-From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does not exhibit loss.}
+From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does not exhibit loss.
+The peculiar feature of `signal gain' at low injection levels is explained in the text.}
 	\label{fig:sigloss_transfercurve}
@@
 
-\noindent we fit a polynomial to each, representing mean signal loss functions.
+\noindent we fit an $8$th order polynomial to each, representing mean signal loss functions.
 We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each $P_{in}$ value:
@@
 
-We note that for PAPER-64, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power), and sometimes centered around zero, representing measurements that are consistent with zero.
+We note that for PAPER-64, depending on the $k$-value, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power) and sometimes centered around zero, representing measurements that are consistent with zero.
 
@@
 This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
+We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals (recall that the spread in these probability density functions mostly comes from bootstrapping the data).
 
@@
 The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction based on observational parameters.}
+The solid green line is the theoretical noise level prediction based on observational parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
 	\label{fig:ps2_data}
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ for fringe-rate filtered PAPER-64 data.
+	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data.
 Values are shown before (grey) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that are down-weighted.
@@
 Also plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance weighted case (red), and added-identity case (cyan).
-All three regularizations shown (black, red, cyan) perform similarly at their best.
+All three regularizations shown (black, red, cyan) perform similarly (when $\sim$$3$ modes are down-weighted for the black curve).
 Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted as solid green.}
@@
 Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied when forming a power spectrum estimate.
-This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation because of this very reason.
+This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so we also regard those results as suspect and superseded by those of \cc{cite kolopanis}).
 

### 2017-11-22 PAPER.tex
made jonnie changes until section 3.3

@@
 In this section we will discuss possible sources of bias in a measurement, as well as techniques that can help mitigate their effects.
-We will also present a series of tests which we suggest be used to help evaluate deep limits and/or detections.
+We will also present a series of tests in a pedagogical fashion which we suggest be used to help evaluate deep limits and/or detections.
 
@@
 We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful jackknife tests.
+Again, we first approach this topic pedagogically as an introduction to the related PAPER discussion in Section \ref{sec:Bias}.
+
 The jackknife is a resampling technique in which a statistic (i.e.
@@
 
-The sensitivity prediction (\citealt{parsons_et_al2012a}) for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
+The sensitivity prediction (\citealt{parsons_et_al2012a}, \citealt{pober_et_al2013}) for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
 
@@
 Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
-For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$.
+For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead of $51$.
 \item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
@@
 
-Power spectrum results for the noise simulation are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \eqref{eq:sense}.
+Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \eqref{eq:sense}.
 All three are in agreement, validating our analytical thermal noise calculation.
@@
 The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
-In P64, a second round of bootstrapping occurred over the baseline bootstrap and time axes simultaneously.
-Random values were sampled with replacement along both axes, drawing as many values as there are number of time integrations.
-Final power spectrum limits were then computed by taking the mean and standard deviation over this second bootstrap axis (which is typically large, on the order of $N_{boot} \sim 400$).
-We emphasize that in this previous version, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly exceeds the number of independent LST samples ($\sim$$8$), under-estimating errors.
-
-Because our dataset is fringe-rate filtered, we have substantially increased our integration time, resulting in fewer independent samples (from $\sim700$ samples to $8$ samples).
-A random draw of $700$ measurements from this dataset therefore has many repeated values, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second step entirely and now simply bootstrap over baselines with the ``single replacement" strategy described in Section \ref{sec:ErrorOverview}.
+
+In P64, a second round of bootstrapping occurred over the time axis.
+A total of $400$ bootstraps were created in this step ($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis.
+More specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering, which is $\sim$$8$).
+Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied).
+Finally, power spectrum limits were computed by taking the mean and standard deviation over all the bootstraps.
+We emphasize again that in this previous analysis, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly exceeded the number of independent LST samples ($\sim$$8$), under-estimating errors.
+A random draw of $700$ measurements from this dataset has many repeated values, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
+
+Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second bootstrapping step along time entirely and now simply bootstrap over baselines with the ``single replacement" strategy described in Section \ref{sec:ErrorOverview}.
 
@@
 The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss.
-As shown in the figure, when the baseline average includes many repeated samples the error is over-estimated, while when only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ modes converges to the theoretical noise level.
+As shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized, while when only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ modes converges to the theoretical noise level.
 However, if more elements are drawn for each bootstrap than the number of independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level.

### 2017-11-22 PAPER.tex
-Most of Jonnie's edits all accounted for except: appendix, and a few outstanding issues

@@
 
-\cc{Should we even include this next section? I included it to follow-up on Section 2.3.1, but it's not saying anything new...}
-
 We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we suppress noise biases.
@@
 
-Although current $21$ cm published power spectrum upper limits lie a couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities.
+Although current $21$ cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities.
 As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife and null tests.
@@
 We have verified our revised prediction extensively using pure noise simulations.
-We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that the theoretical prediction for noise in P64 was too high for its data points.
+We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that if taken at face value, the theoretical prediction for noise in P64 was too high for its data points.
 \end{itemize}
@@
 PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646).
-ARP, JCP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1302774, 1401708, and 1455151, respectively).
+ARP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
 We also graciously thank SKA-SA for site infrastructure and observing support.

### 2017-11-22 PAPER.tex
-Set aside section for Danny/Matt in signal loss

@@
 The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an input power spectrum distribution into an output distribution.
-By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss transfer function and detail the computation used to translate our power spectrum result into one viewed through a signal loss lens.
+By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss transfer function and detail two different computations used to translate our power spectrum result into one viewed through a signal loss lens.
+We showcase two methods...
+\cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
 
 \subsubsection{Signal Loss in Practice}
+
+\begin{center}
+METHOD \#1
+\end{center}
 
@@
 Focusing on the unweighted case alone, the scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$.
-Since we draw different random $\textbf{e}$'s for every bootstrap, there is a range of $P_{out}$ values that results from the same $P_{in}$.
+Since we draw different random $\textbf{e}$'s for every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{out}$ values that results from the same $P_{in}$.
 This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of the spread in the weighted case (left plot).
@@
 There is a second component of scatter that is less intuitive, only applies (at a low level) to the weighted case, and represents intrinsic scatter in signal loss.
-The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$.
+The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
 For example, if we are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
@@
 
-To conclude this section, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
+To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
 The blue dashed line represents the unweighted power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case).
@@
 Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first eight.
-Hence, there is a substantial down-weighting of many random modes, a large loss that the signal loss transfer function captures and corrects for.
+Hence, there is a substantial down-weighting of other modes, a large loss that the signal loss transfer function captures and corrects for.
 We elaborate on this point in the next section, as well as investigate alternate weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
@@
 
+\begin{center}
+METHOD \#2
+\end{center}
+
+The second method we describe here... \cc{Danny and Matt's section}
+
+\cc{refer back to Equations \eqref{eq:Pin} and \eqref{eq:sigloss} and explain why the subtraction term is removed}
+
+\cc{also state at the end that the rest of the analysis uses method \#1 instead of \#2...}
+
 \subsubsection{Minimizing Signal Loss}
@@
 
-With our signal loss formalism established, we now have the capability of experimenting with different weighting options for $\textbf{R}$.
+With a signal loss formalism established (Method \#1, for the rest of this paper), we now have the capability of experimenting with different weighting options for $\textbf{R}$.
 Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
@@
 We see that the amount of signal loss increases as weighting becomes more aggressive (grey curve).
-In other words, more random fluctuations are being overfit and subtracted as more modes are down-weighted.
+In other words, more `weak' (EoR-dominated) fluctuations are being overfit and subtracted as more modes are down-weighted.
 We also find that the power spectrum upper limit, post signal loss correction, increases with the number of down-weighted modes (black curve).
@@
 inverse variance weighting, shown in red), and also add an arbitrarily chosen level of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan).
-We see that all three regularization schemes (black, red, cyan) perform similarly at their best.
-
-We choose to use $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or inverse variance weighting, for the remainder of this paper, which we will denote as $\hat{\textbf{C}}_{eff}$.
+We see that all three regularization schemes (black, red, cyan) perform similarly at their best (i.e.
+when $\sim3$-$4$ eigenmodes are down-weighted in the case of the black curve).
+
+For the remainder of this paper, we choose to use the weighting option of $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or inverse variance weighting, which we will denote as $\hat{\textbf{C}}_{eff}$.
 We choose this weighting scheme due to its simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
@@
 Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting modes in the power spectrum dataset itself.
+Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
 

### 2017-11-22 PAPER.tex
-hard wrap on text -plots in paper now have updated analytic to account for lower Tsys value

@@
 \begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and galaxies led to the ionization of neutral hydrogen in the intergalactic medium.
-There are many experiments investigating the EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate.
-With a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to develop techniques that help maximize sensitivity and validate results.
-Additionally, it is imperative to understand the trade-offs between different methods and their effects on common power spectrum themes.
-In this paper, we focus on three major themes --- signal loss, power spectrum error bar estimation, and bias in measurements.
-We describe techniques that affect these themes using both toy models and data taken by the 64-element configuration of the Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-In particular, we highlight how detailed investigations of these themes have led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64.
-This revised result mostly stems from an updated signal loss calculation for loss associated with empirically estimated covariances and supersedes results from previously published PAPER analyses.
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and 
+galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
+EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
+of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
+develop techniques that help maximize sensitivity and validate results. Additionally, it is imperative to understand the trade-offs 
+between different methods and their effects on common power spectrum themes. In this paper, we focus on three major 
+themes --- signal loss, power spectrum error bar estimation, and bias in measurements. We describe techniques that affect 
+these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
+for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
+led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result mostly stems from an 
+updated signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
+previously published PAPER analyses.
 \end{abstract}
@@
 
-By about one billion years after the Big Bang ($z \sim 6$), the very first stars and galaxies are thought to have ionized all the neutral hydrogen that dominated the baryonic matter content in the Universe.
-This transition period, during which the first luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas into a plasma, is known as the epoch of reionization (EoR).
-The EoR is a relatively unexplored era in our cosmic dawn.
-Its history encodes important information regarding the nature of the first galaxies and the processes of structure formation.
-Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured web of galaxies we observe today.
-
-One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted by neutral hydrogen via its spin-flip transition.
-This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before stretching out as it traveled through expanding space.
-Tracing the 21 cm line as a function of redshift offers a window into the evolution of ionization, temperature, and density fluctuations during this transformative era.
-
-Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using the 21 cm signal from hydrogen to place constraints on the brightness of the EoR.
-Examples of experiments investigating the mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal (BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; \citealt{patra2015}).
-Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; \citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}).
-The Hydrogen Epoch of Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; \citealt{pober_et_al2014}).
-
-The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and instrumental systematics that are, when combined, 4-5 orders of magnitude brighter.
-A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
-With continual progress being made in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact with each other to affect power spectrum results.
-More specifically, it is imperative to develop techniques and tests that ensure the accuracy and reliability of a potential EoR detection.
-In this paper, we discuss three themes that are essential to investigate for a robust $21$ cm power spectrum analysis.
-We also highlight four power spectrum techniques and their trade-offs, potential pitfalls, and connections to the themes.
-We first approach the themes from a broad perspective, and then perform a detailed case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum from the lessons learned.
-
-This paper is organized into two main sections.
-In Section \ref{sec:Themes} we introduce the three themes of our focus, using a toy model to develop intuition for each one.
-In Section \ref{sec:CaseStudy} we present a case study into each theme using data from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}).
-We conclude in Section \ref{sec:Con}.
+By about one billion years after the Big Bang ($z \sim 6$), the very first stars and galaxies are thought to have ionized all the 
+neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
+luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
+into a plasma, is known as the epoch of reionization (EoR). The EoR is a relatively unexplored era in our cosmic dawn. Its 
+history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
+Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections 
+between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
+web of galaxies we observe today.
+
+One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted by neutral hydrogen via 
+its spin-flip transition. This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength 
+of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
+stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
+evolution of ionization, temperature, and density fluctuations during this transformative era.
+
+Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
+the 21 cm signal from hydrogen to place constraints on the brightness of the EoR. Examples of experiments investigating the 
+mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
+\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the 
+Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
+Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
+(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
+\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
+Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
+the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
+\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
+Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
+learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum 
+detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; 
+\citealt{pober_et_al2014}).
+
+The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
+instrumental systematics that are, when combined, 4-5 orders of magnitude brighter. A clean measurement therefore requires 
+an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
+in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
+with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
+the accuracy and reliability of a potential EoR detection. In this paper, we discuss three themes that are essential to investigate 
+for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
+pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
+case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum 
+from the lessons learned.
+
+This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
+toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
+from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
+revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}). We conclude in Section \ref{sec:Con}.
 
@@
 
-There are many choices a data analyst must consider.
-How can time-ordered measurements be combined?
-How can the variance of the data be estimated?
-In what way(s) can the data be weighted to suppress contaminated modes while not destroying an EoR signal?
-How can the source of a detection be properly identified?
-Many common techniques, such as averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs.
-For example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing some EoR signal.
-A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
-
-Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.
-In this paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay with each other and impact the themes.
-We will give brief definitions now, and build intuition for each theme in the sections to follow.
+There are many choices a data analyst must consider. How can time-ordered measurements be combined? How can the 
+variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
+destroying an EoR signal? How can the source of a detection be properly identified? Many common techniques, such as 
+averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
+example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
+some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
+
+Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
+methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.  In this 
+paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
+with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
+follow.
 
@@
 
-A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power spectrum result.
-Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for a rigorous power spectrum analysis.
+A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
+spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
+a rigorous power spectrum analysis.
 \begin{itemize}
-\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Certain analysis techniques can lead to the loss of the EoR signal.
-If not corrected for, this loss could lead to a false non-detection.
-Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
-\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result determine the difference between a detection and a null result, which have two very different implications.
-Errors can be estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds.
-In particular, a successful EoR detection would also imitate a bias.
-Proving a bias is EoR may be the most difficult challenge for $21$ cm analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR.
-In this paper we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must pass.
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Certain analysis techniques can lead to the loss of the EoR 
+signal. If not corrected for, this loss could lead to a false non-detection. Computing signal loss correctly has subtle challenges 
+but is necessary to ensure the accuracy of any result. 
+\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result 
+determine the difference between a detection and a null result, which have two very different implications. Errors can be 
+estimated in a variety of ways, and we will discuss a few of them.
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility 
+measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
+successful EoR detection would also imitate a bias. Proving a bias is EoR may be the most difficult challenge for $21$ cm 
+analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
+we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
+pass.
 \end{itemize}
@@
 
-The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in data.
-However, some have limitations, and we will discuss circumstances in which there are trade-offs.
-We choose to focus on these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also being standard steps in general $21$ cm analyses.
+The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
+data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
+these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
+being standard steps in general $21$ cm analyses.
 \begin{itemize}
-\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data (\citealt{parsons_et_al2016}).
-Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of independent samples by an amount dependent on the width of the averaging window.
-However, it can also affect the presence of foregrounds and systematics.
-We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
-\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others.
-One particular flavor of weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations.
-This weighting has the effect of down-weighting correlated information (i.e.
-foregrounds) and up-weighting noise-like information (i.e.
-EoR).
-However, a challenge of inverse covariance weighting is in accurately defining a covariance matrix that best describes the data.
-\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation methods, bootstrapping is one way to estimate errors.
-Bootstrapping is a useful method for estimating errors of a dataset from itself.
-By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to consider such as the independence of values in a dataset.
-\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different dimensions of a dataset to cross-validate results.
-In particular, null tests can be used to verify whether results are free of systematics (\citealt{keating_et_al2016}).
-An EoR detection must pass jack-knife and null tests.
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
+(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
+independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
+of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
+weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
+weighting that also takes into account frequency correlations. This weighting has the effect of down-weighting correlated 
+information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
+weighting is in accurately defining a covariance matrix that best describes the data. 
+\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
+methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
+itself. By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
+consider such as the independence of values in a dataset.
+\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
+dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
+systematics (\citealt{keating_et_al2016}). An EoR detection must pass jack-knife and null tests.
 \end{itemize}
@@
 In the next three subsections, we study each theme in depth, focusing on how power spectrum technique trade-offs affect each. 
-We use a toy data model to develop intuition into why certain analysis choices may be appealing and discuss ways in which they are limited.
-We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues.
-Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be considered for robust $21$ cm results.
+We use a toy data model to develop intuition into why certain analysis choices may be appealing and discuss ways in which 
+they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
+Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be considered for robust $21$ 
+cm results.
 
@@
 
-In this section we illustrate how signal loss arises in analysis.
-Signal loss refers to attenuation of the target cosmological signal in a power spectrum estimate.
-It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during spectral calibration, applying a delay-domain filter, or by weighting data by itself.
-Here we focus on signal loss associated with applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously underestimated in the P64 analysis
-
-Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
-This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}).
-Before showing how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER analysis.
-
-We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities in Jy.
-It has length ($N_{t}, N_{f}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
-Visibilities are measurements of the Fourier transform of the sky along $2$ spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes we only need to take one Fourier transform of our data along the line-of-sight dimension.
-We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
+In this section we illustrate how signal loss arises in analysis. Signal loss refers to attenuation of the target cosmological signal 
+in a power spectrum estimate. It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during 
+spectral calibration, applying a delay-domain filter, or by weighting data by itself. Here we focus on signal loss associated with 
+applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
+previously underestimated in the P64 analysis
+
+Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
+foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
+estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}). Before showing 
+how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
+analysis.
+
+We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities in Jy. It has length ($N_{t}, N_{f}$), where 
+$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
+the Fourier transform of the sky along $2$ spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes 
+we only need to take one Fourier transform of our data along the line-of-sight dimension. We do this when forming the un-
+normalized power spectrum estimate $\hat{q}_{\alpha}$:
 
@@
 
-\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to Kelvin, as well as cosmological scalings.
-The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}).
-$\textbf{R}$ is a weighting matrix --- as an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $\textbf{R} = \textbf{I}$, the identity matrix.
+\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into 
+power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
+Kelvin, as well as cosmological scalings. The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the 
+Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix --- as 
+an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
+\textbf{R} = \textbf{I}$, the identity matrix.
 
@@
 
-\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum.
-The data analyst has a choice for $\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis of PAPER-64 data as explained in Section \ref{sec:Bias}.
-
-In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$.
-Our ultimate goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
-We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for the sake of completeness.
-The specifics of how signal loss crops up in PAPER's analysis is later described in Section \ref{sec:Sigloss}.
+\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. The data analyst has a choice for $
+\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis 
+of PAPER-64 data as explained in Section \ref{sec:Bias}.
+
+In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
+matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our ultimate goal in 
+experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
+purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for 
+the sake of completeness. The specifics of how signal loss crops up in PAPER's analysis is later described in Section 
+\ref{sec:Sigloss}.
 
@@
 
-To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we use a toy model.
-We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time integrations and $20$ frequency channels).
-This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-For PAPER-64 we use $\sim$$8$ hours of data for our analysis (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of generality.
-
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation.
-Hence, flat spectrum sources (away from zenith) oscillate in time and frequency in our measurements.
-We therefore form a mock bright foreground signal, $\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
-We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal.
-A more realistic EoR signal would have a sloped power spectrum in $\hat{\textbf{p}}$(k) (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
-However, in this paper we treat all $k$'s separately, so a simplistic white noise approximation can be used.
-Our combined data vector is then $\textbf{x} = \textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes.
-The three data vectors are shown in Figure \ref{fig:toy_sigloss1}.
+To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we 
+use a toy model. We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
+integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
+might be used for a power spectrum analysis. For PAPER-64 we use $\sim$$8$ hours of data for our analysis (with channel 
+widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
+generality.
+
+We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation. Hence, flat spectrum sources (away 
+from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
+\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
+single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
+realistic EoR signal would have a sloped power spectrum in $\hat{\textbf{p}}$(k) (instead of flat, as in the case of white noise), 
+which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
+$k$'s separately, so a simplistic white noise approximation can be used. Our combined data vector is then $\textbf{x} = 
+\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data vectors are shown in Figure 
+\ref{fig:toy_sigloss1}.
 
@@
 	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset.
-We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in time and frequency.
-We model a mock EoR signal as a random Gaussian signal.
-Real parts are shown here.}
+	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
+time and frequency. We model a mock EoR signal as a random Gaussian signal. Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 
-One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-The covariance matrix $\textbf{C}$, which in our case describes covariances between frequency channels, can be estimated in a variety of ways.
-Given perfect foreground, instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data.
-However, if our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in the data.
+One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix. This type of weighting is attractive for power 
+spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on 
+a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}). The covariance matrix $\textbf{C}$, which in our case 
+describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
+instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data. However, if 
+our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in 
+the data.
 
@@
 
-\noindent assuming $\langle\textbf{x}\rangle = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient amount of time), where $\langle \rangle$ denotes a finite average over time $t$.
-The inverse covariance matrix is therefore $\textbf{R} = \hat{\textbf{C}}^{-1}$.
+\noindent assuming $\langle\textbf{x}\rangle = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $
+\textbf{R} = \hat{\textbf{C}}^{-1}$.
 
 First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$. 
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3} (the right plot shows an alternate weighting approach and will be discussed further below).
-Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3} (the right plot shows an alternate weighting approach 
+and will be discussed further below). Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $
+\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
 
@@
 	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We use inverse covariance weighting where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right).
-In the former case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$.
-Because $\hat{\textbf{C}}$ is empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization but may not exist in the true covariance.
-Consequently, these modes are over-fitted and down-weighted, leading to signal loss.
-There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes which $\hat{\textbf{C}}$ does not describe accurately.}
+	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
+foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting 
+where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right). In the former 
+case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
+empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization 
+but may not exist in the true covariance. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
+There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
+which $\hat{\textbf{C}}$ does not describe accurately.}
 	\label{fig:toy_sigloss3}
@@
 
-As shown, our inverse covariance-weighted result successfully suppresses foregrounds.
-It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-This is evidence of signal loss.
-In order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$.
-%, which is shown in Figure \ref{fig:toy_sigloss12}.
-
-If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.
-For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
-Here we will describe the origin of this signal loss intuitively.
-
-It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our true $\textbf{C}$, and this difference has consequences on our result.
-An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
-In other words, the eigenvalues encode the strength of different shapes in the dataset.
-The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-This is usually not the case for a covariance matrix, for which a sloped eigenspectrum means that modes are given different weights.
-The modes with the highest eigenvalues are down-weighted the most.
+As shown, our inverse covariance-weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
+recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In 
+order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$. %, which is 
+shown in Figure \ref{fig:toy_sigloss12}.
+
+If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a 
+multiplicative bias (per $k$) to estimates of the signal. For a mathematical derivation of signal loss arising from a data-
+estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}. Here we will describe the origin of this signal loss 
+intuitively.
+
+It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our 
+true $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
+highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
+words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
+\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes. This is usually not the case for a covariance matrix, 
+for which a sloped eigenspectrum means that modes are given different weights. The modes with the highest eigenvalues are 
+down-weighted the most.
 
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
-	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ (green).
-The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing signal loss.
-Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to loss.}
+	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
+(green). The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
+sinusoid. These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, 
+meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing 
+signal loss. Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to 
+loss.}
 	\label{fig:toy_sigloss2}
@@
 
-If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue of $\textbf{C}$ would be representative of real fluctuations in the data.
-However, when using an estimated $\hat{\textbf{C}}$ that is derived from one particular data realization, its eigenvalues may differ from the truth.
-Said differently, shapes that may not exist (or have a weaker existence) in a true covariance may appear stronger in the estimated covariance.
-Hence, they will be down-weighted more than they should be.
-
-In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds --- the most prominent shapes in the data.
-For these `strong' modes, where foregrounds outshine the EoR signal, $\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial.
-This is demonstrated in the toy model by the successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}).
-In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.
-The foreground sinusoid is clearly visible in $\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
+If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue of $\textbf{C}$ would be 
+representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
+particular data realization, its eigenvalues may differ from the truth. Said differently, shapes that may not exist (or have a 
+weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
+more than they should be.
+
+In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
+--- the most prominent shapes in the data. For these `strong' modes, where foregrounds outshine the EoR signal, $
+\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
+successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
+assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
+covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
+$\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
 
@@
 	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
-	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only (middle), and FG + EoR (right). Real parts are shown here.}
+	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
+(middle), and FG + EoR (right). Real parts are shown here.}
 	\label{fig:toy_sigloss12}
@@
 
-The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-If these weak eigenmodes of $\hat{\textbf{C}}$ characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted).
-This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.
-
-Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero signal loss.
-Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode.
-We can project out the zeroth eigenmode (i.e.
-zero out all eigenmodes except the first one), thereby down-weighting the foregrounds perfectly and nothing else.
-Hence, we are not using information from all the weaker eigenmodes which carry the risk of describing EoR fluctuations.
-Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$.
-The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}.
-In this case we recover EoR, demonstrating that if we can model our foregrounds perfectly (and disentangle them from other modes), we can down-weight them without signal loss.
-There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section \ref{sec:otherweight}.
+The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
+\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
+characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-
+weighted). This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.
+
+Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero 
+signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
+project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foregrounds 
+perfectly and nothing else. Hence, we are not using information from all the weaker eigenmodes which carry the risk of 
+describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
+changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
+power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
+demonstrating that if we can model our foregrounds perfectly (and disentangle them from other modes), we can down-weight 
+them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
+\ref{sec:otherweight}.
 
@@
 
-We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes (EoR dominated modes) with a data-estimated covariance.
-We will next show how this effect is exaggerated by reducing the total number of independent samples in a dataset.
+We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes (EoR dominated modes) with a 
+data-estimated covariance. We will next show how this effect is exaggerated by reducing the total number of independent 
+samples in a dataset.
 
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). 
-Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes corresponding to the sidereal motion on the sky, while down-weighting modes which are noise-like.
-
-Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
-To mimic this filter, we average every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix.
-In this case...
-\cc{fill in}}
-
-The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss5} (right plot).
-The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for the last few eigenmodes.
-This is because we have fewer independent modes --- \cc{need help filling out the rest here...
-and also citing galaxy lit}.
+Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes corresponding to 
+the sidereal motion on the sky, while down-weighting modes which are noise-like.
+
+Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent 
+samples in the data. To mimic this filter, we average every four time integrations of our toy model dataset together, yielding 
+$25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of 
+independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.\footnote{If 
+instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank 
+deficient covariance matrix. In this case... \cc{fill in}}
+
+The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
+\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
+the last few eigenmodes. This is because we have fewer independent modes --- \cc{need help filling out the rest here... and 
+also citing galaxy lit}.
 
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
-	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset.
-We average every four samples together, yielding $25$ independent samples in time.
-Real parts are shown here.
-Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
-The dashed spectrum is steeper, resulting in more dramatic differences in weighting between eigenmodes.
-Consequently, if all eigenmodes are used in weighting it is possible to down-weight EoR modes more severely than for the non-averaged case.}
+	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
+yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
+in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green). The dashed spectrum is steeper, 
+resulting in more dramatic differences in weighting between eigenmodes. Consequently, if all eigenmodes are used in weighting 
+it is possible to down-weight EoR modes more severely than for the non-averaged case.}
 	\label{fig:toy_sigloss5}
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
-	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We use inverse covariance weighting where $\textbf{C}$ is computed from the data.
-There is a larger amount of signal loss than for the non-averaged data, a consequence of a steepened, weakly characterized eigenspectrum from using fewer independent modes in the data.
-The power spectrum estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the weakest, EoR-dominated modes, which are down-weighted the least).}
+	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), 
+EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
+computed from the data. There is a larger amount of signal loss than for the non-averaged data, a consequence of a 
+steepened, weakly characterized eigenspectrum from using fewer independent modes in the data. The power spectrum 
+estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the 
+weakest, EoR-dominated modes, which are down-weighted the least).}
 	\label{fig:toy_sigloss7}
@@
 
-The power spectrum results for inverse covariance weighted fringe-rate filtered data is shown in Figure \ref{fig:toy_sigloss7}.
-As expected, there is a much larger amount of signal loss for this time-averaged dataset.
-Additionally, because of the steepened eigenspectrum, the last few eigenmodes receive more weight relative to the others.
-Therefore, most of our power spectrum information is coming from only these last few modes and as a result, it is a noisier estimate.
-This is evident by noticing that the green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
-
-Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal loss and noisier estimates when using data-estimated covariance matrices.
-Longer integrations increase sensitivity but reduce the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit signal greatly.
-We note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be advantageous to use one despite the trade-offs.
+The power spectrum results for inverse covariance weighted fringe-rate filtered data is shown in Figure \ref{fig:toy_sigloss7}. As 
+expected, there is a much larger amount of signal loss for this time-averaged dataset. Additionally, because of the steepened 
+eigenspectrum, the last few eigenmodes receive more weight relative to the others. Therefore, most of our power spectrum 
+information is coming from only these last few modes and as a result, it is a noisier estimate. This is evident by noticing that the 
+green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
+
+Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal 
+loss and noisier estimates when using data-estimated covariance matrices. Longer integrations increase sensitivity but reduce 
+the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit signal greatly. We 
+note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be 
+advantageous to use one despite the trade-offs.
 
@@
 
-In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance matrix from those in an estimated one.
-We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ in order to minimize signal loss.
-We choose four independent regularization methods to highlight in this section, which have been chosen due to their simplicity in implementation and straightforward interpretations.
-We illustrate the resulting power spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
-
-As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be avoided.
-We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its variance encoded along the diagonal.
-We model $\textbf{C}_{EoR}$ as such, instead of computing it based on $\textbf{x}_{EoR}$ itself.
-Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting.
-In Figure \ref{fig:toy_sigloss8} (upper left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
-This is evident when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}.
-We don't see perfect EoR recovery though, as the green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}.
-This deviation is a consequence of the difference between the true and modeled covariance matrices.
-In practice such a weighting option is not feasible, as we do not know $\textbf{C}_{EoR}$.
+In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can 
+make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance 
+matrix from those in an estimated one. We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ 
+in order to minimize signal loss. We choose four independent regularization methods to highlight in this section, which have 
+been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
+spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
+
+As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
+avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
+variance encoded along the diagonal. We model $\textbf{C}_{EoR}$ as such, instead of computing it based on $\textbf{x}
+_{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
+\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+left), we see that there is negligible signal loss. This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting 
+fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would). This is evident 
+when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}. We don't see perfect EoR recovery though, as the 
+green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}. This deviation is a consequence of the difference between the 
+true and modeled covariance matrices. In practice such a weighting option is not feasible, as we do not know $\textbf{C}_{EoR}
+$.
 
@@
 	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
-	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each avoid signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\hat{\textbf{C}}$ (lower right).}
+	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), 
+EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each avoid signal 
+loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to 
+it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
+$\hat{\textbf{C}}$ (lower right).}
 	\label{fig:toy_sigloss8}
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
-	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $\hat{\textbf{C}}$ (magenta).
-All eigenspectra (except the green) are relatively flat and don't exhibit signal loss.
-All were computed for the fringe-rate filtered toy model case.}
+	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
+weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity 
+matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
+\hat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
+computed for the fringe-rate filtered toy model case.}
 	\label{fig:toy_sigloss14}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = \hat{\textbf{C}} + \gamma\textbf{I}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength of $\textbf{I}$ for the purpose of this toy model).
-By adding the identity matrix, element-wise, we are weighting the diagonal elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum.
-If all modes are given similar weights, we avoid down-weighting EoR modes more than others.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - by only using the first three eigenmodes.
-Recalling that the foregrounds can be described entirely by the first eigenmode, this method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the eigenspectrum with $1$'s (equal weights).
-Again, flattening the eigenspectrum results in negligible signal loss.
-However, we do not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
-
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
-In the bottom right panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds.
-For this toy model, our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by the identity, element-wise, results in a diagonal matrix, meaning we are only left with correlation information between the same two frequencies.
-Because we disregard information from all other frequency combinations in this case, we do a poor job suppressing the foreground.
-But because we flattened the eigenspectrum, we also avoid signal loss.
-
-Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there are many options for estimating a covariance matrix, and some may be more effective than others based on the spectral nature of the components in a dataset.
-One may imagine a situation where a particular systematic is contained to an isolated frequency (such as radio frequency interference or crosstalk).
-In such a case, preserving only the diagonal elements of $\hat{\textbf{C}}$ would be an effective way of removing this contamination.
-
-In summary, we have a choice of how to weight $21$ cm data.
-Ideally, we want to down-weight bright foregrounds without removing the underlying cosmological signal.
-As we investigated however, there are trade-offs between the weighting method used, its foreground-removal effectiveness, and the amount of resulting signal loss.
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = 
+\hat{\textbf{C}} + \gamma\textbf{I}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength 
+of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
+elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum. If all modes are given 
+similar weights, we avoid down-weighting EoR modes more than others.
+
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - 
+by only using the first three eigenmodes. Recalling that the foregrounds can be described entirely by the first eigenmode, this 
+method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the 
+eigenspectrum with $1$'s (equal weights). Again, flattening the eigenspectrum results in negligible signal loss. However, we do 
+not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
+
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-
+wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$). In the bottom right 
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds. For this toy model, 
+our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
+the identity, element-wise, results in a diagonal matrix, meaning we are only left with correlation information between the same 
+two frequencies. Because we disregard information from all other frequency combinations in this case, we do a poor job 
+suppressing the foreground. But because we flattened the eigenspectrum, we also avoid signal loss.
+
+Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there 
+are many options for estimating a covariance matrix, and some may be more effective than others based on the spectral nature 
+of the components in a dataset. One may imagine a situation where a particular systematic is contained to an isolated 
+frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
+\hat{\textbf{C}}$ would be an effective way of removing this contamination.
+
+In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without 
+removing the underlying cosmological signal. As we investigated however, there are trade-offs between the weighting method 
+used, its foreground-removal effectiveness, and the amount of resulting signal loss.
 
@@
 
-Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate confidence intervals for our measurements.
-Two popular ways of empirically calculating errors on a power spectrum measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's system temperature and observational parameters.
-In a perfect world, both methods would match up.
-However, in practice the two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform weightings.
-
-For PAPER's analysis, we choose to compute error bars on our measurements that have been derived from its inherent variance.
-A common technique used to do this is bootstrapping.
-For pedagogical purposes, we first define the technique of bootstrapping and then illustrate some of its pitfalls through toy models.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, measurements (like power spectra) can be made from different samples of data.
-Averaging each sample set gives us a realization of the (power spectrum) answer.
-Realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Hence, through the process of resampling and averaging along different axes, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements.
+Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
+confidence intervals for our measurements. Two popular ways of empirically calculating errors on a power spectrum 
+measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's 
+system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
+two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform 
+weightings.
+
+For PAPER's analysis, we choose to compute error bars on our measurements that have been derived from its inherent 
+variance. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
+bootstrapping and then illustrate some of its pitfalls through toy models.
+
+Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
+spectra) can be made from different samples of data. Averaging each sample set gives us a realization of the (power spectrum) 
+answer. Realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common 
+between them. Hence, through the process of resampling and averaging along different axes, we can estimate error bars for 
+our results which represent the underlying distribution of values that are allowed by our measurements.
 
 Suppose we have $N$ different measurements targeting the same quantity ($N$ power spectrum measurements). 
-Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
-Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (every $N$th slot is filled randomly for each bootstrap).
-Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
-The error (on the mean) is then computed as the standard deviation across all bootstraps.
-
-We must be careful in distinguishing $N_{boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
-In the toy models presented in this section, $N_{boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{boot}$.
-It is the value of $N$ that we must be careful in setting, as described in the rest of this section.
+Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
+of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
+from the original set of measurements with replacement (every $N$th slot is filled randomly for each bootstrap). Next we take 
+the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
+here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one). The error (on 
+the mean) is then computed as the standard deviation across all bootstraps.
+
+We must be careful in distinguishing $N_{boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
+values, that comprise a bootstrap. In the toy models presented in this section, $N_{boot}$ is typically large, and the standard 
+deviation across bootstraps (the error we are computing) converges for large $N_{boot}$. It is the value of $N$ that we must be 
+careful in setting, as described in the rest of this section.
 
 For our toy model, suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean). 
-This could represent $1000$ power spectrum measurements, for which we are interested in its error.
-We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-We next form $500$ bootstraps ($N_{boot} = 500$).
-To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
-The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
-This error is indicated by the grey star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data.
-If, for example, a dataset has many repeated values inside it, this would be reflected in each bootstrap.
-The same value would be present multiple times within a bootstrap and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of itself.
-Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates errors.
-The use of a fringe-rate filter, which averages data in time to increase sensitivity, is one example which leads to a reduction in the number of independent samples, creating a situation in which errors can be under-estimated.
-We will now show this effect using our toy model.
-
-Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of independent data samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$.
-This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both under-estimate the error by drawing too many or over-estimate it by drawing too few.
-However, if we know that we have $100$ independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction as expected.
-
-This example highlights the importance of understanding how analysis techniques (e.g.
-fringe-rate filtering) can affect a common statistical procedure like bootstrapping.
-Bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
-For example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the number of averages performed.
-Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
-Hence, we do not recommend bootstrapping unless the number of independent samples along the axis that is being re-sampled is well-determined.
+This could represent $1000$ power spectrum measurements, for which we are interested in its error. We predict that the error 
+on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+We next form $500$ bootstraps ($N_{boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
+original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
+estimate for our dataset. This error is indicated by the grey star in Figure \ref{fig:toy_error1} and matches our theoretical 
+prediction (green).
+
+One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
+values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
+and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
+itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates 
+errors. The use of a fringe-rate filter, which averages data in time to increase sensitivity, is one example which leads to a 
+reduction in the number of independent samples, creating a situation in which errors can be under-estimated. We will now show 
+this effect using our toy model.
+
+Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of 
+independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
+earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$. This occurs 
+because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
+in all bootstraps, leading to less variation between the bootstraps. In fact, the error derived from bootstrapping is a strong 
+function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
+under-estimate the error by drawing too many or over-estimate it by drawing too few. However, if we know that we have $100$ 
+independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction 
+as expected.
+
+This example highlights the importance of understanding how analysis techniques (e.g. fringe-rate filtering) can affect a 
+common statistical procedure like bootstrapping. Bootstrapping as a means of estimating power spectrum errors from real 
+fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task. For 
+example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the 
+number of averages performed. Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-
+trivial with a more complicated convolution function that has long tails. Hence, we do not recommend bootstrapping unless the 
+number of independent samples along the axis that is being re-sampled is well-determined.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
-	\caption{Error estimation produced by bootstrapping as a function of the number of elements drawn per bootstrap when sampling with replacement.
-The star represents the standard deviation of $500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
-The estimated errors match up with the theoretical prediction only at $N=100$.}
+	\caption{Error estimation produced by bootstrapping as a function of the number of elements drawn per bootstrap when 
+sampling with replacement. The star represents the standard deviation of $500$ bootstraps, each created by drawing $1000$ 
+elements (with replacement) from a length $1000$ array of a Gaussian random signal. The black points correspond to time-
+averaged data (correlated data) which has $100$ independent samples. They illustrate how errors can be underestimated if 
+drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
+prediction only at $N=100$.}
 	\label{fig:toy_error1}
@@
 
-We will now discuss a second subtle feature of bootstrapping that fails to maximize the sensitivity of a dataset.
-Suppose we have $5$ independent measurements of the sky (from $5$ different baselines, for example).
-A bootstrap then consists of $5$ measurements that are drawn randomly with replacement from the original set.
-If all $5$ spaces are filled randomly, there is a high probability that some measurements will be repeated in the bootstrap because they are drawn more than once.
-The bootstrap may therefore consist of only $3$ or $4$ independent measurements --- a number smaller than the total number of samples.
-In fact, the probability of drawing $5$ completely independent measurements is less than $4\%$.
-
-In order to maximize sensitivity, we desire as many independent samples as possible. However, solely using all $5$ independent measurements does not allow variation between bootstraps.
-
-Therefore, we use a slightly modified bootstrapping method.
-For each bootstrap, we draw $N-1=4$ samples without replacement and draw the last slot randomly with replacement.
-In doing so there is a small chance a bootstrap will consist of $5$ independent measurements, but even with $4$ our sensitivity is nearly maximized.
-%One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
-However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
-
-In Figure \ref{fig:toy_error2} we compare the two methods of bootstrapping: sampling all elements randomly (black points) versus sampling just the final element randomly (grey points).
-The two converge for datasets with small numbers of elements, when filling a few spots randomly is nearly the same as filling only the last spot randomly.
-However, there is also increased scatter in this regime due to small number statistics.
-
-The difference between the two methods is most pronounced for datasets with large numbers of elements.
-As a dataset grows in size, it becomes increasingly rare to draw entirely independent samples, and thus the benefit of ensuring, say, $999$ independent samples out of $1000$ is most noticeable.
-The more elements in our dataset, the more sensitivity we can gain by mandating that most of our measurements are independent ones.
-An analog for the y-axis in Figure \ref{fig:toy_error2} is therefore the sensitivity of a final power spectrum measurement.
-
-In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset.
-However, we have illustrated two situations in which bootstrapping can lead to under-estimated errors and sensitivities.
-First, we have shown that bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample.
-Estimated errors can drop to arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements.
-We have also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible.
-While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain analysis choices have compromised the method and whether a variation of traditional re-sampling could be preferred instead.
+We will now discuss a second subtle feature of bootstrapping that fails to maximize the sensitivity of a dataset. Suppose we 
+have $5$ independent measurements of the sky (from $5$ different baselines, for example). A bootstrap then consists of $5$ 
+measurements that are drawn randomly with replacement from the original set. If all $5$ spaces are filled randomly, there is a 
+high probability that some measurements will be repeated in the bootstrap because they are drawn more than once. The 
+bootstrap may therefore consist of only $3$ or $4$ independent measurements --- a number smaller than the total number of 
+samples. In fact, the probability of drawing $5$ completely independent measurements is less than $4\%$.
+
+In order to maximize sensitivity, we desire as many independent samples as possible. However, solely using all $5$ 
+independent measurements does not allow variation between bootstraps.
+
+Therefore, we use a slightly modified bootstrapping method. For each bootstrap, we draw $N-1=4$ samples without 
+replacement and draw the last slot randomly with replacement. In doing so there is a small chance a bootstrap will consist of 
+$5$ independent measurements, but even with $4$ our sensitivity is nearly maximized. %One may wonder whether this 
+change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap. However, as 
+long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the 
+inherent variability in a dataset.
+
+In Figure \ref{fig:toy_error2} we compare the two methods of bootstrapping: sampling all elements randomly (black points) 
+versus sampling just the final element randomly (grey points). The two converge for datasets with small numbers of elements, 
+when filling a few spots randomly is nearly the same as filling only the last spot randomly. However, there is also increased 
+scatter in this regime due to small number statistics.
+
+The difference between the two methods is most pronounced for datasets with large numbers of elements. As a dataset grows 
+in size, it becomes increasingly rare to draw entirely independent samples, and thus the benefit of ensuring, say, $999$ 
+independent samples out of $1000$ is most noticeable. The more elements in our dataset, the more sensitivity we can gain by 
+mandating that most of our measurements are independent ones. An analog for the y-axis in Figure \ref{fig:toy_error2} is 
+therefore the sensitivity of a final power spectrum measurement.
+
+In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset. However, we have 
+illustrated two situations in which bootstrapping can lead to under-estimated errors and sensitivities. First, we have shown that 
+bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample. Estimated errors can drop to 
+arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements. We have 
+also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible. While 
+bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain 
+analysis choices have compromised the method and whether a variation of traditional re-sampling could be preferred instead.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
-	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a dataset (i.e.
-if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$).
-A fraction of $1.0$ means that all elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
+	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
+dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
+elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
+of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
 Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
-The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.} %The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
+The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.}
+%The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
 	\label{fig:toy_error2}
@@
 
-In a $21$ cm power spectrum, detections could be the EoR signal, but they could also (and unfortunately more likely) be attributed to other sources of bias.
-Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of future $21$ cm data analyses.
-In this section we will discuss possible sources of bias in a measurement, as well as techniques that can help mitigate their effects.
-We will also present a series of tests in a pedagogical fashion which we suggest be used to help evaluate deep limits and/or detections.
+In a $21$ cm power spectrum, detections could be the EoR signal, but they could also (and unfortunately more likely) be 
+attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
+future $21$ cm data analyses. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
+that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
+help evaluate deep limits and/or detections.
 
@@
 
-Foreground bias is perhaps one of the main factors limiting $21$ cm results.
-Foreground signals lie $\sim4$-$5$ orders of magnitude above the cosmological signal.
-Though there are many techniques proposed for removing foregrounds, most experiments remain ultimately limited by residuals rather than noise.
-
-Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or $k$ modes.
-For a particular baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between two antennas in a baseline.
-For longer baselines, this value increases, producing what is known as ``the wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; \citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}).
-The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is proportional to $k_{\parallel}$).
-Properties of the wedge can be used to isolate and remove foregrounds, as done by P64, \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
-
-However, this isolation is not perfect.
-In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond the length of a baseline are often still contaminated at a low level.
-This leakage, especially at low $k$'s, can be attributed to convolution kernels associated with Fourier-transforming visibilities into delay-space.
-In other words, smooth-spectrum foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
-
-There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from spreading to high $k$ values.
-For example, narrow window functions can be used to minimize the covariance of a particular $k$ value with other ones (\citealt{liu_et_al2014b}).
-In other words, one can construct an estimator using OQE that forces a window function to have a minimum response to low $k$ values.
-The window function used in P64 is constructed in such a way, specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
-Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
-
-Confirming foreground detections at higher $k$'s is more difficult.
-In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
-
-In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is multiplied by itself.
-Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise.
-We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating longer, using more baselines, etc.
-However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}.
-If both copies of $\textbf{x}$ come from the same baseline and time, it can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument.
-One way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days.
-This ensures that the two quantities that go into a measurement have separate noises that don't correlate with each other.
-
-Another type of noise bias can stem from the spurious cross-coupling of signals between antennas.
-This excess is known as instrumental crosstalk and is an inadvertent correlation between two independent measurements via a coupled signal path.
-Crosstalk appears as a constant phase bias in time in visibilities, and it varies slowly compared to the typical fringe-rates of sources.
-Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters.
-However, there remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any suppression techniques.
+Foreground bias is perhaps one of the main factors limiting $21$ cm results. Foreground signals lie $\sim4$-$5$ orders of 
+magnitude above the cosmological signal. Though there are many techniques proposed for removing foregrounds, most 
+experiments remain ultimately limited by residuals rather than noise.
+
+Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or $k$ modes. For a particular 
+baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between two 
+antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
+wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; 
+\citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}). The wedge describes a region in $k$-
+space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
+proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and remove foregrounds, as done by P64, 
+\citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
+
+However, this isolation is not perfect.  In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond 
+the length of a baseline are often still contaminated at a low level. This leakage, especially at low $k$'s, can be attributed to 
+convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
+foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the 
+antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
+
+There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from 
+spreading to high $k$ values. For example, narrow window functions can be used to minimize the covariance of a particular 
+$k$ value with other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
+window function to have a minimum response to low $k$ values. The window function used in P64 is constructed in such a way, 
+specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}). 
+Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since 
+narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
+
+Confirming foreground detections at higher $k$'s is more difficult. In the next section (Section \ref{sec:JackknifeOverview}), we 
+will present some tests that can help distinguish these excesses from that of EoR.
+
+In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is 
+multiplied by itself. Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise. 
+We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating 
+longer, using more baselines, etc. However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by 
+the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}. If both copies of $\textbf{x}$ come from the same baseline and time, it 
+can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument. One 
+way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days. This ensures that the 
+two quantities that go into a measurement have separate noises that don't correlate with each other.
+
+Another type of noise bias can stem from the spurious cross-coupling of signals between antennas. This excess is known as 
+instrumental crosstalk and is an inadvertent correlation between two independent measurements via a coupled signal path. 
+Crosstalk appears as a constant phase bias in time in visibilities, and it varies slowly compared to the typical fringe-rates of 
+sources. Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters. However, there 
+remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any 
+suppression techniques.
 
@@
 
-We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful jackknife tests.
-Again, we first approach this topic pedagogically as an introduction to the related PAPER discussion in Section \ref{sec:Bias}.
-
-The jackknife is a resampling technique in which a statistic (i.e.
-power spectrum) is computed in subsets of the data.
-These subsets are then compared to reveal systematics.
-In this section we define two main tests --- the null test and the traditional jackknife --- and explain how a power spectrum detection must pass each.
-We then highlight how these tests can be used to help distinguish between different sources of bias.
+We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful 
+jackknife tests. Again, we first approach this topic pedagogically as an introduction to the related PAPER discussion in Section 
+\ref{sec:Bias}.
+
+The jackknife is a resampling technique in which a statistic (i.e. power spectrum) is computed in subsets of the data. These 
+subsets are then compared to reveal systematics. In this section we define two main tests --- the null test and the traditional 
+jackknife --- and explain how a power spectrum detection must pass each. We then highlight how these tests can be used to 
+help distinguish between different sources of bias.
 
 \begin{itemize}
-\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to investigate underlying systematics.
-Several null tests on data are described in \citet{keating_et_al2016}.
-For example, one can divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second.
-Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR.
-The resulting power spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs from one of the data subsets to the other (i.e.
-doesn't get subtracted perfectly).
-\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill confidence in a final result.
-A stable result must be steadfast throughout all jackknives no matter how the data is sliced.
-Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new power spectrum every time as a day of data is removed, or a baseline is removed.
-This type of jackknife would reveal bias present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
+\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
+investigate underlying systematics. Several null tests on data are described in \citet{keating_et_al2016}. For example, one can 
+divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
+Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR. The resulting power 
+spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
+from one of the data subsets to the other (i.e. doesn't get subtracted perfectly). 
+\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill 
+confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
+Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new 
+power spectrum every time as a day of data is removed, or a baseline is removed. This type of jackknife would reveal bias 
+present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
 \end{itemize}
 
-While the null test hunts for deviations from thermal noise and the jackknife tests for deviations in subsamples, they are both closely related.
-We can highlight the connection between the two using a toy model dataset.
-
-Suppose we have two measurements (for example, from two baselines), $\textbf{x}_{a}$ and $\textbf{x}_{b}$.
-The measurements have dimensions of $200$ time integrations and $20$ frequency channels.
-They each have separate thermal noises constructed as a Gaussian random signal for each, and identical EoR signals.
-
-To mimic the presence of a systematic in part of the measurement, we add a toy sinusoid foreground, similar to the one used in Section \ref{sec:toymodel}, to the first $100$ time integrations of both measurements.
-This represents a foreground signal present in, for example, the first half of the LST range used for analysis, but not the second half.
-Mathematically, if  $\textbf{n}$ is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
+While the null test hunts for deviations from thermal noise and the jackknife tests for deviations in subsamples, they are both 
+closely related. We can highlight the connection between the two using a toy model dataset.
+
+Suppose we have two measurements (for example, from two baselines), $\textbf{x}_{a}$ and $\textbf{x}_{b}$. The 
+measurements have dimensions of $200$ time integrations and $20$ frequency channels. They each have separate thermal 
+noises constructed as a Gaussian random signal for each, and identical EoR signals.
+
+To mimic the presence of a systematic in part of the measurement, we add a toy sinusoid foreground, similar to the one used in 
+Section \ref{sec:toymodel}, to the first $100$ time integrations of both measurements. This represents a foreground signal 
+present in, for example, the first half of the LST range used for analysis, but not the second half. Mathematically, if  $\textbf{n}$ 
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-
+multiplied to form power spectra) can be written as:
 
@@
 
-\noindent The two jackknife samples are $\textbf{x}_{1}$ and $\textbf{x}_{2}$, representing jackknives in time. These can be written (for both measurements $a$ and $b$) as:
+\noindent The two jackknife samples are $\textbf{x}_{1}$ and $\textbf{x}_{2}$, representing jackknives in time. These can be 
+written (for both measurements $a$ and $b$) as:
 
@@
 
-We do not perform a time-average or apply a fringe-rate filter to this toy model, since we are interested only in what jackknife tests can tell us about biases.
-For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to avoid signal loss.
-
-We form $3$ different power spectrum estimates shown in Figure \ref{fig:toy_bias1}.
-The first is a null test where we subtract $\textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$.
-This is equivalent to splitting up a full dataset along an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
-We cross-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve).
-The second estimate, shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{fg}$ in Equations \ref{eq:bias1} and \ref{eq:bias2}).
-Finally, we also show the noise power spectrum (green).
-
-From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of noise.
-This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
+We do not perform a time-average or apply a fringe-rate filter to this toy model, since we are interested only in what jackknife 
+tests can tell us about biases. For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to 
+avoid signal loss.
+
+We form $3$ different power spectrum estimates shown in Figure \ref{fig:toy_bias1}. The first is a null test where we subtract $
+\textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$. This is equivalent to splitting up a full dataset along 
+an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both. We cross-
+multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve). The second estimate, 
+shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{fg}$ in Equations \ref{eq:bias1} 
+and \ref{eq:bias2}). Finally, we also show the noise power spectrum (green).
+
+From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of 
+noise. This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
-	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without the foreground systematic (red), and noise alone (green).
-Because the first null test is not consistent with noise, it suggests the presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$.
-Null tests of clean measurements should be consistent with thermal noise.}
+	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
+the foreground systematic (red), and noise alone (green). Because the first null test is not consistent with noise, it suggests the 
+presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
+with thermal noise.}
 	\label{fig:toy_bias1}
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
-	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model.
-They suggest the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses.
-Clean measurements should remain consistent despite the jackknife taken.}
+	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
+the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
+measurements should remain consistent despite the jackknife taken.}
 	\label{fig:toy_bias2}
@@
 
-While the null test is useful for testing noise properties and the uniformity of a dataset, jackknives are useful in pinpointing which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $\textbf{x}_{1}$ (Figure \ref{fig:toy_bias2}).
-If foreground or noise biases exist in a dataset, jackknives can tease them out and provide insight into possible sources.
-For example, if jackknives along the time-axis reveal a bias present at a certain LST, a likely explanation would be excess foreground emission from a radio source in the sky at that time.
-A jackknife test involving data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed with the filter, or if similar-shaped detections in both power spectra suggest otherwise.
-There are many other jackknife axes of which we will not go into detail here, including baseline, frequency, and polarization.
-Ultimately, an EoR detection should persist through them all and a clean measurement should exhibit noise-like null spectra.
-
-In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum detection.
-In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to prove that our excesses are not EoR and to identify their likely cause.
+While the null test is useful for testing noise properties and the uniformity of a dataset, jackknives are useful in pinpointing 
+which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $
+\textbf{x}_{1}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
+provide insight into possible sources. For example, if jackknives along the time-axis reveal a bias present at a certain LST, a 
+likely explanation would be excess foreground emission from a radio source in the sky at that time. A jackknife test involving 
+data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed 
+with the filter, or if similar-shaped detections in both power spectra suggest otherwise. There are many other jackknife axes of 
+which we will not go into detail here, including baseline, frequency, and polarization. Ultimately, an EoR detection should persist 
+through them all and a clean measurement should exhibit noise-like null spectra.
+
+In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum 
+detection. In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to prove that our 
+excesses are not EoR and to identify their likely cause.
 
@@
 
-In the previous sections we have discussed three overarching $21$ cm power spectrum themes --- signal loss, error estimation, and bias.
-Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of a power spectrum result.
-
-We now present a case study of these same three themes using data from the PAPER experiment.
-We use the intuition developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in P64 and obtain a revised power spectrum estimate.
-
-As a brief review, PAPER is a dedicated $21$ cm experiment located in the Karoo Desert in South Africa.
-The PAPER-64 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout.
-For our case study, we focus solely on Stokes I estimated data (\citealt{moore_et_al2013}) from PAPER's $30$ m East/West baselines (Figure \ref{fig:ant_layout}).
-For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we refer the reader to \citet{parsons_et_al2010} and P64.
+In the previous sections we have discussed three overarching $21$ cm power spectrum themes --- signal loss, error estimation, 
+and bias. Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of 
+a power spectrum result.
+
+We now present a case study of these same three themes using data from the PAPER experiment. We use the intuition 
+developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in 
+P64 and obtain a revised power spectrum estimate.
+
+As a brief review, PAPER is a dedicated $21$ cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
+configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
+focus solely on Stokes I estimated data (\citealt{moore_et_al2013}) from PAPER's $30$ m East/West baselines (Figure 
+\ref{fig:ant_layout}). For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we 
+refer the reader to \citet{parsons_et_al2010} and P64.
 
@@
 	\includegraphics[width=\columnwidth]{plots/ant_layout.png}
-	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this paper (such as baseline 49\_41).}
+	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
+paper (such as baseline 49\_41).}
 	\label{fig:ant_layout}
@@
 
-The previously best published $21$ cm upper limit result from P64 uses $124$ nights of data to place a $2\sigma$ upper limit on $\Delta^{2}(k)$, defined as
+The previously best published $21$ cm upper limit result from P64 uses $124$ nights of data to place a $2\sigma$ upper limit 
+on $\Delta^{2}(k)$, defined as
 
@@
 
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-%The revision of this limit stems mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we address in the following sections.
-
-For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA range of $0$-$8.6$ hours).
-All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ MHz ($20$ channels), identical to the analysis in P64.
-We note that, besides using only $1$ baseline type instead of the $3$ in P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter.
-In P64, the applied filter was degraded by widening it in fringe-rate space.
-This was chosen in order to increase the number of independent modes and reduce signal loss, though as we will see this signal loss was still under-estimated.
-With the development of a new, robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity.
-This filter is computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band.
-The filter in both the fringe-rate domain and time domain is shown in Figure \ref{fig:frp}.
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$. %The revision of this limit stems 
+mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we 
+address in the following sections.
+
+For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
+range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
+MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only $1$ baseline type instead of the $3$ in 
+P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter. In P64, the 
+applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
+modes and reduce signal loss, though as we will see this signal loss was still under-estimated. With the development of a new, 
+robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
+computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band. The filter in both the fringe-rate 
+domain and time domain is shown in Figure \ref{fig:frp}.
 
@@
 	\includegraphics[width=\columnwidth]{plots/frp.png}
-	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and Stokes I polarization beam.
-Bottom: the time-domain convolution kernel corresponding to the top panel.
-Real and imaginary components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black.
-The fringe-rate filter acts as an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
+	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
+Stokes I polarization beam. Bottom: the time-domain convolution kernel corresponding to the top panel. Real and imaginary 
+components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black. The fringe-rate filter acts as 
+an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
 	\label{fig:frp}
@@
 
-In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data itself.
-Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify the amount of signal loss accompanying a weighting scheme.
-In particular, we highlight major differences from the signal loss computation used in P64, which previously underestimated losses.
+In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data 
+itself. Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify 
+the amount of signal loss accompanying a weighting scheme. In particular, we highlight major differences from the signal loss 
+computation used in P64, which previously underestimated losses.
 
@@
 
-To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ cm signal visibilities.
-Here we use the same method used in P64, where mock Gaussian noise visibilities (mock EoR signals) are filtered in fringe-rate space to retain only ``sky-like" time-modes.
-This signal is then added to the data.
-\footnote{One specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is applied to the data.
-Previously, the addition was done after that final fringe-rate filter step.
-This change results in an increased estimate of signal loss, likely due to the use of the fringe-rate filter as a simulator.
-Whether the loss would be estimated at the same level if different $21$ cm simulations were used remains an open question.}
-
-Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}$ to be the data plus the EoR signal:
+To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
+cm signal visibilities. Here we use the same method used in P64, where mock Gaussian noise visibilities (mock EoR signals) 
+are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.  \footnote{One 
+specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
+applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
+estimate of signal loss, likely due to the use of the fringe-rate filter as a simulator. Whether the loss would be estimated at the 
+same level if different $21$ cm simulations were used remains an open question.}
+
+Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}
+$ to be the data plus the EoR signal:
 
@@
 
-We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power spectrum according to OQE formalism.
-We investigate this by comparing two quantities we call the input power spectrum and output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
+We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
+spectrum according to OQE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
+output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
 
@@
 P_{out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
+&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
 
-$P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal.
-$P_{out}$ is the weighted power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data.
-Comparing the two quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
-
-It is noted that the output power spectrum is comprised of two terms: the weighted power spectrum associated with \textbf{r}, and that of data \textbf{x} alone.
-
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely $P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$.
-In short, this naive expression fails to include correlations between the EoR signal and data, which emerges as statistical noise that is added to the estimate, decreasing the value of $P_{out}$.
-Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
+$P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal. $P_{out}$ is the weighted 
+power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data. Comparing the two 
+quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
+
+It is noted that the output power spectrum is comprised of two terms: the weighted power spectrum associated with \textbf{r}, 
+and that of data \textbf{x} alone.
+
+One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
+$P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
+expression fails to include correlations between the EoR signal and data, which emerges as statistical noise that is added to the 
+estimate, decreasing the value of $P_{out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
 
@@
 \label{eq:crossterm}
-P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
+P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
 
-We see that $P_{out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only $\textbf{x}$ are small, yields:
+We see that $P_{out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only 
+$\textbf{x}$ are small, yields:
 
@@
 \label{eq:pout_expand}
-P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + 
+\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
 &+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
@@
 
-We see that our naive expression for $P_{out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two additional terms.
-An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be zero, since foregrounds and the cosmological signal are statistically unrelated.
-In P64, this assumption is used, and the first term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
-
-However, deeper investigations of these terms reveal that they contain non-negligible power.
-In fact, foreground modes and signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $\textbf{C}_{r}$.
-Mathematically, the covariance of the data plus EoR is:
+We see that our naive expression for $P_{out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
+additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
+zero, since foregrounds and the cosmological signal are statistically unrelated. In P64, this assumption is used, and the first 
+term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
+
+However, deeper investigations of these terms reveal that they contain non-negligible power. In fact, foreground modes and 
+signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $
+\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:
 
@@
 \textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle \\
-&=& \langle \textbf{xx}^{\dagger} \rangle + \langle \textbf{xe}^{\dagger} \rangle + \langle \textbf{ex}^{\dagger} \rangle + \langle \textbf{ee}^{\dagger} \rangle,
+&=& \langle \textbf{xx}^{\dagger} \rangle + \langle \textbf{xe}^{\dagger} \rangle + \langle \textbf{ex}^{\dagger} \rangle + \langle 
+\textbf{ee}^{\dagger} \rangle,
 \end{eqnarray}
 
-\noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices.
-The middle two terms, however, have a larger amount of power in their off-diagonal terms relative to their diagonal elements, since $\textbf{e}$ and $\textbf{x}$ are statistically unrelated.
-Upon inversion, these off-diagonal terms become negative, driving the cross-terms in Equation \ref{eq:pout_expand} to have negative power.
-\cc{someone help me write this more elegantly...}This effect is explained in more depth in \citet{switzer_et_al2015}.
-
-The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss.
-Therefore, in our revised signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
-
-The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an input power spectrum distribution into an output distribution.
-By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss transfer function and detail two different computations used to translate our power spectrum result into one viewed through a signal loss lens.
-We showcase two methods...
-\cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
+\noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices. The middle 
+two terms, however, have a larger amount of power in their off-diagonal terms relative to their diagonal elements, since $
+\textbf{e}$ and $\textbf{x}$ are statistically unrelated. Upon inversion, these off-diagonal terms become negative, driving the 
+cross-terms in Equation \ref{eq:pout_expand} to have negative power. \cc{someone help me write this more elegantly...}This 
+effect is explained in more depth in \citet{switzer_et_al2015}.
+
+The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss. Therefore, in our revised 
+signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
+weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
+
+The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function 
+which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an input power spectrum distribution into an output 
+distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
+distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss 
+transfer function and detail two different computations used to translate our power spectrum result into one viewed through a 
+signal loss lens. We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also 
+state that they yield similar results...}
 
@@
 
-We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset.
-While our methodology outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss.
-With this weighting, our expressions for $P_{in}$ and $P_{out}$ become:
+We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset. While our methodology 
+outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
+($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
+expressions for $P_{in}$ and $P_{out}$ become:
 
@@
 P_{in,\alpha} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x}
+P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}
+\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
 
-Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with the unweighted case ($\textbf{R} = \textbf{I}$, right plot).
-The figures depict a kernel density estimation of our input to output power spectrum transfer function.
-To sample the distribution, we run $40$ total injection levels, where the amplitude of \textbf{e} is increased in even increments on a lin-log grid and ranges from $P_{in} \sim -10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$.
-For each injection, we perform $20$ bootstraps over baselines, as explained in Section \ref{sec:Boot}, resulting in a total of $800$ data points on our $P_{in}$ vs.
-$P_{out}$ grid.
-We have verified that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
-
-The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the unweighted case ($\textbf{R} = \textbf{I}$).
-Therefore, it is worth thinking about the spread, or scatter, around this black line that we see in the right plot (the colored `heat-map').
-One might imagine that there should be one true $P_{out}$ value for every $P_{in}$, implying one well-determined signal loss factor for every data value.
-Focusing on the unweighted case alone, the scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$.
-Since we draw different random $\textbf{e}$'s for every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{out}$ values that results from the same $P_{in}$.
-This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of the spread in the weighted case (left plot).
-
-There is a second component of scatter that is less intuitive, only applies (at a low level) to the weighted case, and represents intrinsic scatter in signal loss.
-The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
-For example, if we are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
-An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
-On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of $P_{in}$ values.
-We correct for this, as explained later in this section.
-
-Finally, the solid grey horizontal lines in Figure \ref{fig:sigloss_transfercurve} mark the peak of the data distribution $\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted cases.
-One can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$ using the transfer curve for the inverse covariance weighted case, implying a signal loss factor of $\sim1000$.
+Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted 
+case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with the unweighted case ($\textbf{R} = \textbf{I}$, right plot). The figures depict a 
+kernel density estimation of our input to output power spectrum transfer function. To sample the distribution, we run $40$ total 
+injection levels, where the amplitude of \textbf{e} is increased in even increments on a lin-log grid and ranges from $P_{in} \sim 
+-10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is 
+negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$. For each injection, we perform $20$ 
+bootstraps over baselines, as explained in Section \ref{sec:Boot}, resulting in a total of $800$ data points on our $P_{in}$ vs. 
+$P_{out}$ grid. We have verified that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all 
+the values into positive ones to increase our signal-to-noise.
+
+The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
+unweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
+we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $P_{out}$ value for every 
+$P_{in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
+scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
+\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
+every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{out}$ values that results from the same 
+$P_{in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
+the spread in the weighted case (left plot).
+
+There is a second component of scatter that is less intuitive, only applies (at a low level) to the weighted case, and represents 
+intrinsic scatter in signal loss. The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to 
+look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for. For example, if we 
+are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$. An 
+empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal. On the other hand, the 
+less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result. The intrinsic scatter we can get is not a 
+dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of 
+$P_{in}$ values. We correct for this, as explained later in this section.
+
+Finally, the solid grey horizontal lines in Figure \ref{fig:sigloss_transfercurve} mark the peak of the data distribution $
+\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted 
+cases. One can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
+value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$ using the transfer curve for the inverse covariance weighted case, implying a 
+signal loss factor of $\sim1000$.
 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Kernel density estimations of the power spectrum transfer functions are shown as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
-The solid black diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data distribution.
-From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does not exhibit loss.
-The peculiar feature of `signal gain' at low injection levels is explained in the text.}
+	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations 
+\eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
+heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
+diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data 
+distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
+for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
+not exhibit loss. The peculiar feature of `signal gain' at low injection levels is explained in the text.}
 	\label{fig:sigloss_transfercurve}
@@
 
-One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have signal gain ($P_{out} > P_{in}$).
-This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
-As $\textbf{e}$ increases, we move into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is large enough to be destroyed if weighting the data using itself.
-Although we only show figures for one $k$ value, we note that the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
-
-We now explain how we use the transfer curves to map our data (a distribution along $P_{out}$) to a signal-loss corrected distribution (along $P_{in}$) that takes into account the range of signal loss that can be associated for a particular $P_{out}$ value.
+One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have 
+signal gain ($P_{out} > P_{in}$). This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}
+$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. As $\textbf{e}$ increases, we move 
+into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is 
+large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
+the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
+
+We now explain how we use the transfer curves to map our data (a distribution along $P_{out}$) to a signal-loss corrected 
+distribution (along $P_{in}$) that takes into account the range of signal loss that can be associated for a particular $P_{out}$ 
+value.
 
@@
 
-Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), defined as:
+Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), defined 
+as:
 
@@
 
-\noindent we fit an $8$th order polynomial to each, representing mean signal loss functions.
-We then account for the second component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each $P_{in}$ value:
+\noindent we fit an $8$th order polynomial to each, representing mean signal loss functions. We then account for the second 
+component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each 
+$P_{in}$ value:
 
@@
 
-In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
-
-Equipped with our new signal loss curves, we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ columns, treating positive and negative halves of the data distribution separately:
+In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be 
+seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
+
+Equipped with our new signal loss curves, we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ 
+columns, treating positive and negative halves of the data distribution separately:
 
@@
 
-We note that for PAPER-64, depending on the $k$-value, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power spectrum values (signifying detections of power) and sometimes centered around zero, representing measurements that are consistent with zero.
+We note that for PAPER-64, depending on the $k$-value, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power 
+spectrum values (signifying detections of power) and sometimes centered around zero, representing measurements that are 
+consistent with zero.
 
@@
 
-This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals (recall that the spread in these probability density functions mostly comes from bootstrapping the data).
+This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute 
+power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals (recall 
+that the spread in these probability density functions mostly comes from bootstrapping the data).
 
@@
 
-To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting.
-The blue dashed line represents the unweighted power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case).
-The black and grey points are positive and negative power spectrum values plotted with $2\sigma$ error bars.
-Prior to signal loss correction, it is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve).
+To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
+loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
+power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
+grey points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss correction, it 
+is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
 Post-correction, the power spectrum values blow up to be higher than both the theory and unweighted power spectrum.
 
-Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of independent samples in PAPER-64.
-PAPER-64 only has $\sim$$8$ independent modes after fringe-rate filtering while our power spectrum bandwidth has $21$ channels.
-Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe real fluctuations beyond the first eight.
-Hence, there is a substantial down-weighting of other modes, a large loss that the signal loss transfer function captures and corrects for.
-We elaborate on this point in the next section, as well as investigate alternate weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
+Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of 
+independent samples in PAPER-64. PAPER-64 only has $\sim$$8$ independent modes after fringe-rate filtering while our 
+power spectrum bandwidth has $21$ channels. Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe 
+real fluctuations beyond the first eight. Hence, there is a substantial down-weighting of other modes, a large loss that the signal 
+loss transfer function captures and corrects for. We elaborate on this point in the next section, as well as investigate alternate 
+weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-
+weighting contaminants with minimizing the loss of EoR.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, with $2\sigma$ error bars) before signal loss correction (left) and after (right).
-The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction based on observational parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, 
+with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
+spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
+parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
 	\label{fig:ps2_data}
@@
 
-With a signal loss formalism established (Method \#1, for the rest of this paper), we now have the capability of experimenting with different weighting options for $\textbf{R}$.
-Our goal here is to choose a weighting method that successfully down-weights foregrounds and systematics in our data without generating large amounts of signal loss.
-We have found that the balance between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
-
-We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e.
-flattening out part of the eigenspectrum) can help minimize signal loss.
-We experiment with this idea on PAPER-64 data, dialing the number of modes down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse covariance weighting of our $21$ channels).
-The power spectrum results for one $k$ value, both before and after signal loss correction, are shown in Figure \ref{fig:sigloss_modeloop}.
-We see that the amount of signal loss increases as weighting becomes more aggressive (grey curve).
-In other words, more `weak' (EoR-dominated) fluctuations are being overfit and subtracted as more modes are down-weighted.
-We also find that the power spectrum upper limit, post signal loss correction, increases with the number of down-weighted modes (black curve).
-As discussed previously, we are limited in our power spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data \cc{elaborate?}.
-
-Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting is beneficial compared to not weighting (blue dashed line).
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs when only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not significant.
+With a signal loss formalism established (Method \#1, for the rest of this paper), we now have the capability of experimenting 
+with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
+foregrounds and systematics in our data without generating large amounts of signal loss. We have found that the balance 
+between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
+
+We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
+eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
+down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
+covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
+correction, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
+becomes more aggressive (grey curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
+subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss correction, 
+increases with the number of down-weighted modes (black curve). As discussed previously, we are limited in our power 
+spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass 
+the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data \cc{elaborate?}.
+
+Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
+is beneficial compared to not weighting (blue dashed line). We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not 
+significant.
 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data.
-Values are shown before (grey) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that are down-weighted.
-This regularization knob is tuned from $0$ modes (i.e.
-unweighted) to $21$ modes (i.e.
-full inverse covariance weighting).
-Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting.
-Also plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance weighted case (red), and added-identity case (cyan).
-All three regularizations shown (black, red, cyan) perform similarly (when $\sim$$3$ modes are down-weighted for the black curve).
-Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted as solid green.}
+	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
+are shown before (grey) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
+are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
+covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
+plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
+weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
+$\sim$$3$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
+as solid green.}
 	\label{fig:sigloss_modeloop}
@@
 
-In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} which denote power spectrum values, post-signal loss correction, for two other regularization schemes.
-We multiply an identity matrix element-wise to $\hat{\textbf{C}}$ (i.e.
-inverse variance weighting, shown in red), and also add an arbitrarily chosen level of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan).
-We see that all three regularization schemes (black, red, cyan) perform similarly at their best (i.e.
-when $\sim3$-$4$ eigenmodes are down-weighted in the case of the black curve).
-
-For the remainder of this paper, we choose to use the weighting option of $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or inverse variance weighting, which we will denote as $\hat{\textbf{C}}_{eff}$.
-We choose this weighting scheme due to its simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
-
-Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure \ref{fig:ps1_data}.
-Again, black and grey points correspond to positive and negative power spectrum values respectively, with $2\sigma$ errors bars.
-Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of noise (solid green).
-From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$).
+In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
+which denote power spectrum values, post-signal loss correction, for two other regularization schemes. We multiply an identity 
+matrix element-wise to $\hat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
+of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
+their best (i.e. when $\sim3$-$4$ eigenmodes are down-weighted in the case of the black curve).
+
+For the remainder of this paper, we choose to use the weighting option of $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or 
+inverse variance weighting, which we will denote as $\hat{\textbf{C}}_{eff}$. We choose this weighting scheme due to its 
+simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
+
+Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure 
+\ref{fig:ps1_data}. Again, black and grey points correspond to positive and negative power spectrum values respectively, with 
+$2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
+noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
+a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
 \cc{ref kolopanis limit instead later}
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$.
-Black and grey points correspond to positive and negative power spectrum values, respectively, with $2\sigma$ error bars also plotted.
-The dashed blue line is the unweighted power spectrum ($2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction based on observational parameters.
-This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m East/West baselines) instead of three.
-Major differences from previously published results stem from revisions regarding signal loss, bootstrapping, and the theoretical error computation.
-We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
+	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and grey points correspond to positive and 
+negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
+power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
+parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m East/West 
+baselines) instead of three. Major differences from previously published results stem from revisions regarding signal loss, 
+bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ 
+$h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
 	\label{fig:ps1_data}
@@
 
-In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 data.
-There are many other weighting schemes that we leave for consideration in future work.
-For example, one could estimate $\hat{\textbf{C}}$ using information from different subsets of baselines.
-For redundant arrays this could mean calculating $\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the horizontal E/W ones).
-Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied when forming a power spectrum estimate.
-This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the $21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so we also regard those results as suspect and superseded by those of \cc{cite kolopanis}).
-
-Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST.
-For example, one could calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to down-weight.
-Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
+In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 
+data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
+$\hat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
+\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
+horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
+when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the 
+$21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation 
+because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
+we also regard those results as suspect and superseded by those of \cc{cite kolopanis}).
+
+Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
+calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-
+quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
+down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from 
+data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-
+weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
 
@@
 
-In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
-We first walk through a derivation for a theoretical error estimation (of thermal noise) based on observational parameters.
-Although a theoretical model often differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
-
-In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the P64 analysis of PAPER-64.
-While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
+In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra. We first walk through a derivation 
+for a theoretical error estimation (of thermal noise) based on observational parameters. Although a theoretical model often 
+differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors 
+that affect its sensitivity. Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to 
+revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
+
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the P64 
+analysis of PAPER-64. While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power 
+spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
 
@@
 
-Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations.
-What we found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations.
-The analytic calculation is only an approximation, however the differences were large enough (factors of $10$ in some cases) to warrant a careful investigation.
-The analytic calculation attempts to combine a large number of pieces of information in an approximate way, and when re-considering some of the approximations, we have found there to be large effects.
-What follows here is an accounting of the differences which have been discovered.
-
-The sensitivity prediction (\citealt{parsons_et_al2012a}, \citealt{pober_et_al2013}) for a power spectral analysis of interferometric $21$ cm data, in temperature-units, is:
+Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations. What we 
+found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations. The analytic 
+calculation is only an approximation, however the differences were large enough (factors of $10$ in some cases) to warrant a 
+careful investigation. The analytic calculation attempts to combine a large number of pieces of information in an approximate 
+way, and when re-considering some of the approximations, we have found there to be large effects. What follows here is an 
+accounting of the differences which have been discovered.
+
+The sensitivity prediction (\citealt{parsons_et_al2012a}, \citealt{pober_et_al2013}) for a power spectral analysis of 
+interferometric $21$ cm data, in temperature-units, is:
 
@@
 \begin{itemize}
-\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving distances).
-For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
+\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving 
+distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
 \item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}, \citealt{pober_et_al2012}). 
-The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-weighted.
-Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate filter.
+The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-
+weighted. Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate 
+filter. 
 \item $T_{sys}$: The system temperature is set by:
@@
 
-where $\nu$ are frequencies in GHz.
-We use a receiver temperature of $200$ K, yielding $T_{sys} = 487$ K at $150$ MHz.
-This is lower than in P64 because of previous failure to correct for using a median statistic.
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum estimates after squaring visibility measurements.
-In P64, a factor of $2$ was mistakenly used.
-\item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation.
-The sensitivity scales as the square root because we integrate incoherently over time.
-For PAPER-64, $N_{lsts} = 8$ hours.
-\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate.
-For the analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$.
-The updated limits in \cc{cite kolopanis paper} use three separation types.
-\item $t_{int}$: The integration time of the data.
-It is crucial to adapt this number if filtering is applied along the time axis (i.e.
-a fringe-rate filter).
-We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time using the following:
+where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
+This is lower than the $T_{sys}$ of $500$ K used in P64 because of several small miscalculation errors that were 
+identified\footnote{such as missing a square root in going from a variance to a standard deviation.}.
+\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
+estimates after squaring visibility measurements. In P64, a factor of $2$ was mistakenly used.
+\item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation. The sensitivity scales as the square root 
+because we integrate incoherently over time. For PAPER-64, $N_{lsts} = 8$ hours.
+\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
+analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in \cc{cite kolopanis paper} 
+use three separation types.
+\item $t_{int}$: The integration time of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
+fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time 
+using the following:
 \begin{equation}
@@
 \end{equation}
-where $t_{int}=43$ seconds, $t_{frf}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is taken over all fringe-rates.
-For PAPER-64, this number is $t_{int} = 3857$ s.
-\item $N_{days}$: The total number of days of data analyzed.
-In P64, this number was set to $135$.
-However, because we divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$.
-Additionally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of $N_{days}$ as:
+where $t_{int}=43$ seconds, $t_{frf}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
+taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
+\item $N_{days}$: The total number of days of data analyzed. In P64, this number was set to $135$. However, because we 
+divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
+because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of 
+$N_{days}$ as:
 \begin{equation}
@@
  \end{equation}
-\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ days.
-\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate.
-In P64, this number was the total number of $30$ m East/West baselines used in the analysis.
-However, using the total number of baselines neglects the fact that baselines are averaged into groups before cross-multiplying data.
-Our revised estimate for the parameter is:
+\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ 
+days.
+\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In P64, this number was 
+the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
+the fact that baselines are averaged into groups before cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 \end{equation}
-\noindent where, for the P64 analysis, $N_{gps} = 5$.
-Each baseline group averages down linearly as the number of baselines entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - N_{gps}}$).
-For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead of $51$.
+\noindent where, for the P64 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
+N_{gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead 
+of $51$. 
 \item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
@@
 
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging together positive and negative $k$'s.
+An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging 
+together positive and negative $k$'s.
 
 Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of P64 in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$.
+Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.
 
@@
 	\includegraphics[width=\columnwidth]{plots/sense_check.png}
-	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously published sensitivity limits (grey).
-Both sensitivity analyses plotted assume only one baseline type (an additional factor of $\sqrt{3}$ for 3 baseline types is needed to match P64 exactly).
-Major factors that contribute to the discrepancy are $\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our sensitivity (higher noise floor) by a factor of $\sim7$.}
+	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
+published sensitivity limits (grey). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
+\sqrt{3}$ for 3 baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
+\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
+sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
 	\label{fig:sense_check}
@@
 
-To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation.
-We create Gaussian random noise assuming a constant $T_{sys}$ (neglecting sky variation) but accounting for the true $N_{days}$ as determined by LST sampling counts for each time and frequency in the LST-binned data.
-We convert $T_{sys}$ into a variance statistic using:
+To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
+random noise assuming a constant $T_{sys}$ (neglecting sky variation) but accounting for the true $N_{days}$ as determined 
+by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{sys}$ into a variance statistic 
+using:
 
@@
 
-\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a particular time and frequency that went into our LST-binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes I).
-This RMS temperature sets the variance of the Gaussian random noise.
-
-Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure \ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation \eqref{eq:sense}.
-All three are in agreement, validating our analytical thermal noise calculation.
+\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a 
+particular time and frequency that went into our LST-binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes 
+I). This RMS temperature sets the variance of the Gaussian random noise.
+
+Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
+\ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with 
+$2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power 
+spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
+\eqref{eq:sense}. All three are in agreement, validating our analytical thermal noise calculation.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_reg.png}
-	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data.
-The weighted power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we use $\hat{\textbf{C}}_{eff}$ to minimize signal loss.
-The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper limit).
-The solid green line is the theoretical noise level prediction as calculated by Equation \eqref{eq:sense}.
-All three estimates agree.}
+	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
+power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
+\hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
+limit). The solid green line is the theoretical noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
+estimates agree.}
 	\label{fig:ps_noise}
@@
 
-We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results.
-In this section, we highlight two major changes in the way we estimate errors since P64, using the lessons we've learned about sampling with replacement and bootstrapping independent samples.
-
-As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised of independent samples.
-The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power spectrum that is a function of $k$ and time.
-
-In P64, a second round of bootstrapping occurred over the time axis.
-A total of $400$ bootstraps were created in this step ($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis.
-More specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering, which is $\sim$$8$).
-Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied).
-Finally, power spectrum limits were computed by taking the mean and standard deviation over all the bootstraps.
-We emphasize again that in this previous analysis, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly exceeded the number of independent LST samples ($\sim$$8$), under-estimating errors.
-A random draw of $700$ measurements from this dataset has many repeated values, and the variance between hundreds ($N_{boot}$) of these random samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second bootstrapping step along time entirely and now simply bootstrap over baselines with the ``single replacement" strategy described in Section \ref{sec:ErrorOverview}.
-
-The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each group.
-In P64, baselines were chosen for groups randomly with replacement.
-In doing so, $\sim$$3$-$4$ baselines per group were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total independent samples) which sacrificed some sensitivity.
-
-Power spectrum estimates with these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure \ref{fig:data_errors}.
-The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss.
-As shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized, while when only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ modes converges to the theoretical noise level.
-However, if more elements are drawn for each bootstrap than the number of independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level.
+We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
+two major changes in the way we estimate errors since P64, using the lessons we've learned about sampling with replacement 
+and bootstrapping independent samples.
+
+As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
+of independent samples. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
+spectrum that is a function of $k$ and time.
+
+In P64, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
+($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
+specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
+$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering, which is $\sim$$8$). 
+Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied). Finally, power 
+spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
+this previous analysis, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly 
+exceeded the number of independent LST samples ($\sim$$8$), under-estimating errors. A random draw of $700$ 
+measurements from this dataset has many repeated values, and the variance between hundreds ($N_{boot}$) of these random 
+samples is smaller than the true underlying variance of the data.
+
+Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
+bootstrapping step along time entirely and now simply bootstrap over baselines with the ``single replacement" strategy 
+described in Section \ref{sec:ErrorOverview}.
+
+The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
+group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim$$3$-$4$ baselines per group 
+were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total 
+independent samples) which sacrificed some sensitivity.
+
+Power spectrum estimates with these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure 
+\ref{fig:data_errors}. The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss. As 
+shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized, while when 
+only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ 
+modes converges to the theoretical noise level.  However, if more elements are drawn for each bootstrap than the number of 
+independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent 
+variation between bootstraps drops, resulting in limits below the predicted noise level.
 
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
-	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping methods.
-The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the effects of bootstrapping from signal loss.
-Three different bootstrapping methods are shown: the blue and black use methods where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly sampled.
-It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent samples (only the last baseline spot is sampled randomly), as shown by the black curve.
-In red, bootstrapping occurs over both the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones (fringe-rate filtering reduces the number of independent samples).
-We use the method illustrated by the black curve in our updated analysis, which is shown to agree with the analytic prediction for noise (green).}
+	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
+methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
+effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
+where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
+sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
+samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
+the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
+(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
+updated analysis, which is shown to agree with the analytic prediction for noise (green).}
 	\label{fig:data_errors}
@@
 
-In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum detections and imitate EoR.
-We discussed the importance of using jackknife and null tests for instilling confidence in an EoR detection, as well as identifying other sources of biases.
-Here we demonstrate methods used by PAPER-64 to mitigate foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.
+In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum 
+detections and imitate EoR. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
+detection, as well as identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
+foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.
 
@@
 
-We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we suppress noise biases.
-These methods are not novel to this analysis but here we frame them in the context of minimizing false (non-EoR) detections.
-
-Tailoring window functions is one way to suppress foreground biases.
-As alluded to in Section \ref{sec:SiglossOverview}, we have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}.
-For the analysis of PAPER-64 data, we compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we 
+suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
+(non-EoR) detections.
+
+Tailoring window functions is one way to suppress foreground biases. As alluded to in Section \ref{sec:SiglossOverview}, we 
+have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
+compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
 
@@
 
-\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$.
-We take the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices:
+\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
+the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices:
 
@@
 
-\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MF}$, becomes:
+\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MF}$, 
+becomes:
 
@@
 
-\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage of foreground power from low $k$ to high $k$ modes.
-Specifically, we order the elements in $\textbf{F}$ in such a way so that power can leak from high $k$ modes to low $k$ modes, but not vice versa.
-Since most foreground power shows up at low $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the contamination of foreground bias.
-
-In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk.
-In order to avoid the former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \eqref{eq:qhat}.
-Namely, the PAPER-64 dataset is divided into two halves: even julian dates and odd julian dates.
-Our data vectors are then $\textbf{x}_{even, 1}$ for the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc.
-We only form $\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for example, in order to prevent the squaring of the same thermal noise.
-
-To mitigate crosstalk bias, which appears as a static bias in time, we apply a fringe-rate filter that suppresses fringe-rates of zero.
-Figure \ref{fig:frp} shows that the filter response is zero for such static signals.
-The effect of filtering out zero fringe-rates on power spectrum results is shown in P64.
-Most notably, power spectrum detections exist at all $k$'s without crosstalk removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
+\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
+of foreground power from low $k$ to high $k$ modes. Specifically, we order the elements in $\textbf{F}$ in such a way so that 
+power can leak from high $k$ modes to low $k$ modes, but not vice versa. Since most foreground power shows up at low 
+$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
+contamination of foreground bias.
+
+In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 
+analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
+former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
+dataset is divided into two halves: even julian dates and odd julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
+the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
+$\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
+example, in order to prevent the squaring of the same thermal noise.
+
+To mitigate crosstalk bias, which appears as a static bias in time, we apply a fringe-rate filter that suppresses fringe-rates of 
+zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
+on power spectrum results is shown in P64. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
+removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
 
@@
 
-The highest sensitivity power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in Figure \ref{fig:ps1_data}, has positive biases at low $k$ values.
-As discussed in Section \ref{sec:BiasTypes}, these detections are most likely attributable to foreground leakage.
-Here we demonstrate $3$ null tests performed on PAPER-64 data that verify that the positive detections are indeed due to foreground variation and not attributable to EoR.
+The highest sensitivity power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in 
+Figure \ref{fig:ps1_data}, has positive biases at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these detections 
+are most likely attributable to foreground leakage. Here we demonstrate $3$ null tests performed on PAPER-64 data that verify 
+that the positive detections are indeed due to foreground variation and not attributable to EoR.
 
@@
 \begin{itemize}
-\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised PAPER-64 power spectrum (one baseline type only) with weighting matrix $\hat{\textbf{C}}_{eff}$.
-There are clear detections at low $k$'s.
-\item Even/Odd (blue): We split our dataset into even (e) and odd (o) days, where $\textbf{x}_{1} = e + o$ and $\textbf{x}_{2} = e - o$.
-We form datasets in this way to ensure that we use the full sensitivity of our data.
-When cross-multiplied, we obtain:
+\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised 
+PAPER-64 power spectrum (one baseline type only) with weighting matrix $\hat{\textbf{C}}_{eff}$. There are clear detections at 
+low $k$'s.
+\item Even/Odd (blue): We split our dataset into even (e) and odd (o) days, where $\textbf{x}_{1} = e + o$ and $\textbf{x}_{2} = 
+e - o$. We form datasets in this way to ensure that we use the full sensitivity of our data. When cross-multiplied, we obtain:
 \begin{equation}
@@
 If the same sky signal is in both the even and odd datasets, we expect it to cancel out.
-\item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the analysis.
-Again, we form $\textbf{x}_{1} = b_{1} + b_{2}$ and $\textbf{x}_{2} = b_{1} - b_{2}$, where $b_{1}$ is the first baseline group and $b_{2}$ is the second baseline group.
-\item LST (purple): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 4.6-8.6 hours).
-We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$.
+\item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the 
+analysis. Again, we form $\textbf{x}_{1} = b_{1} + b_{2}$ and $\textbf{x}_{2} = b_{1} - b_{2}$, where $b_{1}$ is the first baseline 
+group and $b_{2}$ is the second baseline group.
+\item LST (purple): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 
+4.6-8.6 hours). We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$.
 \end{itemize}
@@
 	\includegraphics[width=\columnwidth]{plots/null.png}
-	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ errors (grey shaded region).
-For each, we took jackknives along different axes of the dataset - by julian days (separating even and odd days; blue), by baselines (green), and by LST (purple).
-We expect the sky signal to disappear for a `passing' null test.
-We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to particular baselines or days of data.}
+	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ 
+errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating even 
+and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
+We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
+particular baselines or days of data.}
 	\label{fig:null}
@@
 
-Investigating Figure \ref{fig:null}, we find that both the baselines and even/odd null tests are consistent with noise.
-We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
-
-The null test in LST (purple) is much more illuminating.
-The fact that there are many power spectrum points outside the estimated error region signifies that the bias we see is likely from foregrounds that vary in LST.
-In other words, $t_{1}$ and $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-The errors for this null test are also large, also reflective of residual foregrounds.
-
-We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s.
-This would illuminate the particular LST range that introduces the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source.
-This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the bias we see comes from foregrounds in regions where we expect leakage.
+Investigating Figure \ref{fig:null}, we find that both the baselines and even/odd null tests are consistent with noise. We note that 
+the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to 
+cross-multiplication (when forming baseline groups).
+
+The null test in LST (purple) is much more illuminating. The fact that there are many power spectrum points outside the 
+estimated error region signifies that the bias we see is likely from foregrounds that vary in LST. In other words, $t_{1}$ and 
+$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-
+multiplication. The errors for this null test are also large, also reflective of residual foregrounds.
+
+We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
+similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
+the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
+This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the 
+bias we see comes from foregrounds in regions where we expect leakage.
 
@@
 
-Although current $21$ cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities.
-As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife and null tests.
-
-In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$ cm power spectrum techniques on signal loss, error estimation, and bias, which can be summarized as follows:
+Although current $21$ cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
+ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like 
+HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
+that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately 
+and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife 
+and null tests.
+
+In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$ cm power spectrum techniques on 
+signal loss, error estimation, and bias, which can be summarized as follows:
 
 \begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances (Section \ref{sec:SiglossOverview}).
-Loss of the $21$ cm signal is especially significant if more eigenmodes are down-weighted than exist in the data (having an under-constrained covariance matrix).
-Hence, there exists a trade-off between sensitivity driven time-averaging techniques such as fringe-rate filtering and signal loss.
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}).
-However, a signal-only simulation (i.e.
-comparing an unweighted vs.
-weighted power spectrum of EoR only) can underestimate loss by failing to account for spurious correlations between the data and signal.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated (Section \ref{sec:ErrorOverview}).
-If the number of independent samples in a dataset is well-determined, bootstrapping is a simple and accurate way of estimating errors.
-\item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}).
-Similarly, performing jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection and can also be used to tease out systematics.
+\item Substantial signal loss can result when weighting data using empirically estimated covariances (Section 
+\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant if more eigenmodes are down-weighted than 
+exist in the data (having an under-constrained covariance matrix). Hence, there exists a trade-off between sensitivity driven 
+time-averaging techniques such as fringe-rate filtering and signal loss. 
+\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
+signal-only simulation (i.e. comparing an unweighted vs. weighted power spectrum of EoR only) can underestimate loss by 
+failing to account for spurious correlations between the data and signal.
+\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
+(Section \ref{sec:ErrorOverview}). If the number of independent samples in a dataset is well-determined, bootstrapping is a 
+simple and accurate way of estimating errors.
+\item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}). Similarly, performing 
+jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection and can also be used to tease 
+out systematics.
 \end{itemize}
 
-As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
-For an analysis of only one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.
-The reasons for a previously underestimated limit and ways in which our new analysis differs can be summarized by the following:
+As a consequence of our investigations, we have also revised power spectrum results from PAPER-64. For an analysis of only 
+one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
+P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+ways in which our new analysis differs can be summarized by the following:
 
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting.
-For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}).
-However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ mK higher than previous limits.
-Underestimated signal loss therefore represents the bulk of our revision.
-We note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering.
-They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra (Section \ref{sec:Boot}).
-Hence, the net change for our error estimation is negligible, though the rationale behind the previous estimation was incorrect.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$3$ in mK (Section \ref{sec:PSSense}).
-We have verified our revised prediction extensively using pure noise simulations.
-We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that if taken at face value, the theoretical prediction for noise in P64 was too high for its data points.
+\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse 
+covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
+\ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
+factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
+note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
+revised from new signal loss calculations associated with their singular value decomposition foreground filter.
+\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to 
+oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. They were also 
+overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power 
+spectra (Section \ref{sec:Boot}). Hence, the net change for our error estimation is negligible, though the rationale behind the 
+previous estimation was incorrect.
+\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
+decrease in predicted sensitivity level by a factor of $\sim$$2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
+prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
+power spectrum result, implying that if taken at face value, the theoretical prediction for noise in P64 was too high for its data 
+points.
 \end{itemize}
 
-The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand instruments.
-On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and comprehensive jackknife tests will play critical roles in accurate $21$ cm results.
-Looking ahead, the future promises to bring higher sensitivity measurements, better foreground and instrumental models, more effective and less lossy weighting techniques --- and with all that, an improved understanding of reionization and our early Universe.
+The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
+foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
+instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
+comprehensive jackknife tests will play critical roles in accurate $21$ cm results. Looking ahead, the future promises to bring 
+higher sensitivity measurements, better foreground and instrumental models, more effective and less lossy weighting 
+techniques --- and with all that, an improved understanding of reionization and our early Universe.
 
@@
 \section{Acknowledgements}
-CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions.
-PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646).
-ARP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-We also graciously thank SKA-SA for site infrastructure and observing support.
+CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research 
+Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA 
+are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
+also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). We also graciously thank SKA-
+SA for site infrastructure and observing support.
 \label{sec:Ack}
@@
 
-\cc{Note to Adrian: I standardized all Q indices to be superscripts instead of subscripts. Also standardized equations to be ``Equation eqref" (spell out Equation, and use eqref for references)}
-
-In this Appendix, we examine a toy model for signal loss.
-Our goal is to build intuition by deriving an analytic formula for power spectrum signal loss.
-We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum estimate.
-
-The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by \acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
+\cc{Note to Adrian: I standardized all Q indices to be superscripts instead of subscripts. Also standardized equations to be 
+``Equation eqref" (spell out Equation, and use eqref for references)}
+
+In this Appendix, we examine a toy model for signal loss. Our goal is to build intuition by deriving an analytic formula for power 
+spectrum signal loss. We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum 
+estimate.
+
+The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
+\acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
 \begin{equation}
@@
 \end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix.
-In our case, however, we do not have \emph{a priori} knowledge of the covariance matrix.
-Thus, we replace $\C$ with $\Chat$, its data-derived approximation.
-Our estimator then becomes
+is the $\alpha$th diagonal element of the Fisher matrix. In our case, however, we do not have \emph{a priori} knowledge of the 
+covariance matrix. Thus, we replace $\C$ with $\Chat$, its data-derived approximation. Our estimator then becomes
 \begin{equation}
@@
 \end{equation}
-with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than unity).
-We will now provide an explicit demonstration of this by modeling the estimated covariance as
+with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than 
+unity). We will now provide an explicit demonstration of this by modeling the estimated covariance as
 \begin{equation}
@@
 \end{equation}
-where $\eta$ is parameter quantifying our success at estimating the true covariance matrix.
-If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
-On the other hand, if $\eta =1$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
-
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
-We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
+where $\eta$ is parameter quantifying our success at estimating the true covariance matrix. If $\eta = 0$, our covariance 
+estimate has perfectly modeled the true covariance and $\Chat = \C$. On the other hand, if $\eta =1$, then our covariance 
+estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of 
+overfitting and signal loss.
+
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to 
+express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$. We begin by expressing $
+\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
 \begin{equation}
@@
 \begin{equation}
-\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
-\end{equation}
-where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
-Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$.
-Inserting these expressions into our estimator gives
+\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha 
+\alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
+\end{equation}
+where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha 
+\C^{-1}\x $. Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$. Inserting 
+these expressions into our estimator gives
 \begin{eqnarray}
 \label{eq:phatlossexpanded}
-\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
-&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} \left( \frac{\varepsilon h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\varepsilon^2 h_\alpha^2}{2 F_{\alpha \alpha}}\right)^{n-k},
+\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 
+-\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 
+\frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
+&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} 
+\left( \frac{\varepsilon h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\varepsilon^2 h_\alpha^2}{2 F_{\alpha \alpha}}
+\right)^{n-k},
 \end{eqnarray}
-where $\beta \equiv \eta g/[1+ \eta (g-1)]$ and $\varepsilon \equiv \beta / g$.
-To proceed, we take the ensemble average of $\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties.
-Inspecting Equation \eqref{eq:phatlossexpanded}, we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, where $a$, $b$, and $c$ are integers.
-Expanding $\beta$ in powers of $g$, we have
+where $\beta \equiv \eta g/[1+ \eta (g-1)]$ and $\varepsilon \equiv \beta / g$. To proceed, we take the ensemble average of $
+\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties. Inspecting Equation \eqref{eq:phatlossexpanded}, 
+we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, 
+where $a$, $b$, and $c$ are integers. Expanding $\beta$ in powers of $g$, we have
 \begin{equation}
 \label{eq:betahh}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_{a+d} = 1}^\infty \frac{(-\eta)^{m_1 + \dots + m_{a+d}}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_{a+d}-d} h_\alpha^b h_{\alpha \alpha}^c \rangle.
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_{a+d} = 1}^\infty 
+\frac{(-\eta)^{m_1 + \dots + m_{a+d}}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_{a+d}-d} h_\alpha^b h_{\alpha 
+\alpha}^c \rangle.
 \end{equation}
@@
 \begin{eqnarray}
-\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha \C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
-&=& \sum_{i_1}^N \sum_{j_1}^N \cdots  \sum_{k_1}^N \sum_{l_1}^N \cdots  \sum_{p_1}^N \sum_{q_1}^N \cdots  ( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} )_{p_1 q_1} \dots (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1})_{p_c q_c}  \nonumber \\
-&&  \times ( \C^{-1} \Q^\alpha \C^{-1})_{k_1 l_1} \dots ( \C^{-1} \Q^\alpha \C^{-1})_{k_b l_b} \C^{-1}_{i_1 j_1}\dots \C^{-1}_{i_M j_M} \langle x_{i_1} x_{j_1} \dots   x_{k_1} x_{l_1} \dots  x_{p_1} x_{q_1} \dots \rangle, \quad
+\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha 
+\C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
+&=& \sum_{i_1}^N \sum_{j_1}^N \cdots  \sum_{k_1}^N \sum_{l_1}^N \cdots  \sum_{p_1}^N \sum_{q_1}^N \cdots  ( \C^{-1} 
+\Q^\alpha \C^{-1} \Q^\alpha \C^{-1} )_{p_1 q_1} \dots (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1})_{p_c q_c}  \nonumber \\
+&&  \times ( \C^{-1} \Q^\alpha \C^{-1})_{k_1 l_1} \dots ( \C^{-1} \Q^\alpha \C^{-1})_{k_b l_b} \C^{-1}_{i_1 j_1}\dots \C^{-1}_{i_M 
+j_M} \langle x_{i_1} x_{j_1} \dots   x_{k_1} x_{l_1} \dots  x_{p_1} x_{q_1} \dots \rangle, \quad
 \end{eqnarray}
-where $N$ is the length of vector $\x$, i.e., the number of data points.
-To further simplify this expression, we assume that the data are Gaussian distributed.
-The expectation value on the right hand side can then be reduced to a sum of product of covariances, where each term in the sum is comprised of a particular way to partition the copies of $x$ into pairs.
-However, in the limit of large $N$ one particular partitioning dominates, and the result can be approximated as \acl{Should probably explain this more fully}
-\begin{equation}
-\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_{a+d}} \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
+where $N$ is the length of vector $\x$, i.e., the number of data points. To further simplify this expression, we assume that the 
+data are Gaussian distributed. The expectation value on the right hand side can then be reduced to a sum of product of 
+covariances, where each term in the sum is comprised of a particular way to partition the copies of $x$ into pairs. However, in 
+the limit of large $N$ one particular partitioning dominates, and the result can be approximated as \acl{Should probably explain 
+this more fully}
+\begin{equation}
+\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_{a+d}} \left[ \textrm{tr} 
+(\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
 \end{equation}
@@
 \begin{equation}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a \left[ \frac{\eta }{1+\eta (N-1)} \right]^d \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
-\end{equation}
-With this result, taking the ensemble average of Equation \eqref{eq:phatlossexpanded} is relatively straightforward.
-One simply replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $\varepsilon$ with $\varepsilon_N \equiv  \eta  / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha \alpha}$ with $2F_{\alpha \alpha}$.
-Performing these substitutions and recalling \acl{make sure the reader will indeed be recalling at this point} that $\langle \hat{p}_\alpha \rangle = \langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
-\begin{equation}
-\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle} = \frac{1- 2\varepsilon_N + \varepsilon_N^2 \left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / 2F_{\alpha \alpha}}{(1-\beta_N)^2}.
-\end{equation}
-This quantity is in general less than unity, and quantifies the signal loss relative to the ideal estimator $\hat{p}_\alpha$ where we know the true covariance $\C$.
-As an illustrative example, for cases where $\C \propto \I$, this reduces to
-\begin{equation}
-\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle}  \Bigg{|}_{\C \propto \I} = \left( \frac{1-\varepsilon_N}{1-\beta_N} \right)^2 = \left[\frac{1+ \eta(N-2)}{1- \eta}\right]^2.
-\end{equation}
-This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect estimation of $\C$) and goes to infinity as $\eta$ approaches $1$.
+\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a 
+\left[ \frac{\eta }{1+\eta (N-1)} \right]^d \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
+\end{equation}
+With this result, taking the ensemble average of Equation \eqref{eq:phatlossexpanded} is relatively straightforward. One simply 
+replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $\varepsilon$ with $\varepsilon_N 
+\equiv  \eta  / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha 
+\alpha}$ with $2F_{\alpha \alpha}$. Performing these substitutions and recalling \acl{make sure the reader will indeed be 
+recalling at this point} that $\langle \hat{p}_\alpha \rangle = \langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
+\begin{equation}
+\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle} = \frac{1- 2\varepsilon_N + \varepsilon_N^2 
+\left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / 2F_{\alpha \alpha}}{(1-\beta_N)^2}.
+\end{equation}
+This quantity is in general less than unity, and quantifies the signal loss relative to the ideal estimator $\hat{p}_\alpha$ where 
+we know the true covariance $\C$. As an illustrative example, for cases where $\C \propto \I$, this reduces to
+\begin{equation}
+\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle}  \Bigg{|}_{\C \propto \I} = \left( \frac{1-
+\varepsilon_N}{1-\beta_N} \right)^2 = \left[\frac{1+ \eta(N-2)}{1- \eta}\right]^2.
+\end{equation}
+This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect 
+estimation of $\C$) and goes to infinity as $\eta$ approaches $1$.
 \begin{figure}
@@
 
-In general, one's estimate of the covariance will not be expressible in the form given by Equation \eqref{eq:ChatDef}.
-However, the qualitative point here is that the signal loss can be expressed as a multiplicative factor.
-Even if $\Chat$ is more complicated than the form used for this toy model, the same mathematical technique of expressing the estimator as a series of higher-point functions, reducing these functions (assuming Gaussianity) to two-point functions, and re-summing any power series will show that the signal loss is a multiplicative factor.
-\acl{I can express this last bit more eloquently, but it's late and I'm tired and need to eat dinner.}
+In general, one's estimate of the covariance will not be expressible in the form given by Equation \eqref{eq:ChatDef}. However, 
+the qualitative point here is that the signal loss can be expressed as a multiplicative factor. Even if $\Chat$ is more complicated 
+than the form used for this toy model, the same mathematical technique of expressing the estimator as a series of higher-point 
+functions, reducing these functions (assuming Gaussianity) to two-point functions, and re-summing any power series will show 
+that the signal loss is a multiplicative factor. \acl{I can express this last bit more eloquently, but it's late and I'm tired and need to 
+eat dinner.}
 

### 2017-11-22 PAPER.tex
minor text changes

@@
 with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
-spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
+spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
 parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
@@
 negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
-power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical noise level prediction based on observational 
-parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m East/West 
-baselines) instead of three. Major differences from previously published results stem from revisions regarding signal loss, 
-bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ 
-$h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
+power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
+observational parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m 
+East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
+loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at 
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
 	\label{fig:ps1_data}
@@
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
-power spectrum points and $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
+power spectrum points and their $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
 \hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
-limit). The solid green line is the theoretical noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
-estimates agree.}
+limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
+estimates agree (the analytic curve should encompass $95\%$ of the points).}
 	\label{fig:ps_noise}
@@
 (fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
-updated analysis, which is shown to agree with the analytic prediction for noise (green).}
+updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
 	\label{fig:data_errors}
@@
 	\includegraphics[width=\columnwidth]{plots/null.png}
-	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and estimated $2\sigma$ 
-errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating even 
-and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
+	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
+$2\sigma$ errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating 
+even and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
 We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 

### 2017-11-26 PAPER.tex
first pass at the METHOD 2 section

@@
 \newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
+\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
+
+% Math shortcuts from Danny
+\newcommand{\Prob}{\mathbf{P}}
 
@@
 
-$P_{in}$ represents the unweighted power spectrum of only $\textbf{e}$, our simulated EoR signal. $P_{out}$ is the weighted 
-power spectrum of $\textbf{e}$ that would result from our pipeline if the signal was mixed with our data. Comparing the two 
-quantities yields insight into how much of $\textbf{e}$ is lost due to our choice of weighting.
-
-It is noted that the output power spectrum is comprised of two terms: the weighted power spectrum associated with \textbf{r}, 
-and that of data \textbf{x} alone.
+$P_{in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+$P_x$ is the power spectrum of the data, $P_r$ is the power spectrum of the
+data plus injection, and $P_out$ is the difference in power caused by the injected signal.
 
@@
 \end{center}
-
-The second method we describe here... \cc{Danny and Matt's section}
-
-\cc{refer back to Equations \eqref{eq:Pin} and \eqref{eq:sigloss} and explain why the subtraction term is removed}
-
-\cc{also state at the end that the rest of the analysis uses method \#1 instead of \#2...}
+One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure output. 
+  Small differences in approach here were found to cause large differences in the final answer.
+One important decision is  in the question asked, above we asked "What is the input power associated with an excess similar in amplitude to the data power spectrum?"  Here we rephrase the question to: "At what point would an injected signal be detectable at significant levels?".
+
+  This is phrased visually in  \ref{fig:Pr_vs_Pin}.
+In the 2D space relating total $P_r$ to injected $P_{in}$ very small injected levels begin at the level of the no injection case, as the $P_{in}$ level rises,  as it approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
+Above some level the injected signal is clearly detectable.
+
+  One difference here is that we are exclusively asking about signals detectable \emph{above} the level of the observed data. Thus it is 
+  explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.  This might be 
+  seen as more conservative, however a similar assumption has already been made when choosing to down-weight using the data 
+  itself. In that step one has assumed that significant excess power is associated with a foreground residual. A high SNR detection 
+  will require a different method.
+
+  Formally we can express our test as: ``What is $P_{in}$ such that
+\begin{equation}
+P_{r} > P_{x} \Lambda
+\end{equation}  
+ where $\Lambda$ represents a choice of threshold.'' Of course both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{ie the null test} the same.
+
+ \begin{equation}
+\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
+  \end{equation}
+  where $\Prob(P_x)$ is the probability of obtaining power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the 
+  probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Fig. 
+  \ref{fig:Pr_vs_Pin}.  The probability vs injection level is shown in figure \ref{fig:Prob_vs_Pin}. At low inject levels the variation 
+  between $x$ and $r$ is such that the null test is ruled out to within 20\%. This is the level expected from two distributions with 
+  $\sim$10 effective samples.\dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data the probability of null rejection rises steeply.
+
+Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
+As can be seen in \ref{fig:Pr_vs_Pin} the difference between 80 and 90\% can mean a difference of almost an order of magnitude in the power spectrum level ruled out.
+We can also see that it does not perfectly converge at high injected power levels.
+Rather than insist on a rejection at the 99th percent level we compromise at 95\% \dcj{Matt, put in actual value here}.
+
+The resulting limits in the PSA64 data are shown in figure \ref{fig:cc_vs_mk} next to the limits from Method \#1. \dcj{Hopefully they are similar!} In the rest of the paper method \#1 is used.
+
+%\cc{refer back to Equations \eqref{eq:Pin} and \eqref{eq:sigloss} and explain why the subtraction term is removed}
 

### 2017-11-27 PAPER.tex
-edited first pass of method #2 section

--- 2017-11-22 PAPER.tex
@@
 
-The second method we describe here... \cc{Danny and Matt's section}
-
-\cc{refer back to Equations \eqref{eq:Pin} and \eqref{eq:sigloss} and explain why the subtraction term is removed}
-
-\cc{also state at the end that the rest of the analysis uses method \#1 instead of \#2...}
+One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
+Small differences in approaches were found to cause large differences in the final answer.
+\cc{but aren't we arguing the opposite - that they yield similar answers?}
+
+For Method \#1, we used $P_{out}$ as the output of interest.
+For that method, we had asked the question ``What is the input power associated with an excess similar in amplitude to the data power spectrum?" For this second method, we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
+Instead of looking at $P_{out}$, we now use $P_{r}$, the weighted power spectrum of the data plus signal, as the output of interest.
+
+This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
+In the 2D space relating total $P_r$ to injected $P_{in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+data only).
+\cc{this next sentence does not make sense} As $P_{in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
+Above some level the injected signal is clearly detectable.
+
+One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
+Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
+This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself.
+In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual.
+We note that a high SNR detection will require a different method, but we show this one to...
+\cc{fill in..}
+
+Formally we can express our test as: ``What is the $P_{in}$ such that
+\begin{equation}
+P_{r} > P_{x} \Lambda,
+\end{equation}  
+where $\Lambda$ represents a choice of threshold.'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e.
+the null test} the same.
+
+ \begin{equation}
+\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
+ \end{equation}
+ where $\Prob(P_x)$ is the probability of obtaining the power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+
+Probability vs.
+injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
+At low injection levels the variation between $x$ and $r$ is such that the null test is ruled out to within $20$\%.
+This is the level expected from two distributions with $\sim$10 effective samples.
+\dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
+
+Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
+As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
+We can also see that the probability does not perfectly converge at high injected power levels.
+\cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\% \dcj{Matt, put in actual value here}.
+
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:cc_vs_mk} next to the limits from Method \#1.
+\dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.
 

### 2017-11-28 PAPER.tex
added comparison image between methods and added into text

@@
 \newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
+\newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
 
@@
 We can also see that the probability does not perfectly converge at high injected power levels.
-\cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\% \dcj{Matt, put in actual value here}.
-
-The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:cc_vs_mk} next to the limits from Method \#1.
+\cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\% \dcj{Matt, put in actual value here} \mjk{The current image uses 90th percentile!}.
+
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} next to the limits from Method \#1.
 \dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
+\caption{A comparison of Method \#1 
+signal loss corrected power spectrum (black dots)
+and Method \#2 uppers limits at 90\% confidence (red curve).
+Also shown are the upper limits of the unweighted power spectrum
+(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
+\end{figure}
 

### 2017-11-28 PAPER.tex
removed references to 8 independent modes

--- 2017-11-27 PAPER.tex
@@
 from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
-revised PAPER-64 power spectrum result (\cc{cite retraction or kolopanis paper}). We conclude in Section \ref{sec:Con}.
+revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.
 
@@
 $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of 
-independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.\footnote{If 
-instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank 
-deficient covariance matrix. In this case... \cc{fill in}}
+independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
+%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
 
@@
 \ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
-the last few eigenmodes. This is because we have fewer independent modes --- \cc{need help filling out the rest here... and 
+the last few eigenmodes.
+This is because we have fewer independent modes and therefore less information to characterize the eigenspectrum.
+Because we do a worse job characterizing, we have more signal loss.
+\cc{need help filling out the rest here...
+and
 also citing galaxy lit}.
@@
 
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$. %The revision of this limit stems 
-mostly from previously underestimated signal loss and underestimated error bars \cc{cite retraction paper}, both of which we 
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
+The revision of this limit (Kolopanis et al., \textit{in prep}) stems mostly from previously underestimated signal loss and underestimated error bars, both of which we
 address in the following sections.
@@
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
-estimate of signal loss, likely due to the use of the fringe-rate filter as a simulator. Whether the loss would be estimated at the 
-same level if different $21$ cm simulations were used remains an open question.}
+estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.
+Whether the loss would be estimated at the same level if different $21$ cm simulations were used remains an open question.}
 
@@
 is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
-Post-correction, the power spectrum values blow up to be higher than both the theory and unweighted power spectrum.
-
-Investigating this further, the reason why the post-corrected power spectrum is so high is due to the small number of 
-independent samples in PAPER-64. PAPER-64 only has $\sim$$8$ independent modes after fringe-rate filtering while our 
-power spectrum bandwidth has $21$ channels. Consequently, the eigenvalues of $\hat{\textbf{C}}$ cannot possibly describe 
-real fluctuations beyond the first eight. Hence, there is a substantial down-weighting of other modes, a large loss that the signal 
-loss transfer function captures and corrects for. We elaborate on this point in the next section, as well as investigate alternate 
+Post-correction, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
+We elaborate on this point in the next section, as well as investigate alternate
 weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-
@@
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss correction, 
-increases with the number of down-weighted modes (black curve). As discussed previously, we are limited in our power 
-spectrum accuracy by the number of independent samples in our dataset and our errors dramatically increase as we surpass 
-the $\sim8$ independent samples that we have in fringe-rate filtered PAPER-64 data \cc{elaborate?}.
+increases with the number of down-weighted modes (black curve).
+Because our data is fringe-rate filtered, we have less information to characterize the covariance matrix and therefore do a worse job estimating it.
+Hence, the more modes we use in down-weighting, the greater the error we have in estimating the power spectrum.
 
 Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to not weighting (blue dashed line). We see in Figure \ref{fig:sigloss_modeloop} that this occurs when 
+is beneficial compared to not weighting (blue dashed line).
+In other words, we would like a weighting scheme that down-weights eigenmodes that describe foreground modes, but not EoR modes.
+We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
 only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not 
@@
 a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
-\cc{ref kolopanis limit instead later}
+\cc{replace with kolopanis limit instead later}
 
@@
 loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{ref kolopanis limit instead later}.}
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
 	\label{fig:ps1_data}
@@
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of \cc{cite kolopanis}).
+we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}.
 
@@
 This is lower than the $T_{sys}$ of $500$ K used in P64 because of several small miscalculation errors that were 
-identified\footnote{such as missing a square root in going from a variance to a standard deviation.}.
+identified\footnote{such as missing a square root in going from a variance to a standard deviation}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
@@
 \item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
-analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in \cc{cite kolopanis paper} 
+analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{in prep}
 use three separation types.
@@
 specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering, which is $\sim$$8$). 
+$700$, which we expect to greatly exceed the approximate number of independent samples after fringe-rate filtering.
 Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied). Finally, power 
 spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap ($N \sim $ number of times $\sim$ $700$) greatly 
-exceeded the number of independent LST samples ($\sim$$8$), under-estimating errors. A random draw of $700$ 
+this previous analysis, the number of elements sampled per bootstrap greatly 
+exceeded the number of independent LST samples, under-estimating errors. A random draw of $700$ 
 measurements from this dataset has many repeated values, and the variance between hundreds ($N_{boot}$) of these random 

### 2017-11-29 PAPER.tex
some minor edits

@@
 \newcommand{\x}{\mathbf{x}}
+\newcommand{\f}{\mathbf{f}}
+\newcommand{\s}{\mathbf{s}}
+\newcommand{\e}{\mathbf{e}}
+\newcommand{\p}{\mathbf{p}}
+\newcommand{\phat}{\hat{\mathbf{p}}}
 \newcommand{\C}{\mathbf{C}}
@@
 Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections 
-between the smooth matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
+between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
 web of galaxies we observe today.
 
-One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted by neutral hydrogen via 
-its spin-flip transition. This technique is powerful because it can be observed as a function of redshift --- that is, the wavelength 
+One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted and absorbed by neutral hydrogen via 
+its spin-flip transition. This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
 of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
@@
 Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
-the 21 cm signal from hydrogen to place constraints on the brightness of the EoR. Examples of experiments investigating the 
+the 21 cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
 mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
@@
 detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; 
-\citealt{pober_et_al2014}).
+\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}).
 
 The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, 4-5 orders of magnitude brighter. A clean measurement therefore requires 
+instrumental systematics that are, when combined, four to five orders of magnitude brighter. A clean measurement therefore requires 
 an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
@@
 \begin{itemize}
-\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Certain analysis techniques can lead to the loss of the EoR 
-signal. If not corrected for, this loss could lead to a false non-detection. Computing signal loss correctly has subtle challenges 
-but is necessary to ensure the accuracy of any result. 
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
+in a power spectrum estimate.
+Certain analysis techniques can cause this loss, and if not corrected for, it could lead to false non-detections and overly aggressive upper limits.
+Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
 \item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result 
@@
 measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
-successful EoR detection would also imitate a bias. Proving a bias is EoR may be the most difficult challenge for $21$ cm 
+successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
 analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
@@
 they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
-Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be considered for robust $21$ 
+Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be performed for robust $21$ 
 cm results.
@@
 
-In this section we illustrate how signal loss arises in analysis. Signal loss refers to attenuation of the target cosmological signal 
-in a power spectrum estimate. It can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during 
+Signal loss can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during 
 spectral calibration, applying a delay-domain filter, or by weighting data by itself. Here we focus on signal loss associated with 
@@
 
-We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities in Jy. It has length ($N_{t}, N_{f}$), where 
+We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has length ($N_{t}, N_{f}$), where 
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
-the Fourier transform of the sky along $2$ spatial dimensions, and since we are interested in $3$-dimensional Fourier-modes 
+the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
 we only need to take one Fourier transform of our data along the line-of-sight dimension. We do this when forming the un-
@@
 
-\noindent The matrix $\textbf{Q}$ is an operator that takes our frequency-domain visibilities and Fourier-transforms them into 
+\noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
 power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
@@
 \noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. The data analyst has a choice for $
-\textbf{M}$ --- for simplicity in this section we set $\textbf{M} \propto \textbf{I}$, although we explore other cases for the analysis 
+\textbf{M}$ --- for simplicity in this section we set $\textbf{M} = \textbf{I}$, although we explore other cases for the analysis 
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
@@
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 we use $\sim$$8$ hours of data for our analysis (with channel 
+might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis)we use $\sim$eight hours of data for our analysis (with channel 
 widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
@@
 single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
-realistic EoR signal would have a sloped power spectrum in $\hat{\textbf{p}}$(k) (instead of flat, as in the case of white noise), 
+realistic EoR signal would have a sloped power spectrum in $\textbf{p}$(k) (instead of flat, as in the case of white noise), 
 which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
@@
 
-If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue of $\textbf{C}$ would be 
+If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
 representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
-particular data realization, its eigenvalues may differ from the truth. Said differently, shapes that may not exist (or have a 
+particular data realization, its eigenvalues and eigevectors may differ from the truth. Said differently, shapes that may not exist (or have a 
 weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
@@
 signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
-project out the zeroth eigenmode (i.e. zero out all eigenmodes except the first one), thereby down-weighting the foregrounds 
-perfectly and nothing else. Hence, we are not using information from all the weaker eigenmodes which carry the risk of 
+project out the zeroth eigenmode (i.e.
+zero out all eigenmodes except the first one), thereby down-weighting the foreground-dominating mode only.
+Hence, we are not using information from all the weaker eigenmodes which carry the risk of
 describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
@@
 power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
-demonstrating that if we can model our foregrounds perfectly (and disentangle them from other modes), we can down-weight 
+demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
 them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
@@
 original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
-estimate for our dataset. This error is indicated by the grey star in Figure \ref{fig:toy_error1} and matches our theoretical 
+estimate for our dataset. This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical 
 prediction (green).
@@
 In Figure \ref{fig:toy_error2} we compare the two methods of bootstrapping: sampling all elements randomly (black points) 
-versus sampling just the final element randomly (grey points). The two converge for datasets with small numbers of elements, 
+versus sampling just the final element randomly (gray points). The two converge for datasets with small numbers of elements, 
 when filling a few spots randomly is nearly the same as filling only the last spot randomly. However, there is also increased 
@@
 of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
-Two bootstrapping methods are shown here --- sampling all elements with replacement (grey) and sampling only the last element with replacement (black).
+Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black).
 The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.}
@@
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
-estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.
-Whether the loss would be estimated at the same level if different $21$ cm simulations were used remains an open question.}
+estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.}
 
@@
 spectrum according to OQE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $P_{in}$ and $P_{out}$, defined as (ignoring normalization factors):
+output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as (ignoring normalization factors):
 
@@
 \label{eq:Pin}
-P_{in,\alpha} \propto \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} = \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \label{eq:sigloss}
-P_{out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&\propto& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+P_{\rm out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
+&=& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 
-$P_{in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
-$P_x$ is the power spectrum of the data, $P_r$ is the power spectrum of the
-data plus injection, and $P_out$ is the difference in power caused by the injected signal.
-
-One may wonder why $P_{out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{out,\alpha} \propto \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
-expression fails to include correlations between the EoR signal and data, which emerges as statistical noise that is added to the 
-estimate, decreasing the value of $P_{out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
+$P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+$\hat{\textbf{p}}_{x}$ is the power spectrum of the data, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
+data plus injection, and $P_{\rm out}$ is the difference in power between the two.
+
+In short, we can summarize our signal loss computation as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (though our actual detailed computation is described in the next section).
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\textbf{x}$ by the following reasoning.
+
+In a limit with no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
+\begin{equation}
+\x \equiv \f + \s,
+\end{equation}
+where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
+In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat$.
+This can be parametrized as
+\begin{equation}
+\label{eq:LinearPspecSum}
+\langle \phat \rangle  = \langle g(\x) \rangle = c_{\rm fg} \p_{\rm fg} + c_{\rm eor} \p_{\rm eor},
+\end{equation}
+where $c_{\rm eor}$ and $c_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
+It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the result is an approximation.
+
+Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat / c_{\rm eor}$.
+Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
+The most conceptually straightforward way to compute $c_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
+\begin{equation}
+\label{eq:Deriv1}
+\hat{c}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+\end{equation}
+However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case---if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
+Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $\p^*_{\rm eor}$), computing instead
+\begin{equation}
+\label{eq:Deriv2}
+\hat{c}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{\p^*_{\rm eor}},
+\end{equation}
+which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
+Essentially, one is computing the slope of $\langle \phat \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
+Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$.
+In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.
+
+Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$, and the denominator to $P_{\rm in}$, where the function $g$ is our OQE power spectrum pipeline.
+
+One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
+$P_{out,\alpha} = \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
+expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
+estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
 
@@
 \label{eq:crossterm}
-P_{out,\alpha} &\propto& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+P_{\rm out,\alpha} &=& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
 \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&\propto& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+&=& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
@@
 
-We see that $P_{out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only 
+We see that $P_{\rm out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only 
 $\textbf{x}$ are small, yields:
@@
 \label{eq:pout_expand}
-P_{out, \alpha,\textbf{e} \gg \textbf{x}} &\propto& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + 
+P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + 
 \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
@@
 
-We see that our naive expression for $P_{out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
+We see that our naive expression for $P_{\rm out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
 additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
@@
 The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-simulation, which would yield greater values for $P_{out}$ and thereby underestimate signal loss. Therefore, in our revised 
-signal loss computation we use the full quantity for $P_{out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
+simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
+signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
 weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 
-The relationship between the input and output power spectra, $P_{in}$ and $P_{out}$, can be thought of as a transfer function 
-which, for a sampling of $P_{in}$ and $P_{out}$ provides a mapping from an input power spectrum distribution into an output 
+The relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
+which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
 distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
@@
 ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
-expressions for $P_{in}$ and $P_{out}$ become:
+expressions for $P_{\rm in}$ and $P_{\rm out}$ become (ignoring normalization factors):
 
 \begin{eqnarray}
-P_{in,\alpha} &\propto& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{out,\alpha} &\propto& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}
+P_{\rm in,\alpha} &=& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}
 \textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
@@
 
-Our signal loss transfer function for one $k$ value is shown in Figure \ref{fig:sigloss_transfercurve} and compares the weighted 
-case ($\textbf{R} = \textbf{C}^{-1}$, left plot) with the unweighted case ($\textbf{R} = \textbf{I}$, right plot). The figures depict a 
-kernel density estimation of our input to output power spectrum transfer function. To sample the distribution, we run $40$ total 
-injection levels, where the amplitude of \textbf{e} is increased in even increments on a lin-log grid and ranges from $P_{in} \sim 
--10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$ (negative $P_{in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is 
-negative and the other is positive) to $P_{in} \sim10^{13} \, mK^{2} (h^{-1} Mpc)^{3}$. For each injection, we perform $20$ 
-bootstraps over baselines, as explained in Section \ref{sec:Boot}, resulting in a total of $800$ data points on our $P_{in}$ vs. 
-$P_{out}$ grid. We have verified that the transfer function is symmetric for negative and positive $P_{in}$'s, and so we fold all 
-the values into positive ones to increase our signal-to-noise.
-
-The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
-unweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $P_{out}$ value for every 
-$P_{in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
-scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
-\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{out}$ values that results from the same 
-$P_{in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
-the spread in the weighted case (left plot).
-
-There is a second component of scatter that is less intuitive, only applies (at a low level) to the weighted case, and represents 
-intrinsic scatter in signal loss. The origin of this scatter stems from how much the random EoR signal $\textbf{e}$ happens to 
-look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for. For example, if we 
-are extremely unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$. An 
-empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal. On the other hand, the 
-less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result. The intrinsic scatter we can get is not a 
-dominant factor in this case but it is important to correct for the fact that a particular $P_{out}$ value could arise from a range of 
-$P_{in}$ values. We correct for this, as explained later in this section.
-
-Finally, the solid grey horizontal lines in Figure \ref{fig:sigloss_transfercurve} mark the peak of the data distribution $
-\hat{\textbf{p}}$ (the distribution is created from the $20$ bootstraps) for both the inverse covariance weighted and unweighted 
-cases. One can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
-value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$ using the transfer curve for the inverse covariance weighted case, implying a 
-signal loss factor of $\sim1000$.
+The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
+In practice, however, the signal loss itself is a random variable --- some realizations of the cosmological signal may be more correlated with foreground modes than others, leading to more signal loss.
+This leads to two issues.
+The first is that Equation \eqref{eq:LinearPspecSum} may not hold.
+In particular, a third term that is a quadratic combination of $\f$ and $\s$ (e.g., $\f^\dagger \C^{-1} \s$) may appear.
+However, we can circumvent this issue by decomposing $\f$ into a sum of two vectors, one that is proportional to $\s$ and one that is orthogonal to $\s$.
+The former can be absorbed into the EoR term (modifying the signal loss factor in the process), while the latter can be absorbed into the foreground term.
+
+The second issue to tackle is how one incorporates the randomness of $c_{\rm eor}$ into our signal loss corrections.
+Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat)$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat$, which is given by
+\begin{equation}
+\label{eq:Bayes}
+p( \p_{\rm eor} | \phat) \propto \mathcal{L} (  \phat | \p_{\rm eor})  p( \p_{\rm eor}),
+\end{equation}
+where $p( \p_{\rm eor})$ is the prior on $\p_{\rm eor}$ and $\mathcal{L} $ is the likelihood function.
+Since the likelihood is defined as the distribution of the measured result $ \phat$ given the theoretical power spectrum $\p_{\rm eor}$, we may construct this function simply by fixing $\p_{\rm eor}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum.
+The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $\p_{\rm eor}$.
+
+In our code, we simulate $20$ realizations of $\p_{\rm eor}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
+We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs.
+$P_{\rm out}$ grid.
+We smooth the 2D distribution using kernel density estimators.
+Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
+
+The result is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.
+Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$.
+The final result can then be normalized to give $p( \p_{\rm eor} | \phat)$.
+If $\phat$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat$, before performing the final summation and normalization.
+In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
+\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
+From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
+value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$.
+Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
+We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
+
+As a final complication to our procedure, we note that there will be some intrinsic scatter in our likelihood due to our having only a finite number of simulations.
+This is shown by the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in Figure \ref{fig:sigloss_transfercurve}.
+To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
+The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
+By doing this, we are left with the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
+look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
+As an extreme example, if we are very unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
+An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
+On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
+
+%The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
+%nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
+%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $P_{\rm out}$ value for every 
+%$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
+%scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
+%\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
+%every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{\rm out}$ values that results from the same 
+%$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
+%the spread in the weighted case (left plot).
 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{in}$ and $P_{out}$, as defined by Equations 
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations 
 \eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
 heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
-diagonal line marks a perfect unity mapping, and the solid grey horizontal line denotes the peak of $\hat{\textbf{p}}$, the data 
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}$, the data 
 distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
@@
 
-One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{in}$ values it appears that we can have 
-signal gain ($P_{out} > P_{in}$). This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}
+One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have 
+signal gain ($P_{\rm out} > P_{in}$). This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}
 $ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. As $\textbf{e}$ increases, we move 
-into a regime where $P_{out} \sim P_{in}$, and then eventually into a regime where $P_{out} < P_{in}$ when $\textbf{e}$ is 
+into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
 large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
 the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
-
-We now explain how we use the transfer curves to map our data (a distribution along $P_{out}$) to a signal-loss corrected 
-distribution (along $P_{in}$) that takes into account the range of signal loss that can be associated for a particular $P_{out}$ 
-value.
-
-\cc{can someone help me supplement the next 3 paragraphs with math?}
-
-Beginning with smoothed probability distributions of the transfer function for the two cases (weighted and unweighted), defined 
-as:
-
-\begin{equation}
-\cc{fill in},
-\end{equation}
-
-\noindent we fit an $8$th order polynomial to each, representing mean signal loss functions. We then account for the second 
-component of scatter as described previously by de-convolving out $P_{out, unweighted}$ from $P_{out, weighted}$ for each 
-$P_{in}$ value:
-
-\begin{equation}
-\cc{fill in}.
-\end{equation}
-
-In other words, we only account for the extra scatter that the weighted case has over the unweighted case, which, as can be 
-seen in Figure \ref{fig:sigloss_transfercurve}, is not large.
-
-Equipped with our new signal loss curves, we multiply our data distribution $\hat{\textbf{p}}$ element-wise to all $P_{in}$ 
-columns, treating positive and negative halves of the data distribution separately:
-
-\begin{equation}
-\cc{fill in}.
-\end{equation}
-
-We note that for PAPER-64, depending on the $k$-value, $\hat{\textbf{p}}$ is sometimes narrowly peaked at positive power 
-spectrum values (signifying detections of power) and sometimes centered around zero, representing measurements that are 
-consistent with zero.
-
-Finally, we sum up all rows of $P_{out}$ where each row is a $P_{in}$ probability distribution allowed by our measurements:
-
-\begin{equation}
-\cc{fill in}.
-\end{equation}
-
-This results in a final $P_{in}$ distribution --- the distribution of our data as seen through the signal loss lens. We compute 
-power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals (recall 
-that the spread in these probability density functions mostly comes from bootstrapping the data).
 
@@
 power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
-grey points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss correction, it 
+gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss correction, it 
 is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (grey) points, 
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (gray) points, 
 with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
@@
 
-For Method \#1, we used $P_{out}$ as the output of interest.
+For Method \#1, we used $P_{\rm out}$ as the output of interest.
 For that method, we had asked the question ``What is the input power associated with an excess similar in amplitude to the data power spectrum?" For this second method, we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of looking at $P_{out}$, we now use $P_{r}$, the weighted power spectrum of the data plus signal, as the output of interest.
+Instead of looking at $P_{\rm out}$, we now use $P_{r}$, the weighted power spectrum of the data plus signal, as the output of interest.
 
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $P_r$ to injected $P_{in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
 data only).
-\cc{this next sentence does not make sense} As $P_{in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
+\cc{this next sentence does not make sense} As $P_{\rm in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
 Above some level the injected signal is clearly detectable.
@@
 
-Formally we can express our test as: ``What is the $P_{in}$ such that
+Formally we can express our test as: ``What is the $P_{\rm in}$ such that
 \begin{equation}
@@
 The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} next to the limits from Method \#1.
-\dcj{Hopefully they are similar!} In the rest of this paper, we use Method \#1 \cc{why?}.
+In the rest of this paper, we use Method \#1 \cc{why?}.
 
@@
 \includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
-\caption{A comparison of Method \#1 
-signal loss corrected power spectrum (black dots)
-and Method \#2 uppers limits at 90\% confidence (red curve).
+\caption{A comparison of the Method \#1 
+signal loss corrected power spectrum (black and gray points)
+and Method \#2 uppers limits at $9$0\% confidence (red curve).
 Also shown are the upper limits of the unweighted power spectrum
@@
 correction, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (grey curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
+becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss correction, 
@@
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
-are shown before (grey) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
+are shown before (gray) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
 are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
@@
 Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure 
-\ref{fig:ps1_data}. Again, black and grey points correspond to positive and negative power spectrum values respectively, with 
+\ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
 $2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and grey points correspond to positive and 
+	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
 negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
@@
 	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (grey). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
+published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
 \sqrt{3}$ for 3 baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
@@
 Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}, where the black and grey points represent positive and negative power spectrum values, respectively (with 
+\ref{fig:ps_noise}, where the black and gray points represent positive and negative power spectrum values, respectively (with 
 $2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power 
@@
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
-power spectrum points and their $2\sigma$ errors are show in black and grey (positive and negative values), where we use $
+power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
 \hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
@@
 	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
-$2\sigma$ errors (grey shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating 
+$2\sigma$ errors (gray shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating 
 even and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
@@
 
-\cc{Note to Adrian: I standardized all Q indices to be superscripts instead of subscripts. Also standardized equations to be 
-``Equation eqref" (spell out Equation, and use eqref for references)}
-
-In this Appendix, we examine a toy model for signal loss. Our goal is to build intuition by deriving an analytic formula for power 
-spectrum signal loss. We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum 
-estimate.
+In this Appendix, we examine a toy model for signal loss.
+Our goal is to build intuition by deriving an analytic formula for power spectrum signal loss.
+We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum estimate.
 
 The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\acl{Also need to state in a footnote that for this section only we'll assume without loss of generality that the data are real}
 \begin{equation}
@@
 \end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix. In our case, however, we do not have \emph{a priori} knowledge of the 
-covariance matrix. Thus, we replace $\C$ with $\Chat$, its data-derived approximation. Our estimator then becomes
+is the $\alpha$th diagonal element of the Fisher matrix\footnote{For this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real.}.
+In our case, however, we do not have \emph{a priori} knowledge of the covariance matrix.
+Thus, we replace $\C$ with $\Chat$, its data-derived approximation.
+Our estimator then becomes
 \begin{equation}
@@
 \end{equation}
-with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than 
-unity). We will now provide an explicit demonstration of this by modeling the estimated covariance as
+with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than unity).
+We will now provide an explicit demonstration of this by modeling the estimated covariance as
 \begin{equation}
@@
 \end{equation}
-where $\eta$ is parameter quantifying our success at estimating the true covariance matrix. If $\eta = 0$, our covariance 
-estimate has perfectly modeled the true covariance and $\Chat = \C$. On the other hand, if $\eta =1$, then our covariance 
-estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of 
-overfitting and signal loss.
-
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to 
-express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$. We begin by expressing $
-\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
+where $\eta$ is parameter quantifying our success at estimating the true covariance matrix.
+If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
+On the other hand, if $\eta =1$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
+
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
+We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
 \begin{equation}
@@
 \begin{equation}
-\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha 
-\alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
-\end{equation}
-where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha 
-\C^{-1}\x $. Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$. Inserting 
-these expressions into our estimator gives
-\begin{eqnarray}
+\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
+\end{equation}
+where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
+Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$.
+Inserting these expressions into our estimator gives
+\begin{equation}
 \label{eq:phatlossexpanded}
-\hat{p}_\alpha^\textrm{loss} &=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 
--\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 
-\frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1} \nonumber \\
-&=& \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}}\left(1-2\beta + \beta^2\right)\sum_{n=0}^\infty \sum_{k=0}^n {n \choose k} 
-\left( \frac{\varepsilon h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)^k \left( - \frac{\varepsilon^2 h_\alpha^2}{2 F_{\alpha \alpha}}
-\right)^{n-k},
-\end{eqnarray}
-where $\beta \equiv \eta g/[1+ \eta (g-1)]$ and $\varepsilon \equiv \beta / g$. To proceed, we take the ensemble average of $
-\hat{p}_\alpha^\textrm{loss}$ to understand its average statistical properties. Inspecting Equation \eqref{eq:phatlossexpanded}, 
-we see that its expectation value is a linear sum of terms of the form $\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \rangle$, 
-where $a$, $b$, and $c$ are integers. Expanding $\beta$ in powers of $g$, we have
-\begin{equation}
-\label{eq:betahh}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle = \sum_{m_1 = 1}^\infty \cdots \sum_{m_{a+d} = 1}^\infty 
-\frac{(-\eta)^{m_1 + \dots + m_{a+d}}}{(1-\eta)^{m_1 + \dots + m_a}} \langle g^{m_1 + \dots + m_{a+d}-d} h_\alpha^b h_{\alpha 
-\alpha}^c \rangle.
-\end{equation}
-Writing out the ensemble averaged quantity on the right hand side and defining $M \equiv m_1 + \dots + m_{a+d}$ yields
-\begin{eqnarray}
-\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle &=& \langle (\x^t \C^{-1} \x)^M (\x^t \C^{-1} \Q^\alpha 
-\C^{-1} \x)^b (\x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x )^c \rangle \nonumber \\
-&=& \sum_{i_1}^N \sum_{j_1}^N \cdots  \sum_{k_1}^N \sum_{l_1}^N \cdots  \sum_{p_1}^N \sum_{q_1}^N \cdots  ( \C^{-1} 
-\Q^\alpha \C^{-1} \Q^\alpha \C^{-1} )_{p_1 q_1} \dots (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1})_{p_c q_c}  \nonumber \\
-&&  \times ( \C^{-1} \Q^\alpha \C^{-1})_{k_1 l_1} \dots ( \C^{-1} \Q^\alpha \C^{-1})_{k_b l_b} \C^{-1}_{i_1 j_1}\dots \C^{-1}_{i_M 
-j_M} \langle x_{i_1} x_{j_1} \dots   x_{k_1} x_{l_1} \dots  x_{p_1} x_{q_1} \dots \rangle, \quad
-\end{eqnarray}
-where $N$ is the length of vector $\x$, i.e., the number of data points. To further simplify this expression, we assume that the 
-data are Gaussian distributed. The expectation value on the right hand side can then be reduced to a sum of product of 
-covariances, where each term in the sum is comprised of a particular way to partition the copies of $x$ into pairs. However, in 
-the limit of large $N$ one particular partitioning dominates, and the result can be approximated as \acl{Should probably explain 
-this more fully}
-\begin{equation}
-\langle g^{m_1 + \dots + m_{a+d}} h_\alpha^b h_{\alpha \alpha}^c \rangle \approx N^{m_1 + \dots + m_{a+d}} \left[ \textrm{tr} 
-(\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c,
-\end{equation}
-and re-inserting this into Equation \eqref{eq:betahh} yields
-\begin{equation}
-\langle \beta^a h_\alpha^b h_{\alpha \alpha}^c \varepsilon^d \rangle \approx \left[ \frac{\eta N}{1+\eta (N-1)} \right]^a 
-\left[ \frac{\eta }{1+\eta (N-1)} \right]^d \left[ \textrm{tr} (\C^{-1} \Q^\alpha )\right]^b (2 F_{\alpha \alpha})^c.
-\end{equation}
-With this result, taking the ensemble average of Equation \eqref{eq:phatlossexpanded} is relatively straightforward. One simply 
-replaces every copy of $\beta$ with $\beta_N \equiv \eta N / [1 + \eta (N-1)]$, every copy of $\varepsilon$ with $\varepsilon_N 
-\equiv  \eta  / [1 + \eta (N-1)]$, every copy of $h_\alpha$ with $ \textrm{tr} (\C^{-1} \Q^\alpha )$, and every copy of $h_{\alpha 
-\alpha}$ with $2F_{\alpha \alpha}$. Performing these substitutions and recalling \acl{make sure the reader will indeed be 
-recalling at this point} that $\langle \hat{p}_\alpha \rangle = \langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
-\begin{equation}
-\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle} = \frac{1- 2\varepsilon_N + \varepsilon_N^2 
-\left[ \textrm{tr} (\C^{-1} \Q^\alpha) \right]^2 / 2F_{\alpha \alpha}}{(1-\beta_N)^2}.
-\end{equation}
-This quantity is in general less than unity, and quantifies the signal loss relative to the ideal estimator $\hat{p}_\alpha$ where 
-we know the true covariance $\C$. As an illustrative example, for cases where $\C \propto \I$, this reduces to
-\begin{equation}
-\frac{\langle \hat{p}_\alpha \rangle}{\langle \hat{p}_\alpha^\textrm{loss} \rangle}  \Bigg{|}_{\C \propto \I} = \left( \frac{1-
-\varepsilon_N}{1-\beta_N} \right)^2 = \left[\frac{1+ \eta(N-2)}{1- \eta}\right]^2.
-\end{equation}
-This is shown in Figure \ref{fig:analytic_sig_loss} for $N=20$. As expected, the signal loss factor is unity for $\eta=0$ (perfect 
-estimation of $\C$) and goes to infinity as $\eta$ approaches $1$.
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\columnwidth]{plots/analytic_sig_loss.pdf}
-	\caption{Power spectrum signal loss for $N=20$ for a toy model where $\Chat = (1-\eta) \C + \eta \x \x^t$.}
-	\label{fig:analytic_sig_loss}
-\end{figure}
-
-In general, one's estimate of the covariance will not be expressible in the form given by Equation \eqref{eq:ChatDef}. However, 
-the qualitative point here is that the signal loss can be expressed as a multiplicative factor. Even if $\Chat$ is more complicated 
-than the form used for this toy model, the same mathematical technique of expressing the estimator as a series of higher-point 
-functions, reducing these functions (assuming Gaussianity) to two-point functions, and re-summing any power series will show 
-that the signal loss is a multiplicative factor. \acl{I can express this last bit more eloquently, but it's late and I'm tired and need to 
-eat dinner.}
+\hat{p}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
+\end{equation}
+Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading order in $\eta$. The result is
+\begin{equation}
+\hat{p}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
+\end{equation}
+Taking the ensemble average of both sides and noting that the true power spectrum $p_\alpha$ is equal to $\langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
+\begin{equation}
+\langle \hat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N) p_\alpha,
+\end{equation}
+where $N$ is the length of $\x$.
+In the last step we dropped the final term, since it scales as $\eta p_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
+Now, recall that $p_\alpha$ is the \emph{true} power spectrum.
+This means that it can be decomposed into the sum of foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
+This toy example, while not definitive, serves to motivate the form of Equation \eqref{eq:LinearPspecSum}.
 

### 2017-11-29 PAPER.tex
minor edits

@@
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
-foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting 
-where $\textbf{C}$ is derived from the data (left), contrasted with projecting out the first eigenmode only (right). In the former 
+foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+The foregrounds peak at a $k$ mode based on the frequency of the sinusoid used to create it.
+We compare inverse covariance weighting
+where $\textbf{C}$ is derived from the data (left), with projecting out the first eigenmode only (right). In the former 
 case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 

### 2017-11-29 PAPER.tex
added adrian's math into signal loss sections

@@
 $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
-$\hat{\textbf{p}}_{x}$ is the power spectrum of the data, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
-data plus injection, and $P_{\rm out}$ is the difference in power between the two.
-
-In short, we can summarize our signal loss computation as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (though our actual detailed computation is described in the next section).
+$\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
+data plus injection, and $P_{\rm out}$ is the difference between $\hat{\textbf{p}}_{r}$ and $\hat{\textbf{p}}_{x}$.
+
+In short, we can summarize a signal loss correction factor as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (our detailed computation is described in the next section).
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\textbf{x}$ by the following reasoning.
@@
 
-Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat / c_{\rm eor}$.
+Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / c_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss correction factor.
 Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
@@
 \end{equation}
-However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case---if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
+However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
 Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $\p^*_{\rm eor}$), computing instead
@@
 One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{out,\alpha} = \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
+$P_{\rm out,\alpha} = \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
 expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 

### 2017-11-30 PAPER.tex
added refs

@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Data Analysis Methods for the Detection of the Epoch of Reionization}
+\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization Power Spectrum: A Revised Study of PAPER-64}
 \shortauthors{Cheng et al.}
@@
 \begin{document}
-\title{Data Analysis Methods for the Detection of the Epoch of Reionization}
+\title{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64}
 
@@
 One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition. This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength 
+its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); .
+This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
 of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
@@
 learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum 
-detection with an eventual $350$ elements using current analysis techniques (\citealt{deboer_et_al2017}; 
-\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}).
+detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).
 
 The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter. A clean measurement therefore requires 
+instrumental systematics that are, when combined, four to five orders of magnitude brighter (\citealt{santos_et_al2005}; \citealt{ali_et_al2008}; \citealt{deOliveiraCosta_et_al2008}; \citealt{jelic_et_al2008}; \citealt{bernardi_et_al2009}; \citealt{bernardi_et_al2010}; \citealt{ghosh_et_al2011}).
+A clean measurement therefore requires
 an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE; \citealt{liu_tegmark2011}; \citealt{liu_et_al2014b}). Before showing 
+estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, and \citet{trott_et_al2012}.
+Before showing
 how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
@@
 Foreground bias is perhaps one of the main factors limiting $21$ cm results. Foreground signals lie $\sim4$-$5$ orders of 
-magnitude above the cosmological signal. Though there are many techniques proposed for removing foregrounds, most 
+magnitude above the cosmological signal.
+Though there are many techniques proposed for removing foregrounds (see e.g.
+\citealt{vedantham_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
 experiments remain ultimately limited by residuals rather than noise.

### 2017-11-30 PAPER.tex
added refs

@@
 weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
-weighting that also takes into account frequency correlations. This weighting has the effect of down-weighting correlated 
+weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}).
+This weighting has the effect of down-weighting correlated
 information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
@@
 methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
-itself. By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
+itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
 consider such as the independence of values in a dataset.
@@
 dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
-systematics (\citealt{keating_et_al2016}). An EoR detection must pass jack-knife and null tests.
+systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g.
+\citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
+An EoR detection must pass jack-knife and null tests.
 \end{itemize}

### 2017-11-30 PAPER.tex
work on citations and some minor language tweaks

--- 2017-11-29 PAPER.tex
@@
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today.
+web of galaxies we observe today \citep[for a review, see][]{furlanetto_et_al2006}.
 
@@
 The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter. A clean measurement therefore requires 
+instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{bernardi_et_al2009, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
+A clean measurement therefore requires
 an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
@@
 purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for 
-the sake of completeness. The specifics of how signal loss crops up in PAPER's analysis is later described in Section 
+the sake of completeness. The specifics of how signal loss appears in PAPER's analysis is later described in Section 
 \ref{sec:Sigloss}.
@@
 
-It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our 
+Since $\hat{\textbf{C}}$ is estimated from our data, its eigenspectrum differs from the eigenspectrum of our 
 true $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
@@
 
-In a $21$ cm power spectrum, detections could be the EoR signal, but they could also (and unfortunately more likely) be 
-attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
-future $21$ cm data analyses. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
+In a $21$ cm power spectrum, detections could be the EoR signal, but they could also 
+%(and unfortunately more likely) 
+be attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
+future $21$ cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
 that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
@@
 antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
-wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; 
-\citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}). The wedge describes a region in $k$-
-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
-proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and remove foregrounds, as done by P64, 
+wedge"
+\citep{datta_et_al2010, parsons_et_al2012b, vedantham_et_al2012, pober_et_al2013, thyagarajan_et_al2013, liu_et_al2014a, liu_et_al2014b, patil_et_al2017}. 
+The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
+proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and 
+%remove 
+avoid foregrounds, as done by P64, 
 \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
@@
 foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the 
-antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
+antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017}.
 
@@
 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data (\citealt{moore_et_al2013}) from PAPER's $30$ m East/West baselines (Figure 
+focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
 \ref{fig:ant_layout}). For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we 
@@
 are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
-also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). We also graciously thank SKA-
+also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
+SAK is supported by the University of Pennsylvania School of Arts and Sciences Disseeration Completion Fellowship.
+We graciously thank SKA-
 SA for site infrastructure and observing support.

### 2017-11-30 PAPER.tex

--- 2017-11-30 PAPER.tex
@@
 The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter (\citealt{santos_et_al2005}; \citealt{ali_et_al2008}; \citealt{deOliveiraCosta_et_al2008}; \citealt{jelic_et_al2008}; \citealt{bernardi_et_al2009}; \citealt{bernardi_et_al2010}; \citealt{ghosh_et_al2011}).
+instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
 A clean measurement therefore requires
+
 an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 

### 2017-12-01 PAPER.tex
-Made minor Jonnie edits -Commented out method #2 stuff for now

@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization Power Spectrum: A Revised Study of PAPER-64}
+\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization Power Spectrum}
 \shortauthors{Cheng et al.}
@@
 \usepackage{ctable}
+\usepackage{comment}
 \citestyle{aa}
@@
 in a power spectrum estimate.
-Certain analysis techniques can cause this loss, and if not corrected for, it could lead to false non-detections and overly aggressive upper limits.
+Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits.
 Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
@@
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
-previously underestimated in the P64 analysis
+previously underestimated in the P64 analysis.
 
@@
 Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
-confidence intervals for our measurements. Two popular ways of empirically calculating errors on a power spectrum 
+confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
 measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's 
@@
 of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
-from the original set of measurements with replacement (every $N$th slot is filled randomly for each bootstrap). Next we take 
+from the original set of measurements with replacement (i.e. every $N$th slot is filled randomly for each bootstrap). Next we take 
 the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
@@
 replacement and draw the last slot randomly with replacement. In doing so there is a small chance a bootstrap will consist of 
-$5$ independent measurements, but even with $4$ our sensitivity is nearly maximized. %One may wonder whether this 
-change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap. However, as 
-long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the 
-inherent variability in a dataset.
+$5$ independent measurements, but even with $4$ our sensitivity is nearly maximized. 
+%One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
+However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
 
@@
 However, this isolation is not perfect.  In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond 
-the length of a baseline are often still contaminated at a low level. This leakage, especially at low $k$'s, can be attributed to 
+the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
 convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
@@
 
-Confirming foreground detections at higher $k$'s is more difficult. In the next section (Section \ref{sec:JackknifeOverview}), we 
-will present some tests that can help distinguish these excesses from that of EoR.
+Determining the source of detections at higher $k$'s is more difficult.
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}).
+In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
 
@@
 
-In short, we can summarize a signal loss correction factor as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (our detailed computation is described in the next section).
+In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (our detailed computation is described in the next section).
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\textbf{x}$ by the following reasoning.
@@
 \label{eq:LinearPspecSum}
-\langle \phat \rangle  = \langle g(\x) \rangle = c_{\rm fg} \p_{\rm fg} + c_{\rm eor} \p_{\rm eor},
-\end{equation}
-where $c_{\rm eor}$ and $c_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
+\langle \phat \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
+\end{equation}
+where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
 It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the result is an approximation.
 
-Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / c_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss correction factor.
+Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
 Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $c_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
+The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
 \begin{equation}
 \label{eq:Deriv1}
-\hat{c}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+\hat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
 \end{equation}
@@
 \label{eq:Deriv2}
-\hat{c}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{\p^*_{\rm eor}},
+\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{\p^*_{\rm eor}},
 \end{equation}
@@
 distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss 
-transfer function and detail two different computations used to translate our power spectrum result into one viewed through a 
-signal loss lens. We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also 
-state that they yield similar results...}
+transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
+signal loss lens. 
+%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
 
@@
 
-\begin{center}
-METHOD \#1
-\end{center}
+%\begin{center}
+%METHOD \#1
+%\end{center}
 
@@
 However, we can circumvent this issue by decomposing $\f$ into a sum of two vectors, one that is proportional to $\s$ and one that is orthogonal to $\s$.
-The former can be absorbed into the EoR term (modifying the signal loss factor in the process), while the latter can be absorbed into the foreground term.
-
-The second issue to tackle is how one incorporates the randomness of $c_{\rm eor}$ into our signal loss corrections.
+The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
+
+The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat)$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat$, which is given by
@@
 The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
-By doing this, we are left with the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
+Specifically, we deconvolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
+By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
 look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
@@
 
+\begin{comment}
 \begin{center}
@@
 \caption{A comparison of the Method \#1 
-signal loss corrected power spectrum (black and gray points)
+signal loss estimated power spectrum (black and gray points)
 and Method \#2 uppers limits at $9$0\% confidence (red curve).
@@
 \end{figure}
+\end{comment}
 

### 2017-12-01 PAPER.tex
small changes

--- 2017-11-30 PAPER.tex
@@
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today \citep[for a review, see][]{furlanetto_et_al2006}.
+web of galaxies we observe today.
 
@@
 The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{bernardi_et_al2009, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires
+instrumental systematics that are, when combined, four to five orders of magnitude brighter. A clean measurement therefore requires 
 an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
@@
 purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for 
-the sake of completeness. The specifics of how signal loss appears in PAPER's analysis is later described in Section 
+the sake of completeness. The specifics of how signal loss crops up in PAPER's analysis is later described in Section 
 \ref{sec:Sigloss}.
@@
 
-Since $\hat{\textbf{C}}$ is estimated from our data, its eigenspectrum differs from the eigenspectrum of our 
+It turns out that because we estimated $\hat{\textbf{C}}$ from our data, its eigenspectrum differs from the eigenspectrum of our 
 true $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
@@
 
-In a $21$ cm power spectrum, detections could be the EoR signal, but they could also 
-%(and unfortunately more likely) 
-be attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
-future $21$ cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
+In a $21$ cm power spectrum, detections could be the EoR signal, but they could also (and unfortunately more likely) be 
+attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
+future $21$ cm data analyses. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
 that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
@@
 antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
-wedge"
-\citep{datta_et_al2010, parsons_et_al2012b, vedantham_et_al2012, pober_et_al2013, thyagarajan_et_al2013, liu_et_al2014a, liu_et_al2014b, patil_et_al2017}. 
-The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
-proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and 
-%remove 
-avoid foregrounds, as done by P64, 
+wedge" (\citealt{parsons_et_al2012b}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{vedantham_et_al2012}; 
+\citealt{thyagarajan_et_al2013}; \citealt{pober_et_al2013}; \citealt{datta_et_al2010}). The wedge describes a region in $k$-
+space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
+proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and remove foregrounds, as done by P64, 
 \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
@@
 foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the 
-antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017}.
+antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge.
 
@@
 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
+focus solely on Stokes I estimated data (\citealt{moore_et_al2013}) from PAPER's $30$ m East/West baselines (Figure 
 \ref{fig:ant_layout}). For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we 
@@
 In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
-data only).
-\cc{this next sentence does not make sense} As $P_{\rm in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
-Above some level the injected signal is clearly detectable.
+data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).
+It is in this last region that we search for the point at which an injected signal would be clearly detected.
 
@@
 We note that a high SNR detection will require a different method, but we show this one to...
-\cc{fill in..}
+\cc{fill in..} \dcj{but we show this one to what?
+Why not just leave it with a period}
 
@@
 are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
-also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-SAK is supported by the University of Pennsylvania School of Arts and Sciences Disseeration Completion Fellowship.
-We graciously thank SKA-
+also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). We also graciously thank SKA-
 SA for site infrastructure and observing support.

### 2017-12-01 PAPER.tex
Moved Method 2 to an appendix.  Needs plots

@@
 Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$, and the denominator to $P_{\rm in}$, where the function $g$ is our OQE power spectrum pipeline.
+\dcj{Here is the post-hoc justification for this signal loss method.
+Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross terms in the estimation of a power spectrum.
+So we're just kicking the can down the road.
+}
 
@@
 transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
-signal loss lens. 
+signal loss lens. Interpretation of the signal injection results can framed in multiple ways which result in different answers. One 
+such alternative is described in Appendix \ref{sec:Pr_appendix}.
 %We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
+\dcj{Wait what?
+I think you are saying essentially that some x can remain in Pout which is what we are seeing.
+Or is this some extra bit of method which has been added to the analysis...}
 
@@
 
-\begin{comment}
-\begin{center}
-METHOD \#2
-\end{center}
-
-One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
-Small differences in approaches were found to cause large differences in the final answer.
-\cc{but aren't we arguing the opposite - that they yield similar answers?}
-
-For Method \#1, we used $P_{\rm out}$ as the output of interest.
-For that method, we had asked the question ``What is the input power associated with an excess similar in amplitude to the data power spectrum?" For this second method, we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of looking at $P_{\rm out}$, we now use $P_{r}$, the weighted power spectrum of the data plus signal, as the output of interest.
-
-This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
-data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).
-It is in this last region that we search for the point at which an injected signal would be clearly detected.
-
-One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
-Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
-This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself.
-In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual.
-We note that a high SNR detection will require a different method, but we show this one to...
-\cc{fill in..} \dcj{but we show this one to what?
-Why not just leave it with a period}
-
-Formally we can express our test as: ``What is the $P_{\rm in}$ such that
-\begin{equation}
-P_{r} > P_{x} \Lambda,
-\end{equation}  
-where $\Lambda$ represents a choice of threshold.'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
-One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e.
-the null test} the same.
-
- \begin{equation}
-\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
- \end{equation}
- where $\Prob(P_x)$ is the probability of obtaining the power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
-
-Probability vs.
-injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
-At low injection levels the variation between $x$ and $r$ is such that the null test is ruled out to within $20$\%.
-This is the level expected from two distributions with $\sim$10 effective samples.
-\dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
-
-Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
-As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
-We can also see that the probability does not perfectly converge at high injected power levels.
-\cc{why?} Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\% \dcj{Matt, put in actual value here} \mjk{The current image uses 90th percentile!}.
-
-The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} next to the limits from Method \#1.
-In the rest of this paper, we use Method \#1 \cc{why?}.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
-\caption{A comparison of the Method \#1 
-signal loss estimated power spectrum (black and gray points)
-and Method \#2 uppers limits at $9$0\% confidence (red curve).
-Also shown are the upper limits of the unweighted power spectrum
-(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
-\end{figure}
-\end{comment}
-
 \subsubsection{Minimizing Signal Loss}
@@
 
-With a signal loss formalism established (Method \#1, for the rest of this paper), we now have the capability of experimenting 
+With a signal loss formalism established, we now have the capability of experimenting 
 with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
@@
 also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-SAK is supported by the University of Pennsylvania School of Arts and Sciences Disseeration Completion Fellowship.
+SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
 We graciously thank SKA-
@@
 \label{eq:phatloss}
-\hat{p}_\alpha^\textrm{loss} = \frac{1} {2 \F_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
+\hat{p}_\alpha^\textrm{loss} = \frac{1} {2 \hat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
 \end{equation}
@@
 
+\section{Simplified Loss Correction}
+\label{sec:Pr_appendix}
+One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
+The method described in section \ref{sec:Sigloss} relies on several assumptions which required justification including the neglection of cross-terms in the power spectrum and indeed does not behave as expected at small injected values.
+However it is possible to make a simpler interpretation which requires less motivation.
+
+In the main text we made an estimate of the signal loss effecting only the injected eor by supposing that the lossy injected signal was the difference between the injected and not injected case $ P(s) = P(x+s) - P(x)$.
+Suppose that we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
+Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $P(x+s)$, the weighted power spectrum of the data plus injected signal.
+
+This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
+In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).
+It is in this last region that we search for the point at which an injected signal would be clearly detected.
+
+One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
+Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
+This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself.
+In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual.
+We note that a high SNR detection will require a different method.
+
+Formally we can express our test as: ``What is the $P_{\rm in}$ such that
+\begin{equation}
+P_{r} > P_{x} \Lambda,
+\end{equation}  
+where $\Lambda$ represents a choice of threshold.'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e.
+the null test} the same.
+
+ \begin{equation}
+\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
+ \end{equation}
+ where $\Prob(P_x)$ is the probability of obtaining the power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+
+Probability vs.
+injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
+At low injection levels the variation between $x$ and $r$ is such that the null test is ruled out to within $20$\%.
+This is the level expected from two distributions with $\sim$10 effective samples.
+\dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
+
+Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
+As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
+We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
+Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\%.
+
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
+Overall the limits are slightly lower, with k modes differing by factors of 3 to 37.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
+\caption{A comparison of the Section \ref{sec:SiglossOverview} method
+against this method at $90$\% confidence (red curve).
+Also shown are the upper limits of the unweighted power spectrum
+(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
+\end{figure}
+
 \bibliographystyle{apj}

### 2017-12-01 PAPER.tex
added two new plots to the method2 appendix

@@
 
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
+\caption{The distribution of output power spectrum values for a 
+given injection level P$_{in}$.\label{fig:Pr_vs_Pin}}
+\end{figure}
+
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
@@
 It is in this last region that we search for the point at which an injected signal would be clearly detected.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
+\caption{The probability that an injected signal of level P$_{inj}$
+is observable at a 2$\sigma$ level above the value of P$_{data}$.
+\label{fig:Prob_vs_Pin}}
+\end{figure}
 

### 2017-12-01 PAPER.tex
added cites

--- 2017-12-01 PAPER.tex
@@
 Determining the source of detections at higher $k$'s is more difficult.
-In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}).
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
 In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
@@
 In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
-data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).
-It is in this last region that we search for the point at which an injected signal would be clearly detected.
+data only).
+\cc{this next sentence does not make sense} As $P_{\rm in}$ increases, the signal loss transfer curve approaches the power level of the data it does not dominate the covariance but still contributes enough to suppressing itself.
+Above some level the injected signal is clearly detectable.
 
@@
 We note that a high SNR detection will require a different method, but we show this one to...
-\cc{fill in..} \dcj{but we show this one to what?
-Why not just leave it with a period}
+\cc{fill in..}
 

### 2017-12-01 PAPER.tex
compiled and cleaned up appendix B

@@
 transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
-signal loss lens. Interpretation of the signal injection results can framed in multiple ways which result in different answers. One 
-such alternative is described in Appendix \ref{sec:Pr_appendix}.
+signal loss lens.
+Interpretation of the signal injection results can be framed in multiple ways which result in similar but not identical answers.
+One such alternative is described in Appendix \ref{sec:Pr_appendix}.
 %We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
@@
 
-In the main text we made an estimate of the signal loss effecting only the injected eor by supposing that the lossy injected signal was the difference between the injected and not injected case $ P(s) = P(x+s) - P(x)$.
+In the main text we made an estimate of the signal loss effecting only the injected eor by supposing that the lossy injected signal was the difference between the injected and not injected cases: $ P(e) = P(x+e) - P(x)$.
 Suppose that we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $P(x+s)$, the weighted power spectrum of the data plus injected signal.
+Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $P(x+e)$, the weighted power spectrum of the data plus injected signal ($\hat{\textbf{p}}_{r}$ in Section \ref{sec:Sigloss}).
 
@@
 \caption{The distribution of output power spectrum values for a 
-given injection level P$_{in}$.\label{fig:Pr_vs_Pin}}
+given injection level P$_{in}$.
+The $P_{\rm out}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
+It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
+We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
+The solid black
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data distribution.
+At low injection, $P_{\rm out}$ converges at the data level.}
+\label{fig:Pr_vs_Pin}
 \end{figure}
@@
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $P_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
-data only), very large levels are dominated by the injected signal, and a transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation).
-It is in this last region that we search for the point at which an injected signal would be clearly detected.
+In the 2D space relating total $\hat{\textbf{p}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+data only) and very large levels are dominated by the injected signal.
+It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
 
@@
 \includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
-\caption{The probability that an injected signal of level P$_{inj}$
-is observable at a 2$\sigma$ level above the value of P$_{data}$.
+\caption{The probability that an injected signal of level P$_{in}$
+is observable at a 2$\sigma$ level above the value of $\hat{\textbf{p}}_{x}$ (data).
+The different colors represent different $k$ values. We choose a probably of $90\%$ for our signal loss estimated power spectrum.
 \label{fig:Prob_vs_Pin}}
@@
 \end{equation}  
-where $\Lambda$ represents a choice of threshold.'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
 One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e.
@@
  \end{equation}
- where $\Prob(P_x)$ is the probability of obtaining the power spectrum $P_x$ found via bootstrapping and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $P_r$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+ where $\Prob(P_x)$ is the probability of obtaining the power spectrum $\hat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $\hat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
 
@@
 Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
-As can be seen in Figure \ref{fig:Pr_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
+As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
 We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
@@
 
-The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Method \#1), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
 Overall the limits are slightly lower, with k modes differing by factors of 3 to 37.
@@
 \includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
-\caption{A comparison of the Section \ref{sec:SiglossOverview} method
-against this method at $90$\% confidence (red curve).
+\caption{A comparison of the signal loss Section \ref{sec:Sigloss} method
+against the method in this appendix at $90$\% confidence (red curve).
 Also shown are the upper limits of the unweighted power spectrum

### 2017-12-01 PAPER.tex
added normalization M's to equations

@@
 spectrum according to OQE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as (ignoring normalization factors):
+output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as:
 
@@
 \label{eq:Pin}
-P_{\rm in,\alpha} = \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} = \textbf{M}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 P_{\rm out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&=& \textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
-^{\alpha}\textbf{R}_{x}\textbf{x}.
+&=& \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+^{\alpha}\textbf{R}_{x}\textbf{x},
 \end{eqnarray}
-
-$P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+where all $\textbf{M}$'s are normalization factors. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
 $\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
@@
 One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{\rm out,\alpha} = \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
+$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
 expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &=& (\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
-\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} - \textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+P_{\rm out,\alpha} &=& \textbf{M}_{rr}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+\textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&=& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
+&-& \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 \label{eq:pout_expand}
-P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + 
-\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
+P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
+ \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+ &+&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-P_{\rm in,\alpha} &=& \textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=& \textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} - \textbf{x}^{\dagger}
-\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
+P_{\rm in,\alpha} &=&  \textbf{M}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=&  \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
+&&\phantom{=====} -  \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 $2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
-noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
+noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
+a higher limit than P64 by a factor of $\sim10$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
 \cc{replace with kolopanis limit instead later}
@@
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
-loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
+loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at 
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim10$ in mK \cc{replace with kolopanis limit later}.}
 	\label{fig:ps1_data}
@@
 As a consequence of our investigations, we have also revised power spectrum results from PAPER-64. For an analysis of only 
-one baseline type, we quote a new $2\sigma$ upper limit of $(158.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
-P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+one baseline type, we quote a new $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
+P64 by a factor of $\sim10$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
+factor of $\sim10$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
 note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 

### 2017-12-02 PAPER.tex
added note about diagonal M's

@@
 \label{eq:Pin}
-P_{\rm in,\alpha} = \textbf{M}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} = \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \end{eqnarray}
-where all $\textbf{M}$'s are normalization factors. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+where, for illustrative purposes, all $\textbf{M}$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
 $\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
@@
 \begin{eqnarray}
-P_{\rm in,\alpha} &=&  \textbf{M}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm in,\alpha} &=&  \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
 P_{\rm out,\alpha} &=&  \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-\dcj{Wait what?
-I think you are saying essentially that some x can remain in Pout which is what we are seeing.
-Or is this some extra bit of method which has been added to the analysis...}
+%\dcj{Wait what? I think you are saying essentially that some x can remain in Pout which is what we are seeing. Or is this some extra bit of method which has been added to the analysis...}
 
@@
 This is the level expected from two distributions with $\sim$10 effective samples.
-\dcj{checked with a little python test but needs a cite} As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
+%\dcj{checked with a little python test but needs a cite} 
+As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
 

### 2017-12-02 PAPER.tex
Some changes, not all.

--- 2017-12-01 PAPER.tex
@@
 One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, this naive 
+$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
 expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
@@
 
-We see that $P_{\rm out}$ is comprised of multiple terms. Taking the case of very large $\textbf{e}$ so that any terms involving only 
-$\textbf{x}$ are small, yields:
+We see that $P_{\rm out}$ is comprised of multiple terms. To explore cases where signal loss is strongest, we will take the case where
+$\textbf{e}$ dominates, so that any terms involving only 
+$\textbf{x}$ are small, yielding:
 
@@
 additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
-zero, since foregrounds and the cosmological signal are statistically unrelated. In P64, this assumption is used, and the first 
+zero, since foregrounds and the cosmological signal are statistically uncorrelated. In P64, this assumption is used, and the first 
 term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
 
-However, deeper investigations of these terms reveal that they contain non-negligible power. In fact, foreground modes and 
-signal modes are anti-correlated on average, and this negative cross-term power arises from inverting the covariance matrix $
-\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:
+However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
+is taken to be $\textbf{C}_{r}^{-1}$ and
+$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
+$\textbf{C}_{r}^{-1}\textbf{x}$ and
+$\textbf{C}_{r}^{-1}\textbf{e}$
+become anti-correlated on average. This negative cross-term power arises from inverting the covariance matrix
+$\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:
 
@@
 
-\noindent where the data-only term (first term) and EoR-only term (last term) are approximately diagonal matrices. The middle 
-two terms, however, have a larger amount of power in their off-diagonal terms relative to their diagonal elements, since $
-\textbf{e}$ and $\textbf{x}$ are statistically unrelated. Upon inversion, these off-diagonal terms become negative, driving the 
-cross-terms in Equation \ref{eq:pout_expand} to have negative power. \cc{someone help me write this more elegantly...}This 
-effect is explained in more depth in \citet{switzer_et_al2015}.
+\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
+an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
+The middle 
+two terms, however, can have power in their off-diagonal terms.  As shown in Appendix C of \citet{parsons_et_al2014}, the
+inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
+off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms.
+\cc{someone help me write this more elegantly... (not done yet)}
 

### 2017-12-02 PAPER.tex
Added galaxy survey stuff

--- 2017-12-01 PAPER.tex
@@
 the last few eigenmodes.
-This is because we have fewer independent modes and therefore less information to characterize the eigenspectrum.
-Because we do a worse job characterizing, we have more signal loss.
-\cc{need help filling out the rest here...
-and
-also citing galaxy lit}.
+In many applications, this steep fall is not indicative of the true covariance structure of the data.
+With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix.
+In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given that instrumental noise makes it impossible for any mode to truly have zero variance.
+\acl{Was there noise in this figure?
+Also, I am slightly uncomfortable with the figure.
+FRF \emph{should} affect the covariance, since the data is different.
+What would really tease out the difference between the covariance matrix simply being different vs.
+us not being able to estimate the covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something.
+Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance of the matter power spectrum is estimated using a large---but finite---number of expensive simulations.
+There, the limited number of independent simulations results in inaccuracies in estimated covariance matrices \citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints \citep{hartlap_et_al2007}.
+In our case, the empirically estimated covariances are used for estimating power spectrum, and as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased \emph{low}---which is precisely signal loss.
+In future work, it will be fruitful to investigate whether advanced techniques from the galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ cosmology.
+These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods \citep{pope_szapudi2008,joachimi_2017}.
 
@@
 \subsubsection{Signal Loss Methodology} 
-
+\label{sec:siglossmethod}
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 

### 2017-12-02 PAPER.tex
Modified the way we cite Karto

@@
 \item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
-investigate underlying systematics. Several null tests on data are described in \citet{keating_et_al2016}. For example, one can 
+investigate underlying systematics (e.g., see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
 divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 

### 2017-12-02 PAPER.tex
hard-wrapped adrian's text

@@
 \ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
-the last few eigenmodes.
-In many applications, this steep fall is not indicative of the true covariance structure of the data.
-With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix.
-In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given that instrumental noise makes it impossible for any mode to truly have zero variance.
-\acl{Was there noise in this figure?
-Also, I am slightly uncomfortable with the figure.
-FRF \emph{should} affect the covariance, since the data is different.
-What would really tease out the difference between the covariance matrix simply being different vs.
-us not being able to estimate the covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something.
-Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance of the matter power spectrum is estimated using a large---but finite---number of expensive simulations.
-There, the limited number of independent simulations results in inaccuracies in estimated covariance matrices \citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints \citep{hartlap_et_al2007}.
-In our case, the empirically estimated covariances are used for estimating power spectrum, and as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased \emph{low}---which is precisely signal loss.
-In future work, it will be fruitful to investigate whether advanced techniques from the galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ cosmology.
-These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods \citep{pope_szapudi2008,joachimi_2017}.
+the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
+fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
+true covariance matrix. In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given 
+that instrumental noise makes it impossible for any mode to truly have zero variance. \acl{Was there noise in this figure? Also, I 
+am slightly uncomfortable with the figure. FRF \emph{should} affect the covariance, since the data is different. What would 
+really tease out the difference between the covariance matrix simply being different vs. us not being able to estimate the 
+covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something. 
+Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
+of the matter power spectrum is estimated using a large---but finite---number of expensive simulations. There, the limited 
+number of independent simulations results in inaccuracies in estimated covariance matrices 
+\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
+\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
+as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
+\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
+galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
+cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
+theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
+marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
+\citep{pope_szapudi2008,joachimi_2017}.
 

### 2017-12-03 PAPER.tex
Finished paragraph on how negative correlation arises.  May still want to add an appendix with explicit math.

@@
 $\textbf{C}_{r}^{-1}\textbf{e}$
-become anti-correlated on average. This negative cross-term power arises from inverting the covariance matrix
-$\textbf{C}_{r}$. Mathematically, the covariance of the data plus EoR is:
+can become anti-correlated on average. 
+This negative cross-term power arises from inverting the covariance matrix
+$\textbf{C}_{r}$. 
+Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
+$|\textbf{x}|\ll|\textbf{e}|$ regime:
 
@@
 The middle 
-two terms, however, can have power in their off-diagonal terms.  As shown in Appendix C of \citet{parsons_et_al2014}, the
+two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
+ensemble, $\langle\textbf{xe}^\dagger\rangle$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, the
 inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
-off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms.
-\cc{someone help me write this more elegantly... (not done yet)}
-
-The spurious correlation between $\textbf{e}$ and $\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
+terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}$ is multiplied into $\textbf{x}$,
+the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}$), but
+contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
+correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
+of the off-diagonal terms in $\textbf{C}^{-1}$ while retaining the negative sign that arose from the inversion
+of a diagonal-dominant matrix.
+% XXX [ARP: we may want to write this all out explicitly in an appendix]
+
+The spurious correlation between $\textbf{C}_r^{-1}\textbf{e}$ and $\textbf{C}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 

### 2017-12-03 PAPER.tex
compiled with Aaron's additions

@@
 
-\noindent and we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
+\noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
 an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
@@
 off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}$), but
+terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}_{r}$ is multiplied into $\textbf{x}$,
+the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}_{r}$), but
 contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
 correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\textbf{C}^{-1}$ while retaining the negative sign that arose from the inversion
+of the off-diagonal terms in $\textbf{C}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
 of a diagonal-dominant matrix.

### 2017-12-03 PAPER.tex
minor change
updated compiled plots

@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-%\dcj{Wait what? I think you are saying essentially that some x can remain in Pout which is what we are seeing. Or is this some extra bit of method which has been added to the analysis...}
+\dcj{Wait what? I think you are saying essentially that some x can remain in Pout which is what we are seeing. Or is this some extra bit of method which has been added to the analysis...}
 
@@
 $2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
-noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than P64 by a factor of $\sim10$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
+noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
+a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
 \cc{replace with kolopanis limit instead later}
@@
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
-loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim10$ in mK \cc{replace with kolopanis limit later}.}
+loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
 	\label{fig:ps1_data}
@@
 As a consequence of our investigations, we have also revised power spectrum results from PAPER-64. For an analysis of only 
-one baseline type, we quote a new $2\sigma$ upper limit of $(242.5$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
-P64 by a factor of $\sim10$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+one baseline type, we quote a new $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
+P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim10$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
+factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
 note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 

### 2017-12-04 PAPER.tex
did a comb through of the first half of the paper for typos/syntax

@@
 
-One promising technique to probe the EoR is to target the 21 cm wavelength emission that is emitted and absorbed by neutral hydrogen via 
+One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
 its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); .
@@
 instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires
-
-an intimate understanding of the instrument and a rigorous study of data analysis choices. With continual progress being made 
+A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
+With continual progress being made
 in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
@@
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
-case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 $21$ cm power spectrum 
+case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
 from the lessons learned.
@@
 toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
-from the PAPER-64 array, highlighting key changes from \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
+from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
 revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.
@@
 
-There are many choices a data analyst must consider. How can time-ordered measurements be combined? How can the 
+There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
 variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
@@
 Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
-\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on the $21$ cm power spectrum result 
+\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
 determine the difference between a detection and a null result, which have two very different implications. Errors can be 
@@
 independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
-of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:SiglossOverview}.
+of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
 \item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
@@
 information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
-weighting is in accurately defining a covariance matrix that best describes the data. 
+weighting is in accurately defining a covariance matrix that best describes the data. We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
 \item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
@@
 itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
-consider such as the independence of values in a dataset.
+consider such as the independence of values in a dataset. We explore potential pitfalls of bootstrapping in Section \ref{sec:ErrorOverview}.
 \item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
@@
 \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
-An EoR detection must pass jack-knife and null tests.
+An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
 \end{itemize}
@@
 the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
-we only need to take one Fourier transform of our data along the line-of-sight dimension. We do this when forming the un-
-normalized power spectrum estimate $\hat{q}_{\alpha}$:
+we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
 
@@
 \end{equation}
-
-\noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
+Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
 power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
@@
 In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
-matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our ultimate goal in 
+matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our goal in 
 experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
-purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections, for 
-the sake of completeness. The specifics of how signal loss appears in PAPER's analysis is later described in Section 
+purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section
 \ref{sec:Sigloss}.
@@
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis)we use $\sim$eight hours of data for our analysis (with channel 
+might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis) we use $\sim$$8$ hours of data for our analysis (with channel 
 widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
@@
 which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
-$k$'s separately, so a simplistic white noise approximation can be used. Our combined data vector is then $\textbf{x} = 
-\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data vectors are shown in Figure 
+$k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
+\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data matrices are shown in Figure 
 \ref{fig:toy_sigloss1}.
@@
 
-Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data vector $\textbf{x}$ itself:
+Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data $\textbf{x}$ itself:
 
@@
 foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The foregrounds peak at a $k$ mode based on the frequency of the sinusoid used to create it.
-We compare inverse covariance weighting
-where $\textbf{C}$ is derived from the data (left), with projecting out the first eigenmode only (right). In the former 
+The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal.
+In the two panels, we compare inverse covariance weighting
+where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
 case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
-empirically estimated, its eigenvalues pose the risk of describing random fluctuations that happen to exist in the data realization 
-but may not exist in the true covariance. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
+empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
 There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
@@
 recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In 
-order to understand the behavior of this result, we can closely study our covariance matrix, $\hat{\textbf{C}}$. %, which is 
-shown in Figure \ref{fig:toy_sigloss12}.
+order to understand the behavior of this result, we can closely study our covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
+%, which is shown in Figure \ref{fig:toy_sigloss12}.
 
 If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a 
-multiplicative bias (per $k$) to estimates of the signal. For a mathematical derivation of signal loss arising from a data-
-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}. Here we will describe the origin of this signal loss 
+multiplicative bias (per $k$) to estimates of the signal.
+For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
+Here we will describe the origin of this signal loss
 intuitively.
@@
 representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
-particular data realization, its eigenvalues and eigevectors may differ from the truth. Said differently, shapes that may not exist (or have a 
+particular data realization, its eigenvalues and eigenvectors may differ from the truth. Said differently, shapes that may not exist (or have a 
 weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
@@
 successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
-assigns it the highest eigenvalue (the peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
+assigns it the highest eigenvalue (the first peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
 covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
@@
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
-characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-
-weighted). This leads to the `overfitting' of noise (or `overfitting' of signal), which is signal loss.
-
-Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield zero 
+characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted).
+This leads to the `overfitting' of noise (or rather `overfitting' of signal), which is signal loss.
+
+Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
 signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
@@
 \subsubsection{Toy Model: Fringe-Rate Filtering}
+\label{sec:toymodel_frf}
 
@@
 Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
-of the matter power spectrum is estimated using a large---but finite---number of expensive simulations. There, the limited 
+of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
 number of independent simulations results in inaccuracies in estimated covariance matrices 
@@
 	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
-	\caption{Resulting power spectrum estimate for the fringe-rate filtered toy model simulation --- foregrounds only (blue), 
+	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
 EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
 computed from the data. There is a larger amount of signal loss than for the non-averaged data, a consequence of a 
-steepened, weakly characterized eigenspectrum from using fewer independent modes in the data. The power spectrum 
+steepened, weakly characterized eigenspectrum from fewer independent modes in the data. The power spectrum 
 estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the 
-weakest, EoR-dominated modes, which are down-weighted the least).}
+weakest, EoR-dominated modes).}
 	\label{fig:toy_sigloss7}
@@
 
-The power spectrum results for inverse covariance weighted fringe-rate filtered data is shown in Figure \ref{fig:toy_sigloss7}. As 
+The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
 expected, there is a much larger amount of signal loss for this time-averaged dataset. Additionally, because of the steepened 
@@
 In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can 
-make the difference between zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance 
+make the difference between $\sim$zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance 
 matrix from those in an estimated one. We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ 
@@
 \textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
-left), we see that there is negligible signal loss. This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting 
-fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would). This is evident 
-when comparing the green and red curves in Figure \ref{fig:toy_sigloss14}. We don't see perfect EoR recovery though, as the 
+left), we see that there is negligible signal loss.
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
+This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
+We don't see perfect EoR recovery though, as the
 green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}. This deviation is a consequence of the difference between the 
@@
 	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
-	\caption{Resulting power spectra estimates for our fringe-rate filtered toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each avoid signal 
+	\caption{Resulting power spectra estimates for our `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
+EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each minimize signal 
 loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to 
@@
 \hat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-computed for the fringe-rate filtered toy model case.}
+computed for the `fringe-rate filtered' (time-averaged) toy model case.}
 	\label{fig:toy_sigloss14}
@@
 The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = 
-\hat{\textbf{C}} + \gamma\textbf{I}$, where $i$$=$$j$$=$$20$ (number of frequencies) and $\gamma = 5$ (an arbitrary strength 
+\hat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
 of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum. If all modes are given 
+elements of the covariance matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum. If all modes are given 
 similar weights, we avoid down-weighting EoR modes more than others.
@@
 
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-
-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$). In the bottom right 
+The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
+In the bottom right
 panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds. For this toy model, 
@@
 removing the underlying cosmological signal. As we investigated however, there are trade-offs between the weighting method 
-used, its foreground-removal effectiveness, and the amount of resulting signal loss.
+used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
 
@@
 independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
-earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$. This occurs 
+earlier (drawing $N$=$1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N$=$1000$). This occurs 
 because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
@@
 function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
-under-estimate the error by drawing too many or over-estimate it by drawing too few. However, if we know that we have $100$ 
-independent samples, the error associated with drawing $100$ samples with replacement does match the theoretical prediction 
+under-estimate the error by drawing too many or over-estimate it by drawing too few. However, since we know that we have $100$ 
+independent samples in this toy model, the error associated with drawing $N$=$100$ samples with replacement does match the theoretical prediction 
 as expected.
@@
 example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the 
-number of averages performed. Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-
-trivial with a more complicated convolution function that has long tails. Hence, we do not recommend bootstrapping unless the 
+number of averages performed.
+Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
+Hence, we do not recommend bootstrapping unless the
 number of independent samples along the axis that is being re-sampled is well-determined.
@@
 	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
-	\caption{Error estimation produced by bootstrapping as a function of the number of elements drawn per bootstrap when 
-sampling with replacement. The star represents the standard deviation of $500$ bootstraps, each created by drawing $1000$ 
-elements (with replacement) from a length $1000$ array of a Gaussian random signal. The black points correspond to time-
-averaged data (correlated data) which has $100$ independent samples. They illustrate how errors can be underestimated if 
+	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
+sampling with replacement. The star represents the standard deviation of $N_{boot}$ bootstraps, each created by drawing $1000$ 
+elements (with replacement) from a length $1000$ array of a Gaussian random signal.
+The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
+They illustrate how errors can be under-estimated if
 drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
@@
 
-In Figure \ref{fig:toy_error2} we compare the two methods of bootstrapping: sampling all elements randomly (black points) 
+In Figure \ref{fig:toy_error2} we compare these two methods of bootstrapping: sampling all elements randomly (black points) 
 versus sampling just the final element randomly (gray points). The two converge for datasets with small numbers of elements, 
@@
 
-Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or $k$ modes. For a particular 
+Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or low $k$ modes. For a particular 
 baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between two 
@@
 present in, for example, the first half of the LST range used for analysis, but not the second half. Mathematically, if  $\textbf{n}$ 
-is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-
-multiplied to form power spectra) can be written as:
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
 
@@
 
-We form $3$ different power spectrum estimates shown in Figure \ref{fig:toy_bias1}. The first is a null test where we subtract $
+We form three different power spectrum estimates shown in Figure \ref{fig:toy_bias1}. The first is a null test where we subtract $
 \textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$. This is equivalent to splitting up a full dataset along 

### 2017-12-04 PAPER.tex
comb through for esyntax/typos up until Section 3.3

@@
 	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
-paper (such as baseline 49\_41).}
+paper (such as the baseline involving antennas 49 and 41).}
 	\label{fig:ant_layout}
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit (Kolopanis et al., \textit{in prep}) stems mostly from previously underestimated signal loss and underestimated error bars, both of which we
+The revision of this limit (Kolopanis et al., \textit{in prep}) stems from previously underestimated signal loss and underestimated error bars, both of which we
 address in the following sections.
@@
 range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
-MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only $1$ baseline type instead of the $3$ in 
-P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the fringe-rate filter. In P64, the 
+MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only one baseline type instead of the three in 
+P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the applied fringe-rate filter. In P64, the 
 applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
-modes and reduce signal loss, though as we will see this signal loss was still under-estimated. With the development of a new, 
+modes and reduce signal loss, though as we will explain in the next section, this signal loss was still under-estimated. With the development of a new, 
 robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
-cm signal visibilities. Here we use the same method used in P64, where mock Gaussian noise visibilities (mock EoR signals) 
+cm signal visibilities. Here we use the same method as in P64, where mock Gaussian noise visibilities (mock EoR signals) 
 are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.  \footnote{One 
@@
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
-estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.}
-
-Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data vector. We define $\textbf{r}
+estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in P64 (the dominant reason is explained in the main text).}
+
+Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
 $ to be the data plus the EoR signal:
@@
 
-In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\textbf{x}$ (our detailed computation is described in the next section).
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\textbf{x}$ by the following reasoning.
+In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\hat{\textbf{p}}_{x}$ (our detailed computation is described in the next section).
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\hat{\textbf{p}}_{x}$ by the following reasoning.
 
@@
 
-Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$, and the denominator to $P_{\rm in}$, where the function $g$ is our OQE power spectrum pipeline.
+Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator to $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 
-However, a deeper investigation of these cross-terms reveals that they can contain non-negligible power when $\textbf{R}_{r}$
-is taken to be $\textbf{C}_{r}^{-1}$ and
-$\textbf{C}_{r}$ is estimated from the data itself.  As shown in \citet{switzer_et_al2015}, 
+However, a deeper investigation of these cross-terms reveals that they contain non-negligible power (when $\textbf{R}_{r}$
+is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself).
+Therefore, ignoring the cross-terms significantly under-estimates signal loss, and it is this reason that represents the bulk change of our revised analysis compared to P64.
+
+We now explain why the spurious correlations between $\textbf{e}$ and $\textbf{x}$ contain negative power.  As shown in \citet{switzer_et_al2015}, 
 $\textbf{C}_{r}^{-1}\textbf{x}$ and
@@
 signal loss lens.
-Interpretation of the signal injection results can be framed in multiple ways which result in similar but not identical answers.
-One such alternative is described in Appendix \ref{sec:Pr_appendix}.
+We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
+One alternative to the method described in the next section is described in Appendix \ref{sec:Pr_appendix}.
 %We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
@@
 ($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
-expressions for $P_{\rm in}$ and $P_{\rm out}$ become (ignoring normalization factors):
+expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
 
@@
 $P_{\rm out}$ grid.
-We smooth the 2D distribution using kernel density estimators.
-Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
-
-The result is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.
+%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
+
+We smooth the 2D distribution of $P_{in}$ vs.
+$P_{out}$ using kernel density estimators.
+The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.
 Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations 
-\eqref{eq:Pin} and \eqref{eq:sigloss}. Kernel density estimations of the power spectrum transfer functions are shown as colored 
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+Kernel density estimations of the power spectrum transfer functions are shown as colored
 heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}$, the data 
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data 
 distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
 for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
-not exhibit loss. The peculiar feature of `signal gain' at low injection levels is explained in the text.}
+not exhibit loss.}
 	\label{fig:sigloss_transfercurve}
@@
 
-One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have 
-signal gain ($P_{\rm out} > P_{in}$). This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}
-$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. As $\textbf{e}$ increases, we move 
+One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$).
+\cc{This is a log-plotting effect and is under-construction!}.
+%This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small.
+
+The shape of our signal loss transfer function can be described as follows.
+At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}.
+As $\textbf{e}$ increases, we move
 into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
@@
 To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
-loss correction in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
+loss estimation in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
 power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
-gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss correction, it 
+gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
 is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
-Post-correction, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
+Post-estimation, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
 We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-
-weighting contaminants with minimizing the loss of EoR.
+weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
 
@@
 	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (gray) points, 
-with $2\sigma$ error bars) before signal loss correction (left) and after (right). The dashed blue line is the unweighted power 
+with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the unweighted power 
 spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
@@
 eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
-down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
+that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
 covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
-correction, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
+estimation, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
 becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
-subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss correction, 
+subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
 increases with the number of down-weighted modes (black curve).
@@
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
-are shown before (gray) and after (black) signal loss correction as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
+are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
 are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
@@
 weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
-$\sim$$3$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
+$\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
 as solid green.}
@@
 In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
-which denote power spectrum values, post-signal loss correction, for two other regularization schemes. We multiply an identity 
+which denote power spectrum values, post-signal loss estimation, for two other regularization schemes. We multiply an identity 
 matrix element-wise to $\hat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
 of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
-their best (i.e. when $\sim3$-$4$ eigenmodes are down-weighted in the case of the black curve).
+their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black curve).
 
@@
 noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to $3$). 
+a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
 \cc{replace with kolopanis limit instead later}
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
+	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$ (inverse variance weighting). Black and gray points correspond to positive and 
 negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
@@
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
-loss, bootstrapping, and the theoretical error computation. We quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
+loss, bootstrapping, and the theoretical error computation. From this, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
 $k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
@@
 when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the 
-$21$ cm signal, and it's worth noting that the PAPER-32 results are likely safe from the issue of signal loss underestimation 
+$21$ cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}.
+we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}).
 
 Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-
-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
+calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
 down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from 
-data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-
-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
+data that is similar but not exactly the same as the data that is being down-weighted.
+Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
 
@@
 
-The sensitivity prediction (\citealt{parsons_et_al2012a}, \citealt{pober_et_al2013}) for a power spectral analysis of 
+The sensitivity prediction (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
 interferometric $21$ cm data, in temperature-units, is:
@@
 distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
-\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}, \citealt{pober_et_al2012}). 
-The effective beam area changes with the application of a fringe-rate filter, since parts of the beam are up-weighted and down-
-weighted. Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate 
+\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
+The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted.
+Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
 filter. 
@@
 divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
-because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a realistic value of 
+because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
 $N_{days}$ as:
@@
 the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
-the fact that baselines are averaged into groups before cross-multiplying data. Our revised estimate for the parameter is:
+the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) before cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
-\sqrt{3}$ for 3 baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
+\sqrt{3}$ for three baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
 \Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
@@
 As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
-of independent samples. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
+of independent samples, or the number of independent samples is well known. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
 spectrum that is a function of $k$ and time.
@@
 specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
-$700$, which we expect to greatly exceed the approximate number of independent samples after fringe-rate filtering.
+$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
 Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied). Finally, power 
@@
 The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
-group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim$$3$-$4$ baselines per group 
+group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
 were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total 
@@
 \ref{fig:data_errors}. The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized, while when 
+shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized (blue), while when 
 only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ 
-modes converges to the theoretical noise level.  However, if more elements are drawn for each bootstrap than the number of 
+modes converges to the theoretical noise level (black).  However, if more elements are drawn for each bootstrap than the number of 
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent 
-variation between bootstraps drops, resulting in limits below the predicted noise level.
+variation between bootstraps drops, resulting in limits below the predicted noise level (red).
 

### 2017-12-04 PAPER.tex
finished combing through entire paper for syntax/typos/clarity

@@
 contamination of foreground bias.
+For this paper, we compute $\textbf{M}$ as described above only for the inverse variance weighted PAPER-64 result (our revised result for one baseline type) shown in Figure \ref{fig:ps1_data}.
+For all other power spectrum estimates in this paper, we use $\textbf{M}=\textbf{I}$ for simplicity.
 
@@
 Figure \ref{fig:ps1_data}, has positive biases at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these detections 
-are most likely attributable to foreground leakage. Here we demonstrate $3$ null tests performed on PAPER-64 data that verify 
+are most likely attributable to foreground leakage. Here we demonstrate three null tests performed on PAPER-64 data that verify 
 that the positive detections are indeed due to foreground variation and not attributable to EoR.
 
-The $3$ null test results are shown in Figure \ref{fig:null}, with each test described as the following:
+The three null test results are shown in Figure \ref{fig:null}, with each test described as the following:
 
 \begin{itemize}
-\item Original (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised 
+\item Original Data (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised 
 PAPER-64 power spectrum (one baseline type only) with weighting matrix $\hat{\textbf{C}}_{eff}$. There are clear detections at 
@@
 group and $b_{2}$ is the second baseline group.
-\item LST (purple): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 
+\item LST (magenta): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 
 4.6-8.6 hours). We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$.
@@
 	\includegraphics[width=\columnwidth]{plots/null.png}
-	\caption{Results for $3$ null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
-$2\sigma$ errors (gray shaded region). For each, we took jackknives along different axes of the dataset - by julian days (separating 
-even and odd days; blue), by baselines (green), and by LST (purple). We expect the sky signal to disappear for a `passing' null test. 
+	\caption{Results for three null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
+$2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
+even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test. 
 We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
@@
 
-The null test in LST (purple) is much more illuminating. The fact that there are many power spectrum points outside the 
+The null test in LST (magenta) is much more illuminating. The fact that there are many power spectrum points outside the 
 estimated error region signifies that the bias we see is likely from foregrounds that vary in LST. In other words, $t_{1}$ and 
-$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-
-multiplication. The errors for this null test are also large, also reflective of residual foregrounds.
+$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+The errors for this null test are also large, also reflective of residual foregrounds.
 
@@
 \item Substantial signal loss can result when weighting data using empirically estimated covariances (Section 
-\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant if more eigenmodes are down-weighted than 
-exist in the data (having an under-constrained covariance matrix). Hence, there exists a trade-off between sensitivity driven 
+\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant if fewer modes
+exist in the data. Hence, there exists a trade-off between sensitivity driven 
 time-averaging techniques such as fringe-rate filtering and signal loss. 
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse 
+\item Signal loss, previously found to be $<2\%$ in P64, was under-estimated by a factor of $\sim$$1000$ for inverse 
 covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We 
-note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
+factor of $\sim7$ mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
+note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to 
-oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. They were also 
-overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power 
+\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$2$ due to 
+oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. Our limits were also 
+over-estimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power 
 spectra (Section \ref{sec:Boot}). Hence, the net change for our error estimation is negligible, though the rationale behind the 
@@
 instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
-comprehensive jackknife tests will play critical roles in accurate $21$ cm results. Looking ahead, the future promises to bring 
-higher sensitivity measurements, better foreground and instrumental models, more effective and less lossy weighting 
-techniques --- and with all that, an improved understanding of reionization and our early Universe.
+comprehensive jackknife tests will play critical roles in accurate $21$ cm results.
+With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
 
@@
 SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
-We graciously thank SKA-
-SA for site infrastructure and observing support.
+We graciously thank SKA-SA for site infrastructure and observing support.
 \label{sec:Ack}
@@
 \end{equation}
-where $\eta$ is parameter quantifying our success at estimating the true covariance matrix.
+where $\eta$ is a parameter quantifying our success at estimating the true covariance matrix.
 If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
@@
 Now, recall that $p_\alpha$ is the \emph{true} power spectrum.
-This means that it can be decomposed into the sum of foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
+This means that it can be decomposed into the sum of the foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
 This toy example, while not definitive, serves to motivate the form of Equation \eqref{eq:LinearPspecSum}.
@@
 One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
-The method described in section \ref{sec:Sigloss} relies on several assumptions which required justification including the neglection of cross-terms in the power spectrum and indeed does not behave as expected at small injected values.
+The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the neglection of cross-terms in the power spectrum and indeed does not behave as expected at small injected values.
 However it is possible to make a simpler interpretation which requires less motivation.
 
-In the main text we made an estimate of the signal loss effecting only the injected eor by supposing that the lossy injected signal was the difference between the injected and not injected cases: $ P(e) = P(x+e) - P(x)$.
-Suppose that we rephrase the question to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $P(x+e)$, the weighted power spectrum of the data plus injected signal ($\hat{\textbf{p}}_{r}$ in Section \ref{sec:Sigloss}).
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{out} = \hat{\textbf{p}}_{r} - \hat{\textbf{p}}_{x}$.
+Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
+Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $\hat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
 
@@
 diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data distribution.
-At low injection, $P_{\rm out}$ converges at the data level.}
+At low injection, $P_{\rm out}$ converges to the data level.}
 \label{fig:Pr_vs_Pin}
@@
 \includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
-\caption{The probability that an injected signal of level P$_{in}$
+\caption{The probability that an injected signal of level P$_{inj}$
 is observable at a 2$\sigma$ level above the value of $\hat{\textbf{p}}_{x}$ (data).
@@
 
-One difference in this method is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
+One difference in this method from the one in the main text is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
 Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
@@
 \begin{equation}
-P_{r} > P_{x} \Lambda,
+\hat{\textbf{p}}_{r} > \hat{\textbf{p}}_{x} \Lambda,
 \end{equation}  
@@
  \begin{equation}
-\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(P_x) \Prob(P_r,P_{in}) dr
- \end{equation}
- where $\Prob(P_x)$ is the probability of obtaining the power spectrum $\hat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(P_r,P_{in})$ is the probability of obtaining the summed power spectrum $\hat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(\hat{\textbf{p}}_x) \Prob(\hat{\textbf{p}}_r,P_{in}) dr
+ \end{equation}
+ where $\Prob(\hat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\hat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\hat{\textbf{p}}_r,P_{in})$ is the probability of obtaining the summed power spectrum $\hat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
 
@@
 injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
-At low injection levels the variation between $x$ and $r$ is such that the null test is ruled out to within $20$\%.
+At low injection levels the variation between $\textbf{x}$ and $\textbf{r}$ is such that the null test is ruled out to within $20$\%.
 This is the level expected from two distributions with $\sim$10 effective samples.
@@
 \includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
-\caption{A comparison of the signal loss Section \ref{sec:Sigloss} method
-against the method in this appendix at $90$\% confidence (red curve).
+\caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
+with the method in this appendix at $90$\% confidence (red curve).
 Also shown are the upper limits of the unweighted power spectrum

### 2017-12-04 PAPER.tex
added new FRF plot
consistent variable notation in signal loss section

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
+	\caption{.}
+	\label{fig:toy_sigloss16}
+\end{figure}
+
 The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
@@
 \label{eq:Pin}
-P_{\rm in,\alpha} = \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} \equiv M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \label{eq:sigloss}
-P_{\rm out,\alpha} &=& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
-&=& \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+P_{\rm out,\alpha} &\equiv& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
+&=& M_{\alpha}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x},
 \end{eqnarray}
-where, for illustrative purposes, all $\textbf{M}$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+\cc{fix!}where, for illustrative purposes, all $M$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
 $\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
@@
 where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
-In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat$.
+In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$.
 This can be parametrized as
@@
 \label{eq:LinearPspecSum}
-\langle \phat \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
+\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
 \end{equation}
@@
 However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
-Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $\p^*_{\rm eor}$), computing instead
+Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
 \begin{equation}
 \label{eq:Deriv2}
-\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{\p^*_{\rm eor}},
+\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
 \end{equation}
 which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
-Essentially, one is computing the slope of $\langle \phat \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
+Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
 Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$.
@@
 One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{\rm out,\alpha} = \textbf{M}_{ee}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
+$P_{\rm out,\alpha} = M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
 expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &=& \textbf{M}_{rr}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
-\textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &=& M_{\alpha}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&=& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&-& \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&+& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
+&-& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 \label{eq:pout_expand}
-P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
- \textbf{M}_{rr}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
- &+&  \textbf{M}_{rr}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
+P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
+ M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+ &+&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
 \end{eqnarray}
@@
 $\textbf{C}_{r}$. 
-Intuitively, we can see this by expanding the covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
+Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
 $|\textbf{x}|\ll|\textbf{e}|$ regime:
@@
 \begin{eqnarray}
-\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle \\
-&=& \langle \textbf{xx}^{\dagger} \rangle + \langle \textbf{xe}^{\dagger} \rangle + \langle \textbf{ex}^{\dagger} \rangle + \langle 
-\textbf{ee}^{\dagger} \rangle,
+\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \\
+&=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
+\textbf{ee}^{\dagger} \rangle_{t},
 \end{eqnarray}
@@
 \begin{eqnarray}
-P_{\rm in,\alpha} &=&  \textbf{M}_{ii}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  \textbf{M}_{rr}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
-&&\phantom{=====} -  \textbf{M}_{xx}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
+P_{\rm in,\alpha} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
+&&\phantom{=====} 
+-  M_{\alpha}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat)$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat$, which is given by
+Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
+Since Equation \eqref{eq:Deriv2} is a good approximation of Equation \eqref{eq:Deriv1}, which we argued for in the previous section, we can write $\p_{\rm eor}$ as $P_{in}$, and hence the probability distribution is given by
 \begin{equation}
 \label{eq:Bayes}
-p( \p_{\rm eor} | \phat) \propto \mathcal{L} (  \phat | \p_{\rm eor})  p( \p_{\rm eor}),
-\end{equation}
-where $p( \p_{\rm eor})$ is the prior on $\p_{\rm eor}$ and $\mathcal{L} $ is the likelihood function.
-Since the likelihood is defined as the distribution of the measured result $ \phat$ given the theoretical power spectrum $\p_{\rm eor}$, we may construct this function simply by fixing $\p_{\rm eor}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum.
-The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $\p_{\rm eor}$.
-
-In our code, we simulate $20$ realizations of $\p_{\rm eor}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
+p(P_{in} | \phat_{x}) \propto \mathcal{L} (  \phat_{x} | P_{in})  p(P_{in}),
+\end{equation}
+where $p(P_{in})$ is the prior on $P_{in}$ and $\mathcal{L} $ is the likelihood function.
+Since the likelihood is defined as the distribution of the measured result $ \phat_{x}$ given the theoretical power spectrum $P_{in}$, we may construct this function simply by fixing $P_{in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum.
+The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $P_{in}$.
+
+In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
 We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs.
@@
 The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.
-Bayes' rule then simply instructs us to fix $\phat$ at our measured value $\phat_{x}$, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p( \p_{\rm eor})$.
-The final result can then be normalized to give $p( \p_{\rm eor} | \phat)$.
-If $\phat$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat$, before performing the final summation and normalization.
+Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$.
+The final result can then be normalized to give $p(P_{in} | \phat_{x})$.
+If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
 In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $

### 2017-12-04 PAPER.tex
added figure 7 caption

@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
-	\caption{.}
+	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
+In red, the mock EoR signal is comprised entirely of independent samples.
+Subsequent colors show time-averaged signals.
+As the number of realizations increases, we see that the empirical covariances approach the true covariances.
+With more independent samples, the quicker an empirical covariance converges.}
 	\label{fig:toy_sigloss16}

### 2017-12-04 PAPER.tex
Added discussion of new plot

--- 2017-12-04 PAPER.tex
@@
 fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
-true covariance matrix. In some cases one might even arrive at a rank-deficient empirical covariance, which is unphysical given 
-that instrumental noise makes it impossible for any mode to truly have zero variance. \acl{Was there noise in this figure? Also, I 
-am slightly uncomfortable with the figure. FRF \emph{should} affect the covariance, since the data is different. What would 
-really tease out the difference between the covariance matrix simply being different vs. us not being able to estimate the 
-covariance matrix would be if we ran a large ensemble of these, and we saw the empirical covariance converging to something. 
-Can we make such a figure?} The situation is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
+true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon$ for the empirical covariance, which we define as
+\begin{equation}
+\label{eq:converge}
+\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\Chat_{ij} - \C_{ij})^2}{\sum_{ij} \C_{ij}^2}},
+\end{equation}
+where $\C$ is true covariance matrix.
+In Figure \ref{toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
+With more independent time samples in the data, one converges to the true covariance more quickly.
+The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance
 of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 

### 2017-12-04 PAPER.tex
made sure none of the plots are cut off

@@
 	\centering
-	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\includegraphics[trim={1.5cm 0cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
 	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
-	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
+	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
+	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
 	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
@@
 	\centering
-	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
 	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
@@
 where $\C$ is true covariance matrix.
-In Figure \ref{toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
+In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
 With more independent time samples in the data, one converges to the true covariance more quickly.
+
 The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
@@
 	\centering
-	\includegraphics[trim={1.5cm 0.2cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
+	\includegraphics[trim={1.5cm 0cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
 yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
-in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green). The dashed spectrum is steeper, 
-resulting in more dramatic differences in weighting between eigenmodes. Consequently, if all eigenmodes are used in weighting 
-it is possible to down-weight EoR modes more severely than for the non-averaged case.}
+in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
 	\label{fig:toy_sigloss5}
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
 	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
+	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
 	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
@@
 The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
-expected, there is a much larger amount of signal loss for this time-averaged dataset. Additionally, because of the steepened 
-eigenspectrum, the last few eigenmodes receive more weight relative to the others. Therefore, most of our power spectrum 
-information is coming from only these last few modes and as a result, it is a noisier estimate. This is evident by noticing that the 
+expected, there is a much larger amount of signal loss for this time-averaged dataset.
+We do a worse job estimating the true covariance and, as a result, it is a noisier estimate.
+This is evident by noticing that the
 green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
 	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
 	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
 	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
 	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 

### 2017-12-04 PAPER.tex
added time subscripts to covariance averages

@@
 
-\noindent assuming $\langle\textbf{x}\rangle = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
 amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $
@@
 _{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
-\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+\textbf{x}_{FG}^{\dagger}\rangle_{t}$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
 left), we see that there is negligible signal loss.

### 2017-12-04 PAPER.tex
compiled with 95% method 2 plot

@@
 We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
-Rather than insist on a rejection at the $99$th percent level, we compromise at $90$\%.
+Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\%.
 
 The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
-Overall the limits are slightly lower, with k modes differing by factors of 3 to 37.
+Overall the limits show good agreement, with k modes differing by factors of 2 to 4.
 
@@
 \centering
-\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison.png}
+\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison_95.png}
 \caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
-with the method in this appendix at $90$\% confidence (red curve).
+with the method in this appendix at $95$\% confidence (red curve).
 Also shown are the upper limits of the unweighted power spectrum
-(blue dashed) and theoretical noise model (green). \label{fig:sigloss_compare} }
+(blue dashed) and theoretical noise model (green).} 
+\label{fig:sigloss_compare} 
 \end{figure}

### 2017-12-04 PAPER.tex
syntax typo

@@
 cm signal visibilities. Here we use the same method as in P64, where mock Gaussian noise visibilities (mock EoR signals) 
-are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.  \footnote{One 
+are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
 specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 

### 2017-12-04 PAPER.tex
Edited definition of M_alpha and also responded to some of Danny's comments

--- 2017-12-04 PAPER.tex
@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\includegraphics[trim={1.5cm 0.2cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
 	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
@@
 
-\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+\noindent assuming $\langle\textbf{x}\rangle = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
 amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
-	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
+	\includegraphics[trim={0.3cm 0.2cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
+	\includegraphics[trim={1cm 0.2cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
 	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={1.5cm 0.1cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
 	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
@@
 where $\C$ is true covariance matrix.
-In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
+In Figure \ref{toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
 With more independent time samples in the data, one converges to the true covariance more quickly.
-
 The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance
@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
+	\includegraphics[trim={1.5cm 0.2cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
 yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
-in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
+in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green). The dashed spectrum is steeper, 
+resulting in more dramatic differences in weighting between eigenmodes. Consequently, if all eigenmodes are used in weighting 
+it is possible to down-weight EoR modes more severely than for the non-averaged case.}
 	\label{fig:toy_sigloss5}
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0.3cm 0.2cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
 	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
 	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
@@
 The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
-expected, there is a much larger amount of signal loss for this time-averaged dataset.
-We do a worse job estimating the true covariance and, as a result, it is a noisier estimate.
-This is evident by noticing that the
+expected, there is a much larger amount of signal loss for this time-averaged dataset. Additionally, because of the steepened 
+eigenspectrum, the last few eigenmodes receive more weight relative to the others. Therefore, most of our power spectrum 
+information is coming from only these last few modes and as a result, it is a noisier estimate. This is evident by noticing that the 
 green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
@@
 _{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
-\textbf{x}_{FG}^{\dagger}\rangle_{t}$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+\textbf{x}_{FG}^{\dagger}\rangle$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
 left), we see that there is negligible signal loss.
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
 	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
 	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
 	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
@@
 spectrum according to OQE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as:
+output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as
 
@@
 \end{eqnarray}
-\cc{fix!}where, for illustrative purposes, all $M$'s are diagonal normalizations. $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal, 
+where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices $M$, even though for our numerical results we use a full non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
+$P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal,
 $\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
@@
 Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross terms in the estimation of a power spectrum.
-So we're just kicking the can down the road.
-}
+So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}.
+Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example.
+The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
+Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \eqref{sec:sigloss_appendix}.}
 
@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-\dcj{Wait what? I think you are saying essentially that some x can remain in Pout which is what we are seeing. Or is this some extra bit of method which has been added to the analysis...}
+\dcj{Wait what?
+I think you are saying essentially that some x can remain in Pout which is what we are seeing.
+Or is this some extra bit of method which has been added to the analysis...} \acl{I'm not sure that's what I'm saying.
+(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure".
+What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
+\begin{equation}
+\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
+\end{equation}
+(Note that even this is an approximation.
+In principle there is an infinite series containing all possible powers of $e$ and $f$).
+Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
+Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about.}
 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
+	\includegraphics[trim={0.3cm 0.3cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
 	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 

### 2017-12-04 PAPER.tex
made new signal loss illustration section

--- 2017-12-04 PAPER.tex
@@
 
-One may wonder why $P_{\rm out}$ cannot be computed simply as the weighted power spectrum of $\textbf{e}$ alone, namely 
-$P_{\rm out,\alpha} = M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}$. In short, the reason is because this 
-expression fails to include correlations between the injected EoR signal and data, which emerges as statistical noise that is added to the 
-estimate, decreasing the value of $P_{\rm out}$. Mathematically, we can show this by expanding out Equation \eqref{eq:sigloss}:
+\subsubsection{Signal Loss Illustration}
+
+To explore how our expression for $P_{out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
 
@@
 \end{eqnarray}
-
 We see that $P_{\rm out}$ is comprised of multiple terms. To explore cases where signal loss is strongest, we will take the case where
@@
 
-We see that our naive expression for $P_{\rm out}$ is the first term in Equation \eqref{eq:pout_expand}, but there are also two 
-additional terms. An initial assumption would be that the cross-terms that involve both $\textbf{e}$ and $\textbf{x}$ should be 
-zero, since foregrounds and the cosmological signal are statistically uncorrelated. In P64, this assumption is used, and the first 
-term in Equation \eqref{eq:pout_expand} is directly compared to the input (unweighted) power spectrum to compute signal loss.
-
-However, a deeper investigation of these cross-terms reveals that they contain non-negligible power (when $\textbf{R}_{r}$
-is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself).
-Therefore, ignoring the cross-terms significantly under-estimates signal loss, and it is this reason that represents the bulk change of our revised analysis compared to P64.
+The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
+It is this quantity that was used in P64 to calculate signal loss.
+However, without taking into account the cross-terms (the second and third terms), we can substantially under-estimate loss.
+In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
+Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to P64.
+
+A deep investigation of the cross-terms reveals that they contain non-negligible power (when $\textbf{R}_{r}$
+is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself). We now describe in words the anti-correlation between data and the injected EoR. For a full...
 

### 2017-12-04 PAPER.tex
edited flow of first 3 subsections in Signal Loss section

@@
 
-Using this motivation, the numerator of Equation \eqref{eq:Deriv2} can be mapped to our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator to $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
+Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
-Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \eqref{sec:sigloss_appendix}.}
+Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
+Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
+which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
+distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
+distribution could this (signal-loss affected) data come from?"
+
+In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss, and why this signal loss occurs in the first place.
+Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
+signal loss lens.
+We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
+One alternative to the method described in Section \ref{sec:Practice} is described in Appendix \ref{sec:Pr_appendix}.
+%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
 
 \subsubsection{Signal Loss Illustration}
-
+\label{sec:Illustration}
 To explore how our expression for $P_{out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
@@
 \end{eqnarray}
-We see that $P_{\rm out}$ is comprised of multiple terms. To explore cases where signal loss is strongest, we will take the case where
-$\textbf{e}$ dominates, so that any terms involving only 
-$\textbf{x}$ are small, yielding:
+We see that $P_{\rm out}$ is comprised of multiple terms.
+For illustrative purposes in this subsection only, we build intuition for signal loss in $P_{out}$ by considering a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
+It is in this limit where we expect signal loss to be greatest, and $P_{out}$ becomes:
 
@@
 \label{eq:pout_expand}
-P_{\rm out, \alpha,\textbf{e} \gg \textbf{x}} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
- M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
- &+&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
+P_{\rm out, \alpha} &\approx&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
+ 2M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
 \end{eqnarray}
-
 The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
 It is this quantity that was used in P64 to calculate signal loss.
-However, without taking into account the cross-terms (the second and third terms), we can substantially under-estimate loss.
+However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
 In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
@@
 
-A deep investigation of the cross-terms reveals that they contain non-negligible power (when $\textbf{R}_{r}$
-is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself). We now describe in words the anti-correlation between data and the injected EoR. For a full...
-
-We now explain why the spurious correlations between $\textbf{e}$ and $\textbf{x}$ contain negative power.  As shown in \citet{switzer_et_al2015}, 
-$\textbf{C}_{r}^{-1}\textbf{x}$ and
-$\textbf{C}_{r}^{-1}\textbf{e}$
-can become anti-correlated on average. 
-This negative cross-term power arises from inverting the covariance matrix
-$\textbf{C}_{r}$. 
+When $\textbf{R}_{r}$
+is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself, the second term of Equation \eqref{eq:pout_expand} is a cross correlation between $\textbf{C}_{r}^{-1}\textbf{x}$ and
+$\textbf{C}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross correlation term is non-zero, and in fact negative in expectation. 
+This negative cross-term power arises from a coupling between the inverse of 
+$\textbf{C}_{r}$ and $\mathbf{x}$. 
 Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
@@
 \noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
-an eigenbasis of $\textbf{e}$, so that $\textbf{ee}^{\dagger}$ is diagonal.
+an eigenbasis of $\textbf{e}$, so that $\langle 
+\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. 
 The middle 
 two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
-ensemble, $\langle\textbf{xe}^\dagger\rangle$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, the
-inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\textbf{ee}^{\dagger}$) with smaller
+ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the
+inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\langle 
+\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
 off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
 terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}_{r}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}_{r}$), but
+the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}_{r}$), \acl{I'm not sure the previous claim follows.
+Why does this follow from the diagonal dominance?} but
 contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
@@
 
-The spurious correlation between $\textbf{C}_r^{-1}\textbf{e}$ and $\textbf{C}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+The correlation between $\textbf{C}_r^{-1}\textbf{e}$ and $\textbf{C}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
@@
 
-The relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
-which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
-distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
-distribution could this (signal-loss affected) data come from?" In the next section, we describe the shape of our signal loss 
-transfer function and detail the computation used to translate our power spectrum result into one viewed through a 
-signal loss lens.
-We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
-One alternative to the method described in the next section is described in Appendix \ref{sec:Pr_appendix}.
-%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
+We thus see from this subsection that signal loss generically arises because of couplings between $\textbf{C}^{-1}_{r}$ and $\mathbf{x}$.
+In principle, using $\textbf{C}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
+Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
+However, despite the loosening of these approximations, one sees that the qualitative message (of anti-correlations resulting in signal loss) remains intact.
 
 \subsubsection{Signal Loss in Practice}
-
+\label{sec:Practice}
 %\begin{center}
@@
 Or is this some extra bit of method which has been added to the analysis...} \acl{I'm not sure that's what I'm saying.
-(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure".
+(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure").
 What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
@@
 Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about.}
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}
 

### 2017-12-04 PAPER.tex
put hat's on all empirically estimated C's

@@
 \noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. The data analyst has a choice for $
-\textbf{M}$ --- for simplicity in this section we set $\textbf{M} = \textbf{I}$, although we explore other cases for the analysis 
+\textbf{M}$ --- for simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
@@
 
-Since $\hat{\textbf{C}}$ is estimated from our data, its eigenspectrum differs from the eigenspectrum of our 
-true $\textbf{C}$, and this difference has consequences on our result. An eigenspectrum ranks the eigenvalues of a matrix from 
+If the covariance is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result.
+An eigenspectrum ranks the eigenvalues of a matrix from
 highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
@@
 
-In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\hat{\textbf{p}}_{x}$ (our detailed computation is described in the next section).
+In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\hat{\textbf{p}}_{x}$.
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\hat{\textbf{p}}_{x}$ by the following reasoning.
@@
 When $\textbf{R}_{r}$
-is taken to be $\textbf{C}_{r}^{-1}$ and $\textbf{C}_{r}$ is estimated from the data itself, the second term of Equation \eqref{eq:pout_expand} is a cross correlation between $\textbf{C}_{r}^{-1}\textbf{x}$ and
-$\textbf{C}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross correlation term is non-zero, and in fact negative in expectation. 
+is taken to be $\hat{\textbf{C}}_{r}^{-1}$, the second term of Equation \eqref{eq:pout_expand} is a cross-correlation between $\hat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
+$\hat{\textbf{C}_{r}}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
 This negative cross-term power arises from a coupling between the inverse of 
-$\textbf{C}_{r}$ and $\mathbf{x}$. 
+$\hat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
 Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
@@
 \begin{eqnarray}
-\textbf{C}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \\
+\hat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
 &=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
@@
 ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the
-inversion of a matrix like $\textbf{C}_{r}$ that is diagonal-dominant (from $\langle 
+inversion of a matrix like $\hat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle 
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
 off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\textbf{C}^{-1}_{r}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ (because of the diagonal dominance of $\textbf{C}^{-1}_{r}$), \acl{I'm not sure the previous claim follows.
-Why does this follow from the diagonal dominance?} but
-contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\textbf{C}^{-1}$. The
-correlation is negative because the product $\textbf{C}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\textbf{C}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
+terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\hat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
+the result is a vector that is similar to $\textbf{x}$ but
+contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\hat{\textbf{C}}^{-1}_{r}$. The
+correlation is negative because the product $\hat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
+of the off-diagonal terms in $\hat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
 of a diagonal-dominant matrix.
@@
 
-The correlation between $\textbf{C}_r^{-1}\textbf{e}$ and $\textbf{C}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+The correlation between $\hat{\textbf{C}}_r^{-1}\textbf{e}$ and $\hat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
@@
 
-We thus see from this subsection that signal loss generically arises because of couplings between $\textbf{C}^{-1}_{r}$ and $\mathbf{x}$.
-In principle, using $\textbf{C}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
+We thus see from this subsection that signal loss generically arises because of couplings between $\hat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
+In principle, using $\hat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
 Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
@@
 P_{\rm in,\alpha} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\textbf{C}_{r}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{r}^{-1}\textbf{r} \nonumber \\
+P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\hat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\hat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
 &&\phantom{=====} 
--  M_{\alpha}\textbf{x}^{\dagger}\textbf{C}_{x}^{-1}\textbf{Q}^{\alpha}\textbf{C}_{x}^{-1}\textbf{x} 
+-  M_{\alpha}\textbf{x}^{\dagger}\hat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\hat{\textbf{C}}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 signal-only simulation (i.e. comparing an unweighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for spurious correlations between the data and signal.
+failing to account for correlations between the data and signal (Section \ref{sec:Illustration}).
 \item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 

### 2017-12-19 PAPER.tex
fixed authors out of alphabetical order
Tue Dec 19 13:33:40 EST 2017
Tue Dec 19 14:34:13 EST 2017
jonnie edits until section 2.2

@@
 Zaki S. Ali\altaffilmark{1}, 
-Richard F. Bradley\altaffilmark{6,7,8},
-Gianni Bernardi\altaffilmark{9,10,11}, 
+Gianni Bernardi\altaffilmark{6,7,8}, 
+Richard F. Bradley\altaffilmark{9,10,11},
 Chris L. Carilli\altaffilmark{12,13},
@@
 \altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
-\altaffiltext{6}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
-\altaffiltext{7}{National Radio Astronomy Obs., Charlottesville VA}
-\altaffiltext{8}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
-\altaffiltext{9}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{10}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{11}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
+\altaffiltext{6}{Square Kilometer Array, S. Africa, Cape Town South Africa}
+\altaffiltext{7}{Dept. of Physics and Electronics, Rhodes University, South Africa}
+\altaffiltext{8}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
+\altaffiltext{9}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
+\altaffiltext{10}{National Radio Astronomy Obs., Charlottesville VA}
+\altaffiltext{11}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
 \altaffiltext{12}{National Radio Astronomy Obs., Socorro NM}
@@
 One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}); .
+its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}).
 This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
@@
 Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and is forecasted to be able to make a successful high-significance power spectrum 
+learned from previous experiments and is forecasted to be able to make a high-significance power spectrum 
 detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).
@@
 variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
-destroying an EoR signal? How can the source of a detection be properly identified? Many common techniques, such as 
+destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
 averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
@@
 estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of positive power offset in a visibility 
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
 measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, and \citet{trott_et_al2012}.
+estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, and \citet{trott_et_al2016}.
 Before showing
@@
 
-We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has length ($N_{t}, N_{f}$), where 
+We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has dimensions ($N_{t}, N_{f}$), where 
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
@@
 
-One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix. This type of weighting is attractive for power 
-spectrum analyses because it is an aggressive way to down-weight foregrounds and yields the smallest possible error bars on 
-a measurement (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}). The covariance matrix $\textbf{C}$, which in our case 
-describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
+One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix.
+This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
+Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
+In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for the PAPER analysis.
+
+The covariance matrix $\textbf{C}$, which describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
 instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data. However, if 
@@
 \noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The inverse covariance matrix is therefore $
+amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The weighting matrix is therefore $
 \textbf{R} = \hat{\textbf{C}}^{-1}$.
@@
 In the two panels, we compare inverse covariance weighting
-where $\textbf{C}$ is derived from the data (left),and projecting out the first eigenmode only (right). In the former 
+where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
 case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
-empirically estimated, its eigenvalues pose the risk of describing EoR-dominating modes. Consequently, these modes are over-fitted and down-weighted, leading to signal loss. 
-There is no signal loss when using only the zeroth eigenmode, since we are not using information from the weaker eigenmodes 
+empirically estimated, its eigenvalues differ from those of the true covariance and this error primarily affects the weaker (EoR-dominated) eigenmodes.
+There is no signal loss when using only the first eigenmode, since we are not using information from the weaker eigenmodes 
 which $\hat{\textbf{C}}$ does not describe accurately.}
@@
 \textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes. This is usually not the case for a covariance matrix, 
-for which a sloped eigenspectrum means that modes are given different weights. The modes with the highest eigenvalues are 
+for which a sloped eigenspectrum means that modes are given different weights in OQE power spectrum estimation. The modes with the highest eigenvalues are 
 down-weighted the most.
@@
 The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
-\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds. If these weak eigenmodes of $\hat{\textbf{C}}$ 
-characterize EoR modes, the EoR signal will be down-weighted (not as much as the strong foreground modes, but still down-weighted).
-This leads to the `overfitting' of noise (or rather `overfitting' of signal), which is signal loss.
+\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
+For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes.
+In other words, mis-estimating $\textbf{C}$ affects EoR-dominated eigenmodes more than FG-dominated modes, and it is primarily the error associated in down-weighting these `weak' modes that leads to signal loss.
 
@@
 signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
-project out the zeroth eigenmode (i.e.
-zero out all eigenmodes except the first one), thereby down-weighting the foreground-dominating mode only.
-Hence, we are not using information from all the weaker eigenmodes which carry the risk of
-describing EoR fluctuations. Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are 
+project out the first eigenmode (i.e.
+zero out all eigenmodes of the covariance matrix except the first one), thereby down-weighting the foreground-dominating mode only.
+Hence, we are not using information from all the weaker eigenmodes which have comparatively larger errors.
+Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are
 changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
@@
 	\centering
+	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
+	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
+In red, the mock EoR signal is comprised entirely of independent samples.
+Subsequent colors show time-averaged signals.
+As the number of realizations increases, we see that the empirical covariances approach the true covariances.
+With more independent samples, the quicker an empirical covariance converges.}
+	\label{fig:toy_sigloss16}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
@@
 	\label{fig:toy_sigloss7}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
-	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples.
-Subsequent colors show time-averaged signals.
-As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges.}
-	\label{fig:toy_sigloss16}
 \end{figure}

### 2017-12-20 PAPER.tex
made jonnie syntax edits throughout paper

@@
 \newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
+\newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }
 
@@
 Adrian Liu\altaffilmark{1,5}, 
-James E. Aguirre\altaffilmark{4},
+James E.~Aguirre\altaffilmark{4},
 Zaki S. Ali\altaffilmark{1}, 
@@
 Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
-spectra) can be made from different samples of data. Averaging each sample set gives us a realization of the (power spectrum) 
-answer. Realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common 
+spectra) can be made from different samples of data.
+Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
 between them. Hence, through the process of resampling and averaging along different axes, we can estimate error bars for 
@@
 
-Because foreground spectra are smooth in frequency, they preferentially show up at low delay, or low $k$ modes. For a particular 
-baseline length, there is a maximum delay imposed on foregrounds, which corresponds to the light-crossing time between two 
+For a particular 
+baseline length, there is a maximum delay imposed on sources attached to the sky, which corresponds to the light-crossing time between two 
 antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
@@
 \citep{datta_et_al2010, parsons_et_al2012b, vedantham_et_al2012, pober_et_al2013, thyagarajan_et_al2013, liu_et_al2014a, liu_et_al2014b, patil_et_al2017}. 
-The wedge describes a region in $k$-space contaminated by foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
+The wedge describes a region in $k$-space contaminated by smooth spectrum foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
 proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and 
@@
 
-However, this isolation is not perfect.  In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond 
+Although smooth spectrum foregrounds preferentially show up at low delay, or low $k$ modes, their isolation within the wedge is not perfect.
+In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
 the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
@@
 There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from 
-spreading to high $k$ values. For example, narrow window functions can be used to minimize the covariance of a particular 
+spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the covariance of a particular 
 $k$ value with other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
@@
 focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
-\ref{fig:ant_layout}). For information about the backend system of PAPER-64, its observations, and data reduction pipeline, we 
-refer the reader to \citet{parsons_et_al2010} and P64.
+\ref{fig:ant_layout}).
+All data is compressed, calibrated (using self-calibration and redundant calibration), delay-filtered (to remove foregrounds inside the wedge), LST-binned, and fringe-rate filtered.
+For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
+refer the reader to \citet{parsons_et_al2010} and P64. We note that all data processing steps are identical to those in P64 until after the LST-binning step in Figure 3 of P64.
 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/ant_layout.png}
+	\includegraphics[trim={0cm 4cm 0cm 5cm},width=\columnwidth]{plots/ant_layout_aspect.png}
 	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
-paper (such as the baseline involving antennas 49 and 41).}
+paper (i.e. the shortest horizontal spacings).}
 	\label{fig:ant_layout}
@@
 \begin{equation}
-\Delta^{\textbf{2}}\textbf{(k)} = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)},
+\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)},
 \end{equation}
@@
 
-For our analysis, we use $8$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
+For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
 range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
@@
 itself. Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify 
-the amount of signal loss accompanying a weighting scheme. In particular, we highlight major differences from the signal loss 
+the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation. In particular, we highlight major differences from the signal loss 
 computation used in P64, which previously underestimated losses.
@@
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
-off-diagonal terms results in a new diagonal-dominant matrix with negated off-diagonal terms. These off-diagonal
+off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
 terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\hat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
-($\textbf{R} = \textbf{C}^{-1}$), the weighting scheme used in P64 which leads to substantial loss. With this weighting, our 
+($\textbf{R} = \hat{\textbf{C}}^{-1}$), the weighting scheme used in P64 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
 expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
@@
 \item $t_{int}$: The integration time of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
-fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time 
+fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
 using the following:
 \begin{equation}
-t_{frf} = t_{int} \frac{\int1 \, df}{\int w^{2}(f) \,df},
-\end{equation}
-where $t_{int}=43$ seconds, $t_{frf}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
+t_{int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
+\end{equation}
+where $t_{i}=43$ seconds, $t_{int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
 taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
@@
 \item Substantial signal loss can result when weighting data using empirically estimated covariances (Section 
-\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant if fewer modes
+\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant the fewer number of independent modes that
 exist in the data. Hence, there exists a trade-off between sensitivity driven 
-time-averaging techniques such as fringe-rate filtering and signal loss. 
+time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
 \item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
@@
 In this Appendix, we examine a toy model for signal loss.
-Our goal is to build intuition by deriving an analytic formula for power spectrum signal loss.
+Our goal is to derive an analytic formula for power spectrum signal loss.
 We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum estimate.
@@
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of detangling the part of the output power spectrum dominated by the injected signal we can simply use $\hat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
+Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\hat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
 
@@
 is observable at a 2$\sigma$ level above the value of $\hat{\textbf{p}}_{x}$ (data).
-The different colors represent different $k$ values. We choose a probably of $90\%$ for our signal loss estimated power spectrum.
+The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.
 \label{fig:Prob_vs_Pin}}

### 2017-12-20 PAPER.tex
compiled paper

@@
 \end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix\footnote{For this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real.}.
+is the $\alpha$th diagonal element of the Fisher matrix (for this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real).
 In our case, however, we do not have \emph{a priori} knowledge of the covariance matrix.

### 2017-12-20 PAPER.tex
fixed bug in generating figure 11

@@
 group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
-were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$55\%$ for $10$ total 
+were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$63\%$ for $10$ total 
 independent samples) which sacrificed some sensitivity.

### 2017-12-21 PAPER.tex
edited affiliations
edited gianni's affilication
made gianni edits

@@
 Joshua S. Dillon\altaffilmark{1},
-Pat Klima\altaffilmark{7},
+Pat Klima\altaffilmark{10},
 David H. E. MacMahon\altaffilmark{2},
 David F. Moore\altaffilmark{4},
-Chuneeta D. Nunhokee\altaffilmark{10},
+Chuneeta D. Nunhokee\altaffilmark{7},
 Jonathan C. Pober\altaffilmark{14}, 
-William P. Walbrugh\altaffilmark{9},
-Andre Walker\altaffilmark{9}
+William P. Walbrugh\altaffilmark{6},
+Andre Walker\altaffilmark{6}
 }
@@
 \altaffiltext{7}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{8}{Harvard-Smithsonian Cen. for Astrophysics, Cambridge MA}
+\altaffiltext{8}{INAF-Instituto di Radioastronomia, Bologna Italy}
 \altaffiltext{9}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
@@
 mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
-\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{greenhill_bernardi2012}), the 
+\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
 Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
@@
 power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
-Kelvin, as well as cosmological scalings. The index $\alpha$ denotes a waveband in $k_{\parallel}$, where $k_{\parallel}$ is the 
-Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix --- as 
+Kelvin, as well as cosmological scalings.
+It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\delta\textbf{C}}{\delta p_{\alpha}}$, or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$ is the
+Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b})). $\textbf{R}$ is a weighting matrix --- as 
 an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
@@
 avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{EoR}$ as such, instead of computing it based on $\textbf{x}
+variance encoded along the diagonal. We model $\textbf{C}_{EoR}$ as such (i.e. the identity), instead of computing it based on $\textbf{x}
 _{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
@@
 The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - 
-by only using the first three eigenmodes. Recalling that the foregrounds can be described entirely by the first eigenmode, this 
+by only using the first three eigenmodes. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
 method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the 
@@
 not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
+While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG vs.
+EoR dominated, so selecting a subset of modes to down-weight is not trivial.
 

### 2017-12-22 PAPER.tex
changed P64 to A15

@@
 toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
-from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as P64, which have led to a 
+from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as A15, which have led to a 
 revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.
@@
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
-previously underestimated in the P64 analysis.
+previously underestimated in the A15 analysis.
 
@@
 %remove 
-avoid foregrounds, as done by P64, 
+avoid foregrounds, as done by A15, 
 \citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
@@
 $k$ value with other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
-window function to have a minimum response to low $k$ values. The window function used in P64 is constructed in such a way, 
+window function to have a minimum response to low $k$ values. The window function used in A15 is constructed in such a way, 
 specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}). 
@@
 Determining the source of detections at higher $k$'s is more difficult.
-In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (P64; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (A15; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
 In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
@@
 developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in 
-P64 and obtain a revised power spectrum estimate.
+A15 and obtain a revised power spectrum estimate.
 
@@
 For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
-refer the reader to \citet{parsons_et_al2010} and P64. We note that all data processing steps are identical to those in P64 until after the LST-binning step in Figure 3 of P64.
+refer the reader to \citet{parsons_et_al2010} and A15. We note that all data processing steps are identical to those in A15 until after the LST-binning step in Figure 3 of A15.
 
@@
 
-The previously best published $21$ cm upper limit result from P64 uses $124$ nights of data to place a $2\sigma$ upper limit 
+The previously best published $21$ cm upper limit result from A15 uses $124$ nights of data to place a $2\sigma$ upper limit 
 on $\Delta^{2}(k)$, defined as
@@
 
-For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (P64 uses a slightly different RA 
+For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (A15 uses a slightly different RA 
 range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
-MHz ($20$ channels), identical to the analysis in P64. We note that, besides using only one baseline type instead of the three in 
-P64, the PAPER-64 dataset that we use in this case study differs from that in P64 mainly by the applied fringe-rate filter. In P64, the 
+MHz ($20$ channels), identical to the analysis in A15. We note that, besides using only one baseline type instead of the three in 
+A15, the PAPER-64 dataset that we use in this case study differs from that in A15 mainly by the applied fringe-rate filter. In A15, the 
 applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
@@
 the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation. In particular, we highlight major differences from the signal loss 
-computation used in P64, which previously underestimated losses.
+computation used in A15, which previously underestimated losses.
 
@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$ 
-cm signal visibilities. Here we use the same method as in P64, where mock Gaussian noise visibilities (mock EoR signals) 
+cm signal visibilities. Here we use the same method as in A15, where mock Gaussian noise visibilities (mock EoR signals) 
 are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
-specific change from P64 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
+specific change from A15 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
 estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in P64 (the dominant reason is explained in the main text).}
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text).}
 
@@
 The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-It is this quantity that was used in P64 to calculate signal loss.
+It is this quantity that was used in A15 to calculate signal loss.
 However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
 In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
-Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to P64.
+Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to A15.
 
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
-($\textbf{R} = \hat{\textbf{C}}^{-1}$), the weighting scheme used in P64 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
+($\textbf{R} = \hat{\textbf{C}}^{-1}$), the weighting scheme used in A15 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
 expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
@@
 noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than P64 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
+a higher limit than A15 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
 \cc{replace with kolopanis limit instead later}
@@
 power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
-observational parameters. This power spectrum result differs from P64 in that it only uses data from one type of baseline ($30$ m 
+observational parameters. This power spectrum result differs from A15 in that it only uses data from one type of baseline ($30$ m 
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
 loss, bootstrapping, and the theoretical error computation. From this, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than A15 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
 	\label{fig:ps1_data}
@@
 
-In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the P64 
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the A15 
 analysis of PAPER-64. While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power 
@@
 where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
-This is lower than the $T_{sys}$ of $500$ K used in P64 because of several small miscalculation errors that were 
+This is lower than the $T_{sys}$ of $500$ K used in A15 because of several small miscalculation errors that were 
 identified\footnote{such as missing a square root in going from a variance to a standard deviation}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after squaring visibility measurements. In P64, a factor of $2$ was mistakenly used.
+estimates after squaring visibility measurements. In A15, a factor of $2$ was mistakenly used.
 \item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation. The sensitivity scales as the square root 
@@
 taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
-\item $N_{days}$: The total number of days of data analyzed. In P64, this number was set to $135$. However, because we 
+\item $N_{days}$: The total number of days of data analyzed. In A15, this number was set to $135$. However, because we 
 divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
@@
 days.
-\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In P64, this number was 
+\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In A15, this number was 
 the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
@@
 \end{equation}
-\noindent where, for the P64 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+\noindent where, for the A15 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
 entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
@@
 
-Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of P64 in Figure \ref{fig:sense_check}. 
+Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of A15 in Figure \ref{fig:sense_check}. 
 Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.
@@
 published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
-\sqrt{3}$ for three baseline types is needed to match P64 exactly). Major factors that contribute to the discrepancy are $
+\sqrt{3}$ for three baseline types is needed to match A15 exactly). Major factors that contribute to the discrepancy are $
 \Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-two major changes in the way we estimate errors since P64, using the lessons we've learned about sampling with replacement 
+two major changes in the way we estimate errors since A15, using the lessons we've learned about sampling with replacement 
 and bootstrapping independent samples.
@@
 
-In P64, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
+In A15, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
 ($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
@@
 The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
-group. In P64, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
+group. In A15, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
 were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$63\%$ for $10$ total 
@@
 zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
-on power spectrum results is shown in P64. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
+on power spectrum results is shown in A15. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
 removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
@@
 one baseline type, we quote a new $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
-P64 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+A15 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in P64, was under-estimated by a factor of $\sim$$1000$ for inverse 
+\item Signal loss, previously found to be $<2\%$ in A15, was under-estimated by a factor of $\sim$$1000$ for inverse 
 covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
@@
 prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
-power spectrum result, implying that if taken at face value, the theoretical prediction for noise in P64 was too high for its data 
+power spectrum result, implying that if taken at face value, the theoretical prediction for noise in A15 was too high for its data 
 points.

### 2017-12-22 PAPER.tex
made plots larger

@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
 	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 1cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss3.png}
-	\includegraphics[trim={1cm 0cm 0cm 0.3cm},clip,height=0.3\textwidth]{plots/toy_sigloss4.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.png}
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
 	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={1.5cm 0cm 3.5cm 0.1cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
 	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
@@
 	\centering
-	\includegraphics[trim={1.5cm 0cm 1.5cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss5.png}
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,height=0.29\textwidth]{plots/toy_sigloss15.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss5.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.png}
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss16.png}
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.png}
 	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0.3cm 0.2cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
 	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0.4cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.png}
-	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.png}
-	\includegraphics[trim={0.4cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.png}
-	\includegraphics[trim={1cm 0cm 1.3cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
 	\caption{Resulting power spectra estimates for our `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
 	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.png}
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_error2.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error2.png}
 	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.png}
 	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/toy_bias2.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias2.png}
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
@@
 	\centering
-	\includegraphics[trim={0cm 4cm 0cm 5cm},width=\columnwidth]{plots/ant_layout_aspect.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.png}
 	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 

### 2017-12-23 PAPER.tex
removed bootstrapping text about baseline sampling

@@
 itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
-consider such as the independence of values in a dataset. We explore potential pitfalls of bootstrapping in Section \ref{sec:ErrorOverview}.
+consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
 \item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
@@
 variance. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
-bootstrapping and then illustrate some of its pitfalls through toy models.
+bootstrapping and then illustrate one of its pitfalls through a toy model.
 
@@
 
+\begin{comment} % REMOVED THIS HALF OF BOOTSTRAPPING SECTION
 We will now discuss a second subtle feature of bootstrapping that fails to maximize the sensitivity of a dataset. Suppose we 
@@
 therefore the sensitivity of a final power spectrum measurement.
+\end{comment}
 
 In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset. However, we have 
-illustrated two situations in which bootstrapping can lead to under-estimated errors and sensitivities. First, we have shown that 
+illustrated a situation in which bootstrapping can lead to under-estimated errors and therefore under-estimated power spectrum limits. We have shown that 
 bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample. Estimated errors can drop to 
-arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements. We have 
-also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible. While 
-bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain 
-analysis choices have compromised the method and whether a variation of traditional re-sampling could be preferred instead.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error2.png}
-	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
-dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
-elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
-of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
+arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements. 
+%We have also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible. 
+While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain 
+analysis choices have compromised the method and whether a variation or an avoidance of traditional re-sampling could be preferred instead.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error2.png}
+%	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
+%dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
+%elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
+%of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
 Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black).
@@
 %The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
-	\label{fig:toy_error2}
-\end{figure}
+%	\label{fig:toy_error2}
+%\end{figure}
 
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-two major changes in the way we estimate errors since A15, using the lessons we've learned about sampling with replacement 
-and bootstrapping independent samples.
+one major changes in the way we estimate errors since A15, using the lesson we've learned about bootstrapping independent samples.
 
@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines with the ``single replacement" strategy 
-described in Section \ref{sec:ErrorOverview}.
-
-The single replacement strategy also provides a higher sensitivity estimate as only at most one baseline is repeated in each 
-group. In A15, baselines were chosen for groups randomly with replacement. In doing so, $\sim3$$-4$ baselines per group 
-were repeated (Figure \ref{fig:toy_error2} shows the fraction of independent samples to be $\sim$$63\%$ for $10$ total 
-independent samples) which sacrificed some sensitivity.
-
-Power spectrum estimates with these bootstrapping changes for PAPER-64 fringe-rate filtered data are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum estimates with this bootstrapping change for PAPER-64 fringe-rate filtered data are shown in Figure 
 \ref{fig:data_errors}. The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when the baseline average includes many repeated samples our sensitivity is not maximized (blue), while when 
-only one sample in the same average is allowed the possibility of being a repeat, the error on the noise-dominated higher $k$ 
-modes converges to the theoretical noise level (black).  However, if more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent 
-variation between bootstraps drops, resulting in limits below the predicted noise level (red).
+shown in the figure, when more elements are drawn for each bootstrap than the number of 
+independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level (gray).
 
@@
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$2$ due to 
-oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. Our limits were also 
-over-estimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power 
-spectra (Section \ref{sec:Boot}). Hence, the net change for our error estimation is negligible, though the rationale behind the 
-previous estimation was incorrect.
+\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$1.4$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 

### 2018-01-03 PAPER.tex
Edits to 3.1 intro section

@@
 In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data 
-itself. Here we describe a methodology that simulates the injection and recovery of a cosmological signal in order to quantify 
-the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation. In particular, we highlight major differences from the signal loss 
+itself.
+Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set.
+There is, of course, no way of determining an exact signal loss ``correction factor," i.e., we cannot perfectly undo the effects of a lossy estimator.
+In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
+the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation.  
+There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.
+In this section, we describe a methodology for determining an approximate correction factor which can be applied to a power spectrum estimate; in Appendix \ref{sec:Pr_appendix}, we present an alternate framework that explicitly interprets all measurements as upper limits in the presence of signal loss.
+These two methods yield very similar results, but fundamentally are answering subtly distinct questions.  
+We also highlight major differences from the signal loss 
 computation used in A15, which previously underestimated losses.

### 2018-01-04 PAPER.tex
changed caption for bootstrapping plot

--- 2017-12-23 PAPER.tex
@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
-	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and three different bootstrapping 
+	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and two different bootstrapping 
 methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss. Three different bootstrapping methods are shown: the blue and black use methods 
-where bootstrapping occurs on the baseline axis only (not the time axis), and they differ by how the baselines are randomly 
-sampled. It is evident that sensitivity is maximized when baselines are sampled in a way that ensures mostly independent 
-samples (only the last baseline spot is sampled randomly), as shown by the black curve. In red, bootstrapping occurs over both 
-the baseline and time axes, illustrating how errors can be under-estimated if sampling more values than independent ones 
-(fringe-rate filtering reduces the number of independent samples). We use the method illustrated by the black curve in our 
-updated analysis, which is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
+effects of bootstrapping from signal loss.
+The bootstrapping method used in A15 in shown in gray, where bootstrapping occurs along both the baseline and time axes.
+This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
+We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
+This is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
 	\label{fig:data_errors}

### 2018-01-05 PAPER.tex
revised bootstrapping error plot to show results for noise sim, not data

@@
 \begin{equation}
+\label{eq:noise}
 T_{rms} = \frac{T_{sys}}{\sqrt{\Delta\nu \Delta t N_{days} N_{pols}}},
@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum estimates with this bootstrapping change for PAPER-64 fringe-rate filtered data are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum estimates with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
 \ref{fig:data_errors}. The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss. As 
 shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits below the predicted noise level (gray).
+independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic.
 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/data_errors.png}
-	\caption{$2\sigma$ power spectrum errors (not upper limits) using PAPER-64 data and two different bootstrapping 
-methods. The data is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.png}
+	\caption{$2\sigma$ power spectrum errors (not upper limits) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
+methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
 effects of bootstrapping from signal loss.

### 2018-01-09 PAPER.tex
moved jonnie up in author list

@@
 Adrian Liu\altaffilmark{1,5}, 
+Jonathan C. Pober\altaffilmark{6}, 
 James E.~Aguirre\altaffilmark{4},
 Zaki S. Ali\altaffilmark{1}, 
-Gianni Bernardi\altaffilmark{6,7,8}, 
-Richard F. Bradley\altaffilmark{9,10,11},
-Chris L. Carilli\altaffilmark{12,13},
+Gianni Bernardi\altaffilmark{7,8,9}, 
+Richard F. Bradley\altaffilmark{10,11,12},
+Chris L. Carilli\altaffilmark{13,14},
 David R. DeBoer\altaffilmark{2}, 
@@
 Joshua S. Dillon\altaffilmark{1},
-Pat Klima\altaffilmark{10},
+Pat Klima\altaffilmark{11},
 David H. E. MacMahon\altaffilmark{2},
 David F. Moore\altaffilmark{4},
-Chuneeta D. Nunhokee\altaffilmark{7},
-Jonathan C. Pober\altaffilmark{14}, 
-William P. Walbrugh\altaffilmark{6},
-Andre Walker\altaffilmark{6}
+Chuneeta D. Nunhokee\altaffilmark{8},
+William P. Walbrugh\altaffilmark{7},
+Andre Walker\altaffilmark{7}
 }
@@
 \altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
-\altaffiltext{6}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{7}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{8}{INAF-Instituto di Radioastronomia, Bologna Italy}
-\altaffiltext{9}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
-\altaffiltext{10}{National Radio Astronomy Obs., Charlottesville VA}
-\altaffiltext{11}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
-\altaffiltext{12}{National Radio Astronomy Obs., Socorro NM}
-\altaffiltext{13}{Cavendish Lab., Cambridge UK}
-\altaffiltext{14}{Dept. of Physics, Brown University, Providence RI}
+\altaffiltext{6}{Dept. of Physics, Brown University, Providence RI}
+\altaffiltext{7}{Square Kilometer Array, S. Africa, Cape Town South Africa}
+\altaffiltext{8}{Dept. of Physics and Electronics, Rhodes University, South Africa}
+\altaffiltext{9}{INAF-Instituto di Radioastronomia, Bologna Italy}
+\altaffiltext{10}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
+\altaffiltext{11}{National Radio Astronomy Obs., Charlottesville VA}
+\altaffiltext{12}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
+\altaffiltext{13}{National Radio Astronomy Obs., Socorro NM}
+\altaffiltext{14}{Cavendish Lab., Cambridge UK}
 
@@
 Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
-As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$ and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
+As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$\% and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
 We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
@@
 
-The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
 Overall the limits show good agreement, with k modes differing by factors of 2 to 4.

### 2018-01-10 PAPER.tex
made josh edits until section 2.1

@@
 \author{
-Carina Cheng\altaffilmark{1},
+Carina Cheng\altaffilmark{1}$^{,\diamond}$,
 Aaron R. Parsons\altaffilmark{1,2},
@@
 Saul A. Kohn\altaffilmark{4},
-Adrian Liu\altaffilmark{1,5}, 
+Adrian Liu\altaffilmark{1,5}$^{,\dagger}$, 
 Jonathan C. Pober\altaffilmark{6}, 
@@
 Matthew R. Dexter\altaffilmark{2},
-Joshua S. Dillon\altaffilmark{1},
+Joshua S. Dillon\altaffilmark{1}$^{,*}$,
 Pat Klima\altaffilmark{11},
@@
 \begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and 
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
 galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
@@
 of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
-develop techniques that help maximize sensitivity and validate results. Additionally, it is imperative to understand the trade-offs 
-between different methods and their effects on common power spectrum themes. In this paper, we focus on three major 
-themes --- signal loss, power spectrum error bar estimation, and bias in measurements. We describe techniques that affect 
+develop techniques that help maximize sensitivity while validating results. Additionally, it is imperative to understand the trade-offs 
+between different methods and their effects on power spectrum estimates. In this paper, we focus on three major 
+themes --- signal loss, power spectrum error estimation, and bias in measurements. We describe techniques that affect 
 these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
@@
 led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result mostly stems from an 
-updated signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
+improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
 previously published PAPER analyses.
@@
 
-By about one billion years after the Big Bang ($z \sim 6$), the very first stars and galaxies are thought to have ionized all the 
+{\let\thefootnote\relax\footnote{$^{\diamond}$\href{mailto:ccheng@berkeley.edu}{ccheng@berkeley.edu}}}
+{\let\thefootnote\relax\footnote{$^{\dagger}$Hubble Fellow}}
+{\let\thefootnote\relax\footnote{$^{*}$NSF AAPF Fellow}}
+\setcounter{footnote}{0}
+
+By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
 neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
 luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
-into a plasma, is known as the epoch of reionization (EoR). The EoR is a relatively unexplored era in our cosmic dawn. Its 
+into a plasma, is known as the Epoch of Reionization (EoR).
+The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans from the birth of the first stars to the full reionization of the intergalactic medium (IGM).
+Its
 history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
-Direct measurements of the EoR would unlock powerful information about the intergalactic medium, revealing connections 
+Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
@@
 
-One promising technique to probe the EoR is to target the 21 cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
+One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
 its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}).
-This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
+This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
 of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. Tracing the 21 cm line as a function of redshift offers a window into the 
-evolution of ionization, temperature, and density fluctuations during this transformative era.
+stretching out as it traveled through expanding space. Tracing the 21\,cm line as a function of redshift offers a window into the 
+evolution of ionization, temperature, and density fluctuations.
 
 Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
-the 21 cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
+the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
 mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
@@
 Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and is forecasted to be able to make a high-significance power spectrum 
-detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{deboer_et_al2017}).
-
-The major challenge that faces all 21 cm experiments is isolating a small signal that is buried underneath foregrounds and 
+learned from previous experiments and is forecast to be able to make a high-significance power spectrum 
+detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).
+
+The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
 instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
@@
 with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
-the accuracy and reliability of a potential EoR detection. In this paper, we discuss three themes that are essential to investigate 
+the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics that are essential to investigate 
 for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
@@
 
-Despite there being many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
-methods for determining accurate confidence intervals and rigorous techniques to identify and suppress systematics.  In this 
+Though there are many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
+methods for determining accurate confidence intervals and rigorous techniques to identify and control systematics.  In this 
 paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
@@
 A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
-spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important check-list for 
+spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
 a rigorous power spectrum analysis.
@@
 weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
-weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}).
+weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
 This weighting has the effect of down-weighting correlated
@@
 methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
-itself (\citealt{andrae2010}). By randomly drawing many samples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
+itself (\citealt{andrae2010}). By randomly drawing many subsamples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
 consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, and \citet{trott_et_al2016}.
+estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, and \citet{trott_et_al2016}.
 Before showing
@@
 heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data 
-distribution. From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss 
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\hat{\textbf{p}}_{x}$.
+From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
 for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 

### 2018-01-11 PAPER.tex
made josh edits until 2.2, added new Fig17 for convergence of empirically estimated eigenvectors

@@
 \newcommand{\p}{\mathbf{p}}
-\newcommand{\phat}{\hat{\mathbf{p}}}
+\newcommand{\phat}{\widehat{\mathbf{p}}}
 \newcommand{\C}{\mathbf{C}}
-\newcommand{\Chat}{\mathbf{\hat{C}}}
+\newcommand{\Chat}{\mathbf{\widehat{C}}}
 \newcommand{\F}{\mathbf{F}}
-\newcommand{\Fhat}{\mathbf{\hat{F}}}
+\newcommand{\Fhat}{\mathbf{\widehat{F}}}
 \newcommand{\Q}{\mathbf{Q}}
 \newcommand{\I}{\mathbf{I}}
-%\newcommand{\xhat}{\hat{\mathbf{x}}}
-%\newcommand{\nhat}{\hat{\mathbf{n}}}
+%\newcommand{\xhat}{\widehat{\mathbf{x}}}
+%\newcommand{\nhat}{\widehat{\mathbf{n}}}
 %\newcommand{\A}{\mathbf{A}}
 %\newcommand{\N}{\mathbf{N}}
-%\newcommand{\rhat}{\hat{\mathbf{r}}}
-%\newcommand{\khat}{\hat{\mathbf{k}}}
+%\newcommand{\rhat}{\widehat{\mathbf{r}}}
+%\newcommand{\khat}{\widehat{\mathbf{k}}}
 %\newcommand{\btheta}{\boldsymbol \theta}
@@
 Signal loss can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during 
-spectral calibration, applying a delay-domain filter, or by weighting data by itself. Here we focus on signal loss associated with 
+spectral calibration, applying a delay-domain filter, or by deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
@@
 
-We begin with our data matrix, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy. It has dimensions ($N_{t}, N_{f}$), where 
+We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
+It has length $N_{t} \times N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{t}, N_{f}$), where
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
 the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
-we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\hat{q}_{\alpha}$:
+we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
 
@@
 \label{eq:qhat}
-\hat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
+\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
 \end{equation}
 Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
-power spectrum space, while also taking into account physical constants such as the Boltzmann constant used to convert Jy to 
-Kelvin, as well as cosmological scalings.
-It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\delta\textbf{C}}{\delta p_{\alpha}}$, or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$ is the
+power spectrum space, while also converting from Jy to 
+Kelvin and taking into account cosmological scalings.
+It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\delta\textbf{C}}{\delta p_{\alpha}}$, or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
 Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b})). $\textbf{R}$ is a weighting matrix --- as 
@@
 \label{eq:phat}
-\hat{\textbf{p}} = \textbf{M}\hat{\textbf{q}},
-\end{equation}
-
-\noindent where $\hat{\textbf{p}}$ is the normalized estimate of the true power spectrum. The data analyst has a choice for $
-\textbf{M}$ --- for simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
+\widehat{\textbf{p}} = \textbf{M}\widehat{\textbf{q}},
+\end{equation}
+
+\noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum. The data analyst has a choice for $
+\textbf{M}$ (subject to the constraint that window functions are sensible) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
@@
 In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
-matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\hat{\textbf{p}}$. Our goal in 
+matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\widehat{\textbf{p}}$. Our goal in 
 experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
@@
 realistic EoR signal would have a sloped power spectrum in $\textbf{p}$(k) (instead of flat, as in the case of white noise), 
-which could be simulated by introducing frequency correlations into the mock EoR signal. However, in this paper we treat all 
+which could be simulated by introducing frequency correlations into the mock EoR signal. However, here we treat all 
 $k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
-\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data matrices are shown in Figure 
+\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data components are shown in Figure 
 \ref{fig:toy_sigloss1}.
@@
 
-Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data $\textbf{x}$ itself:
-
-\begin{equation}
-\hat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
+Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data $\textbf{x}$ itself. For instance, one could time-average such that:
+
+\begin{equation}
+\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
 \end{equation}
@@
 \noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle$ denotes a finite average over time $t$. The weighting matrix is therefore $
-\textbf{R} = \hat{\textbf{C}}^{-1}$.
-
-First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\hat{\textbf{C}}^{-1}$. 
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3} (the right plot shows an alternate weighting approach 
-and will be discussed further below). Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix is therefore $
+\textbf{R} = \widehat{\textbf{C}}^{-1}$.
+
+First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\widehat{\textbf{C}}^{-1}$. 
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}. Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $
 \textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
@@
 where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
-case, signal loss arises from using information from all eigenmodes of $\hat{\textbf{C}}$. Because $\hat{\textbf{C}}$ is 
+case, signal loss arises from using information from all eigenmodes of $\widehat{\textbf{C}}$. Because $\widehat{\textbf{C}}$ is 
 empirically estimated, its eigenvalues differ from those of the true covariance and this error primarily affects the weaker (EoR-dominated) eigenmodes.
-There is no signal loss when using only the first eigenmode, since we are not using information from the weaker eigenmodes 
-which $\hat{\textbf{C}}$ does not describe accurately.}
+There is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are not using the relative weights of the weaker eigenmodes 
+which $\widehat{\textbf{C}}$ does not describe accurately.}
 	\label{fig:toy_sigloss3}
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
-	\caption{Eigenspectrum of $\hat{\textbf{C}}_{FG}$ (blue), $\hat{\textbf{C}}_{EoR}$ (red), and $\hat{\textbf{C}}_{FG+EoR}$ 
-(green). The eigenspectrum of $\hat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
+	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG}$ (blue), $\widehat{\textbf{C}}_{EoR}$ (red), and $\widehat{\textbf{C}}_{FG+EoR}$ 
+(green). The eigenspectrum of $\widehat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
 sinusoid. These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, 
@@
 If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
-representative of real fluctuations in the data. However, when using an estimated $\hat{\textbf{C}}$ that is derived from one 
-particular data realization, its eigenvalues and eigenvectors may differ from the truth. Said differently, shapes that may not exist (or have a 
-weaker existence) in a true covariance may appear stronger in the estimated covariance. Hence, they will be down-weighted 
+representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
+particular data realization, its eigenvalues and eigenvectors may differ from the truth.
+Said differently, shapes that may not exist (or exist rarely) in a true covariance may appear stronger in the estimated covariance.
+Hence, they will be down-weighted
 more than they should be.
 
-In general, the strongest modes of $\hat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
+In general, the strongest modes of $\widehat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
 --- the most prominent shapes in the data. For these `strong' modes, where foregrounds outshine the EoR signal, $
-\hat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
+\widehat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
 successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
@@
 covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
-$\hat{\textbf{C}}_{FG}$ but effectively absent from $\hat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
+$\widehat{\textbf{C}}_{FG}$ but effectively absent from $\widehat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
 
@@
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
+In such a case, the empirical covariance believes these modes should be down-weighted more than the true covariance would.
 For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes.
@@
 Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
-signal loss. Recall that our toy model foreground is a sinusoid that can be perfectly described by a single eigenmode. We can 
+signal loss.
+Recall that our toy model foreground is a sinusoid, so it can be perfectly described by a single eigenmode.
+Using the full dataset's (foreground plus EoR signal) empirical covariance, we can
 project out the first eigenmode (i.e.
-zero out all eigenmodes of the covariance matrix except the first one), thereby down-weighting the foreground-dominating mode only.
-Hence, we are not using information from all the weaker eigenmodes which have comparatively larger errors.
-Altering $\hat{\textbf{C}}$ as such is one example of a regularization method, in which we are
-changing $\hat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
+use the true eigenvalue of the first eigenmode, but flatten the rest of the spectrum to have eigenvalues of 1), thereby down-weighting the foreground-dominated mode more than the rest of the modes.
+Hence, we are not using the relative weighting information from all the weaker eigenmodes which have comparatively larger errors.
+Altering $\widehat{\textbf{C}}$ as such is one example of a regularization method, in which we are
+changing $\widehat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
 power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
 demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
-them without signal loss. There are several other ways to regularize $\hat{\textbf{C}}$, and we will discuss some in Section 
+them without signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
 \ref{sec:otherweight}.
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). 
-Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes corresponding to 
+Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes consistent with 
 the sidereal motion on the sky, while down-weighting modes which are noise-like.
@@
 $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of 
-independent samples is similar to the number of frequency channels --- therefore, our matrices will be full rank.
+independent samples is similar to the number of frequency channels --- our matrices will still be full rank.
 %\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
 
+\cc{Note to Adrian - somewhere in the next paragraph would be good to ref Fig17}
 The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
 \ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
-the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data. With 
+the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.
+
+To quantify the convergence of `weak' and `strong' eigenmodes present in a sloped eigenspectrum, we form a mock covariance matrix with diagonal values that span $4$ orders of magnitude.
+We then draw random data realizations from this covariance and compute a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$:
+\begin{equation}
+\label{eq:converge_eig}
+\varepsilon (\widehat{\textbf{v}}) \equiv \frac{1}{N_{f}}\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i},
+\end{equation}
+where $N_{f}$ is the number of frequencies ($20$) in the mock data. We plot this statistic against the number of realizations in Figure \ref{fig:toy_sigloss17}, which shows that...
+
+With 
 fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
-true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon$ for the empirical covariance, which we define as
+true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 \begin{equation}
 \label{eq:converge}
-\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\Chat_{ij} - \C_{ij})^2}{\sum_{ij} \C_{ij}^2}},
+\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
 \end{equation}
@@
 	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\hat{\textbf{C}}_{FG+EoR}$, 
+yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, 
 in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
@@
 \end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.png}
+	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different number of mock data realizations.
+The colors span from the 0th eigenmode (the first one) to the 19th eigenmode (the last one), where they are ordered by eigenvalue in descending order.
+This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes.}
+	\label{fig:toy_sigloss17}
+\end{figure}
 
@@
 
-In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\hat{\textbf{C}}$ can 
-make the difference between $\sim$zero and some signal loss, if we can distinguish between real eigenmodes in a true covariance 
-matrix from those in an estimated one. We will now use our toy model to describe several other ways to tailor $\hat{\textbf{C}}$ 
+In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\widehat{\textbf{C}}$ can 
+make the difference between nearly zero and some signal loss. We will now use our toy model to describe several other ways to tailor $\widehat{\textbf{C}}$ 
 in order to minimize signal loss. We choose four independent regularization methods to highlight in this section, which have 
@@
 spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
+These examples are not meant to be taken as suggested analyses methods but rather as illustrative cases.
 
@@
 variance encoded along the diagonal. We model $\textbf{C}_{EoR}$ as such (i.e. the identity), instead of computing it based on $\textbf{x}
-_{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \hat{\textbf{C}}_{FG}$ (where $\hat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
-\textbf{x}_{FG}^{\dagger}\rangle_{t}$) to obtain a final $\hat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+_{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \widehat{\textbf{C}}_{FG}$ (where $\widehat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
+\textbf{x}_{FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\hat{\textbf{C}}$ would).
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}$ would).
 This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
@@
 green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}. This deviation is a consequence of the difference between the 
-true and modeled covariance matrices. In practice such a weighting option is not feasible, as we do not know $\textbf{C}_{EoR}
-$.
+true and modeled covariance matrices. In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\textbf{C}_{FG}$ is unknown.
 
@@
 EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each minimize signal 
-loss, including modeling the covariance matrix of EoR (upper left), regularizing $\hat{\textbf{C}}$ by adding an identity matrix to 
-it (upper right), using only the first three eigenmodes of $\hat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
-$\hat{\textbf{C}}$ (lower right).}
+loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to 
+it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
+$\widehat{\textbf{C}}$ (lower right).}
 	\label{fig:toy_sigloss8}
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
-	\caption{We compare the eigenspectrum of an empirically calculated $\hat{\textbf{C}}$ (green) to that of four alternate 
-weighting options, including modeling the covariance matrix of EoR (red), regularizing $\hat{\textbf{C}}$ by adding an identity 
-matrix to it (blue), using only the first three eigenmodes of $\hat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
-\hat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
+	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
+weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
+matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
+\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
 computed for the `fringe-rate filtered' (time-averaged) toy model case.}
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\hat{\textbf{C}} = 
-\hat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}} = 
+\widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
 of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
@@
 similar weights, we avoid down-weighting EoR modes more than others.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\hat{\textbf{C}}$ a different way - 
+Although there is negligible signal loss, the small green peak at $k\sim3$ represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
+
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\widehat{\textbf{C}}$ a different way - 
 by only using the first three eigenmodes. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
@@
 
-The last regularization scheme we are highlighting here is setting $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\hat{\textbf{C}}$).
+The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} = \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\widehat{\textbf{C}}$).
 In the bottom right
@@
 frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
-\hat{\textbf{C}}$ would be an effective way of removing this contamination.
+\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
 
 In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without 
-removing the underlying cosmological signal. As we investigated however, there are trade-offs between the weighting method 
+removing the underlying cosmological signal. However, there are trade-offs between the weighting method 
 used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
@@
 \begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\hat{\textbf{p}}\textbf{(k)},
+\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\widehat{\textbf{p}}\textbf{(k)},
 \end{equation}
@@
 \label{eq:sigloss}
-P_{\rm out,\alpha} &\equiv& \hat{\textbf{p}}_{r,\alpha}-\hat{\textbf{p}}_{x,\alpha} \nonumber \\
+P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha}-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
 &=& M_{\alpha}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
@@
 $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal,
-$\hat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\hat{\textbf{p}}_{r}$ is the power spectrum of the
-data plus injection, and $P_{\rm out}$ is the difference between $\hat{\textbf{p}}_{r}$ and $\hat{\textbf{p}}_{x}$.
-
-In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\hat{\textbf{p}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\hat{\textbf{p}}_{x}$ by the following reasoning.
+$\widehat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\widehat{\textbf{p}}_{r}$ is the power spectrum of the
+data plus injection, and $P_{\rm out}$ is the difference between $\widehat{\textbf{p}}_{r}$ and $\widehat{\textbf{p}}_{x}$.
+
+In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning.
 
@@
 \label{eq:Deriv1}
-\hat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
 \end{equation}
@@
 \label{eq:Deriv2}
-\hat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
+\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
 \end{equation}
@@
 When $\textbf{R}_{r}$
-is taken to be $\hat{\textbf{C}}_{r}^{-1}$, the second term of Equation \eqref{eq:pout_expand} is a cross-correlation between $\hat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
-$\hat{\textbf{C}_{r}}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
+is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the second term of Equation \eqref{eq:pout_expand} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
+$\widehat{\textbf{C}_{r}}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
 This negative cross-term power arises from a coupling between the inverse of 
-$\hat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
+$\widehat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
 Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
@@
 \begin{eqnarray}
-\hat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
+\widehat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
 &=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
@@
 ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the
-inversion of a matrix like $\hat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle 
+inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle 
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
 off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\hat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
+terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
 the result is a vector that is similar to $\textbf{x}$ but
-contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\hat{\textbf{C}}^{-1}_{r}$. The
-correlation is negative because the product $\hat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\hat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
+contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
+correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
+of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
 of a diagonal-dominant matrix.
@@
 
-The correlation between $\hat{\textbf{C}}_r^{-1}\textbf{e}$ and $\hat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
@@
 
-We thus see from this subsection that signal loss generically arises because of couplings between $\hat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
-In principle, using $\hat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
+We thus see from this subsection that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
+In principle, using $\widehat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
 Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
-($\textbf{R} = \hat{\textbf{C}}^{-1}$), the weighting scheme used in A15 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
+($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in A15 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
 expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
@@
 P_{\rm in,\alpha} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\hat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\hat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
+P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
 &&\phantom{=====} 
--  M_{\alpha}\textbf{x}^{\dagger}\hat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\hat{\textbf{C}}_{x}^{-1}\textbf{x} 
+-  M_{\alpha}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
-\hat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
+\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
 From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
 value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$.
-Performing a summation and normalization for the entire distribution of $\hat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
+Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
 We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
@@
 heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\hat{\textbf{p}}_{x}$.
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
 From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
@@
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
-are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\hat{\textbf{C}}$ that 
+are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
 are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
@@
 which denote power spectrum values, post-signal loss estimation, for two other regularization schemes. We multiply an identity 
-matrix element-wise to $\hat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
-of $\textbf{I}$ to $\hat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
+matrix element-wise to $\widehat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
+of $\textbf{I}$ to $\widehat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
 their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black curve).
 
-For the remainder of this paper, we choose to use the weighting option of $\hat{\textbf{C}} = \hat{\textbf{C}} \circ \textbf{I}$, or 
-inverse variance weighting, which we will denote as $\hat{\textbf{C}}_{eff}$. We choose this weighting scheme due to its 
+For the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} = \widehat{\textbf{C}} \circ \textbf{I}$, or 
+inverse variance weighting, which we will denote as $\widehat{\textbf{C}}_{eff}$. We choose this weighting scheme due to its 
 simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Power spectrum of PAPER-64 using $\hat{\textbf{C}}_{eff}$ (inverse variance weighting). Black and gray points correspond to positive and 
+	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$ (inverse variance weighting). Black and gray points correspond to positive and 
 negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
@@
 
-In this section we have shown three simple ways of regularizing $\hat{\textbf{C}}$ to minimize signal loss using PAPER-64 
+In this section we have shown three simple ways of regularizing $\widehat{\textbf{C}}$ to minimize signal loss using PAPER-64 
 data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
-$\hat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
-\hat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
+$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
+\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
 horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
@@
 
-Another possible way to regularize $\hat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\hat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
-down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\hat{\textbf{C}}$ from 
+Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
+calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
+down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from 
 data that is similar but not exactly the same as the data that is being down-weighted.
@@
 \ref{fig:ps_noise}, where the black and gray points represent positive and negative power spectrum values, respectively (with 
-$2\sigma$ error bars and weighting matrix $\hat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power 
+$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power 
 spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
@@
 power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
-\hat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
+\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
 limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
@@
 analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
-former, we filter out certain cross-multiplications when forming $\hat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
+former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
 dataset is divided into two halves: even julian dates and odd julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
 the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
-$\hat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
+$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
 example, in order to prevent the squaring of the same thermal noise.
@@
 \item Original Data (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised 
-PAPER-64 power spectrum (one baseline type only) with weighting matrix $\hat{\textbf{C}}_{eff}$. There are clear detections at 
+PAPER-64 power spectrum (one baseline type only) with weighting matrix $\widehat{\textbf{C}}_{eff}$. There are clear detections at 
 low $k$'s.
@@
 
-The minimum-variance quadratic estimator $\hat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\begin{equation}
-\hat{p}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
+The minimum-variance quadratic estimator $\widehat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
+\begin{equation}
+\widehat{p}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
 \end{equation}
@@
 \label{eq:phatloss}
-\hat{p}_\alpha^\textrm{loss} = \frac{1} {2 \hat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
+\widehat{p}_\alpha^\textrm{loss} = \frac{1} {2 \widehat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
 \end{equation}
@@
 \begin{equation}
-\hat{F}_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
+\widehat{F}_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
 \end{equation}
@@
 
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\hat{p}_\alpha^\textrm{loss}$ in terms of $\hat{p}_\alpha$.
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{p}_\alpha^\textrm{loss}$ in terms of $\widehat{p}_\alpha$.
 We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
@@
 \begin{equation}
-\hat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
+\widehat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
 \end{equation}
@@
 \label{eq:phatlossexpanded}
-\hat{p}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
+\widehat{p}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
 \end{equation}
@@
 \begin{equation}
-\hat{p}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
+\widehat{p}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
 \end{equation}
@@
 \begin{equation}
-\langle \hat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N) p_\alpha,
+\langle \widehat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N) p_\alpha,
 \end{equation}
@@
 
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{out} = \hat{\textbf{p}}_{r} - \hat{\textbf{p}}_{x}$.
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$.
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\hat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
+Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
 
@@
 The solid black
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\hat{\textbf{p}}_{x}$, the data distribution.
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
 At low injection, $P_{\rm out}$ converges to the data level.}
@@
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $\hat{\textbf{p}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+In the 2D space relating total $\widehat{\textbf{p}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
 data only) and very large levels are dominated by the injected signal.
@@
 \caption{The probability that an injected signal of level P$_{inj}$
-is observable at a 2$\sigma$ level above the value of $\hat{\textbf{p}}_{x}$ (data).
+is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
 The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.
@@
 \begin{equation}
-\hat{\textbf{p}}_{r} > \hat{\textbf{p}}_{x} \Lambda,
+\widehat{\textbf{p}}_{r} > \widehat{\textbf{p}}_{x} \Lambda,
 \end{equation}  
@@
  \begin{equation}
-\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(\hat{\textbf{p}}_x) \Prob(\hat{\textbf{p}}_r,P_{in}) dr
- \end{equation}
- where $\Prob(\hat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\hat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\hat{\textbf{p}}_r,P_{in})$ is the probability of obtaining the summed power spectrum $\hat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_r,P_{in}) dr
+ \end{equation}
+ where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_r,P_{in})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
 

### 2018-01-11 PAPER.tex
made josh edits until 2.3

@@
 samples in the data. To mimic this filter, we average every four time integrations of our toy model dataset together, yielding 
-$25$ independent samples in time (Figure \ref{fig:toy_sigloss5}, left). We choose these numbers so that the total number of 
+$25$ independent samples in time (Figure \ref{fig:toy_sigloss5}). We choose these numbers so that the total number of 
 independent samples is similar to the number of frequency channels --- our matrices will still be full rank.
@@
 The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
-\ref{fig:toy_sigloss5} (right plot). The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
+\ref{fig:toy_sigloss15}. The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
 the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss5.png}
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.png}
+	\caption{Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
+yielding $25$ independent samples in time. Real parts are shown here.}
+	\label{fig:toy_sigloss5}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.png}
-	\caption{Left: Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here. Right: Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, 
-in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
-	\label{fig:toy_sigloss5}
-\end{figure*}
+	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
+	\label{fig:toy_sigloss15}
+\end{figure}
 
@@
 it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
-$\widehat{\textbf{C}}$ (lower right).}
+$\widehat{\textbf{C}}$ (lower right). The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{FG}$ and $\textbf{C}_{EoR}$ like we do in the toy model.}
 	\label{fig:toy_sigloss8}
@@
 \widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-computed for the `fringe-rate filtered' (time-averaged) toy model case.}
+computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
 	\label{fig:toy_sigloss14}
@@
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does a poor job down-weighting foregrounds. For this toy model, 
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds. For this toy model, 
 our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
@@
 two frequencies. Because we disregard information from all other frequency combinations in this case, we do a poor job 
-suppressing the foreground. But because we flattened the eigenspectrum, we also avoid signal loss.
-
-Although the fourth method did not successfully recover EoR for this particular simulation, it is important that we show that there 
+suppressing the foreground.
+But because we flattened the eigenspectrum, we also avoid signal loss.
+Although this method did not successfully recover EoR for this particular simulation, it is important that we show that there
 are many options for estimating a covariance matrix, and some may be more effective than others based on the spectral nature 
-of the components in a dataset. One may imagine a situation where a particular systematic is contained to an isolated 
-frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
-\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
+of the components in a dataset. 
+%One may imagine a situation where a particular systematic is contained to an isolated 
+%frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
+%\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
 
@@
 independent samples in this toy model, the error associated with drawing $N$=$100$ samples with replacement does match the theoretical prediction 
-as expected.
+as expected (the black points cross the green line at $N$=$100$ in Figure \ref{fig:toy_error1}).
 
@@
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-sampling with replacement. The star represents the standard deviation of $N_{boot}$ bootstraps, each created by drawing $1000$ 
+sampling with replacement. The star represents the standard deviation of $N_{boot}=500$ bootstraps, each created by drawing $1000$ 
 elements (with replacement) from a length $1000$ array of a Gaussian random signal.

### 2018-01-11 PAPER.tex
Made josh edits until Section 3

@@
 \usepackage{comment}
+\usepackage{titlesec}
 \citestyle{aa}
@@
 between them. Hence, through the process of resampling and averaging along different axes, we can estimate error bars for 
-our results which represent the underlying distribution of values that are allowed by our measurements.
+our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
 
@@
 \citealt{vedantham_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
-experiments remain ultimately limited by residuals rather than noise.
+experiments currently remain limited by residuals rather than noise, especially at low $k$.
 
@@
 avoid foregrounds, as done by A15, 
-\citet{parsons_et_al2014}, and \citet{jacobs_et_al2015}.
+\citet{parsons_et_al2014}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{jacobs_et_al2015}, \citet{beardsley_et_al2016}, and \citet{trott_et_al2016}.
 
@@
 convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
-foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum and the 
-antenna response, both of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017}.
+foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum, the signal chain, and the 
+antenna response, all of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017}.
 
@@
 Determining the source of detections at higher $k$'s is more difficult.
-In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, and calibration errors (A15; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (A15; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
 In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
@@
 two quantities that go into a measurement have separate noises that don't correlate with each other.
+We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous by \citet{dillon_et_al2014}.
 
@@
 
-The jackknife is a resampling technique in which a statistic (i.e. power spectrum) is computed in subsets of the data. These 
+The jackknife is a resampling technique in which a statistic (i.e. power spectrum) is computed in subsets of the data (\citealt{quenouille1949}; \citealt{tukey1958}). These 
 subsets are then compared to reveal systematics. In this section we define two main tests --- the null test and the traditional 
@@
 from one of the data subsets to the other (i.e. doesn't get subtracted perfectly). 
-\item \textbf{Traditional Jackknife}: In a more broad sense, it is important to perform many jackknife tests in order to instill 
+\item \textbf{Traditional Jackknife}: In a broader sense, it is important to perform many jackknife tests in order to instill 
 confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
@@
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
-the presence of a systematic in $\textbf{x}_{1}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
+the presence of a systematic in $\textbf{x}_{1}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
 measurements should remain consistent despite the jackknife taken.}

### 2018-01-11 PAPER.tex
made edits from josh until 3.1.4

@@
 range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
-MHz ($20$ channels), identical to the analysis in A15. We note that, besides using only one baseline type instead of the three in 
-A15, the PAPER-64 dataset that we use in this case study differs from that in A15 mainly by the applied fringe-rate filter. In A15, the 
+MHz ($20$ channels), identical to the analysis in A15. We note that, besides using only one baseline type instead of the three as in 
+A15, the PAPER-64 dataset that we use in this case study differs from that in A15 only in the analysis.
+The most significant changes occur in the power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
+In A15, the
 applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
@@
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
-estimate of signal loss (by a factor of $\sim$$10$), likely due to the use of the fringe-rate filter as a simulator.
+estimate of signal loss, %(by a factor of $\sim$$10$), 
+likely due to the use of the fringe-rate filter as a simulator.
 However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text).}
@@
 \label{eq:Pin}
-P_{\rm in,\alpha} \equiv M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} \equiv M^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha}-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
-&=& M_{\alpha}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&=& M^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x},
@@
 
-In short, we can summarize a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning.
-
-In a limit with no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
+In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the next section).
+
+In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
 \begin{equation}
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &=& M_{\alpha}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
-M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &=& M^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&=& M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&-& M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&+& M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + M^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
+&-& M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 \label{eq:pout_expand}
-P_{\rm out, \alpha} &\approx&  M_{\alpha}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
- 2M_{\alpha}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
+P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
+ 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
 \end{eqnarray}
@@
 \begin{eqnarray}
-P_{\rm in,\alpha} &=&  M_{\alpha}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  M_{\alpha}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
+P_{\rm in,\alpha} &=&  M^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=&  M^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
 &&\phantom{=====} 
--  M_{\alpha}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x} 
+-  M^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x} 
 \end{eqnarray}
@@
 As a final complication to our procedure, we note that there will be some intrinsic scatter in our likelihood due to our having only a finite number of simulations.
-This is shown by the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in Figure \ref{fig:sigloss_transfercurve}.
 To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
+This intrinsic scatter is shown as the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in the plot.
 The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
@@
 loss estimation in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
-power spectrum, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
+power spectrum $2\sigma$ upper limit, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
 gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
@@
 We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR.
+weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR signal.
 

### 2018-01-11 PAPER.tex
Made edits from josh until 3.2

@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive (black) and negative (gray) points, 
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive points in black and negative points in gray, 
 with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the unweighted power 
@@
 only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not 
-significant.
+large.
 
@@
 In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
-which denote power spectrum values, post-signal loss estimation, for two other regularization schemes. We multiply an identity 
+which denote power spectrum values, post-signal loss estimation, for two other regularization schemes (these are single-valued and not a function of the number of eigenmodes down-weighted).
+We multiply an identity
 matrix element-wise to $\widehat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
@@
 horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
-when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} in order to avoid suppressing the 
+when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
 $21$ cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
@@
 calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
-down-weight. Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from 
+down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.
+Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from
 data that is similar but not exactly the same as the data that is being down-weighted.

### 2018-01-11 PAPER.tex
finished josh edits

@@
 plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
-weighted case (red), and added-identity case (cyan). All three regularizations shown (black, red, cyan) perform similarly (when 
+weighted case (red), and added-identity case (cyan); all are after signal loss estimation. All three regularizations shown (black, red, cyan) perform similarly (when 
 $\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
@@
 \label{eq:sense}
-p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lsts}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
+p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lst}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
 \end{equation}
@@
 \begin{itemize}
-\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky) to cosmological coordinates (co-moving 
+\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
 distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
@@
 This is lower than the $T_{sys}$ of $500$ K used in A15 because of several small miscalculation errors that were 
-identified\footnote{such as missing a square root in going from a variance to a standard deviation}.
+identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
 estimates after squaring visibility measurements. In A15, a factor of $2$ was mistakenly used.
-\item $N_{lsts}$: The number of LST hours that go into a power spectrum estimation. The sensitivity scales as the square root 
-because we integrate incoherently over time. For PAPER-64, $N_{lsts} = 8$ hours.
+\item $N_{lst}$: The number of LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
+because we integrate incoherently over time. For PAPER-64, $N_{lst} = 8$.
 \item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
@@
 use three separation types.
-\item $t_{int}$: The integration time of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
+\item $t_{int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
 fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
@@
 the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
-the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) before cross-multiplying data. Our revised estimate for the parameter is:
+the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 \sqrt{3}$ for three baseline types is needed to match A15 exactly). Major factors that contribute to the discrepancy are $
-\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as described in Section \ref{sec:PSSense}, which when combined decreases our 
+\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
 sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
@@
 To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
-random noise assuming a constant $T_{sys}$ (neglecting sky variation) but accounting for the true $N_{days}$ as determined 
+random noise assuming a constant $T_{rcvr}$ (translated into $T_{sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{days}$ as determined 
 by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{sys}$ into a variance statistic 
@@
 
-We briefly discuss one way in which we mitigate foreground leakage in a power spectrum estimate, and two in which we 
+We briefly discuss one way we mitigate foreground leakage in a power spectrum estimate, and two ways we 
 suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
@@
 \noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
-the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices:
+the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{F}$ is Hermitian):
 
@@
 example, in order to prevent the squaring of the same thermal noise.
+We recognize that this method results in a hit to our sensitivity.
+Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the A15 analysis (which uses the same groupings), not produce the most sensitive limits of PAPER-64.
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/null.png}
+\begin{figure*}
+	\centering
+	\includegraphics[width=1\textwidth]{plots/null.png}
 	\caption{Results for three null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
 $2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
-even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test. 
-We find that the biases in our power spectrum are likely caused by variation of foregrounds in LST, and are not attributable to 
-particular baselines or days of data.}
+even and odd days; blue), along baselines (green), and along LST (magenta).
+We expect the sky signal to disappear for a `passing' null test (for all error bars to be contained to within the gray shaded region).
+We find that none of the null tests performed pass, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
 	\label{fig:null}
-\end{figure}
-
-Investigating Figure \ref{fig:null}, we find that both the baselines and even/odd null tests are consistent with noise. We note that 
-the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to 
-cross-multiplication (when forming baseline groups).
-
-The null test in LST (magenta) is much more illuminating. The fact that there are many power spectrum points outside the 
-estimated error region signifies that the bias we see is likely from foregrounds that vary in LST. In other words, $t_{1}$ and 
+\end{figure*}
+
+Investigating Figure \ref{fig:null}, we find that none of the null tests are fully consistent with noise; we would expect the null tests' error bars to be contained within the gray shaded region (theoretical error) for a `passable' test.
+We note, however, that the error bars for the baselines test (green) and even/odd test (blue) are smaller than those of the LST test (magenta).
+
+%We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
+estimated error region is LST-dependent, and therefore likely to be residual foregrounds. In other words, $t_{1}$ and 
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-The errors for this null test are also large, also reflective of residual foregrounds.
+While residual foregrounds are the primary cause for power spectrum results above the theoretical noise (as in Figure \ref{fig:ps1_data}), other unexplained variations exist which are present in all the null tests.
+These variations could be attributable to...
+\cc{fill in}
 
@@
 the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
-This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the 
+This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the main source of
 bias we see comes from foregrounds in regions where we expect leakage.
@@
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim7$ mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
+factor of $\sim7$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
 note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
@@
 
-The $21$ cm future is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
+The future of $21$ cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
 foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
@@
 SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
-We graciously thank SKA-SA for site infrastructure and observing support.
+JSD acknowledges NSF AAPF
+award 1701536. We graciously thank SKA-SA for site infrastructure and observing support.
 \label{sec:Ack}
@@
 where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
-One way to interpret this test for the two distributions is to compute the probability that the two distributions are not\footnote{i.e.
-the null test} the same.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e.
+the null test) the same.
 

### 2018-01-11 PAPER.tex
removed text about negative P_ins

@@
 
-In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
-We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs.
+In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
+We also run $25$ total EoR injection levels, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
 $P_{\rm out}$ grid.

### 2018-01-12 PAPER.tex
removed titlesec package which didn't show title/authors/abstract
2-panel sigloss plot is now incorporated, both the figure and in the text description

@@
 \usepackage{comment}
-\usepackage{titlesec}
+%\usepackage{titlesec}
 \citestyle{aa}
@@
 covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
-estimation, are shown in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
+estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
 becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
@@
 is beneficial compared to not weighting (blue dashed line).
-In other words, we would like a weighting scheme that down-weights eigenmodes that describe foreground modes, but not EoR modes.
+In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is not 
-large.
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is small.
+
+We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss.
+We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
+The grey and black lines represent power spectrum limits pre and post signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
+When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to full inverse covariance weighting.
+From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss.
+We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the unweighted case.
 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop.png}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Values 
+	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
+	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
 are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes (i.e. unweighted) to $21$ modes (i.e. full inverse 
-covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Also 
-plotted for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue), inverse variance 
-weighted case (red), and added-identity case (cyan); all are after signal loss estimation. All three regularizations shown (black, red, cyan) perform similarly (when 
-$\sim3$$-4$ modes are down-weighted for the black curve). Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as solid green.}
+are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
+covariance weighting).
+Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting.
+Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
+This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e.
+full inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
+Also
+plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue) and inverse variance 
+weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
+as solid green.
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
 	\label{fig:sigloss_modeloop}
@@
 
-In addition to our thermal noise prediction (green), two additional horizontal lines are shown in Figure \ref{fig:sigloss_modeloop} 
-which denote power spectrum values, post-signal loss estimation, for two other regularization schemes (these are single-valued and not a function of the number of eigenmodes down-weighted).
-We multiply an identity
-matrix element-wise to $\widehat{\textbf{C}}$ (i.e. inverse variance weighting, shown in red), and also add an arbitrarily chosen level 
-of $\textbf{I}$ to $\widehat{\textbf{C}}$ (cyan). We see that all three regularization schemes (black, red, cyan) perform similarly at 
-their best (i.e. when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black curve).
-
-For the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} = \widehat{\textbf{C}} \circ \textbf{I}$, or 
-inverse variance weighting, which we will denote as $\widehat{\textbf{C}}_{eff}$. We choose this weighting scheme due to its 
-simplicity in practice and because its effectiveness is comparable to other weighting schemes that produce minimal signal loss.
-
-Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type) is shown in Figure 
+In addition to our thermal noise prediction (green) and unweighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
+in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
+matrix element-wise to $\widehat{\textbf{C}}$).
+This result is single-valued and not a function of the x-axes.
+We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at
+their best (i.e.
+when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve).
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.04Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
+We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e.
+it doesn't throw away some information as in the other cases) but re-weights them in a way that produces minimal loss.
+
+Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
 \ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
-	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$ (inverse variance weighting). Black and gray points correspond to positive and 
+	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
 negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
@@
 $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
-contamination of foreground bias.
-For this paper, we compute $\textbf{M}$ as described above only for the inverse variance weighted PAPER-64 result (our revised result for one baseline type) shown in Figure \ref{fig:ps1_data}.
-For all other power spectrum estimates in this paper, we use $\textbf{M}=\textbf{I}$ for simplicity.
+contamination of foreground bias. This tailored window function was used in the A15 analysis, however for this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
 

### 2018-01-12 PAPER.tex
Added text to describe the plot showing eigenvector convergence

--- 2018-01-11 PAPER.tex
@@
 
-\cc{Note to Adrian - somewhere in the next paragraph would be good to ref Fig17}
 The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
@@
 the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.
-
-To quantify the convergence of `weak' and `strong' eigenmodes present in a sloped eigenspectrum, we form a mock covariance matrix with diagonal values that span $4$ orders of magnitude.
-We then draw random data realizations from this covariance and compute a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$:
-\begin{equation}
-\label{eq:converge_eig}
-\varepsilon (\widehat{\textbf{v}}) \equiv \frac{1}{N_{f}}\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i},
-\end{equation}
-where $N_{f}$ is the number of frequencies ($20$) in the mock data. We plot this statistic against the number of realizations in Figure \ref{fig:toy_sigloss17}, which shows that...
 
@@
 \citep{pope_szapudi2008,joachimi_2017}.
+
+Just as important as the eigenvalues are the eigenvectors of our empirical covariances.
+In general, different eigenvectors converge to their true forms at different rates.
+This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix whose true form is a diagonal matrix with eigenvalues spanning four orders of magnitude.
+We use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$, defined as:
+\begin{equation}
+\label{eq:converge_eig}
+\varepsilon (\widehat{\textbf{v}}) \equiv \sqrt{\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i}^2},
+\end{equation}
+where $N_{f}$ is the number of frequencies ($20$) in the mock data.
+The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \# 1" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \# 2" for the second largest eigenvalue, and so on.
+One sees that the stronger eigenmodes converge to their true eigenvectors more quickly.
+With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
+As we shall see in Section \acl{insert}, this minimizes signal loss.
+In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
+\acl{Think about whether we need to do the Fourier space version as well.}
 

### 2018-01-12 PAPER.tex
added in new sigloss_terms plot and text to go along with it

--- 2018-01-12 PAPER.tex
@@
 In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the next section).
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
 
@@
 \label{sec:Illustration}
-To explore how our expression for $P_{out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
+To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
 
@@
 We see that $P_{\rm out}$ is comprised of multiple terms.
-For illustrative purposes in this subsection only, we build intuition for signal loss in $P_{out}$ by considering a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $P_{out}$ becomes:
+To build intuition into each of these terms, they are plotted individually in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$, left) and unweighted ($\textbf{R}_{r} = \textbf{I}$, right).
+We leave the details of the simulation to Section \ref{sec:Practice}, but for now highlight that each term in Equation \eqref{eq:crossterm} corresponds to a different color in the plot.
+Specifically, the first term in Equation \eqref{eq:crossterm} is plotted as blue, the second as green, the third and fourth (which are the same) as red, and the last as gray.
+The solid black curve denotes $P_{\rm out}$, which is comprised of all the other terms.
+
+A brief description of Figure \ref{fig:sigloss_terms} is as follows.
+The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed.
+The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$).
+It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$.
+The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$.
+This is the exact term that was compared to $P_{\rm in}$ in the A15 signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
+It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
+We see that the cross-terms can produce a large, negative signal which serves to reduce $P_{\rm out}$ and drive the bulk of our loss.
+In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $P_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
+
+We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
+For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
+It is in this limit where we expect signal loss to be greatest, and $P_{\rm out}$ becomes:
 
@@
 The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-It is this quantity that was used in A15 to calculate signal loss.
+Again, it is this quantity that was used in A15 to calculate signal loss.
 However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
+	\caption{Illustration of the components of the signal loss transfer function, $P_{\rm out}$, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and unweighted case (right).
+The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
+We show the contributions of each signal loss term (blue, red, green, gray), which when combined produce the black $P_{\rm out}$ curve.
+Most notably, the green curves denotes the signal loss analysis used in A15, and the red curves showcase the importance of the cross-terms in Equation \eqref{eq:crossterm} in computing signal loss.
+As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse variance weighted case).
+Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the unweighted case.}
+	\label{fig:sigloss_terms}
+\end{figure*}
+
 When $\textbf{R}_{r}$
 is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the second term of Equation \eqref{eq:pout_expand} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
-$\widehat{\textbf{C}_{r}}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
+$\widehat{\textbf{C}}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
 This negative cross-term power arises from a coupling between the inverse of 
@@
 for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
-not exhibit loss.}
+not exhibit loss.
+The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:pout_expand}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
 	\label{fig:sigloss_transfercurve}
@@
 
-One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$).
+%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$).
 \cc{This is a log-plotting effect and is under-construction!}.
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_reg.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_reg.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.png}
 	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_reg.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_reg.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.png}
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
@@
 \begin{itemize}
-\item Original Data (black): This is identical to the power spectrum in Figure \ref{fig:ps1_data} and represents the best revised 
-PAPER-64 power spectrum (one baseline type only) with weighting matrix $\widehat{\textbf{C}}_{eff}$. There are clear detections at 
+\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
+There are clear detections at
 low $k$'s.
@@
 	\includegraphics[width=1\textwidth]{plots/null.png}
-	\caption{Results for three null tests compared to the PAPER-64 revised power spectrum (black) and analytically estimated 
+	\caption{Results for three null tests compared to the PAPER-64 unweighted revised power spectrum (black) and analytically estimated 
 $2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 

### 2018-01-12 PAPER.tex
adrian's text is in about fig8, changed fig ordering to be consistent

@@
 where $N_{f}$ is the number of frequencies ($20$) in the mock data.
-The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \# 1" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \# 2" for the second largest eigenvalue, and so on.
+The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
 One sees that the stronger eigenmodes converge to their true eigenvectors more quickly.
@@
 In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-\acl{Think about whether we need to do the Fourier space version as well.}
+%\acl{Think about whether we need to do the Fourier space version as well.}
 
@@
 	\label{fig:toy_sigloss15}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.png}
-	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different number of mock data realizations.
-The colors span from the 0th eigenmode (the first one) to the 19th eigenmode (the last one), where they are ordered by eigenvalue in descending order.
-This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes.}
-	\label{fig:toy_sigloss17}
 \end{figure}
@@
 	\label{fig:toy_sigloss16}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.png}
+	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different number of mock data realizations.
+The colors span from the 0th eigenmode (the first one) to the 19th eigenmode (the last one), where they are ordered by eigenvalue in descending order.
+This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes.}
+	\label{fig:toy_sigloss17}
 \end{figure}

### 2018-01-16 PAPER.tex
minor sentence change
Slight tweaks to language re: sensitivity

@@
 With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
-As we shall see in Section \acl{insert}, this minimizes signal loss.
+As we will see in the next section, using only the strongest eigenmodes, which are less coupled to data realizations, minimizes signal loss.
 In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
@@
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after squaring visibility measurements. In A15, a factor of $2$ was mistakenly used.
+estimates after cross-multiplying independent `even' and `odd' visibility measurements (which is done principally to avoid a noise bias). In A15, a factor of $2$ was mistakenly used.
 \item $N_{lst}$: The number of LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 

### 2018-01-17 PAPER.tex
compiled with updated matt plots

--- 2018-01-12 PAPER.tex
@@
 The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
-Overall the limits show good agreement, with k modes differing by factors of 2 to 4.
+Overall the limits show good agreement, with k modes differing by factors of $\sim$$3$.
 

### 2018-01-17 PAPER.tex
JCP comments (but few edits)

--- 2018-01-16 PAPER.tex
@@
 \newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }
+\newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors
 
@@
 diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
-At low injection, $P_{\rm out}$ converges to the data level.}
+At low injection, $P_{\rm out}$ converges to the data level.
+\jp{This figure needs updating (as does this caption).
+The text seems to have settled on $P_{\rm out}$ referring to $\widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$, whereas this signal loss methodology uses only $\widehat{\textbf{p}}_{r}$.
+So the y-axis needs to change.}
+}
 \label{fig:Pr_vs_Pin}

### 2018-01-19 PAPER.tex
Updated text to reflect better justification of linear correction between lossy pspec and true pspec

--- 2018-01-16 PAPER.tex
@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
+In other words, suppose that we have
+\begin{equation}
+\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
+\end{equation}
+in place of Equation \eqref{eq:LinearPspecSum}.
+Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
+Further parameterize $\mathbf{ f}_\parallel \equiv \rho \mathbf{e}$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
+This then gives
+\begin{equation}
+\label{eq:fperpfpara}
+\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
+\end{equation}
+Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
 \dcj{Wait what?
@@
 Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in the main text.}
 
 The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
+This is manifest in Equation \eqref{eq:fperpfpara}, where the randomness of $\rho$ means that there is an inherent spread in the signal loss correction.
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.

### 2018-01-19 PAPER.tex
JCP edits/comments

@@
 Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
+\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
 Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
@@
 Most notably, the green curves denotes the signal loss analysis used in A15, and the red curves showcase the importance of the cross-terms in Equation \eqref{eq:crossterm} in computing signal loss.
-As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse variance weighted case).
+As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
 Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the unweighted case.}

### 2018-01-19 PAPER.tex
made some adrian edits until section 3.1.3

--- 2018-01-19 PAPER.tex
@@
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today \citep[for a review, see][]{furlanetto_et_al2006}.
+web of galaxies we observe today (for a review, see \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
 
@@
 with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
-the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics that are essential to investigate 
+the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
 for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
@@
 We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
-It has length $N_{t} \times N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{t}, N_{f}$), where
+It has length $N_{t} \times N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
@@
 \end{equation}
-Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier-transforms them into 
+Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them into 
 power spectrum space, while also converting from Jy to 
 Kelvin and taking into account cosmological scalings.
-It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\delta\textbf{C}}{\delta p_{\alpha}}$, or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
-Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b})). $\textbf{R}$ is a weighting matrix --- as 
+It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
+Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
 an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
@@
 
-In the next three sections, we investigate the effects of weighting matrices on signal loss by experimenting with different 
-matrices $\textbf{R}$ and examine their impact on the resulting power spectra estimate $\widehat{\textbf{p}}$. Our goal in 
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectra estimate $\widehat{\textbf{p}}$.
+Our goal in
 experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
@@
 \noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix is therefore $
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for inverse covariance weighting is then $
 \textbf{R} = \widehat{\textbf{C}}^{-1}$.
@@
 multiplicative bias (per $k$) to estimates of the signal.
-For a mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
+For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
 Here we will describe the origin of this signal loss
@@
 covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
-$\widehat{\textbf{C}}_{FG}$ but effectively absent from $\widehat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
+$\widehat{\textbf{C}}_{FG}$.% but effectively absent from $\widehat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
 
@@
 For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes.
-In other words, mis-estimating $\textbf{C}$ affects EoR-dominated eigenmodes more than FG-dominated modes, and it is primarily the error associated in down-weighting these `weak' modes that leads to signal loss.
+In other words, mis-estimating $\textbf{C}$ affects EoR-dominated eigenmodes more than FG-dominated modes, and it is primarily the coupling between these mis-estimated modes to the data that leads to signal loss.
 
@@
 Hence, we are not using the relative weighting information from all the weaker eigenmodes which have comparatively larger errors.
-Altering $\widehat{\textbf{C}}$ as such is one example of a regularization method, in which we are
+Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are
 changing $\widehat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
@@
 demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
-them without signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
+them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
 \ref{sec:otherweight}.
@@
 
-We have shown how signal loss can arise due to inaccurately characterizing weak eigenmodes (EoR dominated modes) with a 
-data-estimated covariance. We will next show how this effect is exaggerated by reducing the total number of independent 
+We have shown how signal loss can arise due to the coupling of weak eigenmodes (EoR dominated modes) to the data.
+We will next show how this effect is exaggerated by reducing the total number of independent
 samples in a dataset.
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). 
-Rather than a traditional box-car average, a time domain filter can be designed to up-weight temporal modes consistent with 
+Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with 
 the sidereal motion on the sky, while down-weighting modes which are noise-like.
@@
 fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
-true covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
+true fringe-rate filtered case covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 \begin{equation}
@@
 In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
-With more independent time samples in the data, one converges to the true covariance more quickly.
+With more independent time samples in the data, one converges to the true fringe-rate filtered covariance more quickly.
 
@@
 system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
-two don't always agree due to a number of factors, including time, frequency, and antenna-dependent noise and non-uniform 
+two don't always agree due to a number of factors, including possible non-Gaussianities in the noise properties of our instruments and non-uniform 
 weightings.
 
-For PAPER's analysis, we choose to compute error bars on our measurements that have been derived from its inherent 
-variance. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
+For PAPER's analysis, we choose to compute error bars that have been derived from the inherent 
+variance of our measurements. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
 bootstrapping and then illustrate one of its pitfalls through a toy model.
@@
 Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
-between them. Hence, through the process of resampling and averaging along different axes, we can estimate error bars for 
+between them. Through the process of resampling and averaging along different axes, we can estimate error bars for 
 our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
 
-Suppose we have $N$ different measurements targeting the same quantity ($N$ power spectrum measurements). 
+Suppose we have $N$ different measurements targeting the same quantity ($N$ power spectrum measurements made along different axes, such as baselines or times). 
 Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
 of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
-from the original set of measurements with replacement (i.e. every $N$th slot is filled randomly for each bootstrap). Next we take 
+from the original set of measurements with replacement (i.e. every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
 the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
@@
 values, that comprise a bootstrap. In the toy models presented in this section, $N_{boot}$ is typically large, and the standard 
-deviation across bootstraps (the error we are computing) converges for large $N_{boot}$. It is the value of $N$ that we must be 
-careful in setting, as described in the rest of this section.
+deviation across bootstraps (the error we are computing) converges for large $N_{boot}$.
+Typically $N$ is a straightforward value to set that just depends on the experiment.
+However, we will illustrate one case in which it is not simply the number of samples along the axis that is being re-sampled.
+More specifically, we will see that $N$ depends on sample independence and may not always be straightforward to approximate.
 
@@
 number of independent samples along the axis that is being re-sampled is well-determined.
+In Section \ref{sec:Boot}, we explain how our bootstrapping procedure has changed in PAPER's analysis in light of this issue.
 
@@
 
-Foreground bias is perhaps one of the main factors limiting $21$ cm results. Foreground signals lie $\sim4$-$5$ orders of 
+In Section \ref{sec:SiglossOverview}, we discussed signal loss as a form of multiplicative bias to estimates of the signal.
+Foregrounds are another type of bias, but an additive one instead of multiplicative.
+Foreground bias is perhaps one of the main factors limiting $21$ cm results, as foreground signals lie $\sim4$-$5$ orders of
 magnitude above the cosmological signal.
@@
 In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
-the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
+the delay associated with the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
 convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
@@
 There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from 
-spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the covariance of a particular 
-$k$ value with other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
+spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the leakage from a particular 
+$k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
 window function to have a minimum response to low $k$ values. The window function used in A15 is constructed in such a way, 
@@
 
-Determining the source of detections at higher $k$'s is more difficult.
+Determining the source of positive non-EoR detections at higher $k$'s is more difficult.
 In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (A15; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
@@
 sources. Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters. However, there 
-remains a possibility that power spectrum detections are caused by residual, low-level crosstalk which survived any 
+remains a possibility that power spectrum detections that aren't the cosmological signal are caused by residual, low-level crosstalk which survived any 
 suppression techniques.
@@
 present in, for example, the first half of the LST range used for analysis, but not the second half. Mathematically, if  $\textbf{n}$ 
-is noise, $\textbf{e}$ is the EoR signal, and $\textbf{fg}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
 
@@
 \label{eq:bias1}
-\textbf{x}_{a} = \textbf{n}_{a} + \textbf{e} + \textbf{fg}
+\textbf{x}_{a} = \textbf{n}_{a} + \textbf{e} + \textbf{f}
 \end{equation}
@@
 \label{eq:bias2}
-\textbf{x}_{b} = \textbf{n}_{b} + \textbf{e} + \textbf{fg}.
+\textbf{x}_{b} = \textbf{n}_{b} + \textbf{e} + \textbf{f}.
 \end{equation}
@@
 \begin{eqnarray}
-\textbf{x}_{1} &=& \textbf{n} + \textbf{e} + \textbf{fg} \\
+\textbf{x}_{1} &=& \textbf{n} + \textbf{e} + \textbf{f} \\
 \textbf{x}_{2} &=& \textbf{n} + \textbf{e} 
@@
 \textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$. This is equivalent to splitting up a full dataset along 
-an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both. We cross-
-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve). The second estimate, 
-shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{fg}$ in Equations \ref{eq:bias1} 
+an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
+We cross-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve).
+The second estimate,
+shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{f}$ in Equations \ref{eq:bias1} 
 and \ref{eq:bias2}). Finally, we also show the noise power spectrum (green).
@@
 likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text).}
-
-Suppose that $\textbf{e}$ is the injected EoR (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text in Section \ref{sec:Illustration}).}
+
+Suppose that $\textbf{e}$ is a mock injected EoR signal (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
 $ to be the data plus the EoR signal:
@@
 \end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices $M$, even though for our numerical results we use a full non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
+where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices $M$, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
 $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal,
@@
 where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
-It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the result is an approximation.
+It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation.
 
 Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
-Although such an estimate leaves an additive bias from foregrounds that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
+Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
 The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
@@
 
-In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss, and why this signal loss occurs in the first place.
+In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
 Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
@@
 ($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in A15 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
-expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
+expressions for $P_{\rm in}$ and $P_{\rm out}$ become
 
@@
 &&\phantom{=====} 
--  M^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x} 
+-  M^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
 \end{eqnarray}
@@
 The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-In other words, suppose that we have
-\begin{equation}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
-\end{equation}
-in place of Equation \eqref{eq:LinearPspecSum}.
-Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
-Further parameterize $\mathbf{ f}_\parallel \equiv \rho \mathbf{e}$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-This then gives
-\begin{equation}
-\label{eq:fperpfpara}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
-\end{equation}
-Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
 \dcj{Wait what?
@@
 Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in the main text.}
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}
 
 The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
-This is manifest in Equation \eqref{eq:fperpfpara}, where the randomness of $\rho$ means that there is an inherent spread in the signal loss correction.
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.

### 2018-01-20 PAPER.tex
made adrian edits throughout paper except appendix and covariance language

@@
 specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
-Minimizing foreground leakage in this way however, comes with the trade-off of compromising power spectrum sensitivity, since 
-narrow window functions increases errors for each $k$-mode (\citealt{liu_et_al2014b}).
 
@@
 
-In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
+In our code, we simulate $20$ realizations of $P_{in}$, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
 We also run $25$ total EoR injection levels, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
@@
 As a final complication to our procedure, we note that there will be some intrinsic scatter in our likelihood due to our having only a finite number of simulations.
+Ideally, running many simulations would lead to convergence in our likelihood; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
 To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
@@
 To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
-loss estimation in Figure \ref{fig:ps2_data}, using inverse covariance weighting. The blue dashed line represents the unweighted 
+loss estimation in Figure \ref{fig:ps2_data}, using empirically estimated inverse covariance weighting. The blue dashed line represents the unweighted 
 power spectrum $2\sigma$ upper limit, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
@@
 is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
-Post-estimation, the power spectrum errors blow up to be higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
+Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 foregrounds and systematics in our data without generating large amounts of signal loss. We have found that the balance 
-between the two is a delicate one and requires a careful understanding and altering of covariance matrices.
+between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
 
@@
 
+In Section \ref{sec:Sigloss}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated, and ways it can be minimized.
+We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
+In the remainder of this paper, we will transition to other new aspects of our analysis, framed within the context of error estimation and (non-EoR) bias in PAPER-64.
+
 % SECTION 3 ERROR ESTIMATION ---------------------------------------------------------------------------------
@@
 found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations. The analytic 
-calculation is only an approximation, however the differences were large enough (factors of $10$ in some cases) to warrant a 
+calculation is only an approximation; however, the differences were large enough (factors of $10$ in some cases) to warrant a 
 careful investigation. The analytic calculation attempts to combine a large number of pieces of information in an approximate 
@@
 \label{eq:sense}
-p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lst}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}
-\end{equation}
+p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lst}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}.
+\end{equation}
+We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in A15.
 
@@
 \item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
-distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3} Mpc^{3} str^{-1} GHz^{-1}$.
+distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
 \item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
@@
 \begin{equation}
-N_{bls} = \frac{N_{bls}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
+N_{bls} = \frac{N_{bls\_total}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
 \end{equation}
 \noindent where, for the A15 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{bls}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
+entering the group ($N_{bls\_total}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
 N_{gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead 
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-one major changes in the way we estimate errors since A15, using the lesson we've learned about bootstrapping independent samples.
+one major changes in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
 
@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic.
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic prediction for noise.
 
@@
 
-Tailoring window functions is one way to suppress foreground biases. As alluded to in Section \ref{sec:SiglossOverview}, we 
+Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and A15).
+As alluded to in Section \ref{sec:SiglossOverview}, we
 have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
@@
 low $k$'s.
-\item Even/Odd (blue): We split our dataset into even (e) and odd (o) days, where $\textbf{x}_{1} = e + o$ and $\textbf{x}_{2} = 
-e - o$. We form datasets in this way to ensure that we use the full sensitivity of our data. When cross-multiplied, we obtain:
-\begin{equation}
-\textbf{x}_{1}\textbf{x}_{2}^{\dagger} = ee^{\dagger} - eo^{\dagger} + oe^{\dagger} - oo^{\dagger}
+\item Even/Odd (blue): We split our dataset into even (\textbf{e}) and odd (\textbf{o}) days. We then form the following two datasets: $\textbf{x}_{1} = \textbf{e} + \textbf{o}$ and $\textbf{x}_{2} = 
+\textbf{e} - \textbf{o}$. We form datasets in this way to ensure that we use the full sensitivity of our data. When cross-multiplied, we obtain:
+\begin{equation}
+\textbf{x}_{1}\textbf{x}_{2}^{\dagger} = \textbf{ee}^{\dagger} - \textbf{eo}^{\dagger} + \textbf{oe}^{\dagger} - \textbf{oo}^{\dagger}
 \end{equation}
@@
 \item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the 
-analysis. Again, we form $\textbf{x}_{1} = b_{1} + b_{2}$ and $\textbf{x}_{2} = b_{1} - b_{2}$, where $b_{1}$ is the first baseline 
-group and $b_{2}$ is the second baseline group.
-\item LST (magenta): We split our dataset into two halves based on LST, namely $t_{1}$ (LSTs 0.5-4.6 hours) and $t_{2}$ (LSTs 
-4.6-8.6 hours). We form our two datasets as $\textbf{x}_{1} = t_{1} + t_{2}$ and $\textbf{x}_{2} = t_{1} - t_{2}$.
+analysis. Again, we form $\textbf{x}_{1} = \textbf{b}_{1} + \textbf{b}_{2}$ and $\textbf{x}_{2} = \textbf{b}_{1} - \textbf{b}_{2}$, where $\textbf{b}_{1}$ is the first baseline 
+group and $\textbf{b}_{2}$ is the second baseline group.
+\item LST (magenta): We split our dataset into two halves based on LST, namely $\textbf{t}_{1}$ (LSTs 0.5-4.6 hours) and $\textbf{t}_{2}$ (LSTs 
+4.6-8.6 hours). We form our two datasets as $\textbf{x}_{1} = \textbf{t}_{1} + \textbf{t}_{2}$ and $\textbf{x}_{2} = \textbf{t}_{1} -\textbf{t}_{2}$.
 \end{itemize}
@@
 This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
-estimated error region is LST-dependent, and therefore likely to be residual foregrounds. In other words, $t_{1}$ and 
+estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
+In other words, the fact that many magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
@@
 the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
-This type of detailed analysis will be critical at EoR sensitivities, however, for our current analysis we are not surprised that the main source of
+This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
 bias we see comes from foregrounds in regions where we expect leakage.

### 2018-01-21 PAPER.tex
Lessons learned papers
Context of PAPER style analysis. For Miguel types.

@@
 
+This paper adds to the growing foundations of lessons which have been documented in  \cite{Patil2016,Jacobs2016} and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
+
 This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
@@
 
-There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
+There are many choices a $21$ cm data analyst must consider, though the space is significantly constrained by 
+the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
+only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
+down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
+the sky. However, even within this problem sub-space, questions remain.
+
+ How can time-ordered measurements be combined? How can the 
 variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 

### 2018-01-21 PAPER.tex
Tweaked FRF description for wider audience.

@@
 \item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
-(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
-independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
+(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
+independent samples. However, by adjusting the shape of the filter to match the rate of sidereal motion it can also affect the presence 
 of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.

### 2018-01-21 PAPER.tex
Limit the scope of Appendix A.

@@
 \end{equation}
-where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
-It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation.
+where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
+power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
+\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
+\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
+which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
+small sample size limited to first order perturbations and thus neglects cross correlation between $x$ and $e$.  
+In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
+terms to be remain significant.
 
@@
 \end{equation}
-Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading order in $\eta$. The result is
+Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading 
+order in $\eta$. This approximates the limiting case where the covariance $\Chat$ is close to the ideal and the 
+lossy covariance is a small perturbation.  The result is
 \begin{equation}
@@
 This means that it can be decomposed into the sum of the foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
-This toy example, while not definitive, serves to motivate the form of Equation \eqref{eq:LinearPspecSum}.
+This toy example, while not showing the emergence of cross-terms provides a rudimentary motivation for the form of Equation \eqref{eq:LinearPspecSum}.
 
@@
 One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
-The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the neglection of cross-terms in the power spectrum and indeed does not behave as expected at small injected values.
-However it is possible to make a simpler interpretation which requires less motivation.
+The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the assumption that the number of samples is large enough to treat sample variance as a first order purturbation on the ideal covariance matrix instead of the dominant effect we know it is.
+However it is possible to ask a slightly different question and with less math still get roughly the same answer.
 

### 2018-01-21 PAPER.tex
Update the debate

@@
 \jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
+\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
+covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
+correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
+I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
+then explaining in the next section exactly how cross terms were what messed us up in the first go round.}
+
 Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
@@
 \end{equation}
-(Note that even this is an approximation.
-In principle there is an infinite series containing all possible powers of $e$ and $f$).
-Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
-Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in the main text.}
+(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
+$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
+couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
+some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
+EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
+the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
+dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
+$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
+\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
 

### 2018-01-21 PAPER.tex
Answer Adrian's _questions_ in Appendix B.

@@
 
-Formally we can express our test as: ``What is the $P_{\rm in}$ such that
-\begin{equation}
-\widehat{\textbf{p}}_{r} > \widehat{\textbf{p}}_{x} \Lambda,
-\end{equation}  
-where $\Lambda$ represents a choice of threshold?'' Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of "data + 
+injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 
+In other words, what is $e$ such that,
+\begin{equation}
+\widehat{\textbf{p}}_{e+x} > \widehat{\textbf{p}}_{x},
+\end{equation}  
+?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
 One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e.
@@
  \begin{equation}
-\Prob(P_{in})  =  1 -  \int_{r=x} \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_r,P_{in}) dr
- \end{equation}
- where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_r,P_{in})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{r}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) x
+ \end{equation}
+ where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
 
@@
 injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
-At low injection levels the variation between $\textbf{x}$ and $\textbf{r}$ is such that the null test is ruled out to within $20$\%.
+At low injection levels the variation between $\textbf{x}$ and $\textbf{(e+x)}$ is such that the null test is ruled out to within $20$\%.
 This is the level expected from two distributions with $\sim$10 effective samples.
-%\dcj{checked with a little python test but needs a cite} 
 As the injected signal approaches the level of the data, the probability of null rejection rises steeply.

### 2018-01-22 PAPER.tex
Slight language tweak to 3.1

@@
 Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set.
-There is, of course, no way of determining an exact signal loss ``correction factor," i.e., we cannot perfectly undo the effects of a lossy estimator.
+The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
 In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 

### 2018-01-22 PAPER.tex
-Some edits to covariance language in Section 2 -Updated Figure B1 y-axis

--- 2018-01-21 PAPER.tex
@@
 
-This paper adds to the growing foundations of lessons which have been documented in  \cite{Patil2016,Jacobs2016} and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
-
 This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
@@
 
-There are many choices a $21$ cm data analyst must consider, though the space is significantly constrained by 
-the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
-only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
-down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
-the sky. However, even within this problem sub-space, questions remain.
-
- How can time-ordered measurements be combined? How can the 
+There are many choices a $21$ cm data analyst must consider. How can time-ordered measurements be combined? How can the 
 variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
@@
 \item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
-(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
-independent samples. However, by adjusting the shape of the filter to match the rate of sidereal motion it can also affect the presence 
+(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter increases the sensitivity of a dataset and reduces the number of 
+independent samples by an amount dependent on the width of the averaging window. However, it can also affect the presence 
 of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
@@
 information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
-weighting is in accurately defining a covariance matrix that best describes the data. We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
+weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two has large impacts on signal loss.
+We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
 \item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
@@
 \noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum. The data analyst has a choice for $
-\textbf{M}$ (subject to the constraint that window functions are sensible) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
+\textbf{M}$ (subject to the constraint that window functions are sensible) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal ($\textbf{M} \propto \textbf{I}$), although we explore other cases for the analysis
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
 
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectra estimate $\widehat{\textbf{p}}$.
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimate $\widehat{\textbf{p}}$.
 Our goal in
@@
 
-To build our intuition into how a particular choice of weighting, namely inverse covariance weighting, can lead to signal loss, we 
-use a toy model. We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
+One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
+This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
+Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
+In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for previous PAPER analyses.
+
+One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
+By definition, inverse covariance weighting does not lead to signal loss.
+Therefore, in an ideal world with perfect foreground,
+instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
+
+In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
+We will now build intuition into how estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
+
+We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
@@
 $k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
-\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes. The three data components are shown in Figure 
+\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
 \ref{fig:toy_sigloss1}.
@@
 
-One choice for the weighting matrix $\textbf{R}$ is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
-Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for the PAPER analysis.
-
-The covariance matrix $\textbf{C}$, which describes covariances between frequency channels, can be estimated in a variety of ways. Given perfect foreground, 
-instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data. However, if 
-our foreground model is flawed, for example, our estimate of $\textbf{C}$ would not be successful at down-weighting them in 
-the data.
-
-Therefore, one attractive way to estimate $\textbf{C}$ is to empirically derive it from the data $\textbf{x}$ itself. For instance, one could time-average such that:
+Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself (this is what was done in the previous PAPER analyses).
+For instance, one could time-average such that:
 
@@
 \noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for inverse covariance weighting is then $
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for estimated inverse covariance weighting is then $
 \textbf{R} = \widehat{\textbf{C}}^{-1}$.
 
-First, we compute the power spectrum of $\textbf{x}$ using OQE formalism and a weighting matrix of $\widehat{\textbf{C}}^{-1}$. 
+First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using OQE formalism and $\textbf{R} = \widehat{\textbf{C}}^{-1}$. 
 The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}. Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $
@@
 
-As shown, our inverse covariance-weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
-recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low. This is evidence of signal loss. In 
-order to understand the behavior of this result, we can closely study our covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-%, which is shown in Figure \ref{fig:toy_sigloss12}.
-
-If $\textbf{C}$ is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a 
+As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
+recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
+This is evidence of signal loss.
+In short, if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a
 multiplicative bias (per $k$) to estimates of the signal.
@@
 
+To begin to understand the lossy behavior of this result, we can closely study our covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
 If the covariance is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result.
@@
 
-If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
-representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
-particular data realization, its eigenvalues and eigenvectors may differ from the truth.
+Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
+The strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the first peak in Figure \ref{fig:toy_sigloss2}).
+In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.
+The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{FG}$.
+
+In general, the strongest eigenmodes of $\widehat{\textbf{C}}$ typically describe bright foregrounds --- the most prominent shapes in a dataset.
+For these `strong' modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
+In some sense, we desire signal loss, if by `signal' we mean `foregrounds.' In this case it is okay for the `strong' eigenmodes to be coupled to the data in a way that produces loss.
+For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss2} by the missing foreground peak in the weighted power spectrum estimate (green).
+
+%If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
+%representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
+%particular data realization, its eigenvalues and eigenvectors may differ from the truth.
 Said differently, shapes that may not exist (or exist rarely) in a true covariance may appear stronger in the estimated covariance.
 Hence, they will be down-weighted
-more than they should be.
-
-In general, the strongest modes of $\widehat{\textbf{C}}$ (highest eigenvalues) are expected to be dominated by bright foregrounds 
---- the most prominent shapes in the data. For these `strong' modes, where foregrounds outshine the EoR signal, $
-\widehat{\textbf{C}} \sim \textbf{C}$ and down-weighting these modes is beneficial. This is demonstrated in the toy model by the 
-successful suppression of the foreground mode, where our estimated covariance matrix identifies the sinusoid shape and 
-assigns it the highest eigenvalue (the first peak in Figure \ref{fig:toy_sigloss2}). In Figure \ref{fig:toy_sigloss12} we show the 
-covariances of our toy model datasets along with inverse covariance weighted data. The foreground sinusoid is clearly visible in 
-$\widehat{\textbf{C}}_{FG}$.% but effectively absent from $\widehat{\textbf{C}}^{-1}_{FG}\textbf{x}_{FG}$.
+%more than they should be.
 
@@
 
-The danger of an empirically estimated covariance matrix comes from not being able to describe the `weak' eigenmodes of $
+The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the `weak' eigenmodes of $
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-In such a case, the empirical covariance believes these modes should be down-weighted more than the true covariance would.
+\cc{start editing here later!} In such a case, the empirical covariance believes these modes should be down-weighted more than the true covariance would.
 For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes.
@@
 \end{equation}
-where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
-power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
-\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
-\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
-small sample size limited to first order perturbations and thus neglects cross correlation between $x$ and $e$.  
-In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
-terms to be remain significant.
+where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively.
+It is not \emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix \ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation.
 
@@
 \jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
-\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
-covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
-correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
-I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-then explaining in the next section exactly how cross terms were what messed us up in the first go round.}
-
 Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
@@
 \end{equation}
-(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
-$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
-couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
-some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
-EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
-the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
-dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
+(Note that even this is an approximation.
+In principle there is an infinite series containing all possible powers of $e$ and $f$).
+Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
+Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
+Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in the main text.}
 
@@
 \end{equation}
-Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading 
-order in $\eta$. This approximates the limiting case where the covariance $\Chat$ is close to the ideal and the 
-lossy covariance is a small perturbation.  The result is
+Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading order in $\eta$. The result is
 \begin{equation}
@@
 This means that it can be decomposed into the sum of the foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
-This toy example, while not showing the emergence of cross-terms provides a rudimentary motivation for the form of Equation \eqref{eq:LinearPspecSum}.
+This toy example, while not definitive, serves to motivate the form of Equation \eqref{eq:LinearPspecSum}.
 
@@
 One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
-The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the assumption that the number of samples is large enough to treat sample variance as a first order purturbation on the ideal covariance matrix instead of the dominant effect we know it is.
-However it is possible to ask a slightly different question and with less math still get roughly the same answer.
+The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the neglection of cross-terms in the power spectrum and indeed does not behave as expected at small injected values.
+However it is possible to make a simpler interpretation which requires less motivation.
 
@@
 \includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
-\caption{The distribution of output power spectrum values for a 
+\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
 given injection level P$_{in}$.
-The $P_{\rm out}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
+The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
 It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
@@
 At low injection, $P_{\rm out}$ converges to the data level.
-\jp{This figure needs updating (as does this caption).
-The text seems to have settled on $P_{\rm out}$ referring to $\widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$, whereas this signal loss methodology uses only $\widehat{\textbf{p}}_{r}$.
-So the y-axis needs to change.}
 }

### 2018-01-22 PAPER.tex
covariance language edits throughout section 2

@@
 Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for previous PAPER analyses.
+In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for previous PAPER analyses.
 
@@
 
-To begin to understand the lossy behavior of this result, we can closely study our covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-If the covariance is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result.
+To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
+Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result.
 An eigenspectrum ranks the eigenvalues of a matrix from
@@
 Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-The strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the first peak in Figure \ref{fig:toy_sigloss2}).
+For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the first peak in Figure \ref{fig:toy_sigloss2}).
 In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.
@@
 For these `strong' modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss, if by `signal' we mean `foregrounds.' In this case it is okay for the `strong' eigenmodes to be coupled to the data in a way that produces loss.
+In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for the `strong' eigenmodes to be coupled to the data in a way that produces loss.
 For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss2} by the missing foreground peak in the weighted power spectrum estimate (green).
@@
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-\cc{start editing here later!} In such a case, the empirical covariance believes these modes should be down-weighted more than the true covariance would.
-For these modes, the error that results from not computing $\textbf{C}$ accurately (due to a finite data sample), has a larger impact on the `weak' modes than the `strong' modes.
-In other words, mis-estimating $\textbf{C}$ affects EoR-dominated eigenmodes more than FG-dominated modes, and it is primarily the coupling between these mis-estimated modes to the data that leads to signal loss.
+In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
+In other words, mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
 
@@
 use the true eigenvalue of the first eigenmode, but flatten the rest of the spectrum to have eigenvalues of 1), thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are not using the relative weighting information from all the weaker eigenmodes which have comparatively larger errors.
+Hence, we are changing the weaker part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
+only allowing over-fitting to occur for the first mode).
+
 Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are 
-changing $\widehat{\textbf{C}}$ in a way that flattens its eigenspectrum, making it more similar to that of $\textbf{I}$. The resulting 
+changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. The resulting 
 power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
@@
 In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
-With more independent time samples in the data, one converges to the true fringe-rate filtered covariance more quickly.
+With more independent time samples (i.e.
+more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
 
@@
 In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
+Said differently, a steep covariance eigenspectrum can be especially dangerous because it is the `weak' modes that are both EoR-dominated and converge the slowest and are therefore susceptible to the most loss.
 %\acl{Think about whether we need to do the Fourier space version as well.}
@@
 of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the covariance matrix more heavily than those off-diagonal, thereby flattening out its eigenspectrum. If all modes are given 
-similar weights, we avoid down-weighting EoR modes more than others.
-Although there is negligible signal loss, the small green peak at $k\sim3$ represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} flattens out the eigenspectrum of $\widehat{\textbf{C}}$ a different way - 
-by only using the first three eigenmodes. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
+elements of the covariance matrix more heavily than those off-diagonal.
+Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
+Although there is negligible signal loss using this regularization, the small green peak at $k\sim3$ represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
+
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way - 
+by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
 method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights). Again, flattening the eigenspectrum results in negligible signal loss. However, we do 
+eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of `weak' modes which are coupled to the data results in negligible signal loss. However, we do 
 not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
@@
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds. For this toy model, 
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it's no longer coupled to both the `strong' or `weak' eigenmodes.
+For this toy model,
 our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
@@
 suppressing the foreground.
-But because we flattened the eigenspectrum, we also avoid signal loss.
+But because we de-coupled the whole eigenspectrum from the data, we also avoid signal loss.
 Although this method did not successfully recover EoR for this particular simulation, it is important that we show that there
-are many options for estimating a covariance matrix, and some may be more effective than others based on the spectral nature 
+are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more than others based on the spectral nature 
 of the components in a dataset. 

### 2018-01-22 PAPER.tex
covariance language edits in 3.1

@@
 is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
-Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of not being able to characterize covariances well using the time-averaged fringe-rate filtered data (there is less independent information to use).
+Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
 We elaborate on this point in the next section, as well as investigate alternate
@@
 We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
-eigenspectrum) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
+eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
 that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
@@
 increases with the number of down-weighted modes (black curve).
-Because our data is fringe-rate filtered, we have less information to characterize the covariance matrix and therefore do a worse job estimating it.
-Hence, the more modes we use in down-weighting, the greater the error we have in estimating the power spectrum.
+The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
 

### 2018-01-22 PAPER.tex
Added some responses to Danny questions + added some comments to Appendix B

--- 2018-01-22 PAPER.tex
@@
 then explaining in the next section exactly how cross terms were what messed us up in the first go round.} 
+\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
+It's not.
+It's meant as a motivational example.
+I just wanted something where I could follow through analytically to the end to show that it's ok to think about signal loss as a multiplicative factor.
+At least in expectation.
+And then how one deals with not correcting for the signal loss in expectation is described in Section \ref{sec:Practice}.}
 
@@
 \ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
+\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
+Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
+What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
+So essentially we are defining an effective $
+\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
 
@@
 The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the assumption that the number of samples is large enough to treat sample variance as a first order purturbation on the ideal covariance matrix instead of the dominant effect we know it is.
-However it is possible to ask a slightly different question and with less math still get roughly the same answer.
+\acl{I'm not sure the previous sentence was fair.
+Again, the appendix is a motivating example.
+Carina's numerical computations do not rely on the derivation.} However it is possible to ask a slightly different question and with less math still get roughly the same answer.
 
@@
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
-Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
+\acl{Can we justify better why this is the right question?
+In particular, why is the detection of an injected signal the right thing to look at?
+After all, the universe doesn't do any signal injections.
+I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
 
@@
 the null test) the same.
-
+ \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by
+ \begin{equation}
+ \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{p}}_x) dx = \Lambda,
+ \end{equation}
+ where $\Lambda$ is the appropriate number for $2\sigma$.
+That tells us what $x$ would be needed for us to thing that it was an outlier result without there being an extra $e$ in the data.
+Then we ask how often we get such an outlier result by computing
+  \begin{equation}
+ \int_{x_0}^\infty \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) dx.
+\end{equation}
+Is what you've written equivalent to this? Sorry if this is remedial...
+ }
  \begin{equation}

### 2018-01-22 PAPER.tex

--- 2018-01-22 PAPER.tex
@@
 instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
+In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
 

### 2018-01-23 PAPER.tex
language edits in 2.1, and plot caption edits

@@
 weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
-This weighting has the effect of down-weighting correlated
-information (i.e. foregrounds) and up-weighting noise-like information (i.e. EoR). However, a challenge of inverse covariance 
+Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
+However, a challenge of inverse covariance
 weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two has large impacts on signal loss.
@@
 Kelvin and taking into account cosmological scalings.
-It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance with respect to the true bandpower in $\alpha$, where $\alpha$ denotes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
+It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C}$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
 Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
@@
 \noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum. The data analyst has a choice for $
-\textbf{M}$ (subject to the constraint that window functions are sensible) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal ($\textbf{M} \propto \textbf{I}$), although we explore other cases for the analysis
+\textbf{M}$ (subject to the constraint that window functions integrate to unity) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal ($\textbf{M} \propto \textbf{I}$), although we explore other cases for the analysis
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
@@
 Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some foregrounds since foregrounds have large covariances in frequency, motivating our use of the weighting for previous PAPER analyses.
+In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
 
@@
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis) we use $\sim$$8$ hours of data for our analysis (with channel 
+might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis) we use $\sim$$8$ hours of data (with channel 
 widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
@@
 where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
-case, signal loss arises from using information from all eigenmodes of $\widehat{\textbf{C}}$. Because $\widehat{\textbf{C}}$ is 
-empirically estimated, its eigenvalues differ from those of the true covariance and this error primarily affects the weaker (EoR-dominated) eigenmodes.
-There is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are not using the relative weights of the weaker eigenmodes 
-which $\widehat{\textbf{C}}$ does not describe accurately.}
+case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
+For an empirically estimated $\widehat{\textbf{C}}$, its eigenvalues differ from those of the true covariance, where the weakest (EoR-dominated) eigenmodes are the most strongly coupled to the data and can lead to the most loss.
+Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are not using the relative weights of the weaker eigenmodes.}
 	\label{fig:toy_sigloss3}
@@
 words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
-\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes. This is usually not the case for a covariance matrix, 
-for which a sloped eigenspectrum means that modes are given different weights in OQE power spectrum estimation. The modes with the highest eigenvalues are 
+\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in OQE power spectrum estimation.
+The modes with the highest eigenvalues are
 down-weighted the most.
@@
 (green). The eigenspectrum of $\widehat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
-sinusoid. These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$, 
-meaning that some eigenmodes (shapes in the data) may be down-weighted more significantly than they should be, producing 
-signal loss. Specifically, down-weighting the weak eigenmodes, where the EoR signal is greater than the FG signal, leads to 
-loss.}
+sinusoid.
+These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$.
+Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
 	\label{fig:toy_sigloss2}
@@
 Using the full dataset's (foreground plus EoR signal) empirical covariance, we can
-project out the first eigenmode (i.e.
-use the true eigenvalue of the first eigenmode, but flatten the rest of the spectrum to have eigenvalues of 1), thereby down-weighting the foreground-dominated mode more than the rest of the modes.
+project out the first eigenmode and then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
 Hence, we are changing the weaker part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
@@
 \citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we argue in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}, the resulting estimates are biased 
+as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
 \emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
@@
 As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges.}
+With more independent samples, the quicker an empirical covariance converges, and the less signal loss we would expect to result.}
 	\label{fig:toy_sigloss16}
@@
 The colors span from the 0th eigenmode (the first one) to the 19th eigenmode (the last one), where they are ordered by eigenvalue in descending order.
-This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes.}
+This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes, implying that weighting by empirically estimated `weak' modes poses the most risk for signal loss.}
 	\label{fig:toy_sigloss17}
@@
 EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
-computed from the data. There is a larger amount of signal loss than for the non-averaged data, a consequence of a 
-steepened, weakly characterized eigenspectrum from fewer independent modes in the data. The power spectrum 
-estimate is also noisier, since most of the information used in constructing the estimate came from only a few eigenmodes (the 
-weakest, EoR-dominated modes).}
+computed from the data.
+There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by empirically estimated eigenmodes that are more strongly coupled to the data due to there being fewer independent modes.}
 	\label{fig:toy_sigloss7}
@@
 The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
-expected, there is a much larger amount of signal loss for this time-averaged dataset.
-We do a worse job estimating the true covariance and, as a result, it is a noisier estimate.
+expected, there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
+In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter.
 This is evident by noticing that the
@@
 This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
-We don't see perfect EoR recovery though, as the
-green and red curves vary slightly in Figure \ref{fig:toy_sigloss8}. This deviation is a consequence of the difference between the 
-true and modeled covariance matrices. In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\textbf{C}_{FG}$ is unknown.
+In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\textbf{C}_{FG}$ is unknown.
 

### 2018-01-24 PAPER.tex
updated KDE plots to include pos and neg axes

@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
+	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
 	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
+heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
 From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
@@
 \centering
-\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
+\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
 \caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
@@
 We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
-The solid black
-diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
-At low injection, $P_{\rm out}$ converges to the data level.
+The dotted black
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
+At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
 }

### 2018-01-25 PAPER.tex
updated fig B3 to match
re-made fig 20 with sigloss updates

@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is small.
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted. %, though the improvement from the unweighted case is small.
 
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
 	\label{fig:sigloss_modeloop}
@@
 The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
-Overall the limits show good agreement, with k modes differing by factors of $\sim$$3$.
+Overall the limits show good agreement, with k modes differing by factors of $\sim$$2$ for $k > 0.1$ $h$Mpc$^{-1}$ .
 

### 2018-01-25 PAPER.tex
updated jackknife explanation

@@
 Figure \ref{fig:ps1_data}, has positive biases at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these detections 
-are most likely attributable to foreground leakage. Here we demonstrate three null tests performed on PAPER-64 data that verify 
-that the positive detections are indeed due to foreground variation and not attributable to EoR.
+are most likely attributable to foreground leakage.
+The cause for the detections at higher $k$ values is more difficult to pinpoint.
+Here we demonstrate three null tests performed on PAPER-64 data that aim to explain these detections and verify
+that they are not attributable to EoR.
 
@@
 \begin{itemize}
-\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
-There are clear detections at
-low $k$'s.
+%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
+There are clear detections at low $k$'s.
 \item Even/Odd (blue): We split our dataset into even (\textbf{e}) and odd (\textbf{o}) days. We then form the following two datasets: $\textbf{x}_{1} = \textbf{e} + \textbf{o}$ and $\textbf{x}_{2} = 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/null.png}
-	\caption{Results for three null tests compared to the PAPER-64 unweighted revised power spectrum (black) and analytically estimated 
-$2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
-even and odd days; blue), along baselines (green), and along LST (magenta).
-We expect the sky signal to disappear for a `passing' null test (for all error bars to be contained to within the gray shaded region).
-We find that none of the null tests performed pass, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
+	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
+	\caption{Results for three null tests compared to analytically estimated 
+$2\sigma$ errors (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
+even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
+We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
 	\label{fig:null}
@@
 
-Investigating Figure \ref{fig:null}, we find that none of the null tests are fully consistent with noise; we would expect the null tests' error bars to be contained within the gray shaded region (theoretical error) for a `passable' test.
-We note, however, that the error bars for the baselines test (green) and even/odd test (blue) are smaller than those of the LST test (magenta).
-
-%We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
-
-This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise, and that the even/odd test is mostly consistent with noise.
+For a `passing' null test, we expect $95\%$ of the error bars to be contained within the gray shaded region (theoretical error).
+We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+The null test in LST is much more illuminating.
+Because of the large error bars and variation in its result, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
 estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
-In other words, the fact that many magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
+In other words, the fact that several magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-While residual foregrounds are the primary cause for power spectrum results above the theoretical noise (as in Figure \ref{fig:ps1_data}), other unexplained variations exist which are present in all the null tests.
-These variations could be attributable to...
-\cc{fill in}
 

### 2018-01-26 PAPER.tex
added text explaining how our data points are computed from the no-bootstrapping case

@@
 The final result can then be normalized to give $p(P_{in} | \phat_{x})$.
-If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
+If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping, where our distribution is shifted so that its peak value aligns with the power spectrum estimate from the no-bootstrapping case; see Section \ref{sec:Boot} for more details on this), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
 In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-one major changes in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
+one major change in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
 
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic prediction for noise.
+
+Finally, we note that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation along with the bootstrapped estimates (which are used to compute errors).
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
 

### 2018-01-26 PAPER.tex
added switzer recommended refs

@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, and \citet{trott_et_al2016}.
+estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
 Before showing
@@
 
-Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself (this is what was done in the previous PAPER analyses).
-For instance, one could time-average such that:
+Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
+Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
+In previous PAPER analyses, one time-averages the data such that:
 
@@
 In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
-the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation.  
+the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation (an approach also taken by \citet{masui_et_al2013}).  
 There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.
@@
 The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
+simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
+This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of GBT data.
+Therefore, in our revised
 signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
@@
 The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
+\citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
 

### 2018-01-26 PAPER.tex
added some more refs

@@
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today (for a review, see \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
+web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
 
 One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}).
+its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
 This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
@@
 The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
+instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
 A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
@@
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of GBT data.
+This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of Great Bank Telescope (GBT) data.
 Therefore, in our revised

### 2018-01-26 PAPER.tex
made some edits based on eric's comments

@@
 the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
-for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
+for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
@@
 from the lessons learned.
-
-This paper adds to the growing foundations of lessons which have been documented in  \cite{Patil2016,Jacobs2016} and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
+More specifically, we develop new techniques for computing signal loss and under-go a rigorous re-analysis of PAPER-64 data in order to present a new power spectrum limit.
+A companion paper, Kolopanis et al., \textit{in prep}, builds off of the methods in this paper to present PAPER-64 results for multi-redshifts and multiple baselines.
+
+Finally, this paper adds to the growing foundations of lessons which have been documented in  \citet{Patil2016}, \citet{Jacobs2016}, and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
+These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
 
@@
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-In other words, mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
+More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:Illustration}), which leads to loss.
+Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
 
@@
 confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
-measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's 
+measurement are calculating the variance of power spectrum results, and computing a theoretical error estimate based on an instrument's 
 system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
@@
 weightings.
+
+%A third option which acts as a middle ground between the other two is
 
@@
 \label{eq:LinearPspecSum}
-\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
-\end{equation}
-where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
+\langle \phat_{x} \rangle  = \langle g(\x) \rangle = T_{\rm fg} \p_{\rm fg} + T_{\rm eor} \p_{\rm eor},
+\end{equation}
+where $T_{\rm eor}$ and $T_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
 power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
@@
 
-Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
+Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / T_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
 Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
+The most conceptually straightforward way to compute $T_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
 \begin{equation}
 \label{eq:Deriv1}
-\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+\widehat{T}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
 \end{equation}
@@
 \label{eq:Deriv2}
-\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
+\widehat{T}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
 \end{equation}
@@
 \begin{equation}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
+\phat_x \approx T_{\rm fg} |\mathbf{f}|^2 + T_{\rm eor} |\mathbf{e}|^2 + T_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
 \end{equation}
@@
 \label{eq:fperpfpara}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
+\phat_x \approx T_{\rm fg} |\mathbf{f}|^2 +( T_{\rm eor} + \rho  T_{\rm fe} ) |\mathbf{e}|^2 + T_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
 \end{equation}
@@
 \begin{equation}
-\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
+\phat_x \approx T_{\rm fg} f^2 + T_{\rm eor} e^2 + T_{\rm fe} fe.
 \end{equation}
@@
 dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
-\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
+$g(x)$ to estimate $\hat{T}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
+T_{\rm eor}$ not $(T_{\rm eor} + \rho T_{\rm fe})$? }
+\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(T_{\rm eor} + \rho T_{\rm fe})$.
 Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
 What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
-So essentially we are defining an effective $
-\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
-
-The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
+So essentially we are defining an effective $T_{\rm eor}$, which is given by $(T_{\rm eor} + \rho T_{\rm fe})$.}
+
+The second issue to tackle is how one incorporates the randomness of $T_{\rm eor}$ into our signal loss corrections.
 This is manifest in Equation \eqref{eq:fperpfpara}, where the randomness of $\rho$ means that there is an inherent spread in the signal loss correction.
@@
 To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-This intrinsic scatter is shown as the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in the plot.
+This intrinsic scatter is shown as the smeared `heat-map' around the dotted black diagonal line (representing unity-transfer) in the plot.
 The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
-Specifically, we deconvolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
+Specifically, we de-convolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
+For the case shown in Figure \ref{fig:sigloss_transfercurve}, the intrinsic scatter we obtain from the de-convolution is small or negligible for each $P_{in}$.
+This means that for our analysis, the intrinsic stochasticity of signal loss is not a dominant factor.
+However, it is nevertheless important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
 
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted. %, though the improvement from the unweighted case is small.
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted and the rest are given equal weights.
+For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2014}.
 

### 2018-01-27 PAPER.tex
tweaked jackknife language

@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise, and that the even/odd test is mostly consistent with noise.
-For a `passing' null test, we expect $95\%$ of the error bars to be contained within the gray shaded region (theoretical error).
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are very close or passing through zero).
 We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
@@
 estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
-In other words, the fact that several magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
+In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
 
@@
 This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
-bias we see comes from foregrounds in regions where we expect leakage.
+bias we see comes from foregrounds. % in regions where we expect leakage.
 

### 2018-01-29 PAPER.tex
ref matt's paper in abstract

@@
 for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
-led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result mostly stems from an 
+led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al., \textit{in prep}, mostly stems from an 
 improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 

### 2018-01-30 PAPER.tex
some useful preamble bits

--- 2018-01-26 PAPER.tex
@@
 \usepackage{comment}
+%\usepackage{mathtools}
+\usepackage{xparse}
 %\usepackage{titlesec}
 \citestyle{aa}
+
+%Math stuff from Danny
+\NewDocumentCommand{\evalat}{sO{\big}mm}{%
+  \IfBooleanTF{#1}
+   {\mleft. #3 \mright|_{#4}}
+   {#3#2|_{#4}}%
+}
 
@@
 between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
+web of galaxies we observe today (for a review, see \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
 
 One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
+its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_loeb2012}).
 This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
@@
 The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
+instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, dillon_et_al2014, kohn_et_al2016}.
 A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
@@
 the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
-for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
+for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques and their trade-offs, potential 
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
@@
 from the lessons learned.
-More specifically, we develop new techniques for computing signal loss and under-go a rigorous re-analysis of PAPER-64 data in order to present a new power spectrum limit.
-A companion paper, Kolopanis et al., \textit{in prep}, builds off of the methods in this paper to present PAPER-64 results for multi-redshifts and multiple baselines.
-
-Finally, this paper adds to the growing foundations of lessons which have been documented in  \citet{Patil2016}, \citet{Jacobs2016}, and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
-These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
+
+This paper adds to the growing foundations of lessons which have been documented in  \cite{Patil2016,Jacobs2016} and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
 
@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
+estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, and \citet{trott_et_al2016}.
 Before showing
@@
 
-Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data such that:
+Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself (this is what was done in the previous PAPER analyses).
+For instance, one could time-average such that:
 
@@
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:Illustration}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
+In other words, mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
 
@@
 confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
-measurement are calculating the variance of power spectrum results, and computing a theoretical error estimate based on an instrument's 
+measurement are calculating the variance of a dataset, and computing a theoretical error estimate based on an instrument's 
 system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
@@
 weightings.
-
-%A third option which acts as a middle ground between the other two is
 
@@
 In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
-the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation (an approach also taken by \citet{masui_et_al2013}).  
+the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation.  
 There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.
@@
 \label{eq:LinearPspecSum}
-\langle \phat_{x} \rangle  = \langle g(\x) \rangle = T_{\rm fg} \p_{\rm fg} + T_{\rm eor} \p_{\rm eor},
-\end{equation}
-where $T_{\rm eor}$ and $T_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
+\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
+\end{equation}
+where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
 power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
@@
 
-Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / T_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
+Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
 Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $T_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
+The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
 \begin{equation}
 \label{eq:Deriv1}
-\widehat{T}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
 \end{equation}
@@
 \label{eq:Deriv2}
-\widehat{T}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
+\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
 \end{equation}
@@
 The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of Great Bank Telescope (GBT) data.
-Therefore, in our revised
+simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
 signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
@@
 \begin{equation}
-\phat_x \approx T_{\rm fg} |\mathbf{f}|^2 + T_{\rm eor} |\mathbf{e}|^2 + T_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
+\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
 \end{equation}
@@
 \label{eq:fperpfpara}
-\phat_x \approx T_{\rm fg} |\mathbf{f}|^2 +( T_{\rm eor} + \rho  T_{\rm fe} ) |\mathbf{e}|^2 + T_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
+\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
 \end{equation}
@@
 \begin{equation}
-\phat_x \approx T_{\rm fg} f^2 + T_{\rm eor} e^2 + T_{\rm fe} fe.
+\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
 \end{equation}
@@
 dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-$g(x)$ to estimate $\hat{T}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-T_{\rm eor}$ not $(T_{\rm eor} + \rho T_{\rm fe})$? }
-\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(T_{\rm eor} + \rho T_{\rm fe})$.
+$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
+\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
+\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
 Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
 What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
-So essentially we are defining an effective $T_{\rm eor}$, which is given by $(T_{\rm eor} + \rho T_{\rm fe})$.}
-
-The second issue to tackle is how one incorporates the randomness of $T_{\rm eor}$ into our signal loss corrections.
+So essentially we are defining an effective $
+\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
+
+The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
 This is manifest in Equation \eqref{eq:fperpfpara}, where the randomness of $\rho$ means that there is an inherent spread in the signal loss correction.
@@
 The final result can then be normalized to give $p(P_{in} | \phat_{x})$.
-If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping, where our distribution is shifted so that its peak value aligns with the power spectrum estimate from the no-bootstrapping case; see Section \ref{sec:Boot} for more details on this), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
+If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
 In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
@@
 To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-This intrinsic scatter is shown as the smeared `heat-map' around the dotted black diagonal line (representing unity-transfer) in the plot.
+This intrinsic scatter is shown as the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in the plot.
 The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
-Specifically, we de-convolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
+Specifically, we deconvolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-For the case shown in Figure \ref{fig:sigloss_transfercurve}, the intrinsic scatter we obtain from the de-convolution is small or negligible for each $P_{in}$.
-This means that for our analysis, the intrinsic stochasticity of signal loss is not a dominant factor.
-However, it is nevertheless important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
+	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve.png}
 	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
+heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The solid black 
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
 From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
@@
 The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
-\citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
 
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted and the rest are given equal weights.
-For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2014}.
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is small.
 
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
 	\label{fig:sigloss_modeloop}
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-one major change in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
+one major changes in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
 
@@
 
-Finally, we note that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation along with the bootstrapped estimates (which are used to compute errors).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
-
 \begin{figure}
@@
 Figure \ref{fig:ps1_data}, has positive biases at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these detections 
-are most likely attributable to foreground leakage.
-The cause for the detections at higher $k$ values is more difficult to pinpoint.
-Here we demonstrate three null tests performed on PAPER-64 data that aim to explain these detections and verify
-that they are not attributable to EoR.
+are most likely attributable to foreground leakage. Here we demonstrate three null tests performed on PAPER-64 data that verify 
+that the positive detections are indeed due to foreground variation and not attributable to EoR.
 
@@
 \begin{itemize}
-%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
-There are clear detections at low $k$'s.
+\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
+There are clear detections at
+low $k$'s.
 \item Even/Odd (blue): We split our dataset into even (\textbf{e}) and odd (\textbf{o}) days. We then form the following two datasets: $\textbf{x}_{1} = \textbf{e} + \textbf{o}$ and $\textbf{x}_{2} = 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
-	\caption{Results for three null tests compared to analytically estimated 
-$2\sigma$ errors (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
-even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
-We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
+	\includegraphics[width=1\textwidth]{plots/null.png}
+	\caption{Results for three null tests compared to the PAPER-64 unweighted revised power spectrum (black) and analytically estimated 
+$2\sigma$ errors (gray shaded region). For each, we take a jackknife along a different axis of the dataset - along julian days (separating 
+even and odd days; blue), along baselines (green), and along LST (magenta).
+We expect the sky signal to disappear for a `passing' null test (for all error bars to be contained to within the gray shaded region).
+We find that none of the null tests performed pass, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
 	\label{fig:null}
@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise, and that the even/odd test is mostly consistent with noise.
-For a `passing' null test, we expect $95\%$ of the error bars to be contained within the gray shaded region (theoretical error).
-We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
-
-The null test in LST is much more illuminating.
-Because of the large error bars and variation in its result, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
+Investigating Figure \ref{fig:null}, we find that none of the null tests are fully consistent with noise; we would expect the null tests' error bars to be contained within the gray shaded region (theoretical error) for a `passable' test.
+We note, however, that the error bars for the baselines test (green) and even/odd test (blue) are smaller than those of the LST test (magenta).
+
+%We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
 estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
-In other words, the fact that several magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
+In other words, the fact that many magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+While residual foregrounds are the primary cause for power spectrum results above the theoretical noise (as in Figure \ref{fig:ps1_data}), other unexplained variations exist which are present in all the null tests.
+These variations could be attributable to...
+\cc{fill in}
 
@@
 \centering
-\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
+\includegraphics[width=\textwidth]{plots/method2_heatmap_I.png}
 \caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
@@
 We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
-The dotted black
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
-At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
+The solid black
+diagonal line marks a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
+At low injection, $P_{\rm out}$ converges to the data level.
 }
@@
 The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
-Overall the limits show good agreement, with k modes differing by factors of $\sim$$2$ for $k > 0.1$ $h$Mpc$^{-1}$ .
+Overall the limits show good agreement, with k modes differing by factors of $\sim$$3$.
 

### 2018-01-30 PAPER.tex
Massage case study language a tad.

@@
 
-We now present a case study of these same three themes using data from the PAPER experiment. We use the intuition 
-developed through the toy model simulations in order to make a new analysis of the PAPER-64 dataset originally presented in 
+We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
 A15 and obtain a revised power spectrum estimate.

### 2018-01-30 PAPER.tex
Topic sentences.

@@
 Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set.
-The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
-In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
-the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation.  
-There are, in fact, several different ways of incorporating the result of such a calculation into a revised power spectrum estimate which accounts for signal loss.
-In this section, we describe a methodology for determining an approximate correction factor which can be applied to a power spectrum estimate; in Appendix \ref{sec:Pr_appendix}, we present an alternate framework that explicitly interprets all measurements as upper limits in the presence of signal loss.
+The exact amount of signal loss for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
+In this work, as in A15, we inject simulated cosmological signals into our data and test the recovery of those signals.
+As we will see, correlations between the injected signals and the data are significant complicating factor which was previously not taken into account.
+
+The results of such an injection scheme can be interpreted in multiple ways.
+In this paper we describe two.
+This section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
 These two methods yield very similar results, but fundamentally are answering subtly distinct questions.  
@@
 \label{sec:siglossmethod}
+The gist of our method is to inject a eor-like signal into the data and then measure the amount recovered, with the difference being accounted as signal loss.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$

### 2018-01-30 PAPER.tex
Replace Adrian math with a caveat and some explanation.

@@
 data plus injection, and $P_{\rm out}$ is the difference between $\widehat{\textbf{p}}_{r}$ and $\widehat{\textbf{p}}_{x}$.
-
-In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
+In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation, ie the amount of background EoR power $P_{\rm eor}$ not removed by the foreground downweighting procedure.
+In other words, we make the anzatz that
+
+\begin{equation}
+P_{\rm out} = P_{\rm eor} \label{eqn:anzatz},
+\end{equation}
+folding in our definition from Equation \ref{eq:sigloss}, this definition implies that we are seeking the injected 
+signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$).
+
+%
+%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
-
-In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
-\begin{equation}
-\x \equiv \f + \s,
-\end{equation}
-where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
+%
+%In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
+%\begin{equation}
+%\x \equiv \f + \s,
+%\end{equation}
+%where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
 In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$.
 This can be parametrized as
-\begin{equation}
-\label{eq:LinearPspecSum}
-\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
-\end{equation}
-where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
-power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
-\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
-\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
-small sample size limited to first order perturbations and thus neglects cross correlation between $x$ and $e$.  
-In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
-terms to be remain significant.
-
-Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
+%\begin{equation}
+%\label{eq:LinearPspecSum}
+%\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
+%\end{equation}
+%where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
+%power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
+%\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
+%\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
+%which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
+%small sample size limited to first order perturbations and thus neglects cross correlation between $x$ and $e$.  
+%In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
+%terms to be remain significant.   
+%
+%Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
 Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
 The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
-\begin{equation}
-\label{eq:Deriv1}
-\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
-\end{equation}
-However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
+%\begin{equation}
+%\label{eq:Deriv1}
+%\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
+%\end{equation}
+%However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
 Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
-\begin{equation}
-\label{eq:Deriv2}
-\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
-\end{equation}
-which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
+%\begin{equation}
+%\label{eq:Deriv2}
+%\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
+%\end{equation}
+%which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
 Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
@@
 In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.
-
-Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
+%
+%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
-\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
-\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
-covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
-correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
-I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-then explaining in the next section exactly how cross terms were what messed us up in the first go round.} 
-\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
+%\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
+%\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
+%covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
+%correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
+%I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
+%then explaining in the next section exactly how cross terms were what messed us up in the first go round.} 
+%\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
 It's not.
@@
 And then how one deals with not correcting for the signal loss in expectation is described in Section \ref{sec:Practice}.}
-
-Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
-which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
-distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
-distribution could this (signal-loss affected) data come from?"
-
-In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
+%
+%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
+%which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
+%distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
+%distribution could this (signal-loss affected) data come from?" 
+%
+%In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
 Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
-signal loss lens.
+%signal loss lens.
 We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
 One alternative to the method described in Section \ref{sec:Practice} is described in Appendix \ref{sec:Pr_appendix}.
-%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
-
-\subsubsection{Signal Loss Illustration}
-\label{sec:Illustration}
-To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
+%%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
+
+%\subsubsection{Signal Loss Illustration}
+%\label{sec:Illustration}
+%To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
 

### 2018-01-30 PAPER.tex
signal loss
somewhat more practical description of injection cross terms. Less explanation of how, more explanation of what.

@@
 \end{eqnarray}
-We see that $P_{\rm out}$ is comprised of multiple terms.
-To build intuition into each of these terms, they are plotted individually in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$, left) and unweighted ($\textbf{R}_{r} = \textbf{I}$, right).
-We leave the details of the simulation to Section \ref{sec:Practice}, but for now highlight that each term in Equation \eqref{eq:crossterm} corresponds to a different color in the plot.
-Specifically, the first term in Equation \eqref{eq:crossterm} is plotted as blue, the second as green, the third and fourth (which are the same) as red, and the last as gray.
-The solid black curve denotes $P_{\rm out}$, which is comprised of all the other terms.
-
-A brief description of Figure \ref{fig:sigloss_terms} is as follows.
+
+Assuming R$_{r}$ is symmetric the two cross terms can be summed together as
+
+\begin{eqnarray}
+\label{eq:crossterm}
+P_{\rm out,\alpha} &= &  M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \\
+&+& M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&+& 2 M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \\
+&-& M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+^{\alpha}\textbf{R}_{x}\textbf{x}.
+\end{eqnarray}.
+
+Each of these terms is plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and unweighted ($\textbf{R}_{r} = \textbf{I}$).
+Let us examine the behavior of this equation in the regimes of very weak and very strong injected signal.
+
+{\bf Small injection}
+The first and the fourth term are very similar, differing only in their covariance matrices. When the injected signal 
+is very small compared to the data, their difference can be neglected.  In this limit we might imagine that the 
+cross correlation should also be small enabling us to recover just the EoR term, however examining the cross-
+term plotted in Figure  \ref{fig:sigloss_terms} we see that cross terms are still large enough to have a significant 
+impact. This is trivially demonstrated in the identity case where we even at small injects, large cross terms are 
+evident.
+
+{\bf Large injection}
+When the injected signal is much larger than the data-only power spectrum, the data-only components can 
+be neglected as many orders of magnitude smaller.
+As we can see from Figure  \ref{fig:sigloss_terms}, the cross terms are also small in comparison.
+Here only do we recover the ``loss'' injected simulated eor
+signal as planned.
+
+{\bf In between}
+When the injected signal is of a similar amplitude to the data by itself, the picture becomes murky.  We see that 
+the weighted injected power spectrum component mirrors the input power indicating little loss, eventually 
+departing from unity when the injected amplitude is well above the level of the data power spectrum. However 
+the cross terms have nearly the same amplitude, but a negative sign. The sum of the two is substantially lower and substantially drives down the $P_{\rm out}$ estimator.
+
+%A brief description of Figure \ref{fig:sigloss_terms} is as follows.
 The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed.
@@
 
-We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
+%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross terms don't matter when injected signal is very large.}
+%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
 For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
 It is in this limit where we expect signal loss to be greatest, and $P_{\rm out}$ becomes:
-
-\begin{eqnarray}
-\label{eq:pout_expand}
-P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
- 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
-\end{eqnarray}
-The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
+%
+%\begin{eqnarray}
+%\label{eq:pout_expand}
+%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
+% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
+%\end{eqnarray}
+%The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
 Again, it is this quantity that was used in A15 to calculate signal loss.
@@
 
+The source of the strong negative cross term is not immediately obvious, however it is an explainable effect. 
 When $\textbf{R}_{r}$
@@
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
-signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
-weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
-
-We thus see from this subsection that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
+signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, despite the fact that the cross-terms muddy the waters.
+
+%\dcj{This paragraph has me confused.}
+%The conclusion is that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
 In principle, using $\widehat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
@@
 \label{sec:Practice}
-%\begin{center}
-%METHOD \#1
-%\end{center}
 
@@
 
-The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
+%The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
 In practice, however, the signal loss itself is a random variable --- some realizations of the cosmological signal may be more correlated with foreground modes than others, leading to more signal loss.
@@
 In other words, suppose that we have
-\begin{equation}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
-\end{equation}
-in place of Equation \eqref{eq:LinearPspecSum}.
+%\begin{equation}
+%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
+%\end{equation}
+%in place of Equation \eqref{eq:LinearPspecSum}.
 Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
@@
 This then gives
-\begin{equation}
-\label{eq:fperpfpara}
-\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
-\end{equation}
-Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
-\dcj{Wait what?
+%\begin{equation}
+%\label{eq:fperpfpara}
+%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
+%\end{equation}
+%Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
+%\dcj{Wait what?
 I think you are saying essentially that some x can remain in Pout which is what we are seeing.
@@
 What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
-\begin{equation}
-\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
-\end{equation}
-(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
-$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
-couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
-some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
-Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
-EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
-the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
-dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
-\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
+%\begin{equation}
+%\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
+%\end{equation}
+%(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
+%$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
+%couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
+%some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
+%Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
+%EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
+%the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
+%dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
+%$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
+%\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
+%\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
 Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
@@
 So essentially we are defining an effective $
-\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
-
-The second issue to tackle is how one incorporates the randomness of $\ell_{\rm eor}$ into our signal loss corrections.
-This is manifest in Equation \eqref{eq:fperpfpara}, where the randomness of $\rho$ means that there is an inherent spread in the signal loss correction.
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
-Since Equation \eqref{eq:Deriv2} is a good approximation of Equation \eqref{eq:Deriv1}, which we argued for in the previous section, we can write $\p_{\rm eor}$ as $P_{in}$, and hence the probability distribution is given by
+%\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
+
+One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections.
+A different realization of the test signal is injected with each bootstrap run causing the output to vary according to noise as well as whether the injected signal looks more or less ``like'' the data.
+
+Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | 
+\phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
+Given our guess from section \ref{sec:siglossmethod}, that the change in power caused by the injection injection$P_{\rm out}$ is a good estimate of the injected EoR power $P_{\rm eor}$ we can write
+
 \begin{equation}
 \label{eq:Bayes}
-p(P_{in} | \phat_{x}) \propto \mathcal{L} (  \phat_{x} | P_{in})  p(P_{in}),
-\end{equation}
-where $p(P_{in})$ is the prior on $P_{in}$ and $\mathcal{L} $ is the likelihood function.
-Since the likelihood is defined as the distribution of the measured result $ \phat_{x}$ given the theoretical power spectrum $P_{in}$, we may construct this function simply by fixing $P_{in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal consistent with this power spectrum.
-The resulting distribution can be normalized, and the whole process can then be repeated for a different value of $P_{in}$.
-
-In our code, we simulate $20$ realizations of $P_{in}$, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
+p(P_{\rm eor} | \phat_{x}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
+  p(\phat_{x}) ,
+\end{equation}
+
+\noindent where $p(\phat_x)$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
+as the distribution of data + injection ($P_{\rm out}$) given the injection $P_{\rm in}$ evaluated at P.  We construct this distribution  
+by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
+consistent with this power spectrum. The resulting distribution is normalized such that the sum is unity, and the 
+whole process can then be repeated for a different value of $P_{\rm in}$.  \dcj{am I right about the normalization?}
+
+\subsection{Implementation}
+The implementation details of the injection process require some more detailed explanation.
+In our code, we add a new realization to each independent bootstrap with the goal of simultaneously capturing variance due to noise and signal loss.
+To limit computing time we perform $20$ realizations of $P_{in}$, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
 We also run $25$ total EoR injection levels, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
@@
 We smooth the 2D distribution of $P_{in}$ vs.
-$P_{out}$ using kernel density estimators.
+$P_{out}$ using kernel density estimators\citep{scott2008kernel}.
 The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.
-Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$.
-The final result can then be normalized to give $p(P_{in} | \phat_{x})$.
-If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, before performing the final summation and normalization.
+Although we only show figures for one $k$ value, we note that
+the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$.
+The final result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$.
+If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, to find the distribution of $P_{\rm eor}$.
 In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
@@
 We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
-
-As a final complication to our procedure, we note that there will be some intrinsic scatter in our likelihood due to our having only a finite number of simulations.
-Ideally, running many simulations would lead to convergence in our likelihood; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
-To separate the intrinsic stochasticity of signal loss from that which arises due to simulation noise, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-This intrinsic scatter is shown as the smeared `heat-map' around the solid black diagonal line (representing unity-transfer) in the plot.
-The width of the lossless scenario's signal loss likelihood is then deconvolved from the lossy scenario's signal loss likelihood.
+\dcj{Normalization needs an equation}
+
+As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
+Ideally, running many simulations would lead to convergence; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
+\dcj{This dependence on injection count was checked with a run having 10x the usual number of integrations.} To separate the intrinsic stochasticity of signal loss from that which arises due to simulation sample variance, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
+Here the scatter, evident as deviations from unity-transfer, is entirely due to finite sample variance.
+To remove this effect we measure the width of this lossless case and then deconvolve that extra width from the likelihood for the lossy scenario.
 Specifically, we deconvolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
@@
 %This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. 
-
-The shape of our signal loss transfer function can be described as follows.
+%
+%The shape of our signal loss transfer function can be described as follows.
 At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}.
 As $\textbf{e}$ increases, we move
-into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
-large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
-the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
+%into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
+%large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
+%the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
 
@@
 
-To conclude this method, we also show power spectrum results for fringe-rate filtered PAPER-64 data before and after signal 
-loss estimation in Figure \ref{fig:ps2_data}, using empirically estimated inverse covariance weighting. The blue dashed line represents the unweighted 
-power spectrum $2\sigma$ upper limit, which is identical in both panels (an important check, as we expect no signal loss for this case). The black and 
-gray points are positive and negative power spectrum values plotted with $2\sigma$ error bars. Prior to signal loss estimation, it 
-is clear that the power spectrum is unfeasible because it is well below the theoretical noise level prediction (solid green curve). 
-Post-estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
+The result is the loss-corrected power spectrum shown in Figure \ref{fig:ps2_data} which we can compare  to the original lossy result.
+There are a few important checks to examine.
+We see that the unweighted
+power spectrum $2\sigma$ upper limit is identical in both panels.
+This is an important check, as we expect no signal loss for this case.
+Any difference here would indicate an error in the pipeline or discrepancy in the range of data included.
+Prior to signal loss estimation, it
+is clear that the power spectrum is inconsistent with the (now revised) theoretical noise level prediction. 
+Post signal loss estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
 We elaborate on this point in the next section, as well as investigate alternate

### 2018-01-30 PAPER.tex

@@
 In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data
+
 itself.
 Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set.
-The exact amount of signal loss for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
-In this work, as in A15, we inject simulated cosmological signals into our data and test the recovery of those signals.
-As we will see, correlations between the injected signals and the data are significant complicating factor which was previously not taken into account.
-
+The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
+In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
+the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation (an approach also taken by \citet{masui_et_al2013}).  
 The results of such an injection scheme can be interpreted in multiple ways.
@@
 The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. Therefore, in our revised 
-signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, despite the fact that the cross-terms muddy the waters.
+simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
+This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of Great Bank Telescope (GBT) data.
+Therefore, in our revised
+signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
+weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted, though the improvement from the unweighted case is small.
+only the strongest $\sim3$-$4$ eigenmodes are down-weighted and the rest are given equal weights.
+For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2014}.
 
@@
 
+Finally, we note that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation along with the bootstrapped estimates (which are used to compute errors).
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
+
 \begin{figure}
@@
 
-Investigating Figure \ref{fig:null}, we find that none of the null tests are fully consistent with noise; we would expect the null tests' error bars to be contained within the gray shaded region (theoretical error) for a `passable' test.
-We note, however, that the error bars for the baselines test (green) and even/odd test (blue) are smaller than those of the LST test (magenta).
-
-%We note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
-
-This suggests that the primary systematic driving our power spectrum points and errors to be outside the 
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are very close or passing through zero).
+We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+The null test in LST is much more illuminating.
+Because of the large error bars and variation in its result, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
 estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
-In other words, the fact that many magenta power spectrum points are outside the estimated error region implies that $t_{1}$ and
+In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and
 $t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-While residual foregrounds are the primary cause for power spectrum results above the theoretical noise (as in Figure \ref{fig:ps1_data}), other unexplained variations exist which are present in all the null tests.
-These variations could be attributable to...
-\cc{fill in}
+We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
 

### 2018-01-30 PAPER.tex
Folded back in Carina's text about no bootstrapping. Still need normalization explanation

@@
 
-We smooth the 2D distribution of $P_{in}$ vs.
-$P_{out}$ using kernel density estimators\citep{scott2008kernel}.
+We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators\citep{scott2008kernel}. 
 The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.  
 Although we only show figures for one $k$ value, we note that 
-the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule then simply instructs us to fix $\phat_{x}$ at our measured value, essentially reading Figure \ref{fig:sigloss_transfercurve} horizontally and reinterpreting Equation \eqref{eq:Bayes} as a function of $p(P_{in})$.
-The final result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$.
-If $\phat_{x}$ itself does not take on a single value but is itself a distribution (for our analysis, this comes from bootstrapping), then one simply repeats the process for every single point on the distribution of $\phat_{x}$, to find the distribution of $P_{\rm eor}$.
-In Figure \ref{fig:sigloss_transfercurve}, the peak of our data distribution $
+the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule 
+then simply instructs us compute $p(\phat_{x})$, multiply it horizontally across Figure 
+\ref{fig:sigloss_transfercurve} horizontally as defined in Equation \eqref{eq:Bayes} to get $p(P_{in})$. The final 
+result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$. 
+\dcj{Need to write down the normalization for \eqref{eq:Bayes}}
+The width of the distribution of  $\phat_{x}$ itself is defined as a  gaussian with the mean $\phat_{x}$ and 
+variance determined from the bootstrap process.
+
+Inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the result should be.  The peak of our data distribution $
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.

### 2018-01-30 PAPER.tex
edited/cleaned up Danny's revisions in 3.1.1

@@
 
-In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data
-
-itself.
-Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular data set.
-The exact signal loss ``correction factor" for a particular data set will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
-In this work, we inject simulated cosmological signals into our data and test the recovery of those signals in order to statistically quantify 
-the amount of signal loss accompanying a weighting scheme used in OQE power spectrum estimation (an approach also taken by \citet{masui_et_al2013}).  
+In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data itself.
+Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular dataset.
+The exact amount of signal loss will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
+In this work, as in A15, we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
+As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
+
 The results of such an injection scheme can be interpreted in multiple ways.
-In this paper we describe two.
-This section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
+In this paper we describe two --- this section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
 These two methods yield very similar results, but fundamentally are answering subtly distinct questions.
-We also highlight major differences from the signal loss 
-computation used in A15, which previously underestimated losses.
+We also highlight major differences from the signal loss computation used in A15, which previously underestimated losses.
 
@@
 \label{sec:siglossmethod}
-The gist of our method is to inject a eor-like signal into the data and then measure the amount recovered, with the difference being accounted as signal loss.
+In short, our method consists of injecting an EoR-like signal into the data and then measuring the amount recovered, with the difference being accounted as signal loss.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$
@@
 likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text in Section \ref{sec:Illustration}).}
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
 
@@
 data plus injection, and $P_{\rm out}$ is the difference between $\widehat{\textbf{p}}_{r}$ and $\widehat{\textbf{p}}_{x}$.
-In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation, ie the amount of background EoR power $P_{\rm eor}$ not removed by the foreground downweighting procedure.
+In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
+the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
 In other words, we make the anzatz that
@@
 \end{equation}
-folding in our definition from Equation \ref{eq:sigloss}, this definition implies that we are seeking the injected 
-signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$).
+and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
+signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
 
@@
 \end{eqnarray}
-
-Assuming R$_{r}$ is symmetric the two cross terms can be summed together as
+Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms can be summed together as:
 
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &= &  M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \\
+P_{\rm out,\alpha} &= &  M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
 &+& M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \\
+&+& 2 M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
 &-& M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}.
-
+\end{eqnarray}
 Each of these terms is plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and unweighted ($\textbf{R}_{r} = \textbf{I}$).
-Let us examine the behavior of this equation in the regimes of very weak and very strong injected signal.
-
-{\bf Small injection}
-The first and the fourth term are very similar, differing only in their covariance matrices. When the injected signal 
-is very small compared to the data, their difference can be neglected.  In this limit we might imagine that the 
-cross correlation should also be small enabling us to recover just the EoR term, however examining the cross-
-term plotted in Figure  \ref{fig:sigloss_terms} we see that cross terms are still large enough to have a significant 
-impact. This is trivially demonstrated in the identity case where we even at small injects, large cross terms are 
+We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
+
+{\bf Small injection:}
+In this regime, the first and the fourth terms of Equation \eqref{eq:crossterm} are very similar, differing only in their covariance matrices.
+When the injected signal is very small compared to the data, their difference can be neglected.
+In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
+However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red), we see that this term is still large enough to have a significant
+impact. This is trivially demonstrated in the identity case (right plot) where even at small injects, large cross terms are 
 evident.
 
-{\bf Large injection}
+{\bf Large injection:}
 When the injected signal is much larger than the data-only power spectrum, the data-only components can 
 be neglected as many orders of magnitude smaller.
-As we can see from Figure  \ref{fig:sigloss_terms}, the cross terms are also small in comparison.
-Here only do we recover the ``loss'' injected simulated eor
-signal as planned.
-
-{\bf In between}
-When the injected signal is of a similar amplitude to the data by itself, the picture becomes murky.  We see that 
-the weighted injected power spectrum component mirrors the input power indicating little loss, eventually 
-departing from unity when the injected amplitude is well above the level of the data power spectrum. However 
-the cross terms have nearly the same amplitude, but a negative sign. The sum of the two is substantially lower and substantially drives down the $P_{\rm out}$ estimator.
+As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are also small in comparison.
+Here only do we recover the ``loss'' injected simulated EoR
+signal as intended (the black and green curves agree).
+
+{\bf In between:}
+When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
+the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
+departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
+the cross-terms have nearly the same amplitude, but with a negative sign.
+The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black).
+We note that in A15, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.
+Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in A15.
 
@@
 
-The source of the strong negative cross term is not immediately obvious, however it is an explainable effect. 
+The source of the strong negative cross-term is not immediately obvious, however it is an explainable effect. 
 When $\textbf{R}_{r}$
-is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the second term of Equation \eqref{eq:pout_expand} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
+is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the third term of Equation \eqref{eq:crossterm} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
 $\widehat{\textbf{C}}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
@@
 an eigenbasis of $\textbf{e}$, so that $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. 
-The middle 
+\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
 two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
-ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.  As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the
-inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle 
+ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
+As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
 off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. When $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
+terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
 the result is a vector that is similar to $\textbf{x}$ but
@@
 simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with foreground cleaning of Great Bank Telescope (GBT) data.
+This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
 Therefore, in our revised

### 2018-01-30 PAPER.tex
edited/cleaned up Danny's revisions in 3.1.2 and 3.1.3

@@
 One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections.
-A different realization of the test signal is injected with each bootstrap run causing the output to vary according to noise as well as whether the injected signal looks more or less ``like'' the data.
+A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
+behaves like noise) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
+how much coupling there is, which affects how much loss results).
 
@@
 \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
-Given our guess from section \ref{sec:siglossmethod}, that the change in power caused by the injection injection$P_{\rm out}$ is a good estimate of the injected EoR power $P_{\rm eor}$ we can write
+Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of the injected EoR power $P_{\rm eor}$, we can write
 
@@
 \noindent where $p(\phat_x)$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data + injection ($P_{\rm out}$) given the injection $P_{\rm in}$ evaluated at P.  We construct this distribution  
+as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  
 by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
 consistent with this power spectrum. The resulting distribution is normalized such that the sum is unity, and the 
-whole process can then be repeated for a different value of $P_{\rm in}$.  \dcj{am I right about the normalization?}
-
-\subsection{Implementation}
+whole process can then be repeated for a different value of $P_{\rm in}$.
+
+\subsubsection{Signal Loss Implementation Details}
+\label{sec:Implementation}
+
 The implementation details of the injection process require some more detailed explanation.
 In our code, we add a new realization to each independent bootstrap with the goal of simultaneously capturing variance due to noise and signal loss.
-To limit computing time we perform $20$ realizations of $P_{in}$, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$.
-We also run $25$ total EoR injection levels, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
+To limit computing time we perform $20$ realizations of each $P_{in}$ level.
+We also run $25$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
 $P_{\rm out}$ grid.
@@
 
-We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators\citep{scott2008kernel}. 
+We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators (\citealt{scott2008kernel}). 
 The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.  
 Although we only show figures for one $k$ value, we note that 
-the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).Bayes' rule 
-then simply instructs us compute $p(\phat_{x})$, multiply it horizontally across Figure 
-\ref{fig:sigloss_transfercurve} horizontally as defined in Equation \eqref{eq:Bayes} to get $p(P_{in})$. The final 
-result can then be normalized to give $p(P_{\rm eor} | \phat_{x})$. 
+the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately in computation). Bayes' rule 
+then simply instructs us compute $p(\phat_{x})$ and multiply it horizontally across Figure \ref{fig:sigloss_transfercurve} as defined in Equation \eqref{eq:Bayes} to get $p(P_{in})$.
+We then sum up all rows (vertically) and the final result can be normalized to give $p(P_{\rm eor} | \phat_{x})$.
 \dcj{Need to write down the normalization for \eqref{eq:Bayes}}
-The width of the distribution of  $\phat_{x}$ itself is defined as a  gaussian with the mean $\phat_{x}$ and 
-variance determined from the bootstrap process.
-
-Inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the result should be.  The peak of our data distribution $
+
+We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process, and we smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
+Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
+We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
+
+By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The peak of our data distribution $
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
@@
 value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$.
-Performing a summation and normalization for the entire distribution of $\widehat{\textbf{p}}_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
-\dcj{Normalization needs an equation}
+For the unweighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
 
@@
 Here the scatter, evident as deviations from unity-transfer, is entirely due to finite sample variance.
-To remove this effect we measure the width of this lossless case and then deconvolve that extra width from the likelihood for the lossy scenario.
-Specifically, we deconvolve Gaussian distributions of $P_{out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{in}$.
+To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
+Specifically, we de-convolve Gaussian distributions of $P_{\rm out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 
-The result is the loss-corrected power spectrum shown in Figure \ref{fig:ps2_data} which we can compare  to the original lossy result.
+The loss-corrected power spectrum result for inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (right plot), which we can compare to the original lossy result (left plot).
 There are a few important checks to examine.
-We see that the unweighted
-power spectrum $2\sigma$ upper limit is identical in both panels.
+First, we see that the unweighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
 This is an important check, as we expect no signal loss for this case.
 Any difference here would indicate an error in the pipeline or discrepancy in the range of data included.
-Prior to signal loss estimation, it
-is clear that the power spectrum is inconsistent with the (now revised) theoretical noise level prediction. 
+Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
 Post signal loss estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
 We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants with minimizing the loss of EoR signal.
+weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.
 
@@
 only the strongest $\sim3$-$4$ eigenmodes are down-weighted and the rest are given equal weights.
-For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2014}.
+For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
 

### 2018-01-30 PAPER.tex
added back in that the peak of p_x is from the no-bootstrapping case

@@
 
-We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process, and we smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
+We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
+We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
 Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.

### 2018-01-30 PAPER.tex
added paragraph about gaussian error in 2.2

@@
 systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g.
-\citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
+\citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011b}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
 An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
@@
 
-%A third option which acts as a middle ground between the other two is
-
-For PAPER's analysis, we choose to compute error bars that have been derived from the inherent 
+A third option which acts as a middle ground between purely theoretical and purely empirical errors is using Gaussian error.
+This involves the assumption of Gaussianity, but allows the variance of the power spectrum estimator to be written as a function of the two-point estimator, or covariance.
+One could empirically calculate the covariance and then propagate it into an analytic expression to compute the errors, making this method fall somewhere between fully empirical and fully modeled (see \citet{das_et_al2011a} for an example of its implementation).
+
+For PAPER's analysis, we choose a data-driven method of error estimation that does not rely on assumptions of Gaussianity. Namely, we compute error bars that have been derived from the inherent 
 variance of our measurements. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 

### 2018-01-30 PAPER.tex
fixed section ref

@@
 signal-only simulation (i.e. comparing an unweighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for correlations between the data and signal (Section \ref{sec:Illustration}).
+failing to account for correlations between the data and signal (Section \ref{sec:siglossmethod}).
 \item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 

### 2018-01-31 PAPER.tex
re-compiled updated plots

@@
 
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$.
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$.
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
@@
 \caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
-given injection level P$_{in}$.
+given injection level P$_{\rm in}$.
 The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
@@
 \includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
-\caption{The probability that an injected signal of level P$_{inj}$
+\caption{The probability that an injected signal of level P$_{\rm inj}$
 is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
@@
 
-Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of "data + 
+Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of ``data + 
 injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 

### 2018-01-31 PAPER.tex
changed normalization M's to non-italicized

@@
 \label{eq:Pin}
-P_{\rm in,\alpha} \equiv M^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha}-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
-&=& M^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x},
 \end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices $M$, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
+where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices M, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
 $P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal,
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &=& M^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
-M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
+\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + M^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&-& M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
+&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &= &  M^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&+& M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
+&+& \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&-& M^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
+&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
+&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
 ^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 \begin{eqnarray}
-P_{\rm in,\alpha} &=&  M^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  M^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
+P_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
 &&\phantom{=====} 
--  M^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
+-  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
 \end{eqnarray}

### 2018-01-31 PAPER.tex
cleaned up missing section references

@@
 \citestyle{aa}
+
+\defcitealias{ali_et_al2015}{A15}
 
@@
 toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
-from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as A15, which have led to a 
+from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a 
 revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.
@@
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
-previously underestimated in the A15 analysis.
+previously underestimated in the \citetalias{ali_et_al2015} analysis.
 
@@
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:Illustration}), which leads to loss.
+More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
 Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
@@
 %remove 
-avoid foregrounds, as done by A15, 
+avoid foregrounds, as done by \citetalias{ali_et_al2015}, 
 \citet{parsons_et_al2014}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{jacobs_et_al2015}, \citet{beardsley_et_al2016}, and \citet{trott_et_al2016}.
@@
 $k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
-window function to have a minimum response to low $k$ values. The window function used in A15 is constructed in such a way, 
+window function to have a minimum response to low $k$ values. The window function used in \citetalias{ali_et_al2015} is constructed in such a way, 
 specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
@@
 Determining the source of positive non-EoR detections at higher $k$'s is more difficult.
-In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (A15; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (\citetalias{ali_et_al2015}; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
 In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
@@
 We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
-A15 and obtain a revised power spectrum estimate.
+\citetalias{ali_et_al2015} and obtain a revised power spectrum estimate.
 
@@
 For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
-refer the reader to \citet{parsons_et_al2010} and A15. We note that all data processing steps are identical to those in A15 until after the LST-binning step in Figure 3 of A15.
+refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015}.
+We note that all data processing steps are identical to those in \citetalias{ali_et_al2015} until after the LST-binning step in Figure 3 of \citetalias{ali_et_al2015}.
 
@@
 
-The previously best published $21$ cm upper limit result from A15 uses $124$ nights of data to place a $2\sigma$ upper limit 
+The previously best published $21$ cm upper limit result from \citetalias{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit 
 on $\Delta^{2}(k)$, defined as
@@
 
-For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (A15 uses a slightly different RA 
+For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly different RA 
 range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
-MHz ($20$ channels), identical to the analysis in A15. We note that, besides using only one baseline type instead of the three as in 
-A15, the PAPER-64 dataset that we use in this case study differs from that in A15 only in the analysis.
+MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}. We note that, besides using only one baseline type instead of the three as in 
+\citetalias{ali_et_al2015}, the PAPER-64 dataset that we use in this case study differs from that in \citetalias{ali_et_al2015} only in the analysis.
 The most significant changes occur in the power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
-In A15, the
+In \citetalias{ali_et_al2015}, the
 applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
@@
 The exact amount of signal loss will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
-In this work, as in A15, we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
+In this work, as in \citetalias{ali_et_al2015}, we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
 As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
@@
 These two methods yield very similar results, but fundamentally are answering subtly distinct questions.
-We also highlight major differences from the signal loss computation used in A15, which previously underestimated losses.
+We also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
 
@@
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$
-cm signal visibilities. Here we use the same method as in A15, where mock Gaussian noise visibilities (mock EoR signals) 
+cm signal visibilities. Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals) 
 are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
-specific change from A15 is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
+specific change from \citetalias{ali_et_al2015} is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
 applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
@@
 likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in A15 (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
 
@@
 \begin{eqnarray}
-\label{eq:crossterm}
+\label{eq:crossterm_full}
 P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
@@
 The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black).
-We note that in A15, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in A15.
+We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.
+Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.
 
@@
 The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$.
-This is the exact term that was compared to $P_{\rm in}$ in the A15 signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
+This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
 It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
@@
 %The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-Again, it is this quantity that was used in A15 to calculate signal loss.
+Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
 However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
 In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
-Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to A15.
+Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
 
@@
 We show the contributions of each signal loss term (blue, red, green, gray), which when combined produce the black $P_{\rm out}$ curve.
-Most notably, the green curves denotes the signal loss analysis used in A15, and the red curves showcase the importance of the cross-terms in Equation \eqref{eq:crossterm} in computing signal loss.
+Most notably, the green curves denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in Equation \eqref{eq:crossterm} in computing signal loss.
 As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
-($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in A15 which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
+($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which, with an empirically estimated covariance, leads to substantial loss.
+With this weighting, our
 expressions for $P_{\rm in}$ and $P_{\rm out}$ become
@@
 not exhibit loss.
-The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:pout_expand}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
+The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:crossterm_full}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
 	\label{fig:sigloss_transfercurve}
@@
 noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than A15 by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
 \cc{replace with kolopanis limit instead later}
@@
 power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
-observational parameters. This power spectrum result differs from A15 in that it only uses data from one type of baseline ($30$ m 
+observational parameters. This power spectrum result differs from \citetalias{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m 
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
 loss, bootstrapping, and the theoretical error computation. From this, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than A15 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
+$k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
 	\label{fig:ps1_data}
@@
 
-In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the A15 
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the \citetalias{ali_et_al2015} 
 analysis of PAPER-64. While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power 
@@
 \end{equation}
-We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in A15.
+We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in \citetalias{ali_et_al2015}.
 
@@
 where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
-This is lower than the $T_{sys}$ of $500$ K used in A15 because of several small miscalculation errors that were 
+This is lower than the $T_{sys}$ of $500$ K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
 identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying independent `even' and `odd' visibility measurements (which is done principally to avoid a noise bias). In A15, a factor of $2$ was mistakenly used.
+estimates after cross-multiplying independent `even' and `odd' visibility measurements (which is done principally to avoid a noise bias).
+In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
 \item $N_{lst}$: The number of LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
@@
 taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
-\item $N_{days}$: The total number of days of data analyzed. In A15, this number was set to $135$. However, because we 
+\item $N_{days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
 divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
@@
 days.
-\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In A15, this number was 
+\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
 the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
@@
 \end{equation}
-\noindent where, for the A15 analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+\noindent where, for the \citetalias{ali_et_al2015} analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
 entering the group ($N_{bls\_total}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
@@
 
-Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of A15 in Figure \ref{fig:sense_check}. 
+Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of \citetalias{ali_et_al2015} in Figure \ref{fig:sense_check}. 
 Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.
@@
 published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
-\sqrt{3}$ for three baseline types is needed to match A15 exactly). Major factors that contribute to the discrepancy are $
+\sqrt{3}$ for three baseline types is needed to match \citetalias{ali_et_al2015} exactly). Major factors that contribute to the discrepancy are $
 \Omega_{eff}$, $N_{days}$ and $N_{bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-one major change in the way we estimate errors since A15, using the lesson we have learned about bootstrapping independent samples.
+one major change in the way we estimate errors since \citetalias{ali_et_al2015}, using the lesson we have learned about bootstrapping independent samples.
 
@@
 
-In A15, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
+In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
 ($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
@@
 effects of bootstrapping from signal loss.
-The bootstrapping method used in A15 in shown in gray, where bootstrapping occurs along both the baseline and time axes.
+The bootstrapping method used in \citetalias{ali_et_al2015} in shown in gray, where bootstrapping occurs along both the baseline and time axes.
 This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
@@
 
-Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and A15).
+Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and \citetalias{ali_et_al2015}).
 As alluded to in Section \ref{sec:SiglossOverview}, we
@@
 $k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
-contamination of foreground bias. This tailored window function was used in the A15 analysis, however for this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
+contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however for this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
 
@@
 We recognize that this method results in a hit to our sensitivity.
-Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the A15 analysis (which uses the same groupings), not produce the most sensitive limits of PAPER-64.
+Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the \citetalias{ali_et_al2015} analysis (which uses the same groupings), not produce the most sensitive limits of PAPER-64.
 
@@
 zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
-on power spectrum results is shown in A15. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
+on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
 removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
@@
 one baseline type, we quote a new $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
-A15 by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+\citetalias{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in A15, was under-estimated by a factor of $\sim$$1000$ for inverse 
+\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $\sim$$1000$ for inverse 
 covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
@@
 prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
-power spectrum result, implying that if taken at face value, the theoretical prediction for noise in A15 was too high for its data 
+power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
 points.
@@
 is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
-The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.
-\label{fig:Prob_vs_Pin}}
+The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.}
+\label{fig:Prob_vs_Pin}
 \end{figure}

### 2018-02-01 PAPER.tex
added comment
-Re-ran sigloss for PS plots -Pout = p_x syntax for eq 14&20

@@
 \begin{equation}
-P_{\rm out} = P_{\rm eor} \label{eqn:anzatz},
+P_{\rm out} = \widehat{\textbf{p}}_{x} \label{eqn:anzatz},
 \end{equation}
 and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
-signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
+signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing} Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
 
@@
 \phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
-Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of the injected EoR power $P_{\rm eor}$, we can write
+Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of $\p_{x}$, we can write
 
@@
 \label{eq:Bayes}
-p(P_{\rm eor} | \phat_{x}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
-  p(\phat_{x}) ,
-\end{equation}
-
-\noindent where $p(\phat_x)$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
+p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
+  p(P_{\rm out}) ,
+\end{equation}
+
+\noindent where $p(P_{\rm out})$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
 as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  

### 2018-02-06 PAPER.tex
language edits from unweighted -> uniform weighted

@@
 Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
-an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an unweighted case would use $
+an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an uniform-weighted case would use $
 \textbf{R} = \textbf{I}$, the identity matrix.
@@
 First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using OQE formalism and $\textbf{R} = \widehat{\textbf{C}}^{-1}$. 
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}. Also plotted in the figure are the unweighted ($\textbf{R} = \textbf{I}$) power spectrum of $
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}. Also plotted in the figure are the uniform-weighted($\textbf{R} = \textbf{I}$) power spectrum of $
 \textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
@@
 This is evident by noticing that the
-green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the unweighted EoR power spectrum.
+green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum.
 
@@
 where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices M, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-$P_{\rm in}$ represents the unweighted power spectrum of $\textbf{e}$, our simulated EoR signal,
+$P_{\rm in}$ represents the uniform-weighted power spectrum of $\textbf{e}$, our simulated EoR signal,
 $\widehat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\widehat{\textbf{p}}_{r}$ is the power spectrum of the
@@
 \end{eqnarray}
-Each of these terms is plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and unweighted ($\textbf{R}_{r} = \textbf{I}$).
+Each of these terms is plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
 We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the components of the signal loss transfer function, $P_{\rm out}$, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and unweighted case (right).
+	\caption{Illustration of the components of the signal loss transfer function, $P_{\rm out}$, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and uniform-weighted case (right).
 The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
@@
 As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
-Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the unweighted case.}
+Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
 	\label{fig:sigloss_terms}
@@
 
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution of $p( \p_{\rm eor} | 
-\phat_{x})$ for $\p_{\rm eor}$ given the uncorrected power spectrum estimate $\phat_{x}$.
+Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
+\phat_{x})$, which is the probability of $P_{\rm in}$ given the uncorrected power spectrum estimate $\phat_{x}$.
 Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of $\p_{x}$, we can write
@@
 p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
-  p(P_{\rm out}) ,
-\end{equation}
-
-\noindent where $p(P_{\rm out})$ is the probability of the measured value (given our error) and $\mathcal{L} $ is the likelihood function defined 
+  p(P_{\rm in}) ,
+\end{equation}
+
+\noindent where $\mathcal{L} $ is the likelihood function defined 
 as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  
@@
 value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$.
-For the unweighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
+For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
 
@@
 To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $P_{\rm out}$ in the unweighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
+Specifically, we de-convolve Gaussian distributions of $P_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right). The dotted black 
+heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
 diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
 From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
-for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the unweighted case does 
+for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the uniform-weighted case does 
 not exhibit loss.
@@
 There are a few important checks to examine.
-First, we see that the unweighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
+First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
 This is an important check, as we expect no signal loss for this case.
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post signal loss estimation, the power spectrum errors are higher than both the theory and unweighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
+Post signal loss estimation, the power spectrum errors are higher than both the theory and uniform-weighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
 We elaborate on this point in the next section, as well as investigate alternate
@@
 	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive points in black and negative points in gray, 
-with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the unweighted power 
+with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the uniform-weighted power 
 spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
@@
 eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
-that are down-weighted from zero (which is equivalent to identity-weighting, or the unweighted case) to $21$ (which is full inverse 
+that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is full inverse 
 covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
@@
 From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the unweighted case.
+We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
 
@@
 Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the unweighted case (dashed blue) and inverse variance 
+plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
 weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
@@
 
-In addition to our thermal noise prediction (green) and unweighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
+In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
 in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
@@
 \ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
-$2\sigma$ errors bars. Also plotted are the unweighted power spectrum upper limit (dashed blue) and theoretical prediction of 
+$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
 noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
@@
 	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
-negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the unweighted 
+negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the uniform-weighted 
 power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
@@
 \ref{fig:ps_noise}, where the black and gray points represent positive and negative power spectrum values, respectively (with 
-$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed blue line represents the unweighted power 
+$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed blue line represents the uniform-weighted power 
 spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
@@
 power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
-\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the unweighted power spectrum (also $2\sigma$ upper 
+\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper 
 limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
@@
 bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum estimates with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
-\ref{fig:data_errors}. The estimates are unweighted in order to disentangle the effects of bootstrapping from signal loss. As 
+\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
 shown in the figure, when more elements are drawn for each bootstrap than the number of 
@@
 	\caption{$2\sigma$ power spectrum errors (not upper limits) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (unweighted) is used in order to disentangle the 
+methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
 effects of bootstrapping from signal loss.
@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are very close or passing through zero).
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are passing through zero).
 We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
@@
 \item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
-signal-only simulation (i.e. comparing an unweighted vs. weighted power spectrum of EoR only) can underestimate loss by 
+signal-only simulation (i.e. comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
 failing to account for correlations between the data and signal (Section \ref{sec:siglossmethod}).
@@
 It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
-We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and unweighted data (right).
+We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right).
 The dotted black
@@
 with the method in this appendix at $95$\% confidence (red curve).
-Also shown are the upper limits of the unweighted power spectrum
+Also shown are the upper limits of the uniform-weighted power spectrum
 (blue dashed) and theoretical noise model (green).} 

### 2018-02-07 PAPER.tex
compiled with updated Fig17, and updated explanations of the 3 regimes

@@
 In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red), we see that this term is still large enough to have a significant
-impact. This is trivially demonstrated in the identity case (right plot) where even at small injects, large cross terms are 
-evident.
+However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
+It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black).
+We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
+This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
 
@@
 be neglected as many orders of magnitude smaller.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are also small in comparison.
-Here only do we recover the ``loss'' injected simulated EoR
-signal as intended (the black and green curves agree).
+As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green).
+Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e.
+the black and green curves agree).
+We again see that the cross-terms behave as noise at large injections in the inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.
 
@@
 The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
-We show the contributions of each signal loss term (blue, red, green, gray), which when combined produce the black $P_{\rm out}$ curve.
-Most notably, the green curves denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in Equation \eqref{eq:crossterm} in computing signal loss.
-As explained in the main text, the cross-terms can produce large, negative signal which represents the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
+We show the contributions of each signal loss term (blue, red, green, gray), which when combined via Equation \eqref{eq:crossterm} produce the black $P_{\rm out}$ curve.
+Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss.
+As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels.
+For the inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects).
+However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
+This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
 Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}

### 2018-02-08 PAPER.tex
typo

@@
 Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the first peak in Figure \ref{fig:toy_sigloss2}).
+For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
 In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.

### 2018-02-12 PAPER.tex
edited text about under-estimated errors being a smaller factor for data than for the noise sim

@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic prediction for noise.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
@@
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were under-estimated by a factor of $\sim$$1.4$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
+\item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim$$2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 

### 2018-02-12 PAPER.tex
moved adrian up on author list
quoted matt's best limit

@@
 Daniel C. Jacobs\altaffilmark{3}, 
-Saul A. Kohn\altaffilmark{4},
-Adrian Liu\altaffilmark{1,5}$^{,\dagger}$, 
+Adrian Liu\altaffilmark{1,4}$^{,\dagger}$, 
+Saul A. Kohn\altaffilmark{5},
 Jonathan C. Pober\altaffilmark{6}, 
-James E.~Aguirre\altaffilmark{4},
+James E.~Aguirre\altaffilmark{5},
 Zaki S. Ali\altaffilmark{1}, 
@@
 David H. E. MacMahon\altaffilmark{2},
-David F. Moore\altaffilmark{4},
+David F. Moore\altaffilmark{5},
 Chuneeta D. Nunhokee\altaffilmark{8},
@@
 \altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
-\altaffiltext{4}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
-\altaffiltext{5}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
+\altaffiltext{4}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
+\altaffiltext{5}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
 \altaffiltext{6}{Dept. of Physics, Brown University, Providence RI}
@@
 for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
-led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al., \textit{in prep}, mostly stems from an 
+led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al., \textit{submitted}, mostly stems from an 
 improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
@@
 More specifically, we develop new techniques for computing signal loss and under-go a rigorous re-analysis of PAPER-64 data in order to present a new power spectrum limit.
-A companion paper, Kolopanis et al., \textit{in prep}, builds off of the methods in this paper to present PAPER-64 results for multi-redshifts and multiple baselines.
+A companion paper, Kolopanis et al., \textit{submitted}, builds off of the methods in this paper to present PAPER-64 results for multi-redshifts and multiple baselines.
 
@@
 from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a 
-revised PAPER-64 power spectrum result (Kolopanis et al., \textit{in prep}). We conclude in Section \ref{sec:Con}.
+revised PAPER-64 power spectrum result (Kolopanis et al., \textit{submitted}). We conclude in Section \ref{sec:Con}.
 
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit (Kolopanis et al., \textit{in prep}) stems from previously underestimated signal loss and underestimated error bars, both of which we
+The revision of this limit (Kolopanis et al., \textit{submitted}) stems from previously underestimated signal loss and underestimated error bars, both of which we
 address in the following sections.
@@
 
-Our revised, best to-date PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
+A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
 \ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
 $2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
-noise (solid green). From this result, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, 
-a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim7$ in mK (though we only use one baseline type in our analysis as opposed to three). 
-\cc{replace with kolopanis limit instead later}
+noise (solid green).
+In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
 
@@
 East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
-loss, bootstrapping, and the theoretical error computation. From this, we quote a best $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at 
-$k=0.34$ $h$Mpc$^{-1}$, a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}.}
+loss, bootstrapping, and the theoretical error computation.
+In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
 	\label{fig:ps1_data}
@@
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{in prep}).
+we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{submitted}).
 
@@
 \item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
-analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{in prep}
+analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{submitted}
 use three separation types.
@@
 
-As a consequence of our investigations, we have also revised power spectrum results from PAPER-64. For an analysis of only 
-one baseline type, we quote a new $2\sigma$ upper limit of $(151.0$ mK$)^{2}$ at $k=0.34$ $h$Mpc$^{-1}$, a higher limit than 
-\citetalias{ali_et_al2015} by a factor of $\sim7$ in mK \cc{replace with kolopanis limit later}. The reasons for a previously underestimated limit and 
+As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
+In Kolopanis et al., (\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously underestimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim7$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
+factor of $\sim$$10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
 note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 

### 2018-03-09 PAPER.tex
edited fig 17 caption and compiled revised plot with p_r instead of p_out

@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the components of the signal loss transfer function, $P_{\rm out}$, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and uniform-weighted case (right).
+	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and uniform-weighted case (right).
 The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
-We show the contributions of each signal loss term (blue, red, green, gray), which when combined via Equation \eqref{eq:crossterm} produce the black $P_{\rm out}$ curve.
+We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$).
+The gray curve is the power spectrum value of data alone.
 Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss.

### 2018-03-09 PAPER.tex
updated fig 19 and fig 21 (PS plots) and captions, using sigloss v6

@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_nosigloss.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data.png}
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data (positive points in black and negative points in gray, 
-with $2\sigma$ error bars) before signal loss estimation (left) and after (right). The dashed blue line is the uniform-weighted power 
+	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
+with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
 spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.png}
-	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. Black and gray points correspond to positive and 
-negative power spectrum values, respectively, with $2\sigma$ error bars also plotted. The dashed blue line is the uniform-weighted 
+	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and 
+negative power spectrum values, respectively, with $2\sigma$ error bars).
+The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation.
+There is negligible loss using this regularization.
+The dashed blue line is the uniform-weighted
 power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 

### 2018-03-09 PAPER.tex
updated fig 18 with sigloss v6

@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{r}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$.
-From these plots, it is clear that inverse covariance weighting results in $\sim3$ orders of magnitude of signal loss
-for power spectrum values above $\sim$$2 \times 10^{4}$ $mK^{2} \, (h^{-1} \, Mpc)^{3}$, whereas the uniform-weighted case does 
-not exhibit loss.
-The peculiar `signal gain' tail seen at low injection is driven by the cross-terms in Equation \eqref{eq:crossterm_full}, also shown by the red curve in the right panel in Figure \ref{fig:sigloss_terms}.}
+heat-maps on top of the points for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted.
+From these plots, it is clear that inverse covariance weighting results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
+not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
 	\label{fig:sigloss_transfercurve}

### 2018-03-10 PAPER.tex
first cut at editing signal loss method text in 3.1

@@
 
-The results of such an injection scheme can be interpreted in multiple ways.
+We present our PAPER-64 signal loss investigation in three parts: we first give an overview of our injection framework and illustrate how different power spectrum components affect loss.
+We next describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
+Finally, we build off of Section \ref{sec:SiglossOverview} by experimenting with different regularization schemes on PAPER data in order to minimize loss.
+Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
+
+%The results of such an injection scheme can be interpreted in multiple ways.
 In this paper we describe two --- this section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
@@
 \label{eq:sigloss}
-P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha}-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
-&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r} - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
-^{\alpha}\textbf{R}_{x}\textbf{x},
+P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
+&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
 \end{eqnarray}
 where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices M, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-$P_{\rm in}$ represents the uniform-weighted power spectrum of $\textbf{e}$, our simulated EoR signal,
-$\widehat{\textbf{p}}_{x}$ is the power spectrum of the data alone, $\widehat{\textbf{p}}_{r}$ is the power spectrum of the
-data plus injection, and $P_{\rm out}$ is the difference between $\widehat{\textbf{p}}_{r}$ and $\widehat{\textbf{p}}_{x}$.
-In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
+$P_{\rm in}$ represents the uniform-weighted power spectrum of $\textbf{e}$, our simulated EoR signal, and $\widehat{\textbf{p}}_{r}$ is the power spectrum of the
+data plus injection. \cc{explain why we evaluate $P_{out}$ at $p_{r}$}
+%In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
 the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
@@
 
-\begin{equation}
-P_{\rm out} = \widehat{\textbf{p}}_{x} \label{eqn:anzatz},
-\end{equation}
-and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
-signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing} Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
+%\begin{equation}
+%P_{\rm out} = \widehat{\textbf{p}}_{x} \label{eqn:anzatz},
+%\end{equation}
+%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
+%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}
+
+Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
 
@@
 \label{eq:crossterm_full}
-P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) - 
-\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
+P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
+%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
 &=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
-^{\alpha}\textbf{R}_{x}\textbf{x}.
+&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
+%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \nonumber \\
-&+& \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}
-^{\alpha}\textbf{R}_{x}\textbf{x}.
+&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
+%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
 \end{eqnarray}
-Each of these terms is plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
+In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
 We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
@@
 {\bf Small injection:}
-In this regime, the first and the fourth terms of Equation \eqref{eq:crossterm} are very similar, differing only in their covariance matrices.
-When the injected signal is very small compared to the data, their difference can be neglected.
-In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
+In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
+They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
+This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}.
+In this regime, we also note that the cross-terms (red) behave as noise, even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
+This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
 However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
@@
 {\bf Large injection:}
-When the injected signal is much larger than the data-only power spectrum, the data-only components can 
+When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
 be neglected as many orders of magnitude smaller.
@@
 With this weighting, our
-expressions for $P_{\rm in}$ and $P_{\rm out}$ become
+expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
 
@@
 P_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r} \nonumber \\
-&&\phantom{=====} 
--  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
+P_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
+%&&\phantom{=====} 
+%-  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
 \end{eqnarray}
@@
 
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
+\cc{need edits in this section} Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
 \phat_{x})$, which is the probability of $P_{\rm in}$ given the uncorrected power spectrum estimate $\phat_{x}$.
-Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out}$ is a good estimate of $\p_{x}$, we can write
+Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out} \equiv \widehat{\textbf{p}}_{r}$ is a good estimate of $\p_{x}$, we can write
 
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=P_{\rm x}}
+p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=\widehat{\textbf{p}}_{x}}
   p(P_{\rm in}) ,
@@
 
-\subsubsection{Signal Loss Implementation Details}
-\label{sec:Implementation}
+%\subsubsection{Signal Loss Implementation Details}
+%\label{sec:Implementation}
 
 The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization to each independent bootstrap with the goal of simultaneously capturing variance due to noise and signal loss.
+In our code, we add a new realization of EoR to each independent bootstrap of data with the goal of simultaneously capturing variance due to noise and signal loss.
 To limit computing time we perform $20$ realizations of each $P_{in}$ level.
-We also run $25$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$, resulting in a total of $500$ data points on our $P_{\rm in}$ vs.
+We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
 $P_{\rm out}$ grid.
-%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
-
-We smooth the 2D distribution of $P_{in}$ vs. $P_{out}$ using kernel density estimators (\citealt{scott2008kernel}). 
-The result, for inverse covariance weighting, is shown in the left plot of Figure \ref{fig:sigloss_transfercurve}.  
-Although we only show figures for one $k$ value, we note that 
-the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately in computation). Bayes' rule 
-then simply instructs us compute $p(\phat_{x})$ and multiply it horizontally across Figure \ref{fig:sigloss_transfercurve} as defined in Equation \eqref{eq:Bayes} to get $p(P_{in})$.
-We then sum up all rows (vertically) and the final result can be normalized to give $p(P_{\rm eor} | \phat_{x})$.
-\dcj{Need to write down the normalization for \eqref{eq:Bayes}}
-
-We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
+
+Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$.
+For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one.
+Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for inverse covariance weighting (left) and uniform weighting (right).
+Although we only show figures for one $k$-value, we note that
+the shape of the transfer curve is nearly identical for all $k$'s.
+This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
+We then simply take a horizontal cut across at the data value $\widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
+We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
+
+%We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
 We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
@@
 
-By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The peak of our data distribution $
+By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
@@
 
-As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
+%As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
 Ideally, running many simulations would lead to convergence; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
@@
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
-look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
+%look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
 As an extreme example, if we are very unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
@@
 
-The loss-corrected power spectrum result for inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (right plot), which we can compare to the original lossy result (left plot).
-There are a few important checks to examine.
+The loss-corrected power spectrum result for inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
+%There are a few important checks to examine.
 First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post signal loss estimation, the power spectrum errors are higher than both the theory and uniform-weighted power spectrum, a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
+Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed), a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
 We elaborate on this point in the next section, as well as investigate alternate

### 2018-03-10 PAPER.tex
updated jackknife plot

@@
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{5} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
-value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim1000$.
+From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
+value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$.
 For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
@@
 	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
-	\caption{Results for three null tests compared to analytically estimated 
-$2\sigma$ errors (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
+	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
+$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
 even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations ($95\%$ of the error bars are passing through zero).
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero).
 We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
@@
 The null test in LST is much more illuminating.
-Because of the large error bars and variation in its result, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
+Because of the large variable error bars, many of which do not include zero, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
 estimated error region is LST-dependent, and therefore likely to be residual foregrounds.

### 2018-03-12 PAPER.tex
small text change

@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum estimates with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.png}
-	\caption{$2\sigma$ power spectrum errors (not upper limits) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
+	\caption{$2\sigma$ power spectrum errors for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
 methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
@@
 
+\begin{comment}
 \section{Simplified Loss Correction}
@@
 
+\end{comment}
+
 \bibliographystyle{apj}

### 2018-03-14 PAPER.tex
First crack at revising the signal loss methods section to reflect the fact that we are now using P_r

@@
 \label{sec:siglossmethod}
-In short, our method consists of injecting an EoR-like signal into the data and then measuring the amount recovered, with the difference being accounted as signal loss.
+In short, our method consists of injecting an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$
@@
 \begin{equation}
+\label{eq:rxe}
 \textbf{r} = \textbf{x} + \textbf{e}.
@@
 where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices M, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-$P_{\rm in}$ represents the uniform-weighted power spectrum of $\textbf{e}$, our simulated EoR signal, and $\widehat{\textbf{p}}_{r}$ is the power spectrum of the
-data plus injection. \cc{explain why we evaluate $P_{out}$ at $p_{r}$}
+
+The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
+Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
+The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
+This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments.
+In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
+In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds.
+To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants.
+Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
+\cc{explain why we evaluate $P_{out}$ at $p_{r}$} \acl{Added! See how you like it}
 %In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
@@
 
-Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
+Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
 
@@
 \end{eqnarray}
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
+In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: \acl{can we go through and add the word ``empirical"?
+The phrase ``inverse covariance weight" should be reserved for when one is weighting by the true inverse covariance.} inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
 We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
@@
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
-Therefore, in our revised
+\acl{The following line is no longer true}Therefore, in our revised
 signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
@@
 
+{\bf In general:} Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
+However, the normalization matrix $\mathbf{M}$ is generally derived assuming that the unnormalized estimator is quadratic in the data.
+Thus, neglecting couplings between data and its weightings causes power spectrum estimates to be incorrectly normalized.
+As argued in this section, the resulting bias will tend to bias the results \emph{low}, which is simply another way of describing signal loss.
+
 \subsubsection{Signal Loss in Practice}
@@
 
-We now shift our attention towards computing signal loss for the fringe-rate filtered PAPER-64 dataset. While our methodology 
+We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
 outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
@@
 
-\cc{need edits in this section} Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
-\phat_{x})$, which is the probability of $P_{\rm in}$ given the uncorrected power spectrum estimate $\phat_{x}$.
-Given our ansatz from Section \ref{sec:siglossmethod} that $P_{\rm out} \equiv \widehat{\textbf{p}}_{r}$ is a good estimate of $\p_{x}$, we can write
+\cc{need edits in this section} \acl{Done!} Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
+P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives
 
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto \evalat[\Bigg]{\mathcal{L} (  P_{\rm out} | P_{\rm in})}{P_{\rm out}=\widehat{\textbf{p}}_{x}}
+p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
   p(P_{\rm in}) ,
@@
 \noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$, evaluated at the data level $\phat_x$.  We construct this distribution  
+as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
 by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum is unity, and the 
-whole process can then be repeated for a different value of $P_{\rm in}$.
+consistent with this power spectrum. The resulting distribution is normalized such that the sum over $P_{\rm out}$ is unity, and the 
+whole process is then repeated for a different value of $P_{\rm in}$.
 
@@
 Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for inverse covariance weighting (left) and uniform weighting (right).
-Although we only show figures for one $k$-value, we note that
+\acl{Why not use $P_{\rm out}$ on the vertical axes of these plots?} Although we only show figures for one $k$-value, we note that
 the shape of the transfer curve is nearly identical for all $k$'s.
 This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-We then simply take a horizontal cut across at the data value $\widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
+After multiplying by the prior \acl{right?}, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

### 2018-03-14 PAPER.tex
went through Adrian's edits and made his proposed suggestions

@@
 Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
-\cc{explain why we evaluate $P_{out}$ at $p_{r}$} \acl{Added! See how you like it}
+
 %In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
@@
 \end{eqnarray}
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: \acl{can we go through and add the word ``empirical"?
-The phrase ``inverse covariance weight" should be reserved for when one is weighting by the true inverse covariance.} inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
+In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirical inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
 We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
@@
 This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}.
-In this regime, we also note that the cross-terms (red) behave as noise, even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
+In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
 This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
@@
 the black and green curves agree).
-We again see that the cross-terms behave as noise at large injections in the inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.
+We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.
 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and uniform-weighted case (right).
+	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the empirical inverse covariance weighted case (left) and uniform-weighted case (right).
 The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
@@
 As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels.
-For the inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects).
+For the empirical inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects).
 However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
-This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case).
+This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the empirical inverse covariance weighted case).
 Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
@@
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
-\acl{The following line is no longer true}Therefore, in our revised
-signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
+Therefore, in our revised
+signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
 weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
@@
 We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
-outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
+outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
 ($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which, with an empirically estimated covariance, leads to substantial loss.
@@
 
-\cc{need edits in this section} \acl{Done!} Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
+Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
 P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives
@@
 For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one.
-Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for inverse covariance weighting (left) and uniform weighting (right).
-\acl{Why not use $P_{\rm out}$ on the vertical axes of these plots?} Although we only show figures for one $k$-value, we note that
+Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for empirical inverse covariance weighting (left) and uniform weighting (right).
+Although we only show figures for one $k$-value, we note that
 the shape of the transfer curve is nearly identical for all $k$'s.
 This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-After multiplying by the prior \acl{right?}, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal.
+After multiplying by the prior, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
+From the left plot (empirical inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
 value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$.
@@
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps on top of the points for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
+heat-maps on top of the points for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
 diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that inverse covariance weighting results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
+From these plots, it is clear that the weighted case results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
 not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
@@
 
-The loss-corrected power spectrum result for inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
+The loss-corrected power spectrum result for empirical inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
 %There are a few important checks to examine.
@@
 We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.
+weighting schemes to empirical inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
+	\caption{Empirical inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
 with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
@@
 The grey and black lines represent power spectrum limits pre and post signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
-When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to full inverse covariance weighting.
+When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to the empirical inverse covariance weighted case.
 From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss.
@@
 covariance weighting).
-Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting.
+Over $\sim3$ orders of magnitude of signal loss results when using empirical inverse covariance weighting.
 Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
 This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e.
-full inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
+empirical inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
 Also
@@
 It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
-We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right).
+We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right).
 The dotted black

### 2018-03-14 PAPER.tex
injection is less well defined. use adding instead

@@
 \label{sec:siglossmethod}
-In short, our method consists of injecting an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
+In short, our method consists of adding an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$

### 2018-03-14 PAPER.tex
Removed "small injection" discussion now irrelevant with Pout=Pr interpretation.  Added sentence about model for cross term

@@
 {\bf Small injection:}
-In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
+%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
 They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
-This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}.
-In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
+%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
+In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
+Output values are gaussian distributed around zero, spanning a range of values set by the injection level.
+This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
+In fact, for the unweighted case, the cross term is well modeled by $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}=\sqrt{p_e}\sqrt{p_x}$ %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
 However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.

### 2018-03-15 PAPER.tex
output not outputted

@@
 The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments.
+This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
 In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.

### 2018-03-15 PAPER.tex
Wording in descriptions of Pout regimes.

@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the unweighted case, the cross term is well modeled by $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}=\sqrt{p_e}\sqrt{p_x}$ %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
+In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
 However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
@@
 {\bf Large injection:}
-When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
+When the injected signal is much larger than the measured power spectrum, the data-only components can 
 be neglected as many orders of magnitude smaller.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green).
-Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e.
-the black and green curves agree).
-We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.
+This regime is somewhat academic given that, in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal.
+However it is useful as a check of our system in a relatively simple case.
+As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term.
+Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output.
+We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
+This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
+The cross correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.
 
@@
 departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-the cross-terms have nearly the same amplitude, but with a negative sign.
-The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black).
+the cross-term has nearly the same amplitude, but with a negative sign.
+As explained below, this negativity is the result of cross correlating inverse covariance weighted things.
+This negative component drives down the $P_{\rm out}$ estimator (black).
 We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.

### 2018-03-15 PAPER.tex
revamping sigloss terms caption

@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the empirical inverse covariance weighted case (left) and uniform-weighted case (right).
-The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
-We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$).
-The gray curve is the power spectrum value of data alone.
-Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss.
-As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels.
-For the empirical inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects).
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
-This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the empirical inverse covariance weighted case).
-Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
+	\caption{Illustration of the power spectrum amplitude as a function of injected power level summed into the 
+data. The net output ($P_{out}=P_r$) is shown in black, the individual cross terms, as defined by Equation 
+\eqref{eq:crossterm},  are shown in blue, red, green; the dotted line indicates 1:1 input to output mapping.  The 
+empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and uniform-weighted 
+case on the right. The details of the simulation used to generate the figure is explained in Section 
+\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.   The gray 
+line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
+component is also the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
+than the net output because the cross terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
+regime where cross correlation between injection and data are not dominant, the cross-terms have a noise-like 
+term with width $\sqrt{P_e}$. However, at power levels comparable to the data (the middle region), the cross-
+terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
+$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
+the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for 
+the empirical inverse covariance weighted case). }
 	\label{fig:sigloss_terms}

### 2018-03-15 PAPER.tex
Possibly objectionable footnote

@@
 ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle
+As shown in Appendix C of \citet{parsons_et_al2014}\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller

### 2018-03-15 PAPER.tex
Rejigger Adrians note about how loss is really a normalization issue.

@@
 
-{\bf In general:} Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
-However, the normalization matrix $\mathbf{M}$ is generally derived assuming that the unnormalized estimator is quadratic in the data.
-Thus, neglecting couplings between data and its weightings causes power spectrum estimates to be incorrectly normalized.
-As argued in this section, the resulting bias will tend to bias the results \emph{low}, which is simply another way of describing signal loss.
+{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
+Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
+However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
+The power spectrum estimate will also be incorrectly normalized which manifests as signal loss.
+We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics
 

### 2018-03-15 PAPER.tex
Commenting a repeat statement.

@@
 
-The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
+%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
 Therefore, in our revised
-signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
-weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
+%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
+%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 

### 2018-03-15 PAPER.tex
Variation due between EoR injection realization is not noise, its most like cosmic variance or something.
Slight elaboration in the Bayes intro

@@
 A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
-behaves like noise) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
+cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
 how much coupling there is, which affects how much loss results).
@@
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
-P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives
+P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
+Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know, in other words,
 
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
+p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})},
   p(P_{\rm in}) ,

### 2018-03-15 PAPER.tex
Pedogogic repeat of our argument that Pout is a model of Px so therefor the Posterior should be evaluated at Pout=Px.

@@
 This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-After multiplying by the prior, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal.
+We invoke the Bayes interpretation and re-interpret as it as the posterior $P(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data and make a horizontal cut across at the data value $P_{\rm out} = P_{\rm x}$ to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

### 2018-03-15 PAPER.tex
Making caption consistent with elsewhere. Pout instead of Pr in figures.

@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{r}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.

### 2018-03-15 PAPER.tex
changed optimal weighting case to 2% Tr(C) instead of 4%

--- 2018-03-15 PAPER.tex
@@
 \label{sec:siglossmethod}
-In short, our method consists of adding an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
+In short, our method consists of injecting an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$
@@
 The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
+This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments.
 In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
@@
 {\bf Small injection:}
-%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
+In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
 They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
-%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
-In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
-Output values are gaussian distributed around zero, spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
-%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
+This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}.
+In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
+This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
 However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
@@
 {\bf Large injection:}
-When the injected signal is much larger than the measured power spectrum, the data-only components can 
+When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
 be neglected as many orders of magnitude smaller.
-This regime is somewhat academic given that, in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal.
-However it is useful as a check of our system in a relatively simple case.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term.
-Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
-This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.
+As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green).
+Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e.
+the black and green curves agree).
+We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.
 
@@
 departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-the cross-term has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross correlating inverse covariance weighted things.
-This negative component drives down the $P_{\rm out}$ estimator (black).
+the cross-terms have nearly the same amplitude, but with a negative sign.
+The sum of the two is substantially lower and therefore drives down the $P_{\rm out}$ estimator (black).
 We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the power spectrum amplitude as a function of injected power level summed into the 
-data. The net output ($P_{out}=P_r$) is shown in black, the individual cross terms, as defined by Equation 
-\eqref{eq:crossterm},  are shown in blue, red, green; the dotted line indicates 1:1 input to output mapping.  The 
-empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and uniform-weighted 
-case on the right. The details of the simulation used to generate the figure is explained in Section 
-\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.   The gray 
-line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
-component is also the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
-than the net output because the cross terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
-regime where cross correlation between injection and data are not dominant, the cross-terms have a noise-like 
-term with width $\sqrt{P_e}$. However, at power levels comparable to the data (the middle region), the cross-
-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
-$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for 
-the empirical inverse covariance weighted case). }
+	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the empirical inverse covariance weighted case (left) and uniform-weighted case (right).
+The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves.
+We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$).
+The gray curve is the power spectrum value of data alone.
+Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss.
+As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels.
+For the empirical inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects).
+However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
+This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the empirical inverse covariance weighted case).
+Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
 	\label{fig:sigloss_terms}
@@
 ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle
+As shown in Appendix C of \citet{parsons_et_al2014}, to leading order the inversion of a matrix like $\widehat{\textbf{C}}_{r}$ that is diagonal-dominant (from $\langle
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
@@
 
-%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
+The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
+simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
 Therefore, in our revised
-%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
-%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
+signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
+weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
 
@@
 
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
-Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
-However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
-The power spectrum estimate will also be incorrectly normalized which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics
+{\bf In general:} Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
+However, the normalization matrix $\mathbf{M}$ is generally derived assuming that the unnormalized estimator is quadratic in the data.
+Thus, neglecting couplings between data and its weightings causes power spectrum estimates to be incorrectly normalized.
+As argued in this section, the resulting bias will tend to bias the results \emph{low}, which is simply another way of describing signal loss.
 
@@
 A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
-cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
+behaves like noise) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
 how much coupling there is, which affects how much loss results).
@@
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
-P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know, in other words,
+P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives
 
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})},
+p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
   p(P_{\rm in}) ,
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.02Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
 	\label{fig:sigloss_modeloop}
@@
 when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.04Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.02Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
 We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e.
 it doesn't throw away some information as in the other cases) but re-weights them in a way that produces minimal loss.
+In this paper, we use this weighting scheme as a simple regularization demonstration, though we note that in Kolopanis et al., (\textit{submitted}) we choose the most optimal regularization parameter for our final limits.
 
 A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
-\ref{fig:ps1_data}. Again, black and gray points correspond to positive and negative power spectrum values respectively, with 
+\ref{fig:ps1_data}.
+Again, the dashed black curve represents our upper limit on EoR, post-signal loss estimation.
+Black and gray points correspond to positive and negative power spectrum values respectively (pre-signal loss estimation), with
 $2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 

### 2018-03-15 PAPER.tex
went through danny's changes and made some small typo edits

@@
 In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+We also note that in this regime, $\widehat{\textbf{p}}_{r}$ approaches the data level as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
@@
 the cross-term has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross correlating inverse covariance weighted things.
+As explained below, this negativity is the result of cross correlating inverse covariance weighted terms.
 This negative component drives down the $P_{\rm out}$ estimator (black).
@@
 	\caption{Illustration of the power spectrum amplitude as a function of injected power level summed into the 
-data. The net output ($P_{out}=P_r$) is shown in black, the individual cross terms, as defined by Equation 
+data. The net output ($P_{out}=P_r$) is shown in black, the individual cross-terms, as defined by Equation 
 \eqref{eq:crossterm},  are shown in blue, red, green; the dotted line indicates 1:1 input to output mapping.  The 
-empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and uniform-weighted 
-case on the right. The details of the simulation used to generate the figure is explained in Section 
+empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and the uniform-weighted 
+case is on the right. The details of the simulation used to generate the figure is explained in Section 
 \ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.   The gray 
@@
 component is also the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
-than the net output because the cross terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
-regime where cross correlation between injection and data are not dominant, the cross-terms have a noise-like 
-term with width $\sqrt{P_e}$. However, at power levels comparable to the data (the middle region), the cross-
-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect 
+than the net output because the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
+regime where cross-correlation between injection and data are not dominant, the cross-terms have a noise-like 
+term with width $\sqrt{p_e}$.
+However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
 $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
@@
 However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
-The power spectrum estimate will also be incorrectly normalized which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics
+The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss.
+We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
 
@@
 P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know, in other words,
+Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know.
+In other words,
 
@@
 This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-We invoke the Bayes interpretation and re-interpret as it as the posterior $P(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data and make a horizontal cut across at the data value $P_{\rm out} = P_{\rm x}$ to yield a posterior distribution for the signal.
+We invoke the Bayes interpretation and re-interpret it as the posterior $P(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
+We then make a horizontal cut across at the data value $P_{\rm out} = \widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

### 2018-03-16 PAPER.tex
edited caption of Fig 25

@@
 
-%In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
+%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
 the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
@@
 %which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
-%small sample size limited to first order perturbations and thus neglects cross correlation between $x$ and $e$.  
+%small sample size limited to first order perturbations and thus neglects cross-correlation between $x$ and $e$.  
 %In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
@@
 \dcj{Here is the post-hoc justification for this signal loss method.
-Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross terms in the estimation of a power spectrum.
+Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum.
 So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}.
@@
 The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
-Note that this expectation includes allowances for signal loss due to the cross correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
+Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
 %\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
@@
 %I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-%then explaining in the next section exactly how cross terms were what messed us up in the first go round.} 
+%then explaining in the next section exactly how cross-terms were what messed us up in the first go round.} 
 %\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the unweighted case, the cross term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+In fact, for the uniform weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
 We also note that in this regime, $\widehat{\textbf{p}}_{r}$ approaches the data level as expected.
@@
 be neglected as many orders of magnitude smaller.
-This regime is somewhat academic given that, in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal.
+We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e.
+in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal).
 However it is useful as a check of our system in a relatively simple case.
@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.
+The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.
 
@@
 
-%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross terms don't matter when injected signal is very large.}
+%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
 %We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
-	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
-$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
-even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
-We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
+	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
+	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
+	\caption{Power spectrum results (with $2\sigma$ errors) for two null tests, where a jackknife is taken along the LST axis (left) and baseline axis (right).
+The results shown are unweighted.
+The gray shaded region is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
+We find that there are no significant systematics that differ between the two tests, though the $k$-dependence of the errors suggest that we are dominated by residual foregrounds near the horizon.}
 	\label{fig:null}
 \end{figure*}
+
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
+%	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
+%$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
+%even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
+%We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
+%	\label{fig:null}
+%\end{figure*}
 
@@
 \section{Acknowledgements}
-CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research 
-Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA 
+CC would like to acknowledge the UC Berkeley Chancellor's Fellowship and National Science Foundation Graduate Research 
+Fellowship (Division of Graduate Education award 1106400). She would also like to thank Eric Switzer, Miguel Morales, and Bryna Hazelton for helpful discussions. PAPER and HERA 
 are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
@@
 data only) and very large levels are dominated by the injected signal.
-It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
+It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross-correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
 

### 2018-03-18 PAPER.tex
fixed sqrt(p_e)*sqrt(p_x) in large injection description
updated plots and captions with latest sigloss runs

@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}$.
+The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.png}
-	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The weighted 
+	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The original weighted 
 power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
-\widehat{\textbf{C}}_{eff}$ to minimize signal loss. The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper 
+\widehat{\textbf{C}}_{eff}$ to minimize signal loss.
+The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation.
+The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper
 limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
-estimates agree (the analytic curve should encompass $95\%$ of the points).}
+estimates agree.}
 	\label{fig:ps_noise}

### 2018-03-20 PAPER.tex
edited plot and caption of Fig 25 - null test

@@
 	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
-	\caption{Power spectrum results (with $2\sigma$ errors) for two null tests, where a jackknife is taken along the LST axis (left) and baseline axis (right).
+	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
+	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the LST axis (top left), baseline axis (top right), and even/odd Julian date axis (bottom).
 The results shown are unweighted.
-The gray shaded region is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics that differ between the two tests, though the $k$-dependence of the errors suggest that we are dominated by residual foregrounds near the horizon.}
+The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
+We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to thermal noise squaring).
+All three tests are dominated by residual foregrounds at $k$-values near the horizon, which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
 	\label{fig:null}

### 2018-03-20 PAPER.tex
updated PS plots using 3.5% Tr(C) case

@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.02Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.035Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
 	\label{fig:sigloss_modeloop}
@@
 when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.02Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
 We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e.

### 2018-03-20 PAPER.tex
first pass at revised jackknife text

@@
 
-The highest sensitivity power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in 
-Figure \ref{fig:ps1_data}, has positive biases at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these detections 
+The power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in 
+Figure \ref{fig:ps1_data}, is biased above the predicted noise level, particularly at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these biases
 are most likely attributable to foreground leakage.
-The cause for the detections at higher $k$ values is more difficult to pinpoint.
-Here we demonstrate three null tests performed on PAPER-64 data that aim to explain these detections and verify
+The cause for biases at higher $k$ values is more difficult to pinpoint.
+Here we demonstrate three null tests performed on PAPER-64 data that aim to isolate systematics in the data and verify
 that they are not attributable to EoR.
 
-The three null test results are shown in Figure \ref{fig:null}, with each test described as the following:
+The three null test results are shown in Figure \ref{fig:null}, with each test displaying the differenced power spectrum between two halves of a jackknife.
+We take jackknives along three different axes, described as the following:
 
@@
 There are clear detections at low $k$'s.
-\item Even/Odd (blue): We split our dataset into even (\textbf{e}) and odd (\textbf{o}) days. We then form the following two datasets: $\textbf{x}_{1} = \textbf{e} + \textbf{o}$ and $\textbf{x}_{2} = 
-\textbf{e} - \textbf{o}$. We form datasets in this way to ensure that we use the full sensitivity of our data. When cross-multiplied, we obtain:
-\begin{equation}
-\textbf{x}_{1}\textbf{x}_{2}^{\dagger} = \textbf{ee}^{\dagger} - \textbf{eo}^{\dagger} + \textbf{oe}^{\dagger} - \textbf{oo}^{\dagger}
-\end{equation}
-If the same sky signal is in both the even and odd datasets, we expect it to cancel out.
+\item Even/Odd (blue): We split our dataset into even and odd Julian days.
+We form power spectra for each separately, allowing for the cross-multiplication of `even' with `even', for example.
+Although we don't allow this in our standard pipeline, we include these same-dataset cross-multiplications to allow a power spectrum to be estimated from solely the `even' data (similarly for `odd').
+If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out.
 \item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the 
-analysis. Again, we form $\textbf{x}_{1} = \textbf{b}_{1} + \textbf{b}_{2}$ and $\textbf{x}_{2} = \textbf{b}_{1} - \textbf{b}_{2}$, where $\textbf{b}_{1}$ is the first baseline 
-group and $\textbf{b}_{2}$ is the second baseline group.
-\item LST (magenta): We split our dataset into two halves based on LST, namely $\textbf{t}_{1}$ (LSTs 0.5-4.6 hours) and $\textbf{t}_{2}$ (LSTs 
-4.6-8.6 hours). We form our two datasets as $\textbf{x}_{1} = \textbf{t}_{1} + \textbf{t}_{2}$ and $\textbf{x}_{2} = \textbf{t}_{1} -\textbf{t}_{2}$.
+analysis. There are no baselines repeated between the two datasets.
+\item LST (magenta): We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
+4.6-8.6 hours).
 \end{itemize}
@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero), and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero).
+Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero).
+Additionally, the differenced power spectrum values (black points) all lie within the gray-shaded estimated error region for high $k$'s.
+Therefore, we conclude that particular baselines are not to be blamed for systematics in our dataset.
+
+For the LST test, $90\%$ of the error bars pass through zero, which is slightly low given the expected $95\%$.
+Additionally, not all power spectrum points lie within the gray-shaded region, even at high-$k$.
+This LST-dependent systematic is likely caused by residual foregrounds that vary in LST.
+In other words, the two jackknife halves differ by an amount greater than thermal noise and do not effectively cancel out the sky signal when differencing.
+
+The even/odd test shows $81\%$ of error bars being consistent with zero, with several power spectrum points falling outside the estimated error region.
+Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test).
+This strengthens our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.
+
+Finally, we note that all three null tests exhibit error bars that are strongly $k$-dependent.
+The errors are largest near the horizon, which is expected since foregrounds are brightest in this region post-delay filtering.
+We also note that all three tests result in power spectrum errors that are larger than the estimated thermal noise, even at high-$k$.
+There are a couple possible explanations for this.
+Although we expect each cross-multiplication to have independent noise (except in the even/odd case), there is still the possibility of a noise-foreground coupling term that can introduce power.
+This cross-term would vary with foreground strength, therefore being consistent with the shape of the results.
+Alternatively, our estimate of the thermal noise may be too low, as all three tests seem to imply a larger, but consistent, estimate.
+
+%, and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero).
 We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
 
-The null test in LST is much more illuminating.
+%The null test in LST is much more illuminating.
 Because of the large variable error bars, many of which do not include zero, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
-estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
+%estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
 In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and
-$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+%$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
 We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
 
-We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
-similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
-the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
-This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
-bias we see comes from foregrounds. % in regions where we expect leakage.
+%We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
+%similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
+%the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
+%This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
+%bias we see comes from foregrounds. % in regions where we expect leakage.
 

### 2018-03-21 PAPER.tex
-compiled with new PS plots (sigloss v7) -edited jackknife text

@@
 former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
-dataset is divided into two halves: even julian dates and odd julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
+dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
 the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
@@
 
-The power spectrum result for PAPER-64 using the updated analysis presented in this paper, shown in 
-Figure \ref{fig:ps1_data}, is biased above the predicted noise level, particularly at low $k$ values. As discussed in Section \ref{sec:BiasTypes}, these biases
-are most likely attributable to foreground leakage.
+As shown in Figure \ref{fig:ps1_data}, our re-analysis of the PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low $k$ values.
+As discussed in Section \ref{sec:BiasTypes}, this bias is
+most likely attributable to foreground leakage.
 The cause for biases at higher $k$ values is more difficult to pinpoint.
-Here we demonstrate three null tests performed on PAPER-64 data that aim to isolate systematics in the data and verify
+Here we discuss three null tests performed on PAPER-64 data that aim to isolate systematics in the data and verify
 that they are not attributable to EoR.
-
-The three null test results are shown in Figure \ref{fig:null}, with each test displaying the differenced power spectrum between two halves of a jackknife.
-We take jackknives along three different axes, described as the following:
+We build off of the framework in Section \ref{sec:JackknifeOverview}, which illuminated how jackknife tests can tease out excess variances along different axes of a dataset.
+
+Three null test results are shown in Figure \ref{fig:null}. Each test displays the differenced power spectrum between two halves of a jackknife. We take jackknives along three different axes:
 
@@
 There are clear detections at low $k$'s.
-\item Even/Odd (blue): We split our dataset into even and odd Julian days.
-We form power spectra for each separately, allowing for the cross-multiplication of `even' with `even', for example.
+\item Baselines: We split our dataset into two halves, where each contains half of the total baselines used in the 
+analysis. No baselines are repeated between the two datasets.
+\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
+4.6-8.6 hours).
+\item Day: We split our dataset into even and odd Julian days.
+We form power spectra for each separately, only cross-multiplying `even' with `even', for example.
 Although we don't allow this in our standard pipeline, we include these same-dataset cross-multiplications to allow a power spectrum to be estimated from solely the `even' data (similarly for `odd').
 If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out.
-\item Baselines (green): We split our dataset into two halves, where each contains half of the total baselines used in the 
-analysis. There are no baselines repeated between the two datasets.
-\item LST (magenta): We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
-4.6-8.6 hours).
+However, allowing these cross-multiplications can in practice introduce a low level noise bias...
 \end{itemize}
@@
 	\centering
+	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
 	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
-	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
 	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
-	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the LST axis (top left), baseline axis (top right), and even/odd Julian date axis (bottom).
-The results shown are unweighted.
+	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
+The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra of a jackknife.
 The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
 We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to thermal noise squaring).
-All three tests are dominated by residual foregrounds at $k$-values near the horizon, which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
+All three tests are dominated by residual foregrounds at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
 	\label{fig:null}
@@
 %	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
-%$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along julian days (separating 
+%$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along Julian days (separating 
 %even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
@@
 Additionally, the differenced power spectrum values (black points) all lie within the gray-shaded estimated error region for high $k$'s.
-Therefore, we conclude that particular baselines are not to be blamed for systematics in our dataset.
-
-For the LST test, $90\%$ of the error bars pass through zero, which is slightly low given the expected $95\%$.
+Therefore, we conclude that particular baselines are not to be blamed for the bias in our dataset.
+
+For the LST test, $90\%$ of all the error bars pass through zero, which is slightly lower than the expected $95\%$.
 Additionally, not all power spectrum points lie within the gray-shaded region, even at high-$k$.
 This LST-dependent systematic is likely caused by residual foregrounds that vary in LST.
-In other words, the two jackknife halves differ by an amount greater than thermal noise and do not effectively cancel out the sky signal when differencing.
-
-The even/odd test shows $81\%$ of error bars being consistent with zero, with several power spectrum points falling outside the estimated error region.
+In other words, the two jackknife halves differ by an amount greater than thermal noise and do not completely cancel out the sky signal when differencing.
+
+The even/odd test shows $81\%$ of all error bars being consistent with zero, with several power spectrum points falling outside the estimated error region.
 Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test).
-This strengthens our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.
+This supports our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.
 
 Finally, we note that all three null tests exhibit error bars that are strongly $k$-dependent.
-The errors are largest near the horizon, which is expected since foregrounds are brightest in this region post-delay filtering.
+The errors are largest just outside the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
 We also note that all three tests result in power spectrum errors that are larger than the estimated thermal noise, even at high-$k$.

### 2018-03-22 PAPER.tex
made notes of where to flesh out jackknife section

@@
 If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out.
-However, allowing these cross-multiplications can in practice introduce a low level noise bias...
+%However, allowing these cross-multiplications can in practice introduce a low level noise bias...
 \end{itemize}
@@
 The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to thermal noise squaring).
+We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to \cc{??}).
 All three tests are dominated by residual foregrounds at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
@@
 The even/odd test shows $81\%$ of all error bars being consistent with zero, with several power spectrum points falling outside the estimated error region.
-Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test).
+\cc{why is that?} %Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test).
 This supports our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.

### 2018-03-22 PAPER.tex
edited jackknife text more

@@
 \item Day: We split our dataset into even and odd Julian days.
-We form power spectra for each separately, only cross-multiplying `even' with `even', for example.
-Although we don't allow this in our standard pipeline, we include these same-dataset cross-multiplications to allow a power spectrum to be estimated from solely the `even' data (similarly for `odd').
+We form power spectra for each separately, allowing the cross-multiplication of `even' with `even', for example, for this null test only.
 If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out.
@@
 	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
-The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra of a jackknife.
+The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra produced on either side of the jackknife axis.
 The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test (likely due to foregrounds that vary in LST) and even/odd test (likely due to \cc{??}).
-All three tests are dominated by residual foregrounds at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
+We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test and even/odd test.
+All three tests, whether biased or not, have an extra noise bias that is strongly $k$-dependent.
+Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
 	\label{fig:null}
@@
 
-Investigating Figure \ref{fig:null}, we find that the baselines test is fully consistent with noise (all error bars pass through zero).
-Additionally, the differenced power spectrum values (black points) all lie within the gray-shaded estimated error region for high $k$'s.
+In investigating Figure \ref{fig:null}, we focus on two main aspects of each test - whether the error bars are consistent with zero, and whether they are consistent with thermal noise.
+The former indicates a `passing' null test where there is no bias along the jackknife axis.
+The latter reveals whether there is an additional noise bias present that lies above the thermal noise.
+
+We find that the baselines test is fully consistent with noise, as all error bars pass through zero.
 Therefore, we conclude that particular baselines are not to be blamed for the bias in our dataset.
-
 For the LST test, $90\%$ of all the error bars pass through zero, which is slightly lower than the expected $95\%$.
-Additionally, not all power spectrum points lie within the gray-shaded region, even at high-$k$.
-This LST-dependent systematic is likely caused by residual foregrounds that vary in LST.
+This indicates a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
 In other words, the two jackknife halves differ by an amount greater than thermal noise and do not completely cancel out the sky signal when differencing.
-
-The even/odd test shows $81\%$ of all error bars being consistent with zero, with several power spectrum points falling outside the estimated error region.
-\cc{why is that?} %Rather than attribute these biases to systematics that differ \textit{between} the `even' and `odd' datasets, we believe that they are caused by the squaring of thermal noise (which was allowed in the construction of this test).
-This supports our choice to not allow the cross-multiplication between the same LST-binned datasets in our full pipeline.
+The even/odd test shows $81\%$ of all error bars being consistent with zero, again indicating the presence of a low level bias.
+The cause of this particular systematic is not obvious, and requires further investigation that we do not carry out in this paper.
 
@@
 The errors are largest just outside the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
-We also note that all three tests result in power spectrum errors that are larger than the estimated thermal noise, even at high-$k$.
+We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise at high-$k$.
+This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
+
 There are a couple possible explanations for this.
-Although we expect each cross-multiplication to have independent noise (except in the even/odd case), there is still the possibility of a noise-foreground coupling term that can introduce power.
-This cross-term would vary with foreground strength, therefore being consistent with the shape of the results.
-Alternatively, our estimate of the thermal noise may be too low, as all three tests seem to imply a larger, but consistent, estimate.
+Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
+This is because cross-multiplications produce four additive terms - a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+When differencing two power spectra, we expect the signal-only term to subtract out for a `passing' null test, and we expect the noise-only terms to be consistent with thermal noise.
+The cross-terms, however, can introduce a noise bias that would vary with foreground strength, therefore being consistent with the shape of our results.
+That being said, an alternate explanation for the large error bars seen at high $k$'s could be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate.
 

### 2018-03-22 PAPER.tex
made syntax/typo changes from full-read-through up to Section 2.2

@@
 galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the $21$ cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
+EoR by tracing the 21\,cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
 of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
@@
 for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
-led to a revised, higher $21$ cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al., \textit{submitted}, mostly stems from an 
+led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al. (\textit{submitted}), mostly stems from an 
 improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
@@
 its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
-This tomography technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
+This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
 of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. Tracing the 21\,cm line as a function of redshift offers a window into the 
+stretching out as it traveled through expanding space. 21\,cm tomography offers a unique window into the 
 evolution of ionization, temperature, and density fluctuations.
@@
 with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
-the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, errors, and bias) that are essential to investigate 
-for a robust $21$ cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
+the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, error estimation, and bias) that are essential to investigate 
+for a robust 21\,cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
 case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
-from the lessons learned.
-More specifically, we develop new techniques for computing signal loss and under-go a rigorous re-analysis of PAPER-64 data in order to present a new power spectrum limit.
-A companion paper, Kolopanis et al., \textit{submitted}, builds off of the methods in this paper to present PAPER-64 results for multi-redshifts and multiple baselines.
-
-Finally, this paper adds to the growing foundations of lessons which have been documented in  \citet{Patil2016}, \citet{Jacobs2016}, and \cite{Paciga2013} by the LOFAR, MWA and GMRT projects respectively.
+from the lessons learned. A companion paper, Kolopanis et al. (\textit{submitted}), builds off of the methods in this paper to present PAPER-64 results for multiple redshifts and baseline types.
+
+Finally, this paper adds to the growing foundations of lessons which have been documented in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
 These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
 
-This paper is organized into two main sections. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
+This paper is organized into two main halves. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
 toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
 from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a 
-revised PAPER-64 power spectrum result (Kolopanis et al., \textit{submitted}). We conclude in Section \ref{sec:Con}.
+revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{submitted})). We conclude in Section \ref{sec:Con}.
 
@@
 
-There are many choices a $21$ cm data analyst must consider, though the space is significantly constrained by 
-the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
-only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
-down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
-the sky. However, even within this problem sub-space, questions remain.
-
+There are many choices a 21\,cm data analyst must consider.
+%For PAPER, its grid configuration allows the use of many signal processing tricks to down-weight foregrounds without reference to a sky model.
+However, even with the advantage of being agnostic about the sky, many questions still remain.
+%, though the space is significantly constrained by 
+%the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
+%only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
+%down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
+%the sky. However, even within this problem sub-space, questions remain.
 How can time-ordered measurements be combined? How can the 
@@
 
-Though there are many data analysis choices, measuring the statistical $21$ cm power spectrum ultimately requires robust 
+Though there are many data analysis choices, measuring the statistical 21\,cm power spectrum ultimately requires robust 
 methods for determining accurate confidence intervals and rigorous techniques to identify and control systematics.  In this 
-paper, we focus on three $21$ cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
+paper, we focus on three 21\,cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
 with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
@@
 
-A deep understanding of the following three themes is essential for the accuracy and interpretation of a $21$ cm power 
+A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
 spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
@@
 Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
-\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a $21$ cm power spectrum result 
+\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
 determine the difference between a detection and a null result, which have two very different implications. Errors can be 
@@
 measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
-successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for $21$ cm 
+successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for 21\,cm 
 analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
@@
 these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
-being standard steps in general $21$ cm analyses.
+being standard steps in general 21\,cm analyses.
 \begin{itemize}
@@
 (\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
-independent samples. However, by adjusting the shape of the filter to match the rate of sidereal motion it can also affect the presence 
+independent samples. However, when adjusting the shape of the filter to match the rate of sidereal motion, it can also affect the presence 
 of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
 \item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
-weighting employed by PAPER is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
+weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
 weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
@@
 \item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
-methods, bootstrapping is one way to estimate errors. Bootstrapping is a useful method for estimating errors of a dataset from 
+methods, bootstrapping is one way to estimate errors. Namely, bootstrapping is a useful method for estimating errors of a dataset from 
 itself (\citealt{andrae2010}). By randomly drawing many subsamples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
@@
 \citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011b}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
-An EoR detection must pass jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
+An EoR detection must pass both jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
 \end{itemize}
@@
 they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
-Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be performed for robust $21$ 
-cm results.
+Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be performed for robust 21\,cm results.
 
@@
 
-Signal loss can arise in a variety of ways in the analysis pipeline, such as fitting a polynomial during 
-spectral calibration, applying a delay-domain filter, or by deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
+Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during 
+spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
@@
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
-the Fourier transform of the sky along $2$ spatial dimensions (using the flat-sky approximation), and since we are interested in $3$-dimensional Fourier-modes 
+the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier-modes 
 we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
@@
 Kelvin and taking into account cosmological scalings.
-It is evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C}$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ ($k_{\parallel}$, a cosmological wavenumber, is the
-Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
-an example, inverse covariance weighting would set $\textbf{R} = \textbf{C}^{-1}$ and an uniform-weighted case would use $
-\textbf{R} = \textbf{I}$, the identity matrix.
+It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C}$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
+Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b})). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
+an example, inverse covariance weighting would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
+\textbf{R} \equiv \textbf{I}$, the identity matrix.
 
@@
 
-\noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum. The data analyst has a choice for $
+\noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum $\textbf{p}$. The data analyst has a choice for $
 \textbf{M}$ (subject to the constraint that window functions integrate to unity) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal ($\textbf{M} \propto \textbf{I}$), although we explore other cases for the analysis
@@
 
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimate $\widehat{\textbf{p}}$.
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{p}}$.
 Our goal in
@@
 In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
-We will now build intuition into how estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
+We will now build intuition into how empirically estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
 
@@
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 (both the previous analysis and our new analysis) we use $\sim$$8$ hours of data (with channel 
+might be used for a power spectrum analysis. For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim$$8$ hours of data (with channel 
 widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
@@
 
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift scan observation. Hence, flat spectrum sources (away 
+We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation. Hence, flat spectrum sources (away 
 from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
@@
 single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
-realistic EoR signal would have a sloped power spectrum in $\textbf{p}$(k) (instead of flat, as in the case of white noise), 
+realistic EoR signal would have a sloped power spectrum in $\textbf{p}(k)$ (instead of flat, as in the case of white noise), 
 which could be simulated by introducing frequency correlations into the mock EoR signal. However, here we treat all 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
-	\caption{Our toy model dataset. We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in 
-time and frequency. We model a mock EoR signal as a random Gaussian signal. Real parts are shown here.}
+	\caption{Our toy model dataset to which we apply different weighting schemes to in order to investigate signal loss.
+We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in
+time and frequency. We model a mock EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
+\textbf{x}_{FG} + \textbf{x}_{EoR}$. Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 \noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for estimated inverse covariance weighting is then $
-\textbf{R} = \widehat{\textbf{C}}^{-1}$.
-
-First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using OQE formalism and $\textbf{R} = \widehat{\textbf{C}}^{-1}$. 
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}. Also plotted in the figure are the uniform-weighted($\textbf{R} = \textbf{I}$) power spectrum of $
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
+\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+
+First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using OQE formalism and $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$. 
+The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
+Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $
 \textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
@@
 foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The power spectrum of foregrounds peaks at a $k$ mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare inverse covariance weighting
+The power spectrum of foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
+In the two panels, we compare empirically estimated inverse covariance weighting
 where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
@@
 To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has consequences on our result.
+Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
+
 An eigenspectrum ranks the eigenvalues of a matrix from 
@@
 sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of a true $\textbf{C}$.
+These empirically estimated covariance matrices have eigenspectra that are different from that of the true $\textbf{C}$.
 Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
@@
 For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
-In Figure \ref{fig:toy_sigloss12} we show the covariances of our toy model datasets along with inverse covariance weighted data.
+In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
 The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{FG}$.
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
-	\caption{The covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
+	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
 (middle), and FG + EoR (right). Real parts are shown here.}
@@
 changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. The resulting 
-power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover EoR, 
+power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
 demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
@@
 
-We have shown how signal loss can arise due to the coupling of weak eigenmodes (EoR dominated modes) to the data.
+We have shown how signal loss can arise due to the coupling of weak eigenmodes (EoR-dominated modes) to the data.
 We will next show how this effect is exaggerated by reducing the total number of independent
@@
 $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}). We choose these numbers so that the total number of 
-independent samples is similar to the number of frequency channels --- our matrices will still be full rank.
+independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
 %\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
@@
 fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
-true fringe-rate filtered case covariance matrix. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
+true covariance matrix of the fringe-rate filtered data. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 \begin{equation}
@@
 \end{equation}
-where $\C$ is true covariance matrix.
-In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different curve colors).
+where $\C$ is the true covariance matrix.
+In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors).
 With more independent time samples (i.e.
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.png}
-	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).}
+	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
+The dashed, steep eigenspectrum has a greater risk of signal loss because its weak eigenmodes are more strongly coupled to the data than those of the solid eigenspectrum.}
 	\label{fig:toy_sigloss15}
@@
 	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.png}
-	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different number of mock data realizations.
-The colors span from the 0th eigenmode (the first one) to the 19th eigenmode (the last one), where they are ordered by eigenvalue in descending order.
+	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
+The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
 This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes, implying that weighting by empirically estimated `weak' modes poses the most risk for signal loss.}
@@
 	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We use inverse covariance weighting where $\textbf{C}$ is 
+EoR only (red), and the weighted FG + EoR dataset (green). We use empirically estimated inverse covariance weighting where $\textbf{C}$ is 
 computed from the data.
-There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by empirically estimated eigenmodes that are more strongly coupled to the data due to there being fewer independent modes.}
+There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by eigenmodes that are more strongly coupled to the data due to there being fewer independent modes in the data.}
 	\label{fig:toy_sigloss7}
@@
 
-The power spectrum results for the fringe-rate filtered toy model data is shown in Figure \ref{fig:toy_sigloss7}. As 
+The power spectrum results for the fringe-rate filtered toy model data are shown in Figure \ref{fig:toy_sigloss7}. As 
 expected, there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
@@
 spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
-These examples are not meant to be taken as suggested analyses methods but rather as illustrative cases.
+These examples are not meant to be taken as suggested analysis methods but rather as illustrative cases.
 
@@
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}$ would).
+This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}_{EoR}$ would).
 This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
@@
 
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}} = 
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}} \equiv 
 \widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
 of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the covariance matrix more heavily than those off-diagonal.
+elements of the estimated covariance matrix more heavily than those off-diagonal.
 Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
@@
 by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
-method intentionally projects out modes that are EoR-dominated by replacing all but the three highest weights in the 
+method intentionally projects out the strongest modes only by replacing all but the three highest weights in the 
 eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of `weak' modes which are coupled to the data results in negligible signal loss. However, we do 
-not perfectly recover the shape of EoR because we lost information when projecting out certain modes.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG vs.
-EoR dominated, so selecting a subset of modes to down-weight is not trivial.
-
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} = \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\widehat{\textbf{C}}$).
+not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes.
+While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
+
+The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\widehat{\textbf{C}}$).
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it's no longer coupled to both the `strong' or `weak' eigenmodes.
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it's no longer coupled to either the `strong' or `weak' eigenmodes.
 For this toy model,
@@
 the identity, element-wise, results in a diagonal matrix, meaning we are only left with correlation information between the same 
-two frequencies. Because we disregard information from all other frequency combinations in this case, we do a poor job 
+two pairs of frequencies. Because we disregard information from all other frequency combinations in this case, we do a poor job 
 suppressing the foreground.
 But because we de-coupled the whole eigenspectrum from the data, we also avoid signal loss.
-Although this method did not successfully recover EoR for this particular simulation, it is important that we show that there
+Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
 are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more than others based on the spectral nature 
@@
 
-In summary, we have a choice of how to weight $21$ cm data. Ideally, we want to down-weight bright foregrounds without 
+In summary, we have a choice of how to weight 21\,cm data. Ideally, we want to down-weight bright foregrounds without 
 removing the underlying cosmological signal. However, there are trade-offs between the weighting method 
@@
 
-Our second major $21$ cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
+Our second major 21\,cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
 confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
@@
 
-In a $21$ cm power spectrum, detections could be the EoR signal, but they could also 
+In a 21\,cm power spectrum, detections could be the EoR signal, but they could also 
 %(and unfortunately more likely) 
 be attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
-future $21$ cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
+future 21\,cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
 that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
@@
 Foregrounds are another type of bias, but an additive one instead of multiplicative.
-Foreground bias is perhaps one of the main factors limiting $21$ cm results, as foreground signals lie $\sim4$-$5$ orders of
+Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
 magnitude above the cosmological signal.
@@
 In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is 
-multiplied by itself. Every $21$ cm visibility measurement contains thermal noise that is comprised of receiver and sky noise. 
+multiplied by itself. Every 21\,cm visibility measurement contains thermal noise that is comprised of receiver and sky noise. 
 We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating 
@@
 
-In the previous sections we have discussed three overarching $21$ cm power spectrum themes --- signal loss, error estimation, 
+In the previous sections we have discussed three overarching 21\,cm power spectrum themes --- signal loss, error estimation, 
 and bias. Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of 
@@
 
-As a brief review, PAPER is a dedicated $21$ cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
+As a brief review, PAPER is a dedicated 21\,cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
@@
 
-The previously best published $21$ cm upper limit result from \citetalias{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit 
+The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit 
 on $\Delta^{2}(k)$, defined as
@@
 when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
-$21$ cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
+21\,cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
@@
 The sensitivity prediction (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
-interferometric $21$ cm data, in temperature-units, is:
+interferometric 21\,cm data, in temperature-units, is:
 
@@
 
-Although current $21$ cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
+Although current 21\,cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
 ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like 
@@
 
-In particular, in this paper we have investigated the subtleties and tradeoffs of common $21$ cm power spectrum techniques on 
+In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
 signal loss, error estimation, and bias, which can be summarized as follows:
@@
 \item Substantial signal loss can result when weighting data using empirically estimated covariances (Section 
-\ref{sec:SiglossOverview}). Loss of the $21$ cm signal is especially significant the fewer number of independent modes that
+\ref{sec:SiglossOverview}). Loss of the 21\,cm signal is especially significant the fewer number of independent modes that
 exist in the data. Hence, there exists a trade-off between sensitivity driven 
@@
 
-The future of $21$ cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
+The future of 21\,cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
 foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
 instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
-comprehensive jackknife tests will play critical roles in accurate $21$ cm results.
+comprehensive jackknife tests will play critical roles in accurate 21\,cm results.
 With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.

### 2018-03-22 PAPER.tex
made syntax/typo changes from full-read-through up to Section 3

@@
 Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
-between them. Through the process of resampling and averaging along different axes, we can estimate error bars for 
+between them. Through the process of re-sampling and averaging along different axes, we can estimate error bars for 
 our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
 
-Suppose we have $N$ different measurements targeting the same quantity ($N$ power spectrum measurements made along different axes, such as baselines or times). 
+Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements made along different axes, such as baselines or times). 
 Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
@@
 number of independent samples along the axis that is being re-sampled is well-determined.
-In Section \ref{sec:Boot}, we explain how our bootstrapping procedure has changed in PAPER's analysis in light of this issue.
+In Section \ref{sec:Boot}, we explain how we under-estimated errors in the \citetalias{ali_et_al2015} analysis of PAPER and how our bootstrapping procedure has now changed in light of this issue.
 
@@
 \end{figure}
-
-\begin{comment} % REMOVED THIS HALF OF BOOTSTRAPPING SECTION
-We will now discuss a second subtle feature of bootstrapping that fails to maximize the sensitivity of a dataset. Suppose we 
-have $5$ independent measurements of the sky (from $5$ different baselines, for example). A bootstrap then consists of $5$ 
-measurements that are drawn randomly with replacement from the original set. If all $5$ spaces are filled randomly, there is a 
-high probability that some measurements will be repeated in the bootstrap because they are drawn more than once. The 
-bootstrap may therefore consist of only $3$ or $4$ independent measurements --- a number smaller than the total number of 
-samples. In fact, the probability of drawing $5$ completely independent measurements is less than $4\%$.
-
-In order to maximize sensitivity, we desire as many independent samples as possible. However, solely using all $5$ 
-independent measurements does not allow variation between bootstraps.
-
-Therefore, we use a slightly modified bootstrapping method. For each bootstrap, we draw $N-1=4$ samples without 
-replacement and draw the last slot randomly with replacement. In doing so there is a small chance a bootstrap will consist of 
-$5$ independent measurements, but even with $4$ our sensitivity is nearly maximized. 
-%One may wonder whether this change is still a legitimate way of error estimating since random sampling only occurs for one value in a bootstrap.
-However, as long as the number of possible variations is greater than the number of bootstraps we perform, it is a valid way to uncover the inherent variability in a dataset.
-
-In Figure \ref{fig:toy_error2} we compare these two methods of bootstrapping: sampling all elements randomly (black points) 
-versus sampling just the final element randomly (gray points). The two converge for datasets with small numbers of elements, 
-when filling a few spots randomly is nearly the same as filling only the last spot randomly. However, there is also increased 
-scatter in this regime due to small number statistics.
-
-The difference between the two methods is most pronounced for datasets with large numbers of elements. As a dataset grows 
-in size, it becomes increasingly rare to draw entirely independent samples, and thus the benefit of ensuring, say, $999$ 
-independent samples out of $1000$ is most noticeable. The more elements in our dataset, the more sensitivity we can gain by 
-mandating that most of our measurements are independent ones. An analog for the y-axis in Figure \ref{fig:toy_error2} is 
-therefore the sensitivity of a final power spectrum measurement.
-\end{comment}
 
@@
 Foregrounds are another type of bias, but an additive one instead of multiplicative.
-Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
+Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim$$4$-$5$ orders of
 magnitude above the cosmological signal.
@@
 
-Although smooth spectrum foregrounds preferentially show up at low delay, or low $k$ modes, their isolation within the wedge is not perfect.
+Although smooth spectrum foregrounds preferentially show up at low delay, or low $k$-modes, their isolation within the wedge is not perfect.
 In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
@@
 In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (\citetalias{ali_et_al2015}; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
-In the next section (Section \ref{sec:JackknifeOverview}), we will present some tests that can help distinguish these excesses from that of EoR.
+In the next section, we will present some tests that can help distinguish these excesses from that of EoR.
 
@@
 We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating 
-longer, using more baselines, etc. However, the squaring of noise occurs when cross-multiplying visibilities, which is shown by 
+longer, using more baselines, etc. However, the squaring of noise can occur when cross-multiplying visibilities, which is shown by 
 the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}. If both copies of $\textbf{x}$ come from the same baseline and time, it 
@@
 divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
-Subtracting the two removes signal that is common to both subsets, including foregrounds and EoR. The resulting power 
+Subtracting the two removes signal that is common to both subsets, including foregrounds and the EoR signal. The resulting power 
 spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 

### 2018-03-23 PAPER.tex
made syntax/typo changes from full-read-through up to Section 3.2

@@
 integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim$$8$ hours of data (with channel 
+might be used for a power spectrum analysis. For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel 
 widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
@@
 Foregrounds are another type of bias, but an additive one instead of multiplicative.
-Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim$$4$-$5$ orders of
+Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
 magnitude above the cosmological signal.
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit (Kolopanis et al., \textit{submitted}) stems from previously underestimated signal loss and underestimated error bars, both of which we
+The revision of this limit (Kolopanis et al.
+(\textit{submitted})) stems from previously under-estimated signal loss and under-estimated error bars, both of which we
 address in the following sections.
 
-For our analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly different RA 
-range of $0$-$8.6$ hours). All power spectrum results are produced for a center frequency of $151$ MHz using a width of $10$ 
-MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}. We note that, besides using only one baseline type instead of the three as in 
-\citetalias{ali_et_al2015}, the PAPER-64 dataset that we use in this case study differs from that in \citetalias{ali_et_al2015} only in the analysis.
-The most significant changes occur in the power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
+For our revised analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly longer RA 
+range of $0$-$8.6$ hours; we found that some early LSTs were contaminated).
+All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
+In the case study in this paper, we only use one baseline type instead of the three as in
+\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{submitted}) uses all baselines presented in \citetalias{ali_et_al2015}.
+
+The most significant changes from \citetalias{ali_et_al2015} occur in our revised power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
 In \citetalias{ali_et_al2015}, the
@@
 robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
-computed for a fiducial $30$ m baseline at $150$ MHz, the center frequency in our band. The filter in both the fringe-rate 
+computed for a fiducial 30\,m baseline at 150\,MHz, the center frequency in our band. The filter in both the fringe-rate 
 domain and time domain is shown in Figure \ref{fig:frp}.
@@
 Finally, we build off of Section \ref{sec:SiglossOverview} by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
+Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously under-estimated losses.
 
@@
 In short, our method consists of adding an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
-To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated $21$
-cm signal visibilities. Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals) 
+To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
+Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals)
 are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
@@
 
-Suppose that $\textbf{e}$ is a mock injected EoR signal (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
+Suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
 $ to be the data plus the EoR signal:
@@
 \end{eqnarray}
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirical inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$).
-We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.
+In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$).
+We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
 
@@
 In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
-Output values are gaussian distributed around zero, spanning a range of values set by the injection level.
+Output values are Gaussian distributed around zero, spanning a range of values set by the injection level.
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniform weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
-We also note that in this regime, $\widehat{\textbf{p}}_{r}$ approaches the data level as expected.
+In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a Gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+We also note that in this regime, $\widehat{\textbf{p}}_{r}$ (black) approaches the data level (gray) as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
@@
 We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e.
-in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than a cosmological signal).
-However it is useful as a check of our system in a relatively simple case.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms are small in comparison to the signal-only term.
+in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
+However, it is useful as a check of our system in a relatively simple case.
+As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green).
 Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
+We again see that, in the estimated inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation is no longer profoundly negative and can again be modeled as a gaussian distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+The cross-correlation can again be modeled as a Gaussian distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
 
@@
 departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-the cross-term has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross correlating inverse covariance weighted terms.
+in this regime the cross-term has nearly the same amplitude, but with a negative sign.
+As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
 This negative component drives down the $P_{\rm out}$ estimator (black).
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
-	\caption{Illustration of the power spectrum amplitude as a function of injected power level summed into the 
-data. The net output ($P_{out}=P_r$) is shown in black, the individual cross-terms, as defined by Equation 
-\eqref{eq:crossterm},  are shown in blue, red, green; the dotted line indicates 1:1 input to output mapping.  The 
-empirical inverse covariance weighted case used in \citealt{ali_et_al2015} is on the left and the uniform-weighted 
+	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
+data. The net output ($P_{\rm out}=\widehat{\textbf{p}}_r$) is shown in black, the individual terms, as defined by Equation 
+\eqref{eq:crossterm},  are shown in blue, red, green; the dotted black line indicates 1:1 input to output mapping.  The 
+empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015} is on the left and the uniform-weighted 
 case is on the right. The details of the simulation used to generate the figure is explained in Section 
 \ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.   The gray 
-line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
-component is also the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
+horizontal line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
+component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
 than the net output because the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
-regime where cross-correlation between injection and data are not dominant, the cross-terms have a noise-like 
-term with width $\sqrt{p_e}$.
+regime where cross-correlations between injection and data are not dominant, the cross-terms have a noise-like 
+term with width $\sqrt{p_e}\sqrt{p_x}$.
 However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
@@
 the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for 
-the empirical inverse covariance weighted case). }
+the weighted case). }
 	\label{fig:sigloss_terms}
@@
 ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle
+As shown in Appendix C of \citet{parsons_et_al2014}%\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}
+, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle 
 \textbf{ee}^{\dagger} \rangle_{t}$) with smaller
@@
 
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
+{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator is that it is not properly normalized.
 Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
@@
 The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss, and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
+We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
 
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
-($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which, with an empirically estimated covariance, leads to substantial loss.
-With this weighting, our
+($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. With this weighting, our 
 expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}
-  p(P_{\rm in}) ,
+p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
 \end{equation}
@@
 as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
-by fixing $P_{\rm in}$, and simulating our analysis pipeline for many realizations of the injected EoR signal 
+by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
 consistent with this power spectrum. The resulting distribution is normalized such that the sum over $P_{\rm out}$ is unity, and the 
@@
 In our code, we add a new realization of EoR to each independent bootstrap of data with the goal of simultaneously capturing variance due to noise and signal loss.
-To limit computing time we perform $20$ realizations of each $P_{in}$ level.
+To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
 We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
@@
 
-Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$.
-For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one.
-Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for empirical inverse covariance weighting (left) and uniform weighting (right).
+Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
+We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them).
+Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
 Although we only show figures for one $k$-value, we note that
-the shape of the transfer curve is nearly identical for all $k$'s.
+the shape of the transfer curve is similar for all $k$'s.
 This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-We invoke the Bayes interpretation and re-interpret it as the posterior $P(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
-We then make a horizontal cut across at the data value $P_{\rm out} = \widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
+We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
+To do this we make a horizontal cut across at the data value $P_{\rm out} = \widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 
-By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
+By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirical inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
-value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$.
+From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
+value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10^{4}$.
 For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
 Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps on top of the points for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
+heat-maps on top of the points for the cases of empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
 diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that the weighted case results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
+From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
 not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
@@
 
-The loss-corrected power spectrum result for empirical inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
+The loss-corrected power spectrum result for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
 %There are a few important checks to examine.
@@
 We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to empirical inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.
+weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
-	\caption{Empirical inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
+	\caption{The power spectrum of PAPER-64 data, weighted by an inverse covariance estimator.
+The power spectra values pre-signal loss estimation are shown as black and gray points (positive and negative values, respectively,
 with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
@@
 with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
-foregrounds and systematics in our data without generating large amounts of signal loss. We have found that the balance 
+foregrounds and systematics in our data without generating large amounts of signal loss as we've seen with the inverse covariance estimator. We have found that the balance 
 between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
@@
 eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
-that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is full inverse 
-covariance weighting of our $21$ channels). The power spectrum results for one $k$ value, both before and after signal loss 
+that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
+covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
 estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
 becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
-subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post signal loss estimation, 
+subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
 increases with the number of down-weighted modes (black curve).
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The grey and black lines represent power spectrum limits pre and post signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
-When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to the empirical inverse covariance weighted case.
+The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
 From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss.
 We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
+We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of strengths and while an overall trend from high to low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
 
@@
 are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
-covariance weighting).
-Over $\sim3$ orders of magnitude of signal loss results when using empirical inverse covariance weighting.
+are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
+covariance estimator).
+Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
 Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e.
-empirical inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
+This regularization knob is tuned from $0.01\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e.
+very little regularization) to $100\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
 Also
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.035Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.035Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ as a simple example of regularization that minimizes loss.}
 	\label{fig:sigloss_modeloop}
@@
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
-We choose this weighting scheme because it slightly out-performs the other weighting schemes, likely due to the fact that it retains information from all eigenmodes (i.e.
-it doesn't throw away some information as in the other cases) but re-weights them in a way that produces minimal loss.
-In this paper, we use this weighting scheme as a simple regularization demonstration, though we note that in Kolopanis et al., (\textit{submitted}) we choose the most optimal regularization parameter for our final limits.
+We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, though we note that in Kolopanis et al.
+(\textit{submitted}), we choose the most optimal regularization parameter for our final limits for every redshift bin independently.
+We also note that all of the regularizations described here perform similarly to the uniformly weighted case; this is likely because we are in a regime where it is very difficult to disentangle foreground modes from those of EoR.
+We see that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al.
+(\textit{submitted}).
 
@@
 noise (solid green).
-In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+In Kolopanis et al.
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
@@
 The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation.
-There is negligible loss using this regularization.
+There is a small amount of loss using this regularization.
 The dashed blue line is the uniform-weighted
@@
 loss, bootstrapping, and the theoretical error computation.
-In Kolopanis et al., (\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+In Kolopanis et al.
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
@@
 $\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
-\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$ m diagonal PAPER baselines (instead of the 
+\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$\,m diagonal PAPER baselines (instead of the 
 horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
@@
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al., \textit{submitted}).
+we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{submitted})).
 
 Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
+calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
 down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.
@@
 
-In Section \ref{sec:Sigloss}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated, and ways it can be minimized.
+In Section \ref{sec:Sigloss}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
 We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.

### 2018-03-23 PAPER.tex
made syntax/typo changes from full-read-through up to Section 3.3

@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
@@
 accounting of the differences which have been discovered.
+Our revised theoretical error estimation, which is often plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
 
@@
 
-where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$ K, yielding $T_{sys} = 431$ K at $150$ MHz. 
-This is lower than the $T_{sys}$ of $500$ K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
+where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$\,K, yielding $T_{sys} = 431$\,K at $150$\,MHz. 
+This is lower than the $T_{sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small mis-calculation errors that were 
 identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
@@
 In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
-\item $N_{lst}$: The number of LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
+\item $N_{lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
 because we integrate incoherently over time. For PAPER-64, $N_{lst} = 8$.
 \item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
-analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al., \textit{submitted}
+analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al. (\textit{submitted})
 use three separation types.
@@
 where $t_{i}=43$ seconds, $t_{int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
-taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$ s. 
+taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$\,s. 
 \item $N_{days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
@@
 \item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$ m East/West baselines used in the analysis. However, using the total number of baselines neglects 
+the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines neglects 
 the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
@@
 \end{equation}
-\noindent where, for the \citetalias{ali_et_al2015} analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+\noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
 entering the group ($N_{bls\_total}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
@@
 	\includegraphics[width=\columnwidth]{plots/sense_check.png}
-	\caption{An updated prediction for the noise-level of PAPER-64 data (black) is shown in comparison to previously 
+	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
 published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
@@
 Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}, where the black and gray points represent positive and negative power spectrum values, respectively (with 
-$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed blue line represents the uniform-weighted power 
-spectrum, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
+\ref{fig:ps_noise}, where the black and gray points represent pre-signal loss estimated positive and negative power spectrum values, respectively (with 
+$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed black line represents the post-signal loss $2\sigma$ upper limit on the EoR signal, the dashed blue line represents the $2\sigma$ uniform-weighted power
+spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
 \eqref{eq:sense}. All three are in agreement, validating our analytical thermal noise calculation.
@@
 The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation.
-The dashed blue line is the uniform-weighted power spectrum (also $2\sigma$ upper
-limit). The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
+The dashed blue line is the uniform-weighted power spectrum $2\sigma$ upper
+limit. The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
 estimates agree.}
@@
 $700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Medians were then taken of the values in each bootstrap (with the appropriate median correction factor applied). Finally, power 
+Means were then taken of the values in each bootstrap. Finally, power 
 spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
@@
 effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} in shown in gray, where bootstrapping occurs along both the baseline and time axes.
+The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
 This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).

### 2018-03-23 PAPER.tex
made syntax/typo changes from full-read-through up through acknowledgements

@@
 likely explanation would be excess foreground emission from a radio source in the sky at that time. A jackknife test involving 
-data before and after the application of a fringe-rate filter can reveal whether cross-talk noise bias is successfully suppressed 
+data before and after the application of a fringe-rate filter can reveal whether crosstalk noise bias is successfully suppressed 
 with the filter, or if similar-shaped detections in both power spectra suggest otherwise. There are many other jackknife axes of 
@@
 the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines neglects 
-the fact that baselines are averaged into groups (see Section \ref{sec:Boot}) for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
+the fact that we average baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum 
-detections and imitate EoR. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
+detections and imitate an EoR signal. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
 detection, as well as identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
@@
 \noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
-of foreground power from low $k$ to high $k$ modes. Specifically, we order the elements in $\textbf{F}$ in such a way so that 
-power can leak from high $k$ modes to low $k$ modes, but not vice versa. Since most foreground power shows up at low 
-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the 
-contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however for this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
-
-In addition to mitigating foreground bias at high $k$'s, two other sources of bias that we actively suppress in the PAPER-64 
+of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{F}$ in such a way so that 
+power can leak from high-$k$ modes to low-$k$ modes, but not vice versa.
+Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the
+contamination of foreground bias.
+This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
+
+In addition to mitigating foreground bias at high-$k$'s, two other sources of bias that we actively suppress in the PAPER-64 
 analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
@@
 
-As shown in Figure \ref{fig:ps1_data}, our re-analysis of the PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low $k$ values.
+As shown in Figure \ref{fig:ps1_data}, our re-analysis of the PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
 As discussed in Section \ref{sec:BiasTypes}, this bias is
 most likely attributable to foreground leakage.
-The cause for biases at higher $k$ values is more difficult to pinpoint.
+The cause for biases at higher $k$-values is more difficult to pinpoint.
 Here we discuss three null tests performed on PAPER-64 data that aim to isolate systematics in the data and verify
@@
 4.6-8.6 hours).
-\item Day: We split our dataset into even and odd Julian days.
+\item Day: We split our dataset into even and odd Julian dates.
 We form power spectra for each separately, allowing the cross-multiplication of `even' with `even', for example, for this null test only.
@@
 	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
-	\caption{Power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
+	\caption{Differenced power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
 The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra produced on either side of the jackknife axis.
@@
 The cause of this particular systematic is not obvious, and requires further investigation that we do not carry out in this paper.
+Most importantly, a clean detection of EoR would have passed all three null tests, which is clearly not what we see.
 
@@
 The errors are largest just outside the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
-We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise at high-$k$.
+We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
 This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
@@
 The cross-terms, however, can introduce a noise bias that would vary with foreground strength, therefore being consistent with the shape of our results.
-That being said, an alternate explanation for the large error bars seen at high $k$'s could be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate.
+That being said, an alternate explanation for the large error bars seen at high $k$'s could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate.
 
@@
 \item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
-signal-only simulation (i.e. comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
+signal-only simulation (i.e. comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
 failing to account for correlations between the data and signal (Section \ref{sec:siglossmethod}).
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:ErrorOverview}). If the number of independent samples in a dataset is well-determined, bootstrapping is a 
+\item Errors that are estimated via bootstrapping can be under-estimated if samples in the dataset are significantly correlated 
+(Section \ref{sec:ErrorOverview}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
 simple and accurate way of estimating errors.
@@
 As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
-In Kolopanis et al., (\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(218.7$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
-a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously underestimated limit and 
+In Kolopanis et al.
+(\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously under-estimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $\sim$$1000$ for inverse 
+\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for empirically estimated inverse 
 covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim$$10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
+factor of $\sim10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
 note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim$$2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
+\item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim$$2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
+decrease in predicted sensitivity level by a factor of $\sim2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
 prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
@@
 The future of 21\,cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
-foreground mitigation/removal strategies are being developed, and simulations are being designed to better understand 
+foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
 instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 

### 2018-03-23 PAPER.tex
Polished up appendix

--- 2018-03-23 PAPER.tex
@@
 
-In this Appendix, we examine a toy model for signal loss.
-Our goal is to derive an analytic formula for power spectrum signal loss.
-We will also show that in general, signal loss appears as a multiplicative bias on one's power spectrum estimate.
+In this Appendix, we examine a toy model for signal loss. Our goal is to derive an analytic formula for power spectrum signal loss. While this 
+model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
 
@@
 In the last step we dropped the final term, since it scales as $\eta p_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
-Now, recall that $p_\alpha$ is the \emph{true} power spectrum.
-This means that it can be decomposed into the sum of the foreground and EoR power spectra, since the foregrounds and EoR are uncorrelated in expectation.
-This toy example, while not showing the emergence of cross-terms provides a rudimentary motivation for the form of Equation \eqref{eq:LinearPspecSum}.
+
+Recalling that $p_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
+This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was original a quadratic estimator is no longer quadratic, but contains higher-order correlations.
+This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{LT11}.
+The result is an improperly normalized---and thus lossy---power spectrum estimate.
 

### 2018-03-23 PAPER.tex
fixed small typos in Appendix

@@
 Recalling that $p_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
-This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was original a quadratic estimator is no longer quadratic, but contains higher-order correlations.
-This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{LT11}.
+This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.
+This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e.
+quadratic) statistics \citep{liu_tegmark2011}.
 The result is an improperly normalized---and thus lossy---power spectrum estimate.

### 2018-03-23 PAPER.tex
added additional ref to Appendix

@@
 
-{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator is that it is not properly normalized.
+{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized.
 Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.

### 2018-03-23 PAPER.tex
Added ACL funding information and tweaked notation in appendix

@@
 JSD acknowledges NSF AAPF
-award 1701536. We graciously thank SKA-SA for site infrastructure and observing support.
+award 1701536.
+AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+We graciously thank SKA-SA for site infrastructure and observing support.
 \label{sec:Ack}
@@
 \end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix (for this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real).
-In our case, however, we do not have \emph{a priori} knowledge of the covariance matrix.
-Thus, we replace $\C$ with $\Chat$, its data-derived approximation.
+is the $\alpha$th diagonal element of the Fisher matrix.
+For this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real.
+We also assume for simplicity that $\mathbf{x}$ is the data from a single instant in time, so that it is of length $N_f$, where $N_f$ is the number of frequency channels.
+
+In our case, we do not have \emph{a priori} knowledge of the covariance matrix.
+Thus, we deviate from the true minimum-variance quadratic estimator and replace $\C$ with $\Chat$, its data-derived approximation.
 Our estimator then becomes
@@
 \begin{equation}
-\langle \widehat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N) p_\alpha,
-\end{equation}
-where $N$ is the length of $\x$.
+\langle \widehat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) p_\alpha,
+\end{equation}
+where recall that $N_f$ is the length of $\x$, or the number of frequency channels.
 In the last step we dropped the final term, since it scales as $\eta p_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.

### 2018-03-23 PAPER.tex
added text about analytic not matching perfectly with noise sim

@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to agree with the analytic prediction for noise.
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
+We note that they do not match perfectly, but we find good agreement between them to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic.
 While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
-Finally, we note that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation along with the bootstrapped estimates (which are used to compute errors).
+Finally, one last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation.
 The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-This is shown to agree with the $2\sigma$ analytic prediction for noise (green).}
+While this does not match perfectly with the $2\sigma$ analytic prediction for noise (green), we find good agreement between them to within a factor of two (which we believe is reasonable given the approximations we make in computing the analytic).}
 	\label{fig:data_errors}
@@
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim2$ in mK (Section \ref{sec:PSSense}). We have verified our revised 
-prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our 
+decrease in predicted sensitivity level by a factor of $\sim2$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our 
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 

### 2018-03-26 PAPER.tex
changed 'shows agreement' text to 'shows good agreement'
changed plots to PDFs (except toy model plots)

@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.png}
+	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
 	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
+	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
 	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
+	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
 	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
 	\caption{The power spectrum of PAPER-64 data, weighted by an inverse covariance estimator.
@@
 	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
+	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.pdf}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
 	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and 
@@
 spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
-\eqref{eq:sense}. All three are in agreement, validating our analytical thermal noise calculation.
+\eqref{eq:sense}. All three show good agreement, validating our analytical thermal noise calculation.
 
@@
 	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.png}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.png}
+	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.pdf}
+	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
 	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The original weighted 
@@
 limit. The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
-estimates agree.}
+estimates show good agreement.}
 	\label{fig:ps_noise}
@@
 	\centering
-	\includegraphics[width=0.47\textwidth]{plots/null_bls.png}
-	\includegraphics[width=0.47\textwidth]{plots/null_lsts.png}
-	\includegraphics[width=0.47\textwidth]{plots/null_eo.png}
+	\includegraphics[width=0.47\textwidth]{plots/null_bls.pdf}
+	\includegraphics[width=0.47\textwidth]{plots/null_lsts.pdf}
+	\includegraphics[width=0.47\textwidth]{plots/null_eo.pdf}
 	\caption{Differenced power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).

### 2018-03-26 PAPER.tex
compiled with plots as PDFs

@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.pdf}
 	\caption{Our toy model dataset to which we apply different weighting schemes to in order to investigate signal loss.
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.png}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.pdf}
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
 	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG}$ (blue), $\widehat{\textbf{C}}_{EoR}$ (red), and $\widehat{\textbf{C}}_{FG+EoR}$ 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.png}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
 	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.png}
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
 	\caption{Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
 	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.png}
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.pdf}
 	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.png}
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
 	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
 	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.png}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.png}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.png}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
 	\caption{Resulting power spectra estimates for our `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
 	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.pdf}
 	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias2.png}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias2.pdf}
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/frp.png}
+	\includegraphics[width=\columnwidth]{plots/frp.pdf}
 	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
@@
 	\centering
-	\includegraphics[width=\columnwidth]{plots/sense_check.png}
+	\includegraphics[width=\columnwidth]{plots/sense_check.pdf}
 	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
@@
 	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.png}
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
 	\caption{$2\sigma$ power spectrum errors for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 

### 2018-03-28 PAPER.tex
-Most of Adrian's edits, most notably some syntax and grammar edits and more refs -Made all subscripts non-italicized and standardized units so that they're non-italicized with half spaces

@@
 into a plasma, is known as the Epoch of Reionization (EoR).
-The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans from the birth of the first stars to the full reionization of the intergalactic medium (IGM).
+The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
 Its
@@
 
-Although a detection of the EoR remains elusive, there are several radio telescope experiments that have succeeded in using 
+In addition to the first tentative detection of the EoR signal made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
 the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
-mean brightness temperature of the EoR relative to the CMB are the Experiment to Detect the Global EoR Signature (EDGES; 
-\citealt{bowman2010}), the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
+mean brightness temperature of the EoR relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
 Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
@@
 the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
-\citealt{peterson_et_al2004}; \citealt{wu2009}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
+\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
 Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
@@
 example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
-some EoR signal. A chosen weighting scheme may maximize sensitivity but fail to suppress foregrounds.
+some EoR signal. A chosen weighting scheme may theoretically maximize sensitivity but fail to suppress foregrounds in practice.
 
@@
 \item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
-determine the difference between a detection and a null result, which have two very different implications. Errors can be 
+determine the difference between a detection and a null result, which have two very different implications.
+Additionally, accurate error estimation is crucial for the comparison of results to theoretical models.
+Errors can be
 estimated in a variety of ways, and we will discuss a few of them.
@@
 measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
-successful EoR detection would also imitate a bias. Proving a bias is an EoR detection may be the most difficult challenge for 21\,cm 
+successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
 analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
@@
 (\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
-independent samples. However, when adjusting the shape of the filter to match the rate of sidereal motion, it can also affect the presence 
+independent samples. However, such a filter also affects the presence 
 of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
@@
 foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of optimal quadratic estimators (OQE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
+estimation technique of quadratic estimators (QE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
 Before showing
-how signal loss can arise when using different weighting matrices, we first summarize OQE as performed in the PAPER 
+how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER 
 analysis.
@@
 We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
-It has length $N_{t} \times N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where
+It has length $N_{t}N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where
 $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
-the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier-modes 
+the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes 
 we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
@@
 \end{equation}
-Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them into 
-power spectrum space, while also converting from Jy to 
+Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to 
 Kelvin and taking into account cosmological scalings.
-It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C}$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
-Fourier-dual to frequency under the delay approximation (\citealt{parsons_et_al2012b})). $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as 
-an example, inverse covariance weighting would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
+It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\vec{\textbf{x}}\vec{\textbf{x}}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
+Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximations for the short baselines that PAPER analyzes).
+$\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as
+an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
 \textbf{R} \equiv \textbf{I}$, the identity matrix.
@@
 \noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum $\textbf{p}$. The data analyst has a choice for $
-\textbf{M}$ (subject to the constraint that window functions integrate to unity) --- for simplicity in this section we choose $\textbf{M}$ to be diagonal ($\textbf{M} \propto \textbf{I}$), although we explore other cases for the analysis
-of PAPER-64 data as explained in Section \ref{sec:Bias}.
+\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
+of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{p}}$ is a weighted sum of the elements of $\textbf{p}$ with weights that sum to unity.
 
@@
 This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
-Said differently, it gives the minimum variance estimate of the power spectrum of a signal (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
+Said differently, it gives the minimum variance estimate of the power spectrum (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
 In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
@@
 One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
-By definition, inverse covariance weighting does not lead to signal loss.
+By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
 Therefore, in an ideal world with perfect foreground,
@@
 
-We construct a simple dataset that contains 2-dimensional data (representing visibility data with $100$ time 
-integrations and $20$ frequency channels). This model represents realistic dimensions of about an hour of PAPER data which 
+We construct a simple dataset that contains visibility data with $100$ time 
+integrations and $20$ frequency channels. This model represents realistic dimensions of about an hour of PAPER data which 
 might be used for a power spectrum analysis. For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel 
-widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down for this toy model with no loss of 
+widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of 
 generality.
@@
 single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
-realistic EoR signal would have a sloped power spectrum in $\textbf{p}(k)$ (instead of flat, as in the case of white noise), 
+realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), 
 which could be simulated by introducing frequency correlations into the mock EoR signal. However, here we treat all 
@@
 
-First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using OQE formalism and $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$. 
+First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using QE formalism and $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$. 
 The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
@@
 \textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in OQE power spectrum estimation.
+In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
 The modes with the highest eigenvalues are
@@
 In general, the strongest eigenmodes of $\widehat{\textbf{C}}$ typically describe bright foregrounds --- the most prominent shapes in a dataset.
-For these `strong' modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for the `strong' eigenmodes to be coupled to the data in a way that produces loss.
-For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss2} by the missing foreground peak in the weighted power spectrum estimate (green).
+For these ``strong" modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
+In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for the ``strong" eigenmodes to be coupled to the data in a way that produces loss.
+For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
 
@@
 
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the `weak' eigenmodes of $
+The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the ``weak" eigenmodes of $
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
@@
 More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the `weak' modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
+Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the ``weak" modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
 
@@
 The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
-\ref{fig:toy_sigloss15}. The spectrum, in the case of fringe-rate filtering (dashed line), falls more steeply, especially for 
-the last few eigenmodes. In many applications, this steep fall is not indicative of the true covariance structure of the data.
-
-With 
+\ref{fig:toy_sigloss15}. With 
 fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
@@
 In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-Said differently, a steep covariance eigenspectrum can be especially dangerous because it is the `weak' modes that are both EoR-dominated and converge the slowest and are therefore susceptible to the most loss.
+Said differently, a steep covariance eigenspectrum can be especially dangerous because it is the ``weak" modes that are both EoR-dominated and converge the slowest and are therefore susceptible to the most loss.
 %\acl{Think about whether we need to do the Fourier space version as well.}
@@
 The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that `strong' eigenmodes (those with the highest eigenvalues) converge more quickly than `weak' eigenmodes, implying that weighting by empirically estimated `weak' modes poses the most risk for signal loss.}
+This figure shows that ``strong" eigenmodes (those with the highest eigenvalues) converge more quickly than ``weak" eigenmodes, implying that weighting by empirically estimated ``weak" modes poses the most risk for signal loss.}
 	\label{fig:toy_sigloss17}
@@
 
-In Section \ref{sec:toymodel} we showed one example (projecting the zeroth eigenmode) of how altering $\widehat{\textbf{C}}$ can 
+In Section \ref{sec:toymodel} we showed one example of how altering $\widehat{\textbf{C}}$ can 
 make the difference between nearly zero and some signal loss. We will now use our toy model to describe several other ways to tailor $\widehat{\textbf{C}}$ 
@@
 This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\textbf{C}_{FG}$ is unknown.
+In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\widehat{\textbf{C}}_{FG}$ is unknown because we don't know how to separate out the foregrounds from the EoR in our data.
 
@@
 Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
-Although there is negligible signal loss using this regularization, the small green peak at $k\sim3$ represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way - 
+Although there is negligible signal loss using this regularization, the small green peak at the third $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
+
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
 by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
 method intentionally projects out the strongest modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of `weak' modes which are coupled to the data results in negligible signal loss. However, we do 
+eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of ``weak" modes which are coupled to the data results in negligible signal loss. However, we do 
 not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes.
@@
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it's no longer coupled to either the `strong' or `weak' eigenmodes.
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to either the ``strong" or ``weak" eigenmodes.
 For this toy model,
 our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
-the identity, element-wise, results in a diagonal matrix, meaning we are only left with correlation information between the same 
-two pairs of frequencies. Because we disregard information from all other frequency combinations in this case, we do a poor job 
+the identity, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
 suppressing the foreground.
@@
 system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
-two don't always agree due to a number of factors, including possible non-Gaussianities in the noise properties of our instruments and non-uniform 
-weightings.
+two do not always agree due to a number of factors, including possible non-Gaussianities in the noise properties of our instruments and possible systematics in the data.
 
@@
 This involves the assumption of Gaussianity, but allows the variance of the power spectrum estimator to be written as a function of the two-point estimator, or covariance.
-One could empirically calculate the covariance and then propagate it into an analytic expression to compute the errors, making this method fall somewhere between fully empirical and fully modeled (see \citet{das_et_al2011a} for an example of its implementation).
+One could empirically calculate the covariance and then propagate it into an analytic expression to compute the errors, making this method fall somewhere between being fully empirical and fully modeled (see \citet{das_et_al2011a} for an example of its implementation).
 
@@
 Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
-between them. Through the process of re-sampling and averaging along different axes, we can estimate error bars for 
+between them. Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for 
 our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
 
-Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements made along different axes, such as baselines or times). 
-Bootstrapping means that we form $N_{boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
+Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements). 
+Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
 of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
@@
 
-We must be careful in distinguishing $N_{boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
-values, that comprise a bootstrap. In the toy models presented in this section, $N_{boot}$ is typically large, and the standard 
-deviation across bootstraps (the error we are computing) converges for large $N_{boot}$.
+We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
+values, that comprise a bootstrap. In the toy models presented in this section, $N_{\rm boot}$ is typically large, and the standard 
+deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
 Typically $N$ is a straightforward value to set that just depends on the experiment.
@@
 
-We next form $500$ bootstraps ($N_{boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
+We next form $500$ bootstraps ($N_{\rm boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
 original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
@@
 number of independent samples along the axis that is being re-sampled is well-determined.
-In Section \ref{sec:Boot}, we explain how we under-estimated errors in the \citetalias{ali_et_al2015} analysis of PAPER and how our bootstrapping procedure has now changed in light of this issue.
+In Section \ref{sec:Boot}, we explain how we under-estimated errors in the \citetalias{ali_et_al2015} analysis of PAPER and how our bootstrapping procedure has now changed to avoid the over-sampling of correlated data.
 
@@
 	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-sampling with replacement. The star represents the standard deviation of $N_{boot}=500$ bootstraps, each created by drawing $1000$ 
+sampling with replacement. The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ 
 elements (with replacement) from a length $1000$ array of a Gaussian random signal.
@@
 In Section \ref{sec:SiglossOverview}, we discussed signal loss as a form of multiplicative bias to estimates of the signal.
-Foregrounds are another type of bias, but an additive one instead of multiplicative.
+Foregrounds are another type of bias, but an additive instead of a multiplicative one.
 Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
@@
 Though there are many techniques proposed for removing foregrounds (see e.g.
-\citealt{vedantham_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
+\citealt{vedantham_et_al2012}; \citealt{chapman_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{wolz_et_al2014}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
 experiments currently remain limited by residuals rather than noise, especially at low $k$.
 
-For a particular 
+One common method to isolate and filter foregrounds is to exploit their behavior in $k$-space. For a particular 
 baseline length, there is a maximum delay imposed on sources attached to the sky, which corresponds to the light-crossing time between two 
@@
 
-Although smooth spectrum foregrounds preferentially show up at low delay, or low $k$-modes, their isolation within the wedge is not perfect.
+Although smooth-spectrum foregrounds preferentially show up at low delay, or low $k$-modes, their isolation within the wedge is not perfect.
 In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
@@
 spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the leakage from a particular 
-$k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using OQE that forces a 
+$k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using QE that forces a 
 window function to have a minimum response to low $k$ values. The window function used in \citetalias{ali_et_al2015} is constructed in such a way, 
@@
 two quantities that go into a measurement have separate noises that don't correlate with each other.
-We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous by \citet{dillon_et_al2014}.
+We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous (\citealt{dillon_et_al2014}).
 
@@
 \begin{eqnarray}
-\textbf{x}_{1} &=& \textbf{n} + \textbf{e} + \textbf{f} \\
-\textbf{x}_{2} &=& \textbf{n} + \textbf{e} 
+\textbf{x}_{1} &=& \textbf{n}_{1} + \textbf{e}_{1} + \textbf{f} \\
+\textbf{x}_{2} &=& \textbf{n}_{2} + \textbf{e}_{2}
 \end{eqnarray}
@@
 Similarly, $\textbf{x}_{2b}$ represents a jackknife sample (second half of the data) for the second measurement.
+We note that $\textbf{e}$ itself will be different in two jackknives taken along LST, but could be identical in other cases (such as a jackknife along even/odd Julian days).
 
@@
 \begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\widehat{\textbf{p}}\textbf{(k)},
-\end{equation}
-
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$ h Mpc$^{-1}$ at $z = 8.4$.
+\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{p}(k),
+\end{equation}
+
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$.
 The revision of this limit (Kolopanis et al.
@@
 For our revised analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly longer RA 
-range of $0$-$8.6$ hours; we found that some early LSTs were contaminated).
+range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
 All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
@@
 In \citetalias{ali_et_al2015}, the
-applied filter was degraded by widening it in fringe-rate space. This was chosen in order to increase the number of independent 
+applied filter was not equivalent to the optimal fringe-rate filter (which is designed to maximize power spectrum sensitivity).
+Instead, the optimal filter was degraded by widening it in fringe-rate space.
+This was chosen in order to increase the number of independent
 modes and reduce signal loss, though as we will explain in the next section, this signal loss was still under-estimated. With the development of a new, 
@@
 Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals)
-are filtered in fringe-rate space to retain only ``sky-like" time-modes. This signal is then added to the data.\footnote{One 
+are filtered in time using an optimal fringe-rate filter to retain only ``sky-like" modes.
+Since the optimal filter has a shape that matches the rate of the sidereal motion of the sky, this transforms the Gaussian noise into a measurement that PAPER could make.
+This signal is then added to the data.\footnote{One
 specific change from \citetalias{ali_et_al2015} is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
@@
 We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
-spectrum according to OQE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
+spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
 output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as
@@
 \end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with diagonal normalization matrices M, even though for our numerical results we choose a non-diagonal matrix $\mathbf{M}$ as in Equation \eqref{eq:phat}.
+where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a non-diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
 
@@
 Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
+Therefore, $P_{\rm out}$ can be directly compared to the measurement that we make.
 
@@
 %\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-%which assumes that the covariance used in the OQE analysis is close to the true covariance with effects due to 
+%which assumes that the covariance used in the QE analysis is close to the true covariance with effects due to 
 %small sample size limited to first order perturbations and thus neglects cross-correlation between $x$ and $e$.  
@@
 %
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our OQE power spectrum pipeline.
+%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a Gaussian with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
 We also note that in this regime, $\widehat{\textbf{p}}_{r}$ (black) approaches the data level (gray) as expected.
@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a Gaussian distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
 
@@
 $\widehat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
-Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$ in the
-$|\textbf{x}|\ll|\textbf{e}|$ regime:
+Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$:
 
@@
 
-{\bf In general:} Another way to phrase the shortcoming of the inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized.
+{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized.
 Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
@@
 P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the reverse probability, which we do know.
+Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
 In other words,
@@
 To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
-We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
+We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
 $P_{\rm out}$ grid.
@@
 We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $P_{\rm out} = \widehat{\textbf{p}}_{x}$ to yield a posterior distribution for the signal.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{p}}_{x}$ (setting $P_{\rm out} = \widehat{\textbf{p}}_{x}$) to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 \widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a
-value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10^{4}$.
-For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.
+From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{8} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
+For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.
 
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed), a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data.
+Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
-foregrounds and systematics in our data without generating large amounts of signal loss as we've seen with the inverse covariance estimator. We have found that the balance 
+foregrounds and systematics in our data without generating large amounts of signal loss as we have seen with the inverse covariance estimator. We have found that the balance 
 between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
@@
 We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
-eigenspectrum and effectively de-coupling the `weak' eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
+eigenspectrum and effectively de-coupling the ``weak" eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
 that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
@@
 estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (gray curve). In other words, more `weak' (EoR-dominated) fluctuations are being overfit and 
+becomes more aggressive (gray curve). In other words, more ``weak" (EoR-dominated) fluctuations are being overfit and 
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
-From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss.
+The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the Tr($\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
+From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
 We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
+	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
 are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
@@
 Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $0.01\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e.
-very little regularization) to $100\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left.
+This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e.
+very little regularization) to $\gamma = 1$ on the left.
 Also
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.035Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ as a simple example of regularization that minimizes loss.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss.}
 	\label{fig:sigloss_modeloop}
@@
 matrix element-wise to $\widehat{\textbf{C}}$).
-This result is single-valued and not a function of the x-axes.
+This result is single-valued and not a function of the horizontal axis.
 We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at
@@
 when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035Tr(\widehat{\textbf{C}})$, which we will denote as $\widehat{\textbf{C}}_{eff}$.
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
 We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, though we note that in Kolopanis et al.
 (\textit{submitted}), we choose the most optimal regularization parameter for our final limits for every redshift bin independently.
-We also note that all of the regularizations described here perform similarly to the uniformly weighted case; this is likely because we are in a regime where it is very difficult to disentangle foreground modes from those of EoR.
-We see that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al.
+We also note that all of the regularizations described here perform similarly to the uniformly weighted case.
+However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al.
 (\textit{submitted}).
 
-A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{eff}$) is shown in Figure 
+A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
 \ref{fig:ps1_data}.
@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{eff}$. The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and 
+	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{\rm eff}$.
+The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and
 negative power spectrum values, respectively, with $2\sigma$ error bars).
@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
@@
 when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
-21\,cm signal, and it's worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
+21\,cm signal, and it is worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
@@
 
-In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra. We first walk through a derivation 
-for a theoretical error estimation (of thermal noise) based on observational parameters. Although a theoretical model often 
+In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
+We first walk through an expression for a theoretical error estimation (of thermal noise) based on observational parameters.
+Although a theoretical model often
 differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors 
@@
 
-The sensitivity prediction (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
+The noise prediction $n(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
 interferometric 21\,cm data, in temperature-units, is:
@@
 \label{eq:sense}
-p(k) = \frac{X^{2}Y \Omega_{eff} T_{sys}^{2}}{\sqrt{2N_{lst}N_{seps}}\,t_{int}N_{days}N_{bls}N_{pols}}.
+n(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
 \end{equation}
@@
 \item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
-distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
-\item $\Omega_{eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
+distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} \, h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
+\item $\Omega_{\rm eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
 The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted.
-Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
-filter. 
-\item $T_{sys}$: The system temperature is set by:
+Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{\rm eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
+filter and the PAPER primary beam. 
+\item $T_{\rm sys}$: The system temperature is set by:
 
@@
 \label{eq:sys}
-T_{sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{rcvr},
-\end{equation}
-
-where $\nu$ are frequencies in GHz. We use a receiver temperature of $144$\,K, yielding $T_{sys} = 431$\,K at $150$\,MHz. 
-This is lower than the $T_{sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small mis-calculation errors that were 
+T_{\rm sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{\rm rcvr},
+\end{equation}
+
+where $\nu$ are frequencies in GHz (\citealt{thompson_et_al2001}). We use a receiver temperature of $144$\,K, yielding $T_{\rm sys} = 431$\,K at $150$\,MHz. 
+This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small mis-calculation errors that were 
 identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying independent `even' and `odd' visibility measurements (which is done principally to avoid a noise bias).
+estimates after cross-multiplying independent ``even" and ``odd" visibility measurements (this cross-multiplication is done principally to avoid a noise bias).
 In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
-\item $N_{lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
-because we integrate incoherently over time. For PAPER-64, $N_{lst} = 8$.
-\item $N_{seps}$: The number of baseline separation types averaged incoherently in a final power spectrum estimate. For the 
-analysis in this paper, we only use one type of baseline, hence $N_{seps}=1$. The updated limits in Kolopanis et al. (\textit{submitted})
+\item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
+because we integrate incoherently over time. For PAPER-64, $N_{\rm lst} = 8$.
+\item $N_{\rm seps}$: The number of baseline separation types (where baselines of a unique separation type have the same orientation and length) averaged incoherently in a final power spectrum estimate.
+For the
+analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines), hence $N_{\rm seps}=1$. The updated limits in Kolopanis et al. (\textit{submitted})
 use three separation types.
-\item $t_{int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
+\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
 fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
@@
 \begin{equation}
-t_{int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
-\end{equation}
-where $t_{i}=43$ seconds, $t_{int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
-taken over all fringe-rates. For PAPER-64, this number is $t_{int} = 3857$\,s. 
-\item $N_{days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form `even' and `odd' datasets), this number should be reduced by a factor of $2$. Additionally, 
+t_{\rm int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
+\end{equation}
+where $t_{i}=43$ seconds, $t_{\rm int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
+taken over all fringe-rates. For PAPER-64, this number is $t_{\rm int} = 3857$\,s. 
+\item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
+divide our data in half (to form ``even" and ``odd" datasets), this number should be reduced by a factor of $2$. Additionally, 
 because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
-$N_{days}$ as:
-\begin{equation}
- \frac{1}{N_{days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ is over LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{days}$ is $\sim34$ 
+$N_{\rm days}$ as:
+\begin{equation}
+ \frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
+ \end{equation}
+\noindent where $i$ indexes LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim34$ 
 days.
-\item $N_{bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines neglects 
+\item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
+the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total}$) neglects 
 the fact that we average baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
-N_{bls} = \frac{N_{bls\_total}}{N_{gps}}\sqrt{N_{gps}^{2}-N_{gps}},
-\end{equation}
-\noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{bls\_total}/N_{gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{gps}^{2} - 
-N_{gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{bls} \sim 46$ instead 
+N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{N_{\rm gps}^{2}-N_{\rm gps}},
+\end{equation}
+\noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{\rm gps}^{2} - 
+N_{\rm gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 46$ instead 
 of $51$. 
-\item $N_{pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{pols}=2$.
+\item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
 \end{itemize}
 
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding our power spectra into $\Delta^{2}(k)$, due to averaging 
-together positive and negative $k$'s.
+An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s.
 
@@
 \sqrt{3}$ for three baseline types is needed to match \citetalias{ali_et_al2015} exactly). Major factors that contribute to the discrepancy are $
-\Omega_{eff}$, $N_{days}$ and $N_{bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
+\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
 sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
@@
 To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
-random noise assuming a constant $T_{rcvr}$ (translated into $T_{sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{days}$ as determined 
-by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{sys}$ into a variance statistic 
+random noise assuming a constant $T_{\rm rcvr}$ (translated into $T_{\rm sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{\rm days}$ as determined 
+by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{\rm sys}$ into a root-mean-square variance statistic 
 using:
@@
 \label{eq:noise}
-T_{rms} = \frac{T_{sys}}{\sqrt{\Delta\nu \Delta t N_{days} N_{pols}}},
-\end{equation}
-
-\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{days}$ is the number of daily counts for a 
-particular time and frequency that went into our LST-binned set, and $N_{pols}$ is the number of polarizations ($2$ for Stokes 
-I). This RMS temperature sets the variance of the Gaussian random noise.
+T_{\rm rms} = \frac{T_{\rm sys}}{\sqrt{\Delta\nu \Delta t N_{\rm days} N_{\rm pols}}},
+\end{equation}
+
+\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{\rm days}$ is the number of daily counts for a 
+particular time and frequency that went into our LST-binned set, and $N_{\rm pols}$ is the number of polarizations ($2$ for Stokes 
+I). This temperature sets the variance of the Gaussian random noise.
 
@@
 \ref{fig:ps_noise}, where the black and gray points represent pre-signal loss estimated positive and negative power spectrum values, respectively (with 
-$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{eff}$), the dashed black line represents the post-signal loss $2\sigma$ upper limit on the EoR signal, the dashed blue line represents the $2\sigma$ uniform-weighted power
+$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{\rm eff}$), the dashed black line represents the post-signal loss $2\sigma$ upper limit on the EoR signal, the dashed blue line represents the $2\sigma$ uniform-weighted power
 spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
@@
 power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
-\widehat{\textbf{C}}_{eff}$ to minimize signal loss.
+\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
 The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation.
@@
 In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
-($N_{boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
+($N_{\rm boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
 specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
@@
 exceeded the number of independent LST samples, under-estimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds ($N_{boot}$) of these random 
+measurements from this dataset has many repeated values, and the variance between hundreds ($N_{\rm boot}$) of these random 
 samples is smaller than the true underlying variance of the data.
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
-We note that they do not match perfectly, but we find good agreement between them to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic.
+We note that they do not match perfectly, but we find good agreement between them to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.
 While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
-Finally, one last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), is now computed as the power spectrum estimate resulting from not bootstrapping at all.
+Finally, one last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
 More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation.
@@
 have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
-compute $\textbf{M}$ using the Fisher matrix $\textbf{F}$, defined as:
+compute $\textbf{M}$ using the matrix $\textbf{F}$ (chosen because this would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:
 
@@
 Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the
-contamination of foreground bias.
-This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use $\textbf{M} \propto \textbf{I}$ for simplicity.
+contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use a diagonal $\textbf{M}$ for simplicity.
 
@@
 dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
-the `even' dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the `odd' dataset and baseline group $1$, etc. We only form 
-$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying `even' with `even', for 
+the ``even" dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline group $1$, etc. We only form 
+$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``even" with ``even", for 
 example, in order to prevent the squaring of the same thermal noise.
@@
 zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
-on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, power spectrum detections exist at all $k$'s without crosstalk 
+on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, detections of bias exist at all $k$'s without crosstalk 
 removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
 
-\subsubsection{Jackknife Tests}
+\subsubsection{Jackknife/Null Tests}
 
@@
 \item Day: We split our dataset into even and odd Julian dates.
-We form power spectra for each separately, allowing the cross-multiplication of `even' with `even', for example, for this null test only.
-If the same sky signal is in both the `even' and `odd' datasets, we expect it to cancel out.
+We form power spectra for each separately, allowing the cross-multiplication of ``even" with ``even", for example, for this null test only.
+If the same sky signal is in both the ``even" and ``odd" datasets, we expect it to cancel out.
 %However, allowing these cross-multiplications can in practice introduce a low level noise bias...
@@
 All three tests, whether biased or not, have an extra noise bias that is strongly $k$-dependent.
-Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
+Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
 	\label{fig:null}
@@
 %	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
-%	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{eff}$, compared to the analytically estimated 
+%	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{\rm eff}$, compared to the analytically estimated 
 %$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along Julian days (separating 
@@
 
-In investigating Figure \ref{fig:null}, we focus on two main aspects of each test - whether the error bars are consistent with zero, and whether they are consistent with thermal noise.
+In investigating Figure \ref{fig:null}, we focus on two main aspects of each test --- whether the error bars are consistent with zero, and whether they are consistent with thermal noise.
 The former indicates a `passing' null test where there is no bias along the jackknife axis.
@@
 Finally, we note that all three null tests exhibit error bars that are strongly $k$-dependent.
-The errors are largest just outside the horizon ($k\sim\pm 0.1$ $h$Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
+The errors are largest just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
 We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
@@
 Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
-This is because cross-multiplications produce four additive terms - a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
 When differencing two power spectra, we expect the signal-only term to subtract out for a `passing' null test, and we expect the noise-only terms to be consistent with thermal noise.
@@
 In Kolopanis et al.
-(\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$\,$h$ Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously under-estimated limit and 
@@
 \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. We 
-note that PAPER's analysis is not the first to under-estimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also 
+factor of $\sim10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. 
+This revision is similar to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.

### 2018-03-28 PAPER.tex
added to jackknife section to clarify that the PSA64 tests are a hybrid approach

@@
 As discussed in Section \ref{sec:BiasTypes}, this bias is
-most likely attributable to foreground leakage.
-The cause for biases at higher $k$-values is more difficult to pinpoint.
-Here we discuss three null tests performed on PAPER-64 data that aim to isolate systematics in the data and verify
+most likely attributable to foreground leakage. The cause for biases at higher $k$-values is more difficult to pinpoint.
+
+Here we perform three hybrid jackknife/null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
 that they are not attributable to EoR.
-We build off of the framework in Section \ref{sec:JackknifeOverview}, which illuminated how jackknife tests can tease out excess variances along different axes of a dataset.
-
-Three null test results are shown in Figure \ref{fig:null}. Each test displays the differenced power spectrum between two halves of a jackknife. We take jackknives along three different axes:
+Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
+In addition, we difference them to tease out excess variances, which can be thought of as a type of null test.
+
+The three results are shown in Figure \ref{fig:null}. Each test displays the differenced power spectrum between two halves of a jackknife. We take jackknives along three different axes:
 
@@
 The cause of this particular systematic is not obvious, and requires further investigation that we do not carry out in this paper.
-Most importantly, a clean detection of EoR would have passed all three null tests, which is clearly not what we see.
+Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
 

### 2018-03-28 PAPER.tex
standardized axes labels with no italicized for units, also removed italicization in subscripts in text

@@
 from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
-\textbf{x}_{FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
-single bright source. We also create a mock EoR signal, $\textbf{x}_{EoR}$, as a complex, Gaussian random signal. A more 
+\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
+single bright source. We also create a mock EoR signal, $\textbf{x}_{\rm EoR}$, as a complex, Gaussian random signal. A more 
 realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), 
@@
 $k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
-\textbf{x}_{FG} + \textbf{x}_{EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
+\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
 \ref{fig:toy_sigloss1}.
@@
 time and frequency. We model a mock EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
-\textbf{x}_{FG} + \textbf{x}_{EoR}$. Real parts are shown here.}
+\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$. Real parts are shown here.}
 	\label{fig:toy_sigloss1}
@@
 Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $
-\textbf{x}_{FG}$ (blue) and $\textbf{x}_{EoR}$ (red).
+\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
-	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG}$ (blue), $\widehat{\textbf{C}}_{EoR}$ (red), and $\widehat{\textbf{C}}_{FG+EoR}$ 
-(green). The eigenspectrum of $\widehat{\textbf{C}}_{FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
+	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
+(green). The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
 sinusoid.
@@
 In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
-The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{FG}$.
+The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
-	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
+	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
 The dashed, steep eigenspectrum has a greater risk of signal loss because its weak eigenmodes are more strongly coupled to the data than those of the solid eigenspectrum.}
@@
 avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{EoR}$ as such (i.e. the identity), instead of computing it based on $\textbf{x}
-_{EoR}$ itself. Next, we add $\textbf{C}_{EoR} + \widehat{\textbf{C}}_{FG}$ (where $\widehat{\textbf{C}}_{FG} = \langle\textbf{x}_{FG}
-\textbf{x}_{FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e. the identity), instead of computing it based on $\textbf{x}
+_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
+\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}_{EoR}$ would).
+This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would).
 This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{EoR}$, and $\widehat{\textbf{C}}_{FG}$ is unknown because we don't know how to separate out the foregrounds from the EoR in our data.
+In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we don't know how to separate out the foregrounds from the EoR in our data.
 
@@
 it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
-$\widehat{\textbf{C}}$ (lower right). The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{FG}$ and $\textbf{C}_{EoR}$ like we do in the toy model.}
+$\widehat{\textbf{C}}$ (lower right). The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
 	\label{fig:toy_sigloss8}
@@
 two quantities that go into a measurement have separate noises that don't correlate with each other.
-We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous (\citealt{dillon_et_al2014}).
+We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous (\citealt{dillon_et_al2014}; \citealt{parsons_et_al2014}).
 

### 2018-03-30 PAPER.tex
made all of Jonnie's minor edits

@@
 The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
+instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
 A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
@@
 
-Finally, this paper adds to the growing foundations of lessons which have been documented in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
+Finally, this paper adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
 These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
@@
 Kelvin and taking into account cosmological scalings.
-It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\vec{\textbf{x}}\vec{\textbf{x}}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
-Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximations for the short baselines that PAPER analyzes).
+It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
+Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
 $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 \label{eq:phat}
-\widehat{\textbf{p}} = \textbf{M}\widehat{\textbf{q}},
-\end{equation}
-
-\noindent where $\widehat{\textbf{p}}$ is the estimate of the true power spectrum $\textbf{p}$. The data analyst has a choice for $
+\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}},
+\end{equation}
+
+\noindent where $\widehat{\textbf{P}}$ is the estimate of the true power spectrum $\textbf{P}$. The data analyst has a choice for $
 \textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
-of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{p}}$ is a weighted sum of the elements of $\textbf{p}$ with weights that sum to unity.
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{p}}$.
+of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{P}}$ is a weighted sum of the elements of $\textbf{P}$ with weights that sum to unity.
+
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
 Our goal in
@@
 We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation. Hence, flat spectrum sources (away 
-from zenith) oscillate in time and frequency in our measurements. We therefore form a mock bright foreground signal, $
+from zenith) lead to measured visibilities which oscillate in time and frequency. We therefore form a mock visibility measurement of a bright foreground signal, $
 \textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
-single bright source. We also create a mock EoR signal, $\textbf{x}_{\rm EoR}$, as a complex, Gaussian random signal. A more 
+single bright source. We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal. A more 
 realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), 
@@
 We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in
-time and frequency. We model a mock EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
+time and frequency. We model a mock visibility of an EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
 \textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$. Real parts are shown here.}
@@
 power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
-demonstrating that if we can disentangle the foreground-dominating modes from EoR-dominating modes, we can down-weight 
+demonstrating that if we can disentangle the foreground-dominating modes and EoR-dominating modes, we can down-weight 
 them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
@@
 We have shown how signal loss can arise due to the coupling of weak eigenmodes (EoR-dominated modes) to the data.
-We will next show how this effect is exaggerated by reducing the total number of independent
+We will next show how this effect is exacerbated by reducing the total number of independent
 samples in a dataset.
@@
 foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum, the signal chain, and the 
-antenna response, all of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017}.
+antenna response, all of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017, kerrigan_et_al2018}.
 
@@
 \begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{p}(k),
+\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{P}(k),
 \end{equation}
@@
 \label{eq:sigloss}
-P_{\rm out,\alpha} &\equiv& \widehat{\textbf{p}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{p}}_{x,\alpha} \nonumber \\
+P_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
 &=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
@@
 %\begin{equation}
-%P_{\rm out} = \widehat{\textbf{p}}_{x} \label{eqn:anzatz},
+%P_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
 %\end{equation}
@@
 %
-%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{p}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{p}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
+%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
+We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
 %
@@
 \end{eqnarray}
-Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms can be summed together as:
+Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:
 
@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
-We also note that in this regime, $\widehat{\textbf{p}}_{r}$ (black) approaches the data level (gray) as expected.
+In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
+We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data level (gray) as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{p_e}\sqrt{p_x}$.
+The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
 
@@
 	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
-data. The net output ($P_{\rm out}=\widehat{\textbf{p}}_r$) is shown in black, the individual terms, as defined by Equation 
+data. The net output ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, the individual terms, as defined by Equation 
 \eqref{eq:crossterm},  are shown in blue, red, green; the dotted black line indicates 1:1 input to output mapping.  The 
@@
 regime where cross-correlations between injection and data are not dominant, the cross-terms have a noise-like 
-term with width $\sqrt{p_e}\sqrt{p_x}$.
+term with width $\sqrt{P_e}\sqrt{P_x}$.
 However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
@@
 We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{p}}_{x}$ (setting $P_{\rm out} = \widehat{\textbf{p}}_{x}$) to yield a posterior distribution for the signal.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $P_{\rm out} = \widehat{\textbf{P}}_{x}$) to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
-\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines.
+\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
 From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{8} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
@@
 heat-maps on top of the points for the cases of empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted.
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.
 From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed).
+Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (blue dashed).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim3$-$4$ eigenmodes are down-weighted and the rest are given equal weights.
+only the strongest $\sim2$ eigenmodes are down-weighted and the rest are given equal weights.
 For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the Tr($\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$.
+The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
+We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
 From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
@@
 This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e.
-very little regularization) to $\gamma = 1$ on the left.
+very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
 Also
@@
 their best (i.e.
-when $\sim3$$-4$ eigenmodes are down-weighted in the case of the black solid curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
+when $\sim2$ eigenmodes are down-weighted in the case of the black solid curve).
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
 We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, though we note that in Kolopanis et al.
@@
 \label{eq:sense}
-n(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
+N(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
 \end{equation}
@@
 
-The minimum-variance quadratic estimator $\widehat{p}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\begin{equation}
-\widehat{p}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
+The minimum-variance quadratic estimator $\widehat{P}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
+\begin{equation}
+\widehat{P}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
 \end{equation}
@@
 \label{eq:phatloss}
-\widehat{p}_\alpha^\textrm{loss} = \frac{1} {2 \widehat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
+\widehat{P}_\alpha^\textrm{loss} = \frac{1} {2 \widehat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
 \end{equation}
@@
 
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{p}_\alpha^\textrm{loss}$ in terms of $\widehat{p}_\alpha$.
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{P}_\alpha^\textrm{loss}$ in terms of $\widehat{P}_\alpha$.
 We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
@@
 \label{eq:phatlossexpanded}
-\widehat{p}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
+\widehat{P}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
 \end{equation}
@@
 \begin{equation}
-\widehat{p}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
+\widehat{P}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
 \end{equation}
@@
 \begin{equation}
-\langle \widehat{p}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) p_\alpha,
+\langle \widehat{P}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) p_\alpha,
 \end{equation}
@@
 
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{p}}_{r} - \widehat{\textbf{p}}_{x}$.
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
@@
 After all, the universe doesn't do any signal injections.
-I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{p}}_{r}$, the weighted power spectrum of the data plus injected signal.
+I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{P}}_{r}$, the weighted power spectrum of the data plus injected signal.
 
@@
 \includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
-\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
+\caption{The distribution of $\widehat{\textbf{P}}_{r}$ values for a 
 given injection level P$_{\rm in}$.
-The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
+The $\widehat{\textbf{P}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
 It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
@@
 The dotted black
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution.
-At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{P}}_{x}$, the data distribution.
+At low injection, $\widehat{\textbf{P}}_{r}$ converges to the data level.
 }
@@
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $\widehat{\textbf{p}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
+In the 2D space relating total $\widehat{\textbf{P}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
 data only) and very large levels are dominated by the injected signal.
@@
 \caption{The probability that an injected signal of level P$_{\rm inj}$
-is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{p}}_{x}$ (data).
+is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{P}}_{x}$ (data).
 The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.}
@@
 Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of ``data + 
-injected eor" ($\widehat{p}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{p}_x$. 
+injected eor" ($\widehat{P}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{P}_x$. 
 In other words, what is $e$ such that,
 \begin{equation}
-\widehat{\textbf{p}}_{e+x} > \widehat{\textbf{p}}_{x},
+\widehat{\textbf{P}}_{e+x} > \widehat{\textbf{P}}_{x},
 \end{equation}  
@@
  \begin{equation}
- \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{p}}_x) dx = \Lambda,
+ \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{P}}_x) dx = \Lambda,
  \end{equation}
@@
   \begin{equation}
- \int_{x_0}^\infty \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) dx.
+ \int_{x_0}^\infty \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) dx.
 \end{equation}
@@
  \begin{equation}
-\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{p}}_x) \Prob(\widehat{\textbf{p}}_{e+x}|P_{e}) x
- \end{equation}
- where $\Prob(\widehat{\textbf{p}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{p}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{p}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{p}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{P}}_x) \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) x
+ \end{equation}
+ where $\Prob(\widehat{\textbf{P}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{P}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{P}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{P}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
 

### 2018-03-30 PAPER.tex
made more of Jonnie's edits, namely removed text referring to 'strong' vs. 'weak' modes

@@
 case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
-For an empirically estimated $\widehat{\textbf{C}}$, its eigenvalues differ from those of the true covariance, where the weakest (EoR-dominated) eigenmodes are the most strongly coupled to the data and can lead to the most loss.
-Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are not using the relative weights of the weaker eigenmodes.}
+For an empirically estimated $\widehat{\textbf{C}}$, its eigenvalues differ from those of the true covariance, where the coupling between EoR-dominated eigenmodes and the data can lead to loss.
+Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are only down-weighting the FG-dominating mode in this case.}
 	\label{fig:toy_sigloss3}
@@
 Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-For example, the strongest mode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
+For example, the highest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
 In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
@@
 
-In general, the strongest eigenmodes of $\widehat{\textbf{C}}$ typically describe bright foregrounds --- the most prominent shapes in a dataset.
-For these ``strong" modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for the ``strong" eigenmodes to be coupled to the data in a way that produces loss.
+In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
+For these FG-dominating modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
+In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
 For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
@@
 
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the ``weak" eigenmodes of $
+The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominating eigenmodes of $
 \textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
@@
 More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the ``weak" modes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
+Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
 
@@
 project out the first eigenmode and then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the weaker part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
+Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
 only allowing over-fitting to occur for the first mode).
@@
 
-We have shown how signal loss can arise due to the coupling of weak eigenmodes (EoR-dominated modes) to the data.
-We will next show how this effect is exacerbated by reducing the total number of independent
+We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data. We will next show how this effect is exacerbated by reducing the total number of independent 
 samples in a dataset.
@@
 where $\C$ is the true covariance matrix.
-In Figure \ref{fig:toy_sigloss16} we show this convergence statistic as a function of the number of independent ensemble realizations in one's simulations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors).
+To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average.
+We then compare this to the ``true' covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
+As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors).
 With more independent time samples (i.e.
@@
 The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-One sees that the stronger eigenmodes converge to their true eigenvectors more quickly.
+One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
 With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
-As we will see in the next section, using only the strongest eigenmodes, which are less coupled to data realizations, minimizes signal loss.
-In contrast, the weaker eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-Said differently, a steep covariance eigenspectrum can be especially dangerous because it is the ``weak" modes that are both EoR-dominated and converge the slowest and are therefore susceptible to the most loss.
+As we will see in the next section, using only these eigenmodes, which are less coupled to data realizations, minimizes signal loss.
+In contrast, the lower-valued eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
+Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
 %\acl{Think about whether we need to do the Fourier space version as well.}
@@
 	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
-The dashed, steep eigenspectrum has a greater risk of signal loss because its weak eigenmodes are more strongly coupled to the data than those of the solid eigenspectrum.}
+The dashed, steep eigenspectrum has a greater risk of signal loss because its lowest-valued eigenmodes are both more strongly coupled to the data (than those of the solid eigenspectrum) and, in this example, are also EoR-dominated.}
 	\label{fig:toy_sigloss15}
@@
 The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that ``strong" eigenmodes (those with the highest eigenvalues) converge more quickly than ``weak" eigenmodes, implying that weighting by empirically estimated ``weak" modes poses the most risk for signal loss.}
+This figure shows that the highest-valued modes converge more quickly than the others, implying that weighting by the lowest-valued empirically estimated modes poses the most risk for loss.
+Since these modes are also typically EoR-dominated, this can lead to cosmological signal loss.}
 	\label{fig:toy_sigloss17}
@@
 by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
-method intentionally projects out the strongest modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of ``weak" modes which are coupled to the data results in negligible signal loss. However, we do 
+method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
+eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominating modes which are coupled to the data results in negligible signal loss. However, we do 
 not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes.
@@
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to either the ``strong" or ``weak" eigenmodes.
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to any of the empirically estimated eigenmodes.
 For this toy model,
@@
 In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
-We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data level (gray) as expected.
+We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
@@
 This negative component drives down the $P_{\rm out}$ estimator (black).
-We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data level.
+We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
 Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.
@@
 	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
-data. The net output ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, the individual terms, as defined by Equation 
-\eqref{eq:crossterm},  are shown in blue, red, green; the dotted black line indicates 1:1 input to output mapping.  The 
-empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015} is on the left and the uniform-weighted 
-case is on the right. The details of the simulation used to generate the figure is explained in Section 
+data.
+Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}.
+The output power spectrum ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
+\eqref{eq:crossterm} are shown in blue, red, and green.
+The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss).
+The details of the simulation used to generate the figure is explained in Section
 \ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
-horizontal line is the power spectrum value of data alone (doesn't depend on injected power). The green signal-signal 
+horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
 component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
-than the net output because the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
-regime where cross-correlations between injection and data are not dominant, the cross-terms have a noise-like 
+than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
+regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
 term with width $\sqrt{P_e}\sqrt{P_x}$.
@@
 $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for 
-the weighted case). }
+the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
 	\label{fig:sigloss_terms}
@@
 
-\noindent where we can neglect the first term because $\textbf{x}$ is small.  Without loss of generality, we will assume
+\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e.
+the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
+Without loss of generality, we will assume
 an eigenbasis of $\textbf{e}$, so that $\langle 
@@
 The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data with the goal of simultaneously capturing variance due to noise and signal loss.
+In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing variance due to noise and signal loss.
 To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
@@
 diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does
+From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does
 not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
@@
 We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
-eigenspectrum and effectively de-coupling the ``weak" eigenmodes from the data) can help minimize signal loss. We experiment with this idea on PAPER-64 data, dialing the number of modes 
+eigenspectrum and effectively de-coupling the lowest-valued eigenmodes from the data, which converge to the true eigenspectrum the slowest and are often EoR-dominated) can help minimize signal loss.
+We experiment with this idea on PAPER-64 data, dialing the number of modes
 that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
@@
 estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (gray curve). In other words, more ``weak" (EoR-dominated) fluctuations are being overfit and 
+becomes more aggressive (gray curve). In other words, more EoR-dominated fluctuations are being overfit and 
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the strongest $\sim2$ eigenmodes are down-weighted and the rest are given equal weights.
+only the $\sim2$ highest-valued eigenmodes are down-weighted and the rest are given equal weights.
 For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
@@
 spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
-\eqref{eq:sense}. All three show good agreement, validating our analytical thermal noise calculation.
+\eqref{eq:sense}. All three show good agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.
 
@@
 limit. The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
-estimates show good agreement.}
+estimates show agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.}
 	\label{fig:ps_noise}
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
-We note that they do not match perfectly, but we find good agreement between them to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.
+We note that they do not match perfectly, but we find good agreement given the approximations we make in computing the thermal noise level.
 While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
@@
 More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation.
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the maximum likelihood estimate of our data.
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.
 
@@
 We recognize that this method results in a hit to our sensitivity.
-Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the \citetalias{ali_et_al2015} analysis (which uses the same groupings), not produce the most sensitive limits of PAPER-64.
+Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the \citetalias{ali_et_al2015} analysis (which uses the same groupings).
 
@@
 zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
-on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, detections of bias exist at all $k$'s without crosstalk 
-removal and these are detections that, depending on the power spectrum level, could be mistaken for EoR.
+on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, even without accounting for signal loss, the crosstalk bias at all $k$'s is very strong compared to the removed case.
 
@@
 We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test and even/odd test.
-All three tests, whether biased or not, have an extra noise bias that is strongly $k$-dependent.
+All three tests, whether biased or not, have an extra variance that is strongly $k$-dependent.
 Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
@@
 The former indicates a `passing' null test where there is no bias along the jackknife axis.
-The latter reveals whether there is an additional noise bias present that lies above the thermal noise.
+The latter reveals whether there is additional variance present that lies above the thermal noise.
 
@@
 When differencing two power spectra, we expect the signal-only term to subtract out for a `passing' null test, and we expect the noise-only terms to be consistent with thermal noise.
-The cross-terms, however, can introduce a noise bias that would vary with foreground strength, therefore being consistent with the shape of our results.
+The cross-terms, however, can introduce extra variance that would vary with foreground strength, therefore being consistent with the shape of our results.
 That being said, an alternate explanation for the large error bars seen at high $k$'s could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate.

### 2018-03-30 PAPER.tex
removed language about Kolopanis exploring a larger parameter space for gamma

@@
 We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
-We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of strengths and while an overall trend from high to low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
+We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
 
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
-We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, though we note that in Kolopanis et al.
-(\textit{submitted}), we choose the most optimal regularization parameter for our final limits for every redshift bin independently.
+We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
 We also note that all of the regularizations described here perform similarly to the uniformly weighted case.
@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), multiple baselines are used in the analysis to produce a $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
@@
 In Kolopanis et al.
-(\textit{submitted}), a larger parameter space is explored for regularization and multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
+(\textit{submitted}), multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
 a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}

### 2018-03-30 PAPER.tex
edited signal loss definition

@@
 \begin{itemize}
-\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target cosmological signal 
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
 in a power spectrum estimate.
 Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits.
-Computing signal loss correctly has subtle challenges but is necessary to ensure the accuracy of any result.
+Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
 \item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 

### 2018-03-31 PAPER.tex
added conclusion paragraph to jackknife section

@@
 We find that the baselines test is fully consistent with noise, as all error bars pass through zero.
-Therefore, we conclude that particular baselines are not to be blamed for the bias in our dataset.
+Therefore, we conclude that the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias.
+We suspect it is the former, though more thorough jackknives along this axis are needed to make this conclusion.
 For the LST test, $90\%$ of all the error bars pass through zero, which is slightly lower than the expected $95\%$.
@@
 This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
-When differencing two power spectra, we expect the signal-only term to subtract out for a `passing' null test, and we expect the noise-only terms to be consistent with thermal noise.
+When differencing two power spectra, we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
 The cross-terms, however, can introduce extra variance that would vary with foreground strength, therefore being consistent with the shape of our results.
-That being said, an alternate explanation for the large error bars seen at high $k$'s could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate.
+One additional explanation, specifically for the slightly large error bars seen at high $k$'s, could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate in this high-$k$ regime.
+Regardless of a potentially larger thermal noise prediction, however, the large error bars near the horizon limit still signify the presence of excess variance in our data.
+
+In this section we have presented the first jackknife and null tests from the PAPER experiment.
+While simple, they outline a framework that can be used in the future.
+The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough tests.
 

### 2018-04-03 PAPER.tex
updated toy model jackknife/null test section with new model

@@
 
-Suppose we have two measurements (for example, from two baselines), $\textbf{x}_{a}$ and $\textbf{x}_{b}$. The 
-measurements have dimensions of $200$ time integrations and $20$ frequency channels. They each have separate thermal 
+Suppose we have four independent measurements made along two different axes.
+As an example, we construct $\textbf{x}_{1a}$, $\textbf{x}_{1b}$, $\textbf{x}_{2a}$, and $\textbf{x}_{2b}$, where the numbers symbolize two different days of data and the letters represent two different baselines.
+Each of the
+measurements have dimensions of $100$ time integrations and $20$ frequency channels. They each have separate thermal 
 noises constructed as a Gaussian random signal for each, and identical EoR signals.
 
-To mimic the presence of a systematic in part of the measurement, we add a toy sinusoid foreground, similar to the one used in 
-Section \ref{sec:toymodel}, to the first $100$ time integrations of both measurements. This represents a foreground signal 
-present in, for example, the first half of the LST range used for analysis, but not the second half. Mathematically, if  $\textbf{n}$ 
-is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
-
-\begin{equation}
+To mimic the presence of a systematic, we add a toy sinusoid foreground, similar to the one used in 
+Section \ref{sec:toymodel}, to only $\textbf{x}_{2a}$ and $\textbf{x}_{2b}$. This represents a foreground signal 
+present in only the second day of data, but not the first. Mathematically, if  $\textbf{n}$ 
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the four measurements can be written as:
+
+\begin{eqnarray}
 \label{eq:bias1}
-\textbf{x}_{a} = \textbf{n}_{a} + \textbf{e} + \textbf{f}
-\end{equation}
-
-\noindent and
-
-\begin{equation}
-\label{eq:bias2}
-\textbf{x}_{b} = \textbf{n}_{b} + \textbf{e} + \textbf{f}.
-\end{equation}
-
-\noindent The two jackknife samples are $\textbf{x}_{1}$ and $\textbf{x}_{2}$, representing jackknives in time. These can be 
-written (for both measurements $a$ and $b$) as:
+\textbf{x}_{1a} &=& \textbf{n}_{1a} + \textbf{e}  \\ 
+\textbf{x}_{1b} &=& \textbf{n}_{1b} + \textbf{e}  \\ 
+\textbf{x}_{2a} &=& \textbf{n}_{2a} + \textbf{e} + \textbf{f} \\ 
+\textbf{x}_{2b} &=& \textbf{n}_{2b} + \textbf{e} + \textbf{f}.
+\end{eqnarray}
+
+\noindent We now take a jackknife along the day-axis, forming separate power spectrum estimates for each day:
 
 \begin{eqnarray}
-\textbf{x}_{1} &=& \textbf{n}_{1} + \textbf{e}_{1} + \textbf{f} \\
-\textbf{x}_{2} &=& \textbf{n}_{2} + \textbf{e}_{2}
+\widehat{\textbf{P}}_{1} &\propto& \textbf{x}_{1a}\textbf{x}_{1b}^{\dagger} \\
+\widehat{\textbf{P}}_{2} &\propto& \textbf{x}_{2a}\textbf{x}_{2b}^{\dagger}.
 \end{eqnarray}
-
-\noindent For example, $\textbf{x}_{1a}$ represents a jackknife sample (first half of the data) for the first measurement. 
-Similarly, $\textbf{x}_{2b}$ represents a jackknife sample (second half of the data) for the second measurement.
-We note that $\textbf{e}$ itself will be different in two jackknives taken along LST, but could be identical in other cases (such as a jackknife along even/odd Julian days).
 
@@
 
-We form three different power spectrum estimates shown in Figure \ref{fig:toy_bias1}. The first is a null test where we subtract $
-\textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$. This is equivalent to splitting up a full dataset along 
-an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
-We cross-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve).
-The second estimate,
-shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{f}$ in Equations \ref{eq:bias1} 
-and \ref{eq:bias2}). Finally, we also show the noise power spectrum (green).
-
-From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of 
+To construct a null test, we difference the two power spectra, with the result shown in Figure \ref{fig:toy_bias1} (black) along with the power spectrum of noise only (green).
+Subtracting the two estimates removes sky signal that should ideally be present in both jackknives.
+However, we see a clear difference between the null test and the power spectrum of
 noise. This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.pdf}
-	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
-the foreground systematic (red), and noise alone (green). Because the first null test is not consistent with noise, it suggests the 
+	\caption{A null jackknife test shown as the power spectrum difference between two measurements (black), compared to the power spectrum of noise alone (green).
+Because the null test is not consistent with noise, it suggests the
 presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
@@
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
-the presence of a systematic in $\textbf{x}_{1}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
+the presence of a systematic in $\textbf{x}_{2}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
 measurements should remain consistent despite the jackknife taken.}
@@
 which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $
-\textbf{x}_{1}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
+\textbf{x}_{2}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
 provide insight into possible sources. For example, if jackknives along the time-axis reveal a bias present at a certain LST, a 
@@
 
-Here we perform three hybrid jackknife/null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
+Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
 that they are not attributable to EoR.
 Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
-In addition, we difference them to tease out excess variances, which can be thought of as a type of null test.
+We then difference them (i.e.
+the null test) to tease out excess variances.
 

### 2018-04-04 PAPER.tex
changed P_out's to have hats (estimates) and some of the P_in's as well

@@
 spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as
+output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as
 
@@
 \label{eq:Pin}
-P_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+\widehat{P}_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \label{eq:sigloss}
-P_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
+\widehat{P}_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
 &=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
@@
 
-The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
+The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
 Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
-The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
+The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
+This is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
+In principle, one could compute the true $\widehat{P}_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
 In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds.
@@
 Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
-Therefore, $P_{\rm out}$ can be directly compared to the measurement that we make.
+Therefore, $\widehat{P}_{\rm out}$ can be directly compared to the measurement that we make.
 
@@
 %\begin{equation}
-%P_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
+%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
 %\end{equation}
@@
 
-Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
+Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:
 
 %
-%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
+%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
@@
 %
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
+%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 %
-%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
-%which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
+%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
+%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
 %distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
@@
 %\label{sec:Illustration}
-%To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
+%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
 
@@
 \label{eq:crossterm_full}
-P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
+\widehat{P}_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
 %\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
@@
 \label{eq:crossterm}
-P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+\widehat{P}_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
+In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
 We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
-It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black).
+However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$.
+It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black).
 We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
+The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
 
@@
 As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
-This negative component drives down the $P_{\rm out}$ estimator (black).
+This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
 We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
@@
 It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
-We see that the cross-terms can produce a large, negative signal which serves to reduce $P_{\rm out}$ and drive the bulk of our loss.
-In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $P_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
+We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss.
+In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
 
@@
 For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $P_{\rm out}$ becomes:
+It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
 %
@@
 %\end{eqnarray}
-%The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
+%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
 Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
 However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
-In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
+In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
 Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
@@
 Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}.
-The output power spectrum ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
+The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
 \eqref{eq:crossterm} are shown in blue, red, and green.
@@
 regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
-term with width $\sqrt{P_e}\sqrt{P_x}$.
+term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
 However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
@@
 %The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
+%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss.
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
 Therefore, in our revised
-%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
+%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
 %weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
@@
 ($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. With this weighting, our 
-expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
+expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
 
 \begin{eqnarray}
-P_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-P_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
+\widehat{P}_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+\widehat{P}_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
 %&&\phantom{=====} 
@@
 
-One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections.
+One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
 A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
@@
 how much coupling there is, which affects how much loss results).
+For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$.
 
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
-P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
+\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.
 Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
@@
 \label{eq:Bayes}
-p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
+p(P_{\rm in} | \widehat{P}_{\rm out}) \propto {\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
 \end{equation}
@@
 \noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
+as the distribution of data plus injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
 by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum over $P_{\rm out}$ is unity, and the 
+consistent with this power spectrum. The resulting distribution is normalized such that the sum over $\widehat{P}_{\rm out}$ is unity, and the 
 whole process is then repeated for a different value of $P_{\rm in}$.
@@
 We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
-$P_{\rm out}$ grid.
+$\widehat{P}_{\rm out}$ grid.
 
 Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them).
+We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them).
 Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
@@
 the shape of the transfer curve is similar for all $k$'s.
-This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $P_{\rm out} = \widehat{\textbf{P}}_{x}$) to yield a posterior distribution for the signal.
+This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
+We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and multiply by our prior to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $P_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
+Specifically, we de-convolve Gaussian distributions of $\widehat{P}_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $\widehat{P}_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
 
@@
 %nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $P_{\rm out}$ value for every 
+%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $\widehat{P}_{\rm out}$ value for every 
 %$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
@@
 %\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-%every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{\rm out}$ values that results from the same 
+%every bootstrap (for reasons made clear in the next paragraph), there is a range of $\widehat{P}_{\rm out}$ values that results from the same 
 %$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
@@
 
-%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$).
+%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($\widehat{P}_{\rm out} > P_{in}$).
 \cc{This is a log-plotting effect and is under-construction!}.
@@
 As $\textbf{e}$ increases, we move
-%into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
+%into a regime where $\widehat{P}_{\rm out} \sim P_{in}$, and then eventually into a regime where $\widehat{P}_{\rm out} < P_{in}$ when $\textbf{e}$ is 
 %large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
@@
 
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".

### 2018-04-04 PAPER.tex
re-compiled all PS plots with sigloss v8

@@
 We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and multiply by our prior to yield a posterior distribution for the signal.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits are roughly constant across a large range of values of $\gamma$.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}

### 2018-04-04 PAPER.tex
altered language about 3 variations: cosmic variance, noise, signal loss

@@
 One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
-cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
+A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
 how much coupling there is, which affects how much loss results).
-For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$.
-
+
+For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator.
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} |
@@
 The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing variance due to noise and signal loss.
+In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss.
 To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
@@
 Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them).
+We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalize them).
 Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.

### 2018-04-04 PAPER.tex
revised text about N_bls and N_days --- moved a sqrt(2) factor around

@@
 \item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form ``even" and ``odd" datasets), this number should be reduced by a factor of $2$. Additionally, 
-because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
-$N_{\rm days}$ as:
-\begin{equation}
- \frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ indexes LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim34$ 
+divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
+Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even", for reasons explained in Section \ref{sec:MitBias}).
+Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
+$N_{\rm days}$. Our expression therefore becomes:
+\begin{equation}
+N_{\rm days} = \sqrt{\langle N_{i}^{2}\rangle} \sqrt{(N_{\rm datasets}^{2}-N_{\rm datasets})}
+ %\frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
+ \end{equation}
+\noindent where $i$ indexes LST and frequency channel over all datasets (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim47$ 
 days.
@@
 \begin{equation}
-N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{N_{\rm gps}^{2}-N_{\rm gps}},
+N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{\frac{N_{\rm gps}^{2}-N_{\rm gps}}{2}},
 \end{equation}
 \noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{\rm gps}^{2} - 
-N_{\rm gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 46$ instead 
+entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
+N_{\rm gps}}{2}}$\Big). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 32$ instead 
 of $51$. 
@@
 \subsubsection{Mitigating Bias}
+\label{sec:MitBias}
 

### 2018-04-05 PAPER.tex
Thu Apr  5 13:21:06 EDT 2018

@@
-\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
+\documentclass[preprint2,numberedappendix,tighten]{aastex6}  
+% USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
@@
 \newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors
+
+\newcommand{\invC}{\ensuremath{C^{-1}}}
+\newcommand{\dC}[1]{\ensuremath{C_{,#1}}}
+\DeclareMathOperator{\Tr}{Tr}
+\newcommand{\half}{\ensuremath{\frac{1}{2}}}
+\newcommand{\PDeriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
 
@@
 
+\color{blue}
+
+\appendix
+\section{A toy model for inverse covariance weighting}
+\label{sec:icw_appendix}
+
+Assume we have $N$ data points where
+\begin{equation}
+\Delta_i = \sigma_i + \gamma_i
+\end{equation}
+and
+\begin{eqnarray}
+\langle \sigma_i \rangle & = & 0 \\
+\langle \sigma^2_i \rangle & = & s \\
+ \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
+\end{eqnarray}
+\begin{eqnarray}
+\langle \gamma_i \rangle & = & 0 \\
+\langle \gamma^2_i \rangle & = & g \\
+ \langle \gamma \gamma^T \rangle & = & g I_{N \times N} \equiv G
+\end{eqnarray}
+and in addition
+\begin{equation}
+\langle \sigma_i \gamma_j \rangle = 0
+\end{equation}
+That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
+If we want to estimate $s$ using only the inverse covariance weighting, we find
+\begin{equation}
+\label{eq:CaseOneICW}
+\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right)
+\end{equation}
+and plugging in the relevant quantities gives
+\begin{eqnarray}
+\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
+& = & \frac{\Delta^T \Delta}{N}
+\end{eqnarray}
+We note that
+\begin{equation}
+\langle \hat{s} \rangle = s + g
+\end{equation}
+so we could derive that the correct additive bias is $g$, but this requires a separate step, and the ICW by itself does not provide an unbiased answer.
+This is because the covariance structure of the contaminant and the data are identical.
+In this case, it is necessary to use additional information to estimate the additive bias and subtract it.
+
+If instead of the foreground contaminant being given by Eq \ref{eq:ToyOne}, suppose we now have
+\begin{equation}
+\Delta_i = \sigma_i + \gamma m_i
+\end{equation}
+where again
+\begin{eqnarray}
+\langle \sigma_i \rangle & = & 0 \\
+\langle \sigma^2_i \rangle & = & s \\
+ \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
+\end{eqnarray}
+but now $\gamma$ is a random variable and $m_i$ is a fixed function of $i$ with
+\begin{eqnarray}
+\langle \gamma \rangle & = & 0 \\
+\langle \gamma^2 \rangle & = & g \\
+ \langle \gamma \gamma^T \rangle & = & g m m^T \equiv G \\
+ m^T m & = & 1
+\end{eqnarray}
+This is the case where each data point is an independent draw from a variable with a fixed variance $s$ we would like to estimate, and $m$ represents a mode which is correlated across many data points with correlation given by $m$, and amplitude in realization of $\gamma$.
+This is the essence of the toy model presented in Section \ref{sec:}
+
+\color{black}
+
 \appendix

### 2018-04-11 PAPER.tex
Tue Apr 10 22:22:23 EDT 2018

@@
 
-Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during 
-spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
+Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself.
+Here we focus on signal loss associated with
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
 previously underestimated in the \citetalias{ali_et_al2015} analysis.
+
+% Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
+
+% Some things we never quite say as explicitly as I'd like:
+% - "foreground suppression" happens because the foregrounds have a different covariance structure (Figure 4), and we 
+% hope we pick this out by picking big eigenvalues
+% - additive bias is a thing
+
+\subsubsection{The Quadratic Estimator Method}
 
@@
 
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in
-experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
-purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section
-\ref{sec:Sigloss}.
-
-\subsubsection{Toy Model: Inverse Covariance Weighting}
-\label{sec:toymodel}
-
 One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
@@
 
-In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
+%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
+
+Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
+Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
+In previous PAPER analyses, one time-averages the data such that:
+
+\begin{equation}
+\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
+\end{equation}
+
+\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
+\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+
+% ---
+
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
+Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
+We note that we
+purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section
+\ref{sec:Sigloss}.
+
+\subsubsection{Toy Model: Empirical Inverse Covariance Weighting}
+\label{sec:toymodel}
+
 We will now build intuition into how empirically estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
-
 We construct a simple dataset that contains visibility data with $100$ time
@@
 \end{figure}
-
-Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data such that:
-
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
-\end{equation}
-
-\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 
@@
 
-To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
+% While a later section does show that the large eigenvalue modes converge to the eigenvectors quicker, it is _not_ true that modes with big eigenvalues are downweighted more.
+It is the modes which have a structure different from dC/dp_alpha.
+Our regularization actually forces both eigenvalues and eigenmodes to be like the "signal" part of the covariance.
+Thus, I don't think the next two paragraphs are helping the explanation of what is going on.
+
+%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
 Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
 
-An eigenspectrum ranks the eigenvalues of a matrix from 
-highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
-words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
-\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
+In other words, the eigenvalues encode the strength of different shapes in the dataset.
+The eigenspectrum of the identity matrix $ \textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
 In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-The modes with the highest eigenvalues are
-down-weighted the most.
+The modes with the highest eigenvalues are down-weighted the most.
 
@@
 Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-For example, the highest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
+In this case, the eigenmode of $\widehat{\textbf{C}}$ with the largest eigenvalue describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
 In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
@@
 
-In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
-For these FG-dominating modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
+%In general, 
+We have made the assumption that the highest-valued eigenmodes of $\widehat{\textbf{C}}$ will typically (but not always) describe bright foregrounds, though we have not checked that indeed the eigenvectors do describe correlations between frequencies.
+% --- the most prominent shapes in a dataset. 
+%For these FG-dominating modes, where foregrounds outshine the EoR signal, 
+If such modes do describe foregrounds, then down-weighting is beneficial.
 In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.'  In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.

### 2018-04-24 PAPER.tex
updated fig 24 comparing bootstrapping methods, along with text

--- 2018-04-04 PAPER.tex
@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ upper limits with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
-We note that they do not match perfectly, but we find good agreement given the approximations we make in computing the thermal noise level.
-While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
+Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$$2$-$3$ in mK$^{2}$.
 
@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
+	\caption{$2\sigma$ power spectrum upper limits for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
 methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-While this does not match perfectly with the $2\sigma$ analytic prediction for noise (green), we find good agreement between them to within a factor of two (which we believe is reasonable given the approximations we make in computing the analytic).}
+We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green) and are a factor of $\sim$$2$-$3$ (in mK$^{2}$) higher than those using the original method.}
 	\label{fig:data_errors}

### 2018-04-24 PAPERugh.tex
Tue Apr 24 18:10:09 EDT 2018

--- 2018-04-24 PAPER.tex
@@
 \newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
-\newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }
+\newcommand{\jea}[1]{{\color{blue} \textbf{ #1}} }
 \newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors
@@
 
+% First, explain the estimator and what it is supposed to do.
+% Then show that using empirical covariance naively will lead to problems.
+% Then discuss what happens with not enough modes - here the convergence to the correct eigenvectors is discussed
+
 \subsection{Signal Loss}
@@
 
+\jea{One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
+By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
+Therefore, in an ideal world with perfect foreground,
+instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
+In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.}
+
 In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in
-experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
+Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
+We note that we
 purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
@@
 In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
-
-One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
-By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
-Therefore, in an ideal world with perfect foreground,
-instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
-In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
 
@@
 
-Suppose we have four independent measurements made along two different axes.
-As an example, we construct $\textbf{x}_{1a}$, $\textbf{x}_{1b}$, $\textbf{x}_{2a}$, and $\textbf{x}_{2b}$, where the numbers symbolize two different days of data and the letters represent two different baselines.
-Each of the
-measurements have dimensions of $100$ time integrations and $20$ frequency channels. They each have separate thermal 
+Suppose we have two measurements (for example, from two baselines), $\textbf{x}_{a}$ and $\textbf{x}_{b}$. The 
+measurements have dimensions of $200$ time integrations and $20$ frequency channels. They each have separate thermal 
 noises constructed as a Gaussian random signal for each, and identical EoR signals.
 
-To mimic the presence of a systematic, we add a toy sinusoid foreground, similar to the one used in 
-Section \ref{sec:toymodel}, to only $\textbf{x}_{2a}$ and $\textbf{x}_{2b}$. This represents a foreground signal 
-present in only the second day of data, but not the first. Mathematically, if  $\textbf{n}$ 
-is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the four measurements can be written as:
+To mimic the presence of a systematic in part of the measurement, we add a toy sinusoid foreground, similar to the one used in 
+Section \ref{sec:toymodel}, to the first $100$ time integrations of both measurements. This represents a foreground signal 
+present in, for example, the first half of the LST range used for analysis, but not the second half. Mathematically, if  $\textbf{n}$ 
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the two measurements (which are cross-multiplied to form power spectra) can be written as:
+
+\begin{equation}
+\label{eq:bias1}
+\textbf{x}_{a} = \textbf{n}_{a} + \textbf{e} + \textbf{f}
+\end{equation}
+
+\noindent and
+
+\begin{equation}
+\label{eq:bias2}
+\textbf{x}_{b} = \textbf{n}_{b} + \textbf{e} + \textbf{f}.
+\end{equation}
+
+\noindent The two jackknife samples are $\textbf{x}_{1}$ and $\textbf{x}_{2}$, representing jackknives in time. These can be 
+written (for both measurements $a$ and $b$) as:
 
 \begin{eqnarray}
-\label{eq:bias1}
-\textbf{x}_{1a} &=& \textbf{n}_{1a} + \textbf{e}  \\ 
-\textbf{x}_{1b} &=& \textbf{n}_{1b} + \textbf{e}  \\ 
-\textbf{x}_{2a} &=& \textbf{n}_{2a} + \textbf{e} + \textbf{f} \\ 
-\textbf{x}_{2b} &=& \textbf{n}_{2b} + \textbf{e} + \textbf{f}.
+\textbf{x}_{1} &=& \textbf{n}_{1} + \textbf{e}_{1} + \textbf{f} \\
+\textbf{x}_{2} &=& \textbf{n}_{2} + \textbf{e}_{2}
 \end{eqnarray}
 
-\noindent We now take a jackknife along the day-axis, forming separate power spectrum estimates for each day:
-
-\begin{eqnarray}
-\widehat{\textbf{P}}_{1} &\propto& \textbf{x}_{1a}\textbf{x}_{1b}^{\dagger} \\
-\widehat{\textbf{P}}_{2} &\propto& \textbf{x}_{2a}\textbf{x}_{2b}^{\dagger}.
-\end{eqnarray}
+\noindent For example, $\textbf{x}_{1a}$ represents a jackknife sample (first half of the data) for the first measurement. 
+Similarly, $\textbf{x}_{2b}$ represents a jackknife sample (second half of the data) for the second measurement.
+We note that $\textbf{e}$ itself will be different in two jackknives taken along LST, but could be identical in other cases (such as a jackknife along even/odd Julian days).
 
@@
 
-To construct a null test, we difference the two power spectra, with the result shown in Figure \ref{fig:toy_bias1} (black) along with the power spectrum of noise only (green).
-Subtracting the two estimates removes sky signal that should ideally be present in both jackknives.
-However, we see a clear difference between the null test and the power spectrum of
+We form three different power spectrum estimates shown in Figure \ref{fig:toy_bias1}. The first is a null test where we subtract $
+\textbf{x}_{2}$ from $\textbf{x}_{1}$ for both measurements $a$ and $b$. This is equivalent to splitting up a full dataset along 
+an axis (in this case, time) and subtracting the two to remove sky signal that should ideally be present in both.
+We cross-multiply measurements $a$ and $b$ to form an un-biased (thermal noise-wise) estimate (blue curve).
+The second estimate,
+shown in red, is the same null test with the foreground systematic removed (eliminate $\textbf{f}$ in Equations \ref{eq:bias1} 
+and \ref{eq:bias2}). Finally, we also show the noise power spectrum (green).
+
+From this test we see a clear difference between the null test with the presence of the foregrounds, and the power spectrum of 
 noise. This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.pdf}
-	\caption{A null jackknife test shown as the power spectrum difference between two measurements (black), compared to the power spectrum of noise alone (green).
-Because the null test is not consistent with noise, it suggests the
+	\caption{Power spectrum estimates for a null jackknife test with the presence of a foreground systematic (blue), without 
+the foreground systematic (red), and noise alone (green). Because the first null test is not consistent with noise, it suggests the 
 presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
@@
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
-the presence of a systematic in $\textbf{x}_{2}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
+the presence of a systematic in $\textbf{x}_{1}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
 measurements should remain consistent despite the jackknife taken.}
@@
 which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $
-\textbf{x}_{2}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
+\textbf{x}_{1}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
 provide insight into possible sources. For example, if jackknives along the time-axis reveal a bias present at a certain LST, a 
@@
 configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
+focus solely on Stokes I estimated data (rather than the full Stokes considered in 
+\citep{moore_et_al2017})
+%JEA - I didn't understand the original citation to Moore 2013
+from PAPER's $30$ m East/West baselines (Figure 
 \ref{fig:ant_layout}).
@@
 spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as
+output power spectrum: $P_{\rm in}$ and $P_{\rm out}$, defined as
 
@@
 \label{eq:Pin}
-\widehat{P}_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+P_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \label{eq:sigloss}
-\widehat{P}_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
+P_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
 &=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
@@
 
-The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
+The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
 Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
-The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-This is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-In principle, one could compute the true $\widehat{P}_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
+The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
+This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
+In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
 In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds.
@@
 Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
-Therefore, $\widehat{P}_{\rm out}$ can be directly compared to the measurement that we make.
+Therefore, $P_{\rm out}$ can be directly compared to the measurement that we make.
 
@@
 %\begin{equation}
-%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
+%P_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
 %\end{equation}
@@
 
-Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:
+Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $P_{\rm out}$ becomes:
 
 %
-%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
+%In short, we can approximate a signal loss estimate as the ratio of $P_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
 We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
@@
 %
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
+%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $P_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
 \dcj{Here is the post-hoc justification for this signal loss method.
@@
 %
-%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
-%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
+%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $P_{\rm out}$, can be thought of as a transfer function 
+%which, for a sampling of $P_{\rm in}$ and $P_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
 %distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
@@
 %\label{sec:Illustration}
-%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
+%To explore how our expression for $P_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
 
@@
 \label{eq:crossterm_full}
-\widehat{P}_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
+P_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
 %\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
@@
 \label{eq:crossterm}
-\widehat{P}_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
@@
 This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
+In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
 We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
 %In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$.
-It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black).
+However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$.
+It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black).
 We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
@@
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
+The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{P_e}\sqrt{P_x}$.
 
@@
 As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
-This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
+This negative component drives down the $P_{\rm out}$ estimator (black).
 We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
@@
 It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
-We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss.
-In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
+We see that the cross-terms can produce a large, negative signal which serves to reduce $P_{\rm out}$ and drive the bulk of our loss.
+In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $P_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
 
@@
 For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
+It is in this limit where we expect signal loss to be greatest, and $P_{\rm out}$ becomes:
 %
@@
 %\end{eqnarray}
-%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
+%The first term of $P_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
 Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
 However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
-In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
+In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $P_{\rm out}$.
 Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
@@
 Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}.
-The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
+The output power spectrum ($P_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
 \eqref{eq:crossterm} are shown in blue, red, and green.
@@
 regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
-term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
+term with width $\sqrt{P_e}\sqrt{P_x}$.
 However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
@@
 %The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss.
+%simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss.
 This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
 Therefore, in our revised
-%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
+%signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
 %weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
@@
 ($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. With this weighting, our 
-expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
+expressions for $P_{\rm in}$ and $P_{\rm out}$ become:
 
 \begin{eqnarray}
-\widehat{P}_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-\widehat{P}_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
+P_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+P_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
 %&&\phantom{=====} 
@@
 
-One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
+One issue to address is how one incorporates the randomness of $P_{\rm out}$ into our signal loss corrections.
+A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in two ways ---  there is a variation driven by the random seed (i.e.
+cosmic variance) and a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
 how much coupling there is, which affects how much loss results).
 
-For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator.
 Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
-\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.
+P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$.
 Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
@@
 \label{eq:Bayes}
-p(P_{\rm in} | \widehat{P}_{\rm out}) \propto {\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
+p(P_{\rm in} | P_{\rm out}) \propto {\mathcal{L} (  P_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
 \end{equation}
@@
 \noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
+as the distribution of data plus injection ($P_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
 by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum over $\widehat{P}_{\rm out}$ is unity, and the 
+consistent with this power spectrum. The resulting distribution is normalized such that the sum over $P_{\rm out}$ is unity, and the 
 whole process is then repeated for a different value of $P_{\rm in}$.
@@
 The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss.
+In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing variance due to noise and signal loss.
 To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
 We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
-$\widehat{P}_{\rm out}$ grid.
+$P_{\rm out}$ grid.
 
 Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalize them).
+We bin our simulation outputs along the $P_{\rm in}$ axis, and smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalizing them).
 Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
@@
 the shape of the transfer curve is similar for all $k$'s.
-This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal.
+This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$.
+We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|P_{\rm out})$ where we recall that $P_{\rm out}$ is a model of our data.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $P_{\rm out} = \widehat{\textbf{P}}_{x}$) to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $\widehat{P}_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
+Specifically, we de-convolve Gaussian distributions of $P_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
 By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
@@
 On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $\widehat{P}_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
+The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $P_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
 
@@
 %nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $\widehat{P}_{\rm out}$ value for every 
+%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $P_{\rm out}$ value for every 
 %$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
@@
 %\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-%every bootstrap (for reasons made clear in the next paragraph), there is a range of $\widehat{P}_{\rm out}$ values that results from the same 
+%every bootstrap (for reasons made clear in the next paragraph), there is a range of $P_{\rm out}$ values that results from the same 
 %$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
+	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $P_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
@@
 
-%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($\widehat{P}_{\rm out} > P_{in}$).
+%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($P_{\rm out} > P_{in}$).
 \cc{This is a log-plotting effect and is under-construction!}.
@@
 As $\textbf{e}$ increases, we move
-%into a regime where $\widehat{P}_{\rm out} \sim P_{in}$, and then eventually into a regime where $\widehat{P}_{\rm out} < P_{in}$ when $\textbf{e}$ is 
+%into a regime where $P_{\rm out} \sim P_{in}$, and then eventually into a regime where $P_{\rm out} < P_{in}$ when $\textbf{e}$ is 
 %large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
@@
 as solid green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 
-The noise prediction $n(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
+The noise prediction $N(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
 interferometric 21\,cm data, in temperature-units, is:
@@
 \item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even", for reasons explained in Section \ref{sec:MitBias}).
-Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
-$N_{\rm days}$. Our expression therefore becomes:
-\begin{equation}
-N_{\rm days} = \sqrt{\langle N_{i}^{2}\rangle} \sqrt{(N_{\rm datasets}^{2}-N_{\rm datasets})}
- %\frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ indexes LST and frequency channel over all datasets (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim47$ 
+divide our data in half (to form ``even" and ``odd" datasets), this number should be reduced by a factor of $2$. Additionally, 
+because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we compute a more realistic value of 
+$N_{\rm days}$ as:
+\begin{equation}
+ \frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
+ \end{equation}
+\noindent where $i$ indexes LST (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim34$ 
 days.
@@
 \begin{equation}
-N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{\frac{N_{\rm gps}^{2}-N_{\rm gps}}{2}},
+N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{N_{\rm gps}^{2}-N_{\rm gps}},
 \end{equation}
 \noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 32$ instead 
+entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs ($\sqrt{N_{\rm gps}^{2} - 
+N_{\rm gps}}$). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 46$ instead 
 of $51$. 
@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ upper limits with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$$2$-$3$ in mK$^{2}$.
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
+We note that they do not match perfectly, but we find good agreement given the approximations we make in computing the thermal noise level.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum upper limits for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
+	\caption{$2\sigma$ power spectrum errors for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
 methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green) and are a factor of $\sim$$2$-$3$ (in mK$^{2}$) higher than those using the original method.}
+While this does not match perfectly with the $2\sigma$ analytic prediction for noise (green), we find good agreement between them to within a factor of two (which we believe is reasonable given the approximations we make in computing the analytic).}
 	\label{fig:data_errors}
@@
 \subsubsection{Mitigating Bias}
-\label{sec:MitBias}
 
@@
 
-Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
+Here we perform three hybrid jackknife/null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
 that they are not attributable to EoR.
 Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
-We then difference them (i.e.
-the null test) to tease out excess variances.
+In addition, we difference them to tease out excess variances, which can be thought of as a type of null test.
 
@@
 
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $P_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
 Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".

### 2018-04-24 PAPER.tex
Tue Apr 24 18:29:09 EDT 2018

--- 2018-04-11 PAPER.tex
@@
 
-Assume we have $N$ data points where
+We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum by considering the simpler, but similar, case of estimating the variance of data.
+We have specifically chosen a toy model where the data covariance is diagonal, as we expect the EoR signal to be.
+We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\kappa_i$
 \begin{equation}
@@
 \end{equation}
-so we could derive that the correct additive bias is $g$, but this requires a separate step, and the ICW by itself does not provide an unbiased answer.
-This is because the covariance structure of the contaminant and the data are identical.
-In this case, it is necessary to use additional information to estimate the additive bias and subtract it.
+so in this case, {\it where the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
 

### 2018-04-24 PAPER.tex
Tue Apr 24 19:35:58 EDT 2018

@@
 
-We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum by considering the simpler, but similar, case of estimating the variance of data.
+We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
 We have specifically chosen a toy model where the data covariance is diagonal, as we expect the EoR signal to be.
-We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\kappa_i$
-\begin{equation}
-\Delta_i = \sigma_i + \gamma_i
-\end{equation}
-and
-\begin{eqnarray}
-\langle \sigma_i \rangle & = & 0 \\
-\langle \sigma^2_i \rangle & = & s \\
- \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
-\end{eqnarray}
-\begin{eqnarray}
-\langle \gamma_i \rangle & = & 0 \\
-\langle \gamma^2_i \rangle & = & g \\
- \langle \gamma \gamma^T \rangle & = & g I_{N \times N} \equiv G
-\end{eqnarray}
-and in addition
-\begin{equation}
-\langle \sigma_i \gamma_j \rangle = 0
-\end{equation}
+We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\phi_i$
+\begin{equation}
+\Delta_i = \sigma_i + \phi_i
+\end{equation}
+with 
+\begin{equation}
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
+\end{equation}
+and we wish to estimate $s$.  The contaminant has a similar structure for its covariance, and is assumed uncorrelated
+\begin{equation}
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
+\end{equation}
+$\langle \phi_i \rangle = 0$, 
+$\langle \phi^2_i \rangle = g$, $\angle \phi \phi^T \rangle = g I_{N \times N} \equiv F$, 
+$\langle \sigma_i \phi_j \rangle = 0$.
 That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
@@
 \begin{equation}
-\Delta_i = \sigma_i + \gamma m_i
+\Delta_i = \sigma_i + \phi m_i
 \end{equation}
@@
 \end{eqnarray}
-but now $\gamma$ is a random variable and $m_i$ is a fixed function of $i$ with
+but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
 \begin{eqnarray}
-\langle \gamma \rangle & = & 0 \\
-\langle \gamma^2 \rangle & = & g \\
- \langle \gamma \gamma^T \rangle & = & g m m^T \equiv G \\
+\langle \phi \rangle & = & 0 \\
+\langle \phi^2 \rangle & = & g \\
+ \langle \phi \phi^T \rangle & = & g m m^T \equiv G \\
  m^T m & = & 1
 \end{eqnarray}
-This is the case where each data point is an independent draw from a variable with a fixed variance $s$ we would like to estimate, and $m$ represents a mode which is correlated across many data points with correlation given by $m$, and amplitude in realization of $\gamma$.
+This is the case where each data point is an independent draw from a variable with a fixed variance $s$ we would like to estimate, and $m$ represents a mode which is correlated across many data points with correlation given by $m$, and amplitude in realization of $\phi$.
 This is the essence of the toy model presented in Section \ref{sec:}

### 2018-04-25 PAPER.tex
Tue Apr 24 22:58:57 EDT 2018

@@
 \end{equation}
-and we wish to estimate $s$.  The contaminant has a similar structure for its covariance, and is assumed uncorrelated
-\begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
-\end{equation}
-$\langle \phi_i \rangle = 0$, 
-$\langle \phi^2_i \rangle = g$, $\angle \phi \phi^T \rangle = g I_{N \times N} \equiv F$, 
-$\langle \sigma_i \phi_j \rangle = 0$.
-That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
-If we want to estimate $s$ using only the inverse covariance weighting, we find
+and we wish to estimate $s$.  The contaminant in this case has a similar structure for its covariance, and is assumed uncorrelated with the signal
+\begin{equation}
+\langle \phi_i \rangle = 0; \; 
+\langle \phi^2_i \rangle = f; \; 
+\langle \phi \phi^T \rangle = f I_{N \times N} \equiv F; {\rm and}~ 
+\langle \sigma_i \phi_j \rangle = 0
+\end{equation}
+%That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
+The estimator for $s$ using the inverse covariance weighting prescription is
 \begin{equation}
@@
 \hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) 
-\end{equation}
-and plugging in the relevant quantities gives
-\begin{eqnarray}
-\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
-& = & \frac{\Delta^T \Delta}{N}
-\end{eqnarray}
+= \frac{\Delta^T \Delta}{N}
+\end{equation}
+%and plugging in the relevant quantities gives
+%\begin{eqnarray}
+%\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
+%& = & \frac{\Delta^T \Delta}{N}
+%\end{eqnarray}
 We note that
@@
 \end{equation}
-so in this case, {\it where the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
-
-If instead of the foreground contaminant being given by Eq \ref{eq:ToyOne}, suppose we now have
+In this case, the quadratic estimator returns an entirely reasonable result, but, 
+{\it since the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
+
+Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
 \begin{equation}
@@
 \end{equation}
-where again
-\begin{eqnarray}
-\langle \sigma_i \rangle & = & 0 \\
-\langle \sigma^2_i \rangle & = & s \\
- \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
-\end{eqnarray}
+where the properties of $\sigma_i$ are as before,
+%\begin{eqnarray}
+%\langle \sigma_i \rangle & = & 0 \\
+%\langle \sigma^2_i \rangle & = & s \\
+% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
+%\end{eqnarray}
 but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
-\begin{eqnarray}
-\langle \phi \rangle & = & 0 \\
-\langle \phi^2 \rangle & = & g \\
- \langle \phi \phi^T \rangle & = & g m m^T \equiv G \\
- m^T m & = & 1
-\end{eqnarray}
-This is the case where each data point is an independent draw from a variable with a fixed variance $s$ we would like to estimate, and $m$ represents a mode which is correlated across many data points with correlation given by $m$, and amplitude in realization of $\phi$.
-This is the essence of the toy model presented in Section \ref{sec:}
+\begin{equation}
+\langle \phi \rangle = 0; \;
+\langle \phi^2 \rangle = f; \; 
+ \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
+ m^T m = 1
+\end{equation}
+Here $m$ represents a mode which is correlated across many data points, with correlation given by $m m^T$, and, and the amplitude of its realization is $\phi$.
 

### 2018-04-25 PAPER.tex
Wed Apr 25 07:47:42 EDT 2018

@@
 \end{equation}
-Here $m$ represents a mode which is correlated across many data points, with correlation given by $m m^T$, and, and the amplitude of its realization is $\phi$.
+Here $m$ represents a mode which is correlated across many data points, with amplitude given by  $\phi$.
+
+Here we can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+\begin{equation}
+\xi \equiv \frac{f/s}{1+f/s}
+\end{equation} 
+we have
+\begin{equation}
+\invC %& = & \frac{1}{s} I - \frac{g}{1+g/s} \frac{1}{s^2} m m^T \\
+=   \frac{1}{s} \left(I - \xi m m^T \right)
+\end{equation}
+and the virtue of weighting by $\invC$ becomes clearer: in the limit $f \gg s$, $\xi \to 1$, and this becomes
+\begin{equation}
+\invC  = \frac{1}{s} \left(I - m m^T \right)
+\end{equation}
+where $I - m m^T$ is the projection operator, projecting out $m$ from any any vector it acts on.   Proceeding to calculate the full estimator
+\begin{equation}
+\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) = \frac{ \Delta^T  (I -  (\eta^2 - 2 \eta)  m m^T)  \Delta}{N + \eta^2 - 2 \eta} 
+\end{equation}
+we note that the expectation is
+\begin{equation}
+\hat{s} = 
+\end{equation}
 

### 2018-04-30 PAPER.tex
Wed Apr 25 12:26:14 EDT 2018
updated fig 22 sensitivity comparison to reflect A15 analysis, and edited text to highlight where changes have been made to this analysis

--- 2018-04-25 PAPER.tex
@@
-\documentclass[preprint2,numberedappendix,tighten]{aastex6}  
-% USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
+\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
@@
 
-\newcommand{\invC}{\ensuremath{C^{-1}}}
-\newcommand{\dC}[1]{\ensuremath{C_{,#1}}}
-\DeclareMathOperator{\Tr}{Tr}
-\newcommand{\half}{\ensuremath{\frac{1}{2}}}
-\newcommand{\PDeriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
-
 % Math shortcuts from Danny
@@
 
-Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself.
-Here we focus on signal loss associated with
+Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during 
+spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
 applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
 previously underestimated in the \citetalias{ali_et_al2015} analysis.
-
-% Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
-
-% Some things we never quite say as explicitly as I'd like:
-% - "foreground suppression" happens because the foregrounds have a different covariance structure (Figure 4), and we 
-% hope we pick this out by picking big eigenvalues
-% - additive bias is a thing
-
-\subsubsection{The Quadratic Estimator Method}
 
@@
 
+In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
+Our goal in
+experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
+purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section
+\ref{sec:Sigloss}.
+
+\subsubsection{Toy Model: Inverse Covariance Weighting}
+\label{sec:toymodel}
+
 One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
@@
 
-%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
-
-Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data such that:
-
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
-\end{equation}
-
-\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-
-% ---
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
-We note that we
-purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section
-\ref{sec:Sigloss}.
-
-\subsubsection{Toy Model: Empirical Inverse Covariance Weighting}
-\label{sec:toymodel}
-
+In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
 We will now build intuition into how empirically estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
+
 We construct a simple dataset that contains visibility data with $100$ time 
@@
 \end{figure}
+
+Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
+Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
+In previous PAPER analyses, one time-averages the data such that:
+
+\begin{equation}
+\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
+\end{equation}
+
+\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
+\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 
@@
 
-% While a later section does show that the large eigenvalue modes converge to the eigenvectors quicker, it is _not_ true that modes with big eigenvalues are downweighted more.
-It is the modes which have a structure different from dC/dp_alpha.
-Our regularization actually forces both eigenvalues and eigenmodes to be like the "signal" part of the covariance.
-Thus, I don't think the next two paragraphs are helping the explanation of what is going on.
-
-%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
+To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
 Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
 
-%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
-In other words, the eigenvalues encode the strength of different shapes in the dataset.
-The eigenspectrum of the identity matrix $ \textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+An eigenspectrum ranks the eigenvalues of a matrix from 
+highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
+words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
+\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
 In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-The modes with the highest eigenvalues are down-weighted the most.
+The modes with the highest eigenvalues are
+down-weighted the most.
 
@@
 Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-In this case, the eigenmode of $\widehat{\textbf{C}}$ with the largest eigenvalue describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
+For example, the highest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
 In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
@@
 
-%In general, 
-We have made the assumption that the highest-valued eigenmodes of $\widehat{\textbf{C}}$ will typically (but not always) describe bright foregrounds, though we have not checked that indeed the eigenvectors do describe correlations between frequencies.
-% --- the most prominent shapes in a dataset. 
-%For these FG-dominating modes, where foregrounds outshine the EoR signal, 
-If such modes do describe foregrounds, then down-weighting is beneficial.
+In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
+For these FG-dominating modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
 In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
@@
 For the
-analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines), hence $N_{\rm seps}=1$. The updated limits in Kolopanis et al. (\textit{submitted})
-use three separation types.
+analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines).
+However, both the updated limits in Kolopanis et al.
+(\textit{submitted}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
 \item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
@@
 \item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total}$) neglects 
-the fact that we average baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
+the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total} = 51$) neglects 
+the fact that the \citetalias{ali_et_al2015} analysis averages baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 \end{equation}
-\noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+\noindent where, in the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
 entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 32$ instead 
-of $51$. 
+N_{\rm gps}}{2}}$\Big).
+A revised \citetalias{ali_et_al2015} analysis should therefore use $N_{\rm bls} \sim 32$ instead of $51$, and this change is taken into account in Figure \ref{fig:sense_check}.
+However, the analysis in this paper and in Kolopanis et al.
+(\textit{submitted}) does not average baselines into groups ($N_{\rm gps} = 1$), and hence $N_{\rm bls} = 51$ for the revised PAPER-64 analysis.
 \item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
@@
 
-Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of \citetalias{ali_et_al2015} in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.
+Our revised sensitivity estimate for the \citetalias{ali_et_al2015} analysis of PAPER-64 is shown in Figure \ref{fig:sense_check}. 
+Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.
 
@@
 	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
-\sqrt{3}$ for three baseline types is needed to match \citetalias{ali_et_al2015} exactly). Major factors that contribute to the discrepancy are $
+published sensitivity limits (gray), both computed for the analysis methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
 \Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
-sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
+sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
 	\label{fig:sense_check}
@@
 spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
-\eqref{eq:sense}. All three show good agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.
+\eqref{eq:sense}. All three show good agreement.
 
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-While this does not match perfectly with the $2\sigma$ analytic prediction for noise (green), we find good agreement between them to within a factor of two (which we believe is reasonable given the approximations we make in computing the analytic).}
+We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
 	\label{fig:data_errors}
@@
 
-\color{blue}
-
-\appendix
-\section{A toy model for inverse covariance weighting}
-\label{sec:icw_appendix}
-
-We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
-We have specifically chosen a toy model where the data covariance is diagonal, as we expect the EoR signal to be.
-We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\phi_i$
-\begin{equation}
-\Delta_i = \sigma_i + \phi_i
-\end{equation}
-with 
-\begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
-\end{equation}
-and we wish to estimate $s$.  The contaminant in this case has a similar structure for its covariance, and is assumed uncorrelated with the signal
-\begin{equation}
-\langle \phi_i \rangle = 0; \; 
-\langle \phi^2_i \rangle = f; \; 
-\langle \phi \phi^T \rangle = f I_{N \times N} \equiv F; {\rm and}~ 
-\langle \sigma_i \phi_j \rangle = 0
-\end{equation}
-%That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
-The estimator for $s$ using the inverse covariance weighting prescription is
-\begin{equation}
-\label{eq:CaseOneICW}
-\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) 
-= \frac{\Delta^T \Delta}{N}
-\end{equation}
-%and plugging in the relevant quantities gives
-%\begin{eqnarray}
-%\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
-%& = & \frac{\Delta^T \Delta}{N}
-%\end{eqnarray}
-We note that
-\begin{equation}
-\langle \hat{s} \rangle = s + g
-\end{equation}
-In this case, the quadratic estimator returns an entirely reasonable result, but, 
-{\it since the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
-
-Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
-\begin{equation}
-\Delta_i = \sigma_i + \phi m_i
-\end{equation}
-where the properties of $\sigma_i$ are as before,
-%\begin{eqnarray}
-%\langle \sigma_i \rangle & = & 0 \\
-%\langle \sigma^2_i \rangle & = & s \\
-% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
-%\end{eqnarray}
-but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
-\begin{equation}
-\langle \phi \rangle = 0; \;
-\langle \phi^2 \rangle = f; \; 
- \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
- m^T m = 1
-\end{equation}
-Here $m$ represents a mode which is correlated across many data points, with correlation given by $m m^T$, and, and the amplitude of its realization is $\phi$.
-
-\color{black}
-
 \appendix

### 2018-05-01 PAPER.tex
edited boot methods plot and text to be compatible to 'all bl cross-multiplications' run

@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ upper limits with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
+bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
+Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$$2$-$3$ in mK$^{2}$.
-
-Finally, one last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $2$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
+
+In addition to no longer bootstrapping along the time axis, we have made two other changes from the \citetalias{ali_et_al2015} analysis regarding bootstrapping.
+The first is that we now bootstrap over baseline cross-products, instead of baselines themselves.
+In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
+On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e.
+the power spectrum).
+This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.
+
+Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
 The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.
@@
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim2$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our 
+decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our 
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 

### 2018-05-01 plotting_scripts/plot_PS_invcov.py
adding directory with plotting scripts and data needed for final plotting

@@ -1,0 +1,537 @@
+#!/usr/bin/env python
+"""Create (pre-sigloss) 2 sigma upper limit plot.
+
+Also plots 2 sigma EoR upper limit post-sigloss.
+Takes outputs from pspec_final_sepXXX_full.npz.
+"""
+old_analytical = False
+import numpy as np
+import sys
+import os
+import argparse
+import py21cmsense as py21cm
+import capo
+from capo.cosmo_units import f212z
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+import itertools
+
+parser = argparse.ArgumentParser(
+    description=('Calculate power spectra for a run '
+                 'from pspec_oqe_2d.py'))
+args = parser.parse_args()
+
+files = ['plot_PS_invcov.npz']
+
+zs = []
+for filename in files:
+    F = np.load(filename)
+    freq = F['freq']
+    zs.append(f212z(freq * 1e9))
+
+# reverse order to make high redshift of left of plot
+zs = np.unique(zs)[::-1]
+Nzs = len(zs)
+# define some color format sets for the plotter
+# colors = ['r', 'g', 'k', 'b']
+markers = ['o', ',', 'd', '^', 's', 'v']
+# markers = itertools.cycle(markers)
+marker_count = [0 for i in xrange(Nzs)]
+figsize = (5 * (1 + Nzs)/2., 6)
+
+# Create figure and prep subplot sizes for Delta^2
+fig = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax1 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
+
+# Create figure and prep subplots for P(k)
+fig2 = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax2 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
+
+# Create figure and prep subplot sizes for Delta^2 Noise
+fig3 = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax3 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
[…]

### 2018-05-01 plotting_scripts/plot_PS_reg.py

@@ -1,0 +1,537 @@
+#!/usr/bin/env python
+"""Create (pre-sigloss) 2 sigma upper limit plot.
+
+Also plots 2 sigma EoR upper limit post-sigloss.
+Takes outputs from pspec_final_sepXXX_full.npz.
+"""
+old_analytical = False
+import numpy as np
+import sys
+import os
+import argparse
+import py21cmsense as py21cm
+import capo
+from capo.cosmo_units import f212z
+import matplotlib.pyplot as plt
+from matplotlib import gridspec
+import itertools
+
+parser = argparse.ArgumentParser(
+    description=('Calculate power spectra for a run '
+                 'from pspec_oqe_2d.py'))
+args = parser.parse_args()
+
+files = ['plot_PS_reg.npz']
+
+zs = []
+for filename in files:
+    F = np.load(filename)
+    freq = F['freq']
+    zs.append(f212z(freq * 1e9))
+
+# reverse order to make high redshift of left of plot
+zs = np.unique(zs)[::-1]
+Nzs = len(zs)
+# define some color format sets for the plotter
+# colors = ['r', 'g', 'k', 'b']
+markers = ['o', ',', 'd', '^', 's', 'v']
+# markers = itertools.cycle(markers)
+marker_count = [0 for i in xrange(Nzs)]
+figsize = (5 * (1 + Nzs)/2., 6)
+
+# Create figure and prep subplot sizes for Delta^2
+fig = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax1 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
+
+# Create figure and prep subplots for P(k)
+fig2 = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax2 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
+
+# Create figure and prep subplot sizes for Delta^2 Noise
+fig3 = plt.figure(figsize=figsize)
+gs = gridspec.GridSpec(1, Nzs)
+gs.update(hspace=0.0, wspace=0.2)
+ax3 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
+plt.subplots_adjust(left=0.2)
+
[…]

### 2018-05-01 plotting_scripts/plot_ant_layout.py

@@ -1,0 +1,47 @@
+#! /usr/bin/env python
+import aipy as a, numpy as n, pylab as p
+import sys, optparse
+
+o = optparse.OptionParser()
+a.scripting.add_standard_options(o, cal=True)
+o.add_option('--aspect_neq', action='store_true', help='Do not force equal aspect in x/y plot.')
+o.add_option('--nonumbers', action='store_true', help='Do not plot antenna numbers next to symbols.')
+opts, args = o.parse_args(sys.argv[1:])
+
+th = n.arange(0, 2*n.pi, .01)
+r = 5.
+
+aa = a.cal.get_aa('psa6240_v003', .1, .1, 1)
+antpos = [aa.get_baseline(0,i,src='z') for i in range(len(aa.ants))]
+antpos = n.array(antpos) * a.const.len_ns / 100.
+x,y,z = antpos[:,0], antpos[:,1], antpos[:,2]
+x -= n.average(x)
+y -= n.average(y)
+p.plot(x,y, 'k.')
+if False:
+    im = a.img.Img(size=300, res=30)
+    DIM = 300./30
+    im.put((x,y,z), z)
+    _z = a.img.recenter(im.uv, (DIM/2,DIM/2))
+    print _z
+    _z = n.ma.array(_z, mask=n.where(_z == 0, 1, 0))
+    _x,_y = im.get_uv()
+    _x = a.img.recenter(_x, (DIM/2,DIM/2))
+    _y = a.img.recenter(_y, (DIM/2,DIM/2))
+    p.contourf(_x,_y,_z,n.arange(-5,5,.5))
+for ant,(xa,ya,za) in enumerate(zip(x,y,z)):
+    hx,hy = r*za*n.cos(th)+xa, r*za*n.sin(th)+ya
+    if za > 0: fmt = '#eeeeee'
+    else: fmt = '#a0a0a0'
+    #p.fill(hx,hy, fmt)
+    #if not opts.nonumbers: p.text(xa,ya, str(ant))
+p.grid()
+#p.xlim(-100,100)
+p.xlabel("East-West Antenna Position (m)",fontsize=18)
+p.ylabel("North-South \nAntenna Position (m)",fontsize=18)
+p.tick_params(axis='both', which='major', labelsize=18)
+p.ylim(-25,25)
+a = p.gca()
+if not opts.aspect_neq: a.set_aspect('equal')
+p.tight_layout()
+p.show()

### 2018-05-01 plotting_scripts/plot_bootmethods.py

@@ -1,0 +1,27 @@
+#! /usr/bin/env python
+
+import numpy as n
+import matplotlib.pyplot as plt
+
+# Files to read
+boot_bl = n.load('plot_bootmethods.npz')
+boot_time = n.load('plot_bootmethods_time.npz')
+
+noise = 2827408.41233 #4436767.36822 # XXX
+
+# Plot
+plt.plot(boot_bl['kpl'], boot_bl['pIn_err_old']*2, color='black', linewidth=2, label='Bootstrap baselines only')
+plt.plot(boot_time['kpl'], boot_time['pIn_err_old']*2, color='0.5', linewidth=2, label='Bootstrap baselines and times')
+plt.axhline(y=noise*2, color='green', linestyle='-', linewidth=2, label='Analytic')
+plt.legend(numpoints=1,prop={'size':14},loc='best')
+plt.grid()
+plt.yscale('log')
+#plt.title('2$\sigma$ errors for PAPER-64 using different bootstrapping methods')
+plt.xlabel('$k_{\\parallel}$ [$h$ Mpc$^{-1}$]',fontsize=18)
+plt.ylabel('$P(k)$ [mK$^{2}$($h^{-1}$ Mpc)$^{3}$]',fontsize=18)
+plt.tick_params(axis='both', which='major', labelsize=14)
+#plt.ylim(1e6,7e9) # for data
+plt.ylim(5e5,1e8)
+plt.show()
+
+

### 2018-05-01 plotting_scripts/plot_jackknives.py

@@ -1,0 +1,91 @@
+#! /usr/bin/env python
+
+import numpy as n
+import pylab as p
+
+"""
+Error bars are errors of each PS half added in quadrature 
+(equivalent script: ~/capo/ctc/code/plot_jackknives_v2.py)
+"""
+
+# New jackknives (differencing of 2 PS)
+file_lst_diff = n.load('plot_jackknives_lst.npz')
+file_lst_1 = n.load('plot_jackknives_lst1.npz')
+file_lst_2 = n.load('plot_jackknives_lst2.npz')
+file_bls_diff = n.load('plot_jackknives_bls.npz')
+file_bls_1 = n.load('plot_jackknives_bls1.npz')
+file_bls_2 = n.load('plot_jackknives_bls2.npz')
+file_eo_diff = n.load('plot_jackknives_evenodd.npz')
+file_eo_1 = n.load('plot_jackknives_eo1.npz')
+file_eo_2 = n.load('plot_jackknives_eo2.npz')
+
+# Mask for masking out inner horizon points
+mask = n.ones_like(file_lst_diff['kpl'])
+mask[9:12] = 0
+mask = n.ma.masked_where(mask==0, mask)
+
+# Horizon limit
+horizon = 0.06272882578029243 # computed using hera_pspec.conversions.Cosmo_Conversions.tau_to_kpara
+
+# Plot range
+ymin=-0.7e9
+ymax=0.7e9
+
+#------------------------
+
+# LST null test
+noise_lst = n.sqrt(2*5190369.42535**2) # 1-sigma noise added in quadrature (sqrt(n^2 + n^2))
+p.figure()
+p.errorbar(file_lst_diff['kpl']*mask,file_lst_diff['pIv_old']*mask,n.sqrt(file_lst_1['pIv_err_old']**2 + file_lst_2['pIv_err_old']**2)*2*mask,linestyle='',marker='.',color='k')#,label='LST Null Test')
+#p.errorbar(file_lst_1['kpl']-0.005,file_lst_1['pIv_old'],file_lst_1['pIv_err_old']*2,linestyle='',marker='.',color='k',label='LST1')
+#p.errorbar(file_lst_2['kpl']+0.005,file_lst_2['pIv_old'],file_lst_2['pIv_err_old']*2,linestyle='',marker='.',color='0.5',label='LST2')
[…]

### 2018-05-01 plotting_scripts/plot_sigloss.py

@@ -1,0 +1,164 @@
+#! /usr/bin/env python
+
+import numpy as n
+import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+from scipy import stats
+
+# Read file and get data
+file = n.load('plot_sigloss.npz')
+k = file['k']
+xs = 10**file['xs']
+ys = 10**n.abs(file['ys'])*n.sign(file['ys'])
+ysI = 10**n.abs(file['ysI'])*n.sign(file['ysI'])
+M = file['kdeC']
+M_I = file['kdeI']
+pC = file['pC']
+pI = file['pI']
+binsx = file['binsx']
+binsy = file['binsy']
+binsy_full = 10**n.abs(binsy)*n.sign(binsy)
+
+"""
+file2 = n.load('inject_sep0,1_0.001/pspec_pk_k3pk.npz')
+file_pts = file2['pCv']
+file_pts_I = file2['pIv']
+k_pts_ind = n.where(file2['kpl'] == k)[0][0]
+Pins = n.array(file['Pins']).flatten() # P_in
+Pouts = n.array(file['Pouts']).flatten() # P_out
+Pouts_I = n.array(file['Pouts_I']).flatten() # P_out for I case
+ind = n.where(Pins > 0)[0] # positive P_ins only
+Pins = Pins[ind]
+Pouts = Pouts[ind]
+Pouts_I = Pouts_I[ind]
+bins_concat = file['bins_concat']
+binsx = file['binsx']
+binsy = file['binsy']
+#binsx = file['bins']
+#binsy = file['bins']
+binsy_full = n.concatenate((-10**binsy[::-1],10**binsy))
+"""
+"""
+# Fit polynomial to mean signal loss transfer curve
+xs = n.log10(n.abs(Pins.flatten())) # absolute value since symmetric
+ys = n.log10(n.abs(Pouts.flatten()))
+ys_I = n.log10(n.abs(Pouts_I.flatten()))
+xs = n.append(n.repeat(0,100000),xs) # force fit to go through zero
+ys = n.append(n.repeat(0,100000),ys)
+ys_I = n.append(n.repeat(0,100000),ys_I)
+order = n.argsort(xs) # re-order after padding
[…]

### 2018-05-01 plotting_scripts/plot_sigloss_modeloop.py

@@ -1,0 +1,148 @@
+#! /usr/bin/env python
+
+import numpy as n
+import matplotlib.pyplot as p
+from scipy.optimize import curve_fit
+
+# Reads in power spectrum results from projecting out 0,1,2... modes
+# Plots power spectrum results before and after signal loss correction as a function of modes removed
+
+if True: # eigenmodes set to 1
+    path = 'plot_sigloss_modeloop_mode'
+    startmode=0
+    nmodes=22
+    deltamode=1
+    xlabel='Number of modes down-weighted using inverse covariance weighting'
+    f1 = '/project_'
+    f2 = '_modes'
+    loop = n.arange(startmode,nmodes,deltamode)
+
+if True: # added identity parameters in LOG space
+    path_add = 'plot_sigloss_modeloop_add'
+    startmode_add=-4 
+    endmode_add=0
+    nmodes_add=20 #20000 
+    xlabel_add='Strength of identity added: $\mathbf{\widehat{C}}$ + $\gamma$Tr$(\mathbf{\widehat{C}})\mathbf{I}$'
+    f1_add = '/add_'
+    f2_add = '_identity'
+    loop_add = n.logspace(startmode_add,endmode_add,nmodes_add)
+
+# Read files
+sense=4436767.36822*2 # XXX from plotting one of the "project_#_modes" directories
+PS_i_up = []
+PS_f_up = []
+PS_i = []
+PS_f = []
+k_ind = -3
+
+for mode_num in loop:
+    filename = path + f1 + str(mode_num) + f2
+    print 'Reading', filename
+    print mode_num
+    f = n.load(filename+'/pspec_final_sep0,1_full.npz')
+    kpl = f['kpl']
+    k = kpl[k_ind] 
+    PS_i_up.append(2*n.array(f['pCv_err_old'])[k_ind])
+    PS_f_up.append(2*n.array(f['pCv_err'])[k_ind])
+    PS_i.append(n.abs(f['pCv_old'])[k_ind])
+    PS_f.append(n.abs(f['pCv'])[k_ind])
+
+#""" # Read in added identity case as a second curve being plotted
+PS_i_up_add = []
+PS_f_up_add = []
+PS_i_add = []
+PS_f_add = []
+for mode_num in loop_add:
[…]

### 2018-05-01 plotting_scripts/plot_sigloss_terms.py

@@ -1,0 +1,181 @@
+#! /usr/bin/env python
+
+import numpy as n
+import matplotlib.pyplot as p
+from scipy import stats
+
+# Read file and get data
+file = n.load('plot_sigloss_terms.npz')
+k = file['k']
+Pins = n.array(file['Pins']).flatten() # P_in
+ind = n.where(Pins > 0)[0] # only pos P_ins
+ind2 = n.argsort(Pins[ind]) # sort if using both neg and pos
+Pins = Pins[ind][ind2]
+Pouts = n.array(file['Pouts']).flatten()[ind][ind2] # P_out
+Pouts_I = n.array(file['Pouts_I']).flatten()[ind][ind2] # P_out for I case
+pCvs_Cr = n.array(file['pCvs_Cr_fold']).flatten()[ind][ind2]
+pCes_Cr = n.array(file['pCes_Cr_fold']).flatten()[ind][ind2]
+pCves = n.array(file['pCves_fold']).flatten()[ind][ind2]
+pIves = n.array(file['pIves_fold']).flatten()[ind][ind2]
+pCrs = n.array(file['pCrs_fold']).flatten()[ind][ind2]
+pCv = file['pCv'] # final PS points per k
+pIv = file['pIv'] 
+
+# Smooth curves
+poly_dim = 4
+#"""
+    # absolute value
+poly_data_Cr = n.polyfit(n.log10(n.abs(Pins)),n.log10(n.abs(pCvs_Cr)),poly_dim)
+blue = 10**n.polyval(poly_data_Cr,n.log10(Pins))
+
+red_ind_pos = n.where(pCves>=0)[0] # where positive pCves
+red_ind_neg = n.where(pCves<0)[0] # where negative pCves
+Pins_red_pos = Pins[red_ind_pos] # adjust Pins
+Pins_red_neg = Pins[red_ind_neg]
+poly_cross_pos = n.polyfit(n.log10(Pins_red_pos),n.log10(pCves[red_ind_pos]),poly_dim)
+poly_cross_neg = n.polyfit(n.log10(Pins_red_neg),n.log10(-pCves[red_ind_neg]),poly_dim)
+red_neg = -10**n.polyval(poly_cross_neg,n.log10(Pins_red_neg))
[…]

### 2018-05-02 PAPER.tex
revised text to reflect new plotting style, and new plotting color choices

@@
 The details of the simulation used to generate the figure is explained in Section
-\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
+\ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.  The gray 
 horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
@@
 $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
+the data-only power spectrum value) and the black curve (which exhibits $\sim$$4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
 	\label{fig:sigloss_terms}
@@
 \widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{8} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
+From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
 For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.
@@
 
-The loss-corrected power spectrum result for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
+The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red).
 %There are a few important checks to examine.
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (blue dashed).
+Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{The power spectrum of PAPER-64 data, weighted by an inverse covariance estimator.
-The power spectra values pre-signal loss estimation are shown as black and gray points (positive and negative values, respectively,
-with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
-spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
-parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
+	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
+Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
+The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
+Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.}
 \label{fig:ps2_data}
@@
 estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (gray curve). In other words, more EoR-dominated fluctuations are being overfit and 
+becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
-increases with the number of down-weighted modes (black curve).
+increases with the number of down-weighted modes (solid red).
 The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
@@
 Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to not weighting (blue dashed line).
+is beneficial compared to uniform weighting (blue).
 In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
+The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
 We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
 From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
+We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
 We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
@@
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
-are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
+are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
 are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
@@
 Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
-Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
+Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
 This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e.
@@
 Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
-weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as solid green.
+plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
+weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
+as green.
 In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
@@
 In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
-in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
+in both panels and represents a third regularization technique.
+This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity
 matrix element-wise to $\widehat{\textbf{C}}$).
 This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at
+We see that all three regularization schemes shown (solid red, dashed red, black) perform similarly at
 their best (i.e.
-when $\sim2$ eigenmodes are down-weighted in the case of the black solid curve).
+when $\sim2$ eigenmodes are down-weighted in the case of the solid red curve).
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
@@
 
-A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
+A revised PAPER-64 power spectrum for our subset of data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
 \ref{fig:ps1_data}.
-Again, the dashed black curve represents our upper limit on EoR, post-signal loss estimation.
-Black and gray points correspond to positive and negative power spectrum values respectively (pre-signal loss estimation), with
-$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
-noise (solid green).
+Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework.
+The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
+$2\sigma$ errors bars).
+It is also shown as an upper limit using the signal injection framework (solid blue).
+Finally, the gray shaded regions combine the measured uniform weighted power spectrum values and the thermal noise.
+We show this power spectrum result as one example of how a simple regularization can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
 In Kolopanis et al.
-(\textit{submitted}), multiple baselines are used in the analysis to produce a $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
-a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
+(\textit{submitted}), multiple redshifts are explored and found to benefit from weighting differently.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{\rm eff}$.
-The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and
-negative power spectrum values, respectively, with $2\sigma$ error bars).
-The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation.
-There is a small amount of loss using this regularization.
-The dashed blue line is the uniform-weighted
-power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
-observational parameters. This power spectrum result differs from \citetalias{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m 
-East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
-loss, bootstrapping, and the theoretical error computation.
-In Kolopanis et al.
-(\textit{submitted}), multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
-a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
+	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
+The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
+Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
+This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
+(\textit{submitted}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
+loss, bootstrapping, and the theoretical error computation.}
 	\label{fig:ps1_data}
@@
 
-As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
-In Kolopanis et al.
-(\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$\,$h$ Mpc$^{-1}$ and $z=8.37$,
-a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously under-estimated limit and 
+As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
+This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, accurately estimating thermal noise, and implementing jackknife tests.
+Our revised PAPER-64 limits are presented in Kolopanis et al.
+(\textit{submitted}), which supersede all previously published PAPER limits.
+The main reasons for a previously under-estimated limit and
 ways in which our new analysis differs can be summarized by the following:
@@
 \item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for empirically estimated inverse 
-covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
-\ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. 
+covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
+\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, our results are still a 
+factor of $\sim10$ in mK higher than the lossy empirical inverse covariance limits. Under-estimated signal loss therefore represents the bulk of our revision. 
 This revision is similar to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
@@
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our 
+decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our overall
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 

### 2018-05-02 PAPER.tex
edited language to reflect using a subset of the data only; also careful about using the word 'revised PS' since this paper does not revise the A15 PS

@@
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
-case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
-from the lessons learned. A companion paper, Kolopanis et al. (\textit{submitted}), builds off of the methods in this paper to present PAPER-64 results for multiple redshifts and baseline types.
+case study using data from the 64-element configuration of PAPER.
+In this study we use a subset of the PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
+(\textit{submitted}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
 
@@
 
-We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
-\citetalias{ali_et_al2015} and obtain a revised power spectrum estimate.
+We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
+\citetalias{ali_et_al2015}) in order to illustrate our revised analysis pipeline.
 
@@
 	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
-	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
-paper (i.e. the shortest horizontal spacings).}
+	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
+paper (i.e. a subset of the shortest horizontal spacings).}
 	\label{fig:ant_layout}
@@
 
-For our revised analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly longer RA 
+For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
 range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
+We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}.
 All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
@@
 as green.
-In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
+In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 
-A revised PAPER-64 power spectrum for our subset of data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
+The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
 \ref{fig:ps1_data}.
@@
 accounting of the differences which have been discovered.
-Our revised theoretical error estimation, which is often plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
+Our revised theoretical error estimation, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
 
@@
 However, the analysis in this paper and in Kolopanis et al.
-(\textit{submitted}) does not average baselines into groups ($N_{\rm gps} = 1$), and hence $N_{\rm bls} = 51$ for the revised PAPER-64 analysis.
+(\textit{submitted}) does not average baselines into groups ($N_{\rm gps} = 1$).
+For the subset of data presented in this paper, $N_{\rm bls} = 10$.
 \item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
@@
 dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
-the ``even" dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline group $1$, etc. We only form 
+the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
 $\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``even" with ``even", for 
 example, in order to prevent the squaring of the same thermal noise.
-We recognize that this method results in a hit to our sensitivity.
-Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the \citetalias{ali_et_al2015} analysis (which uses the same groupings).
 

### 2018-05-03 PAPER.tex
edited jackknife text to reflect the interpretation of the latest null tests made with a subset of baselines

@@
 
-As shown in Figure \ref{fig:ps1_data}, our re-analysis of the PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
+As shown in Figure \ref{fig:ps1_data}, our illustrative PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
 As discussed in Section \ref{sec:BiasTypes}, this bias is
-most likely attributable to foreground leakage. The cause for biases at higher $k$-values is more difficult to pinpoint.
+most likely attributable to foreground leakage. %The cause for biases at higher $k$-values is more difficult to pinpoint.
 
 Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
-that they are not attributable to EoR.
+that our biases are not attributable to EoR.
 Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
@@
 
-The three results are shown in Figure \ref{fig:null}. Each test displays the differenced power spectrum between two halves of a jackknife. We take jackknives along three different axes:
+The three results are shown in Figure \ref{fig:null}.
+Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the errors of the two dataset halves added in quadrature.
+The expected thermal noise level (gray shaded regions) is the thermal noise of each dataset added in quadrature as well.
+Constructing the tests as such ensures that we are probing whether the variances of each dataset differ by an amount consistent with the thermal noise.
+
+We take jackknives along three different axes:
 
@@
 analysis. No baselines are repeated between the two datasets.
-\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
-4.6-8.6 hours).
+\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.5 hours) and second half (LSTs 
+4.5-8.6 hours).
 \item Day: We split our dataset into even and odd Julian dates.
@@
 The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test and even/odd test.
-All three tests, whether biased or not, have an extra variance that is strongly $k$-dependent.
-Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
+We find that there are no significant systematics for $k > \pm 0.2$\,$h$ Mpc$^{-1}$ for all three tests.
+However, we find that all tests exhibit an extra variance at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), likely due to foreground-noise coupling terms when foregrounds are brightest.
+Additionally, we find that the LST null test is not fully consistent with zero, implying a bias that is LST dependent and likely caused by varying foregrounds.}
 	\label{fig:null}
@@
 
-In investigating Figure \ref{fig:null}, we focus on two main aspects of each test --- whether the error bars are consistent with zero, and whether they are consistent with thermal noise.
-The former indicates a `passing' null test where there is no bias along the jackknife axis.
-The latter reveals whether there is additional variance present that lies above the thermal noise.
-
-We find that the baselines test is fully consistent with noise, as all error bars pass through zero.
-Therefore, we conclude that the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias.
-We suspect it is the former, though more thorough jackknives along this axis are needed to make this conclusion.
-For the LST test, $90\%$ of all the error bars pass through zero, which is slightly lower than the expected $95\%$.
-This indicates a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
-In other words, the two jackknife halves differ by an amount greater than thermal noise and do not completely cancel out the sky signal when differencing.
-The even/odd test shows $81\%$ of all error bars being consistent with zero, again indicating the presence of a low level bias.
-The cause of this particular systematic is not obvious, and requires further investigation that we do not carry out in this paper.
-Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
-
-Finally, we note that all three null tests exhibit error bars that are strongly $k$-dependent.
-The errors are largest just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
-We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
+In investigating Figure \ref{fig:null}, we focus on three main possibilities --- whether the data points and error bars are consistent with thermal noise (``passing"), whether the error bars are consistent with zero but not consistent with thermal noise (``passing but has an additional variance"), or whether the error bars are not consistent with zero at all (``failing").
+We examine each case in the context of our results below.
+
+Firstly, all three null tests display data points that lie within the thermal noise gray band for $k > \pm 0.2$\,$h$ Mpc$^{-1}$.
+In addition, all three null tests show error bars consistent with the thermal noise level for those same $k$'s.
+This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e.
+the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
+We deem these as ``passing" null tests for the specific jackknives taken (again, dividing up the data in a different way along the same axes may not yield the same results, so more thorough testing is needed to be sure).
+
+The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests.
+This indicates an additive noise component that is increasing our errors.
+More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
+This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
+The cross-terms, however, can introduce extra variance that would vary with foreground strength.
+It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.
+
+Lastly, a third null test result is an error bar not consistent with zero.
+This is the case for the LST null test at $k\sim-0.15$\,$h$ Mpc$^{-1}$ and $k\sim-0.2$\,$h$ Mpc$^{-1}$.
+In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e.
+the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
+This result implies that there exists a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
+Again, it is not surprising that this type of bias occurs near the horizon limit.
+
+%Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
+
+%We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
 This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
 
-There are a couple possible explanations for this.
+%There are a couple possible explanations for this.
 Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
@@
 In this section we have presented the first jackknife and null tests from the PAPER experiment.
-While simple, they outline a framework that can be used in the future.
-The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough tests.
+Unsurprisingly, they imply that our measurements are biased by foregrounds, and not the EoR signal (a clean detection of EoR would have passed all three tests).
+While simple, these tests outline a framework that can be used by future measurements.
+The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough investigations of this nature.
 

### 2018-05-03 PAPER.tex
compiled with latest plots, edited text/caption to noise sim PS plot to reflect new plotting style

@@
 Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}, where the black and gray points represent pre-signal loss estimated positive and negative power spectrum values, respectively (with 
-$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{\rm eff}$), the dashed black line represents the post-signal loss $2\sigma$ upper limit on the EoR signal, the dashed blue line represents the $2\sigma$ uniform-weighted power
-spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
-\eqref{eq:sense}. All three show good agreement.
+\ref{fig:ps_noise}, where again the solid red curve is the $2\sigma$ upper limit on the EoR signal after the signal injection framework.
+The solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation
+\eqref{eq:sense}. Both show good agreement with each other, as well as with the various uniform weighted limits (data points and error bars, solid blue line, gray shaded region).
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The original weighted 
-power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
-\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
-The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation.
-The dashed blue line is the uniform-weighted power spectrum $2\sigma$ upper
-limit. The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
-estimates show agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.}
+	\caption{The power spectrum for a noise simulation that mimics the noise level of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
+The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
+Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
+All estimates show good agreement.}
 	\label{fig:ps_noise}
@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to better agree with the analytic prediction for noise.
 While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $2$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
+We find that these revised limits better agree with the $2\sigma$ analytic prediction for noise (green).}
 	\label{fig:data_errors}

### 2018-05-03 PAPER.tex
updated PS caption wording

@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
+	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of empirical inverse covariance weighting.
+The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
 Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
+	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of $\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
+The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework.
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{The power spectrum for a noise simulation that mimics the noise level of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
+	\caption{The power spectrum for a noise simulation that mimics the noise level of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.

### 2018-05-03 PAPER.tex
minor text change

@@
 the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
-$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``even" with ``even", for 
+$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``baseline 1" with ``baseline 1", for 
 example, in order to prevent the squaring of the same thermal noise.

### 2018-05-08 PAPER.tex
Tue May  8 17:15:34 EDT 2018

--- 2018-05-03 PAPER.tex
@@
 
+\newcommand{\invC}{\ensuremath{C^{-1}}}
+\newcommand{\dC}[1]{\ensuremath{C_{,#1}}}
+\DeclareMathOperator{\Tr}{Tr}
+\newcommand{\half}{\ensuremath{\frac{1}{2}}}
+\newcommand{\PDeriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
+
 % Math shortcuts from Danny
@@
 pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
-case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of the PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
-(\textit{submitted}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
+case study using data from the 64-element configuration of PAPER, motivating a revised PAPER-64 power spectrum 
+from the lessons learned. A companion paper, Kolopanis et al. (\textit{submitted}), builds off of the methods in this paper to present PAPER-64 results for multiple redshifts and baseline types.
 
@@
 
-\begin{center}
-Power Spectrum Themes
-\end{center}
-
-A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
-spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
-a rigorous power spectrum analysis.
+%\begin{center}
+%Power Spectrum Themes
+%\end{center}
+%
+%A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
+%spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
+%a rigorous power spectrum analysis.
 \begin{itemize}
@@
 \end{equation}
-Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to 
-Kelvin and taking into account cosmological scalings.
-It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
+
+The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$.
+In practice, it also implements a transform of the frequency-domain visibilities to
+$\mathbf{k}$ space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+
+their Fourier conjugates, and converts from Jy to Kelvin and .
+It is formally evaluated as  (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
 Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
@@
 of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{P}}$ is a weighted sum of the elements of $\textbf{P}$ with weights that sum to unity.
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in
-experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
-purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section
-\ref{sec:Sigloss}.
-
-\subsubsection{Toy Model: Inverse Covariance Weighting}
-\label{sec:toymodel}
 
@@
 
-We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
-\citetalias{ali_et_al2015}) in order to illustrate our revised analysis pipeline.
+We now apply these lessons to data from the PAPER experiment to make a new analysis of the PAPER-64 dataset originally presented in 
+\citetalias{ali_et_al2015} and obtain a revised power spectrum estimate.
 
@@
 	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
-	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
-paper (i.e. a subset of the shortest horizontal spacings).}
+	\caption{The PAPER-64 antenna layout. We use only the $30$ m East/West baselines for the revised analysis in this 
+paper (i.e. the shortest horizontal spacings).}
 	\label{fig:ant_layout}
@@
 
-For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
+For our revised analysis, we use $8.1$ hours of LST (RA $0.5$-$8.6$ hours) and $51$ total baselines (\citetalias{ali_et_al2015} uses a slightly longer RA 
 range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
-We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}.
 All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
@@
 The details of the simulation used to generate the figure is explained in Section
-\ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.  The gray 
+\ref{sec:Practice}; here we fit smooth polynomials to our data points to make an illustrative example.  The gray 
 horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
@@
 $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data-only power spectrum value) and the black curve (which exhibits $\sim$$4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
+the data-only power spectrum value) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
 	\label{fig:sigloss_terms}
@@
 \widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
+From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{4} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{8} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
 For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.
@@
 
-The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red).
+The loss-corrected power spectrum result for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points).
 %There are a few important checks to examine.
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
+Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (blue dashed).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
-Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.}
+	\caption{The power spectrum of PAPER-64 data, weighted by an inverse covariance estimator.
+The power spectra values pre-signal loss estimation are shown as black and gray points (positive and negative values, respectively,
+with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
+spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
+parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
 	\label{fig:ps2_data}
@@
 estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
+becomes more aggressive (gray curve). In other words, more EoR-dominated fluctuations are being overfit and 
 subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
-increases with the number of down-weighted modes (solid red).
+increases with the number of down-weighted modes (black curve).
 The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
@@
 Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to uniform weighting (blue).
+is beneficial compared to not weighting (blue dashed line).
 In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
+The gray and black lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
 We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
 From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
+We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.
 We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
@@
 	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
-are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
+are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
 are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
@@
 Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
-Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
+Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance.
 This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e.
@@
 Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
-weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
+plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
+weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
+as solid green.
+In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
-in both panels and represents a third regularization technique.
-This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity
+in both panels and represents a third regularization technique. This line (red) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity 
 matrix element-wise to $\widehat{\textbf{C}}$).
 This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (solid red, dashed red, black) perform similarly at
+We see that all three regularization schemes shown (black solid, black dashed, red) perform similarly at
 their best (i.e.
-when $\sim2$ eigenmodes are down-weighted in the case of the solid red curve).
+when $\sim2$ eigenmodes are down-weighted in the case of the black solid curve).
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
@@
 
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
+A revised PAPER-64 power spectrum (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
 \ref{fig:ps1_data}.
-Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework.
-The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
-$2\sigma$ errors bars).
-It is also shown as an upper limit using the signal injection framework (solid blue).
-Finally, the gray shaded regions combine the measured uniform weighted power spectrum values and the thermal noise.
-We show this power spectrum result as one example of how a simple regularization can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
+Again, the dashed black curve represents our upper limit on EoR, post-signal loss estimation.
+Black and gray points correspond to positive and negative power spectrum values respectively (pre-signal loss estimation), with
+$2\sigma$ errors bars. Also plotted are the uniform-weighted power spectrum upper limit (dashed blue) and theoretical prediction of 
+noise (solid green).
 In Kolopanis et al.
-(\textit{submitted}), multiple redshifts are explored and found to benefit from weighting differently.
+(\textit{submitted}), multiple baselines are used in the analysis to produce a $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{The power spectrum of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
-(\textit{submitted}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
-loss, bootstrapping, and the theoretical error computation.}
+	\caption{Power spectrum of PAPER-64 using $\widehat{\textbf{C}}_{\rm eff}$.
+The weighted power spectrum, pre-signal loss estimation, is shown by the black and gray points (corresponding to positive and
+negative power spectrum values, respectively, with $2\sigma$ error bars).
+The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation.
+There is a small amount of loss using this regularization.
+The dashed blue line is the uniform-weighted
+power spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on 
+observational parameters. This power spectrum result differs from \citetalias{ali_et_al2015} in that it only uses data from one type of baseline ($30$ m 
+East/West baselines) instead of three. Major differences from previously published results stem from revisions regarding signal 
+loss, bootstrapping, and the theoretical error computation.
+In Kolopanis et al.
+(\textit{submitted}), multiple baselines are used in the analysis to produce a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$ $h$ Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK.}
 	\label{fig:ps1_data}
@@
 accounting of the differences which have been discovered.
-Our revised theoretical error estimation, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
+Our revised theoretical error estimation, which is often plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
 
@@
 For the
-analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines).
-However, both the updated limits in Kolopanis et al.
-(\textit{submitted}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
+analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines), hence $N_{\rm seps}=1$. The updated limits in Kolopanis et al. (\textit{submitted})
+use three separation types.
 \item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
@@
 \item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total} = 51$) neglects 
-the fact that the \citetalias{ali_et_al2015} analysis averages baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
+the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total}$) neglects 
+the fact that we average baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
 \begin{equation}
@@
 \end{equation}
-\noindent where, in the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
+\noindent where, as with the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
 entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big).
-A revised \citetalias{ali_et_al2015} analysis should therefore use $N_{\rm bls} \sim 32$ instead of $51$, and this change is taken into account in Figure \ref{fig:sense_check}.
-However, the analysis in this paper and in Kolopanis et al.
-(\textit{submitted}) does not average baselines into groups ($N_{\rm gps} = 1$).
-For the subset of data presented in this paper, $N_{\rm bls} = 10$.
+N_{\rm gps}}{2}}$\Big). For the revised PAPER-64 analysis with only one baseline separation type, this becomes $N_{\rm bls} \sim 32$ instead 
+of $51$. 
 \item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
@@
 
-Our revised sensitivity estimate for the \citetalias{ali_et_al2015} analysis of PAPER-64 is shown in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.
+Our revised sensitivity estimate for PAPER-64 is shown in comparison with that of \citetalias{ali_et_al2015} in Figure \ref{fig:sense_check}. 
+Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.
 
@@
 	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray), both computed for the analysis methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
+published sensitivity limits (gray). Both sensitivity analyses plotted assume only one baseline type (an additional factor of $
+\sqrt{3}$ for three baseline types is needed to match \citetalias{ali_et_al2015} exactly). Major factors that contribute to the discrepancy are $
 \Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
-sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
+sensitivity (higher noise floor) by a factor of $\sim5$ in mK$^{2}$.}
 	\label{fig:sense_check}
@@
 Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}, where again the solid red curve is the $2\sigma$ upper limit on the EoR signal after the signal injection framework.
-The solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation
-\eqref{eq:sense}. Both show good agreement with each other, as well as with the various uniform weighted limits (data points and error bars, solid blue line, gray shaded region).
+\ref{fig:ps_noise}, where the black and gray points represent pre-signal loss estimated positive and negative power spectrum values, respectively (with 
+$2\sigma$ error bars and weighting matrix $\widehat{\textbf{C}}_{\rm eff}$), the dashed black line represents the post-signal loss $2\sigma$ upper limit on the EoR signal, the dashed blue line represents the $2\sigma$ uniform-weighted power
+spectrum limit, and the solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation 
+\eqref{eq:sense}. All three show good agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.
 
@@
 	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{The power spectrum for a noise simulation that mimics the noise level of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-All estimates show good agreement.}
+	\caption{Power spectrum estimate for a noise simulation that mimics the noise level of PAPER-64 data. The original weighted 
+power spectrum points and their $2\sigma$ errors are show in black and gray (positive and negative values), where we use $
+\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
+The dashed black line is the $2\sigma$ upper limit on EoR post-signal loss estimation.
+The dashed blue line is the uniform-weighted power spectrum $2\sigma$ upper
+limit. The solid green line is the theoretical $2\sigma$ noise level prediction as calculated by Equation \eqref{eq:sense}. All three 
+estimates show agreement to within a factor of two, which we believe is reasonable given the approximations we make in computing the analytic expression for thermal noise.}
 	\label{fig:ps_noise}
@@
 Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure
+bootstrapping step along time entirely and now simply bootstrap over baselines. Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure 
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to better agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $2$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
-
-In addition to no longer bootstrapping along the time axis, we have made two other changes from the \citetalias{ali_et_al2015} analysis regarding bootstrapping.
-The first is that we now bootstrap over baseline cross-products, instead of baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e.
-the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.
-
-Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the errors (black) are shown to better agree with the analytic prediction for noise.
+We note that they do not match perfectly, but we find good agreement given the approximations we make in computing the thermal noise level.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$$7$ in mK$^{2}$ for the noise simulation, in practice this factor is slightly lower for the case of real data (a factor of $\sim$$5$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+
+Finally, one last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling over the baseline axis (all baselines are used), and this estimate is propagated through our signal loss computation.
 The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.
@@
 We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits better agree with the $2\sigma$ analytic prediction for noise (green).}
+While this does not match perfectly with the $2\sigma$ analytic prediction for noise (green), we find good agreement between them to within a factor of two (which we believe is reasonable given the approximations we make in computing the analytic).}
 	\label{fig:data_errors}
@@
 dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
-the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
+the ``even" dataset and baseline group $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline group $1$, etc. We only form 
 $\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``even" with ``even", for 
 example, in order to prevent the squaring of the same thermal noise.
+We recognize that this method results in a hit to our sensitivity.
+Sensitivity can be gained, for example, by only dividing up the dataset once (either along time or baselines), or by creating more groups (more cross-multiplications), but in this paper we only attempt to revise the \citetalias{ali_et_al2015} analysis (which uses the same groupings).
 
@@
 
-As shown in Figure \ref{fig:ps1_data}, our illustrative PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
+As shown in Figure \ref{fig:ps1_data}, our re-analysis of the PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
 As discussed in Section \ref{sec:BiasTypes}, this bias is
-most likely attributable to foreground leakage. %The cause for biases at higher $k$-values is more difficult to pinpoint.
+most likely attributable to foreground leakage. The cause for biases at higher $k$-values is more difficult to pinpoint.
 
 Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
-that our biases are not attributable to EoR.
+that they are not attributable to EoR.
 Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
@@
 
-The three results are shown in Figure \ref{fig:null}.
-Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the errors of the two dataset halves added in quadrature.
-The expected thermal noise level (gray shaded regions) is the thermal noise of each dataset added in quadrature as well.
-Constructing the tests as such ensures that we are probing whether the variances of each dataset differ by an amount consistent with the thermal noise.
-
-We take jackknives along three different axes:
+The three results are shown in Figure \ref{fig:null}. Each test displays the differenced power spectrum between two halves of a jackknife. We take jackknives along three different axes:
 
@@
 analysis. No baselines are repeated between the two datasets.
-\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.5 hours) and second half (LSTs 
-4.5-8.6 hours).
+\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.6 hours) and second half (LSTs 
+4.6-8.6 hours).
 \item Day: We split our dataset into even and odd Julian dates.
@@
 The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics for $k > \pm 0.2$\,$h$ Mpc$^{-1}$ for all three tests.
-However, we find that all tests exhibit an extra variance at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), likely due to foreground-noise coupling terms when foregrounds are brightest.
-Additionally, we find that the LST null test is not fully consistent with zero, implying a bias that is LST dependent and likely caused by varying foregrounds.}
+We find that there are no significant systematics that differ between the tests, though there are low level biases at high-$k$ values in both the LST test and even/odd test.
+All three tests, whether biased or not, have an extra variance that is strongly $k$-dependent.
+Residual foregrounds dominate at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), which is not surprising given that foregrounds are brightest in this region post-delay filtering.}
 	\label{fig:null}
@@
 
-In investigating Figure \ref{fig:null}, we focus on three main possibilities --- whether the data points and error bars are consistent with thermal noise (``passing"), whether the error bars are consistent with zero but not consistent with thermal noise (``passing but has an additional variance"), or whether the error bars are not consistent with zero at all (``failing").
-We examine each case in the context of our results below.
-
-Firstly, all three null tests display data points that lie within the thermal noise gray band for $k > \pm 0.2$\,$h$ Mpc$^{-1}$.
-In addition, all three null tests show error bars consistent with the thermal noise level for those same $k$'s.
-This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e.
-the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
-We deem these as ``passing" null tests for the specific jackknives taken (again, dividing up the data in a different way along the same axes may not yield the same results, so more thorough testing is needed to be sure).
-
-The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests.
-This indicates an additive noise component that is increasing our errors.
-More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
-This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
-When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
-The cross-terms, however, can introduce extra variance that would vary with foreground strength.
-It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.
-
-Lastly, a third null test result is an error bar not consistent with zero.
-This is the case for the LST null test at $k\sim-0.15$\,$h$ Mpc$^{-1}$ and $k\sim-0.2$\,$h$ Mpc$^{-1}$.
-In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e.
-the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
-This result implies that there exists a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
-Again, it is not surprising that this type of bias occurs near the horizon limit.
-
-%Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
-
-%We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
+In investigating Figure \ref{fig:null}, we focus on two main aspects of each test --- whether the error bars are consistent with zero, and whether they are consistent with thermal noise.
+The former indicates a `passing' null test where there is no bias along the jackknife axis.
+The latter reveals whether there is additional variance present that lies above the thermal noise.
+
+We find that the baselines test is fully consistent with noise, as all error bars pass through zero.
+Therefore, we conclude that the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias.
+We suspect it is the former, though more thorough jackknives along this axis are needed to make this conclusion.
+For the LST test, $90\%$ of all the error bars pass through zero, which is slightly lower than the expected $95\%$.
+This indicates a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
+In other words, the two jackknife halves differ by an amount greater than thermal noise and do not completely cancel out the sky signal when differencing.
+The even/odd test shows $81\%$ of all error bars being consistent with zero, again indicating the presence of a low level bias.
+The cause of this particular systematic is not obvious, and requires further investigation that we do not carry out in this paper.
+Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
+
+Finally, we note that all three null tests exhibit error bars that are strongly $k$-dependent.
+The errors are largest just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) which is expected since foregrounds are brightest in this region post-delay filtering.
+We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
 This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
 
-%There are a couple possible explanations for this.
+There are a couple possible explanations for this.
 Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
@@
 In this section we have presented the first jackknife and null tests from the PAPER experiment.
-Unsurprisingly, they imply that our measurements are biased by foregrounds, and not the EoR signal (a clean detection of EoR would have passed all three tests).
-While simple, these tests outline a framework that can be used by future measurements.
-The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough investigations of this nature.
+While simple, they outline a framework that can be used in the future.
+The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough tests.
 
@@
 
-As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, accurately estimating thermal noise, and implementing jackknife tests.
-Our revised PAPER-64 limits are presented in Kolopanis et al.
-(\textit{submitted}), which supersede all previously published PAPER limits.
-The main reasons for a previously under-estimated limit and
+As a consequence of our investigations, we have also revised power spectrum results from PAPER-64.
+In Kolopanis et al.
+(\textit{submitted}), we quote a best $2\sigma$ power spectrum upper limit of $(240.0$ mK$)^{2}$ at $k=0.3$\,$h$ Mpc$^{-1}$ and $z=8.37$,
+a higher limit than \citetalias{ali_et_al2015} by a factor of $\sim$$10$ in mK. The reasons for a previously under-estimated limit and 
 ways in which our new analysis differs can be summarized by the following:
@@
 \item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for empirically estimated inverse 
-covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
-\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim10$ in mK higher than the lossy empirical inverse covariance limits. Under-estimated signal loss therefore represents the bulk of our revision. 
+covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section 
+\ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a 
+factor of $\sim10$ in mK higher than previous limits. Under-estimated signal loss therefore represents the bulk of our revision. 
 This revision is similar to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
@@
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our overall
+decrease in predicted sensitivity level by a factor of $\sim2$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our 
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
@@
 % APPENDIX ---------------------------------------------------------------------------------
+
+\color{blue}
+
+\appendix
+\section{A toy model for inverse covariance weighting}
+\label{sec:icw_appendix}
+
+We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
+We have specifically chosen a toy model where the data covariance is diagonal, as we expect the EoR signal to be.
+We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\phi_i$
+\begin{equation}
+\Delta_i = \sigma_i + \phi_i
+\end{equation}
+with 
+\begin{equation}
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
+\end{equation}
+and we wish to estimate $s$.  The contaminant in this case has a similar structure for its covariance, and is assumed uncorrelated with the signal
+\begin{equation}
+\langle \phi_i \rangle = 0; \; 
+\langle \phi^2_i \rangle = f; \; 
+\langle \phi \phi^T \rangle = f I_{N \times N} \equiv F; {\rm and}~ 
+\langle \sigma_i \phi_j \rangle = 0
+\end{equation}
+%That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
+The estimator for $s$ using the inverse covariance weighting prescription is
+\begin{equation}
+\label{eq:CaseOneICW}
+\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) 
+= \frac{\Delta^T \Delta}{N}
+\end{equation}
+%and plugging in the relevant quantities gives
+%\begin{eqnarray}
+%\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
+%& = & \frac{\Delta^T \Delta}{N}
+%\end{eqnarray}
+We note that
+\begin{equation}
+\langle \hat{s} \rangle = s + g
+\end{equation}
+In this case, the quadratic estimator returns an entirely reasonable result, but, 
+{\it since the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
+
+Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
+\begin{equation}
+\Delta_i = \sigma_i + \phi m_i
+\end{equation}
+where the properties of $\sigma_i$ are as before,
+%\begin{eqnarray}
+%\langle \sigma_i \rangle & = & 0 \\
+%\langle \sigma^2_i \rangle & = & s \\
+% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
+%\end{eqnarray}
+but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
+\begin{equation}
+\langle \phi \rangle = 0; \;
+\langle \phi^2 \rangle = f; \; 
+ \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
+ m^T m = 1
+\end{equation}
+Here $m$ represents a mode which is correlated across many data points, with amplitude given by  $\phi$.
+
+Here we can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+\begin{equation}
+\xi \equiv \frac{f/s}{1+f/s}
+\end{equation} 
+we have
+\begin{equation}
+\invC %& = & \frac{1}{s} I - \frac{g}{1+g/s} \frac{1}{s^2} m m^T \\
+=   \frac{1}{s} \left(I - \xi m m^T \right)
+\end{equation}
+and the virtue of weighting by $\invC$ becomes clearer: in the limit $f \gg s$, $\xi \to 1$, and this becomes
+\begin{equation}
+\invC  = \frac{1}{s} \left(I - m m^T \right)
+\end{equation}
+where $I - m m^T$ is the projection operator, projecting out $m$ from any any vector it acts on.   Proceeding to calculate the full estimator
+\begin{equation}
+\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) = \frac{ \Delta^T  (I -  (\eta^2 - 2 \eta)  m m^T)  \Delta}{N + \eta^2 - 2 \eta} 
+\end{equation}
+we note that the expectation is
+\begin{equation}
+\langle \hat{s} = 
+\end{equation}
+
+\color{black}
 

### 2018-05-10 PAPER.tex
listed bootstrapping changes in bullet-point form; added some text in the jackknife section about the cross-term not averaging down

--- 2018-05-03 PAPER.tex
@@
 We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-one major change in the way we estimate errors since \citetalias{ali_et_al2015}, using the lesson we have learned about bootstrapping independent samples.
-
-As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
+four specific changes in the way we estimate errors since \citetalias{ali_et_al2015}, the first of which builds off of the lesson we have learned previously about bootstrapping independent samples.
+
+\begin{itemize}
+
+\item{As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
 of independent samples, or the number of independent samples is well known. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
@@
 While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $2$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
-
-In addition to no longer bootstrapping along the time axis, we have made two other changes from the \citetalias{ali_et_al2015} analysis regarding bootstrapping.
-The first is that we now bootstrap over baseline cross-products, instead of baselines themselves.
+}%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
+
+\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of baselines themselves.
 In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
@@
 the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.
-
-Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
+This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
+
+\item{In \citetalias{ali_et_al2015}, individual baselines were divided into $5$ independent groups, where no baselines were repeated in each group.
+Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
+This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
+Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
+
+\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
 More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
+
+\end{itemize}
 
@@
 When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
-The cross-terms, however, can introduce extra variance that would vary with foreground strength.
+While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples).
+Combined with the fact that the foregrounds are so bright, these couplings can introduce extra variance that would vary with foreground strength.
 It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.

### 2018-05-11 PAPER.tex
minor syntax edit

@@
 While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples).
-Combined with the fact that the foregrounds are so bright, these couplings can introduce extra variance that would vary with foreground strength.
+Combined with the fact that the foregrounds are so bright, the finite ensemble of the couplings can introduce extra variance that varies with foreground strength.
 It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.

### 2018-05-16 PAPER.tex
added phil to acknowledgements
Tue May 15 22:39:37 EDT 2018

--- 2018-05-08 PAPER.tex
@@
 \usepackage{comment}
+\usepackage{bm}
 %\usepackage{mathtools}
@@
 
-\newcommand{\invC}{\ensuremath{C^{-1}}}
-\newcommand{\dC}[1]{\ensuremath{C_{,#1}}}
+\newcommand{\invC}{\ensuremath{\C^{-1}}}
+\newcommand{\dC}[1]{\ensuremath{\C_{,#1}}}
 \DeclareMathOperator{\Tr}{Tr}
@@
 We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
-We have specifically chosen a toy model where the data covariance is diagonal, as we expect the EoR signal to be.
-We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and some contaminant $\phi_i$
-\begin{equation}
-\Delta_i = \sigma_i + \phi_i
+We have specifically chosen a toy model where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
+\begin{equation}
+\Delta_i = \sigma_i + \upsilon_i
 \end{equation}
@@
 \begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \sigma \sigma^T \rangle = s I_{N \times N} \equiv S
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S}
 \end{equation}
@@
 \begin{equation}
-\langle \phi_i \rangle = 0; \; 
-\langle \phi^2_i \rangle = f; \; 
-\langle \phi \phi^T \rangle = f I_{N \times N} \equiv F; {\rm and}~ 
-\langle \sigma_i \phi_j \rangle = 0
-\end{equation}
-%That is, we have the sum of $N$ independent samples of two random variables and we wish to estimate the variance of one of the random variables in the sum; in this case, $s$.
-The estimator for $s$ using the inverse covariance weighting prescription is
+\langle \upsilon_i \rangle = 0; \; 
+\langle \upsilon^2_i \rangle = u; \; 
+\langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{I}_{N \times N} \equiv \mathbf{U}; {\rm and}~ 
+\langle \sigma_i \upsilon_j \rangle = 0
+\end{equation}
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using the optimal quadratic estimator prescription is
 \begin{equation}
 \label{eq:CaseOneICW}
-\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) 
-= \frac{\Delta^T \Delta}{N}
-\end{equation}
-%and plugging in the relevant quantities gives
-%\begin{eqnarray}
-%\hat{s} & = & \half \frac{2}{N} (s+g)^2 \left( \Delta^T \frac{1}{s+g} I \frac{1}{s+g} \Delta \right) \\
-%& = & \frac{\Delta^T \Delta}{N}
-%\end{eqnarray}
+\hat{s} = \half {\F}^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{s}  \invC \bm{\Delta} \right) 
+= \frac{\bm{\Delta^T \Delta}}{N}
+\end{equation}
 We note that
 \begin{equation}
-\langle \hat{s} \rangle = s + g
-\end{equation}
-In this case, the quadratic estimator returns an entirely reasonable result, but, 
-{\it since the covariance structure of the contaminant is identical to the signal}, it is only possible to achieve an unbiased estimate by using some additional information to estimate the additive bias and subtract it.
-
-Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data have an additive contaminant given by
-\begin{equation}
-\Delta_i = \sigma_i + \phi m_i
-\end{equation}
-where the properties of $\sigma_i$ are as before,
-%\begin{eqnarray}
-%\langle \sigma_i \rangle & = & 0 \\
-%\langle \sigma^2_i \rangle & = & s \\
-% \langle \sigma \sigma^T \rangle & = & s I_{N \times N} \equiv S
-%\end{eqnarray}
-but now $\phi$ is a random variable and $m_i$ is a fixed function of $i$ with
-\begin{equation}
-\langle \phi \rangle = 0; \;
-\langle \phi^2 \rangle = f; \; 
- \langle \phi \phi^T \rangle = f m m^T \equiv F; \;
- m^T m = 1
-\end{equation}
-Here $m$ represents a mode which is correlated across many data points, with amplitude given by  $\phi$.
-
-Here we can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
-\begin{equation}
-\xi \equiv \frac{f/s}{1+f/s}
+\langle \hat{s} \rangle = s + u
+\end{equation}
+In this case, the quadratic estimator returns an entirely reasonable result, but, since 
+$\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, that is, {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
+
+Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data again have an additive contaminant, now given by
+\begin{equation}
+\Delta_i = \sigma_i + \upsilon m_i
+\end{equation}
+where the properties of $\sigma_i$ are as before, but now $\upsilon$ is a random variable and $m_i$ is a fixed function of $i$ with
+\begin{equation}
+\langle \upsilon \rangle = 0; \;
+\langle \upsilon^2 \rangle = u; \; 
+ \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{m m}^T \equiv \mathbf{U}; \;
+ \mathbf{m}^T \mathbf{m} = N; \; {\rm and}~ 
+\langle \sigma_i \upsilon \rangle = 0
+\end{equation}
+Here $\mathbf{m}$ represents a mode which is correlated across many data points, with amplitude given by  $\upsilon$.
+
+We can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+\begin{equation}
+\xi \equiv \frac{u/s}{1+u/s}
 \end{equation} 
@@
 \begin{equation}
-\invC %& = & \frac{1}{s} I - \frac{g}{1+g/s} \frac{1}{s^2} m m^T \\
-=   \frac{1}{s} \left(I - \xi m m^T \right)
-\end{equation}
-and the virtue of weighting by $\invC$ becomes clearer: in the limit $f \gg s$, $\xi \to 1$, and this becomes
-\begin{equation}
-\invC  = \frac{1}{s} \left(I - m m^T \right)
-\end{equation}
-where $I - m m^T$ is the projection operator, projecting out $m$ from any any vector it acts on.   Proceeding to calculate the full estimator
-\begin{equation}
-\hat{s} = \half {\cal F}^{-1} \left( \Delta^T \invC \PDeriv{C}{s}  \invC \Delta \right) = \frac{ \Delta^T  (I -  (\eta^2 - 2 \eta)  m m^T)  \Delta}{N + \eta^2 - 2 \eta} 
+\invC  =   \frac{1}{s} \left(\I - \xi \mathbf{m m}^T \right)
+\end{equation}
+and the virtue of weighting by $\invC$ becomes clearer: in the limit $u \gg s$, $\xi \to 1$, and this becomes
+\begin{equation}
+\invC  = \frac{1}{s} \left(\I - \mathbf{m m}^T \right)
+\end{equation}
+where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any any vector it acts on.   Proceeding to calculate the full estimator
+\begin{equation}
+\hat{s} = \half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = \frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
 \end{equation}
@@
 \begin{equation}
-\langle \hat{s} = 
+\langle \hat{s} \rangle = \frac{ N(s + u + (\xi^2 - 2 \xi) 
+[u + \langle(\bm{\sigma} \cdot \mathbf{m})^2 \rangle])} 
+{N + \xi^2 - 2 \xi} 
+\end{equation}
+This again has a simple interpretation in the limit $\xi \to 1$, where
+\begin{equation}
+\langle \hat{s} \rangle = \frac{ s - \langle(\bm{\sigma} \cdot \mathbf{m})^2\rangle} {N -1} 
 \end{equation}

### 2018-05-16 PAPER_JA_edits.tex
Wed May 16 10:08:39 EDT 2018

--- 2018-05-16 PAPER.tex
@@
 \end{equation}
-we note that the expectation is
+The expectation is
 \begin{equation}
@@
 \begin{equation}
-\langle \hat{s} \rangle = \frac{ s - \langle(\bm{\sigma} \cdot \mathbf{m})^2\rangle} {N -1} 
-\end{equation}
+\langle \hat{s} \rangle = \frac{N}{N -1}  (s - \langle(\bm{\sigma} \cdot \mathbf{m})^2\rangle )
+\end{equation}
+Thus, in the limit the contaminant is large compared to $s$, and to the extent that $\bm \sigma \cdot \mathbf{m} \approx 0$, this yields a nearly unbiased estimator for $s$ and the inverse covariance weighting has completely removed the effect of the contaminant.
 

### 2018-05-16 PAPER.tex
Wed May 16 10:36:46 EDT 2018
Wed May 16 10:42:29 EDT 2018

--- 2018-05-11 PAPER.tex
@@
 \newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors
+
+% Math shortcuts from James
+\newcommand{\invC}{\ensuremath{\C^{-1}}}
+\newcommand{\dC}[1]{\ensuremath{\C_{,#1}}}
+\DeclareMathOperator{\Tr}{Tr}
+\newcommand{\half}{\ensuremath{\frac{1}{2}}}
+\newcommand{\PDeriv}[2]{\ensuremath{\frac{\partial #1}{\partial #2}}}
 
@@
 CC would like to acknowledge the UC Berkeley Chancellor's Fellowship and National Science Foundation Graduate Research 
-Fellowship (Division of Graduate Education award 1106400). She would also like to thank Eric Switzer, Miguel Morales, and Bryna Hazelton for helpful discussions. PAPER and HERA 
+Fellowship (Division of Graduate Education award 1106400). She would also like to thank Phil Bull, Bryna Hazelton, Miguel Morales, and Eric Switzer for helpful discussions. PAPER and HERA 
 are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
@@
 % APPENDIX ---------------------------------------------------------------------------------
+
+\color{blue}
+
+\appendix
+\section{A toy model for inverse covariance weighting}
+\label{sec:icw_appendix}
+
+We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
+We have specifically chosen a toy model where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
+\begin{equation}
+\Delta_i = \sigma_i + \upsilon_i
+\end{equation}
+with 
+\begin{equation}
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S}
+\end{equation}
+and we wish to estimate $s$.  The contaminant in this case has a similar structure for its covariance, and is assumed uncorrelated with the signal
+\begin{equation}
+\langle \upsilon_i \rangle = 0; \; 
+\langle \upsilon^2_i \rangle = u; \; 
+\langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{I}_{N \times N} \equiv \mathbf{U}; {\rm and}~ 
+\langle \sigma_i \upsilon_j \rangle = 0
+\end{equation}
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using the optimal quadratic estimator prescription is
+\begin{equation}
+\label{eq:CaseOneICW}
+\hat{s} = \half {\F}^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{s}  \invC \bm{\Delta} \right) 
+= \frac{\bm{\Delta^T \Delta}}{N}
+\end{equation}
+We note that
+\begin{equation}
+\langle \hat{s} \rangle = s + u
+\end{equation}
+In this case, the quadratic estimator returns an entirely reasonable result, but, since 
+$\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, that is, {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
+
+Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data again have an additive contaminant, now given by
+\begin{equation}
+\Delta_i = \sigma_i + \upsilon m_i
+\end{equation}
+where the properties of $\sigma_i$ are as before, but now $\upsilon$ is a random variable and $m_i$ is a fixed function of $i$ with
+\begin{equation}
+\langle \upsilon \rangle = 0; \;
+\langle \upsilon^2 \rangle = u; \; 
+ \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{m m}^T \equiv \mathbf{U}; \;
+ \mathbf{m}^T \mathbf{m} = N; \; {\rm and}~ 
+\langle \sigma_i \upsilon \rangle = 0
+\end{equation}
+Here $\mathbf{m}$ represents a mode which is correlated across many data points, with amplitude given by  $\upsilon$.
+
+We can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+\begin{equation}
+\xi \equiv \frac{u/s}{1+u/s}
+\end{equation} 
+we have
+\begin{equation}
+\invC  =   \frac{1}{s} \left(\I - \xi \mathbf{m m}^T \right)
+\end{equation}
+and the virtue of weighting by $\invC$ becomes clearer: in the limit $u \gg s$, $\xi \to 1$, and this becomes
+\begin{equation}
+\invC  = \frac{1}{s} \left(\I - \mathbf{m m}^T \right)
+\end{equation}
+where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any any vector it acts on.   Proceeding to calculate the full estimator
+\begin{equation}
+\hat{s} = \half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = \frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
+\end{equation}
+The expectation is
+\begin{equation}
+\langle \hat{s} \rangle = \frac{ N(s + u + (\xi^2 - 2 \xi) 
+[u + \langle(\bm{\sigma} \cdot \mathbf{m})^2 \rangle])} 
+{N + \xi^2 - 2 \xi} 
+\end{equation}
+This again has a simple interpretation in the limit $\xi \to 1$, where
+\begin{equation}
+\langle \hat{s} \rangle = \frac{N}{N -1}  (s - \langle(\bm{\sigma} \cdot \mathbf{m})^2\rangle )
+\end{equation}
+Thus, in the limit the contaminant is large compared to $s$, and to the extent that $\bm \sigma \cdot \mathbf{m} \approx 0$, this yields a nearly unbiased estimator for $s$ and the inverse covariance weighting has completely removed the effect of the contaminant.
+
+\color{black}
 

### 2018-05-16 PAPER.tex
Wed May 16 16:17:44 EDT 2018

@@
 
-We illustrate the way in which the quadratic estimator, Equation \ref{eq:QuadraticEstimator}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering the simpler, but similar, case of estimating the variance of data.
+%AAAXXX
+
+We illustrate the way in which the quadratic estimator, Equations \ref{eq:qhat} and \ref{eq:phat}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
 We have specifically chosen a toy model where the data covariance is diagonal, as indeed we expect the EoR signal to be.
@@
 \begin{equation}
-\label{eq:CaseOneICW}
+\label{eq:ICWFormula}
 \hat{s} = \half {\F}^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{s}  \invC \bm{\Delta} \right) 
-= \frac{\bm{\Delta^T \Delta}}{N}
-\end{equation}
-We note that
-\begin{equation}
-\langle \hat{s} \rangle = s + u
+\end{equation}
+In this case, the estimator becomes
+\begin{equation}
+\langle \hat{s} \rangle = \frac{\langle \bm{\Delta^T \Delta} \rangle}{N} = s + u
 \end{equation}
@@
 
-Now consider a case, chosen to be very similar to the toy model in \ref{sec:},  in which the data again have an additive contaminant, now given by
+Now consider a case, chosen to be very similar to the toy model in \ref{sec:toymodel},  in which the data again have an additive contaminant, now given by
 \begin{equation}
@@
 
-We can again calculate the estimator given by \ref{eq:} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+We can again calculate the estimator given by \ref{eq:ICWFormula} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
 \begin{equation}
@@
 Thus, in the limit the contaminant is large compared to $s$, and to the extent that $\bm \sigma \cdot \mathbf{m} \approx 0$, this yields a nearly unbiased estimator for $s$ and the inverse covariance weighting has completely removed the effect of the contaminant.
+This is indeed the desired behavior of the inverse covariance weighting, where removal of contamination with a known covariance can be suppressed by projection of the offending modes.
+But even in this case, it is worth pointing out that estimator is still not unbiased in general, having both the effect of leaving in some contaminated mode for finite $\xi$ and also in the limit of some correlation between the signal and contaminant, or of mis-estimation of the contaminating mode $\mathbf{m}$.
 

### 2018-05-18 PAPER.tex
-Added Appendix C: Jeffreys Prior Derivation and Plots -Re-compiled all new PS plots using sigloss v9, which uses jeffreys prior -Added text explaining the additional sample variance that arises from the injection framework

@@
 Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and smooth the distribution of $\widehat{P}_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}) for each bin (and normalize them).
-Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
+We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and, assuming we are accurately sampling a Gaussian distribution, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
+Stitching all of them together results in a 2-dimensional transfer function --- the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
+We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
+For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
+
+Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
+Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior.
 Although we only show figures for one $k$-value, we note that
 the shape of the transfer curve is similar for all $k$'s.
-This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
 We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$) and assume a uniform prior to yield a posterior distribution for the signal.
+To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
 We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
@@
 In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs when
-only the $\sim2$ highest-valued eigenmodes are down-weighted and the rest are given equal weights.
+We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
+only the $\sim2$-$3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting does not actually outperform uniform weighting).
 For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
@@
 as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.035 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.035$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
+In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.9 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.9$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 their best (i.e.
-when $\sim2$ eigenmodes are down-weighted in the case of the solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.035 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.035$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
+when $\sim2$-$3$ eigenmodes are down-weighted in the case of the solid red curve).
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.9 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.9$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
 We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
 We also note that all of the regularizations described here perform similarly to the uniformly weighted case.
-However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshift bins in which there are stronger foregrounds, as presented in Kolopanis et al.
+However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshifts (and $k$-values) for which there are stronger foregrounds, as presented in Kolopanis et al.
 (\textit{submitted}).
@@
 $2\sigma$ errors bars).
-It is also shown as an upper limit using the signal injection framework (solid blue).
+It is also shown as an upper limit using the signal injection framework (solid blue), which is interestingly larger than the errors computed from bootstrapping, likely because the full injection framework takes into account additional sample variance whereas the bootstrapped errors do not.
 Finally, the gray shaded regions combine the measured uniform weighted power spectrum values and the thermal noise.
@@
 Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}, where again the solid red curve is the $2\sigma$ upper limit on the EoR signal after the signal injection framework.
-The solid green line denotes our $2\sigma$ theoretical noise prediction as calculated by Equation
-\eqref{eq:sense}. Both show good agreement with each other, as well as with the various uniform weighted limits (data points and error bars, solid blue line, gray shaded region).
+\ref{fig:ps_noise}.
+We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance.
+However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
 
@@
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-All estimates show good agreement.}
+We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
 	\label{fig:ps_noise}
@@
 bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors with this bootstrapping change for fringe-rate filtered noise are shown in Figure
+Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for fringe-rate filtered noise are shown in Figure
 \ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
@@
 	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping 
+	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
 methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
@@
 The three results are shown in Figure \ref{fig:null}.
-Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the errors of the two dataset halves added in quadrature.
+Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the bootstrapped errors of the two dataset halves added in quadrature.
 The expected thermal noise level (gray shaded regions) is the thermal noise of each dataset added in quadrature as well.
 Constructing the tests as such ensures that we are probing whether the variances of each dataset differ by an amount consistent with the thermal noise.
+We use uniform weightings for all tests.
 
@@
 	\includegraphics[width=0.47\textwidth]{plots/null_eo.pdf}
-	\caption{Differenced power spectrum results (with $2\sigma$ errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
+	\caption{Differenced power spectrum results (with $2\sigma$ bootstrapped errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
 The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra produced on either side of the jackknife axis.
@@
 
-We illustrate the way in which the quadratic estimator, Equations \ref{eq:qhat} and \ref{eq:phat}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
+We illustrate the way in which the quadratic estimator, Equations \eqref{eq:qhat} and \eqref{eq:phat}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
 We have specifically chosen a toy model where the data covariance is diagonal, as indeed we expect the EoR signal to be.
@@
 
-We can again calculate the estimator given by \ref{eq:ICWFormula} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+We can again calculate the estimator given by \eqref{eq:ICWFormula} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
 \begin{equation}
@@
 
-\appendix
+%\appendix
 \section{A toy model for signal loss}
@@
 
+\section{Derivation of the Jeffreys Prior}
+\label{sec:jeffreys}
+
+The Jeffreys prior is an objective, non-informative prior distribution for a parameter space using Bayesian probability (\citealt{jaynes1968}).
+For the signal injection framework outlined in Section \ref{sec:Practice}, we wish to compute the prior $p(P_{\rm in})$, or the probability density of the power spectrum of the EoR signal.
+
+The Jeffreys prior is defined as:
+
+\begin{equation}
+\label{eq:jeffreys}
+p(P_{\rm in}) \propto \sqrt {\Bigg\langle \Bigg(\frac{\partial \mathcal{L}}{\partial P_{\rm in}} \Bigg)^{2}\Bigg\rangle},
+\end{equation}
+
+\noindent where
+
+\begin{equation}
+\label{eq:logprob}
+\mathcal{L} = log \, p(\widehat{P}_{\rm out} | P_{\rm in}),
+\end{equation}
+
+\noindent recalling that in our framework $P_{\rm in}$ is the power spectrum of the EoR signal (uniformly weighted), and $\widehat{P}_{\rm out}$ is the weighted output power spectrum of the data plus EoR.
+
+For a single injection amplitude, our bootstrapped $\widehat{P}_{\rm out}$ values sample a Gaussian distribution. Simplifying our notation so that $x = P_{\rm in}$ and $y = \widehat{P}_{\rm out}$:
+
+\begin{equation}
+\label{eq:prob}
+p(y | x) = \frac{1}{\sigma(x) \sqrt{2\pi}} e^{-\frac{1}{2}\big(\frac{y-\bar y(x)}{\sigma}\big)^{2}},
+\end{equation}
+
+\noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
+Plugging in Equation \eqref{eq:prob} into Equation \eqref{eq:logprob} becomes:
+
+\begin{equation}
+\label{eq:logprob_full}
+\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
+\end{equation}
+
+Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
+
+\begin{eqnarray}
+\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
+&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
+\end{eqnarray}
+
+Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to 0.
+Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
+Finally, after some additional simplification the Jeffreys prior becomes:
+
+\begin{equation}
+\label{eq:jeffreys_final}
+p(x) \propto \sqrt{ \frac{1}{\sigma^{2}}\Big(2\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} + \Big(\frac{\partial \bar y}{\partial x}\Big)^{2}\Big) }.
+\end{equation}
+
+When we simulate our full injection framework as in Section \ref{sec:Practice}, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
+An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though we note in practice we fit solutions for every $k$-value and simulation independently.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
+	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
+Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.}
+	\label{fig:jeffreys1}
+\end{figure}
+
+We also show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
+Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often assumed to be an uninformative prior, is actually informative.
+Therefore, due to its objective nature we choose to use a Jeffreys prior in our analysis, multiplying our likelihood functions by Equation \eqref{eq:jeffreys_final} before computing posterior distributions.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=10cm]{plots/jeffrey_prior.pdf}
+	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis. Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
+	\label{fig:jeffreys2}
+\end{figure}
+
+%------------------------------- commented below---------------------------------------
 \begin{comment}

### 2018-05-18 PAPER.tex
added text saying we normalize the final posterior
edited caption to fig 18

@@
 To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
-We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.
+We normalize this final distribution and compute the $95\%$ confidence interval (an upper limit on EoR).
 
@@
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
-Kernel density estimations of the power spectrum transfer functions are shown as colored
-heat-maps on top of the points for the cases of empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
+Assuming our $\widehat{P}_{\rm out}$ values sample a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
+This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored
+heat-maps on top of the points. Two cases are displayed: empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
 diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.

### 2018-05-21 PAPER.tex
edited jeffreys prior appendix according to Adrian edits

@@
 Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level), and, assuming we are accurately sampling a Gaussian distribution, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
+We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level) and, since they are well-approximated by a Gaussian distribution in our numerical results, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
 Stitching all of them together results in a 2-dimensional transfer function --- the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
@@
 Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
-Assuming our $\widehat{P}_{\rm out}$ values sample a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
+Since our $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
 This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored
@@
 \label{eq:logprob}
-\mathcal{L} = log \, p(\widehat{P}_{\rm out} | P_{\rm in}),
+\mathcal{L} = \mathrm{ln} \, p(\widehat{P}_{\rm out} | P_{\rm in}),
 \end{equation}
@@
 
-For a single injection amplitude, our bootstrapped $\widehat{P}_{\rm out}$ values sample a Gaussian distribution. Simplifying our notation so that $x = P_{\rm in}$ and $y = \widehat{P}_{\rm out}$:
+For a single injection amplitude, our bootstrapped $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution.
+Simplifying our notation so that $x = P_{\rm in}$ and $y = \widehat{P}_{\rm out}$:
 
@@
 \noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Plugging in Equation \eqref{eq:prob} into Equation \eqref{eq:logprob} becomes:
-
-\begin{equation}
-\label{eq:logprob_full}
-\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
-\end{equation}
-
-Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
+Using Equations \eqref{eq:prob} and \eqref{eq:logprob}, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} becomes:
+
+%\begin{equation}
+%\label{eq:logprob_full}
+%\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
+%\end{equation}
+
+%Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of %Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
 
@@
 
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
+When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, so we note that the prior is set to zero outside those regions.
+For the injections that we do sample, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
 An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though we note in practice we fit solutions for every $k$-value and simulation independently.
@@
 	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
-Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.}
+Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
+The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
 	\label{fig:jeffreys1}
@@
 We also show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
-Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often assumed to be an uninformative prior, is actually informative.
+Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.
 Therefore, due to its objective nature we choose to use a Jeffreys prior in our analysis, multiplying our likelihood functions by Equation \eqref{eq:jeffreys_final} before computing posterior distributions.
@@
 	\includegraphics[width=10cm]{plots/jeffrey_prior.pdf}
-	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis. Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
+	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final}.
+Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
 	\label{fig:jeffreys2}

### 2018-05-21 PAPER.tex
jeffrey prior plot with boxcar avg

@@
 
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, so we note that the prior is set to zero outside those regions.
+When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
 For the injections that we do sample, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
@@
 	\includegraphics[width=10cm]{plots/jeffrey_prior.pdf}
-	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final}.
-Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
+	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final} (black).
+We smooth the prior using a sliding boxcar average for every $5$ injections (red).
+Most noticeably, the Jeffreys prior is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
 	\label{fig:jeffreys2}

### 2018-06-04 PAPER.tex
Mon Jun  4 09:25:47 EDT 2018

@@
 \end{equation}
-In this case, the estimator becomes
+where $\F$ is the Fisher matrix.  
+The expectation of the estimator is then
 \begin{equation}
@@
 \end{equation}
-In this case, the quadratic estimator returns an entirely reasonable result, but, since 
+In this case, the quadratic estimator returns an entirely reasonable result, but, since the 
 $\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, that is, {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.

### 2018-06-04 PAPER.tex
Mon Jun  4 09:33:32 EDT 2018

@@
 \end{equation}
-In this case, the quadratic estimator returns an entirely reasonable result, but, since the 
-$\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, that is, {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
+In this case, the quadratic estimator returns an entirely reasonable result, but, since the covariance of the undesired signal has the same form as the desired signal, that is,
+$\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, we find that when {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
+In fact, if one uses the standard formula \citep[e.g.][, Equation 6]{dillon14} for the additive bias
+\begin{equation}
+b = \half \F^{-1} \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{s} \invC \right]
+\end{equation}
+one indeed finds $b = g$.
 

### 2018-06-04 PAPER.tex
Mon Jun  4 10:09:27 EDT 2018

@@
 \end{equation}
-one indeed finds $b = g$.
+one indeed finds $b = u$.
 
@@
  \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{m m}^T \equiv \mathbf{U}; \;
- \mathbf{m}^T \mathbf{m} = N; \; {\rm and}~ 
+ \mathbf{m}^T \mathbf{m} = 1; \; {\rm and}~ 
 \langle \sigma_i \upsilon \rangle = 0
 \end{equation}
-Here $\mathbf{m}$ represents a mode which is correlated across many data points, with amplitude given by  $\upsilon$.
+Here $\mathbf{m}$ represents a mode which is correlated across many data points (i.e., we are assuming $\mathbf{U}$ need {\it not} be diagonal), with amplitude given by  $\upsilon$.
+The normalization of $\mathbf{m}$ is a matter of convention, and can be absorbed in the variance $u$; the choice above will be convenient for understanding the limiting case $u \gg s$.
 
@@
 \end{equation}
-and the virtue of weighting by $\invC$ becomes clearer: in the limit $u \gg s$, $\xi \to 1$, and this becomes
+Proceeding to calculate the full estimator
+\begin{equation}
+\hat{s} = \half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = \frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
+\end{equation}
+The expectation is
+\begin{equation}
+\langle \hat{s} \rangle = 
+s + \frac{1 - 2 \xi + \xi^2}{N + - 2 \xi + \xi^2} u 
+\end{equation}
+It is worth observing immediately that there is no multiplicative bias on $s$, and that the additive bias is strictly $< u/N$.
+
+An instructive limit is $u \gg s$, $\xi \to 1$, in which case the the virtue of weighting by $\invC$ becomes clearer: it becomes
 \begin{equation}
@@
 \end{equation}
-where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any any vector it acts on.   Proceeding to calculate the full estimator
-\begin{equation}
-\hat{s} = \half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = \frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
-\end{equation}
-The expectation is
-\begin{equation}
-\langle \hat{s} \rangle = \frac{ N(s + u + (\xi^2 - 2 \xi) 
-[u + \langle(\bm{\sigma} \cdot \mathbf{m})^2 \rangle])} 
-{N + \xi^2 - 2 \xi} 
-\end{equation}
-This again has a simple interpretation in the limit $\xi \to 1$, where
-\begin{equation}
-\langle \hat{s} \rangle = \frac{N}{N -1}  (s - \langle(\bm{\sigma} \cdot \mathbf{m})^2\rangle )
-\end{equation}
-Thus, in the limit the contaminant is large compared to $s$, and to the extent that $\bm \sigma \cdot \mathbf{m} \approx 0$, this yields a nearly unbiased estimator for $s$ and the inverse covariance weighting has completely removed the effect of the contaminant.
-This is indeed the desired behavior of the inverse covariance weighting, where removal of contamination with a known covariance can be suppressed by projection of the offending modes.
-But even in this case, it is worth pointing out that estimator is still not unbiased in general, having both the effect of leaving in some contaminated mode for finite $\xi$ and also in the limit of some correlation between the signal and contaminant, or of mis-estimation of the contaminating mode $\mathbf{m}$.
+where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any any vector it acts on, and further, the linear bias tends to 0 as $\xi \to 1$, i.e., the projection is ``perfect'' and not ``undone'' by the Fisher matrix normalization.
+
+This is indeed the desired behavior of the inverse covariance weighting, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
+But even in this case, it is worth pointing out that estimator still has a linear bias for finite $u$.
+We also assume that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
 

### 2018-06-04 PAPER.tex
Mon Jun  4 11:03:46 EDT 2018

@@
 
+We find the following things:
+\begin{itemize}
+
+\item If the covariance of residual foreground contamination were known perfectly, and its covariance structure is sufficiently different from the EoR signal, then we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
+to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
+If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
+We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
+That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
+
+\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
+
+\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which in general is strongly biased {\it low} relative to the true value.
+In this context, this is what we call ``signal loss.''
+
+\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced.
+
+\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
+Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable.
+
+% JEA - I really struggle with whether this is intuitively reasonable ...
+it's hard to get a sense of what "noise" is averaging down slower.
+All modes have the same number of samples going into the estimate.
+But the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
+% Also, have we shown this sufficiently rigorously?
+Is the toy model sufficiently general?
+(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
+Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
+
+\end{itemize}
+
 \color{black}

### 2018-06-04 PAPER.tex
Mon Jun  4 11:30:08 EDT 2018

@@
 
-\begin{center}
-Power Spectrum Themes
-\end{center}
-
-A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power 
-spectrum result. Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for 
-a rigorous power spectrum analysis.
+%\begin{center}
+%Power Spectrum Themes
+%\end{center}
+
+%A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power spectrum result.
+Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for a rigorous power spectrum analysis.
 \begin{itemize}
@@
 
-\begin{center}
-Power Spectrum Techniques
-\end{center}
+%\begin{center}
+%Power Spectrum Techniques
+%\end{center}
 
@@
 % SECTION 2 SIGLOSS ---------------------------------------------------------------------------------
+\color{blue}
 
@@
 
-Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during 
-spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
-applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was 
-previously underestimated in the \citetalias{ali_et_al2015} analysis.
-
-Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight 
-foregrounds. This weighting is applied to data, which is then propagated into a final estimator using the power spectrum 
-estimation technique of quadratic estimators (QE) as done in \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
+Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself.
+Here we focus on signal loss associated with
+% we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
+the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
+This loss was significantly 
+%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
+underestimated in the \citetalias{ali_et_al2015} analysis.
+
+% Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
+
+\subsubsection{The Quadratic Estimator Method}
+
+The goal of the power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
+Prior to power spectrum estimation, the data will often have been prepared to have as little foreground as possible by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual to some subtraction process not in the power spectrum domain.
+If we possess a good estimate of the total covariance of the data, including both the desired signal nd any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the
+
+%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
+This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in
+\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
 Before showing
@@
 used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
+
+\color{black}
 
@@
 \appendix
-\section{A toy model for inverse covariance weighting}
+\section{A toy model of inverse covariance weighting}
 \label{sec:icw_appendix}

### 2018-06-04 PAPER.tex
Mon Jun  4 11:48:25 EDT 2018

@@
 \label{sec:SiglossOverview}
+% JEA - We never totally nail down what ``signal loss'' is ...
 
@@
 Here we focus on signal loss associated with
-% we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
+% JEA - we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
 the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
@@
 
-% Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
+% JEA - Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
 
 \subsubsection{The Quadratic Estimator Method}
+
+%AAAICW
 
@@
 Prior to power spectrum estimation, the data will often have been prepared to have as little foreground as possible by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual to some subtraction process not in the power spectrum domain.
-If we possess a good estimate of the total covariance of the data, including both the desired signal nd any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the
-
+If we possess a good estimate of the total covariance of the data, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal
+% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
 %Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
@@
 analysis.
+
+The optimal quadratic estimator prescription is
+\begin{equation}
+\label{eq:OQE}
+\hat{p}_\alpha = \half ({\F}^{\alpha \beta})^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{p_\beta}  \invC \bm{\Delta} + \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{s} \invC \right] \right)
+\end{equation}
+where $\F$ is the Fisher matrix.
 
@@
 \ref{sec:Sigloss}.
+
+In summary, we expect:
+\begin{itemize}
+
+\item If the covariance of residual foreground contamination were known perfectly, and its covariance structure is sufficiently different from the EoR signal, then we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
+to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
+If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
+We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
+That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
+
+\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
+
+\end{itemize}
+
+In the following sections, we find
+
+\begin{itemize}
+
+\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which in general is strongly biased {\it low} relative to the true value.
+In this context, this is what we call ``signal loss.''
+
+\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced.
+
+\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
+Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable.
+
+% JEA - I really struggle with whether this is intuitively reasonable ...
+it's hard to get a sense of what "noise" is averaging down slower.
+All modes have the same number of samples going into the estimate.
+But the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
+% Also, have we shown this sufficiently rigorously?
+Is the toy model sufficiently general?
+(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
+Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
+
+\end{itemize}
 
@@
 \end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using the optimal quadratic estimator prescription is
-\begin{equation}
-\label{eq:ICWFormula}
-\hat{s} = \half {\F}^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{s}  \invC \bm{\Delta} \right) 
-\end{equation}
-where $\F$ is the Fisher matrix.  
-The expectation of the estimator is then
-\begin{equation}
-\langle \hat{s} \rangle = \frac{\langle \bm{\Delta^T \Delta} \rangle}{N} = s + u
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using the quadratic part of Equation \ref{eq:OQE} is
+\begin{equation}
+\hat{s} = \frac{ \bm{\Delta^T \Delta}}{N} 
+\end{equation}
+and its expectation is
+\begin{equation}
+\langle \hat{s} \rangle = s + u
 \end{equation}
@@
 $\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, we find that when {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
-In fact, if one uses the standard formula \citep[e.g.][, Equation 6]{dillon14} for the additive bias
-\begin{equation}
-b = \half \F^{-1} \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{s} \invC \right]
-\end{equation}
-one indeed finds $b = u$.
+In fact, computing the linear bias from Equation, \ref{eq:OQE}one indeed finds $b = u$.
 
@@
 \end{equation}
-Proceeding to calculate the full estimator
-\begin{equation}
-\hat{s} = \half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = \frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
-\end{equation}
-The expectation is
+Again calculating only the quadratic portion of the estimator,
+\begin{equation}
+\hat{s} = 
+%\half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = 
+\frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
+\end{equation}
+with expectation
 \begin{equation}
@@
 We also assume that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
-
-We find the following things:
-\begin{itemize}
-
-\item If the covariance of residual foreground contamination were known perfectly, and its covariance structure is sufficiently different from the EoR signal, then we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
-to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
-If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
-We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
-That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
-
-\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
-
-\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which in general is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss.''
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced.
-
-\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
-Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable.
-
-% JEA - I really struggle with whether this is intuitively reasonable ...
-it's hard to get a sense of what "noise" is averaging down slower.
-All modes have the same number of samples going into the estimate.
-But the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
-% Also, have we shown this sufficiently rigorously?
-Is the toy model sufficiently general?
-(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
-Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
-
-\end{itemize}
 

### 2018-06-04 PAPER.tex
Mon Jun  4 12:09:25 EDT 2018

@@
 \citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
-Before showing
-how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER 
-analysis.
-
-The optimal quadratic estimator prescription is
+%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
+
+We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
+It has length $N_{t}N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
+Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
+
+The covariance of the data is given by 
+\begin{equation}
+\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle,
+\end{equation}
+where we assume the covariance can be written as a sum $\textbf{C} = \textbf{S} + \textbf{U}$
+of the desired signal $\textbf{S}$ and other terms $\textbf{U}$.
+In general, we are interested in estimating band powers of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, and the fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in $\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}$.
+In practice, this matrix also implements a transform of the frequency-domain visibilities to $\mathbf{k}$ space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+
+The optimal quadratic estimator prescription is then to compute
 \begin{equation}
 \label{eq:OQE}
-\hat{p}_\alpha = \half ({\F}^{\alpha \beta})^{-1} \left( \bm{\Delta}^T \invC \PDeriv{\C}{p_\beta}  \invC \bm{\Delta} + \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{s} \invC \right] \right)
-\end{equation}
-where $\F$ is the Fisher matrix.
-
-We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
-It has length $N_{t}N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where
-$N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. Visibilities are measurements of 
-the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes 
-we only need to take one Fourier transform of our visibilities along the line-of-sight dimension. We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-
+\widehat{p}_{\alpha}  =  \half ({\F}^{\alpha \beta})^{-1} (\widehat{q}_{\beta} + \widehat{b}_{\beta} )
+\end{equation}
+where $\F$ is the Fisher matrix and
+\begin{equation}
+\label{eq:OQEQuadratic}
+\hat{q}_\beta =  \textbf{x}^\dagger \invC \PDeriv{\C}{p_\beta}  \invC \textbf{x} 
+\end{equation}
+and
+\begin{equation}
+\label{eq:OQELinear}
+\widehat{b}_{\beta} = \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p_\beta} \invC \right] 
+\end{equation}
+
+%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
+It is also possible to define a more generalized version of this minimum-variance, unbiased estimator by
 \begin{equation}
@@
 \end{equation}
-Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to 
-Kelvin and taking into account cosmological scalings.
-It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$ (which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the
-Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
+%Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to Kelvin and taking into account cosmological scalings.
+It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$
+
+(which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
 $\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as

### 2018-06-04 PAPER.tex
Mon Jun  4 14:10:47 EDT 2018

@@
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-
-We begin with our data vector, $\textbf{x}$, which contains our measured visibilities for a single baseline in Jy.
-It has length $N_{t}N_{f}$, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels.
+We provide a brief summary of the quadratic estimator below.
+
+% JEA - The discussion of dimensions here is confusing ...
+"a baseline" is mentioned, but it's not clear if the redundant baseline averaging has already happened or what.
+I believe we are only considering covariance between frequencies, but this isn't explicitly said, and the matrix equations don't make sense unless all the dimensions are N_f N_t.
+%We begin with our 
+The measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
+% JEA - not sure this helps
+%, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), 
+where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. The covariance of the data is given by 
+\begin{equation}
+\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle = \textbf{S} + \textbf{U}
+\end{equation}
+where we assume the covariance can be written as a sum of the desired signal $\textbf{S}$ and other terms $\textbf{U}$.
+
+We are interested in estimating the three-dimensional power spectrum of the EoR.  
 Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
-
-The covariance of the data is given by 
-\begin{equation}
-\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle,
-\end{equation}
-where we assume the covariance can be written as a sum $\textbf{C} = \textbf{S} + \textbf{U}$
-of the desired signal $\textbf{S}$ and other terms $\textbf{U}$.
-In general, we are interested in estimating band powers of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, and the fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in $\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}$.
+We consider band powers $p_\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
+The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in
+\begin{equation}
+\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
+\end{equation}
+which has dimensions ($N_{f}$,$N_{f}$).
 In practice, this matrix also implements a transform of the frequency-domain visibilities to $\mathbf{k}$ space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
@@
 \end{equation}
+This estimator is the minimum variance (smallest error bar) estimate of the power spectrum \citep{tegmark_et_al1997a,bond_et_al1998}, and is unbiased according to the usual definition that the ensemble average of the estimator is equal to the true value
+\begin{equation}
+\langle \widehat{p}_{\alpha} \rangle = p_\alpha
+\end{equation}
+
+It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator Equation \ref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
+The way in which this comes about is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
+There we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\textbf{Q}^\alpha$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
+
+if the covariance of the contaminant is known perfectly, and its covariance structure is sufficiently different from the EoR signal, then
+
+we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
+to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
+If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
+We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
+That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
+
+In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
 
@@
 \end{equation}
-%Here, \noindent $\textbf{Q}$ is a family of matrices that takes our frequency-domain visibilities and Fourier transforms them, while also converting from Jy to Kelvin and taking into account cosmological scalings.
-It is formally evaluated as $\textbf{Q}^{\alpha} \equiv \frac{\partial\textbf{C}}{\partial p_{\alpha}}$
-
-(which has dimensions ($N_{f}$,$N_{f}$)), or the derivative of the covariance $\textbf{C} \equiv \langle\textbf{x}\textbf{x}^{\dagger}\rangle$ with respect to the true bandpower $p_\alpha$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-$\textbf{R}$ is a weighting matrix with dimensions ($N_{f}$,$N_{f}$) --- as
-an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
-\textbf{R} \equiv \textbf{I}$, the identity matrix.
-
-We normalize our power spectrum estimates using the matrix $\textbf{M}$:
-
+where $\textbf{R}$ is a weighting matrix chosen by the data analyst.
+%with dimensions ($N_{f}$,$N_{f}$) --- as 
+%an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
+%\textbf{R} \equiv \textbf{I}$, the identity matrix.
+With an appropriate normalization 
+%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
 \begin{equation}
@@
 
-One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
+%One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
 This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
@@
 In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
-
-One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
+%
+%One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
 By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
 Therefore, in an ideal world with perfect foreground,
-instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
+%instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
 In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
@@
 
-We illustrate the way in which the quadratic estimator, Equations \eqref{eq:qhat} and \eqref{eq:phat}, is intended to estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
-We have specifically chosen a toy model where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+We illustrate the way in which the quadratic estimator, Equations \eqref{eq:OQE}, \eqref{eq:OQEQuadratic}, and \eqref{eq:OQELinear} estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
+We have specifically chosen toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
 We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
@@
 \end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using the quadratic part of Equation \ref{eq:OQE} is
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \ref{eq:OQE} is
 \begin{equation}
@@
 \end{equation}
-In this case, the quadratic estimator returns an entirely reasonable result, but, since the covariance of the undesired signal has the same form as the desired signal, that is,
-$\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$, we find that when {\it the covariance structure of the contaminant is identical to the signal}, the information available to the quadratic estimator to distinguish the two is degenerate, and  is only possible to achieve an unbiased estimate of $s$ by using some additional information to estimate the additive bias due to $u$ and subtract it.
-In fact, computing the linear bias from Equation, \ref{eq:OQE}one indeed finds $b = u$.
+Thus, {\it when the covariance structure of the contaminant is identical to the signal} ($\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$), the information available to the quadratic portion of the estimator to distinguish the two is degenerate, and knowledge only of $\C$ and $\PDeriv{\C}{s}$ is inadequate.
+In order to obtain an unbiased estimate of $s$, one must also use knowledge of $\mathbf{U}$.
+Indeed, computing the linear bias from Equation \eqref{eq:OQELinear}, one finds $b = u$.
 
@@
 
-We can again calculate the estimator given by \eqref{eq:ICWFormula} explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
+We can calculate the quadratic portion of the estimator explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
 \begin{equation}
@@
 \end{equation}
-Again calculating only the quadratic portion of the estimator,
+and
 \begin{equation}
@@
 
-This is indeed the desired behavior of the inverse covariance weighting, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
+This is the ideal case for the inverse covariance weighting performed in the PAPER analysis, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
 But even in this case, it is worth pointing out that estimator still has a linear bias for finite $u$.
-We also assume that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
+We have also assumed that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
 

### 2018-06-04 PAPER.tex
Mon Jun  4 14:26:43 EDT 2018

@@
 We consider band powers $p_\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded in
-\begin{equation}
+The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as
+\begin{equation}
+%\textbf{S} = p_{\alpha} 
 \frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
@@
 
-It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator Equation \ref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
+It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator defined by Equation \eqref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
 The way in which this comes about is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
 There we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\textbf{Q}^\alpha$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
-
-if the covariance of the contaminant is known perfectly, and its covariance structure is sufficiently different from the EoR signal, then
-
-we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
-to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
-If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
-We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
-That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
-
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
+These effects for a more realistic model of the EoR and foregrounds were shown in \citet{liu_tegmark2011}.
+
+The toy model also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\PDeriv{\C}{p_\beta}$, but not $\mathbf{U}$.
+We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies, whereas the EoR is not.
+Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, leading to a conservative estimate.
+These considerations, and the difficulty of obtaining an estimate for $\mathbf{U}$, motivate the neglect of the linear bias in the rest of this analysis.
 

### 2018-06-04 PAPER.tex
Mon Jun  4 15:30:31 EDT 2018

@@
 The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as
+% Should distinguish slightly more clearly between Q and dC/dp_alpha
 \begin{equation}
@@
 The way in which this comes about is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
-There we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\textbf{Q}^\alpha$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
+There we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
 These effects for a more realistic model of the EoR and foregrounds were shown in \citet{liu_tegmark2011}.
 
-The toy model also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\PDeriv{\C}{p_\beta}$, but not $\mathbf{U}$.
+The toy model also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\partial \C/\partial p_\alpha$, but not $\mathbf{U}$.
 We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies, whereas the EoR is not.
-Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, leading to a conservative estimate.
+Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, and which can conservatively be interpreted as an upper limit.
 These considerations, and the difficulty of obtaining an estimate for $\mathbf{U}$, motivate the neglect of the linear bias in the rest of this analysis.
@@
 %We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-It is also possible to define a more generalized version of this minimum-variance, unbiased estimator by
+It is also possible to define a more generalized version of the optimal quadratic estimator which may still produce an unbiased estimate, where Equation \eqref{eq:OQEQuadratic} is replaced by
 \begin{equation}
@@
 \end{equation}
-
-\noindent where $\widehat{\textbf{P}}$ is the estimate of the true power spectrum $\textbf{P}$. The data analyst has a choice for $
+$\widehat{\textbf{P}}$ is the estimate of the true power spectrum $\textbf{P}$. The data analyst has a choice for $
 \textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
 of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{P}}$ is a weighted sum of the elements of $\textbf{P}$ with weights that sum to unity.
+% JEA - is one really free to choose M and R independently?
+
+% JEA - I don't think it's attractive at all
+%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
+Given the advantages of inverse covariance weighting, a question arises how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
+Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
+In previous PAPER analyses, one time-averages the data to obtain:
+\begin{equation}
+\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
+\end{equation}
+assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
+\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 
 In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in
-experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it. We note that we 
-purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section
-\ref{sec:Sigloss}.
-
-In summary, we expect:
+Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
+We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:Sigloss}.
+
+%\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
+
+In the following sections, we find
+
 \begin{itemize}
 
-\item If the covariance of residual foreground contamination were known perfectly, and its covariance structure is sufficiently different from the EoR signal, then we can expect a quadratic estimator of the form Equation \ref{} % Need to put the full equation in the main body, I think
-to produce an estimate of the EoR power spectrum with a small linear bias, which is always positive, and no multiplicative bias.
-If the foregrounds have a very similar covariance structure to the EoR, then this linear bias could be large.
-We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies.
-That is, the OQE with the correct covariance matrix but without linear bias subtraction will always produce an estimate which is {\it high} relative to the true value.
-
-\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
-
-\end{itemize}
-
-In the following sections, we find
-
-\begin{itemize}
-
 \item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which in general is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss.''
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced.
+In this context, this is what we call ``signal loss.''  (Section \ref{sec:toymodel})
+
+\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced. (Section \ref{sec:toymodel})
 
@@
 Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable.
-
-% JEA - I really struggle with whether this is intuitively reasonable ...
+(Section \ref{sec:toymodel})
+
+% JEA - I really struggle with whether this is intuitively obvious ...
 it's hard to get a sense of what "noise" is averaging down slower.
@@
 
+% JEA  - This material was moved up
 %One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
@@
 
-In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss.
-We will now build intuition into how empirically estimated inverse covariance weighting can give rise to signal loss through the use of a toy model.
-
-We construct a simple dataset that contains visibility data with $100$ time 
-integrations and $20$ frequency channels. This model represents realistic dimensions of about an hour of PAPER data which 
-might be used for a power spectrum analysis. For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel 
-widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of 
-generality.
-
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation. Hence, flat spectrum sources (away 
-from zenith) lead to measured visibilities which oscillate in time and frequency. We therefore form a mock visibility measurement of a bright foreground signal, $
-\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a 
-single bright source. We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal. A more 
-realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), 
-which could be simulated by introducing frequency correlations into the mock EoR signal. However, here we treat all 
-$k$'s separately, so a simplistic white noise approximation can be used. Our combined data matrix is then $\textbf{x} = 
+%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss. 
+We will now build intuition using a toy model into how weighting using the inverse of the empirically estimated covariance $\widehat{\textbf{C}}^{-1}$ can give rise to signal loss.
+We construct a simple dataset that contains visibility data with $100$ time integrations and $20$ frequency channels.
+This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
+For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of generality.
+
+We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation.
+Hence, flat spectrum sources (away from zenith) lead to measured visibilities which oscillate in time and frequency.
+We therefore form a mock visibility measurement of a bright foreground signal, $\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
+We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal.
+A more realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
+However, here we treat all $k$'s separately, so a simplistic white noise approximation can be used.
+Our combined data matrix is then $\textbf{x} =
 \textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
@@
 
-Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
+%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
 Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
 In previous PAPER analyses, one time-averages the data such that:
-
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
-\end{equation}
-
-\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+%
+%\begin{equation}
+%\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
+%\end{equation}
+%
+%\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+%amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
+%\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 
@@
 The power spectrum of foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare empirically estimated inverse covariance weighting
-where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right). In the former 
-case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
+In the two panels, we compare empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right).
+In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
 For an empirically estimated $\widehat{\textbf{C}}$, its eigenvalues differ from those of the true covariance, where the coupling between EoR-dominated eigenmodes and the data can lead to loss.
-Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are only down-weighting the FG-dominating mode in this case.}
+Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are only down-weighting the FG-dominated mode in this case.}
 	\label{fig:toy_sigloss3}
@@
 
-As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds. It is also evident that our result fails to 
-recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
+As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds.
+It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
 This is evidence of signal loss.
-In short, if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a
-multiplicative bias (per $k$) to estimates of the signal.
-For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
+In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.} For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
 Here we will describe the origin of this signal loss

### 2018-06-04 PAPER.tex
Mon Jun  4 15:39:57 EDT 2018
read through James' edits and edited syntax

@@
 % SECTION 2 SIGLOSS ---------------------------------------------------------------------------------
-\color{blue}
+%\color{blue}
 
@@
 %applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis.
+under-estimated in the \citetalias{ali_et_al2015} analysis.
 
@@
 
-The goal of the power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
-Prior to power spectrum estimation, the data will often have been prepared to have as little foreground as possible by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual to some subtraction process not in the power spectrum domain.
-If we possess a good estimate of the total covariance of the data, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal
+The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
+Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain.
+If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in
 % JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
@@
 which has dimensions ($N_{f}$,$N_{f}$).
-In practice, this matrix also implements a transform of the frequency-domain visibilities to $\mathbf{k}$ space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+In practice, this matrix also implements a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 
@@
 \label{eq:OQELinear}
-\widehat{b}_{\beta} = \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p_\beta} \invC \right] 
-\end{equation}
-This estimator is the minimum variance (smallest error bar) estimate of the power spectrum \citep{tegmark_et_al1997a,bond_et_al1998}, and is unbiased according to the usual definition that the ensemble average of the estimator is equal to the true value
-\begin{equation}
-\langle \widehat{p}_{\alpha} \rangle = p_\alpha
+\widehat{b}_{\beta} = \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p_\beta} \invC \right].
+\end{equation}
+This estimator is the minimum variance (smallest error bar) estimate of the power spectrum \citep{tegmark_et_al1997a,bond_et_al1998} and is unbiased if the ensemble average of the estimator is equal to its true value
+\begin{equation}
+\langle \widehat{p}_{\alpha} \rangle = p_\alpha.
 \end{equation}
@@
 It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator defined by Equation \eqref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
-The way in which this comes about is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
-There we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
-These effects for a more realistic model of the EoR and foregrounds were shown in \citet{liu_tegmark2011}.
-
-The toy model also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\partial \C/\partial p_\alpha$, but not $\mathbf{U}$.
-We do have a reasonable expectation of different covariance structure since the foregrounds, before any processing, {\it are} strongly correlated between frequencies, whereas the EoR is not.
+The way in which the optimal estimator can suppress contaminates is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
+In this appendix, we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
+Similar effects for a more realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
+
+The toy model in Appendix \ref{sec:icw_appendix} also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\partial \C/\partial p_\alpha$, but not $\mathbf{U}$.
+Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
 Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, and which can conservatively be interpreted as an upper limit.
@@
 %Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
-Given the advantages of inverse covariance weighting, a question arises how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
+Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
 Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
@@
 
-In the following sections, we find
+As a brief summary, in the following sections, we find:
 
@@
 
-\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which in general is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss.''  (Section \ref{sec:toymodel})
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced. (Section \ref{sec:toymodel})
+\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
+In this context, this is what we call ``signal loss''  (Section \ref{sec:toymodel}).
+
+\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced (Section \ref{sec:toymodel_frf}).
 
 \item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
-Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable.
-(Section \ref{sec:toymodel})
+Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable (Section \ref{sec:toymodel_frf}).
+
+\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
 
@@
 All modes have the same number of samples going into the estimate.
-But the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
+Should I think of the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
 % Also, have we shown this sufficiently rigorously?
@@
 %In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss. 
-We will now build intuition using a toy model into how weighting using the inverse of the empirically estimated covariance $\widehat{\textbf{C}}^{-1}$ can give rise to signal loss.
+Using a toy model, we will now build intuition into how weighting by the inverse of the empirically estimated covariance, $\widehat{\textbf{C}}^{-1}$, can give rise to signal loss.
 We construct a simple dataset that contains visibility data with $100$ time integrations and $20$ frequency channels.
@@
 
-\color{blue}
+%\color{blue}
 
 \appendix
-\section{A toy model of inverse covariance weighting}
+\section{A toy model for inverse covariance weighting}
 \label{sec:icw_appendix}
@@
 
-We illustrate the way in which the quadratic estimator, Equations \eqref{eq:OQE}, \eqref{eq:OQEQuadratic}, and \eqref{eq:OQELinear} estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
+We illustrate the way in which the quadratic estimator, Equations \eqref{eq:OQE}, \eqref{eq:OQEQuadratic}, and \eqref{eq:OQELinear}, estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
 We have specifically chosen toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
@@
 \begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S}
-\end{equation}
-and we wish to estimate $s$.  The contaminant in this case has a similar structure for its covariance, and is assumed uncorrelated with the signal
+\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S},
+\end{equation}
+where we wish to estimate $s$.  The contaminant in this case has a similar structure (as the EoR) for its covariance, and is assumed uncorrelated with the signal
 \begin{equation}
@@
 \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{I}_{N \times N} \equiv \mathbf{U}; {\rm and}~ 
-\langle \sigma_i \upsilon_j \rangle = 0
+\langle \sigma_i \upsilon_j \rangle = 0.
 \end{equation}
@@
 \begin{equation}
-\langle \hat{s} \rangle = s + u
-\end{equation}
-Thus, {\it when the covariance structure of the contaminant is identical to the signal} ($\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$), the information available to the quadratic portion of the estimator to distinguish the two is degenerate, and knowledge only of $\C$ and $\PDeriv{\C}{s}$ is inadequate.
+\langle \hat{s} \rangle = s + u.
+\end{equation}
+Thus, {\it when the covariance structure of the contaminant is identical to the signal} ($\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$), the information available to the quadratic portion of the estimator to distinguish between the two is degenerate, and knowledge only of $\C$ and $\PDeriv{\C}{s}$ is inadequate.
 In order to obtain an unbiased estimate of $s$, one must also use knowledge of $\mathbf{U}$.
@@
  \mathbf{m}^T \mathbf{m} = 1; \; {\rm and}~ 
-\langle \sigma_i \upsilon \rangle = 0
+\langle \sigma_i \upsilon \rangle = 0.
 \end{equation}
@@
 \begin{equation}
-\xi \equiv \frac{u/s}{1+u/s}
+\xi \equiv \frac{u/s}{1+u/s},
 \end{equation} 
@@
 \langle \hat{s} \rangle = 
-s + \frac{1 - 2 \xi + \xi^2}{N + - 2 \xi + \xi^2} u 
+s + \frac{1 - 2 \xi + \xi^2}{N + - 2 \xi + \xi^2} u. 
 \end{equation}
@@
 
-An instructive limit is $u \gg s$, $\xi \to 1$, in which case the the virtue of weighting by $\invC$ becomes clearer: it becomes
+An instructive limit is $u \gg s$, $\xi \to 1$, in which case the virtue of weighting by $\invC$ becomes clearer, as it becomes
 \begin{equation}
@@
 \end{equation}
-where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any any vector it acts on, and further, the linear bias tends to 0 as $\xi \to 1$, i.e., the projection is ``perfect'' and not ``undone'' by the Fisher matrix normalization.
+where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any vector it acts on, and further, the linear bias tends to 0 as $\xi \to 1$ (i.e., the projection is ``perfect'' and not ``undone'' by the Fisher matrix normalization).
 
 This is the ideal case for the inverse covariance weighting performed in the PAPER analysis, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
-But even in this case, it is worth pointing out that estimator still has a linear bias for finite $u$.
+But even in this case, it is worth pointing out that the estimator still has a linear bias for finite $u$.
 We have also assumed that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.

### 2018-06-04 PAPER.tex
dominating -> dominated

@@
 In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
-For these FG-dominating modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
+For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
 In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
@@
 power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
-demonstrating that if we can disentangle the foreground-dominating modes and EoR-dominating modes, we can down-weight 
+demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can down-weight 
 them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
@@
 method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominating modes which are coupled to the data results in negligible signal loss. However, we do 
+eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominated modes which are coupled to the data results in negligible signal loss. However, we do 
 not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes.

### 2018-06-04 PAPER.tex
minor typo and syntax changes

@@
 \end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a non-diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
+where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
 
@@
 departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-in this regime the cross-term has nearly the same amplitude, but with a negative sign.
+in this regime the cross-term (red) has nearly the same amplitude, but with a negative sign.
 As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
@@
 as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.9 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.9$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
+In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.09 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.09$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
 	\label{fig:sigloss_modeloop}
@@
 This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (solid red, dashed red, black) perform similarly at
+We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
 their best (i.e.
-when $\sim2$-$3$ eigenmodes are down-weighted in the case of the solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.9 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.9$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
+when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
 We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
@@
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
+We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework (red and blue) are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
 	\label{fig:ps_noise}
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to better agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $2$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 }%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
 
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of baselines themselves.
+\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
 In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
@@
 More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
-This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+This is because cross-multiplications produce four additive terms --- a signal-squared term (where ``signal" includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
 When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
@@
 factor of $\sim10$ in mK higher than the lossy empirical inverse covariance limits. Under-estimated signal loss therefore represents the bulk of our revision. 
-This revision is similar to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
+This revision is similar in nature to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
 revised from new signal loss calculations associated with their singular value decomposition foreground filter.
 \item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
+Several other errors were also found regarding error estimation, though with smaller effects.
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
@@
 
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
+When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
 For the injections that we do sample, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though we note in practice we fit solutions for every $k$-value and simulation independently.
+An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
 
@@
 	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final} (black).
-We smooth the prior using a sliding boxcar average for every $5$ injections (red).
+We smooth the prior using a sliding boxcar average over every $5$ injections (red).
 Most noticeably, the Jeffreys prior is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}

### 2018-06-05 PAPER.tex
moved james up on author list
Minor syntax

@@
 Saul A. Kohn\altaffilmark{5},
+James E.~Aguirre\altaffilmark{5},
 Jonathan C. Pober\altaffilmark{6}, 
-James E.~Aguirre\altaffilmark{5},
 Zaki S. Ali\altaffilmark{1}, 
@@
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-We provide a brief summary of the quadratic estimator below.
+We provide a brief summary of the optimal quadratic estimator below.
 
@@
 \end{equation}
-where we assume the covariance can be written as a sum of the desired signal $\textbf{S}$ and other terms $\textbf{U}$.
+where we assume the covariance can be written as a sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
 

### 2018-06-06 PAPER.tex
Wed Jun  6 11:44:31 EDT 2018

@@
 \newcommand{\dC}[1]{\ensuremath{\C_{,#1}}}
-\DeclareMathOperator{\Tr}{Tr}
+\DeclareMathOperator{\Tr}{tr}
 \newcommand{\half}{\ensuremath{\frac{1}{2}}}
@@
 \end{equation}
-where we assume the covariance can be written as a sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
+where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as a sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
 
@@
 The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as
-% Should distinguish slightly more clearly between Q and dC/dp_alpha
-\begin{equation}
-%\textbf{S} = p_{\alpha} 
-\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
-\end{equation}
-which has dimensions ($N_{f}$,$N_{f}$).
-In practice, this matrix also implements a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
+\begin{equation}
+\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
+%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
+\end{equation}
+where we use the Einstein summation convention.
+% JEA - ah, the dimensions again
+% which has dimensions ($N_{f}$,$N_{f}$).
 
@@
 \label{eq:OQE}
-\widehat{p}_{\alpha}  =  \half ({\F}^{\alpha \beta})^{-1} (\widehat{q}_{\beta} + \widehat{b}_{\beta} )
-\end{equation}
-where $\F$ is the Fisher matrix and
+\widehat{p}_{\alpha}  =  ({\F^{-1}})_\alpha^{\beta} (\widehat{q}_{\beta} - \widehat{b}_{\beta} )
+\end{equation}
+where $\F$ is the Fisher matrix 
+\begin{equation}
+F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \frac{\partial\textbf{C}}{\partial p_{\alpha}} \C^{-1} \frac{\partial\textbf{C}}{\partial p_{\beta}} \right)
+\end{equation}
+and
 \begin{equation}
 \label{eq:OQEQuadratic}
-\hat{q}_\beta =  \textbf{x}^\dagger \invC \PDeriv{\C}{p_\beta}  \invC \textbf{x} 
+\hat{q}_\alpha =  \half \textbf{x}^\dagger \invC \PDeriv{\C}{p^\alpha}  \invC \textbf{x} 
 \end{equation}
@@
 \label{eq:OQELinear}
-\widehat{b}_{\beta} = \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p_\beta} \invC \right].
-\end{equation}
-This estimator is the minimum variance (smallest error bar) estimate of the power spectrum \citep{tegmark_et_al1997a,bond_et_al1998} and is unbiased if the ensemble average of the estimator is equal to its true value
+\widehat{b}_{\alpha} = \half \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p^\alpha} \invC \right].
+\end{equation}
+This estimator is the minimum variance (smallest error bar) estimate of the power spectrum  subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
 \begin{equation}
@@
 \end{equation}
+\citep{tegmark_et_al1997a,bond_et_al1998}
 
@@
 %We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-It is also possible to define a more generalized version of the optimal quadratic estimator which may still produce an unbiased estimate, where Equation \eqref{eq:OQEQuadratic} is replaced by
+Motivated by the desire to retain the desirable behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a more generalized version of the quadratic estimator
+%which may still produce an unbiased estimate, 
+where Equation \eqref{eq:OQEQuadratic} is replaced by
 \begin{equation}
@@
 where $\textbf{R}$ is a weighting matrix chosen by the data analyst.
+For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
+The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p_\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
-%an example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $
-%\textbf{R} \equiv \textbf{I}$, the identity matrix.
+
+%%% COME BACK HERE
+% Need to still explain the motivation for this
 With an appropriate normalization 

### 2018-06-06 PAPER.tex
Wed Jun  6 14:33:35 EDT 2018

@@
 \subsubsection{The Quadratic Estimator Method}
+\label{sec:QE}
 
@@
 However, here we treat all $k$'s separately, so a simplistic white noise approximation can be used.
-Our combined data matrix is then $\textbf{x} =
+Our combined data vector is then $\textbf{x} =
 \textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
@@
 
-%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data such that:
-%
-%\begin{equation}
-%\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t},
-%\end{equation}
-%
-%\noindent assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
-%amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-%\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-
-First, we compute the power spectrum of our toy model dataset $\textbf{x}$ using QE formalism and $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$. 
-The result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
-Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $
-\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
+%First, 
+We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \ref{eq:qhat} and \ref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
+The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
+The power spectrum result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
+Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
+As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds,
+%For our toy model, the successful suppression of the foreground mode is 
+demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
+It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
+It is this behavior which we describe as signal loss.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
+	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
+(middle), and FG + EoR (right). Real parts are shown here.}
+	\label{fig:toy_sigloss12}
+\end{figure}
 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.pdf}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- 
-foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
 The power spectrum of foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
@@
 In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
-For an empirically estimated $\widehat{\textbf{C}}$, its eigenvalues differ from those of the true covariance, where the coupling between EoR-dominated eigenmodes and the data can lead to loss.
-Hence, there is negligible signal loss when assigning identical weights to all eigenmodes except the first, since we are only down-weighting the FG-dominated mode in this case.}
+% JEA - redundant
+%For an empirically estimated $\widehat{\textbf{C}}$, 
+%its eigenvalues differ from those of the true covariance, where 
+%the coupling between EoR-dominated eigenmodes and the data can lead to loss.
+%Hence, 
+There is negligible signal loss when the other eigenmodes besides the foreground one are no longer correlated with the data.
+%assigning identical weights to all eigenmodes except the first, 
+%constructing a covariance proportional to the identity and the outer product of the sinusoid eigenmode, since we are only down-weighting the FG-dominated mode in this case.
+}
 	\label{fig:toy_sigloss3}
@@
 
-As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds.
-It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-This is evidence of signal loss.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.} For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
-Here we will describe the origin of this signal loss
-intuitively.
-
-To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
+As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use $\textbf{C}^{-1}$ weighting.
+Rather, we would obtain the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (c.f.
+Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in a nearly unbiased estimate of the power spectrum.
+The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
+
+For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the covariance matrix will result in the desired suppression via a kind of projection (c.f.
+Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator});  whether or not it is strongly correlated with the the actual data vector is irrelevant.
+However, in the case the covariance matrix is empirically estimated, the eigenmodes of $\textbf{C}_{\rm EoR}$ will both be incorrect and correlated with the data.
+Incorrect eigenmodes of $\textbf{C}_{\rm EoR}$ will lead to non-minimum variance estimates, but will not produce the suppression of the power spectrum amplitude seen.
+As indicated in Appendix \ref{sec:sigloss_appendix}, however, having $\widehat{\mathbf{C}}$ correlated with the data vector $\mathbf{x}$ also produces a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
+In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
+
+%For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
+Here we will describe the origin of this signal loss intuitively.
+
+%% JEA - I don't think the eigenspectrum really helps, but at some point we probably want to show it ...
+%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
 Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
-
-An eigenspectrum ranks the eigenvalues of a matrix from 
-highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data. In other 
-words, the eigenvalues encode the strength of different shapes in the dataset. The eigenspectrum of the identity matrix $
-\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
+%
+%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
+In other words, the eigenvalues encode the strength of different shapes in the dataset.
+The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
 In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-The modes with the highest eigenvalues are
-down-weighted the most.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
-	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
-(green). The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one 
-sinusoid.
+%% JEA - I think this is actually NOT true - see the toy model as an example.
+The size of the eigenvalues isn't what determines that the undesired mode is downweighted and the others left alone.
+I haven't computed the eigenvalues explicitly, but down-weighting of m occurs regardless of the relative size of s and u.
+%The modes with the highest eigenvalues are down-weighted the most.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
+%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
+%(green).
+The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
 These empirically estimated covariance matrices have eigenspectra that are different from that of the true $\textbf{C}$.
 Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
-	\label{fig:toy_sigloss2}
-\end{figure}
-
-Because $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-For example, the highest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}).
-In Figure \ref{fig:toy_sigloss12} we show the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
-The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
-
-In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
+%	\label{fig:toy_sigloss2}
+%\end{figure}
+
+%We show the {\it eigenspectrum} (the eigenvalues of the matrix in descending order) of this toy model in Figure \ref{fig:toy_sigloss2}.  In this case,
+%For example, 
+%the largest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}). 
+%
+
+%In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
 For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
 In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
-For our toy model, the successful suppression of the foreground mode is demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
-	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
-(middle), and FG + EoR (right). Real parts are shown here.}
-	\label{fig:toy_sigloss12}
-\end{figure}
-
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominating eigenmodes of $
-\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
+The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
@@
 
-Using what we've learned about the eigenspectrum, we can tweak it in a simple way to suppress foregrounds and yield minimal 
-signal loss.
-Recall that our toy model foreground is a sinusoid, so it can be perfectly described by a single eigenmode.
-Using the full dataset's (foreground plus EoR signal) empirical covariance, we can
-project out the first eigenmode and then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
+Armed with this information,
+%Using what we've learned about the eigenspectrum, 
+we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
+% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
+%is a sinusoid, so it 
+can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
+project out the first eigenmode and 
+%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
 Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
 only allowing over-fitting to occur for the first mode).
-
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are 
-changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. The resulting 
-power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. In this case we recover the EoR signal, 
-demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can down-weight 
-them with negligible signal loss. There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
+then take the remaining covariance to be the identity matrix.  
+This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
+In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
+% down-weight them 
+foregrounds with negligible signal loss.
+
+Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization.
+There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
 \ref{sec:otherweight}.
@@
 \begin{equation}
+\label{eq:IdealToyModelCovariance}
 \langle \upsilon_i \rangle = 0; \; 
@@
 \begin{equation}
+\label{eq:IdealToyModelEstimator}
 \hat{s} = \frac{ \bm{\Delta^T \Delta}}{N} 
@@
 
-In this Appendix, we examine a toy model for signal loss. Our goal is to derive an analytic formula for power spectrum signal loss. While this 
-model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
+In this Appendix, we examine a toy model for signal loss.
+Our goal is to derive an analytic formula for power spectrum signal loss.
+While this model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
 

### 2018-06-06 PAPER.tex
Wed Jun  6 14:45:35 EDT 2018

@@
 
-We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data. We will next show how this effect is exacerbated by reducing the total number of independent 
-samples in a dataset.
+We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data.
+We will next show how this effect is exacerbated by reducing the total number of independent samples in a dataset.
 
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with 
-the sidereal motion on the sky, while down-weighting modes which are noise-like.
-
-Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent 
-samples in the data. To mimic this filter, we average every four time integrations of our toy model dataset together, yielding 
-$25$ independent samples in time (Figure \ref{fig:toy_sigloss5}). We choose these numbers so that the total number of 
-independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
+Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes which are noise-like.
+
+Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
+To mimic this filter, we average every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
 %\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
 
-The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure 
-\ref{fig:toy_sigloss15}. With 
-fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the 
-true covariance matrix of the fringe-rate filtered data. This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
+% JEA - Death to eigenspectra!
+%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}. 
+With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
+This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 \begin{equation}
@@
 
-Just as important as the eigenvalues are the eigenvectors of our empirical covariances.
-In general, different eigenvectors converge to their true forms at different rates.
+%Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
+The overall convergence of the covariance is important, but it is an important fact that, in general, different eigenvectors converge to their true forms at different rates.
 This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix whose true form is a diagonal matrix with eigenvalues spanning four orders of magnitude.
@@
 In contrast, the lower-valued eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
+% JEA - this is redundant
+%Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
 %\acl{Think about whether we need to do the Fourier space version as well.}
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
-	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
+% JEA - death to eigenspectra!
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
+%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
 The dashed, steep eigenspectrum has a greater risk of signal loss because its lowest-valued eigenmodes are both more strongly coupled to the data (than those of the solid eigenspectrum) and, in this example, are also EoR-dominated.}
-	\label{fig:toy_sigloss15}
-\end{figure}
+%	\label{fig:toy_sigloss15}
+%\end{figure}
 
@@
 loss and noisier estimates when using data-estimated covariance matrices. Longer integrations increase sensitivity but reduce 
-the number of independent samples, resulting in poorly characterized, steep eigenspectra that can overfit signal greatly. We 
+the number of independent samples, resulting in 
+eigenmodes correlated with the data
+% JEA - it's not that they are wrong, but that they are correlated
+%poorly characterized, steep eigenspectra 
+that can overfit signal greatly. We 
 note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be 
@@
 been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
-spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8} and \ref{fig:toy_sigloss14}.
+spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8}.
+% and \ref{fig:toy_sigloss14}. 
 These examples are not meant to be taken as suggested analysis methods but rather as illustrative cases.
@@
 This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would).
-This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}.
+%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
 In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we don't know how to separate out the foregrounds from the EoR in our data.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
-	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
-weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
-matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
-\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
-	\label{fig:toy_sigloss14}
-\end{figure}
-
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
+%	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
+%weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
+%matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
+%\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
+%computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
+%	\label{fig:toy_sigloss14}
+%\end{figure}
+%
 The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}} \equiv 

### 2018-06-07 PAPER.tex
Made some changes to OQE descriptions

@@
 \label{eq:OQELinear}
-\widehat{b}_{\alpha} = \half \Tr\left[ (\C - \mathbf{S}) \invC \PDeriv{\C}{p^\alpha} \invC \right].
+\widehat{b}_{\alpha} = \half \Tr\left( \mathbf{U} \invC \PDeriv{\C}{p^\alpha} \invC \right).
 \end{equation}
@@
 \begin{equation}
+\label{eq:super_unbiased}
 \langle \widehat{p}_{\alpha} \rangle = p_\alpha.
@@
 It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator defined by Equation \eqref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
-The way in which the optimal estimator can suppress contaminates is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
+By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
+However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
+The way in which the optimal estimator accomplishes this is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
 In this appendix, we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
@@
 %We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-Motivated by the desire to retain the desirable behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a more generalized version of the quadratic estimator
+Motivated by the desire to retain the desirable behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
 %which may still produce an unbiased estimate, 
@@
 % Need to still explain the motivation for this
-With an appropriate normalization 
+With an appropriate normalization matrix $\textbf{M}$, the quantity
 %We normalize our power spectrum estimates using the matrix $\textbf{M}$:
@@
 \label{eq:phat}
-\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}},
-\end{equation}
-$\widehat{\textbf{P}}$ is the estimate of the true power spectrum $\textbf{P}$. The data analyst has a choice for $
+\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
+\end{equation}
+is a sensible estimate of the true power spectrum $\textbf{P}$.
+To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
+\begin{eqnarray}
+\langle \widehat{P}_\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M_{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
+&\equiv & \sum_{\beta} W_{\alpha \beta} p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
+\end{eqnarray}
+where $W_{\alpha \beta}$ are elements of a window function matrix.
+Consider the first term of this expression.
+(Again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
+If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
+However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimates.
+In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized.
+Beyond this, the data analyst has a choice for $
 \textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
-of PAPER-64 data as explained in Section \ref{sec:Bias}, subject to the constraint that each element of $\widehat{\textbf{P}}$ is a weighted sum of the elements of $\textbf{P}$ with weights that sum to unity.
+of PAPER-64 data as explained in Section \ref{sec:Bias}.
+In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
+If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
 % JEA - is one really free to choose M and R independently?
@@
 However, in the case the covariance matrix is empirically estimated, the eigenmodes of $\textbf{C}_{\rm EoR}$ will both be incorrect and correlated with the data.
-Incorrect eigenmodes of $\textbf{C}_{\rm EoR}$ will lead to non-minimum variance estimates, but will not produce the suppression of the power spectrum amplitude seen.
+Incorrect eigenmodes of $\textbf{C}_{\rm EoR}$ that are not correlated with the data will lead to non-minimum variance estimates, but will not produce the suppression of the power spectrum amplitude seen.
 As indicated in Appendix \ref{sec:sigloss_appendix}, however, having $\widehat{\mathbf{C}}$ correlated with the data vector $\mathbf{x}$ also produces a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.

### 2018-06-07 PAPER.tex
changed dC/dP's to Q's and changed some minor syntax stuff in Section 2.1.1

@@
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-We provide a brief summary of the optimal quadratic estimator below.
+We provide a brief summary of the optimal quadratic estimator and explain its advantages below.
 
@@
 \begin{equation}
-\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
+\textbf{S} = \sum_\alpha p_\alpha \frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \sum_\alpha p_\alpha \textbf{Q}_\alpha
+%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
 %\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
 \end{equation}
-where we use the Einstein summation convention.
+where we define $\frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \textbf{Q}_{\alpha}$.
 % JEA - ah, the dimensions again
@@
 \begin{equation}
-F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \frac{\partial\textbf{C}}{\partial p_{\alpha}} \C^{-1} \frac{\partial\textbf{C}}{\partial p_{\beta}} \right)
+F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right)
 \end{equation}
@@
 \label{eq:OQEQuadratic}
-\hat{q}_\alpha =  \half \textbf{x}^\dagger \invC \PDeriv{\C}{p^\alpha}  \invC \textbf{x} 
+\widehat{q}_\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
 \end{equation}
@@
 \label{eq:OQELinear}
-\widehat{b}_{\alpha} = \half \Tr\left( \mathbf{U} \invC \PDeriv{\C}{p^\alpha} \invC \right).
+\widehat{b}_{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
 \end{equation}
@@
 In this appendix, we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
-Similar effects for a more realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-
-The toy model in Appendix \ref{sec:icw_appendix} also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\partial \C/\partial p_\alpha$, but not $\mathbf{U}$.
+Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
+
+The toy model in Appendix \ref{sec:icw_appendix} also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
 Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
@@
 %We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-Motivated by the desire to retain the desirable behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
+Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
 %which may still produce an unbiased estimate, 
@@
 \label{eq:qhat}
-\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}.
+\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
 \end{equation}
@@
 where $W_{\alpha \beta}$ are elements of a window function matrix.
-Consider the first term of this expression.
-(Again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
+Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
 If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
-However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimates.
+However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
 In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized.
 Beyond this, the data analyst has a choice for $
-\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we explore other cases for the analysis 
+\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we discuss other cases for the analysis 
 of PAPER-64 data as explained in Section \ref{sec:Bias}.
@@
 
-As a brief summary, in the following sections, we find:
+As a brief preview, we summarize our findings in the following sections here:
 

### 2018-06-07 PAPER.tex
syntax edits to 2.1.2

@@
 We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \ref{eq:qhat} and \ref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with $\widehat{\textbf{C}}^{-1}$ weighted data.
+Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
 The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
@@
 %Hence, 
-There is negligible signal loss when the other eigenmodes besides the foreground one are no longer correlated with the data.
+There is negligible signal loss when all eigenmodes besides the foreground one are no longer correlated with the data.
 %assigning identical weights to all eigenmodes except the first, 
@@
 
-As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (c.f.
-Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in a nearly unbiased estimate of the power spectrum.
-The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it.
-
-For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the covariance matrix will result in the desired suppression via a kind of projection (c.f.
-Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator});  whether or not it is strongly correlated with the the actual data vector is irrelevant.
-However, in the case the covariance matrix is empirically estimated, the eigenmodes of $\textbf{C}_{\rm EoR}$ will both be incorrect and correlated with the data.
-Incorrect eigenmodes of $\textbf{C}_{\rm EoR}$ that are not correlated with the data will lead to non-minimum variance estimates, but will not produce the suppression of the power spectrum amplitude seen.
-As indicated in Appendix \ref{sec:sigloss_appendix}, however, having $\widehat{\mathbf{C}}$ correlated with the data vector $\mathbf{x}$ also produces a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
+As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
+Rather, we would obtain the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in a nearly unbiased estimate of the power spectrum.
+The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
+
+For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
+However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
+If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
+As shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
 In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}

### 2018-06-07 PAPER.tex
syntax edits to 2.1.3

@@
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
+More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), which leads to loss.
 Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
@@
 With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
-This can be quantified by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
+We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 \begin{equation}
@@
 To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average.
-We then compare this to the ``true' covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
+We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
 As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors).

### 2018-06-07 PAPER.tex
syntax edits to 2.1.4

@@
 been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
-spectra and eigenspectra for the different cases in Figures \ref{fig:toy_sigloss8}.
+spectra for the different cases in Figure \ref{fig:toy_sigloss8}.
 % and \ref{fig:toy_sigloss14}. 
@@
 While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
-
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (keeping only the diagonal elements of $\widehat{\textbf{C}}$).
+We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
+
+The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e.
+keeping only the diagonal elements of $\widehat{\textbf{C}}$).
 In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to any of the empirically estimated eigenmodes.
+panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
 For this toy model,
@@
 Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
-are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more than others based on the spectral nature 
+are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more effectively than others based on the spectral nature 
 of the components in a dataset. 

### 2018-06-07 PAPER.tex
Straightened out index and summation notation

@@
 \begin{equation}
-\textbf{S} = \sum_\alpha p_\alpha \frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \sum_\alpha p_\alpha \textbf{Q}_\alpha
+\textbf{S} = \sum_\alpha p^\alpha \frac{\partial\textbf{C}}{\partial p^\alpha} \equiv \sum_\alpha p^\alpha \textbf{Q}^\alpha
 %\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
@@
 \label{eq:OQE}
-\widehat{p}_{\alpha}  =  ({\F^{-1}})_\alpha^{\beta} (\widehat{q}_{\beta} - \widehat{b}_{\beta} )
+\widehat{p}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
 \end{equation}
@@
 \label{eq:OQEQuadratic}
-\widehat{q}_\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
+\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
 \end{equation}
@@
 \label{eq:OQELinear}
-\widehat{b}_{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
+\widehat{b}^{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
 \end{equation}
@@
 \label{eq:super_unbiased}
-\langle \widehat{p}_{\alpha} \rangle = p_\alpha.
+\langle \widehat{p}^{\alpha} \rangle = p^\alpha.
 \end{equation}
@@
 \label{eq:qhat}
-\widehat{q}_{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
+\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
 \end{equation}
@@
 For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p_\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p^\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 \begin{eqnarray}
-\langle \widehat{P}_\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M_{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
-&\equiv & \sum_{\beta} W_{\alpha \beta} p_\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
+\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
+&\equiv & \sum_{\beta} W^{\alpha \beta} p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
 \end{eqnarray}
-where $W_{\alpha \beta}$ are elements of a window function matrix.
+where $W^{\alpha \beta}$ are elements of a window function matrix.
 Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
@@
 \label{eq:Pin}
-\widehat{P}_{\rm in,\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
+\widehat{P}_{\rm in}^{\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
 \end{equation}
@@
 \label{eq:sigloss}
-\widehat{P}_{\rm out,\alpha} &\equiv& \widehat{\textbf{P}}_{r,\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
+\widehat{P}_{\rm out}^{\alpha} &\equiv& \widehat{\textbf{P}}_{r}^{\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
 &=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
@@
 \label{eq:crossterm_full}
-\widehat{P}_{\rm out,\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
+\widehat{P}_{\rm out}^{\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
 %\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
@@
 \label{eq:crossterm}
-\widehat{P}_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
+\widehat{P}_{\rm out}^{\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
@@
 \begin{eqnarray}
-\widehat{P}_{\rm in,\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-\widehat{P}_{\rm out,\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
+\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
 %&&\phantom{=====} 
@@
 have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
-compute $\textbf{M}$ using the matrix $\textbf{F}$ (chosen because this would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:
-
-\begin{equation}
-\textbf{F}_{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
+compute $\textbf{M}$ using the matrix $\textbf{G}$ (which would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:
+
+\begin{equation}
+\textbf{G}^{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
 \end{equation}
@@
 \noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
-the Cholesky decomposition of $\textbf{F}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{F}$ is Hermitian):
-
-\begin{equation}
-\textbf{F} = \textbf{LL}^{\dagger}.
+the Cholesky decomposition of $\textbf{G}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{G}$ is Hermitian):
+
+\begin{equation}
+\textbf{G} = \textbf{LL}^{\dagger}.
 \end{equation}
@@
 
-\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MF}$, 
-becomes:
+\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MG}$ (see Equation \eqref{eq:Wpplusbias}), 
+becomes
 
@@
 \noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
-of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{F}$ in such a way so that 
+of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{G}$ in such a way so that 
 power can leak from high-$k$ modes to low-$k$ modes, but not vice versa.

### 2018-06-14 PAPER.tex
made alpha into superscript instead of subscript in text right after eqn 2
changed caption to fig 6 and description to reflect new toy model

@@
 \end{equation}
-where we define $\frac{\partial\textbf{C}}{\partial p_\alpha} \equiv \textbf{Q}_{\alpha}$.
+where we define $\frac{\partial\textbf{C}}{\partial p^\alpha} \equiv \textbf{Q}^{\alpha}$.
 % JEA - ah, the dimensions again
@@
 The overall convergence of the covariance is important, but it is an important fact that, in general, different eigenvectors converge to their true forms at different rates.
-This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix whose true form is a diagonal matrix with eigenvalues spanning four orders of magnitude.
-We use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$ for the empirical eigenvectors $\widehat{\textbf{v}}$, defined as:
+This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
+For this simulation, we construct a covariance whose ``true" form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the power spectrum domain, where the signal is expected to be uncorrelated; its Fourier-transform is then the ``true" covariance of the EoR in the visibility-domain, or $\textbf{C}_{\rm EoR}$).
+For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance (average over the realizations).
+The eigenvectors of this empirical covariance are then compared to the ``true" eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
 \begin{equation}
@@
 The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
+We see that the zeroth eigenmode is quickest to converge --- this mode describes the foreground signal, which has a distinctly different covariance structure than that of the EoR.
+\cc{add discussion of eigenmode degeneracies and how that affects convergence rates...
+also state that the toy model happens to have a FG mode that dominates the highest eigenvalue, but it's not always that way}.
+
+%One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
 With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
@@
 The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the highest-valued modes converge more quickly than the others, implying that weighting by the lowest-valued empirically estimated modes poses the most risk for loss.
-Since these modes are also typically EoR-dominated, this can lead to cosmological signal loss.}
+This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors that differ in structure from those of the EoR (i.e.
+the FG-dominated mode in the toy model has a different covariance structure than the EoR) converge to the true eigenvectors the quickest.}
 	\label{fig:toy_sigloss17}

### 2018-06-14 PAPER.tex
first pass at describing eigenvector convergence rates

@@
 %Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-The overall convergence of the covariance is important, but it is an important fact that, in general, different eigenvectors converge to their true forms at different rates.
+\cc{start of carina edits}The overall convergence of the covariance is important, but it is an important fact that, in general, different eigenvectors converge to their true forms at different rates.
 This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
@@
 The eigenmode convergence curves  in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-We see that the zeroth eigenmode is quickest to converge --- this mode describes the foreground signal, which has a distinctly different covariance structure than that of the EoR.
-\cc{add discussion of eigenmode degeneracies and how that affects convergence rates...
-also state that the toy model happens to have a FG mode that dominates the highest eigenvalue, but it's not always that way}.
+We see that the zeroth eigenmode is quickest to converge --- this mode describes the foreground signal.
+We will now explain this behavior and describe how the convergence rates of empirical eigenmodes is related to sample variance in our empirical estimate.
+
+In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances.
+When there are many similarly-shaped eigenmodes (i.e.
+modes $1$-$19$), this sample variance can lead to degeneracies between modes, where some modes are swapping with others and fluctuating about.
+In other words, it takes more realizations in order to sort out the degeneracies and approach the true eigenmodes.
+However, an eigenmode that differs substantially from the others (i.e.
+mode $0$, or the foreground mode), can more easily converge to its true shape because the sample variance isn't large enough for it to be mistaken for a different mode (i.e.
+it can decouple from the other modes more easily).
+Another way of thinking about this, is that for the case of a completely flat eigenspectrum (all equal eigenvalues), any linear combination of eigenvectors is allowed, and hence convergence is very difficult.
+The more color, or steepness, given to an eigenspectrum, the easier it is for the eigenmodes to de-couple and approach their true ones.
+
+While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
+In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
+Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
+However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.\cc{end of carina edits}
 

### 2018-06-14 PAPER.tex
added transition back to FRF toy model

@@
 Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
-However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.\cc{end of carina edits}
+However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.
 
@@
 
-The power spectrum results for the fringe-rate filtered toy model data are shown in Figure \ref{fig:toy_sigloss7}. As 
-expected, there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
+With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our fringe-rate filtered toy model.
+\cc{end of carina edits}The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as
+expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
 In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter.

### 2018-06-15 PAPER.tex
Revised language in eigenmode convergence section

@@
 %Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-\cc{start of carina edits}The overall convergence of the covariance is important, but it is an important fact that, in general, different eigenvectors converge to their true forms at different rates.
+\cc{start of carina edits}The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
 This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
-For this simulation, we construct a covariance whose ``true" form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the power spectrum domain, where the signal is expected to be uncorrelated; its Fourier-transform is then the ``true" covariance of the EoR in the visibility-domain, or $\textbf{C}_{\rm EoR}$).
-For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance (average over the realizations).
-The eigenvectors of this empirical covariance are then compared to the ``true" eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
+For this simulation, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
+For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance by averaging over the realizations.
+The eigenvectors of this empirical covariance are then compared to the true eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
 \begin{equation}
@@
 The eigenmode convergence curves in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-We see that the zeroth eigenmode is quickest to converge --- this mode describes the foreground signal.
-We will now explain this behavior and describe how the convergence rates of empirical eigenmodes is related to sample variance in our empirical estimate.
-
+We see that the zeroth eigenmode --- the mode describing the foreground signal --- is quickest to converge.
+
+Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate.
 In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances.
-When there are many similarly-shaped eigenmodes (i.e.
-modes $1$-$19$), this sample variance can lead to degeneracies between modes, where some modes are swapping with others and fluctuating about.
-In other words, it takes more realizations in order to sort out the degeneracies and approach the true eigenmodes.
-However, an eigenmode that differs substantially from the others (i.e.
-mode $0$, or the foreground mode), can more easily converge to its true shape because the sample variance isn't large enough for it to be mistaken for a different mode (i.e.
-it can decouple from the other modes more easily).
-Another way of thinking about this, is that for the case of a completely flat eigenspectrum (all equal eigenvalues), any linear combination of eigenvectors is allowed, and hence convergence is very difficult.
-The more color, or steepness, given to an eigenspectrum, the easier it is for the eigenmodes to de-couple and approach their true ones.
+Consider first a limiting case where all eigenvalues are equal.
+In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors.
+In our current test, aside from the first mode, the eigenvalues have similar values but are not precisely equal.
+There are thus a well-defined set of eigenvectors to converge to.
+However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
+Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to de-couple from each other and approach their true forms.
+A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate.
+To break degeneracies in the remaining modes, however, requires many more realizations.
 
 While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
+The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged, there will not be any signal loss.
+However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
+
 In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.

### 2018-06-15 PAPER.tex
edit to fig 6 caption

@@
 In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors.
-In our current test, aside from the first mode, the eigenvalues have similar values but are not precisely equal.
-There are thus a well-defined set of eigenvectors to converge to.
+In our current test, aside from the zeroth mode, the eigenvalues have similar values but are not precisely equal.
+Hence, there is a well-defined set of eigenvectors to converge to.
 However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
@@
 The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors that differ in structure from those of the EoR (i.e.
-the FG-dominated mode in the toy model has a different covariance structure than the EoR) converge to the true eigenvectors the quickest.}
+This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (i.e.
+the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
+On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
 	\label{fig:toy_sigloss17}

### 2018-06-18 PAPER.tex
revised refs to Matt paper - no longer says that Matt's paper explores regularization options

@@
 for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
-led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64. This revised result, presented in a companion paper by Kolopanis et al. (\textit{submitted}), mostly stems from an 
-improved signal loss calculation for loss associated with empirically estimated covariances and supersedes results from 
+led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
+While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a companion paper by Kolopanis et al.
+(\textit{in prep.}) and supersede results from
 previously published PAPER analyses.
@@
 In this study we use a subset of the PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
-(\textit{submitted}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
+(\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
 
@@
 from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a 
-revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{submitted})). We conclude in Section \ref{sec:Con}.
+revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{in prep.})). We conclude in Section \ref{sec:Con}.
 
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$.
-The revision of this limit (Kolopanis et al.
-(\textit{submitted})) stems from previously under-estimated signal loss and under-estimated error bars, both of which we
+The need to revise this limit stems from previously under-estimated signal loss and under-estimated error bars, both of which we
 address in the following sections.
@@
 In the case study in this paper, we only use one baseline type instead of the three as in
-\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{submitted}) uses all baselines presented in \citetalias{ali_et_al2015}.
+\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{in prep.}) uses all baselines presented in \citetalias{ali_et_al2015}.
 
@@
 We also note that all of the regularizations described here perform similarly to the uniformly weighted case.
-However, we find that the regularization of empirical covariances does outperform the uniform weighted case for redshifts (and $k$-values) for which there are stronger foregrounds, as presented in Kolopanis et al.
-(\textit{submitted}).
+Thus, in Kolopanis et al.
+(\textit{in prep.}), uniform weightings are used to produce straightforward power spectrum limits that do not suffer from loss.
 
@@
 We show this power spectrum result as one example of how a simple regularization can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
-In Kolopanis et al.
-(\textit{submitted}), multiple redshifts are explored and found to benefit from weighting differently.
 
@@
 This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
-(\textit{submitted}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
+(\textit{in prep.}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
 loss, bootstrapping, and the theoretical error computation.}
@@
 because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{submitted})).
+we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{in prep.})).
 
@@
 However, both the updated limits in Kolopanis et al.
-(\textit{submitted}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
+(\textit{in prep.}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
 \item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
@@
 However, the analysis in this paper and in Kolopanis et al.
-(\textit{submitted}) does not average baselines into groups ($N_{\rm gps} = 1$).
+(\textit{in prep.}) does not average baselines into groups ($N_{\rm gps} = 1$).
 For the subset of data presented in this paper, $N_{\rm bls} = 10$.
@@
 Our revised PAPER-64 limits are presented in Kolopanis et al.
-(\textit{submitted}), which supersede all previously published PAPER limits.
+(\textit{in prep.}), which supersede all previously published PAPER limits.
 The main reasons for a previously under-estimated limit and

### 2018-06-20 plotting_scripts/plot_PS_invcov.py
latest plotting scripts

@@ -1,25 +1,33 @@
 #!/usr/bin/env python
-"""Create (pre-sigloss) 2 sigma upper limit plot.
+"""Create simple 2 sigma upper limit plot.
 
-Also plots 2 sigma EoR upper limit post-sigloss.
-Takes outputs from pspec_final_sepXXX_full.npz.
+Takes outputs from pspec_final_???.py and creates 2 sigma errorbar plots.
 """
-old_analytical = False
 import numpy as np
 import sys
 import os
 import argparse
 import py21cmsense as py21cm
 import capo
-from capo.cosmo_units import f212z
+from capo.cosmo_units import f212z, DM, E, ckm, Ho
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
-import itertools
+from capo import sensitivity
 
 parser = argparse.ArgumentParser(
     description=('Calculate power spectra for a run '
                  'from pspec_oqe_2d.py'))
+parser.add_argument('--noisefiles', type=str, nargs='*',
+                    help='supply 21cmSense files to plot sensitivity')
+parser.add_argument('--outfile', type=str, default='pspec_k3pk',
+                    help='give custom output file name')
+parser.add_argument('--Trcvr', type=float, default=144,
+                    help='Receiver Temperature in Kelvin (defualt 144)')
+parser.add_argument('--models', type=str,
+                    help=('a string that globs a list of 21cmfast pspec'
+                          ' output files'))
 args = parser.parse_args()
+
 
 files = ['plot_PS_invcov.npz']
 
@@ -33,10 +41,7 @@ for filename in files:
 zs = np.unique(zs)[::-1]
 Nzs = len(zs)
 # define some color format sets for the plotter
-# colors = ['r', 'g', 'k', 'b']
-markers = ['o', ',', 'd', '^', 's', 'v']
-# markers = itertools.cycle(markers)
-marker_count = [0 for i in xrange(Nzs)]
+marker = 'o'
 figsize = (5 * (1 + Nzs)/2., 6)
 
 # Create figure and prep subplot sizes for Delta^2
@@ -67,23 +72,46 @@ gs.update(hspace=0.0, wspace=0.2)
 ax4 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
 plt.subplots_adjust(left=0.2)
 
[…]

### 2018-06-20 plotting_scripts/plot_PS_reg.py

@@ -1,25 +1,33 @@
 #!/usr/bin/env python
-"""Create (pre-sigloss) 2 sigma upper limit plot.
+"""Create simple 2 sigma upper limit plot.
 
-Also plots 2 sigma EoR upper limit post-sigloss.
-Takes outputs from pspec_final_sepXXX_full.npz.
+Takes outputs from pspec_final_???.py and creates 2 sigma errorbar plots.
 """
-old_analytical = False
 import numpy as np
 import sys
 import os
 import argparse
 import py21cmsense as py21cm
 import capo
-from capo.cosmo_units import f212z
+from capo.cosmo_units import f212z, DM, E, ckm, Ho
 import matplotlib.pyplot as plt
 from matplotlib import gridspec
-import itertools
+from capo import sensitivity
 
 parser = argparse.ArgumentParser(
     description=('Calculate power spectra for a run '
                  'from pspec_oqe_2d.py'))
+parser.add_argument('--noisefiles', type=str, nargs='*',
+                    help='supply 21cmSense files to plot sensitivity')
+parser.add_argument('--outfile', type=str, default='pspec_k3pk',
+                    help='give custom output file name')
+parser.add_argument('--Trcvr', type=float, default=144,
+                    help='Receiver Temperature in Kelvin (defualt 144)')
+parser.add_argument('--models', type=str,
+                    help=('a string that globs a list of 21cmfast pspec'
+                          ' output files'))
 args = parser.parse_args()
+
 
 files = ['plot_PS_reg.npz']
 
@@ -33,10 +41,7 @@ for filename in files:
 zs = np.unique(zs)[::-1]
 Nzs = len(zs)
 # define some color format sets for the plotter
-# colors = ['r', 'g', 'k', 'b']
-markers = ['o', ',', 'd', '^', 's', 'v']
-# markers = itertools.cycle(markers)
-marker_count = [0 for i in xrange(Nzs)]
+marker = 'o'
 figsize = (5 * (1 + Nzs)/2., 6)
 
 # Create figure and prep subplot sizes for Delta^2
@@ -67,23 +72,46 @@ gs.update(hspace=0.0, wspace=0.2)
 ax4 = [plt.subplot(gs[:, i]) for i in range(Nzs)]
 plt.subplots_adjust(left=0.2)
 
[…]

### 2018-06-20 plotting_scripts/plot_bootmethods.py

@@ -7,12 +7,14 @@ import matplotlib.pyplot as plt
 boot_bl = n.load('plot_bootmethods.npz')
 boot_time = n.load('plot_bootmethods_time.npz')
 
-noise = 2827408.41233 #4436767.36822 # XXX
+noise = 14419782.9029 # subset (10 baselines)
+#2827408.41233 # all-cross
+#4436767.36822 # all baselines, 5 groups
 
 # Plot
-plt.plot(boot_bl['kpl'], boot_bl['pIn_err_old']*2, color='black', linewidth=2, label='Bootstrap baselines only')
-plt.plot(boot_time['kpl'], boot_time['pIn_err_old']*2, color='0.5', linewidth=2, label='Bootstrap baselines and times')
-plt.axhline(y=noise*2, color='green', linestyle='-', linewidth=2, label='Analytic')
+plt.plot(boot_bl['kpl'], boot_bl['pIn_err_old']*2, color='black', linewidth=3, label='Bootstrap baselines only')
+plt.plot(boot_time['kpl'], boot_time['pIn_err_old']*2, color='0.5', linewidth=3, label='Bootstrap baselines and times')
+plt.axhline(y=noise*2, color='green', linestyle='-', linewidth=3)
 plt.legend(numpoints=1,prop={'size':14},loc='best')
 plt.grid()
 plt.yscale('log')
@@ -21,7 +23,7 @@ plt.xlabel('$k_{\\parallel}$ [$h$ Mpc$^{-1}$]',fontsize=18)
 plt.ylabel('$P(k)$ [mK$^{2}$($h^{-1}$ Mpc)$^{3}$]',fontsize=18)
 plt.tick_params(axis='both', which='major', labelsize=14)
 #plt.ylim(1e6,7e9) # for data
-plt.ylim(5e5,1e8)
+plt.ylim(3e6,3e8)
 plt.show()
 
 

### 2018-06-20 plotting_scripts/plot_jackknives.py

@@ -28,15 +28,15 @@ mask = n.ma.masked_where(mask==0, mask)
 horizon = 0.06272882578029243 # computed using hera_pspec.conversions.Cosmo_Conversions.tau_to_kpara
 
 # Plot range
-ymin=-0.7e9
-ymax=0.7e9
+ymin=-6e9
+ymax=6e9
 
 #------------------------
 
 # LST null test
-noise_lst = n.sqrt(2*5190369.42535**2) # 1-sigma noise added in quadrature (sqrt(n^2 + n^2))
+noise_lst = n.sqrt(12126854.2805**2 + 26470884.0693**2) # 1-sigma noise added in quadrature (the noise differs for lst_1 and lst_2)
 p.figure()
-p.errorbar(file_lst_diff['kpl']*mask,file_lst_diff['pIv_old']*mask,n.sqrt(file_lst_1['pIv_err_old']**2 + file_lst_2['pIv_err_old']**2)*2*mask,linestyle='',marker='.',color='k')#,label='LST Null Test')
+p.errorbar(file_lst_diff['kpl']*mask,file_lst_diff['pIv_old']*mask,n.sqrt(file_lst_1['pIv_err_old']**2 + file_lst_2['pIv_err_old']**2)*2*mask,linestyle='',marker='.',color='k',linewidth=2)#,label='LST Null Test')
 #p.errorbar(file_lst_1['kpl']-0.005,file_lst_1['pIv_old'],file_lst_1['pIv_err_old']*2,linestyle='',marker='.',color='k',label='LST1')
 #p.errorbar(file_lst_2['kpl']+0.005,file_lst_2['pIv_old'],file_lst_2['pIv_err_old']*2,linestyle='',marker='.',color='0.5',label='LST2')
 p.axvline(x=horizon,color='k',linestyle='--')
@@ -52,9 +52,9 @@ p.grid()
 p.title('Null Test: LST',fontsize=18)
 
 # Baselines null test
-noise_bl = n.sqrt(2*5546070.34727**2)
+noise_bl = n.sqrt(2*28839565.8058**2) # 1-sigma noise added in quadrature (sqrt(x^2 + x^2)) where the noise is the same for each half
 p.figure()
[…]

### 2018-06-20 plotting_scripts/plot_sigloss.py

@@ -8,9 +8,9 @@ from scipy import stats
 # Read file and get data
 file = n.load('plot_sigloss.npz')
 k = file['k']
-xs = 10**file['xs']
-ys = 10**n.abs(file['ys'])*n.sign(file['ys'])
-ysI = 10**n.abs(file['ysI'])*n.sign(file['ysI'])
+xs = file['xs']
+ys = file['ys']
+ysI = file['ysI']
 M = file['kdeC']
 M_I = file['kdeI']
 pC = file['pC']
@@ -101,7 +101,7 @@ pkhi=1e11#1e13
 plt.figure(figsize=(12,6))
 plt.subplot(121)
 plt.plot(xs,ys,'k.')
-plt.pcolormesh(10**binsx,binsy_full,n.log10(M),cmap='hot_r',vmin=0,vmax=15)
+plt.pcolormesh(10**binsx,binsy_full,M,cmap='hot_r',vmin=0,vmax=0.04)
 plt.plot([pklo, pkhi], [pklo, pkhi], 'k:')  # diagonal line
 plt.plot([pklo, pkhi], [-pklo,-pkhi], 'k:')  # diagonal line
 #plt.hlines(y=n.abs(file_pts[k_pts_ind]),xmin=pklo,xmax=pkhi,color='0.5',linewidth=3) # peak of original distribution
@@ -123,7 +123,7 @@ plt.subplot(122)
 #plt.hlines(y=file_pts_I[k_pts_ind],xmin=pklo,xmax=pkhi,color='0.5',linewidth=3)
 plt.hlines(y=pI,xmin=pklo,xmax=pkhi,color='0.5',linewidth=3)
 plt.plot(xs,ysI,'k.')
-plt.pcolormesh(10**binsx,binsy_full,n.log10(M_I),cmap='hot_r',vmin=0,vmax=15)
+plt.pcolormesh(10**binsx,binsy_full,M_I,cmap='hot_r',vmin=0,vmax=0.04)
 plt.plot([pklo, pkhi], [pklo, pkhi], 'k:')  # diagonal line
 plt.plot([pklo, pkhi], [-pklo,-pkhi], 'k:')  # diagonal line
 plt.yscale('symlog',linthreshy=1e2)

### 2018-06-20 plotting_scripts/plot_sigloss_modeloop.py

@@ -28,26 +28,33 @@ if True: # added identity parameters in LOG space
     loop_add = n.logspace(startmode_add,endmode_add,nmodes_add)
 
 # Read files
-sense=4436767.36822*2 # XXX from plotting one of the "project_#_modes" directories
+sense=14419782.9029*2 / n.sqrt(2) # XXX from plotting one of the "project_#_modes" directories (divide by sqrt(2) for folded case)
+#sense=14419782.9029*2  # unfolded version
 PS_i_up = []
 PS_f_up = []
 PS_i = []
 PS_f = []
 k_ind = -3
 
+# Read in range of projected eigenmodes
 for mode_num in loop:
     filename = path + f1 + str(mode_num) + f2
     print 'Reading', filename
     print mode_num
     f = n.load(filename+'/pspec_final_sep0,1_full.npz')
-    kpl = f['kpl']
+    kpl = f['kpl_fold'] # folded version
+    #kpl = f['kpl'] # unfolded version
     k = kpl[k_ind] 
-    PS_i_up.append(2*n.array(f['pCv_err_old'])[k_ind])
-    PS_f_up.append(2*n.array(f['pCv_err'])[k_ind])
-    PS_i.append(n.abs(f['pCv_old'])[k_ind])
-    PS_f.append(n.abs(f['pCv'])[k_ind])
+    PS_i_up.append(2*n.array(f['pCv_fold_err_old'])[k_ind]) # folded version
+    PS_f_up.append(2*n.array(f['pCv_fold_err'])[k_ind])
+    PS_i.append(n.abs(f['pCv_fold_old'])[k_ind])
+    PS_f.append(n.abs(f['pCv_fold'])[k_ind])
+    #PS_i_up.append(2*n.array(f['pCv_err_old'])[k_ind]) # unfolded version
+    #PS_f_up.append(2*n.array(f['pCv_err'])[k_ind])
+    #PS_i.append(n.abs(f['pCv_old'])[k_ind])
+    #PS_f.append(n.abs(f['pCv'])[k_ind])
 
-#""" # Read in added identity case as a second curve being plotted
+# Read in added identity case as a second curve being plotted
 PS_i_up_add = []
 PS_f_up_add = []
 PS_i_add = []
@@ -57,13 +64,18 @@ for mode_num in loop_add:
     print 'Reading', filename
[…]

### 2018-06-20 plotting_scripts/plot_sigloss_terms.py

@@ -21,6 +21,15 @@ pCrs = n.array(file['pCrs_fold']).flatten()[ind][ind2]
 pCv = file['pCv'] # final PS points per k
 pIv = file['pIv'] 
 
+# XXX hack to get rid of occasional positive cross-term point when it should really be all negative
+ind_region = n.where(n.logical_and(Pins<1e9,Pins>1e7))[0]
+ind_mask = n.where(pCves[ind_region] > 0)[0]
+if len(ind_mask) > 0:
+    print "Found",len(ind_mask),"cross-term data points in positive regime when they should really be negative... masking them out!!!"
+    mask = n.zeros_like(pCves)
+    mask[ind_region[0] + ind_mask] = 1
+    pCves = n.ma.masked_array(pCves,mask)
+
 # Smooth curves
 poly_dim = 4
 #"""
@@ -28,7 +37,8 @@ poly_dim = 4
 poly_data_Cr = n.polyfit(n.log10(n.abs(Pins)),n.log10(n.abs(pCvs_Cr)),poly_dim)
 blue = 10**n.polyval(poly_data_Cr,n.log10(Pins))
 
-red_ind_pos = n.where(pCves>=0)[0] # where positive pCves
+try: red_ind_pos = n.ma.where(pCves>=0)[0] # where positive pCves
+except: red_ind_pos = n.where(pCves>=0)[0]
 red_ind_neg = n.where(pCves<0)[0] # where negative pCves
 Pins_red_pos = Pins[red_ind_pos] # adjust Pins
 Pins_red_neg = Pins[red_ind_neg]
@@ -64,12 +74,12 @@ black_neg = -10**n.polyval(poly_Pouts_neg,n.log10(Pins_black_neg))
 black_pos = 10**n.polyval(poly_Pouts_pos,n.log10(Pins_black_pos))
 
 black_ind_pos_I = n.where(Pouts_I>=0)[0] # where positive Pouts_I
-black_ind_neg_I = n.where(Pouts_I<0)[0] # where negative Pouts_I
+black_ind_neg_I = n.where(Pouts_I<0)[0][:-1] # where negative Pouts_I # XXX remove last entry (outlier in some cases that cause the curve to look weird)
[…]

### 2018-06-21 PAPER.tex
read through up until 2.2, corrected minor syntax stuff and also added new summary bullet point

@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization Power Spectrum}
+\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21\,cm Reionization Power Spectrum}
 \shortauthors{Cheng et al.}
@@
 develop techniques that help maximize sensitivity while validating results. Additionally, it is imperative to understand the trade-offs 
-between different methods and their effects on power spectrum estimates. In this paper, we focus on three major 
+between different analysis methods and their effects on power spectrum estimates. In this paper, we focus on three major 
 themes --- signal loss, power spectrum error estimation, and bias in measurements. We describe techniques that affect 
@@
 of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. 21\,cm tomography offers a unique window into the 
+stretching out as it traveled through expanding space. Hence, 21\,cm tomography offers a unique window into both the spatial and temporal
 evolution of ionization, temperature, and density fluctuations.
@@
 case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of the PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
+In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
 (\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
@@
 
-This paper is organized into two main halves. In Section \ref{sec:Themes} we introduce the three themes of our focus, using a 
-toy model to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
-from the PAPER-64 array, highlighting key changes from the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a 
+This paper is organized into two main halves. In Section \ref{sec:Themes} we introduce the three themes of our focus, using 
+toy models to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
+from the PAPER-64 array, highlighting key changes from the methods used in the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a
 revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{in prep.})). We conclude in Section \ref{sec:Con}.
@@
 measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
-successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for 21\,cm 
+successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for future 21\,cm 
 analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
-we will highlight some sources of bias, discuss ways to mitigate their effects, and describe tests that a true EoR detection must 
+we will highlight some sources of bias, discuss ways to mitigate their effects, and describe example tests that a true EoR detection must 
 pass.
@@
 However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two has large impacts on signal loss.
+weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two can have large impacts on signal loss.
 We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
@@
 In the next three subsections, we study each theme in depth, focusing on how power spectrum technique trade-offs affect each. 
-We use a toy data model to develop intuition into why certain analysis choices may be appealing and discuss ways in which 
+We use toy data models to develop intuition into why certain analysis choices may be appealing and discuss ways in which 
 they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
@@
 
-Signal loss can arise in a variety of ways in the analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay-domain filter, or deriving weights from data and applying them to itself.
+Signal loss can arise in a variety of ways in an analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay domain filter, or deriving weights from data and applying them to itself.
 Here we focus on signal loss associated with
@@
 \end{equation}
-where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as a sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
+where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as the sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
 
@@
 \label{eq:super_unbiased}
-\langle \widehat{p}^{\alpha} \rangle = p^\alpha.
-\end{equation}
-\citep{tegmark_et_al1997a,bond_et_al1998}
+\langle \widehat{p}^{\alpha} \rangle = p^\alpha
+\end{equation}
+\citep{tegmark_et_al1997a,bond_et_al1998}.
 
@@
 For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p^\alpha$ but in practice also does other things, including implementing a transform of the frequency-domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.
 
@@
 
-\item If the covariance matrix is estimated from the data, the strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
+\item If the covariance matrix is estimated from the data, a strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
 In this context, this is what we call ``signal loss''  (Section \ref{sec:toymodel}).
@@
 
-\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
+\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate, the number of realizations in the estimate, and the steepness of the empirical eigenspectrum (Section \ref{sec:toymodel_frf}).
+In general, larger sample variances, fewer realizations, and flatter eigenspectra lead to more loss.
+
+%\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
 Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable (Section \ref{sec:toymodel_frf}).
 
-\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
+\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to decouple it from the data and produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
 
@@
 	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The power spectrum of foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the first eigenmode only (right).
+The power spectrum of the foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
+In the two panels, we compare using empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the zeroth eigenmode only (right).
 In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
@@
 can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
-project out the first eigenmode and 
+project out the zeroth eigenmode and 
 %then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
@@
 Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization.
-There are several other ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
+There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
 \ref{sec:otherweight}.
@@
 We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
-As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and the number of independent samples in the data following fringe-rate filtering (different colors).
+As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following fringe-rate filtering (different colors).
 With more independent time samples (i.e.
@@
 %Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-\cc{start of carina edits}The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
+The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
 This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
-For this simulation, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
+For this particular toy model, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
 For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance by averaging over the realizations.
@@
 However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
-Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to de-couple from each other and approach their true forms.
+Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to decouple from each other and approach their true forms.
 A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate.
@@
 Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
-However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.
+However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
 
@@
 	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
-	\caption{Our `fringe-rate filtered' (time-averaged) toy model dataset. We average every four samples together, 
+	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
 yielding $25$ independent samples in time. Real parts are shown here.}
@@
 	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.pdf}
-	\caption{The convergence level, as defined in Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
+	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
 In red, the mock EoR signal is comprised entirely of independent samples.
@@
 As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges, and the less signal loss we would expect to result.}
+With more independent samples, the quicker an empirical covariance converges (i.e.
+the quicker it decouples from the data), and the less signal loss we would expect to result.}
 	\label{fig:toy_sigloss16}
@@
 	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
-	\caption{The convergence level, as defined in Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
+	\caption{The convergence level, as defined by Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
 The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the 0th eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (i.e.
-the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
+This figure shows that the zeroth eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
 On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
-	\caption{Resulting power spectrum estimate for the `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
+	\caption{Resulting power spectrum estimate for the ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
 EoR only (red), and the weighted FG + EoR dataset (green). We use empirically estimated inverse covariance weighting where $\textbf{C}$ is 
@@
 With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our fringe-rate filtered toy model.
-\cc{end of carina edits}The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as
+The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as
 expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
@@
 This is evident by noticing that the
-green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum.
+green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
 
@@
 %This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we don't know how to separate out the foregrounds from the EoR in our data.
+In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.
 
@@
 The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
-by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the first eigenmode, this 
+by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this 
 method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
 eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominated modes which are coupled to the data results in negligible signal loss. However, we do 
-not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most modes.
+not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most of the modes.
 While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
@@
 suppressing the foreground.
-But because we de-coupled the whole eigenspectrum from the data, we also avoid signal loss.
+But because we decoupled the whole eigenspectrum from the data, we also avoid signal loss.
 Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
@@
 	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
-Stokes I polarization beam. Bottom: the time-domain convolution kernel corresponding to the top panel. Real and imaginary 
+Stokes I polarization beam. Bottom: the time domain convolution kernel corresponding to the top panel. Real and imaginary 
 components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black. The fringe-rate filter acts as 

### 2018-06-21 PAPER.tex
small edits until section 2.3, added gianni's acknowledgements

@@
 
-\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate, the number of realizations in the estimate, and the steepness of the empirical eigenspectrum (Section \ref{sec:toymodel_frf}).
-In general, larger sample variances, fewer realizations, and flatter eigenspectra lead to more loss.
+\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness of the empirical eigenspectrum (Section \ref{sec:toymodel_frf}).
+In general, larger sample variances and flatter eigenspectra lead to more loss.
 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our `fringe-rate filtered' (time-averaged) toy model simulation --- foregrounds only (blue), 
+	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
 EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each minimize signal 
@@
 independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
-earlier (drawing $N$=$1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N$=$1000$). This occurs 
+earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$). This occurs 
 because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
@@
 under-estimate the error by drawing too many or over-estimate it by drawing too few. However, since we know that we have $100$ 
-independent samples in this toy model, the error associated with drawing $N$=$100$ samples with replacement does match the theoretical prediction 
-as expected (the black points cross the green line at $N$=$100$ in Figure \ref{fig:toy_error1}).
-
-This example highlights the importance of understanding how analysis techniques (e.g. fringe-rate filtering) can affect a 
+independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction 
+as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
+
+This example highlights the importance of understanding how analysis techniques (such as fringe-rate filtering) can affect a 
 common statistical procedure like bootstrapping. Bootstrapping as a means of estimating power spectrum errors from real 
@@
 AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
+GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184.
+This work is based on research supported in part by the National Research Foundation of South Africa (award 103424).
 We graciously thank SKA-SA for site infrastructure and observing support.

### 2018-06-21 PAPER.tex
minor edits until section 3

@@
 \item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
-investigate underlying systematics (e.g., see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
+investigate underlying systematics (see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
 divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
@@
 	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
-the presence of a systematic in $\textbf{x}_{2}$ only (which is exactly what was put in), illustrating how jackknives can be used to tease out excesses. Clean 
+the presence of a systematic in $\textbf{x}_{2}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
 measurements should remain consistent despite the jackknife taken.}
@@
 In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum 
-detection. In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to prove that our 
+detection. In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to show that our 
 excesses are not EoR and to identify their likely cause.

### 2018-06-21 PAPER.tex
small edits until 3.2

@@
 
-\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness of the empirical eigenspectrum (Section \ref{sec:toymodel_frf}).
-In general, larger sample variances and flatter eigenspectra lead to more loss.
+\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness (the degeneracy) of the empirical eigenspectrum.
+In general, larger sample variances and flatter eigenspectra (more degeneracies) lead to more loss (Section \ref{sec:toymodel_frf}).
 
@@
 We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
-\citetalias{ali_et_al2015}) in order to illustrate our revised analysis pipeline.
+\citetalias{ali_et_al2015} in order to illustrate our revised analysis pipeline.
 
@@
 \noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$.
-The need to revise this limit stems from previously under-estimated signal loss and under-estimated error bars, both of which we
+The need to revise this limit stems mostly from previously under-estimated signal loss and under-estimated error bars, both of which we
 address in the following sections.
@@
 range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
-We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}.
+We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}, in order to illustrate our revised methods.
 All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
 In the case study in this paper, we only use one baseline type instead of the three as in
-\citetalias{ali_et_al2015}, but Kolopanis et al. (\textit{in prep.}) uses all baselines presented in \citetalias{ali_et_al2015}.
+\citetalias{ali_et_al2015}, but Kolopanis et al.
+(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts.
 
@@
 applied filter was not equivalent to the optimal fringe-rate filter (which is designed to maximize power spectrum sensitivity).
-Instead, the optimal filter was degraded by widening it in fringe-rate space.
+Instead, the optimal filter was degraded slightly by widening it in fringe-rate space.
 This was chosen in order to increase the number of independent
@@
 To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants.
-Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
+Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
 Therefore, $\widehat{P}_{\rm out}$ can be directly compared to the measurement that we make.
@@
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} %\nonumber \\
+&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
+%\nonumber \\
 %&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 ^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
+&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}. %\nonumber \\
 %&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
@@
 Here only does the signal-only term used in  \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the estimated inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
+We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
 This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
-	\caption{Illustration of the power spectrum amplitude of various power spectrum terms as a function of injected EoR power level summed into the 
+	\caption{Illustration of the power spectrum amplitude of different power spectrum terms as a function of injected EoR power level summed into the 
 data.
@@
 term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect
+However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect
 $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data-only power spectrum value) and the black curve (which exhibits $\sim$$4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
+the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
 	\label{fig:sigloss_terms}
@@
 Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
+Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars from bootstrapping, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
 We elaborate on this point in the next section, as well as investigate alternate
@@
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.}
+Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
+In this example, we see that the lossy power spectrum limit is $\sim 4$ orders of magnitude too low when using empirical inverse covariance weighting.}
 \label{fig:ps2_data}
@@
 We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
-eigenspectrum and effectively de-coupling the lowest-valued eigenmodes from the data, which converge to the true eigenspectrum the slowest and are often EoR-dominated) can help minimize signal loss.
+eigenspectrum and effectively decoupling the lowest-valued eigenmodes, which are typically EoR-dominated, from the data) can help minimize signal loss.
 We experiment with this idea on PAPER-64 data, dialing the number of modes
@@
 
-Optimistically, we expect there to be a `sweet spot' as we dial our regularization knob; a level of regularization where weighting 
+Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
 is beneficial compared to uniform weighting (blue).
@@
 only the $\sim2$-$3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting does not actually outperform uniform weighting).
-For a similar discussion on projecting out modes (zero-ing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
+For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
 
@@
 We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
+The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as a percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
 We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
@@
 We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
-We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear `minimum' that produces the least loss.
+We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear ``minimum" that produces the least loss.
 
@@
 covariance estimator).
-Over $\sim3$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
+$\sim4$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
 Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
@@
 
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
+The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
 \ref{fig:ps1_data}.
@@
 The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
-$2\sigma$ errors bars).
+$2\sigma$ errors bars from bootstrapping).
 It is also shown as an upper limit using the signal injection framework (solid blue), which is interestingly larger than the errors computed from bootstrapping, likely because the full injection framework takes into account additional sample variance whereas the bootstrapped errors do not.
-Finally, the gray shaded regions combine the measured uniform weighted power spectrum values and the thermal noise.
-We show this power spectrum result as one example of how a simple regularization can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
+Finally, the gray shaded regions combine the measured uniform weighted power spectrum values with thermal noise errors.
+We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
 
@@
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
@@
 (\textit{in prep.}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
-loss, bootstrapping, and the theoretical error computation.}
+loss, bootstrapping, and the theoretical error computation. We see that the regularization scheme used here produces limits similar to the unweighted limits.}
 	\label{fig:ps1_data}
@@
 data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
-$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this could mean calculating $
+$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this might mean calculating $
 \widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$\,m diagonal PAPER baselines (instead of the 
-horizontal E/W ones). Alternately, covariances could be estimated from all other baselines except the two being cross-multiplied 
+horizontal E/W ones). Alternatively, covariances could be estimated from all baselines except the two being cross-multiplied 
 when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
@@
 Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the `foreground-quiet' range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
+calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
 down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.

### 2018-06-21 PAPER.tex
small edits until 3.3

@@
 
-The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} uses $124$ nights of data to place a $2\sigma$ upper limit 
+The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} placed a $2\sigma$ upper limit 
 on $\Delta^{2}(k)$, defined as
@@
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
@@
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
@@
 Although a theoretical model often
-differs from true errors as explained in Section \ref{sec:ErrorOverview}, it is helpful to understand the ideal case and the factors 
+differs from true errors, it is helpful to understand the ideal case and the factors 
 that affect its sensitivity. Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to 
@@
 where $\nu$ are frequencies in GHz (\citealt{thompson_et_al2001}). We use a receiver temperature of $144$\,K, yielding $T_{\rm sys} = 431$\,K at $150$\,MHz. 
-This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small mis-calculation errors that were 
+This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
 identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
@@
 However, the analysis in this paper and in Kolopanis et al.
-(\textit{in prep.}) does not average baselines into groups ($N_{\rm gps} = 1$).
+(\textit{in prep.}) no longer averages baselines into groups ($N_{\rm gps} = 1$).
 For the subset of data presented in this paper, $N_{\rm bls} = 10$.
@@
 
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s.
+An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s to form $\Delta^{2}(k)$.
 
@@
 	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray), both computed for the analysis methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
+published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
 \Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
@@
 
-\noindent where $\Delta\nu$ is channel spacing, $\Delta t$ is integration time, $N_{\rm days}$ is the number of daily counts for a 
+\noindent where $\Delta\nu$ is the channel spacing, $\Delta t$ is the integration time, $N_{\rm days}$ is the number of daily counts for a 
 particular time and frequency that went into our LST-binned set, and $N_{\rm pols}$ is the number of polarizations ($2$ for Stokes 
@@
 The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
-Additionally, the power spectrum results for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
+Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
 The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
@@
 \end{itemize}
+
+In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
+Additionally, we have carried out substantial testing with these changes in place to verify that the computed errors for our noise simulations are accurate and agree with thermal noise predictions.
 
@@
 detections and imitate an EoR signal. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
-detection, as well as identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
+detection, as well as for identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
 foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.

### 2018-06-21 PAPER.tex
small edits until appendices

@@
 \begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances (Section 
+\item Substantial signal loss can result when weighting data using empirically estimated covariances due to couplings with the data realizations (Section 
 \ref{sec:SiglossOverview}). Loss of the 21\,cm signal is especially significant the fewer number of independent modes that
@@
 signal-only simulation (i.e. comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
-failing to account for correlations between the data and signal (Section \ref{sec:siglossmethod}).
+failing to account for correlations between the data and signal which can be large and negative (Section \ref{sec:siglossmethod}).
 \item Errors that are estimated via bootstrapping can be under-estimated if samples in the dataset are significantly correlated 
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for empirically estimated inverse 
+\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
 covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
-\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, our results are still a 
-factor of $\sim10$ in mK higher than the lossy empirical inverse covariance limits. Under-estimated signal loss therefore represents the bulk of our revision. 
+\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
+Under-estimated signal loss therefore represents the bulk of our revision.
 This revision is similar in nature to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
@@
 also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
+AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
 SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
@@
 award 1701536.
-AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
 GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184.

### 2018-06-22 PAPER.tex
small edits up until the end of the paper. Changed all i.e.'s to i.e.,'s

@@
 %then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e.
-only allowing over-fitting to occur for the first mode).
+Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e., only allowing over-fitting to occur for the first mode).
 then take the remaining covariance to be the identity matrix.  
@@
 As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following fringe-rate filtering (different colors).
-With more independent time samples (i.e.
-more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
+With more independent time samples (i.e., more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
 
@@
 As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges (i.e.
-the quicker it decouples from the data), and the less signal loss we would expect to result.}
+With more independent samples, the quicker an empirical covariance converges (i.e., the quicker it decouples from the data), and the less signal loss we would expect to result.}
 	\label{fig:toy_sigloss16}
@@
 avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e. the identity), instead of computing it based on $\textbf{x}
+variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
 _{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
@@
 
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e.
-keeping only the diagonal elements of $\widehat{\textbf{C}}$).
+The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
 In the bottom right
@@
 of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
-from the original set of measurements with replacement (i.e. every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
+from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
 the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
@@
 %	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
-%dataset (i.e. if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
+%dataset (i.e., if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
 %elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
@@
 
-The jackknife is a resampling technique in which a statistic (i.e. power spectrum) is computed in subsets of the data (\citealt{quenouille1949}; \citealt{tukey1958}). These 
+The jackknife is a resampling technique in which a statistic (i.e., power spectrum) is computed in subsets of the data (\citealt{quenouille1949}; \citealt{tukey1958}). These 
 subsets are then compared to reveal systematics. In this section we define two main tests --- the null test and the traditional 
@@
 spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
-from one of the data subsets to the other (i.e. doesn't get subtracted perfectly). 
+from one of the data subsets to the other (i.e., doesn't get subtracted perfectly). 
 \item \textbf{Traditional Jackknife}: In a broader sense, it is important to perform many jackknife tests in order to instill 
@@
 	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
-paper (i.e. a subset of the shortest horizontal spacings).}
+paper (i.e., a subset of the shortest horizontal spacings).}
 	\label{fig:ant_layout}
@@
 
-%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e.
-the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
+%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e., the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
 In other words, we make the anzatz that
@@
 be neglected as many orders of magnitude smaller.
-We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e.
-in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
+We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e., in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
 However, it is useful as a check of our system in a relatively simple case.
@@
 When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
-the weighted injected power spectrum component mirrors the input power indicating little loss (i.e. the green curve follows the dotted black line), eventually 
+the weighted injected power spectrum component mirrors the input power indicating little loss (i.e., the green curve follows the dotted black line), eventually 
 departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
@@
 
-\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e.
-the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
+\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e., the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
 Without loss of generality, we will assume
@@
 One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e.
-how much coupling there is, which affects how much loss results).
+A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e., how much coupling there is, which affects how much loss results).
 
@@
 
-We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e. flattening out part of the 
+We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e., flattening out part of the 
 eigenspectrum and effectively decoupling the lowest-valued eigenmodes, which are typically EoR-dominated, from the data) can help minimize signal loss.
@@
 are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. the full inverse 
+are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e., unweighted) to $21$ modes on the right (i.e., the full inverse 
 covariance estimator).
@@
 Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e.
-very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
+This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e., very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
 Also
@@
 We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e.
-when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
+their best (i.e., when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
@@
 (\textit{in prep.}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
-\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e. a 
+\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e., a 
 fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
@@
 In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e.
-the power spectrum).
+On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
 This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
@@
 Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
-We then difference them (i.e.
-the null test) to tease out excess variances.
+We then difference them (i.e., the null test) to tease out excess variances.
 
@@
 In addition, all three null tests show error bars consistent with the thermal noise level for those same $k$'s.
-This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e.
-the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
+This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e., the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
 We deem these as ``passing" null tests for the specific jackknives taken (again, dividing up the data in a different way along the same axes may not yield the same results, so more thorough testing is needed to be sure).
@@
 This is the case for the LST null test at $k\sim-0.15$\,$h$ Mpc$^{-1}$ and $k\sim-0.2$\,$h$ Mpc$^{-1}$.
-In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e.
-the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
+In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e., the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
 This result implies that there exists a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
@@
 \item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
-signal-only simulation (i.e. comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
+signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
 failing to account for correlations between the data and signal which can be large and negative (Section \ref{sec:siglossmethod}).
@@
 This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.
-This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e.
-quadratic) statistics \citep{liu_tegmark2011}.
+This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{liu_tegmark2011}.
 The result is an improperly normalized---and thus lossy---power spectrum estimate.
@@
 
-Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to 0.
+Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
 Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
@@
 When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
-For the injections that we do sample, we can easily fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
+For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
 An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
@@
 	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final} (black).
-We smooth the prior using a sliding boxcar average over every $5$ injections (red).
+We smooth the prior using a sliding boxcar average over every $5$ injection levels (red).
 Most noticeably, the Jeffreys prior is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
@@
 This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $\widehat{\textbf{P}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e.
-data only) and very large levels are dominated by the injected signal.
+In the 2D space relating total $\widehat{\textbf{P}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e., data only) and very large levels are dominated by the injected signal.
 It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross-correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
@@
 ?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
-One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e.
-the null test) the same.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e., the null test) the same.
  \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by

### 2018-06-22 PAPER.tex
changed p_alpha's to capital P's

@@
 Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
-We consider band powers $p_\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-The fundamental dependence of the covariance on the power spectrum band powers $p_\alpha$ is encoded as
+We consider band powers $P^\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
+The fundamental dependence of the covariance on the power spectrum band powers $P^\alpha$ is encoded as
 % JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
 \begin{equation}
-\textbf{S} = \sum_\alpha p^\alpha \frac{\partial\textbf{C}}{\partial p^\alpha} \equiv \sum_\alpha p^\alpha \textbf{Q}^\alpha
+\textbf{S} = \sum_\alpha P^\alpha \frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \sum_\alpha P^\alpha \textbf{Q}^\alpha
 %\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
@@
 \end{equation}
-where we define $\frac{\partial\textbf{C}}{\partial p^\alpha} \equiv \textbf{Q}^{\alpha}$.
+where we define $\frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \textbf{Q}^{\alpha}$.
 % JEA - ah, the dimensions again
@@
 \label{eq:OQE}
-\widehat{p}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
+\widehat{P}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
 \end{equation}
@@
 \label{eq:super_unbiased}
-\langle \widehat{p}^{\alpha} \rangle = p^\alpha
+\langle \widehat{P}^{\alpha} \rangle = P^\alpha
 \end{equation}
@@
 For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial p^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial P^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 \begin{eqnarray}
-\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
-&\equiv & \sum_{\beta} W^{\alpha \beta} p^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
+\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
+&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
 \end{eqnarray}
@@
 \end{equation}
-Taking the ensemble average of both sides and noting that the true power spectrum $p_\alpha$ is equal to $\langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
-\begin{equation}
-\langle \widehat{P}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) p_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) p_\alpha,
+Taking the ensemble average of both sides and noting that the true power spectrum $P_\alpha$ is equal to $\langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
+\begin{equation}
+\langle \widehat{P}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) P_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) P_\alpha,
 \end{equation}
 where recall that $N_f$ is the length of $\x$, or the number of frequency channels.
-In the last step we dropped the final term, since it scales as $\eta p_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
-
-Recalling that $p_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
+In the last step we dropped the final term, since it scales as $\eta P_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
+
+Recalling that $P_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
 This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.

### 2018-06-22 PAPER.tex
changed subscript alpha's to superscripts in appendix B

@@
 
-The minimum-variance quadratic estimator $\widehat{P}_\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\begin{equation}
-\widehat{P}_\alpha = \frac{1} {2 \F_{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
+The minimum-variance quadratic estimator $\widehat{P}^\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
+\begin{equation}
+\widehat{P}^\alpha = \frac{1} {2 \F^{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
 \end{equation}
@@
 \begin{equation}
-F_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \right)
+F^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \right)
 \end{equation}
@@
 \label{eq:phatloss}
-\widehat{P}_\alpha^\textrm{loss} = \frac{1} {2 \widehat{\F}_{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
+\widehat{P}^\alpha_\textrm{loss} = \frac{1} {2 \widehat{\F}^{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
 \end{equation}
@@
 \begin{equation}
-\widehat{F}_{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
+\widehat{F}^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
 \end{equation}
@@
 
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{P}_\alpha^\textrm{loss}$ in terms of $\widehat{P}_\alpha$.
+Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{P}^\alpha_\textrm{loss}$ in terms of $\widehat{P}^\alpha$.
 We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
@@
 \begin{equation}
-\widehat{F}_{\alpha \alpha} = \frac{F_{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right],
-\end{equation}
-where $h_\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h_{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
-Note that $g$, $h_\alpha$, and $h_{\alpha \alpha}$ are all random variables, since they depend on $\x$.
+\widehat{F}^{\alpha \alpha} = \frac{F^{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^{\alpha})^2}{F^{\alpha \alpha}}\right],
+\end{equation}
+where $h^\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h^{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
+Note that $g$, $h^\alpha$, and $h^{\alpha \alpha}$ are all random variables, since they depend on $\x$.
 Inserting these expressions into our estimator gives
@@
 \label{eq:phatlossexpanded}
-\widehat{P}_\alpha^\textrm{loss} = \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{h_\alpha^2}{F_{\alpha \alpha}}\right]^{-1}.
+\widehat{P}^\alpha_\textrm{loss} = \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^\alpha)^2}{F^{\alpha \alpha}}\right]^{-1}.
 \end{equation}
@@
 \begin{equation}
-\widehat{P}_\alpha^\textrm{loss} \approx \frac{1}{2} \frac{h_\alpha}{F_{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h_{\alpha \alpha}}{F_{\alpha \alpha}}\right)\right].
-\end{equation}
-Taking the ensemble average of both sides and noting that the true power spectrum $P_\alpha$ is equal to $\langle h_\alpha \rangle / 2 F_{\alpha \alpha}$, we obtain
-\begin{equation}
-\langle \widehat{P}_\alpha^\textrm{loss} \rangle \approx (1- \eta N_f) P_\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) P_\alpha,
+\widehat{P}^\alpha_\textrm{loss} \approx \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}}\right)\right].
+\end{equation}
+Taking the ensemble average of both sides and noting that the true power spectrum $P^\alpha$ is equal to $\langle h^\alpha \rangle / 2 F^{\alpha \alpha}$, we obtain
+\begin{equation}
+\langle \widehat{P}^\alpha_\textrm{loss} \rangle \approx (1- \eta N_f) P^\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) P^\alpha,
 \end{equation}
 where recall that $N_f$ is the length of $\x$, or the number of frequency channels.
-In the last step we dropped the final term, since it scales as $\eta P_\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
-
-Recalling that $P_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
+In the last step we dropped the final term, since it scales as $\eta P^\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
+
+Recalling that $P^\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
 This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.
-This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{liu_tegmark2011}.
+This violates the assumptions implicit in the derivation of $F^{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{liu_tegmark2011}.
 The result is an improperly normalized---and thus lossy---power spectrum estimate.

### 2018-08-29 PAPER.tex
put half space for 21 cm in title
first pass at major re-structuring. No broken links.

@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21\,cm Reionization Power Spectrum}
+\shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
 \shortauthors{Cheng et al.}
@@
 \begin{document}
-\title{Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64}
+\title{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64}
 
@@
 galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the 21\,cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
-of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
-develop techniques that help maximize sensitivity while validating results. Additionally, it is imperative to understand the trade-offs 
-between different analysis methods and their effects on power spectrum estimates. In this paper, we focus on three major 
-themes --- signal loss, power spectrum error estimation, and bias in measurements. We describe techniques that affect 
-these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
-for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
-led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
-While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a companion paper by Kolopanis et al.
-(\textit{in prep.}) and supersede results from
-previously published PAPER analyses.
+EoR by tracing the 21\,cm line of neutral hydrogen.
+Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data.
+It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
+Specifically, with a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
+In this paper, we focus on signal loss specifically associated with quadratic estimators and power spectrum estimation.
+We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
+Backer Precision Array for Probing the Epoch of Reionization (PAPER).
+In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
+Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
+While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
+(\textit{in prep.}) and supersede results from previously published PAPER analyses.
 \end{abstract}
@@
 into a plasma, is known as the Epoch of Reionization (EoR).
-The EoR is a relatively unexplored era in our \textit{cosmic dawn}, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
-Its
-history encodes important information regarding the nature of the first galaxies and the processes of structure formation. 
+The EoR is a relatively unexplored era in our Universe's history, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
+This epoch encodes important information regarding the nature of the first galaxies and the processes of structure formation.
 Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
@@
 
-In addition to the first tentative detection of the EoR signal made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
+In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
 the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
-mean brightness temperature of the EoR relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
+mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
 Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
@@
 Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and is forecast to be able to make a high-significance power spectrum 
+learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
 detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).
@@
 instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
-With continual progress being made
-in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
-with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
-the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, error estimation, and bias) that are essential to investigate 
-for a robust 21\,cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
-pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
+A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often chosen to maximize sensitivity and minimize contaminants, affect power spectrum results.
+More specifically, it is imperative to develop techniques that ensure
+the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss may have resulted.
+In this paper, we discuss signal loss associated with specifically with power spectrum estimation --- a topic that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has been underestimated in previous PAPER analyses.
+We first approach this topic from a broad perspective, and then perform a detailed
 case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
+In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al.
 (\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
 
-Finally, this paper adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
+Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
+This paper adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
 These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
 
-This paper is organized into two main halves. In Section \ref{sec:Themes} we introduce the three themes of our focus, using 
-toy models to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
-from the PAPER-64 array, highlighting key changes from the methods used in the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a
-revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{in prep.})). We conclude in Section \ref{sec:Con}.
-
-% SECTION 2 INTRO ---------------------------------------------------------------------------------
-
-\section{Power Spectrum Themes and Techniques}
-\label{sec:Themes}
-
-There are many choices a 21\,cm data analyst must consider.
-%For PAPER, its grid configuration allows the use of many signal processing tricks to down-weight foregrounds without reference to a sky model.
-However, even with the advantage of being agnostic about the sky, many questions still remain.
-%, though the space is significantly constrained by 
-%the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
-%only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
-%down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
-%the sky. However, even within this problem sub-space, questions remain.
-How can time-ordered measurements be combined? How can the 
-variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
-destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
-averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
-example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
-some EoR signal. A chosen weighting scheme may theoretically maximize sensitivity but fail to suppress foregrounds in practice.
-
-Though there are many data analysis choices, measuring the statistical 21\,cm power spectrum ultimately requires robust 
-methods for determining accurate confidence intervals and rigorous techniques to identify and control systematics.  In this 
-paper, we focus on three 21\,cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
-with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
-follow.
-
-%\begin{center}
-%Power Spectrum Themes
-%\end{center}
-
-%A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power spectrum result.
-Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for a rigorous power spectrum analysis.
-\begin{itemize}
-\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
+This paper is organized into three main sections.
+In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
+In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss.
+In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis.
+Finally, we conclude in Section \ref{sec:Con}.
+
+% SECTION 2 SIGLOSS TOY MODEL ---------------------------------------------------------------------------------
+%\color{blue}
+
+\section{Signal Loss Toy Models}
+\label{sec:SiglossOverview}
+% JEA - We never totally nail down what ``signal loss'' is ...
+
+Signal loss refers to attenuation of the target \textit{cosmological} signal 
 in a power spectrum estimate.
@@
 Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
-\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
-determine the difference between a detection and a null result, which have two very different implications.
-Additionally, accurate error estimation is crucial for the comparison of results to theoretical models.
-Errors can be
-estimated in a variety of ways, and we will discuss a few of them.
-\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
-measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
-successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for future 21\,cm 
-analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
-we will highlight some sources of bias, discuss ways to mitigate their effects, and describe example tests that a true EoR detection must 
-pass.
-\end{itemize}
-
-%\begin{center}
-%Power Spectrum Techniques
-%\end{center}
-
-The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
-data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
-these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
-being standard steps in general 21\,cm analyses.
-\begin{itemize}
-\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
-(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
-independent samples. However, such a filter also affects the presence 
-of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
-\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
-weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
-weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
-Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
-However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two can have large impacts on signal loss.
-We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
-\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
-methods, bootstrapping is one way to estimate errors. Namely, bootstrapping is a useful method for estimating errors of a dataset from 
-itself (\citealt{andrae2010}). By randomly drawing many subsamples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
-consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
-\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
-dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
-systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g.
-\citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011b}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
-An EoR detection must pass both jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
-\end{itemize}
-
-In the next three subsections, we study each theme in depth, focusing on how power spectrum technique trade-offs affect each. 
-We use toy data models to develop intuition into why certain analysis choices may be appealing and discuss ways in which 
-they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
-Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be performed for robust 21\,cm results.
-
-% SECTION 2 SIGLOSS ---------------------------------------------------------------------------------
-%\color{blue}
-
-\subsection{Signal Loss}
-\label{sec:SiglossOverview}
-% JEA - We never totally nail down what ``signal loss'' is ...
 
@@
 % JEA - we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
-the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
+the latter.
+
+A dataset can be weighted to emphasize certain features and minimize others, and one particular flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
+Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
+However, a challenge of inverse covariance
+weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
+Here we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
 This loss was significantly 
 %applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-under-estimated in the \citetalias{ali_et_al2015} analysis.
+underestimated in the \citetalias{ali_et_al2015} analysis.
 
@@
 
-\subsubsection{The Quadratic Estimator Method}
+\subsection{The Quadratic Estimator Method}
 \label{sec:QE}
@@
 
+We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation.
 The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
@@
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-We provide a brief summary of the optimal quadratic estimator and explain its advantages below.
 
@@
 %We begin with our 
-The measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
+Suppose that the measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
 % JEA - not sure this helps
@@
 where we define $\frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \textbf{Q}^{\alpha}$.
+In other words, $\textbf{Q}$ describes the response of the covariance to a change in the power spectrum, relating a quadratic statistic of the data (the covariance) to a quadratic statistic in Fourier-space (the power spectrum).
 % JEA - ah, the dimensions again
@@
 \end{equation}
-where $\F$ is the Fisher matrix 
-\begin{equation}
-F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right)
-\end{equation}
-and
+where $\F$ is the Fisher matrix (which determines errors on the power spectrum estimate)
+\begin{equation}
+F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right),
+\end{equation}
+$\widehat{q}$ is the un-normalized power spectrum estimate
 \begin{equation}
 \label{eq:OQEQuadratic}
-\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x} 
-\end{equation}
-and
+\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x},
+\end{equation}
+and $\widehat{b}$ is the additive bias
 \begin{equation}
@@
 \end{equation}
-This estimator is the minimum variance (smallest error bar) estimate of the power spectrum  subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
+The power spectrum estimator in Equation \eqref{eq:OQE} is the minimum variance (smallest error bar) estimate of the power spectrum subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
 \begin{equation}
@@
 
-It is clear that in order to obtain an unbiased estimate in the presence of contaminants, the estimator defined by Equation \eqref{eq:OQE} must be capable of ``suppressing'' or ``removing'' their effects.
+Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminates in order to obtain an unbiased estimate of the power spectrum.
 By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
@@
 Beyond this, the data analyst has a choice for $
-\textbf{M}$. For simplicity in this section we choose $\textbf{M}$ to be diagonal, although we discuss other cases for the analysis 
-of PAPER-64 data as explained in Section \ref{sec:Bias}.
+\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal.
 In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
@@
 We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:Sigloss}.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:CaseStudy}.
 
@@
 
-\subsubsection{Toy Model: Inverse Covariance Weighting}
+\subsection{Inverse Covariance Weighting}
 \label{sec:toymodel}
@@
 
-\subsubsection{Toy Model: Fringe-Rate Filtering}
+\subsection{Fringe-Rate Filtering}
 \label{sec:toymodel_frf}
@@
 Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
-To mimic this filter, we average every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
-%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
+With fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
+We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
 
@@
 %The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}.
-With fringe-rate filtering resulting in fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
-We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
+
 \begin{equation}
@@
 We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
-As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following fringe-rate filtering (different colors).
+As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following time-averaging, or ``fringe-rate filtering" (different colors).
 With more independent time samples (i.e., more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
@@
 In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
-Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
+Even for the case of real PAPER data (Section \ref{sec:CaseStudy}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
 However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
@@
 %\acl{Think about whether we need to do the Fourier space version as well.}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
-	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here.}
-	\label{fig:toy_sigloss5}
-\end{figure}
 
@@
 	\centering
+	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
+	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
+yielding $25$ independent samples in time. Real parts are shown here.}
+	\label{fig:toy_sigloss5}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
@@
 
-With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our fringe-rate filtered toy model.
+With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal.
+We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
+We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
+%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
+
 The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
@@
 green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
+It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
+This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
 
@@
 
-\subsubsection{Toy Model: Other Weighting Options}
+\subsection{Other Weighting Options}
 \label{sec:otherweight}
@@
 _{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
-\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}$ to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
+\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would).
+This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
 %This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
@@
 %
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}} \equiv 
+The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}}_{\rm reg} \equiv 
 \widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
@@
 Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
-Although there is negligible signal loss using this regularization, the small green peak at the third $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
+%Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
 
@@
 
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
+The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}}_{\rm reg} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
 In the bottom right
@@
 
-\color{black}
-
-% SECTION 2 ERROR ESTIMATION ---------------------------------------------------------------------------------
-
-\subsection{Error Estimation}
-\label{sec:ErrorOverview}
-
-Our second major 21\,cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
-confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
-measurement are calculating the variance of power spectrum results, and computing a theoretical error estimate based on an instrument's 
-system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
-two do not always agree due to a number of factors, including possible non-Gaussianities in the noise properties of our instruments and possible systematics in the data.
-
-A third option which acts as a middle ground between purely theoretical and purely empirical errors is using Gaussian error.
-This involves the assumption of Gaussianity, but allows the variance of the power spectrum estimator to be written as a function of the two-point estimator, or covariance.
-One could empirically calculate the covariance and then propagate it into an analytic expression to compute the errors, making this method fall somewhere between being fully empirical and fully modeled (see \citet{das_et_al2011a} for an example of its implementation).
-
-For PAPER's analysis, we choose a data-driven method of error estimation that does not rely on assumptions of Gaussianity. Namely, we compute error bars that have been derived from the inherent 
-variance of our measurements. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
-bootstrapping and then illustrate one of its pitfalls through a toy model.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
-spectra) can be made from different samples of data.
-Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
-between them. Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for 
-our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements). 
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
-of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
-from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
-the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
-here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one). The error (on 
-the mean) is then computed as the standard deviation across all bootstraps.
-
-We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
-values, that comprise a bootstrap. In the toy models presented in this section, $N_{\rm boot}$ is typically large, and the standard 
-deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
-Typically $N$ is a straightforward value to set that just depends on the experiment.
-However, we will illustrate one case in which it is not simply the number of samples along the axis that is being re-sampled.
-More specifically, we will see that $N$ depends on sample independence and may not always be straightforward to approximate.
-
-For our toy model, suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean). 
-This could represent $1000$ power spectrum measurements, for which we are interested in its error. We predict that the error 
-on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-We next form $500$ bootstraps ($N_{\rm boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
-original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
-estimate for our dataset. This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical 
-prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
-values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
-and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
-itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates 
-errors. The use of a fringe-rate filter, which averages data in time to increase sensitivity, is one example which leads to a 
-reduction in the number of independent samples, creating a situation in which errors can be under-estimated. We will now show 
-this effect using our toy model.
-
-Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of 
-independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
-earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$). This occurs 
-because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
-in all bootstraps, leading to less variation between the bootstraps. In fact, the error derived from bootstrapping is a strong 
-function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
-under-estimate the error by drawing too many or over-estimate it by drawing too few. However, since we know that we have $100$ 
-independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction 
-as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-This example highlights the importance of understanding how analysis techniques (such as fringe-rate filtering) can affect a 
-common statistical procedure like bootstrapping. Bootstrapping as a means of estimating power spectrum errors from real 
-fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task. For 
-example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the 
-number of averages performed.
-Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
-Hence, we do not recommend bootstrapping unless the
-number of independent samples along the axis that is being re-sampled is well-determined.
-In Section \ref{sec:Boot}, we explain how we under-estimated errors in the \citetalias{ali_et_al2015} analysis of PAPER and how our bootstrapping procedure has now changed to avoid the over-sampling of correlated data.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-sampling with replacement. The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ 
-elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be under-estimated if
-drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
-prediction only at $N=100$.}
-	\label{fig:toy_error1}
-\end{figure}
-
-In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset. However, we have 
-illustrated a situation in which bootstrapping can lead to under-estimated errors and therefore under-estimated power spectrum limits. We have shown that 
-bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample. Estimated errors can drop to 
-arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements. 
-%We have also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible. 
-While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain 
-analysis choices have compromised the method and whether a variation or an avoidance of traditional re-sampling could be preferred instead.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error2.png}
-%	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
-%dataset (i.e., if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
-%elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
-%of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
-Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black).
-The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.}
-%The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
-%	\label{fig:toy_error2}
-%\end{figure}
-
-% SECTION 2 BIAS ---------------------------------------------------------------------------------
-
-\subsection{Bias}
-\label{sec:BiasOverview}
-
-In a 21\,cm power spectrum, detections could be the EoR signal, but they could also 
-%(and unfortunately more likely) 
-be attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
-future 21\,cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
-that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
-help evaluate deep limits and/or detections.
-
-\subsubsection{Foreground and Noise Bias}
-\label{sec:BiasTypes}
-
-In Section \ref{sec:SiglossOverview}, we discussed signal loss as a form of multiplicative bias to estimates of the signal.
-Foregrounds are another type of bias, but an additive instead of a multiplicative one.
-Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
-magnitude above the cosmological signal.
-Though there are many techniques proposed for removing foregrounds (see e.g.
-\citealt{vedantham_et_al2012}; \citealt{chapman_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{wolz_et_al2014}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
-experiments currently remain limited by residuals rather than noise, especially at low $k$.
-
-One common method to isolate and filter foregrounds is to exploit their behavior in $k$-space. For a particular 
-baseline length, there is a maximum delay imposed on sources attached to the sky, which corresponds to the light-crossing time between two 
-antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
-wedge"
-\citep{datta_et_al2010, parsons_et_al2012b, vedantham_et_al2012, pober_et_al2013, thyagarajan_et_al2013, liu_et_al2014a, liu_et_al2014b, patil_et_al2017}. 
-The wedge describes a region in $k$-space contaminated by smooth spectrum foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
-proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and 
-%remove 
-avoid foregrounds, as done by \citetalias{ali_et_al2015}, 
-\citet{parsons_et_al2014}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{jacobs_et_al2015}, \citet{beardsley_et_al2016}, and \citet{trott_et_al2016}.
-
-Although smooth-spectrum foregrounds preferentially show up at low delay, or low $k$-modes, their isolation within the wedge is not perfect.
-In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
-the delay associated with the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
-convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
-foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum, the signal chain, and the 
-antenna response, all of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017, kerrigan_et_al2018}.
-
-There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from 
-spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the leakage from a particular 
-$k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using QE that forces a 
-window function to have a minimum response to low $k$ values. The window function used in \citetalias{ali_et_al2015} is constructed in such a way, 
-specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
-
-Determining the source of positive non-EoR detections at higher $k$'s is more difficult.
-In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (\citetalias{ali_et_al2015}; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
-In the next section, we will present some tests that can help distinguish these excesses from that of EoR.
-
-In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is 
-multiplied by itself. Every 21\,cm visibility measurement contains thermal noise that is comprised of receiver and sky noise. 
-We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating 
-longer, using more baselines, etc. However, the squaring of noise can occur when cross-multiplying visibilities, which is shown by 
-the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}. If both copies of $\textbf{x}$ come from the same baseline and time, it 
-can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument. One 
-way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days. This ensures that the 
-two quantities that go into a measurement have separate noises that don't correlate with each other.
-We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous (\citealt{dillon_et_al2014}; \citealt{parsons_et_al2014}).
-
-Another type of noise bias can stem from the spurious cross-coupling of signals between antennas. This excess is known as 
-instrumental crosstalk and is an inadvertent correlation between two independent measurements via a coupled signal path. 
-Crosstalk appears as a constant phase bias in time in visibilities, and it varies slowly compared to the typical fringe-rates of 
-sources. Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters. However, there 
-remains a possibility that power spectrum detections that aren't the cosmological signal are caused by residual, low-level crosstalk which survived any 
-suppression techniques.
-
-\subsubsection{Jackknife Tests}
-\label{sec:JackknifeOverview}
-
-We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful 
-jackknife tests. Again, we first approach this topic pedagogically as an introduction to the related PAPER discussion in Section 
-\ref{sec:Bias}.
-
-The jackknife is a resampling technique in which a statistic (i.e., power spectrum) is computed in subsets of the data (\citealt{quenouille1949}; \citealt{tukey1958}). These 
-subsets are then compared to reveal systematics. In this section we define two main tests --- the null test and the traditional 
-jackknife --- and explain how a power spectrum detection must pass each. We then highlight how these tests can be used to 
-help distinguish between different sources of bias.
-
-\begin{itemize}
-\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
-investigate underlying systematics (see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
-divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
-Subtracting the two removes signal that is common to both subsets, including foregrounds and the EoR signal. The resulting power 
-spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
-from one of the data subsets to the other (i.e., doesn't get subtracted perfectly). 
-\item \textbf{Traditional Jackknife}: In a broader sense, it is important to perform many jackknife tests in order to instill 
-confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
-Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new 
-power spectrum every time as a day of data is removed, or a baseline is removed. This type of jackknife would reveal bias 
-present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
-\end{itemize}
-
-While the null test hunts for deviations from thermal noise and the jackknife tests for deviations in subsamples, they are both 
-closely related. We can highlight the connection between the two using a toy model dataset.
-
-Suppose we have four independent measurements made along two different axes.
-As an example, we construct $\textbf{x}_{1a}$, $\textbf{x}_{1b}$, $\textbf{x}_{2a}$, and $\textbf{x}_{2b}$, where the numbers symbolize two different days of data and the letters represent two different baselines.
-Each of the
-measurements have dimensions of $100$ time integrations and $20$ frequency channels. They each have separate thermal 
-noises constructed as a Gaussian random signal for each, and identical EoR signals.
-
-To mimic the presence of a systematic, we add a toy sinusoid foreground, similar to the one used in 
-Section \ref{sec:toymodel}, to only $\textbf{x}_{2a}$ and $\textbf{x}_{2b}$. This represents a foreground signal 
-present in only the second day of data, but not the first. Mathematically, if  $\textbf{n}$ 
-is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the four measurements can be written as:
-
-\begin{eqnarray}
-\label{eq:bias1}
-\textbf{x}_{1a} &=& \textbf{n}_{1a} + \textbf{e}  \\ 
-\textbf{x}_{1b} &=& \textbf{n}_{1b} + \textbf{e}  \\ 
-\textbf{x}_{2a} &=& \textbf{n}_{2a} + \textbf{e} + \textbf{f} \\ 
-\textbf{x}_{2b} &=& \textbf{n}_{2b} + \textbf{e} + \textbf{f}.
-\end{eqnarray}
-
-\noindent We now take a jackknife along the day-axis, forming separate power spectrum estimates for each day:
-
-\begin{eqnarray}
-\widehat{\textbf{P}}_{1} &\propto& \textbf{x}_{1a}\textbf{x}_{1b}^{\dagger} \\
-\widehat{\textbf{P}}_{2} &\propto& \textbf{x}_{2a}\textbf{x}_{2b}^{\dagger}.
-\end{eqnarray}
-
-We do not perform a time-average or apply a fringe-rate filter to this toy model, since we are interested only in what jackknife 
-tests can tell us about biases. For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to 
-avoid signal loss.
-
-To construct a null test, we difference the two power spectra, with the result shown in Figure \ref{fig:toy_bias1} (black) along with the power spectrum of noise only (green).
-Subtracting the two estimates removes sky signal that should ideally be present in both jackknives.
-However, we see a clear difference between the null test and the power spectrum of
-noise. This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.pdf}
-	\caption{A null jackknife test shown as the power spectrum difference between two measurements (black), compared to the power spectrum of noise alone (green).
-Because the null test is not consistent with noise, it suggests the
-presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
-with thermal noise.}
-	\label{fig:toy_bias1}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias2.pdf}
-	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
-the presence of a systematic in $\textbf{x}_{2}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
-measurements should remain consistent despite the jackknife taken.}
-	\label{fig:toy_bias2}
-\end{figure}
-
-While the null test is useful for testing noise properties and the uniformity of a dataset, jackknives are useful in pinpointing 
-which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $
-\textbf{x}_{2}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
-provide insight into possible sources. For example, if jackknives along the time-axis reveal a bias present at a certain LST, a 
-likely explanation would be excess foreground emission from a radio source in the sky at that time. A jackknife test involving 
-data before and after the application of a fringe-rate filter can reveal whether crosstalk noise bias is successfully suppressed 
-with the filter, or if similar-shaped detections in both power spectra suggest otherwise. There are many other jackknife axes of 
-which we will not go into detail here, including baseline, frequency, and polarization. Ultimately, an EoR detection should persist 
-through them all and a clean measurement should exhibit noise-like null spectra.
-
-In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum 
-detection. In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to show that our 
-excesses are not EoR and to identify their likely cause.
-
-% SECTION 3  ---------------------------------------------------------------------------------
-
-\section{Demonstration in PAPER-64 Data}
+% SECTION 3 CASE STUDY ---------------------------------------------------------------------------------
+
+\section{Signal Loss Case Study}
 \label{sec:CaseStudy}
 
-In the previous sections we have discussed three overarching 21\,cm power spectrum themes --- signal loss, error estimation, 
-and bias. Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of 
-a power spectrum result.
+In the previous section we used toy models to show how signal loss arises when weighting data with empirically estimated covariances.
+We also demonstrated how an analysis technique like fringe-rate filtering can increase loss, and how simple regularization methods can minimize loss.
 
@@
 
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$.
-The need to revise this limit stems mostly from previously under-estimated signal loss and under-estimated error bars, both of which we
-address in the following sections.
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$. The need to revise this limit stems mostly from previously underestimated signal loss, which we 
+address in this section.
 
@@
 \citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts.
+(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues presented in this paper).
 
@@
 This was chosen in order to increase the number of independent
-modes and reduce signal loss, though as we will explain in the next section, this signal loss was still under-estimated. With the development of a new, 
+modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still underestimated. With the development of a new, 
 robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
@@
 domain and time domain is shown in Figure \ref{fig:frp}.
+
+Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
+As mentioned in Section \ref{sec:SiglossOverview}, there are several other ways the PAPER analysis pipeline can lead to loss, including through calibration and delay-filtering.
+We refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015} for discussions about these other types of signal loss, noting here that they are much less significant than the loss focused on in this paper.
 
@@
 
+We present our PAPER-64 signal loss investigation in three parts.
+We first give an overview of our signal injection framework which is used to estimate loss.
+In this framework (and as in \citetalias{ali_et_al2015}), we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
+As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
+Next, we describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
+Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
+Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
+
 % SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
 
-\subsection{PAPER-64: Signal Loss}
-\label{sec:Sigloss}
-
-In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data itself.
-Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular dataset.
-The exact amount of signal loss will depend on the specific realizations of the signals present in the data and is not something we can directly compute.
-In this work, as in \citetalias{ali_et_al2015}, we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
-As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
-
-We present our PAPER-64 signal loss investigation in three parts: we first give an overview of our injection framework and illustrate how different power spectrum components affect loss.
-We next describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
-Finally, we build off of Section \ref{sec:SiglossOverview} by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously under-estimated losses.
-
-%The results of such an injection scheme can be interpreted in multiple ways.
-In this paper we describe two --- this section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
-These two methods yield very similar results, but fundamentally are answering subtly distinct questions.
-We also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
-
-\subsubsection{Signal Loss Methodology} 
+\subsection{Signal Loss Methodology} 
 \label{sec:siglossmethod}
-In short, our method consists of adding an EoR-like signal into the data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
+In short, our method consists of adding an EoR-like signal into the visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
@@
 Since the optimal filter has a shape that matches the rate of the sidereal motion of the sky, this transforms the Gaussian noise into a measurement that PAPER could make.
-This signal is then added to the data.\footnote{One
-specific change from \citetalias{ali_et_al2015} is that we add this simulated signal into the analysis pipeline before the final fringe-rate filter is 
-applied to the data. Previously, the addition was done after that final fringe-rate filter step.  This change results in an increased 
+This signal is then added to the visibility data.\footnote{One
+specific change from \citetalias{ali_et_al2015} is that we add this simulated signal - which has been fringe-rate filtered once already in order to transform it into a ``sky-like" signal - into the analysis pipeline before a fringe-rate filter is
+applied to the data (i.e., prior to the analysis step of fringe-rate filtering). Previously, the addition was done after the fringe-rate filter analysis step.  This change results in an increased 
 estimate of signal loss, %(by a factor of $\sim$$10$), 
 likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
-
-Suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level), and $\textbf{x}$ is our data. We define $\textbf{r}
-$ to be the data plus the EoR signal:
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was underestimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
+
+Mathematically, suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level).
+We do not know the true EoR signal contained within our visibility data, $\textbf{x}$, so $\textbf{e}$ takes on the role of the true EoR signal (for which we measure its loss).
+Furthermore, one can make the assumption that the true EoR signal is small within our measured data, so the data vector $\textbf{x}$ itself is representative of mostly contaminants.
+Using this assumption, the sum of $\textbf{x}$ and $\textbf{e}$, defined as $\textbf{r}$:
 
@@
 \label{eq:rxe}
-\textbf{r} = \textbf{x} + \textbf{e}.
-\end{equation}
+\textbf{r} = \textbf{x} + \textbf{e},
+\end{equation}
+can be thought of as the sum of contaminants plus EoR.
+The quantity $\textbf{r}$ then becomes the dataset for which we are measuring how much loss of $\textbf{e}$ there is due to our power spectrum pipeline.
 
@@
 The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
-Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
+It can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
 The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-This is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-In principle, one could compute the true $\widehat{P}_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline.
-In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds.
-To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants.
-Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
-Therefore, $\widehat{P}_{\rm out}$ can be directly compared to the measurement that we make.
+The input power spectrum is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
 
@@
 \end{eqnarray}
+One of the key takeaways of this section is that the \citetalias{ali_et_al2015} analysis estimated signal loss by comparing \textit{only} the signal-only term (second term in Equation \eqref{eq:crossterm}) with $\widehat{P}_{\rm in}$, whereas in fact the cross-term (third term in Equation \eqref{eq:crossterm}) can substantially lower $\widehat{P}_{\rm out}$.
 In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$).
-We will now examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
+We will now go into further detail and examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
 
@@
 When the injected signal is much larger than the measured power spectrum, the data-only components can 
-be neglected as many orders of magnitude smaller.
+be neglected as they are many orders of magnitude smaller.
 We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e., in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
@@
 This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
-We note that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.
+Again, we emphasize that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
+Ignoring the effect of the negative power from the cross-terms is the main reason for underestimating power spectrum limits in \citetalias{ali_et_al2015}.
 
@@
 Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
-However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
+However, without taking into account the cross-terms (the second term), we can substantially underestimate loss.
 In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
@@
 	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
-	\caption{Illustration of the power spectrum amplitude of different power spectrum terms as a function of injected EoR power level summed into the 
-data.
-Left: The empirically estimated inverse covariance weighted case used in \citetalias{ali_et_al2015}.
-The output power spectrum ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) is shown in black, and the individual terms in Equation
-\eqref{eq:crossterm} are shown in blue, red, and green.
+	\caption{Illustration of the power spectrum amplitude of five different power spectrum terms, each a function of visibility data ($\textbf{x}$), simulated injected EoR signal ($\textbf{e}$), or both ($\textbf{r}$).
+This figure shows how these quantities behave as the power level of the injected EoR signal increases (along the x-axis).
+The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.
+We emphasize that the output power spectrum in black ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
+Roughly speaking, it can be compared to the input signal level ($P_{\rm in}$) to estimate the amount of signal loss.
+Left: Empirical inverse covariance weighting is used in power spectrum estimation, as done in \citetalias{ali_et_al2015}.
 The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss).
-The details of the simulation used to generate the figure is explained in Section
-\ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.  The gray 
-horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power). The green signal-signal 
-component is the term used in \citetalias{ali_et_al2015} to estimate signal loss. It is significantly higher 
-than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue) . In the 
-regime where cross-correlations between injection and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like 
-term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect
-$\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at 
-the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss). Right: The same power spectrum terms illustrated for the uniform weighted case.}
+The gray horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power).
+The green signal-signal component is the term used in \citetalias{ali_et_al2015} to estimate signal loss.
+It is significantly higher than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue).
+In the regime where cross-correlations between signal and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
+However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative estimates due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
+This causes the difference between the green curve (which exhibits negligible loss at the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss).
+Right: The same power spectrum terms illustrated for the uniform weighted case.}
 \label{fig:sigloss_terms}
@@
 
-\subsubsection{Signal Loss in Practice}
+\subsection{Signal Loss in Practice}
 \label{sec:Practice}
@@
 outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
-($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. With this weighting, our 
-expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
-
-\begin{eqnarray}
-\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
-%&&\phantom{=====} 
-%-  \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\widehat{\textbf{C}}_{x}^{-1}\textbf{Q}^{\alpha}\widehat{\textbf{C}}_{x}^{-1}\textbf{x}. 
-\end{eqnarray}
+($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. %With this weighting, our 
+%expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
+
+%\begin{eqnarray}
+%\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
+%\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}%\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
+%\end{eqnarray}
 
@@
 \noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
+as the distribution of data plus signal injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
 by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
@@
 the shape of the transfer curve is similar for all $k$'s.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ is a model of our data.
+We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ represents a (lossy) power spectrum.
 To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
@@
 From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
-For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$.
 
@@
 Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
+The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:Error}.
 Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
@@
 
-\subsubsection{Minimizing Signal Loss}
+\subsection{Minimizing Signal Loss}
 \label{sec:Weight}
@@
 their best (i.e., when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
+However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
 We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
-We also note that all of the regularizations described here perform similarly to the uniformly weighted case.
-Thus, in Kolopanis et al.
-(\textit{in prep.}), uniform weightings are used to produce straightforward power spectrum limits that do not suffer from loss.
-
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) is shown in Figure 
+
+It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
+Realistically, these details about the EoR signal are unknown, and therefore our signal loss framework is subject to bias.
+Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
+(\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.
+
+The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) using the analysis presented in this paper is shown in Figure
 \ref{fig:ps1_data}.
@@
 Finally, the gray shaded regions combine the measured uniform weighted power spectrum values with thermal noise errors.
-We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case.
+We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case, thus further motivating uniform-weighting for Kolopanis et al.
+(\textit{in prep.}).
 
@@
 
-In Section \ref{sec:Sigloss}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
+In Section \ref{sec:CaseStudy}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
 We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
@@
 
-% SECTION 3 ERROR ESTIMATION ---------------------------------------------------------------------------------
-
-\subsection{PAPER-64: Error Estimation}
+% SECTION 4 OTHER ERRORS ---------------------------------------------------------------------------------
+
+\section{Summary of Additional Errors}
+\label{sec:OtherErrors}
+
+Underestimated signal loss is the main reason for the revision of the power spectrum limits from \citetalias{ali_et_al2015}.
+It is interesting to note that --- had all the other aspects of the original analysis been correct --- the underestimated limits may have been more easily caught.
+Unfortunately, two related power spectrum components, namely the error bars on the power spectrum data points and the theoretical noise prediction, were also calculated incorrectly.
+
+In this section, we summarize multiple inconsistencies and errors that have been found since the previous analysis in terms of error estimation.
+We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
+We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified.
+
+\subsection{Bootstrapping}
+\label{sec:Boot}
+
+Broadly speaking, we desire robust methods for determining accurate 
+confidence intervals for our measurements. For PAPER's analysis, we choose a data-driven method of error estimation, computing error bars that have been derived from the inherent 
+variance of our measurements. A common technique used to do this is bootstrapping, which we first define below and then discuss its application to PAPER.
+
+Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
+spectra) can be made from different samples of data.
+Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
+between them. Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for 
+our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
+
+Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements). 
+Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
+of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
+from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
+the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
+here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one). The error (on 
+the mean) is then computed as the standard deviation across all bootstraps.
+
+We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
+values, that comprise a bootstrap. $N_{\rm boot}$ is typically large, and the standard 
+deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
+Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
+However, we will see that $N$ depends on sample independence, and it is this dependence that led to the underestimation of errors in \citetalias{ali_et_al2015}.
+
+Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean). 
+This could represent $1000$ power spectrum measurements, for which we are interested in its error. We predict that the error 
+on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+We next form $500$ bootstraps ($N_{\rm boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
+original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
+estimate for our dataset. This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical 
+prediction (green).
+
+One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
+values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
+and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
+itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, underestimates 
+errors.
+
+As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of 
+independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
+earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$). This occurs 
+because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
+in all bootstraps, leading to less variation between the bootstraps. In fact, the error derived from bootstrapping is a strong 
+function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
+underestimate the error by drawing too many or overestimate it by drawing too few. However, since we know that we have $100$ 
+independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction 
+as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
+	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
+sampling with replacement. The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ 
+elements (with replacement) from a length $1000$ array of a Gaussian random signal.
+The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
+They illustrate how errors can be underestimated if
+drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
+prediction only at $N=100$.}
+	\label{fig:toy_error1}
+\end{figure}
+
+Analogous to the toy model just presented, errors on the power spectrum of PAPER-64 were originally underestimated because the use of a fringe-rate filter, which averages data in time to increase sensitivity, reduces the number of independent samples along the bootstrapping axis, thus decreasing the variance of the bootstraps.
+
+More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
+spectrum that is a function of $k$ and time. In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
+($N_{\rm boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
+$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
+Means were then taken of the values in each bootstrap. Finally, power 
+spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
+this previous analysis, the number of elements sampled per bootstrap greatly 
+exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
+measurements from this dataset has many repeated values, and the variance between hundreds ($N_{\rm boot}$) of these random 
+samples is smaller than the true underlying variance of the data.
+
+Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
+bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
+Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
+\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
+shown in the figure, when more elements are drawn for each bootstrap than the number of 
+independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
+While Figure \ref{fig:data_errors} implies that errors are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally underestimated by a factor of $\sim$ $5$ in mK$^{2}$.
+
+In addition to learning how sample independence affects bootstrapped errors, we have made three additional changes to our bootstrapping procedure since \citetalias{ali_et_al2015}, summarized here:
+
+\begin{itemize}
+
+\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
+In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
+On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
+This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
+
+\item{In \citetalias{ali_et_al2015}, individual baselines were divided into $5$ independent groups, where no baselines were repeated in each group.
+Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
+This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
+Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
+
+\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
+
+\end{itemize}
+
+In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
+Bootstrapping can be an effective and straightforward way to estimate errors of a dataset, however, bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
+We have thus avoided this issue by removing one of our bootstrap axes, as well as updated several other details of our procedure to ensure accurate re-sampling and error estimation.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
+	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
+methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
+effects of bootstrapping from signal loss.
+The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
+This underestimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
+We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
+We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
+	\label{fig:data_errors}
+\end{figure}
+
+\subsection{Theoretical Error Estimation}
 \label{sec:Error}
 
-In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
-We first walk through an expression for a theoretical error estimation (of thermal noise) based on observational parameters.
-Although a theoretical model often
-differs from true errors, it is helpful to understand the ideal case and the factors 
-that affect its sensitivity. Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to 
-revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
-
-In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the \citetalias{ali_et_al2015} 
-analysis of PAPER-64. While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power 
-spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
-
-\subsubsection{Theoretical Error Estimation}
-\label{sec:PSSense}
-
-Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations. What we 
+In addition to bootstrapping, another method of error estimation is to compute a theoretical estimation of thermal noise based on observational parameters.
+Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
+
+Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations, and what was 
 found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations. The analytic 
 calculation is only an approximation; however, the differences were large enough (factors of $10$ in some cases) to warrant a 
-careful investigation. The analytic calculation attempts to combine a large number of pieces of information in an approximate 
+careful investigation. This calculation attempts to combine a large number of pieces of information in an approximate 
 way, and when re-considering some of the approximations, we have found there to be large effects. What follows here is an 
@@
 divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even", for reasons explained in Section \ref{sec:MitBias}).
+Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even" in order to avoid noise biases).
 Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
@@
 published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
-\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
+\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:Error}, which when combined decreases our 
 sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
@@
 However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
+While the noise simulation provides an indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
+We therefore interpret our noise prediction as the sensitivity floor for our measurements.
 
@@
 
-\subsubsection{Bootstrapping}
-\label{sec:Boot}
-
-We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
-four specific changes in the way we estimate errors since \citetalias{ali_et_al2015}, the first of which builds off of the lesson we have learned previously about bootstrapping independent samples.
-
-\begin{itemize}
-
-\item{As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
-of independent samples, or the number of independent samples is well known. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time.
-
-In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
-($N_{\rm boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
-specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Means were then taken of the values in each bootstrap. Finally, power 
-spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap greatly 
-exceeded the number of independent LST samples, under-estimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds ($N_{\rm boot}$) of these random 
-samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for fringe-rate filtered noise are shown in Figure
-\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to better agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-}%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
-
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
-
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into $5$ independent groups, where no baselines were repeated in each group.
-Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
-This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
-Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
-
-\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
-
-\end{itemize}
-
-In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
-Additionally, we have carried out substantial testing with these changes in place to verify that the computed errors for our noise simulations are accurate and agree with thermal noise predictions.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
-This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
-We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits better agree with the $2\sigma$ analytic prediction for noise (green).}
-	\label{fig:data_errors}
-\end{figure}
-
-% SECTION 3 BIAS ---------------------------------------------------------------------------------
-
-\subsection{PAPER-64: Bias}
-\label{sec:Bias}
-
-In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum 
-detections and imitate an EoR signal. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
-detection, as well as for identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
-foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.
-
-\subsubsection{Mitigating Bias}
-\label{sec:MitBias}
-
-We briefly discuss one way we mitigate foreground leakage in a power spectrum estimate, and two ways we 
-suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
-(non-EoR) detections.
-
-Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and \citetalias{ali_et_al2015}).
-As alluded to in Section \ref{sec:SiglossOverview}, we
-have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
-compute $\textbf{M}$ using the matrix $\textbf{G}$ (which would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:
-
-\begin{equation}
-\textbf{G}^{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
-\end{equation}
-
-\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
-the Cholesky decomposition of $\textbf{G}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{G}$ is Hermitian):
-
-\begin{equation}
-\textbf{G} = \textbf{LL}^{\dagger}.
-\end{equation}
-
-\noindent Next, we construct $\textbf{M}$:
-
-\begin{equation}
-\textbf{M} = \textbf{DL}^{-1}
-\end{equation}
-
-\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MG}$ (see Equation \eqref{eq:Wpplusbias}), 
-becomes
-
-\begin{equation}
-\textbf{W} = \textbf{DL}^{\dagger}.
-\end{equation}
-
-\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
-of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{G}$ in such a way so that 
-power can leak from high-$k$ modes to low-$k$ modes, but not vice versa.
-Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the
-contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use a diagonal $\textbf{M}$ for simplicity.
-
-In addition to mitigating foreground bias at high-$k$'s, two other sources of bias that we actively suppress in the PAPER-64 
-analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
-former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
-dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
-the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
-$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``baseline 1" with ``baseline 1", for 
-example, in order to prevent the squaring of the same thermal noise.
-
-To mitigate crosstalk bias, which appears as a static bias in time, we apply a fringe-rate filter that suppresses fringe-rates of 
-zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
-on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, even without accounting for signal loss, the crosstalk bias at all $k$'s is very strong compared to the removed case.
-
-\subsubsection{Jackknife/Null Tests}
-
-As shown in Figure \ref{fig:ps1_data}, our illustrative PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
-As discussed in Section \ref{sec:BiasTypes}, this bias is
-most likely attributable to foreground leakage. %The cause for biases at higher $k$-values is more difficult to pinpoint.
-
-Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
-that our biases are not attributable to EoR.
-Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
-We then difference them (i.e., the null test) to tease out excess variances.
-
-The three results are shown in Figure \ref{fig:null}.
-Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the bootstrapped errors of the two dataset halves added in quadrature.
-The expected thermal noise level (gray shaded regions) is the thermal noise of each dataset added in quadrature as well.
-Constructing the tests as such ensures that we are probing whether the variances of each dataset differ by an amount consistent with the thermal noise.
-We use uniform weightings for all tests.
-
-We take jackknives along three different axes:
-
-\begin{itemize}
-%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
-There are clear detections at low $k$'s.
-\item Baselines: We split our dataset into two halves, where each contains half of the total baselines used in the 
-analysis. No baselines are repeated between the two datasets.
-\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.5 hours) and second half (LSTs 
-4.5-8.6 hours).
-\item Day: We split our dataset into even and odd Julian dates.
-We form power spectra for each separately, allowing the cross-multiplication of ``even" with ``even", for example, for this null test only.
-If the same sky signal is in both the ``even" and ``odd" datasets, we expect it to cancel out.
-%However, allowing these cross-multiplications can in practice introduce a low level noise bias...
-\end{itemize}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.47\textwidth]{plots/null_bls.pdf}
-	\includegraphics[width=0.47\textwidth]{plots/null_lsts.pdf}
-	\includegraphics[width=0.47\textwidth]{plots/null_eo.pdf}
-	\caption{Differenced power spectrum results (with $2\sigma$ bootstrapped errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
-The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra produced on either side of the jackknife axis.
-The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
-We find that there are no significant systematics for $k > \pm 0.2$\,$h$ Mpc$^{-1}$ for all three tests.
-However, we find that all tests exhibit an extra variance at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), likely due to foreground-noise coupling terms when foregrounds are brightest.
-Additionally, we find that the LST null test is not fully consistent with zero, implying a bias that is LST dependent and likely caused by varying foregrounds.}
-	\label{fig:null}
-\end{figure*}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
-%	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{\rm eff}$, compared to the analytically estimated 
-%$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along Julian days (separating 
-%even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
-%We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
-%	\label{fig:null}
-%\end{figure*}
-
-In investigating Figure \ref{fig:null}, we focus on three main possibilities --- whether the data points and error bars are consistent with thermal noise (``passing"), whether the error bars are consistent with zero but not consistent with thermal noise (``passing but has an additional variance"), or whether the error bars are not consistent with zero at all (``failing").
-We examine each case in the context of our results below.
-
-Firstly, all three null tests display data points that lie within the thermal noise gray band for $k > \pm 0.2$\,$h$ Mpc$^{-1}$.
-In addition, all three null tests show error bars consistent with the thermal noise level for those same $k$'s.
-This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e., the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
-We deem these as ``passing" null tests for the specific jackknives taken (again, dividing up the data in a different way along the same axes may not yield the same results, so more thorough testing is needed to be sure).
-
-The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests.
-This indicates an additive noise component that is increasing our errors.
-More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
-This is because cross-multiplications produce four additive terms --- a signal-squared term (where ``signal" includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
-When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
-While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples).
-Combined with the fact that the foregrounds are so bright, the finite ensemble of the couplings can introduce extra variance that varies with foreground strength.
-It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.
-
-Lastly, a third null test result is an error bar not consistent with zero.
-This is the case for the LST null test at $k\sim-0.15$\,$h$ Mpc$^{-1}$ and $k\sim-0.2$\,$h$ Mpc$^{-1}$.
-In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e., the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
-This result implies that there exists a low level bias that is LST-dependent, and likely caused by residual foregrounds that vary in LST.
-Again, it is not surprising that this type of bias occurs near the horizon limit.
-
-%Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
-
-%We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
-This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
-
-%There are a couple possible explanations for this.
-Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
-This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
-When differencing two power spectra, we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
-The cross-terms, however, can introduce extra variance that would vary with foreground strength, therefore being consistent with the shape of our results.
-One additional explanation, specifically for the slightly large error bars seen at high $k$'s, could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate in this high-$k$ regime.
-Regardless of a potentially larger thermal noise prediction, however, the large error bars near the horizon limit still signify the presence of excess variance in our data.
-
-In this section we have presented the first jackknife and null tests from the PAPER experiment.
-Unsurprisingly, they imply that our measurements are biased by foregrounds, and not the EoR signal (a clean detection of EoR would have passed all three tests).
-While simple, these tests outline a framework that can be used by future measurements.
-The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough investigations of this nature.
-
-%, and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero).
-We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
-
-%The null test in LST is much more illuminating.
-Because of the large variable error bars, many of which do not include zero, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
-%estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
-In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and
-%$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
-We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
-
-%We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
-%similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
-%the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
-%This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
-%bias we see comes from foregrounds. % in regions where we expect leakage.
-
 % CONCLUSION ---------------------------------------------------------------------------------
@@
 HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
-that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately 
-and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife 
-and null tests.
+that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline and be able to accurately 
+and robustly calculate both power spectrum and theoretical errors.
 
 In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
-signal loss, error estimation, and bias, which can be summarized as follows:
+signal loss and error estimation, which can be summarized as follows:
 
@@
 time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
-signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
-failing to account for correlations between the data and signal which can be large and negative (Section \ref{sec:siglossmethod}).
-\item Errors that are estimated via bootstrapping can be under-estimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:ErrorOverview}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
+\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:siglossmethod}). However, a 
+signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
+failing to account for correlations between the data and signal which can be large and negative.
+\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
+(Section \ref{sec:Boot}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
 simple and accurate way of estimating errors.
-\item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}). Similarly, performing 
-jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection and can also be used to tease 
-out systematics.
 \end{itemize}
@@
 As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, accurately estimating thermal noise, and implementing jackknife tests.
+This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, and accurately estimating thermal noise.
 Our revised PAPER-64 limits are presented in Kolopanis et al.
 (\textit{in prep.}), which supersede all previously published PAPER limits.
-The main reasons for a previously under-estimated limit and
-ways in which our new analysis differs can be summarized by the following:
+Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
+(\textit{in prep.}) uses a straightforward power spectrum estimation approach that is not lossy.
+However, the main reasons for a previously underestimated limit and
+ways in which our new analysis differs can still be summarized by the following:
 
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
+\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was underestimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
 covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
 \ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-Under-estimated signal loss therefore represents the bulk of our revision.
-This revision is similar in nature to the re-analysis of results from the GMRT (\citealt{paciga_et_al2013}) which were also 
-revised from new signal loss calculations associated with their singular value decomposition foreground filter.
-\item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
+underestimated signal loss therefore represents the bulk of our revision.
+\item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
 Several other errors were also found regarding error estimation, though with smaller effects.
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our overall
+decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:Error}). We note that our sensitivity prediction is revised by a factor less than our overall
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
@@
 foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
-instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
-comprehensive jackknife tests will play critical roles in accurate 21\,cm results.
+instruments.
+On the power spectrum analysis side, robust signal loss simulations and precise error calculations will play critical roles in accurate 21\,cm results.
 With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
@@
 
-We illustrate the way in which the quadratic estimator, Equations \eqref{eq:OQE}, \eqref{eq:OQEQuadratic}, and \eqref{eq:OQELinear}, estimate the power spectrum of EoR in the presence of contamination by other terms by considering two simpler, but similar, cases of estimating the variance of data.
-We have specifically chosen toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+In this Appendix, we focus on the optimal quadratic estimator, Equation \eqref{eq:OQE}, and mathematically illustrate its role in estimating the power spectrum of EoR.
+While there exists detailed literature about quadratic estimators in general (e.g., \citealt{liu_tegmark2011}; \citealt{trott_et_al2012}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}), here we focus on two simple cases in order to outline one situation where the estimator successfully suppresses contamination and one where it does not.
+By describing these two cases, we hope to clarify and motivate the desire to use OQE while also understanding its limitations.
+
+In our toy model, we specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
 We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
@@
 \end{equation}
-where we wish to estimate $s$.  The contaminant in this case has a similar structure (as the EoR) for its covariance, and is assumed uncorrelated with the signal
+where we wish to estimate $s$.  The contaminant in this first case has a similar structure (as the EoR) for its covariance, and is assumed uncorrelated with the signal
 \begin{equation}
@@
 
-%------------------------------- commented below---------------------------------------
-\begin{comment}
-\section{Simplified Loss Correction}
-\label{sec:Pr_appendix}
-One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
-The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the assumption that the number of samples is large enough to treat sample variance as a first order purturbation on the ideal covariance matrix instead of the dominant effect we know it is.
-\acl{I'm not sure the previous sentence was fair.
-Again, the appendix is a motivating example.
-Carina's numerical computations do not rely on the derivation.} However it is possible to ask a slightly different question and with less math still get roughly the same answer.
-
-In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
-Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
-\acl{Can we justify better why this is the right question?
-In particular, why is the detection of an injected signal the right thing to look at?
-After all, the universe doesn't do any signal injections.
-I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{P}}_{r}$, the weighted power spectrum of the data plus injected signal.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
-\caption{The distribution of $\widehat{\textbf{P}}_{r}$ values for a 
-given injection level P$_{\rm in}$.
-The $\widehat{\textbf{P}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
-It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
-We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right).
-The dotted black
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{P}}_{x}$, the data distribution.
-At low injection, $\widehat{\textbf{P}}_{r}$ converges to the data level.
-}
-\label{fig:Pr_vs_Pin}
-\end{figure}
-
-This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
-In the 2D space relating total $\widehat{\textbf{P}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e., data only) and very large levels are dominated by the injected signal.
-It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross-correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
-
-\begin{figure}[tp]
-\centering
-\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
-\caption{The probability that an injected signal of level P$_{\rm inj}$
-is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{P}}_{x}$ (data).
-The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.}
-\label{fig:Prob_vs_Pin}
-\end{figure}
-
-One difference in this method from the one in the main text is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
-Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
-This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself.
-In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual.
-We note that a high SNR detection will require a different method.
-
-Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of ``data + 
-injected eor" ($\widehat{P}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{P}_x$. 
-In other words, what is $e$ such that,
-\begin{equation}
-\widehat{\textbf{P}}_{e+x} > \widehat{\textbf{P}}_{x},
-\end{equation}  
-?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
-One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e., the null test) the same.
- \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by
- \begin{equation}
- \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{P}}_x) dx = \Lambda,
- \end{equation}
- where $\Lambda$ is the appropriate number for $2\sigma$.
-That tells us what $x$ would be needed for us to thing that it was an outlier result without there being an extra $e$ in the data.
-Then we ask how often we get such an outlier result by computing
-  \begin{equation}
- \int_{x_0}^\infty \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) dx.
-\end{equation}
-Is what you've written equivalent to this? Sorry if this is remedial...
- }
- \begin{equation}
-\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{P}}_x) \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) x
- \end{equation}
- where $\Prob(\widehat{\textbf{P}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{P}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{P}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{P}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
-
-Probability vs.
-injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
-At low injection levels the variation between $\textbf{x}$ and $\textbf{(e+x)}$ is such that the null test is ruled out to within $20$\%.
-This is the level expected from two distributions with $\sim$10 effective samples.
-As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
-
-Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
-As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$\% and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
-We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
-Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\%.
-
-The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
-Overall the limits show good agreement, with k modes differing by factors of $\sim$$2$ for $k > 0.1$ $h$Mpc$^{-1}$ .
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison_95.png}
-\caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
-with the method in this appendix at $95$\% confidence (red curve).
-Also shown are the upper limits of the uniform-weighted power spectrum
-(blue dashed) and theoretical noise model (green).} 
-\label{fig:sigloss_compare} 
-\end{figure}
-
-\end{comment}
-
 \bibliographystyle{apj}

### 2018-08-29 PAPER.tex
read-through edits up until section 3

@@
 Specifically, with a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
-In this paper, we focus on signal loss specifically associated with quadratic estimators and power spectrum estimation.
+In this paper, we focus on signal loss associated with power spectrum estimation.
 We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
@@
 
-In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
+In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
 the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
@@
 instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often chosen to maximize sensitivity and minimize contaminants, affect power spectrum results.
+A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results.
 More specifically, it is imperative to develop techniques that ensure
-the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss may have resulted.
-In this paper, we discuss signal loss associated with specifically with power spectrum estimation --- a topic that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has been underestimated in previous PAPER analyses.
+the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method.
+In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation.
+This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis.
 We first approach this topic from a broad perspective, and then perform a detailed
@@
 
-Signal loss refers to attenuation of the target \textit{cosmological} signal 
+Signal loss refers to attenuation of the target cosmological signal 
 in a power spectrum estimate.
@@
 
-Signal loss can arise in a variety of ways in an analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay domain filter, or deriving weights from data and applying them to itself.
-Here we focus on signal loss associated with
-% JEA - we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
-the latter.
-
-A dataset can be weighted to emphasize certain features and minimize others, and one particular flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
+One type of signal loss can occur when weighting data by itself.
+Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others.
+For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
 Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
@@
 weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
-Here we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
+In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
 This loss was significantly 
 %applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis.
+underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.
 
@@
 For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial P^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
+Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 \end{equation}
-is a sensible estimate of the true power spectrum $\textbf{P}$.
+is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.
+
 To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
@@
 where $W^{\alpha \beta}$ are elements of a window function matrix.
-Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
-If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
+Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
 However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
@@
 \end{equation}
-assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
+assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
 amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
@@
 
-\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness (the degeneracy) of the empirical eigenspectrum.
-In general, larger sample variances and flatter eigenspectra (more degeneracies) lead to more loss (Section \ref{sec:toymodel_frf}).
+\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum.
+In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).
 
@@
 
-\subsection{Inverse Covariance Weighting}
+\subsection{Empirical Inverse Covariance Weighting}
 \label{sec:toymodel}
@@
 
-For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
+For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
 However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
 If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
+As described in Section \ref{sec:siglossmethod} and shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
+In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
 
@@
 %then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e., only allowing over-fitting to occur for the first mode).
+Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
 then take the remaining covariance to be the identity matrix.  
@@
 
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization.
+Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization.
 There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes which are noise-like.
+Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.
 
@@
 
-While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
-The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged, there will not be any signal loss.
+While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
+The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss.
 However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
@@
 We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank.
 We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
@@
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
+This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
 %This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
@@
 elements of the estimated covariance matrix more heavily than those off-diagonal.
-Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
+Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data and there is no loss.
 %Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
 
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
-by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this 
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss by only using the first three eigenmodes of the estimated covariance.
+Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this
 method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominated modes which are coupled to the data results in negligible signal loss. However, we do 
-not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most of the modes.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
+eigenspectrum with $1$'s (equal weights).
+Again, avoiding the overfitting of EoR-dominated modes which are coupled to the data results in negligible signal loss.
+While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are foreground or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
 We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
@@
 panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
-For this toy model,
-our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
-the identity, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
+To understand this, we recall that our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
+Multiplying by
+the identity matrix, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
 suppressing the foreground.
@@
 
-In summary, we have a choice of how to weight 21\,cm data. Ideally, we want to down-weight bright foregrounds without 
-removing the underlying cosmological signal. However, there are trade-offs between the weighting method 
-used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
+In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are not converged to their true forms.
+We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
 
@@
 data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
+Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
 

### 2018-08-29 PAPER.tex
read-through edits up until section 4.2

@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each minimize signal 
-loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to 
-it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
-$\widehat{\textbf{C}}$ (lower right). The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
+	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
+We show four alternate weighting options that each minimize signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\widehat{\textbf{C}}$ (lower right).
+The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
 	\label{fig:toy_sigloss8}
@@
 
-In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are not converged to their true forms.
+In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are coupled to data and not converged to their true forms.
 We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
@@
 
-\section{Signal Loss Case Study}
+\section{Signal Loss in PAPER-64}
 \label{sec:CaseStudy}
 
-In the previous section we used toy models to show how signal loss arises when weighting data with empirically estimated covariances.
-We also demonstrated how an analysis technique like fringe-rate filtering can increase loss, and how simple regularization methods can minimize loss.
-
-We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
-\citetalias{ali_et_al2015} in order to illustrate our revised analysis pipeline.
+We now turn to a detailed signal loss investigation using a subset of the PAPER-64 dataset from \citetalias{ali_et_al2015}.
+In the previous section we showed how signal loss arises when weighting data with empirically estimated covariances; in this section we highlight how the amount of this loss was underestimated in the previous analysis.
+Additionally, we illustrate how we have revised our analysis pipeline in light of our growing understandings.
 
@@
 	\centering
-	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
 	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
@@
 \citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues presented in this paper).
+(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues that will be made clear later on).
 
@@
 Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
+Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}.
 
@@
 \label{sec:siglossmethod}
-In short, our method consists of adding an EoR-like signal into the visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
+In short, our method for estimating signal loss consists of adding an EoR-like signal into visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
@@
 We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
-In the remainder of this paper, we will transition to other new aspects of our analysis, framed within the context of error estimation and (non-EoR) bias in PAPER-64.
+In the remainder of this paper, we will transition to other aspects of our analysis that have been revised since \citetalias{ali_et_al2015}.
 
@@
 
-\section{Summary of Additional Errors}
+\section{Additional PAPER-64 Revisions}
 \label{sec:OtherErrors}
@@
 We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
-We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified.
+We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified through simulations.
 
@@
 
-Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
-spectra) can be made from different samples of data.
-Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
-between them. Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for 
-our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements). 
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
-of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
-from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
-the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
-here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one). The error (on 
-the mean) is then computed as the standard deviation across all bootstraps.
-
-We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
-values, that comprise a bootstrap. $N_{\rm boot}$ is typically large, and the standard 
-deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
+Bootstrapping uses sampling with replacement to estimate a posterior distribution.
+For example, bootstrap measurements (of power spectra, for example) can be made from different random samples of data.
+Each of these bootstraps is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
+Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
+
+%Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements).
+Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
+Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap).
+Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
+The error (on the mean) is then computed as the standard deviation across all bootstraps.
+
+%We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
+$N_{\rm boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
 Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
@@
 
-Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean). 
-This could represent $1000$ power spectrum measurements, for which we are interested in its error. We predict that the error 
-on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-We next form $500$ bootstraps ($N_{\rm boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
-original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
-estimate for our dataset. This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical 
-prediction (green).
+%Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
+This could represent $1000$ power spectrum measurements, for which we are interested in its error.
+We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+%We next form $500$ bootstraps ($N_{\rm boot} = 500$).
+To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
+The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
+This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
 
@@
 
-As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of 
-independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
-earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$). This occurs 
-because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
-in all bootstraps, leading to less variation between the bootstraps. In fact, the error derived from bootstrapping is a strong 
-function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
-underestimate the error by drawing too many or overestimate it by drawing too few. However, since we know that we have $100$ 
-independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction 
-as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-sampling with replacement. The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ 
-elements (with replacement) from a length $1000$ array of a Gaussian random signal.
+%As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of independent data samples to $N/10 = 100$.
+Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$).
+This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
+In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both underestimate the error by drawing too many or overestimate it by drawing too few.
+However, since we know that we have $100$ independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
+%	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
+%sampling with replacement.
+The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
 The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if
-drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
-prediction only at $N=100$.}
-	\label{fig:toy_error1}
-\end{figure}
-
-Analogous to the toy model just presented, errors on the power spectrum of PAPER-64 were originally underestimated because the use of a fringe-rate filter, which averages data in time to increase sensitivity, reduces the number of independent samples along the bootstrapping axis, thus decreasing the variance of the bootstraps.
+They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
+The estimated errors match up with the theoretical prediction only at $N=100$.}
+%	\label{fig:toy_error1}
+%\end{figure}
+
+This is the precisely how errors were underestimated in PAPER-64.
+Because of fringe-rate filtering, which averages data in time to increase sensitivity, PAPER-64 data is correlated along the time axis.
+Hence, there are fewer independent samples after filtering, thus decreasing the variance of the bootstraps.
 
 More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time. In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
-($N_{\rm boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
+spectrum that is a function of $k$ and time.
+In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis, and a total of $400$ bootstraps were created in this step, each comprised of randomly selected values sampled with replacement (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
 $700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
@@
 exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds ($N_{\rm boot}$) of these random 
+measurements from this dataset has many repeated values, and the variance between hundreds of these random 
 samples is smaller than the true underlying variance of the data.
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally underestimated by a factor of $\sim$ $5$ in mK$^{2}$.
+While Figure \ref{fig:data_errors} implies that errors are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
@@
 
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into $5$ independent groups, where no baselines were repeated in each group.
+\item{In \citetalias{ali_et_al2015}, individual baselines were divided into five independent groups, where no baselines were repeated in each group.
 Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.

### 2018-08-30 PAPER.tex
read-through edits up until appendices

@@
 
-In addition to bootstrapping, another method of error estimation is to compute a theoretical estimation of thermal noise based on observational parameters.
+One useful way of cross-checking measured power spectrum values and errors is to compute a theoretical estimation of thermal noise based on observational parameters.
 Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-
-Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations, and what was 
-found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations. The analytic 
-calculation is only an approximation; however, the differences were large enough (factors of $10$ in some cases) to warrant a 
-careful investigation. This calculation attempts to combine a large number of pieces of information in an approximate 
-way, and when re-considering some of the approximations, we have found there to be large effects. What follows here is an 
+Upon re-analysis of PAPER-64, we have discovered that this estimate was also underestimated in previous analyses.
+
+To compute our theoretical noise estimate, we use an analytic sensitivity calculation.
+Through detailed studies using several independently generated noise simulations, what we found was that our simulations all agreed but were discrepant with the previous calculations.
+The analytic
+calculation is only an approximation and attempts to combine a large number of pieces of information in an approximate way; however, when re-considering some of the approximations, the differences were large enough (factors of $10$ in some cases) to warrant a
+careful investigation. What follows here is an 
 accounting of the differences which have been discovered.
-Our revised theoretical error estimation, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
+We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
 
@@
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying independent ``even" and ``odd" visibility measurements (this cross-multiplication is done principally to avoid a noise bias).
-In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
+estimates after cross-multiplying two independent visibility measurements. In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
 \item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
@@
 However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
-While the noise simulation provides an indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
+While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
 We therefore interpret our noise prediction as the sensitivity floor for our measurements.
@@
 Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
-(\textit{in prep.}) uses a straightforward power spectrum estimation approach that is not lossy.
+(\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
 However, the main reasons for a previously underestimated limit and
@@
 \ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-underestimated signal loss therefore represents the bulk of our revision.
+Underestimated signal loss therefore represents the bulk of our revision.
 \item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).

### 2018-08-30 PAPER.tex
read-through edits up until the end

@@
 
-In our toy model, we specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+We specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
 We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
@@
 \noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Using Equations \eqref{eq:prob} and \eqref{eq:logprob}, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} becomes:
-
-%\begin{equation}
-%\label{eq:logprob_full}
-%\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
-%\end{equation}
-
-%Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of %Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
-
-\begin{eqnarray}
-\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
-&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
-\end{eqnarray}
-
-Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
+Combining Equations \eqref{eq:jeffreys}, \eqref{eq:logprob}, and \eqref{eq:prob} the Jeffreys prior simplifies to become:
+
+%\begin{eqnarray}
+%\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
+%&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
+%\end{eqnarray}
+
+%Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
 Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
@@
 For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
-	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
+%An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
+%	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
 Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
 The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
-	\label{fig:jeffreys1}
-\end{figure}
-
-We also show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
+%	\label{fig:jeffreys1}
+%\end{figure}
+
+We show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
 Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.

### 2018-09-10 PAPER.tex
all new plots compiled in paper

@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
-only the $\sim2$-$3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting does not actually outperform uniform weighting).
+only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting).
 For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
@@
 We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e., when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
+their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.

### 2018-09-10 plotting_scripts/plot_PS_invcov.py
status of directories and scripts for referee response

@@ -128,8 +128,6 @@ for filename in files:
     cosmo_factor /= (1+z) * (ckm/Ho)
     horizon = 90 * cosmo_factor * np.pi/180 * pspec_dict['kperp']
     horizon_delta2 = np.sqrt(horizon**2 + pspec_dict['kperp']**2)
-    horizon /= 2 # XXX divide by 2 because of bug (kperp two times too big?)
-    horizon_delta2 /= 2
     for _ax in delta2_list:
         _ax[gs_ind].axvline(horizon_delta2, color='black', linestyle='--',
                             ymin=-.1, ymax=1.1)

### 2018-09-10 plotting_scripts/plot_PS_reg.py

@@ -128,8 +128,6 @@ for filename in files:
     cosmo_factor /= (1+z) * (ckm/Ho)
     horizon = 90 * cosmo_factor * np.pi/180 * pspec_dict['kperp']
     horizon_delta2 = np.sqrt(horizon**2 + pspec_dict['kperp']**2)
-    #horizon /= 2 # XXX divide by 2 because of bug (kperp two times too big?)
-    #horizon_delta2 /= 2
     for _ax in delta2_list:
         _ax[gs_ind].axvline(horizon_delta2, color='black', linestyle='--',
                             ymin=-.1, ymax=1.1)

### 2018-09-10 plotting_scripts/plot_jackknives.py

@@ -28,8 +28,8 @@ mask = n.ma.masked_where(mask==0, mask)
 horizon = 0.06272882578029243 # computed using hera_pspec.conversions.Cosmo_Conversions.tau_to_kpara
 
 # Plot range
-ymin=-6e9
-ymax=6e9
+ymin=-1e9
+ymax=1e9
 
 #------------------------
 

### 2018-09-10 plotting_scripts/plot_sigloss_modeloop.py

@@ -28,7 +28,7 @@ if True: # added identity parameters in LOG space
     loop_add = n.logspace(startmode_add,endmode_add,nmodes_add)
 
 # Read files
-sense=14419782.9029*2 / n.sqrt(2) # XXX from plotting one of the "project_#_modes" directories (divide by sqrt(2) for folded case)
+sense=14419782.9029*2 #/ n.sqrt(2) # XXX from plotting one of the "project_#_modes" directories (divide by sqrt(2) for folded case)
 #sense=14419782.9029*2  # unfolded version
 PS_i_up = []
 PS_f_up = []
@@ -42,17 +42,17 @@ for mode_num in loop:
     print 'Reading', filename
     print mode_num
     f = n.load(filename+'/pspec_final_sep0,1_full.npz')
-    kpl = f['kpl_fold'] # folded version
-    #kpl = f['kpl'] # unfolded version
+    #kpl = f['kpl_fold'] # folded version
+    kpl = f['kpl'] # unfolded version
     k = kpl[k_ind] 
-    PS_i_up.append(2*n.array(f['pCv_fold_err_old'])[k_ind]) # folded version
-    PS_f_up.append(2*n.array(f['pCv_fold_err'])[k_ind])
-    PS_i.append(n.abs(f['pCv_fold_old'])[k_ind])
-    PS_f.append(n.abs(f['pCv_fold'])[k_ind])
-    #PS_i_up.append(2*n.array(f['pCv_err_old'])[k_ind]) # unfolded version
-    #PS_f_up.append(2*n.array(f['pCv_err'])[k_ind])
-    #PS_i.append(n.abs(f['pCv_old'])[k_ind])
-    #PS_f.append(n.abs(f['pCv'])[k_ind])
+    #PS_i_up.append(2*n.array(f['pCv_fold_err_old'])[k_ind]) # folded version
+    #PS_f_up.append(2*n.array(f['pCv_fold_err'])[k_ind])
+    #PS_i.append(n.abs(f['pCv_fold_old'])[k_ind])
+    #PS_f.append(n.abs(f['pCv_fold'])[k_ind])
+    PS_i_up.append(2*n.array(f['pCv_err_old'])[k_ind]) # unfolded version
+    PS_f_up.append(2*n.array(f['pCv_err'])[k_ind])
+    PS_i.append(n.abs(f['pCv_old'])[k_ind])
[…]

### 2018-09-10 plotting_scripts/plot_sigloss_terms.py

@@ -68,13 +68,17 @@ black_ind_pos = n.where(Pouts>=0)[0] # where positive Pouts
 black_ind_neg = n.where(Pouts<0)[0] # where negative Pouts
 Pins_black_pos = Pins[black_ind_pos] # adjust Pins
 Pins_black_neg = Pins[black_ind_neg]
-poly_Pouts_pos = n.polyfit(n.log10(Pins_black_pos),n.log10(Pouts[black_ind_pos]),poly_dim)
-poly_Pouts_neg = n.polyfit(n.log10(Pins_black_neg),n.log10(-Pouts[black_ind_neg]),poly_dim)
+Pins_black_neg = n.append(10,Pins_black_neg) # XXX hack to add first point to extend curve back
+Pouts_black_pos = Pouts[black_ind_pos]
+Pouts_black_neg = -Pouts[black_ind_neg]
+Pouts_black_neg = n.append(1e5,Pouts_black_neg)*3 # XXX hack to add first point to extend curve back and drag the curve down just a tad (otherwise the polynomial fit drags it up due to some outliers)
+poly_Pouts_pos = n.polyfit(n.log10(Pins_black_pos),n.log10(Pouts_black_pos),poly_dim)
+poly_Pouts_neg = n.polyfit(n.log10(Pins_black_neg),n.log10(Pouts_black_neg),poly_dim)
 black_neg = -10**n.polyval(poly_Pouts_neg,n.log10(Pins_black_neg))
 black_pos = 10**n.polyval(poly_Pouts_pos,n.log10(Pins_black_pos))
 
 black_ind_pos_I = n.where(Pouts_I>=0)[0] # where positive Pouts_I
-black_ind_neg_I = n.where(Pouts_I<0)[0][:-1] # where negative Pouts_I # XXX remove last entry (outlier in some cases that cause the curve to look weird)
+black_ind_neg_I = n.where(Pouts_I<0)[0]#[:-1] # where negative Pouts_I # XXX remove last entry (outlier in some cases that cause the curve to look weird)
 Pins_black_pos_I = Pins[black_ind_pos_I] # adjust Pins
 Pins_black_neg_I = Pins[black_ind_neg_I]
 poly_Pouts_pos_I = n.polyfit(n.log10(Pins_black_pos_I),n.log10(Pouts_I[black_ind_pos_I]),poly_dim)

### 2018-09-10 PAPER.tex
version of paper and diffs sent to collaboration as response to referee report

@@
 It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
-Specifically, with a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
+Specifically, with a statistical power spectrum detection in HERA's foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
 In this paper, we focus on signal loss associated with power spectrum estimation.
@@
 Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
-While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
+We focus on a subset of PAPER-64 data in this paper; revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
 (\textit{in prep.}) and supersede results from previously published PAPER analyses.
@@
 Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
-This paper adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
+This paper accompanies the erratum of \citet{ali_et_al2018} and adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
 These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
@@
 (\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
-However, the main reasons for a previously underestimated limit and
+However, the main reasons for a previously underestimated limit (\citealt{ali_et_al2018}) and
 ways in which our new analysis differs can still be summarized by the following:

### 2018-09-20 PAPER.tex
made small adrian edits

@@
 green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
-It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
+%It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
 This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
@@
 It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
-Realistically, these details about the EoR signal are unknown, and therefore our signal loss framework is subject to bias.
+Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations.
 Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
@@
 bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
-\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
+Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
+\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
 shown in the figure, when more elements are drawn for each bootstrap than the number of 
@@
 Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
 
@@
 While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
-We therefore interpret our noise prediction as the sensitivity floor for our measurements.
+Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations.
+Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
 

### 2018-09-21 PAPER.tex
made jonnie edits

@@
 
-Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminates in order to obtain an unbiased estimate of the power spectrum.
+Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminants in order to obtain an unbiased estimate of the power spectrum.
 By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
@@
 The way in which the optimal estimator accomplishes this is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
-In this appendix, we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
+In this appendix, we show that the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
 Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
@@
 %First, 
-We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \ref{eq:qhat} and \ref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \eqref{eq:qhat} and \eqref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
@@
 
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
+For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \eqref{eq:IdealToyModelCovariance} and \eqref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
 However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
@@
 	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples.
+In red, the mock EoR signal is comprised entirely of independent samples (100 of them).
 Subsequent colors show time-averaged signals.
@@
 accounting of the differences which have been discovered.
-We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
+We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots in this paper, is computed with these changes accounted for.
 
@@
 \end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \ref{eq:OQE} is
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \eqref{eq:OQE} is
 \begin{equation}

### 2018-10-08 PAPER.tex
-Removed appendices and all references to them :( -Clarified statement about sources of signal loss in the analysis pipeline pre-PS

@@
 However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
-The way in which the optimal estimator accomplishes this is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
-In this appendix, we show that the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
+
+More specifically, the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
 Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-
-The toy model in Appendix \ref{sec:icw_appendix} also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
+If the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
 Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
@@
 As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in a nearly unbiased estimate of the power spectrum.
+Rather, we would obtain %the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in
+a nearly unbiased estimate of the power spectrum.
 The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
 
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \eqref{eq:IdealToyModelCovariance} and \eqref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
+For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection; whether or not it is strongly correlated with the the actual data vector is irrelevant.
 However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
 If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As described in Section \ref{sec:siglossmethod} and shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
+As described in Section \ref{sec:siglossmethod}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
 In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
@@
 In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), which leads to loss.
+More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
 Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
@@
 \citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
+as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
 \emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
@@
 Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
-As mentioned in Section \ref{sec:SiglossOverview}, there are several other ways the PAPER analysis pipeline can lead to loss, including through calibration and delay-filtering.
-We refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015} for discussions about these other types of signal loss, noting here that they are much less significant than the loss focused on in this paper.
+As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
+Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
 
@@
 
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized.
+{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
 Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
@@
 We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
-For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
+%For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
 
@@
 
+\begin{comment}
+
 \appendix

### 2018-10-09 PAPER.tex
-Edited paragraph about signal loss from other analysis changes to state that future work will exercise more caution

@@
 As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
-Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
+Here we only focus on the most significant source of loss we have identified and note that Kolopanis et al.
+(\textit{in prep.}) and other future work will consider additional sources of signal loss and exercise increased caution in reporting results.
 

### 2018-10-09 Memo1_inversecov.tex
adding memos corresponding to 3 appendices

--- 2018-10-08 PAPER.tex
@@
-\documentclass[preprint2,numberedappendix,tighten]{aastex6}  % USE THIS TO MAKE BIB, THEN FORMAT USING EMULATEAPJ
-%\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
-\shortauthors{Cheng et al.}
-
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[figuresright]{rotating}
-\usepackage{natbib}
-\usepackage{ctable}
-\usepackage{comment}
-\usepackage{bm}
-%\usepackage{mathtools}
-\usepackage{xparse}
-%\usepackage{titlesec}
+\documentclass[12pt,preprint]{aastex}
+\usepackage[margin=1in]{geometry}
+\usepackage{float,amsmath,bm,natbib,graphicx}
 \citestyle{aa}
@@
 
-%Math stuff from Danny
-\NewDocumentCommand{\evalat}{sO{\big}mm}{%
-  \IfBooleanTF{#1}
-   {\mleft. #3 \mright|_{#4}}
-   {#3#2|_{#4}}%
-}
-
-%		Math Shortcuts from Adrian
-%\def\b{\mathbf{b}}
-%\def\k{\mathbf{k}}
-%\def\r{\mathbf{r}}
-%\def\q{\mathbf{q}}
-%\def\b{\mathbf{b}}
-%\def\kp{\mathbf{k}^\prime}
-%\def\kpp{\mathbf{k}^{\prime\prime}}
-%\def\V{\mathbb{V}}
-%\def\At{\tilde{A}}
-%\def\Vt{\tilde{V}}
-%\def\Tt{\tilde{T}}
-%\def\tb{\langle T_b\rangle}
-%\newcommand{\vis}{\mathbf{v}}
 \newcommand{\x}{\mathbf{x}}
@@
 \newcommand{\I}{\mathbf{I}}
-%\newcommand{\xhat}{\widehat{\mathbf{x}}}
-%\newcommand{\nhat}{\widehat{\mathbf{n}}}
-%\newcommand{\A}{\mathbf{A}}
-%\newcommand{\N}{\mathbf{N}}
-%\newcommand{\rhat}{\widehat{\mathbf{r}}}
-%\newcommand{\khat}{\widehat{\mathbf{k}}}
-%\newcommand{\btheta}{\boldsymbol \theta}
-
-\newcommand{\cc}[1]{{\color{purple} \textbf{[CC: #1]}}}
-\newcommand{\acl}[1]{{\color{red} \textbf{[ACL:  #1]}}}
-\newcommand{\dcj}[1]{{\color{orange} \textbf{[DCJ: #1]}}}
-\newcommand{\mjk}[1]{ {\color{olive} \textbf{[MJK: #1]}} }
-\newcommand{\jea}[1]{{\color{blue} \textbf{[JEA: #1]}} }
-\newcommand{\jp}[1]{ {\color{pink} \textbf{[JCP: #1]}} } %y'all picked all the good colors
-
-% Math shortcuts from James
 \newcommand{\invC}{\ensuremath{\C^{-1}}}
@@
 
-% Math shortcuts from Danny
-\newcommand{\Prob}{\mathbf{P}}
+\begin{document}
 
-\begin{document}
-\title{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64}
+\title{A Toy Model for Inverse Covariance Weighting} 
+\author{James Aguirre, Carina Cheng, and the PAPER Collaboration}
+\maketitle
+\vspace{1cm}
+%\section{A Toy Model for Signal Loss}
 
-\author{
-Carina Cheng\altaffilmark{1}$^{,\diamond}$,
-Aaron R. Parsons\altaffilmark{1,2},
-Matthew Kolopanis \altaffilmark{3},
-Daniel C. Jacobs\altaffilmark{3}, 
-Adrian Liu\altaffilmark{1,4}$^{,\dagger}$, 
-Saul A. Kohn\altaffilmark{5},
-James E.~Aguirre\altaffilmark{5},
-Jonathan C. Pober\altaffilmark{6}, 
-Zaki S. Ali\altaffilmark{1}, 
-Gianni Bernardi\altaffilmark{7,8,9}, 
-Richard F. Bradley\altaffilmark{10,11,12},
-Chris L. Carilli\altaffilmark{13,14},
-David R. DeBoer\altaffilmark{2}, 
-Matthew R. Dexter\altaffilmark{2},
-Joshua S. Dillon\altaffilmark{1}$^{,*}$,
-Pat Klima\altaffilmark{11},
-David H. E. MacMahon\altaffilmark{2},
-David F. Moore\altaffilmark{5},
-Chuneeta D. Nunhokee\altaffilmark{8},
-William P. Walbrugh\altaffilmark{7},
-Andre Walker\altaffilmark{7}
-}
+In this memo, we focus on the optimal quadratic estimator, defined as:
 
-\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
-\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
-\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
-\altaffiltext{4}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
-\altaffiltext{5}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
-\altaffiltext{6}{Dept. of Physics, Brown University, Providence RI}
-\altaffiltext{7}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{8}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{9}{INAF-Instituto di Radioastronomia, Bologna Italy}
-\altaffiltext{10}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
-\altaffiltext{11}{National Radio Astronomy Obs., Charlottesville VA}
-\altaffiltext{12}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
-\altaffiltext{13}{National Radio Astronomy Obs., Socorro NM}
-\altaffiltext{14}{Cavendish Lab., Cambridge UK}
-
-%		Notes
-
-%Reference section with: \ref{sec:Intro}
-%Reference equation with: \eqref{eq:eqtest}
-%Reference figure with: \ref{fig:figtest}
-%Cite paper inside sentence: \citet{ref}
-%Cite paper at end of sentence: \citep{ref}
-%Cite paper inside a parenthetical sentence: \citealt{ref}
-
-%To compile with references shown, compile in BibTeX once and LaTeX twice
-
-%		Sample Equation Syntax
-%\begin{equation}
-%\label{eqtest}
-%\langle \widetilde{T} (\mathbf{k}) \widetilde{T}^* (\mathbf{k^\prime}) \rangle = (2 \pi)^3 \delta^D (\mathbf{k} - \mathbf{k}^\prime) P(k),
-%\end{equation}
-
-% ABSTRACT ---------------------------------------------------------------------------------
-
-\begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
-galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the 21\,cm line of neutral hydrogen.
-Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data.
-It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
-Specifically, with a statistical power spectrum detection in HERA's foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
-In this paper, we focus on signal loss associated with power spectrum estimation.
-We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
-Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
-We focus on a subset of PAPER-64 data in this paper; revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
-(\textit{in prep.}) and supersede results from previously published PAPER analyses.
-\end{abstract}
-
-% INTRO ---------------------------------------------------------------------------------
-
-\section{Introduction}
-\label{sec:Intro}
-
-{\let\thefootnote\relax\footnote{$^{\diamond}$\href{mailto:ccheng@berkeley.edu}{ccheng@berkeley.edu}}}
-{\let\thefootnote\relax\footnote{$^{\dagger}$Hubble Fellow}}
-{\let\thefootnote\relax\footnote{$^{*}$NSF AAPF Fellow}}
-\setcounter{footnote}{0}
-
-By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
-neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
-luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
-into a plasma, is known as the Epoch of Reionization (EoR).
-The EoR is a relatively unexplored era in our Universe's history, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
-This epoch encodes important information regarding the nature of the first galaxies and the processes of structure formation.
-Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
-between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
-
-One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
-This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
-of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. Hence, 21\,cm tomography offers a unique window into both the spatial and temporal
-evolution of ionization, temperature, and density fluctuations.
-
-In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
-the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
-mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
-Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
-Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
-(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
-\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
-Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
-the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
-\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
-Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
-detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).
-
-The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results.
-More specifically, it is imperative to develop techniques that ensure
-the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method.
-In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation.
-This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis.
-We first approach this topic from a broad perspective, and then perform a detailed
-case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al.
-(\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
-
-Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
-This paper accompanies the erratum of \citet{ali_et_al2018} and adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
-These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
-
-This paper is organized into three main sections.
-In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
-In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss.
-In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis.
-Finally, we conclude in Section \ref{sec:Con}.
-
-% SECTION 2 SIGLOSS TOY MODEL ---------------------------------------------------------------------------------
-%\color{blue}
-
-\section{Signal Loss Toy Models}
-\label{sec:SiglossOverview}
-% JEA - We never totally nail down what ``signal loss'' is ...
-
-Signal loss refers to attenuation of the target cosmological signal 
-in a power spectrum estimate.
-Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits.
-Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
-
-One type of signal loss can occur when weighting data by itself.
-Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others.
-For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
-Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
-However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
-In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
-This loss was significantly 
-%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.
-
-% JEA - Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
-
-\subsection{The Quadratic Estimator Method}
-\label{sec:QE}
-
-%AAAICW
-
-We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation.
-The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
-Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain.
-If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in
-% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
-%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
-This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in
-\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
-%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-
-% JEA - The discussion of dimensions here is confusing ...
-"a baseline" is mentioned, but it's not clear if the redundant baseline averaging has already happened or what.
-I believe we are only considering covariance between frequencies, but this isn't explicitly said, and the matrix equations don't make sense unless all the dimensions are N_f N_t.
-%We begin with our 
-Suppose that the measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
-% JEA - not sure this helps
-%, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), 
-where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. The covariance of the data is given by 
-\begin{equation}
-\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle = \textbf{S} + \textbf{U}
-\end{equation}
-where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as the sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
-
-We are interested in estimating the three-dimensional power spectrum of the EoR.  
-Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
-We consider band powers $P^\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-The fundamental dependence of the covariance on the power spectrum band powers $P^\alpha$ is encoded as
-% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
-\begin{equation}
-\textbf{S} = \sum_\alpha P^\alpha \frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \sum_\alpha P^\alpha \textbf{Q}^\alpha
-%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
-%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
-\end{equation}
-where we define $\frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \textbf{Q}^{\alpha}$.
-In other words, $\textbf{Q}$ describes the response of the covariance to a change in the power spectrum, relating a quadratic statistic of the data (the covariance) to a quadratic statistic in Fourier-space (the power spectrum).
-% JEA - ah, the dimensions again
-% which has dimensions ($N_{f}$,$N_{f}$).
-
-The optimal quadratic estimator prescription is then to compute
 \begin{equation}
@@
 \end{equation}
-The power spectrum estimator in Equation \eqref{eq:OQE} is the minimum variance (smallest error bar) estimate of the power spectrum subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
-\begin{equation}
-\label{eq:super_unbiased}
-\langle \widehat{P}^{\alpha} \rangle = P^\alpha
-\end{equation}
-\citep{tegmark_et_al1997a,bond_et_al1998}.
 
-Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminants in order to obtain an unbiased estimate of the power spectrum.
-By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
-However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
-
-More specifically, the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
-Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-If the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
-Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
-Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, and which can conservatively be interpreted as an upper limit.
-These considerations, and the difficulty of obtaining an estimate for $\mathbf{U}$, motivate the neglect of the linear bias in the rest of this analysis.
-
-%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
-%which may still produce an unbiased estimate, 
-where Equation \eqref{eq:OQEQuadratic} is replaced by
-\begin{equation}
-\label{eq:qhat}
-\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
-\end{equation}
-where $\textbf{R}$ is a weighting matrix chosen by the data analyst.
-For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
-%with dimensions ($N_{f}$,$N_{f}$) --- as
-
-%%% COME BACK HERE
-% Need to still explain the motivation for this
-With an appropriate normalization matrix $\textbf{M}$, the quantity
-%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
-\begin{equation}
-\label{eq:phat}
-\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
-\end{equation}
-is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.
-
-To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
-\begin{eqnarray}
-\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
-&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
-\end{eqnarray}
-where $W^{\alpha \beta}$ are elements of a window function matrix.
-Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
-However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
-In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized.
-Beyond this, the data analyst has a choice for $
-\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal.
-In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
-If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
-% JEA - is one really free to choose M and R independently?
-
-% JEA - I don't think it's attractive at all
-%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
-Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data to obtain:
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
-\end{equation}
-assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
-We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:CaseStudy}.
-
-%\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
-
-As a brief preview, we summarize our findings in the following sections here:
-
-\begin{itemize}
-
-\item If the covariance matrix is estimated from the data, a strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss''  (Section \ref{sec:toymodel}).
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced (Section \ref{sec:toymodel_frf}).
-
-\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum.
-In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).
-
-%\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
-Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable (Section \ref{sec:toymodel_frf}).
-
-\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to decouple it from the data and produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
-
-% JEA - I really struggle with whether this is intuitively obvious ...
-it's hard to get a sense of what "noise" is averaging down slower.
-All modes have the same number of samples going into the estimate.
-Should I think of the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
-% Also, have we shown this sufficiently rigorously?
-Is the toy model sufficiently general?
-(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
-Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
-
-\end{itemize}
-
-\subsection{Empirical Inverse Covariance Weighting}
-\label{sec:toymodel}
-
-% JEA  - This material was moved up
-%One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
-Said differently, it gives the minimum variance estimate of the power spectrum (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
-%
-%One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
-By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
-Therefore, in an ideal world with perfect foreground,
-%instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
-In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
-
-%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss. 
-Using a toy model, we will now build intuition into how weighting by the inverse of the empirically estimated covariance, $\widehat{\textbf{C}}^{-1}$, can give rise to signal loss.
-We construct a simple dataset that contains visibility data with $100$ time integrations and $20$ frequency channels.
-This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of generality.
-
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation.
-Hence, flat spectrum sources (away from zenith) lead to measured visibilities which oscillate in time and frequency.
-We therefore form a mock visibility measurement of a bright foreground signal, $\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
-We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal.
-A more realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
-However, here we treat all $k$'s separately, so a simplistic white noise approximation can be used.
-Our combined data vector is then $\textbf{x} =
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
-\ref{fig:toy_sigloss1}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.pdf}
-	\caption{Our toy model dataset to which we apply different weighting schemes to in order to investigate signal loss.
-We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in
-time and frequency. We model a mock visibility of an EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$. Real parts are shown here.}
-	\label{fig:toy_sigloss1}
-\end{figure}
-
-%First, 
-We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \eqref{eq:qhat} and \eqref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
-The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
-The power spectrum result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
-Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
-As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds,
-%For our toy model, the successful suppression of the foreground mode is 
-demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
-It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-It is this behavior which we describe as signal loss.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
-	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
-(middle), and FG + EoR (right). Real parts are shown here.}
-	\label{fig:toy_sigloss12}
-\end{figure}
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.pdf}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The power spectrum of the foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare using empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the zeroth eigenmode only (right).
-In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
-% JEA - redundant
-%For an empirically estimated $\widehat{\textbf{C}}$, 
-%its eigenvalues differ from those of the true covariance, where 
-%the coupling between EoR-dominated eigenmodes and the data can lead to loss.
-%Hence, 
-There is negligible signal loss when all eigenmodes besides the foreground one are no longer correlated with the data.
-%assigning identical weights to all eigenmodes except the first, 
-%constructing a covariance proportional to the identity and the outer product of the sinusoid eigenmode, since we are only down-weighting the FG-dominated mode in this case.
-}
-	\label{fig:toy_sigloss3}
-\end{figure*}
-
-As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain %the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in
-a nearly unbiased estimate of the power spectrum.
-The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
-
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection; whether or not it is strongly correlated with the the actual data vector is irrelevant.
-However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
-If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As described in Section \ref{sec:siglossmethod}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
-
-%For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
-Here we will describe the origin of this signal loss intuitively.
-
-%% JEA - I don't think the eigenspectrum really helps, but at some point we probably want to show it ...
-%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
-%
-%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
-In other words, the eigenvalues encode the strength of different shapes in the dataset.
-The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-%% JEA - I think this is actually NOT true - see the toy model as an example.
-The size of the eigenvalues isn't what determines that the undesired mode is downweighted and the others left alone.
-I haven't computed the eigenvalues explicitly, but down-weighting of m occurs regardless of the relative size of s and u.
-%The modes with the highest eigenvalues are down-weighted the most.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
-%(green).
-The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of the true $\textbf{C}$.
-Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
-%	\label{fig:toy_sigloss2}
-%\end{figure}
-
-%We show the {\it eigenspectrum} (the eigenvalues of the matrix in descending order) of this toy model in Figure \ref{fig:toy_sigloss2}.  In this case,
-%For example, 
-%the largest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}). 
-%
-
-%In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
-For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
-
-%If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
-%representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
-%particular data realization, its eigenvalues and eigenvectors may differ from the truth.
-Said differently, shapes that may not exist (or exist rarely) in a true covariance may appear stronger in the estimated covariance.
-Hence, they will be down-weighted
-%more than they should be.
-
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
-
-Armed with this information,
-%Using what we've learned about the eigenspectrum, 
-we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
-% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
-%is a sinusoid, so it 
-can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
-project out the zeroth eigenmode and 
-%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
-then take the remaining covariance to be the identity matrix.  
-This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
-In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
-% down-weight them 
-foregrounds with negligible signal loss.
-
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization.
-There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
-\ref{sec:otherweight}.
-
-\subsection{Fringe-Rate Filtering}
-\label{sec:toymodel_frf}
-
-We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data.
-We will next show how this effect is exacerbated by reducing the total number of independent samples in a dataset.
-
-A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.
-
-Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
-With fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
-We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
-
-% JEA - Death to eigenspectra!
-%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}.
-
-\begin{equation}
-\label{eq:converge}
-\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
-\end{equation}
-where $\C$ is the true covariance matrix.
-To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average.
-We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
-As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following time-averaging, or ``fringe-rate filtering" (different colors).
-With more independent time samples (i.e., more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
-
-The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
-of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
-number of independent simulations results in inaccuracies in estimated covariance matrices 
-\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
-\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
-\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
-galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
-cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
-theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
-marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
-\citep{pope_szapudi2008,joachimi_2017}.
-
-%Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
-This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
-For this particular toy model, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
-For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance by averaging over the realizations.
-The eigenvectors of this empirical covariance are then compared to the true eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
-\begin{equation}
-\label{eq:converge_eig}
-\varepsilon (\widehat{\textbf{v}}) \equiv \sqrt{\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i}^2},
-\end{equation}
-where $N_{f}$ is the number of frequencies ($20$) in the mock data.
-The eigenmode convergence curves in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-We see that the zeroth eigenmode --- the mode describing the foreground signal --- is quickest to converge.
-
-Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate.
-In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances.
-Consider first a limiting case where all eigenvalues are equal.
-In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors.
-In our current test, aside from the zeroth mode, the eigenvalues have similar values but are not precisely equal.
-Hence, there is a well-defined set of eigenvectors to converge to.
-However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
-Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to decouple from each other and approach their true forms.
-A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate.
-To break degeneracies in the remaining modes, however, requires many more realizations.
-
-While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
-The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss.
-However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
-
-In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
-Even for the case of real PAPER data (Section \ref{sec:CaseStudy}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
-However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
-
-%One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
-With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
-As we will see in the next section, using only these eigenmodes, which are less coupled to data realizations, minimizes signal loss.
-In contrast, the lower-valued eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-% JEA - this is redundant
-%Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
-%\acl{Think about whether we need to do the Fourier space version as well.}
-
-% JEA - death to eigenspectra!
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
-The dashed, steep eigenspectrum has a greater risk of signal loss because its lowest-valued eigenmodes are both more strongly coupled to the data (than those of the solid eigenspectrum) and, in this example, are also EoR-dominated.}
-%	\label{fig:toy_sigloss15}
-%\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples (100 of them).
-Subsequent colors show time-averaged signals.
-As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges (i.e., the quicker it decouples from the data), and the less signal loss we would expect to result.}
-	\label{fig:toy_sigloss16}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
-The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the zeroth eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
-On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
-	\label{fig:toy_sigloss17}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
-	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here.}
-	\label{fig:toy_sigloss5}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
-	\caption{Resulting power spectrum estimate for the ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We use empirically estimated inverse covariance weighting where $\textbf{C}$ is 
-computed from the data.
-There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by eigenmodes that are more strongly coupled to the data due to there being fewer independent modes in the data.}
-	\label{fig:toy_sigloss7}
-\end{figure}
-
-With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal.
-We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank.
-We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
-%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
-
-The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
-expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
-In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter.
-This is evident by noticing that the
-green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
-%It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
-This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
-
-Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal 
-loss and noisier estimates when using data-estimated covariance matrices. Longer integrations increase sensitivity but reduce 
-the number of independent samples, resulting in 
-eigenmodes correlated with the data
-% JEA - it's not that they are wrong, but that they are correlated
-%poorly characterized, steep eigenspectra 
-that can overfit signal greatly. We 
-note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be 
-advantageous to use one despite the trade-offs.
-
-\subsection{Other Weighting Options}
-\label{sec:otherweight}
-
-In Section \ref{sec:toymodel} we showed one example of how altering $\widehat{\textbf{C}}$ can 
-make the difference between nearly zero and some signal loss. We will now use our toy model to describe several other ways to tailor $\widehat{\textbf{C}}$ 
-in order to minimize signal loss. We choose four independent regularization methods to highlight in this section, which have 
-been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
-spectra for the different cases in Figure \ref{fig:toy_sigloss8}.
-% and \ref{fig:toy_sigloss14}. 
-These examples are not meant to be taken as suggested analysis methods but rather as illustrative cases.
-
-As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
-avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
-_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
-\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
-left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
-%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each minimize signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\widehat{\textbf{C}}$ (lower right).
-The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
-	\label{fig:toy_sigloss8}
-\end{figure*}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
-%	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
-%weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
-%matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
-%\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-%computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
-%	\label{fig:toy_sigloss14}
-%\end{figure}
-%
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}}_{\rm reg} \equiv 
-\widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
-of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the estimated covariance matrix more heavily than those off-diagonal.
-Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data and there is no loss.
-%Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss by only using the first three eigenmodes of the estimated covariance.
-Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this
-method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights).
-Again, avoiding the overfitting of EoR-dominated modes which are coupled to the data results in negligible signal loss.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are foreground or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
-We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
-
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}}_{\rm reg} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
-In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
-To understand this, we recall that our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by
-the identity matrix, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
-suppressing the foreground.
-But because we decoupled the whole eigenspectrum from the data, we also avoid signal loss.
-Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
-are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more effectively than others based on the spectral nature 
-of the components in a dataset. 
-%One may imagine a situation where a particular systematic is contained to an isolated 
-%frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
-%\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
-
-In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are coupled to data and not converged to their true forms.
-We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
-
-% SECTION 3 CASE STUDY ---------------------------------------------------------------------------------
-
-\section{Signal Loss in PAPER-64}
-\label{sec:CaseStudy}
-
-We now turn to a detailed signal loss investigation using a subset of the PAPER-64 dataset from \citetalias{ali_et_al2015}.
-In the previous section we showed how signal loss arises when weighting data with empirically estimated covariances; in this section we highlight how the amount of this loss was underestimated in the previous analysis.
-Additionally, we illustrate how we have revised our analysis pipeline in light of our growing understandings.
-
-As a brief review, PAPER is a dedicated 21\,cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
-configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
-\ref{fig:ant_layout}).
-All data is compressed, calibrated (using self-calibration and redundant calibration), delay-filtered (to remove foregrounds inside the wedge), LST-binned, and fringe-rate filtered.
-For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
-refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015}.
-We note that all data processing steps are identical to those in \citetalias{ali_et_al2015} until after the LST-binning step in Figure 3 of \citetalias{ali_et_al2015}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
-	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
-paper (i.e., a subset of the shortest horizontal spacings).}
-	\label{fig:ant_layout}
-\end{figure}
-
-The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} placed a $2\sigma$ upper limit 
-on $\Delta^{2}(k)$, defined as
-
-\begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{P}(k),
-\end{equation}
-
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$. The need to revise this limit stems mostly from previously underestimated signal loss, which we 
-address in this section.
-
-For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
-range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
-We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}, in order to illustrate our revised methods.
-All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
-In the case study in this paper, we only use one baseline type instead of the three as in
-\citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues that will be made clear later on).
-
-The most significant changes from \citetalias{ali_et_al2015} occur in our revised power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
-In \citetalias{ali_et_al2015}, the
-applied filter was not equivalent to the optimal fringe-rate filter (which is designed to maximize power spectrum sensitivity).
-Instead, the optimal filter was degraded slightly by widening it in fringe-rate space.
-This was chosen in order to increase the number of independent
-modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still underestimated. With the development of a new, 
-robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
-computed for a fiducial 30\,m baseline at 150\,MHz, the center frequency in our band. The filter in both the fringe-rate 
-domain and time domain is shown in Figure \ref{fig:frp}.
-
-Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
-As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
-Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/frp.pdf}
-	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
-Stokes I polarization beam. Bottom: the time domain convolution kernel corresponding to the top panel. Real and imaginary 
-components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black. The fringe-rate filter acts as 
-an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
-	\label{fig:frp}
-\end{figure}
-
-We present our PAPER-64 signal loss investigation in three parts.
-We first give an overview of our signal injection framework which is used to estimate loss.
-In this framework (and as in \citetalias{ali_et_al2015}), we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
-As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
-Next, we describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
-Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}.
-
-% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
-
-\subsection{Signal Loss Methodology} 
-\label{sec:siglossmethod}
-In short, our method for estimating signal loss consists of adding an EoR-like signal into visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
-To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
-Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals)
-are filtered in time using an optimal fringe-rate filter to retain only ``sky-like" modes.
-Since the optimal filter has a shape that matches the rate of the sidereal motion of the sky, this transforms the Gaussian noise into a measurement that PAPER could make.
-This signal is then added to the visibility data.\footnote{One
-specific change from \citetalias{ali_et_al2015} is that we add this simulated signal - which has been fringe-rate filtered once already in order to transform it into a ``sky-like" signal - into the analysis pipeline before a fringe-rate filter is
-applied to the data (i.e., prior to the analysis step of fringe-rate filtering). Previously, the addition was done after the fringe-rate filter analysis step.  This change results in an increased 
-estimate of signal loss, %(by a factor of $\sim$$10$), 
-likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was underestimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
-
-Mathematically, suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level).
-We do not know the true EoR signal contained within our visibility data, $\textbf{x}$, so $\textbf{e}$ takes on the role of the true EoR signal (for which we measure its loss).
-Furthermore, one can make the assumption that the true EoR signal is small within our measured data, so the data vector $\textbf{x}$ itself is representative of mostly contaminants.
-Using this assumption, the sum of $\textbf{x}$ and $\textbf{e}$, defined as $\textbf{r}$:
-
-\begin{equation}
-\label{eq:rxe}
-\textbf{r} = \textbf{x} + \textbf{e},
-\end{equation}
-can be thought of as the sum of contaminants plus EoR.
-The quantity $\textbf{r}$ then becomes the dataset for which we are measuring how much loss of $\textbf{e}$ there is due to our power spectrum pipeline.
-
-We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
-spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as
-
-\begin{equation}
-\label{eq:Pin}
-\widehat{P}_{\rm in}^{\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
-\end{equation}
-
-\noindent and
-
-\begin{eqnarray}
-\label{eq:sigloss}
-\widehat{P}_{\rm out}^{\alpha} &\equiv& \widehat{\textbf{P}}_{r}^{\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
-&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
-\end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-
-The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
-It can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
-The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-The input power spectrum is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-
-%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e., the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
-In other words, we make the anzatz that
-
-%\begin{equation}
-%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
-%\end{equation}
-%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
-%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}
-
-Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:
-
-%
-%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
-%
-%In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
-%\begin{equation}
-%\x \equiv \f + \s,
-%\end{equation}
-%where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
-In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$.
-This can be parametrized as
-%\begin{equation}
-%\label{eq:LinearPspecSum}
-%\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
-%\end{equation}
-%where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
-%power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
-%\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
-%\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-%which assumes that the covariance used in the QE analysis is close to the true covariance with effects due to 
-%small sample size limited to first order perturbations and thus neglects cross-correlation between $x$ and $e$.  
-%In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
-%terms to be remain significant.   
-%
-%Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
-Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
-%\begin{equation}
-%\label{eq:Deriv1}
-%\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
-%\end{equation}
-%However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
-Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
-%\begin{equation}
-%\label{eq:Deriv2}
-%\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
-%\end{equation}
-%which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
-Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
-Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$.
-In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.
-%
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
-\dcj{Here is the post-hoc justification for this signal loss method.
-Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum.
-So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}.
-Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example.
-The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
-Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
-%\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
-%\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
-%covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
-%correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
-%I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-%then explaining in the next section exactly how cross-terms were what messed us up in the first go round.} 
-%\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
-It's not.
-It's meant as a motivational example.
-I just wanted something where I could follow through analytically to the end to show that it's ok to think about signal loss as a multiplicative factor.
-At least in expectation.
-And then how one deals with not correcting for the signal loss in expectation is described in Section \ref{sec:Practice}.}
-%
-%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
-%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
-%distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
-%distribution could this (signal-loss affected) data come from?" 
-%
-%In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
-Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
-%signal loss lens.
-We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
-One alternative to the method described in Section \ref{sec:Practice} is described in Appendix \ref{sec:Pr_appendix}.
-%%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
-
-%\subsubsection{Signal Loss Illustration}
-%\label{sec:Illustration}
-%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
-
-\begin{eqnarray}
-\label{eq:crossterm_full}
-\widehat{P}_{\rm out}^{\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
-%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
-%\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:
-
-\begin{eqnarray}
-\label{eq:crossterm}
-\widehat{P}_{\rm out}^{\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}. %\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-One of the key takeaways of this section is that the \citetalias{ali_et_al2015} analysis estimated signal loss by comparing \textit{only} the signal-only term (second term in Equation \eqref{eq:crossterm}) with $\widehat{P}_{\rm in}$, whereas in fact the cross-term (third term in Equation \eqref{eq:crossterm}) can substantially lower $\widehat{P}_{\rm out}$.
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$).
-We will now go into further detail and examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
-
-{\bf Small injection:}
-%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
-They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
-%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
-In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
-Output values are Gaussian distributed around zero, spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
-%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$.
-It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black).
-We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-
-{\bf Large injection:}
-When the injected signal is much larger than the measured power spectrum, the data-only components can 
-be neglected as they are many orders of magnitude smaller.
-We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e., in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
-However, it is useful as a check of our system in a relatively simple case.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green).
-Here only does the signal-only term used in \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
-This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-
-{\bf In between:}
-When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
-the weighted injected power spectrum component mirrors the input power indicating little loss (i.e., the green curve follows the dotted black line), eventually 
-departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-in this regime the cross-term (red) has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
-This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
-Again, we emphasize that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for underestimating power spectrum limits in \citetalias{ali_et_al2015}.
-
-%A brief description of Figure \ref{fig:sigloss_terms} is as follows.
-The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed.
-The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$).
-It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$.
-The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$.
-This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
-It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
-We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss.
-In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
-
-%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
-%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
-For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
-%
-%\begin{eqnarray}
-%\label{eq:pout_expand}
-%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
-% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
-%\end{eqnarray}
-%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
-However, without taking into account the cross-terms (the second term), we can substantially underestimate loss.
-In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
-Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
-	\caption{Illustration of the power spectrum amplitude of five different power spectrum terms, each a function of visibility data ($\textbf{x}$), simulated injected EoR signal ($\textbf{e}$), or both ($\textbf{r}$).
-This figure shows how these quantities behave as the power level of the injected EoR signal increases (along the x-axis).
-The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.
-We emphasize that the output power spectrum in black ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-Roughly speaking, it can be compared to the input signal level ($P_{\rm in}$) to estimate the amount of signal loss.
-Left: Empirical inverse covariance weighting is used in power spectrum estimation, as done in \citetalias{ali_et_al2015}.
-The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss).
-The gray horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power).
-The green signal-signal component is the term used in \citetalias{ali_et_al2015} to estimate signal loss.
-It is significantly higher than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue).
-In the regime where cross-correlations between signal and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative estimates due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
-This causes the difference between the green curve (which exhibits negligible loss at the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss).
-Right: The same power spectrum terms illustrated for the uniform weighted case.}
-\label{fig:sigloss_terms}
-\end{figure*}
-
-The source of the strong negative cross-term is not immediately obvious, however it is an explainable effect. 
-When $\textbf{R}_{r}$
-is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the third term of Equation \eqref{eq:crossterm} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
-$\widehat{\textbf{C}}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
-This negative cross-term power arises from a coupling between the inverse of 
-$\widehat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
-Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$:
-
-\begin{eqnarray}
-\widehat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
-&=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
-\textbf{ee}^{\dagger} \rangle_{t},
-\end{eqnarray}
-
-\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e., the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
-Without loss of generality, we will assume
-an eigenbasis of $\textbf{e}$, so that $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
-two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
-ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}%\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}
-, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
-off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ but
-contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
-correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
-of a diagonal-dominant matrix.
-% XXX [ARP: we may want to write this all out explicitly in an appendix]
-
-%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
-Therefore, in our revised
-%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
-%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
-
-%\dcj{This paragraph has me confused.}
-%The conclusion is that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
-In principle, using $\widehat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
-Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
-However, despite the loosening of these approximations, one sees that the qualitative message (of anti-correlations resulting in signal loss) remains intact.
-
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
-Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
-However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
-The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
-
-\subsection{Signal Loss in Practice}
-\label{sec:Practice}
-
-We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
-outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
-($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. %With this weighting, our 
-%expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
-
-%\begin{eqnarray}
-%\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-%\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}%\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
-%\end{eqnarray}
-
-%The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
-In practice, however, the signal loss itself is a random variable --- some realizations of the cosmological signal may be more correlated with foreground modes than others, leading to more signal loss.
-This leads to two issues.
-The first is that Equation \eqref{eq:LinearPspecSum} may not hold.
-In particular, a third term that is a quadratic combination of $\f$ and $\s$ (e.g., $\f^\dagger \C^{-1} \s$) may appear.
-However, we can circumvent this issue by decomposing $\f$ into a sum of two vectors, one that is proportional to $\s$ and one that is orthogonal to $\s$.
-The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-In other words, suppose that we have
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
-%\end{equation}
-%in place of Equation \eqref{eq:LinearPspecSum}.
-Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
-Further parameterize $\mathbf{ f}_\parallel \equiv \rho \mathbf{e}$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-This then gives
-%\begin{equation}
-%\label{eq:fperpfpara}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
-%\end{equation}
-%Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
-%\dcj{Wait what?
-I think you are saying essentially that some x can remain in Pout which is what we are seeing.
-Or is this some extra bit of method which has been added to the analysis...} \acl{I'm not sure that's what I'm saying.
-(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure").
-What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
-%\end{equation}
-%(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
-%$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
-%couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
-%some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
-%Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
-%EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
-%the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
-%dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-%$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-%\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
-%\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
-Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
-What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
-So essentially we are defining an effective $
-%\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
-
-One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e., how much coupling there is, which affects how much loss results).
-
-For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator.
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} |
-\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
-In other words,
-
-\begin{equation}
-\label{eq:Bayes}
-p(P_{\rm in} | \widehat{P}_{\rm out}) \propto {\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
-\end{equation}
-
-\noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus signal injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
-by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum over $\widehat{P}_{\rm out}$ is unity, and the 
-whole process is then repeated for a different value of $P_{\rm in}$.
-
-%\subsubsection{Signal Loss Implementation Details}
-%\label{sec:Implementation}
-
-The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss.
-To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
-We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
-$\widehat{P}_{\rm out}$ grid.
-
-Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level) and, since they are well-approximated by a Gaussian distribution in our numerical results, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
-Stitching all of them together results in a 2-dimensional transfer function --- the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
-We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
-%For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
-
-Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
-Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior.
-Although we only show figures for one $k$-value, we note that
-the shape of the transfer curve is similar for all $k$'s.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ represents a (lossy) power spectrum.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
-We normalize this final distribution and compute the $95\%$ confidence interval (an upper limit on EoR).
-
-%We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
-We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
-Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
-
-By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
-\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
-
-%As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
-Ideally, running many simulations would lead to convergence; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
-\dcj{This dependence on injection count was checked with a run having 10x the usual number of integrations.} To separate the intrinsic stochasticity of signal loss from that which arises due to simulation sample variance, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-Here the scatter, evident as deviations from unity-transfer, is entirely due to finite sample variance.
-To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $\widehat{P}_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
-By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
-%look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
-As an extreme example, if we are very unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
-An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
-On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $\widehat{P}_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
-
-%The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
-%nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $\widehat{P}_{\rm out}$ value for every 
-%$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
-%scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
-%\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-%every bootstrap (for reasons made clear in the next paragraph), there is a range of $\widehat{P}_{\rm out}$ values that results from the same 
-%$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
-%the spread in the weighted case (left plot).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
-Since our $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
-This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored
-heat-maps on top of the points. Two cases are displayed: empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does
-not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
-	\label{fig:sigloss_transfercurve}
-\end{figure*}
-
-%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($\widehat{P}_{\rm out} > P_{in}$).
-\cc{This is a log-plotting effect and is under-construction!}.
-%This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. 
-%
-%The shape of our signal loss transfer function can be described as follows.
-At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}.
-As $\textbf{e}$ increases, we move
-%into a regime where $\widehat{P}_{\rm out} \sim P_{in}$, and then eventually into a regime where $\widehat{P}_{\rm out} < P_{in}$ when $\textbf{e}$ is 
-%large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
-%the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
-%	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on %PAPER-64 data after signal loss correction.
-Power spectrum points are computed from the peak of the distributions.
-Errors are computed using $95\%$ confidence intervals.}
-%	\label{fig:sigloss_datadist_inversecovariance}
-%\end{figure*}
-
-The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red).
-%There are a few important checks to examine.
-First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
-This is an important check, as we expect no signal loss for this case.
-Any difference here would indicate an error in the pipeline or discrepancy in the range of data included.
-Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars from bootstrapping, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
-We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of empirical inverse covariance weighting.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
-Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:Error}.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-In this example, we see that the lossy power spectrum limit is $\sim 4$ orders of magnitude too low when using empirical inverse covariance weighting.}
-\label{fig:ps2_data}
-\end{figure*}
-
-\subsection{Minimizing Signal Loss}
-\label{sec:Weight}
-
-With a signal loss formalism established, we now have the capability of experimenting 
-with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
-foregrounds and systematics in our data without generating large amounts of signal loss as we have seen with the inverse covariance estimator. We have found that the balance 
-between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
-
-We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e., flattening out part of the 
-eigenspectrum and effectively decoupling the lowest-valued eigenmodes, which are typically EoR-dominated, from the data) can help minimize signal loss.
-We experiment with this idea on PAPER-64 data, dialing the number of modes
-that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
-covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
-estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
-subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
-increases with the number of down-weighted modes (solid red).
-The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
-\citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
-
-Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to uniform weighting (blue).
-In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
-only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting).
-For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
-
-We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss.
-We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as a percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
-We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
-From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
-We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear ``minimum" that produces the least loss.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
-are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e., unweighted) to $21$ modes on the right (i.e., the full inverse 
-covariance estimator).
-$\sim4$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
-Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e., very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
-Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
-weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.09 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.09$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
-	\label{fig:sigloss_modeloop}
-\end{figure*}
-
-In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
-in both panels and represents a third regularization technique.
-This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity
-matrix element-wise to $\widehat{\textbf{C}}$).
-This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
-We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
-
-It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
-Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations.
-Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
-(\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.
-
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) using the analysis presented in this paper is shown in Figure
-\ref{fig:ps1_data}.
-Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework.
-The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
-$2\sigma$ errors bars from bootstrapping).
-It is also shown as an upper limit using the signal injection framework (solid blue), which is interestingly larger than the errors computed from bootstrapping, likely because the full injection framework takes into account additional sample variance whereas the bootstrapped errors do not.
-Finally, the gray shaded regions combine the measured uniform weighted power spectrum values with thermal noise errors.
-We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case, thus further motivating uniform-weighting for Kolopanis et al.
-(\textit{in prep.}).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of $\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
-(\textit{in prep.}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
-loss, bootstrapping, and the theoretical error computation. We see that the regularization scheme used here produces limits similar to the unweighted limits.}
-	\label{fig:ps1_data}
-\end{figure*}
-
-In this section we have shown three simple ways of regularizing $\widehat{\textbf{C}}$ to minimize signal loss using PAPER-64 
-data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
-$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this might mean calculating $
-\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$\,m diagonal PAPER baselines (instead of the 
-horizontal E/W ones). Alternatively, covariances could be estimated from all baselines except the two being cross-multiplied 
-when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
-21\,cm signal, and it is worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
-because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{in prep.})).
-
-Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
-down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.
-Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from
-data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
-
-In Section \ref{sec:CaseStudy}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
-We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
-In the remainder of this paper, we will transition to other aspects of our analysis that have been revised since \citetalias{ali_et_al2015}.
-
-% SECTION 4 OTHER ERRORS ---------------------------------------------------------------------------------
-
-\section{Additional PAPER-64 Revisions}
-\label{sec:OtherErrors}
-
-Underestimated signal loss is the main reason for the revision of the power spectrum limits from \citetalias{ali_et_al2015}.
-It is interesting to note that --- had all the other aspects of the original analysis been correct --- the underestimated limits may have been more easily caught.
-Unfortunately, two related power spectrum components, namely the error bars on the power spectrum data points and the theoretical noise prediction, were also calculated incorrectly.
-
-In this section, we summarize multiple inconsistencies and errors that have been found since the previous analysis in terms of error estimation.
-We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
-We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified through simulations.
-
-\subsection{Bootstrapping}
-\label{sec:Boot}
-
-Broadly speaking, we desire robust methods for determining accurate 
-confidence intervals for our measurements. For PAPER's analysis, we choose a data-driven method of error estimation, computing error bars that have been derived from the inherent 
-variance of our measurements. A common technique used to do this is bootstrapping, which we first define below and then discuss its application to PAPER.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, bootstrap measurements (of power spectra, for example) can be made from different random samples of data.
-Each of these bootstraps is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-%Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements).
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
-Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap).
-Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
-The error (on the mean) is then computed as the standard deviation across all bootstraps.
-
-%We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
-$N_{\rm boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
-Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
-However, we will see that $N$ depends on sample independence, and it is this dependence that led to the underestimation of errors in \citetalias{ali_et_al2015}.
-
-%Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
-This could represent $1000$ power spectrum measurements, for which we are interested in its error.
-We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-%We next form $500$ bootstraps ($N_{\rm boot} = 500$).
-To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
-The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
-This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
-values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
-and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
-itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, underestimates 
-errors.
-
-%As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of independent data samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$).
-This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both underestimate the error by drawing too many or overestimate it by drawing too few.
-However, since we know that we have $100$ independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-%	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-%sampling with replacement.
-The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
-The estimated errors match up with the theoretical prediction only at $N=100$.}
-%	\label{fig:toy_error1}
-%\end{figure}
-
-This is the precisely how errors were underestimated in PAPER-64.
-Because of fringe-rate filtering, which averages data in time to increase sensitivity, PAPER-64 data is correlated along the time axis.
-Hence, there are fewer independent samples after filtering, thus decreasing the variance of the bootstraps.
-
-More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time.
-In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis, and a total of $400$ bootstraps were created in this step, each comprised of randomly selected values sampled with replacement (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Means were then taken of the values in each bootstrap. Finally, power 
-spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap greatly 
-exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds of these random 
-samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
-\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-
-In addition to learning how sample independence affects bootstrapped errors, we have made three additional changes to our bootstrapping procedure since \citetalias{ali_et_al2015}, summarized here:
-
-\begin{itemize}
-
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
-
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into five independent groups, where no baselines were repeated in each group.
-Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
-This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
-Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
-
-\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
-
-\end{itemize}
-
-In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
-Bootstrapping can be an effective and straightforward way to estimate errors of a dataset, however, bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
-We have thus avoided this issue by removing one of our bootstrap axes, as well as updated several other details of our procedure to ensure accurate re-sampling and error estimation.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
-This underestimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
-We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
-	\label{fig:data_errors}
-\end{figure}
-
-\subsection{Theoretical Error Estimation}
-\label{sec:Error}
-
-One useful way of cross-checking measured power spectrum values and errors is to compute a theoretical estimation of thermal noise based on observational parameters.
-Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-Upon re-analysis of PAPER-64, we have discovered that this estimate was also underestimated in previous analyses.
-
-To compute our theoretical noise estimate, we use an analytic sensitivity calculation.
-Through detailed studies using several independently generated noise simulations, what we found was that our simulations all agreed but were discrepant with the previous calculations.
-The analytic
-calculation is only an approximation and attempts to combine a large number of pieces of information in an approximate way; however, when re-considering some of the approximations, the differences were large enough (factors of $10$ in some cases) to warrant a
-careful investigation. What follows here is an 
-accounting of the differences which have been discovered.
-We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots in this paper, is computed with these changes accounted for.
-
-The noise prediction $n(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
-interferometric 21\,cm data, in temperature-units, is:
-
-\begin{equation}
-\label{eq:sense}
-N(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
-\end{equation}
-We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in \citetalias{ali_et_al2015}.
-
-\begin{itemize}
-\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
-distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} \, h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
-\item $\Omega_{\rm eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
-The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted.
-Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{\rm eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
-filter and the PAPER primary beam. 
-\item $T_{\rm sys}$: The system temperature is set by:
-
-\begin{equation}
-\label{eq:sys}
-T_{\rm sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{\rm rcvr},
-\end{equation}
-
-where $\nu$ are frequencies in GHz (\citealt{thompson_et_al2001}). We use a receiver temperature of $144$\,K, yielding $T_{\rm sys} = 431$\,K at $150$\,MHz. 
-This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
-identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying two independent visibility measurements. In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
-\item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
-because we integrate incoherently over time. For PAPER-64, $N_{\rm lst} = 8$.
-\item $N_{\rm seps}$: The number of baseline separation types (where baselines of a unique separation type have the same orientation and length) averaged incoherently in a final power spectrum estimate.
-For the
-analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines).
-However, both the updated limits in Kolopanis et al.
-(\textit{in prep.}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
-\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e., a 
-fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
-using the following:
-\begin{equation}
-t_{\rm int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
-\end{equation}
-where $t_{i}=43$ seconds, $t_{\rm int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
-taken over all fringe-rates. For PAPER-64, this number is $t_{\rm int} = 3857$\,s. 
-\item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even" in order to avoid noise biases).
-Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
-$N_{\rm days}$. Our expression therefore becomes:
-\begin{equation}
-N_{\rm days} = \sqrt{\langle N_{i}^{2}\rangle} \sqrt{(N_{\rm datasets}^{2}-N_{\rm datasets})}
- %\frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ indexes LST and frequency channel over all datasets (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim47$ 
-days.
-\item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total} = 51$) neglects 
-the fact that the \citetalias{ali_et_al2015} analysis averages baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
-\begin{equation}
-N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{\frac{N_{\rm gps}^{2}-N_{\rm gps}}{2}},
-\end{equation}
-\noindent where, in the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big).
-A revised \citetalias{ali_et_al2015} analysis should therefore use $N_{\rm bls} \sim 32$ instead of $51$, and this change is taken into account in Figure \ref{fig:sense_check}.
-However, the analysis in this paper and in Kolopanis et al.
-(\textit{in prep.}) no longer averages baselines into groups ($N_{\rm gps} = 1$).
-For the subset of data presented in this paper, $N_{\rm bls} = 10$.
-\item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
-\end{itemize}
-
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s to form $\Delta^{2}(k)$.
-
-Our revised sensitivity estimate for the \citetalias{ali_et_al2015} analysis of PAPER-64 is shown in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/sense_check.pdf}
-	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
-\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:Error}, which when combined decreases our 
-sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
-	\label{fig:sense_check}
-\end{figure}
-
-To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
-random noise assuming a constant $T_{\rm rcvr}$ (translated into $T_{\rm sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{\rm days}$ as determined 
-by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{\rm sys}$ into a root-mean-square variance statistic 
-using:
-
-\begin{equation}
-\label{eq:noise}
-T_{\rm rms} = \frac{T_{\rm sys}}{\sqrt{\Delta\nu \Delta t N_{\rm days} N_{\rm pols}}},
-\end{equation}
-
-\noindent where $\Delta\nu$ is the channel spacing, $\Delta t$ is the integration time, $N_{\rm days}$ is the number of daily counts for a 
-particular time and frequency that went into our LST-binned set, and $N_{\rm pols}$ is the number of polarizations ($2$ for Stokes 
-I). This temperature sets the variance of the Gaussian random noise.
-
-Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}.
-We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance.
-However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
-While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
-Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations.
-Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{The power spectrum for a noise simulation that mimics the noise level of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework (red and blue) are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
-	\label{fig:ps_noise}
-\end{figure*}
-
-% CONCLUSION ---------------------------------------------------------------------------------
-
-\section{Conclusion}
-\label{sec:Con}
-
-Although current 21\,cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
-ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like 
-HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
-that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline and be able to accurately 
-and robustly calculate both power spectrum and theoretical errors.
-
-In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
-signal loss and error estimation, which can be summarized as follows:
-
-\begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances due to couplings with the data realizations (Section 
-\ref{sec:SiglossOverview}). Loss of the 21\,cm signal is especially significant the fewer number of independent modes that
-exist in the data. Hence, there exists a trade-off between sensitivity driven 
-time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:siglossmethod}). However, a 
-signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for correlations between the data and signal which can be large and negative.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:Boot}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
-simple and accurate way of estimating errors.
-\end{itemize}
-
-As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, and accurately estimating thermal noise.
-Our revised PAPER-64 limits are presented in Kolopanis et al.
-(\textit{in prep.}), which supersede all previously published PAPER limits.
-Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
-(\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
-However, the main reasons for a previously underestimated limit (\citealt{ali_et_al2018}) and
-ways in which our new analysis differs can still be summarized by the following:
-
-\begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was underestimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
-covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
-\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-Underestimated signal loss therefore represents the bulk of our revision.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
-Several other errors were also found regarding error estimation, though with smaller effects.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:Error}). We note that our sensitivity prediction is revised by a factor less than our overall
-power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
-points.
-\end{itemize}
-
-The future of 21\,cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
-foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
-instruments.
-On the power spectrum analysis side, robust signal loss simulations and precise error calculations will play critical roles in accurate 21\,cm results.
-With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
-
-% ACKNOWLEDGEMENTS ---------------------------------------------------------------------------------
-
-\section{Acknowledgements}
-CC would like to acknowledge the UC Berkeley Chancellor's Fellowship and National Science Foundation Graduate Research 
-Fellowship (Division of Graduate Education award 1106400). She would also like to thank Phil Bull, Bryna Hazelton, Miguel Morales, and Eric Switzer for helpful discussions. PAPER and HERA 
-are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
-also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
-SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
-JSD acknowledges NSF AAPF
-award 1701536.
-GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184.
-This work is based on research supported in part by the National Research Foundation of South Africa (award 103424).
-We graciously thank SKA-SA for site infrastructure and observing support.
-\label{sec:Ack}
-
-% APPENDIX ---------------------------------------------------------------------------------
-
-%\color{blue}
-
-\begin{comment}
-
-\appendix
-\section{A toy model for inverse covariance weighting}
-\label{sec:icw_appendix}
-
-%AAAXXX
-
-In this Appendix, we focus on the optimal quadratic estimator, Equation \eqref{eq:OQE}, and mathematically illustrate its role in estimating the power spectrum of EoR.
+We will mathematically illustrate its role in estimating the power spectrum of EoR.
 While there exists detailed literature about quadratic estimators in general (e.g., \citealt{liu_tegmark2011}; \citealt{trott_et_al2012}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}), here we focus on two simple cases in order to outline one situation where the estimator successfully suppresses contamination and one where it does not.
@@
 
-\color{black}
-
-%\appendix
-\section{A toy model for signal loss}
-\label{sec:sigloss_appendix}
-
-In this Appendix, we examine a toy model for signal loss.
-Our goal is to derive an analytic formula for power spectrum signal loss.
-While this model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
-
-The minimum-variance quadratic estimator $\widehat{P}^\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\begin{equation}
-\widehat{P}^\alpha = \frac{1} {2 \F^{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
-\end{equation}
-where
-\begin{equation}
-F^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \right)
-\end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix.
-For this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real.
-We also assume for simplicity that $\mathbf{x}$ is the data from a single instant in time, so that it is of length $N_f$, where $N_f$ is the number of frequency channels.
-
-In our case, we do not have \emph{a priori} knowledge of the covariance matrix.
-Thus, we deviate from the true minimum-variance quadratic estimator and replace $\C$ with $\Chat$, its data-derived approximation.
-Our estimator then becomes
-\begin{equation}
-\label{eq:phatloss}
-\widehat{P}^\alpha_\textrm{loss} = \frac{1} {2 \widehat{\F}^{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
-\end{equation}
-where
-\begin{equation}
-\widehat{F}^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
-\end{equation}
-with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than unity).
-We will now provide an explicit demonstration of this by modeling the estimated covariance as
-\begin{equation}
-\label{eq:ChatDef}
-\Chat = (1-\eta) \C + \eta \x \x^t,
-\end{equation}
-where $\eta$ is a parameter quantifying our success at estimating the true covariance matrix.
-If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
-On the other hand, if $\eta =1$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
-
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{P}^\alpha_\textrm{loss}$ in terms of $\widehat{P}^\alpha$.
-We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
-\begin{equation}
-\Chat^{-1} = \frac{\C^{-1}}{1-\eta} \left[ \I - \frac{\eta \x \x^t \C^{-1}}{1+ \eta (g-1)}\right],
-\end{equation}
-where we have defined $g \equiv \x^t \C^{-1} \x$. Inserting this into our Fisher estimate we have
-\begin{equation}
-\widehat{F}^{\alpha \alpha} = \frac{F^{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^{\alpha})^2}{F^{\alpha \alpha}}\right],
-\end{equation}
-where $h^\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h^{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
-Note that $g$, $h^\alpha$, and $h^{\alpha \alpha}$ are all random variables, since they depend on $\x$.
-Inserting these expressions into our estimator gives
-\begin{equation}
-\label{eq:phatlossexpanded}
-\widehat{P}^\alpha_\textrm{loss} = \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^\alpha)^2}{F^{\alpha \alpha}}\right]^{-1}.
-\end{equation}
-Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading 
-order in $\eta$. This approximates the limiting case where the covariance $\Chat$ is close to the ideal and the 
-lossy covariance is a small perturbation.  The result is
-\begin{equation}
-\widehat{P}^\alpha_\textrm{loss} \approx \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}}\right)\right].
-\end{equation}
-Taking the ensemble average of both sides and noting that the true power spectrum $P^\alpha$ is equal to $\langle h^\alpha \rangle / 2 F^{\alpha \alpha}$, we obtain
-\begin{equation}
-\langle \widehat{P}^\alpha_\textrm{loss} \rangle \approx (1- \eta N_f) P^\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) P^\alpha,
-\end{equation}
-where recall that $N_f$ is the length of $\x$, or the number of frequency channels.
-In the last step we dropped the final term, since it scales as $\eta P^\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
-
-Recalling that $P^\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
-This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.
-This violates the assumptions implicit in the derivation of $F^{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{liu_tegmark2011}.
-The result is an improperly normalized---and thus lossy---power spectrum estimate.
-
-\section{Derivation of the Jeffreys Prior}
-\label{sec:jeffreys}
-
-The Jeffreys prior is an objective, non-informative prior distribution for a parameter space using Bayesian probability (\citealt{jaynes1968}).
-For the signal injection framework outlined in Section \ref{sec:Practice}, we wish to compute the prior $p(P_{\rm in})$, or the probability density of the power spectrum of the EoR signal.
-
-The Jeffreys prior is defined as:
-
-\begin{equation}
-\label{eq:jeffreys}
-p(P_{\rm in}) \propto \sqrt {\Bigg\langle \Bigg(\frac{\partial \mathcal{L}}{\partial P_{\rm in}} \Bigg)^{2}\Bigg\rangle},
-\end{equation}
-
-\noindent where
-
-\begin{equation}
-\label{eq:logprob}
-\mathcal{L} = \mathrm{ln} \, p(\widehat{P}_{\rm out} | P_{\rm in}),
-\end{equation}
-
-\noindent recalling that in our framework $P_{\rm in}$ is the power spectrum of the EoR signal (uniformly weighted), and $\widehat{P}_{\rm out}$ is the weighted output power spectrum of the data plus EoR.
-
-For a single injection amplitude, our bootstrapped $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution.
-Simplifying our notation so that $x = P_{\rm in}$ and $y = \widehat{P}_{\rm out}$:
-
-\begin{equation}
-\label{eq:prob}
-p(y | x) = \frac{1}{\sigma(x) \sqrt{2\pi}} e^{-\frac{1}{2}\big(\frac{y-\bar y(x)}{\sigma}\big)^{2}},
-\end{equation}
-
-\noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Combining Equations \eqref{eq:jeffreys}, \eqref{eq:logprob}, and \eqref{eq:prob} the Jeffreys prior simplifies to become:
-
-%\begin{eqnarray}
-%\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
-%&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
-%\end{eqnarray}
-
-%Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
-Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
-Finally, after some additional simplification the Jeffreys prior becomes:
-
-\begin{equation}
-\label{eq:jeffreys_final}
-p(x) \propto \sqrt{ \frac{1}{\sigma^{2}}\Big(2\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} + \Big(\frac{\partial \bar y}{\partial x}\Big)^{2}\Big) }.
-\end{equation}
-
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
-For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-%An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
-%	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
-Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
-The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
-%	\label{fig:jeffreys1}
-%\end{figure}
-
-We show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
-Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.
-Therefore, due to its objective nature we choose to use a Jeffreys prior in our analysis, multiplying our likelihood functions by Equation \eqref{eq:jeffreys_final} before computing posterior distributions.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=10cm]{plots/jeffrey_prior.pdf}
-	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final} (black).
-We smooth the prior using a sliding boxcar average over every $5$ injection levels (red).
-Most noticeably, the Jeffreys prior is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
-	\label{fig:jeffreys2}
-\end{figure}
-
-\end{comment}
-
 \bibliographystyle{apj}

### 2018-10-09 Memo2_signallossmath.tex
adding memos corresponding to 3 appendices

--- 2018-10-08 PAPER.tex
@@
 
-% Math shortcuts from Danny
-\newcommand{\Prob}{\mathbf{P}}
+\begin{document}
 
-\begin{document}
-\title{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64}
+\title{A Toy Model for Signal Loss} 
+\author{Adrian Liu, Carina Cheng, and the PAPER Collaboration}
+\maketitle
+\vspace{1cm}
 
-\author{
-Carina Cheng\altaffilmark{1}$^{,\diamond}$,
-Aaron R. Parsons\altaffilmark{1,2},
-Matthew Kolopanis \altaffilmark{3},
-Daniel C. Jacobs\altaffilmark{3}, 
-Adrian Liu\altaffilmark{1,4}$^{,\dagger}$, 
-Saul A. Kohn\altaffilmark{5},
-James E.~Aguirre\altaffilmark{5},
-Jonathan C. Pober\altaffilmark{6}, 
-Zaki S. Ali\altaffilmark{1}, 
-Gianni Bernardi\altaffilmark{7,8,9}, 
-Richard F. Bradley\altaffilmark{10,11,12},
-Chris L. Carilli\altaffilmark{13,14},
-David R. DeBoer\altaffilmark{2}, 
-Matthew R. Dexter\altaffilmark{2},
-Joshua S. Dillon\altaffilmark{1}$^{,*}$,
-Pat Klima\altaffilmark{11},
-David H. E. MacMahon\altaffilmark{2},
-David F. Moore\altaffilmark{5},
-Chuneeta D. Nunhokee\altaffilmark{8},
-William P. Walbrugh\altaffilmark{7},
-Andre Walker\altaffilmark{7}
-}
-
-\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
-\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
-\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
-\altaffiltext{4}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
-\altaffiltext{5}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
-\altaffiltext{6}{Dept. of Physics, Brown University, Providence RI}
-\altaffiltext{7}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{8}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{9}{INAF-Instituto di Radioastronomia, Bologna Italy}
-\altaffiltext{10}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
-\altaffiltext{11}{National Radio Astronomy Obs., Charlottesville VA}
-\altaffiltext{12}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
-\altaffiltext{13}{National Radio Astronomy Obs., Socorro NM}
-\altaffiltext{14}{Cavendish Lab., Cambridge UK}
-
-%		Notes
-
-%Reference section with: \ref{sec:Intro}
-%Reference equation with: \eqref{eq:eqtest}
-%Reference figure with: \ref{fig:figtest}
-%Cite paper inside sentence: \citet{ref}
-%Cite paper at end of sentence: \citep{ref}
-%Cite paper inside a parenthetical sentence: \citealt{ref}
-
-%To compile with references shown, compile in BibTeX once and LaTeX twice
-
-%		Sample Equation Syntax
-%\begin{equation}
-%\label{eqtest}
-%\langle \widetilde{T} (\mathbf{k}) \widetilde{T}^* (\mathbf{k^\prime}) \rangle = (2 \pi)^3 \delta^D (\mathbf{k} - \mathbf{k}^\prime) P(k),
-%\end{equation}
-
-% ABSTRACT ---------------------------------------------------------------------------------
-
-\begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
-galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the 21\,cm line of neutral hydrogen.
-Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data.
-It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
-Specifically, with a statistical power spectrum detection in HERA's foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
-In this paper, we focus on signal loss associated with power spectrum estimation.
-We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
-Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
-We focus on a subset of PAPER-64 data in this paper; revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
-(\textit{in prep.}) and supersede results from previously published PAPER analyses.
-\end{abstract}
-
-% INTRO ---------------------------------------------------------------------------------
-
-\section{Introduction}
-\label{sec:Intro}
-
-{\let\thefootnote\relax\footnote{$^{\diamond}$\href{mailto:ccheng@berkeley.edu}{ccheng@berkeley.edu}}}
-{\let\thefootnote\relax\footnote{$^{\dagger}$Hubble Fellow}}
-{\let\thefootnote\relax\footnote{$^{*}$NSF AAPF Fellow}}
-\setcounter{footnote}{0}
-
-By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
-neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
-luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
-into a plasma, is known as the Epoch of Reionization (EoR).
-The EoR is a relatively unexplored era in our Universe's history, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
-This epoch encodes important information regarding the nature of the first galaxies and the processes of structure formation.
-Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
-between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
-
-One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
-This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
-of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. Hence, 21\,cm tomography offers a unique window into both the spatial and temporal
-evolution of ionization, temperature, and density fluctuations.
-
-In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
-the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
-mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
-Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
-Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
-(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
-\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
-Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
-the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
-\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
-Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
-detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).
-
-The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results.
-More specifically, it is imperative to develop techniques that ensure
-the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method.
-In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation.
-This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis.
-We first approach this topic from a broad perspective, and then perform a detailed
-case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al.
-(\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
-
-Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
-This paper accompanies the erratum of \citet{ali_et_al2018} and adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
-These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
-
-This paper is organized into three main sections.
-In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
-In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss.
-In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis.
-Finally, we conclude in Section \ref{sec:Con}.
-
-% SECTION 2 SIGLOSS TOY MODEL ---------------------------------------------------------------------------------
-%\color{blue}
-
-\section{Signal Loss Toy Models}
-\label{sec:SiglossOverview}
-% JEA - We never totally nail down what ``signal loss'' is ...
-
-Signal loss refers to attenuation of the target cosmological signal 
-in a power spectrum estimate.
-Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits.
-Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
-
-One type of signal loss can occur when weighting data by itself.
-Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others.
-For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
-Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
-However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
-In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
-This loss was significantly 
-%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.
-
-% JEA - Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
-
-\subsection{The Quadratic Estimator Method}
-\label{sec:QE}
-
-%AAAICW
-
-We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation.
-The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
-Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain.
-If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in
-% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
-%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
-This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in
-\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
-%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-
-% JEA - The discussion of dimensions here is confusing ...
-"a baseline" is mentioned, but it's not clear if the redundant baseline averaging has already happened or what.
-I believe we are only considering covariance between frequencies, but this isn't explicitly said, and the matrix equations don't make sense unless all the dimensions are N_f N_t.
-%We begin with our 
-Suppose that the measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
-% JEA - not sure this helps
-%, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), 
-where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. The covariance of the data is given by 
-\begin{equation}
-\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle = \textbf{S} + \textbf{U}
-\end{equation}
-where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as the sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
-
-We are interested in estimating the three-dimensional power spectrum of the EoR.  
-Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
-We consider band powers $P^\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-The fundamental dependence of the covariance on the power spectrum band powers $P^\alpha$ is encoded as
-% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
-\begin{equation}
-\textbf{S} = \sum_\alpha P^\alpha \frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \sum_\alpha P^\alpha \textbf{Q}^\alpha
-%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
-%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
-\end{equation}
-where we define $\frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \textbf{Q}^{\alpha}$.
-In other words, $\textbf{Q}$ describes the response of the covariance to a change in the power spectrum, relating a quadratic statistic of the data (the covariance) to a quadratic statistic in Fourier-space (the power spectrum).
-% JEA - ah, the dimensions again
-% which has dimensions ($N_{f}$,$N_{f}$).
-
-The optimal quadratic estimator prescription is then to compute
-\begin{equation}
-\label{eq:OQE}
-\widehat{P}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
-\end{equation}
-where $\F$ is the Fisher matrix (which determines errors on the power spectrum estimate)
-\begin{equation}
-F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right),
-\end{equation}
-$\widehat{q}$ is the un-normalized power spectrum estimate
-\begin{equation}
-\label{eq:OQEQuadratic}
-\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x},
-\end{equation}
-and $\widehat{b}$ is the additive bias
-\begin{equation}
-\label{eq:OQELinear}
-\widehat{b}^{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
-\end{equation}
-The power spectrum estimator in Equation \eqref{eq:OQE} is the minimum variance (smallest error bar) estimate of the power spectrum subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
-\begin{equation}
-\label{eq:super_unbiased}
-\langle \widehat{P}^{\alpha} \rangle = P^\alpha
-\end{equation}
-\citep{tegmark_et_al1997a,bond_et_al1998}.
-
-Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminants in order to obtain an unbiased estimate of the power spectrum.
-By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
-However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
-
-More specifically, the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
-Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-If the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
-Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
-Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, and which can conservatively be interpreted as an upper limit.
-These considerations, and the difficulty of obtaining an estimate for $\mathbf{U}$, motivate the neglect of the linear bias in the rest of this analysis.
-
-%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
-%which may still produce an unbiased estimate, 
-where Equation \eqref{eq:OQEQuadratic} is replaced by
-\begin{equation}
-\label{eq:qhat}
-\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
-\end{equation}
-where $\textbf{R}$ is a weighting matrix chosen by the data analyst.
-For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
-%with dimensions ($N_{f}$,$N_{f}$) --- as
-
-%%% COME BACK HERE
-% Need to still explain the motivation for this
-With an appropriate normalization matrix $\textbf{M}$, the quantity
-%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
-\begin{equation}
-\label{eq:phat}
-\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
-\end{equation}
-is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.
-
-To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
-\begin{eqnarray}
-\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
-&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
-\end{eqnarray}
-where $W^{\alpha \beta}$ are elements of a window function matrix.
-Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
-However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
-In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized.
-Beyond this, the data analyst has a choice for $
-\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal.
-In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
-If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
-% JEA - is one really free to choose M and R independently?
-
-% JEA - I don't think it's attractive at all
-%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
-Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data to obtain:
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
-\end{equation}
-assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
-We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:CaseStudy}.
-
-%\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
-
-As a brief preview, we summarize our findings in the following sections here:
-
-\begin{itemize}
-
-\item If the covariance matrix is estimated from the data, a strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss''  (Section \ref{sec:toymodel}).
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced (Section \ref{sec:toymodel_frf}).
-
-\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum.
-In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).
-
-%\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
-Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable (Section \ref{sec:toymodel_frf}).
-
-\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to decouple it from the data and produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
-
-% JEA - I really struggle with whether this is intuitively obvious ...
-it's hard to get a sense of what "noise" is averaging down slower.
-All modes have the same number of samples going into the estimate.
-Should I think of the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
-% Also, have we shown this sufficiently rigorously?
-Is the toy model sufficiently general?
-(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
-Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
-
-\end{itemize}
-
-\subsection{Empirical Inverse Covariance Weighting}
-\label{sec:toymodel}
-
-% JEA  - This material was moved up
-%One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
-Said differently, it gives the minimum variance estimate of the power spectrum (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
-%
-%One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
-By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
-Therefore, in an ideal world with perfect foreground,
-%instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
-In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
-
-%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss. 
-Using a toy model, we will now build intuition into how weighting by the inverse of the empirically estimated covariance, $\widehat{\textbf{C}}^{-1}$, can give rise to signal loss.
-We construct a simple dataset that contains visibility data with $100$ time integrations and $20$ frequency channels.
-This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of generality.
-
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation.
-Hence, flat spectrum sources (away from zenith) lead to measured visibilities which oscillate in time and frequency.
-We therefore form a mock visibility measurement of a bright foreground signal, $\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
-We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal.
-A more realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
-However, here we treat all $k$'s separately, so a simplistic white noise approximation can be used.
-Our combined data vector is then $\textbf{x} =
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
-\ref{fig:toy_sigloss1}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.pdf}
-	\caption{Our toy model dataset to which we apply different weighting schemes to in order to investigate signal loss.
-We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in
-time and frequency. We model a mock visibility of an EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$. Real parts are shown here.}
-	\label{fig:toy_sigloss1}
-\end{figure}
-
-%First, 
-We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \eqref{eq:qhat} and \eqref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
-The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
-The power spectrum result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
-Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
-As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds,
-%For our toy model, the successful suppression of the foreground mode is 
-demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
-It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-It is this behavior which we describe as signal loss.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
-	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
-(middle), and FG + EoR (right). Real parts are shown here.}
-	\label{fig:toy_sigloss12}
-\end{figure}
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.pdf}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The power spectrum of the foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare using empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the zeroth eigenmode only (right).
-In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
-% JEA - redundant
-%For an empirically estimated $\widehat{\textbf{C}}$, 
-%its eigenvalues differ from those of the true covariance, where 
-%the coupling between EoR-dominated eigenmodes and the data can lead to loss.
-%Hence, 
-There is negligible signal loss when all eigenmodes besides the foreground one are no longer correlated with the data.
-%assigning identical weights to all eigenmodes except the first, 
-%constructing a covariance proportional to the identity and the outer product of the sinusoid eigenmode, since we are only down-weighting the FG-dominated mode in this case.
-}
-	\label{fig:toy_sigloss3}
-\end{figure*}
-
-As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain %the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in
-a nearly unbiased estimate of the power spectrum.
-The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
-
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection; whether or not it is strongly correlated with the the actual data vector is irrelevant.
-However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
-If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As described in Section \ref{sec:siglossmethod}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
-
-%For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
-Here we will describe the origin of this signal loss intuitively.
-
-%% JEA - I don't think the eigenspectrum really helps, but at some point we probably want to show it ...
-%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
-%
-%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
-In other words, the eigenvalues encode the strength of different shapes in the dataset.
-The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-%% JEA - I think this is actually NOT true - see the toy model as an example.
-The size of the eigenvalues isn't what determines that the undesired mode is downweighted and the others left alone.
-I haven't computed the eigenvalues explicitly, but down-weighting of m occurs regardless of the relative size of s and u.
-%The modes with the highest eigenvalues are down-weighted the most.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
-%(green).
-The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of the true $\textbf{C}$.
-Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
-%	\label{fig:toy_sigloss2}
-%\end{figure}
-
-%We show the {\it eigenspectrum} (the eigenvalues of the matrix in descending order) of this toy model in Figure \ref{fig:toy_sigloss2}.  In this case,
-%For example, 
-%the largest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}). 
-%
-
-%In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
-For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
-
-%If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
-%representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
-%particular data realization, its eigenvalues and eigenvectors may differ from the truth.
-Said differently, shapes that may not exist (or exist rarely) in a true covariance may appear stronger in the estimated covariance.
-Hence, they will be down-weighted
-%more than they should be.
-
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
-
-Armed with this information,
-%Using what we've learned about the eigenspectrum, 
-we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
-% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
-%is a sinusoid, so it 
-can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
-project out the zeroth eigenmode and 
-%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
-then take the remaining covariance to be the identity matrix.  
-This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
-In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
-% down-weight them 
-foregrounds with negligible signal loss.
-
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization.
-There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
-\ref{sec:otherweight}.
-
-\subsection{Fringe-Rate Filtering}
-\label{sec:toymodel_frf}
-
-We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data.
-We will next show how this effect is exacerbated by reducing the total number of independent samples in a dataset.
-
-A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.
-
-Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
-With fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
-We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
-
-% JEA - Death to eigenspectra!
-%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}.
-
-\begin{equation}
-\label{eq:converge}
-\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
-\end{equation}
-where $\C$ is the true covariance matrix.
-To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average.
-We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
-As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following time-averaging, or ``fringe-rate filtering" (different colors).
-With more independent time samples (i.e., more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
-
-The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
-of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
-number of independent simulations results in inaccuracies in estimated covariance matrices 
-\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
-\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
-\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
-galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
-cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
-theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
-marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
-\citep{pope_szapudi2008,joachimi_2017}.
-
-%Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
-This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
-For this particular toy model, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
-For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance by averaging over the realizations.
-The eigenvectors of this empirical covariance are then compared to the true eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
-\begin{equation}
-\label{eq:converge_eig}
-\varepsilon (\widehat{\textbf{v}}) \equiv \sqrt{\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i}^2},
-\end{equation}
-where $N_{f}$ is the number of frequencies ($20$) in the mock data.
-The eigenmode convergence curves in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-We see that the zeroth eigenmode --- the mode describing the foreground signal --- is quickest to converge.
-
-Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate.
-In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances.
-Consider first a limiting case where all eigenvalues are equal.
-In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors.
-In our current test, aside from the zeroth mode, the eigenvalues have similar values but are not precisely equal.
-Hence, there is a well-defined set of eigenvectors to converge to.
-However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
-Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to decouple from each other and approach their true forms.
-A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate.
-To break degeneracies in the remaining modes, however, requires many more realizations.
-
-While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
-The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss.
-However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
-
-In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
-Even for the case of real PAPER data (Section \ref{sec:CaseStudy}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
-However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
-
-%One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
-With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
-As we will see in the next section, using only these eigenmodes, which are less coupled to data realizations, minimizes signal loss.
-In contrast, the lower-valued eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-% JEA - this is redundant
-%Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
-%\acl{Think about whether we need to do the Fourier space version as well.}
-
-% JEA - death to eigenspectra!
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
-The dashed, steep eigenspectrum has a greater risk of signal loss because its lowest-valued eigenmodes are both more strongly coupled to the data (than those of the solid eigenspectrum) and, in this example, are also EoR-dominated.}
-%	\label{fig:toy_sigloss15}
-%\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples (100 of them).
-Subsequent colors show time-averaged signals.
-As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges (i.e., the quicker it decouples from the data), and the less signal loss we would expect to result.}
-	\label{fig:toy_sigloss16}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
-The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the zeroth eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
-On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
-	\label{fig:toy_sigloss17}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
-	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here.}
-	\label{fig:toy_sigloss5}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
-	\caption{Resulting power spectrum estimate for the ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We use empirically estimated inverse covariance weighting where $\textbf{C}$ is 
-computed from the data.
-There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by eigenmodes that are more strongly coupled to the data due to there being fewer independent modes in the data.}
-	\label{fig:toy_sigloss7}
-\end{figure}
-
-With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal.
-We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank.
-We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
-%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
-
-The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
-expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
-In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter.
-This is evident by noticing that the
-green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
-%It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
-This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
-
-Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal 
-loss and noisier estimates when using data-estimated covariance matrices. Longer integrations increase sensitivity but reduce 
-the number of independent samples, resulting in 
-eigenmodes correlated with the data
-% JEA - it's not that they are wrong, but that they are correlated
-%poorly characterized, steep eigenspectra 
-that can overfit signal greatly. We 
-note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be 
-advantageous to use one despite the trade-offs.
-
-\subsection{Other Weighting Options}
-\label{sec:otherweight}
-
-In Section \ref{sec:toymodel} we showed one example of how altering $\widehat{\textbf{C}}$ can 
-make the difference between nearly zero and some signal loss. We will now use our toy model to describe several other ways to tailor $\widehat{\textbf{C}}$ 
-in order to minimize signal loss. We choose four independent regularization methods to highlight in this section, which have 
-been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
-spectra for the different cases in Figure \ref{fig:toy_sigloss8}.
-% and \ref{fig:toy_sigloss14}. 
-These examples are not meant to be taken as suggested analysis methods but rather as illustrative cases.
-
-As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
-avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
-_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
-\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
-left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
-%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each minimize signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\widehat{\textbf{C}}$ (lower right).
-The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
-	\label{fig:toy_sigloss8}
-\end{figure*}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
-%	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
-%weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
-%matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
-%\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-%computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
-%	\label{fig:toy_sigloss14}
-%\end{figure}
-%
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}}_{\rm reg} \equiv 
-\widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
-of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the estimated covariance matrix more heavily than those off-diagonal.
-Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data and there is no loss.
-%Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss by only using the first three eigenmodes of the estimated covariance.
-Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this
-method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights).
-Again, avoiding the overfitting of EoR-dominated modes which are coupled to the data results in negligible signal loss.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are foreground or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
-We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
-
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}}_{\rm reg} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
-In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
-To understand this, we recall that our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by
-the identity matrix, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
-suppressing the foreground.
-But because we decoupled the whole eigenspectrum from the data, we also avoid signal loss.
-Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
-are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more effectively than others based on the spectral nature 
-of the components in a dataset. 
-%One may imagine a situation where a particular systematic is contained to an isolated 
-%frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
-%\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
-
-In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are coupled to data and not converged to their true forms.
-We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
-
-% SECTION 3 CASE STUDY ---------------------------------------------------------------------------------
-
-\section{Signal Loss in PAPER-64}
-\label{sec:CaseStudy}
-
-We now turn to a detailed signal loss investigation using a subset of the PAPER-64 dataset from \citetalias{ali_et_al2015}.
-In the previous section we showed how signal loss arises when weighting data with empirically estimated covariances; in this section we highlight how the amount of this loss was underestimated in the previous analysis.
-Additionally, we illustrate how we have revised our analysis pipeline in light of our growing understandings.
-
-As a brief review, PAPER is a dedicated 21\,cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
-configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
-\ref{fig:ant_layout}).
-All data is compressed, calibrated (using self-calibration and redundant calibration), delay-filtered (to remove foregrounds inside the wedge), LST-binned, and fringe-rate filtered.
-For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
-refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015}.
-We note that all data processing steps are identical to those in \citetalias{ali_et_al2015} until after the LST-binning step in Figure 3 of \citetalias{ali_et_al2015}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
-	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
-paper (i.e., a subset of the shortest horizontal spacings).}
-	\label{fig:ant_layout}
-\end{figure}
-
-The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} placed a $2\sigma$ upper limit 
-on $\Delta^{2}(k)$, defined as
-
-\begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{P}(k),
-\end{equation}
-
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$. The need to revise this limit stems mostly from previously underestimated signal loss, which we 
-address in this section.
-
-For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
-range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
-We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}, in order to illustrate our revised methods.
-All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
-In the case study in this paper, we only use one baseline type instead of the three as in
-\citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues that will be made clear later on).
-
-The most significant changes from \citetalias{ali_et_al2015} occur in our revised power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
-In \citetalias{ali_et_al2015}, the
-applied filter was not equivalent to the optimal fringe-rate filter (which is designed to maximize power spectrum sensitivity).
-Instead, the optimal filter was degraded slightly by widening it in fringe-rate space.
-This was chosen in order to increase the number of independent
-modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still underestimated. With the development of a new, 
-robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
-computed for a fiducial 30\,m baseline at 150\,MHz, the center frequency in our band. The filter in both the fringe-rate 
-domain and time domain is shown in Figure \ref{fig:frp}.
-
-Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
-As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
-Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/frp.pdf}
-	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
-Stokes I polarization beam. Bottom: the time domain convolution kernel corresponding to the top panel. Real and imaginary 
-components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black. The fringe-rate filter acts as 
-an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
-	\label{fig:frp}
-\end{figure}
-
-We present our PAPER-64 signal loss investigation in three parts.
-We first give an overview of our signal injection framework which is used to estimate loss.
-In this framework (and as in \citetalias{ali_et_al2015}), we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
-As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
-Next, we describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
-Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}.
-
-% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
-
-\subsection{Signal Loss Methodology} 
-\label{sec:siglossmethod}
-In short, our method for estimating signal loss consists of adding an EoR-like signal into visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
-To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
-Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals)
-are filtered in time using an optimal fringe-rate filter to retain only ``sky-like" modes.
-Since the optimal filter has a shape that matches the rate of the sidereal motion of the sky, this transforms the Gaussian noise into a measurement that PAPER could make.
-This signal is then added to the visibility data.\footnote{One
-specific change from \citetalias{ali_et_al2015} is that we add this simulated signal - which has been fringe-rate filtered once already in order to transform it into a ``sky-like" signal - into the analysis pipeline before a fringe-rate filter is
-applied to the data (i.e., prior to the analysis step of fringe-rate filtering). Previously, the addition was done after the fringe-rate filter analysis step.  This change results in an increased 
-estimate of signal loss, %(by a factor of $\sim$$10$), 
-likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was underestimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
-
-Mathematically, suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level).
-We do not know the true EoR signal contained within our visibility data, $\textbf{x}$, so $\textbf{e}$ takes on the role of the true EoR signal (for which we measure its loss).
-Furthermore, one can make the assumption that the true EoR signal is small within our measured data, so the data vector $\textbf{x}$ itself is representative of mostly contaminants.
-Using this assumption, the sum of $\textbf{x}$ and $\textbf{e}$, defined as $\textbf{r}$:
-
-\begin{equation}
-\label{eq:rxe}
-\textbf{r} = \textbf{x} + \textbf{e},
-\end{equation}
-can be thought of as the sum of contaminants plus EoR.
-The quantity $\textbf{r}$ then becomes the dataset for which we are measuring how much loss of $\textbf{e}$ there is due to our power spectrum pipeline.
-
-We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
-spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as
-
-\begin{equation}
-\label{eq:Pin}
-\widehat{P}_{\rm in}^{\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
-\end{equation}
-
-\noindent and
-
-\begin{eqnarray}
-\label{eq:sigloss}
-\widehat{P}_{\rm out}^{\alpha} &\equiv& \widehat{\textbf{P}}_{r}^{\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
-&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
-\end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-
-The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
-It can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
-The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-The input power spectrum is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-
-%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e., the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
-In other words, we make the anzatz that
-
-%\begin{equation}
-%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
-%\end{equation}
-%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
-%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}
-
-Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:
-
-%
-%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
-%
-%In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
-%\begin{equation}
-%\x \equiv \f + \s,
-%\end{equation}
-%where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
-In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$.
-This can be parametrized as
-%\begin{equation}
-%\label{eq:LinearPspecSum}
-%\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
-%\end{equation}
-%where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
-%power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
-%\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
-%\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-%which assumes that the covariance used in the QE analysis is close to the true covariance with effects due to 
-%small sample size limited to first order perturbations and thus neglects cross-correlation between $x$ and $e$.  
-%In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
-%terms to be remain significant.   
-%
-%Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
-Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
-%\begin{equation}
-%\label{eq:Deriv1}
-%\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
-%\end{equation}
-%However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
-Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
-%\begin{equation}
-%\label{eq:Deriv2}
-%\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
-%\end{equation}
-%which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
-Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
-Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$.
-In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.
-%
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
-\dcj{Here is the post-hoc justification for this signal loss method.
-Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum.
-So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}.
-Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example.
-The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
-Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
-%\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
-%\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
-%covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
-%correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
-%I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-%then explaining in the next section exactly how cross-terms were what messed us up in the first go round.} 
-%\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
-It's not.
-It's meant as a motivational example.
-I just wanted something where I could follow through analytically to the end to show that it's ok to think about signal loss as a multiplicative factor.
-At least in expectation.
-And then how one deals with not correcting for the signal loss in expectation is described in Section \ref{sec:Practice}.}
-%
-%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
-%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
-%distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
-%distribution could this (signal-loss affected) data come from?" 
-%
-%In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
-Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
-%signal loss lens.
-We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
-One alternative to the method described in Section \ref{sec:Practice} is described in Appendix \ref{sec:Pr_appendix}.
-%%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
-
-%\subsubsection{Signal Loss Illustration}
-%\label{sec:Illustration}
-%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
-
-\begin{eqnarray}
-\label{eq:crossterm_full}
-\widehat{P}_{\rm out}^{\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
-%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
-%\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:
-
-\begin{eqnarray}
-\label{eq:crossterm}
-\widehat{P}_{\rm out}^{\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}. %\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-One of the key takeaways of this section is that the \citetalias{ali_et_al2015} analysis estimated signal loss by comparing \textit{only} the signal-only term (second term in Equation \eqref{eq:crossterm}) with $\widehat{P}_{\rm in}$, whereas in fact the cross-term (third term in Equation \eqref{eq:crossterm}) can substantially lower $\widehat{P}_{\rm out}$.
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$).
-We will now go into further detail and examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
-
-{\bf Small injection:}
-%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
-They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
-%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
-In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
-Output values are Gaussian distributed around zero, spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
-%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$.
-It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black).
-We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-
-{\bf Large injection:}
-When the injected signal is much larger than the measured power spectrum, the data-only components can 
-be neglected as they are many orders of magnitude smaller.
-We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e., in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
-However, it is useful as a check of our system in a relatively simple case.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green).
-Here only does the signal-only term used in \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
-This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-
-{\bf In between:}
-When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
-the weighted injected power spectrum component mirrors the input power indicating little loss (i.e., the green curve follows the dotted black line), eventually 
-departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-in this regime the cross-term (red) has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
-This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
-Again, we emphasize that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for underestimating power spectrum limits in \citetalias{ali_et_al2015}.
-
-%A brief description of Figure \ref{fig:sigloss_terms} is as follows.
-The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed.
-The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$).
-It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$.
-The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$.
-This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
-It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
-We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss.
-In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
-
-%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
-%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
-For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
-%
-%\begin{eqnarray}
-%\label{eq:pout_expand}
-%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
-% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
-%\end{eqnarray}
-%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
-However, without taking into account the cross-terms (the second term), we can substantially underestimate loss.
-In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
-Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
-	\caption{Illustration of the power spectrum amplitude of five different power spectrum terms, each a function of visibility data ($\textbf{x}$), simulated injected EoR signal ($\textbf{e}$), or both ($\textbf{r}$).
-This figure shows how these quantities behave as the power level of the injected EoR signal increases (along the x-axis).
-The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.
-We emphasize that the output power spectrum in black ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-Roughly speaking, it can be compared to the input signal level ($P_{\rm in}$) to estimate the amount of signal loss.
-Left: Empirical inverse covariance weighting is used in power spectrum estimation, as done in \citetalias{ali_et_al2015}.
-The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss).
-The gray horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power).
-The green signal-signal component is the term used in \citetalias{ali_et_al2015} to estimate signal loss.
-It is significantly higher than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue).
-In the regime where cross-correlations between signal and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative estimates due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
-This causes the difference between the green curve (which exhibits negligible loss at the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss).
-Right: The same power spectrum terms illustrated for the uniform weighted case.}
-\label{fig:sigloss_terms}
-\end{figure*}
-
-The source of the strong negative cross-term is not immediately obvious, however it is an explainable effect. 
-When $\textbf{R}_{r}$
-is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the third term of Equation \eqref{eq:crossterm} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
-$\widehat{\textbf{C}}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
-This negative cross-term power arises from a coupling between the inverse of 
-$\widehat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
-Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$:
-
-\begin{eqnarray}
-\widehat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
-&=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
-\textbf{ee}^{\dagger} \rangle_{t},
-\end{eqnarray}
-
-\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e., the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
-Without loss of generality, we will assume
-an eigenbasis of $\textbf{e}$, so that $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
-two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
-ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}%\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}
-, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
-off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ but
-contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
-correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
-of a diagonal-dominant matrix.
-% XXX [ARP: we may want to write this all out explicitly in an appendix]
-
-%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
-Therefore, in our revised
-%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
-%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
-
-%\dcj{This paragraph has me confused.}
-%The conclusion is that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
-In principle, using $\widehat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
-Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
-However, despite the loosening of these approximations, one sees that the qualitative message (of anti-correlations resulting in signal loss) remains intact.
-
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
-Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
-However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
-The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
-
-\subsection{Signal Loss in Practice}
-\label{sec:Practice}
-
-We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
-outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
-($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. %With this weighting, our 
-%expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
-
-%\begin{eqnarray}
-%\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-%\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}%\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
-%\end{eqnarray}
-
-%The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
-In practice, however, the signal loss itself is a random variable --- some realizations of the cosmological signal may be more correlated with foreground modes than others, leading to more signal loss.
-This leads to two issues.
-The first is that Equation \eqref{eq:LinearPspecSum} may not hold.
-In particular, a third term that is a quadratic combination of $\f$ and $\s$ (e.g., $\f^\dagger \C^{-1} \s$) may appear.
-However, we can circumvent this issue by decomposing $\f$ into a sum of two vectors, one that is proportional to $\s$ and one that is orthogonal to $\s$.
-The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-In other words, suppose that we have
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
-%\end{equation}
-%in place of Equation \eqref{eq:LinearPspecSum}.
-Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
-Further parameterize $\mathbf{ f}_\parallel \equiv \rho \mathbf{e}$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-This then gives
-%\begin{equation}
-%\label{eq:fperpfpara}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
-%\end{equation}
-%Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
-%\dcj{Wait what?
-I think you are saying essentially that some x can remain in Pout which is what we are seeing.
-Or is this some extra bit of method which has been added to the analysis...} \acl{I'm not sure that's what I'm saying.
-(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure").
-What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
-%\end{equation}
-%(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
-%$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
-%couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
-%some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
-%Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
-%EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
-%the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
-%dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-%$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-%\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
-%\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
-Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
-What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
-So essentially we are defining an effective $
-%\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
-
-One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e., how much coupling there is, which affects how much loss results).
-
-For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator.
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} |
-\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
-In other words,
-
-\begin{equation}
-\label{eq:Bayes}
-p(P_{\rm in} | \widehat{P}_{\rm out}) \propto {\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
-\end{equation}
-
-\noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus signal injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
-by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum over $\widehat{P}_{\rm out}$ is unity, and the 
-whole process is then repeated for a different value of $P_{\rm in}$.
-
-%\subsubsection{Signal Loss Implementation Details}
-%\label{sec:Implementation}
-
-The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss.
-To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
-We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
-$\widehat{P}_{\rm out}$ grid.
-
-Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level) and, since they are well-approximated by a Gaussian distribution in our numerical results, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
-Stitching all of them together results in a 2-dimensional transfer function --- the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
-We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
-%For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
-
-Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
-Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior.
-Although we only show figures for one $k$-value, we note that
-the shape of the transfer curve is similar for all $k$'s.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ represents a (lossy) power spectrum.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
-We normalize this final distribution and compute the $95\%$ confidence interval (an upper limit on EoR).
-
-%We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
-We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
-Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
-
-By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
-\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
-
-%As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
-Ideally, running many simulations would lead to convergence; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
-\dcj{This dependence on injection count was checked with a run having 10x the usual number of integrations.} To separate the intrinsic stochasticity of signal loss from that which arises due to simulation sample variance, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-Here the scatter, evident as deviations from unity-transfer, is entirely due to finite sample variance.
-To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $\widehat{P}_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
-By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
-%look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
-As an extreme example, if we are very unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
-An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
-On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $\widehat{P}_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
-
-%The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
-%nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $\widehat{P}_{\rm out}$ value for every 
-%$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
-%scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
-%\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-%every bootstrap (for reasons made clear in the next paragraph), there is a range of $\widehat{P}_{\rm out}$ values that results from the same 
-%$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
-%the spread in the weighted case (left plot).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
-Since our $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
-This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored
-heat-maps on top of the points. Two cases are displayed: empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does
-not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
-	\label{fig:sigloss_transfercurve}
-\end{figure*}
-
-%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($\widehat{P}_{\rm out} > P_{in}$).
-\cc{This is a log-plotting effect and is under-construction!}.
-%This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. 
-%
-%The shape of our signal loss transfer function can be described as follows.
-At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}.
-As $\textbf{e}$ increases, we move
-%into a regime where $\widehat{P}_{\rm out} \sim P_{in}$, and then eventually into a regime where $\widehat{P}_{\rm out} < P_{in}$ when $\textbf{e}$ is 
-%large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
-%the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
-%	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on %PAPER-64 data after signal loss correction.
-Power spectrum points are computed from the peak of the distributions.
-Errors are computed using $95\%$ confidence intervals.}
-%	\label{fig:sigloss_datadist_inversecovariance}
-%\end{figure*}
-
-The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red).
-%There are a few important checks to examine.
-First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
-This is an important check, as we expect no signal loss for this case.
-Any difference here would indicate an error in the pipeline or discrepancy in the range of data included.
-Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars from bootstrapping, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
-We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of empirical inverse covariance weighting.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
-Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:Error}.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-In this example, we see that the lossy power spectrum limit is $\sim 4$ orders of magnitude too low when using empirical inverse covariance weighting.}
-\label{fig:ps2_data}
-\end{figure*}
-
-\subsection{Minimizing Signal Loss}
-\label{sec:Weight}
-
-With a signal loss formalism established, we now have the capability of experimenting 
-with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
-foregrounds and systematics in our data without generating large amounts of signal loss as we have seen with the inverse covariance estimator. We have found that the balance 
-between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
-
-We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e., flattening out part of the 
-eigenspectrum and effectively decoupling the lowest-valued eigenmodes, which are typically EoR-dominated, from the data) can help minimize signal loss.
-We experiment with this idea on PAPER-64 data, dialing the number of modes
-that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
-covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
-estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
-subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
-increases with the number of down-weighted modes (solid red).
-The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
-\citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
-
-Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to uniform weighting (blue).
-In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
-only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting).
-For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
-
-We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss.
-We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as a percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
-We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
-From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
-We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear ``minimum" that produces the least loss.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
-are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e., unweighted) to $21$ modes on the right (i.e., the full inverse 
-covariance estimator).
-$\sim4$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
-Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e., very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
-Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
-weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.09 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.09$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
-	\label{fig:sigloss_modeloop}
-\end{figure*}
-
-In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
-in both panels and represents a third regularization technique.
-This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity
-matrix element-wise to $\widehat{\textbf{C}}$).
-This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
-We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
-
-It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
-Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations.
-Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
-(\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.
-
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) using the analysis presented in this paper is shown in Figure
-\ref{fig:ps1_data}.
-Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework.
-The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
-$2\sigma$ errors bars from bootstrapping).
-It is also shown as an upper limit using the signal injection framework (solid blue), which is interestingly larger than the errors computed from bootstrapping, likely because the full injection framework takes into account additional sample variance whereas the bootstrapped errors do not.
-Finally, the gray shaded regions combine the measured uniform weighted power spectrum values with thermal noise errors.
-We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case, thus further motivating uniform-weighting for Kolopanis et al.
-(\textit{in prep.}).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of $\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
-(\textit{in prep.}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
-loss, bootstrapping, and the theoretical error computation. We see that the regularization scheme used here produces limits similar to the unweighted limits.}
-	\label{fig:ps1_data}
-\end{figure*}
-
-In this section we have shown three simple ways of regularizing $\widehat{\textbf{C}}$ to minimize signal loss using PAPER-64 
-data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
-$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this might mean calculating $
-\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$\,m diagonal PAPER baselines (instead of the 
-horizontal E/W ones). Alternatively, covariances could be estimated from all baselines except the two being cross-multiplied 
-when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
-21\,cm signal, and it is worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
-because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{in prep.})).
-
-Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
-down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.
-Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from
-data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
-
-In Section \ref{sec:CaseStudy}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
-We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
-In the remainder of this paper, we will transition to other aspects of our analysis that have been revised since \citetalias{ali_et_al2015}.
-
-% SECTION 4 OTHER ERRORS ---------------------------------------------------------------------------------
-
-\section{Additional PAPER-64 Revisions}
-\label{sec:OtherErrors}
-
-Underestimated signal loss is the main reason for the revision of the power spectrum limits from \citetalias{ali_et_al2015}.
-It is interesting to note that --- had all the other aspects of the original analysis been correct --- the underestimated limits may have been more easily caught.
-Unfortunately, two related power spectrum components, namely the error bars on the power spectrum data points and the theoretical noise prediction, were also calculated incorrectly.
-
-In this section, we summarize multiple inconsistencies and errors that have been found since the previous analysis in terms of error estimation.
-We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
-We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified through simulations.
-
-\subsection{Bootstrapping}
-\label{sec:Boot}
-
-Broadly speaking, we desire robust methods for determining accurate 
-confidence intervals for our measurements. For PAPER's analysis, we choose a data-driven method of error estimation, computing error bars that have been derived from the inherent 
-variance of our measurements. A common technique used to do this is bootstrapping, which we first define below and then discuss its application to PAPER.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, bootstrap measurements (of power spectra, for example) can be made from different random samples of data.
-Each of these bootstraps is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-%Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements).
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
-Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap).
-Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
-The error (on the mean) is then computed as the standard deviation across all bootstraps.
-
-%We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
-$N_{\rm boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
-Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
-However, we will see that $N$ depends on sample independence, and it is this dependence that led to the underestimation of errors in \citetalias{ali_et_al2015}.
-
-%Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
-This could represent $1000$ power spectrum measurements, for which we are interested in its error.
-We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-%We next form $500$ bootstraps ($N_{\rm boot} = 500$).
-To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
-The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
-This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
-values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
-and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
-itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, underestimates 
-errors.
-
-%As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of independent data samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$).
-This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both underestimate the error by drawing too many or overestimate it by drawing too few.
-However, since we know that we have $100$ independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-%	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-%sampling with replacement.
-The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
-The estimated errors match up with the theoretical prediction only at $N=100$.}
-%	\label{fig:toy_error1}
-%\end{figure}
-
-This is the precisely how errors were underestimated in PAPER-64.
-Because of fringe-rate filtering, which averages data in time to increase sensitivity, PAPER-64 data is correlated along the time axis.
-Hence, there are fewer independent samples after filtering, thus decreasing the variance of the bootstraps.
-
-More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time.
-In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis, and a total of $400$ bootstraps were created in this step, each comprised of randomly selected values sampled with replacement (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Means were then taken of the values in each bootstrap. Finally, power 
-spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap greatly 
-exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds of these random 
-samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
-\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-
-In addition to learning how sample independence affects bootstrapped errors, we have made three additional changes to our bootstrapping procedure since \citetalias{ali_et_al2015}, summarized here:
-
-\begin{itemize}
-
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
-
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into five independent groups, where no baselines were repeated in each group.
-Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
-This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
-Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
-
-\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
-
-\end{itemize}
-
-In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
-Bootstrapping can be an effective and straightforward way to estimate errors of a dataset, however, bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
-We have thus avoided this issue by removing one of our bootstrap axes, as well as updated several other details of our procedure to ensure accurate re-sampling and error estimation.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
-This underestimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
-We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
-	\label{fig:data_errors}
-\end{figure}
-
-\subsection{Theoretical Error Estimation}
-\label{sec:Error}
-
-One useful way of cross-checking measured power spectrum values and errors is to compute a theoretical estimation of thermal noise based on observational parameters.
-Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-Upon re-analysis of PAPER-64, we have discovered that this estimate was also underestimated in previous analyses.
-
-To compute our theoretical noise estimate, we use an analytic sensitivity calculation.
-Through detailed studies using several independently generated noise simulations, what we found was that our simulations all agreed but were discrepant with the previous calculations.
-The analytic
-calculation is only an approximation and attempts to combine a large number of pieces of information in an approximate way; however, when re-considering some of the approximations, the differences were large enough (factors of $10$ in some cases) to warrant a
-careful investigation. What follows here is an 
-accounting of the differences which have been discovered.
-We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots in this paper, is computed with these changes accounted for.
-
-The noise prediction $n(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
-interferometric 21\,cm data, in temperature-units, is:
-
-\begin{equation}
-\label{eq:sense}
-N(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
-\end{equation}
-We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in \citetalias{ali_et_al2015}.
-
-\begin{itemize}
-\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
-distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} \, h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
-\item $\Omega_{\rm eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
-The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted.
-Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{\rm eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
-filter and the PAPER primary beam. 
-\item $T_{\rm sys}$: The system temperature is set by:
-
-\begin{equation}
-\label{eq:sys}
-T_{\rm sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{\rm rcvr},
-\end{equation}
-
-where $\nu$ are frequencies in GHz (\citealt{thompson_et_al2001}). We use a receiver temperature of $144$\,K, yielding $T_{\rm sys} = 431$\,K at $150$\,MHz. 
-This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
-identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying two independent visibility measurements. In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
-\item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
-because we integrate incoherently over time. For PAPER-64, $N_{\rm lst} = 8$.
-\item $N_{\rm seps}$: The number of baseline separation types (where baselines of a unique separation type have the same orientation and length) averaged incoherently in a final power spectrum estimate.
-For the
-analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines).
-However, both the updated limits in Kolopanis et al.
-(\textit{in prep.}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
-\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e., a 
-fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
-using the following:
-\begin{equation}
-t_{\rm int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
-\end{equation}
-where $t_{i}=43$ seconds, $t_{\rm int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
-taken over all fringe-rates. For PAPER-64, this number is $t_{\rm int} = 3857$\,s. 
-\item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even" in order to avoid noise biases).
-Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
-$N_{\rm days}$. Our expression therefore becomes:
-\begin{equation}
-N_{\rm days} = \sqrt{\langle N_{i}^{2}\rangle} \sqrt{(N_{\rm datasets}^{2}-N_{\rm datasets})}
- %\frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ indexes LST and frequency channel over all datasets (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim47$ 
-days.
-\item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total} = 51$) neglects 
-the fact that the \citetalias{ali_et_al2015} analysis averages baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
-\begin{equation}
-N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{\frac{N_{\rm gps}^{2}-N_{\rm gps}}{2}},
-\end{equation}
-\noindent where, in the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big).
-A revised \citetalias{ali_et_al2015} analysis should therefore use $N_{\rm bls} \sim 32$ instead of $51$, and this change is taken into account in Figure \ref{fig:sense_check}.
-However, the analysis in this paper and in Kolopanis et al.
-(\textit{in prep.}) no longer averages baselines into groups ($N_{\rm gps} = 1$).
-For the subset of data presented in this paper, $N_{\rm bls} = 10$.
-\item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
-\end{itemize}
-
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s to form $\Delta^{2}(k)$.
-
-Our revised sensitivity estimate for the \citetalias{ali_et_al2015} analysis of PAPER-64 is shown in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/sense_check.pdf}
-	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
-\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:Error}, which when combined decreases our 
-sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
-	\label{fig:sense_check}
-\end{figure}
-
-To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
-random noise assuming a constant $T_{\rm rcvr}$ (translated into $T_{\rm sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{\rm days}$ as determined 
-by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{\rm sys}$ into a root-mean-square variance statistic 
-using:
-
-\begin{equation}
-\label{eq:noise}
-T_{\rm rms} = \frac{T_{\rm sys}}{\sqrt{\Delta\nu \Delta t N_{\rm days} N_{\rm pols}}},
-\end{equation}
-
-\noindent where $\Delta\nu$ is the channel spacing, $\Delta t$ is the integration time, $N_{\rm days}$ is the number of daily counts for a 
-particular time and frequency that went into our LST-binned set, and $N_{\rm pols}$ is the number of polarizations ($2$ for Stokes 
-I). This temperature sets the variance of the Gaussian random noise.
-
-Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}.
-We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance.
-However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
-While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
-Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations.
-Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{The power spectrum for a noise simulation that mimics the noise level of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework (red and blue) are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
-	\label{fig:ps_noise}
-\end{figure*}
-
-% CONCLUSION ---------------------------------------------------------------------------------
-
-\section{Conclusion}
-\label{sec:Con}
-
-Although current 21\,cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
-ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like 
-HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
-that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline and be able to accurately 
-and robustly calculate both power spectrum and theoretical errors.
-
-In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
-signal loss and error estimation, which can be summarized as follows:
-
-\begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances due to couplings with the data realizations (Section 
-\ref{sec:SiglossOverview}). Loss of the 21\,cm signal is especially significant the fewer number of independent modes that
-exist in the data. Hence, there exists a trade-off between sensitivity driven 
-time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:siglossmethod}). However, a 
-signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for correlations between the data and signal which can be large and negative.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:Boot}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
-simple and accurate way of estimating errors.
-\end{itemize}
-
-As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, and accurately estimating thermal noise.
-Our revised PAPER-64 limits are presented in Kolopanis et al.
-(\textit{in prep.}), which supersede all previously published PAPER limits.
-Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
-(\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
-However, the main reasons for a previously underestimated limit (\citealt{ali_et_al2018}) and
-ways in which our new analysis differs can still be summarized by the following:
-
-\begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was underestimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
-covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
-\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-Underestimated signal loss therefore represents the bulk of our revision.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
-Several other errors were also found regarding error estimation, though with smaller effects.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:Error}). We note that our sensitivity prediction is revised by a factor less than our overall
-power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
-points.
-\end{itemize}
-
-The future of 21\,cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
-foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
-instruments.
-On the power spectrum analysis side, robust signal loss simulations and precise error calculations will play critical roles in accurate 21\,cm results.
-With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
-
-% ACKNOWLEDGEMENTS ---------------------------------------------------------------------------------
-
-\section{Acknowledgements}
-CC would like to acknowledge the UC Berkeley Chancellor's Fellowship and National Science Foundation Graduate Research 
-Fellowship (Division of Graduate Education award 1106400). She would also like to thank Phil Bull, Bryna Hazelton, Miguel Morales, and Eric Switzer for helpful discussions. PAPER and HERA 
-are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
-also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
-SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
-JSD acknowledges NSF AAPF
-award 1701536.
-GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184.
-This work is based on research supported in part by the National Research Foundation of South Africa (award 103424).
-We graciously thank SKA-SA for site infrastructure and observing support.
-\label{sec:Ack}
-
-% APPENDIX ---------------------------------------------------------------------------------
-
-%\color{blue}
-
-\begin{comment}
-
-\appendix
-\section{A toy model for inverse covariance weighting}
-\label{sec:icw_appendix}
-
-%AAAXXX
-
-In this Appendix, we focus on the optimal quadratic estimator, Equation \eqref{eq:OQE}, and mathematically illustrate its role in estimating the power spectrum of EoR.
-While there exists detailed literature about quadratic estimators in general (e.g., \citealt{liu_tegmark2011}; \citealt{trott_et_al2012}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}), here we focus on two simple cases in order to outline one situation where the estimator successfully suppresses contamination and one where it does not.
-By describing these two cases, we hope to clarify and motivate the desire to use OQE while also understanding its limitations.
-
-We specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
-We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
-\begin{equation}
-\Delta_i = \sigma_i + \upsilon_i
-\end{equation}
-with 
-\begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S},
-\end{equation}
-where we wish to estimate $s$.  The contaminant in this first case has a similar structure (as the EoR) for its covariance, and is assumed uncorrelated with the signal
-\begin{equation}
-\label{eq:IdealToyModelCovariance}
-\langle \upsilon_i \rangle = 0; \; 
-\langle \upsilon^2_i \rangle = u; \; 
-\langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{I}_{N \times N} \equiv \mathbf{U}; {\rm and}~ 
-\langle \sigma_i \upsilon_j \rangle = 0.
-\end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \eqref{eq:OQE} is
-\begin{equation}
-\label{eq:IdealToyModelEstimator}
-\hat{s} = \frac{ \bm{\Delta^T \Delta}}{N} 
-\end{equation}
-and its expectation is
-\begin{equation}
-\langle \hat{s} \rangle = s + u.
-\end{equation}
-Thus, {\it when the covariance structure of the contaminant is identical to the signal} ($\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$), the information available to the quadratic portion of the estimator to distinguish between the two is degenerate, and knowledge only of $\C$ and $\PDeriv{\C}{s}$ is inadequate.
-In order to obtain an unbiased estimate of $s$, one must also use knowledge of $\mathbf{U}$.
-Indeed, computing the linear bias from Equation \eqref{eq:OQELinear}, one finds $b = u$.
-
-Now consider a case, chosen to be very similar to the toy model in \ref{sec:toymodel},  in which the data again have an additive contaminant, now given by
-\begin{equation}
-\Delta_i = \sigma_i + \upsilon m_i
-\end{equation}
-where the properties of $\sigma_i$ are as before, but now $\upsilon$ is a random variable and $m_i$ is a fixed function of $i$ with
-\begin{equation}
-\langle \upsilon \rangle = 0; \;
-\langle \upsilon^2 \rangle = u; \; 
- \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{m m}^T \equiv \mathbf{U}; \;
- \mathbf{m}^T \mathbf{m} = 1; \; {\rm and}~ 
-\langle \sigma_i \upsilon \rangle = 0.
-\end{equation}
-Here $\mathbf{m}$ represents a mode which is correlated across many data points (i.e., we are assuming $\mathbf{U}$ need {\it not} be diagonal), with amplitude given by  $\upsilon$.
-The normalization of $\mathbf{m}$ is a matter of convention, and can be absorbed in the variance $u$; the choice above will be convenient for understanding the limiting case $u \gg s$.
-
-We can calculate the quadratic portion of the estimator explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
-\begin{equation}
-\xi \equiv \frac{u/s}{1+u/s},
-\end{equation} 
-we have
-\begin{equation}
-\invC  =   \frac{1}{s} \left(\I - \xi \mathbf{m m}^T \right)
-\end{equation}
-and
-\begin{equation}
-\hat{s} = 
-%\half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = 
-\frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
-\end{equation}
-with expectation
-\begin{equation}
-\langle \hat{s} \rangle = 
-s + \frac{1 - 2 \xi + \xi^2}{N + - 2 \xi + \xi^2} u. 
-\end{equation}
-It is worth observing immediately that there is no multiplicative bias on $s$, and that the additive bias is strictly $< u/N$.
-
-An instructive limit is $u \gg s$, $\xi \to 1$, in which case the virtue of weighting by $\invC$ becomes clearer, as it becomes
-\begin{equation}
-\invC  = \frac{1}{s} \left(\I - \mathbf{m m}^T \right)
-\end{equation}
-where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any vector it acts on, and further, the linear bias tends to 0 as $\xi \to 1$ (i.e., the projection is ``perfect'' and not ``undone'' by the Fisher matrix normalization).
-
-This is the ideal case for the inverse covariance weighting performed in the PAPER analysis, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
-But even in this case, it is worth pointing out that the estimator still has a linear bias for finite $u$.
-We have also assumed that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
-
-\color{black}
-
-%\appendix
-\section{A toy model for signal loss}
-\label{sec:sigloss_appendix}
-
-In this Appendix, we examine a toy model for signal loss.
+In this memo, we examine a toy model for signal loss.
 Our goal is to derive an analytic formula for power spectrum signal loss.
-While this model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
+While this model does not apply generally to all the scenarios, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
 
@@
 
-\section{Derivation of the Jeffreys Prior}
-\label{sec:jeffreys}
-
-The Jeffreys prior is an objective, non-informative prior distribution for a parameter space using Bayesian probability (\citealt{jaynes1968}).
-For the signal injection framework outlined in Section \ref{sec:Practice}, we wish to compute the prior $p(P_{\rm in})$, or the probability density of the power spectrum of the EoR signal.
-
-The Jeffreys prior is defined as:
-
-\begin{equation}
-\label{eq:jeffreys}
-p(P_{\rm in}) \propto \sqrt {\Bigg\langle \Bigg(\frac{\partial \mathcal{L}}{\partial P_{\rm in}} \Bigg)^{2}\Bigg\rangle},
-\end{equation}
-
-\noindent where
-
-\begin{equation}
-\label{eq:logprob}
-\mathcal{L} = \mathrm{ln} \, p(\widehat{P}_{\rm out} | P_{\rm in}),
-\end{equation}
-
-\noindent recalling that in our framework $P_{\rm in}$ is the power spectrum of the EoR signal (uniformly weighted), and $\widehat{P}_{\rm out}$ is the weighted output power spectrum of the data plus EoR.
-
-For a single injection amplitude, our bootstrapped $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution.
-Simplifying our notation so that $x = P_{\rm in}$ and $y = \widehat{P}_{\rm out}$:
-
-\begin{equation}
-\label{eq:prob}
-p(y | x) = \frac{1}{\sigma(x) \sqrt{2\pi}} e^{-\frac{1}{2}\big(\frac{y-\bar y(x)}{\sigma}\big)^{2}},
-\end{equation}
-
-\noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Combining Equations \eqref{eq:jeffreys}, \eqref{eq:logprob}, and \eqref{eq:prob} the Jeffreys prior simplifies to become:
-
-%\begin{eqnarray}
-%\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
-%&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
-%\end{eqnarray}
-
-%Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
-Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
-Finally, after some additional simplification the Jeffreys prior becomes:
-
-\begin{equation}
-\label{eq:jeffreys_final}
-p(x) \propto \sqrt{ \frac{1}{\sigma^{2}}\Big(2\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} + \Big(\frac{\partial \bar y}{\partial x}\Big)^{2}\Big) }.
-\end{equation}
-
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
-For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-%An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
-%	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
-Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
-The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
-%	\label{fig:jeffreys1}
-%\end{figure}
-
-We show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
-Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.
-Therefore, due to its objective nature we choose to use a Jeffreys prior in our analysis, multiplying our likelihood functions by Equation \eqref{eq:jeffreys_final} before computing posterior distributions.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=10cm]{plots/jeffrey_prior.pdf}
-	\caption{An example of the typical Jeffreys prior shape for the PAPER-64 analysis as computed by Equation \eqref{eq:jeffreys_final} (black).
-We smooth the prior using a sliding boxcar average over every $5$ injection levels (red).
-Most noticeably, the Jeffreys prior is not constant with $P_{\rm in}$, meaning a uniform prior would be an informative prior.}
-	\label{fig:jeffreys2}
-\end{figure}
-
-\end{comment}
-
 \bibliographystyle{apj}

### 2018-10-09 Memo3_jeffreysprior.tex
adding memos corresponding to 3 appendices

--- 2018-10-08 PAPER.tex
@@
 
-% Math shortcuts from Danny
-\newcommand{\Prob}{\mathbf{P}}
+\begin{document}
 
-\begin{document}
-\title{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64}
-
-\author{
-Carina Cheng\altaffilmark{1}$^{,\diamond}$,
-Aaron R. Parsons\altaffilmark{1,2},
-Matthew Kolopanis \altaffilmark{3},
-Daniel C. Jacobs\altaffilmark{3}, 
-Adrian Liu\altaffilmark{1,4}$^{,\dagger}$, 
-Saul A. Kohn\altaffilmark{5},
-James E.~Aguirre\altaffilmark{5},
-Jonathan C. Pober\altaffilmark{6}, 
-Zaki S. Ali\altaffilmark{1}, 
-Gianni Bernardi\altaffilmark{7,8,9}, 
-Richard F. Bradley\altaffilmark{10,11,12},
-Chris L. Carilli\altaffilmark{13,14},
-David R. DeBoer\altaffilmark{2}, 
-Matthew R. Dexter\altaffilmark{2},
-Joshua S. Dillon\altaffilmark{1}$^{,*}$,
-Pat Klima\altaffilmark{11},
-David H. E. MacMahon\altaffilmark{2},
-David F. Moore\altaffilmark{5},
-Chuneeta D. Nunhokee\altaffilmark{8},
-William P. Walbrugh\altaffilmark{7},
-Andre Walker\altaffilmark{7}
-}
-
-\altaffiltext{1}{Astronomy Dept., U. California, Berkeley, CA}
-\altaffiltext{2}{Radio Astronomy Lab., U. California, Berkeley CA}
-\altaffiltext{3}{School of Earth and Space Exploration, Arizona State U., Tempe AZ}
-\altaffiltext{4}{Berkeley Center for Cosmological Physics, Berkeley, CA} 
-\altaffiltext{5}{Dept. of Physics and Astronomy, U. Penn., Philadelphia PA} 
-\altaffiltext{6}{Dept. of Physics, Brown University, Providence RI}
-\altaffiltext{7}{Square Kilometer Array, S. Africa, Cape Town South Africa}
-\altaffiltext{8}{Dept. of Physics and Electronics, Rhodes University, South Africa}
-\altaffiltext{9}{INAF-Instituto di Radioastronomia, Bologna Italy}
-\altaffiltext{10}{Dept. of Electrical and Computer Engineering, U. Virginia, Charlottesville VA}
-\altaffiltext{11}{National Radio Astronomy Obs., Charlottesville VA}
-\altaffiltext{12}{Dept. of Astronomy, U. Virginia, Charlottesville VA}
-\altaffiltext{13}{National Radio Astronomy Obs., Socorro NM}
-\altaffiltext{14}{Cavendish Lab., Cambridge UK}
-
-%		Notes
-
-%Reference section with: \ref{sec:Intro}
-%Reference equation with: \eqref{eq:eqtest}
-%Reference figure with: \ref{fig:figtest}
-%Cite paper inside sentence: \citet{ref}
-%Cite paper at end of sentence: \citep{ref}
-%Cite paper inside a parenthetical sentence: \citealt{ref}
-
-%To compile with references shown, compile in BibTeX once and LaTeX twice
-
-%		Sample Equation Syntax
-%\begin{equation}
-%\label{eqtest}
-%\langle \widetilde{T} (\mathbf{k}) \widetilde{T}^* (\mathbf{k^\prime}) \rangle = (2 \pi)^3 \delta^D (\mathbf{k} - \mathbf{k}^\prime) P(k),
-%\end{equation}
-
-% ABSTRACT ---------------------------------------------------------------------------------
-
-\begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
-galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the 21\,cm line of neutral hydrogen.
-Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data.
-It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
-Specifically, with a statistical power spectrum detection in HERA's foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
-In this paper, we focus on signal loss associated with power spectrum estimation.
-We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
-Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
-We focus on a subset of PAPER-64 data in this paper; revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
-(\textit{in prep.}) and supersede results from previously published PAPER analyses.
-\end{abstract}
-
-% INTRO ---------------------------------------------------------------------------------
-
-\section{Introduction}
-\label{sec:Intro}
-
-{\let\thefootnote\relax\footnote{$^{\diamond}$\href{mailto:ccheng@berkeley.edu}{ccheng@berkeley.edu}}}
-{\let\thefootnote\relax\footnote{$^{\dagger}$Hubble Fellow}}
-{\let\thefootnote\relax\footnote{$^{*}$NSF AAPF Fellow}}
-\setcounter{footnote}{0}
-
-By about one billion years after the Big Bang ($z \sim 6$), the first stars and galaxies are thought to have ionized all the 
-neutral hydrogen that dominated the baryonic matter content in the Universe. This transition period, during which the first 
-luminous structures formed from gravitational collapse and began to emit intense radiation that ionized the cold neutral gas 
-into a plasma, is known as the Epoch of Reionization (EoR).
-The EoR is a relatively unexplored era in our Universe's history, which spans the birth of the first stars to the full reionization of the intergalactic medium (IGM).
-This epoch encodes important information regarding the nature of the first galaxies and the processes of structure formation.
-Direct measurements of the EoR would unlock powerful characteristics about the IGM, revealing connections 
-between the matter distribution exhibited via cosmic microwave background (CMB) studies and the highly structured 
-web of galaxies we observe today (for a review, see \citet{barkana_and_loeb2001}, \citet{furlanetto_et_al2006} and \citet{loeb_furlanetto_2013}).
-
-One promising technique to probe the EoR is to target the 21\,cm wavelength signal that is emitted and absorbed by neutral hydrogen via 
-its spin-flip transition (\citealt{furlanetto_et_al2006}; \citealt{barkana_and_loeb2008}; \citealt{morales_and_wyithe2010}; \citealt{pritchard_and_loeb2010}; \citealt{pritchard_loeb2012}).
-This technique is powerful because it can be observed both spatially and as a function of redshift --- that is, the wavelength
-of the signal reaching our telescopes can be directly mapped to a distance from where the emission originated before 
-stretching out as it traveled through expanding space. Hence, 21\,cm tomography offers a unique window into both the spatial and temporal
-evolution of ionization, temperature, and density fluctuations.
-
-In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
-the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
-mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
-Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
-Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
-(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
-\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
-Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
-the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
-\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
-Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
-learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
-detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).
-
-The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
-instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results.
-More specifically, it is imperative to develop techniques that ensure
-the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method.
-In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation.
-This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis.
-We first approach this topic from a broad perspective, and then perform a detailed
-case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al.
-(\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
-
-Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
-This paper accompanies the erratum of \citet{ali_et_al2018} and adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
-These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
-
-This paper is organized into three main sections.
-In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
-In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss.
-In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis.
-Finally, we conclude in Section \ref{sec:Con}.
-
-% SECTION 2 SIGLOSS TOY MODEL ---------------------------------------------------------------------------------
-%\color{blue}
-
-\section{Signal Loss Toy Models}
-\label{sec:SiglossOverview}
-% JEA - We never totally nail down what ``signal loss'' is ...
-
-Signal loss refers to attenuation of the target cosmological signal 
-in a power spectrum estimate.
-Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits.
-Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
-
-One type of signal loss can occur when weighting data by itself.
-Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others.
-For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
-Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
-However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
-In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
-This loss was significantly 
-%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.
-
-% JEA - Put all of the (O)QE / ICW theory here, rather than sprinkled throughout this section.
-
-\subsection{The Quadratic Estimator Method}
-\label{sec:QE}
-
-%AAAICW
-
-We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation.
-The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
-Prior to power spectrum estimation, the data will often have been prepared to have minimal foregrounds by some method of subtraction, so this foreground emission may appear either directly (because it was not subtracted) or as a residual of some subtraction process not in the power spectrum domain.
-If an accurate estimate of the total covariance of the data is known, including both the desired signal and any contaminants, then the ``optimal quadratic estimator'' formalism provides a method of producing a minimum variance, unbiased estimator of the desired signal, as shown in
-% JEA - I cut this b/c I wanted to step back and explain a bit more clearly what we were actually hoping for 
-%Driven by the need to mitigate foreground bias, PAPER's previous analyses use a weighting method that aims to down-weight foregrounds.
-This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in
-\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
-%Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
-
-% JEA - The discussion of dimensions here is confusing ...
-"a baseline" is mentioned, but it's not clear if the redundant baseline averaging has already happened or what.
-I believe we are only considering covariance between frequencies, but this isn't explicitly said, and the matrix equations don't make sense unless all the dimensions are N_f N_t.
-%We begin with our 
-Suppose that the measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
-% JEA - not sure this helps
-%, but in practice we manipulate it as an array with dimensions ($N_{f}, N_{t}$), 
-where $N_{t}$ is the number of time integrations and $N_{f}$ is the number of frequency channels. The covariance of the data is given by 
-\begin{equation}
-\textbf{C} \equiv \langle\textbf{xx}^{\dagger}\rangle = \textbf{S} + \textbf{U}
-\end{equation}
-where the average over an ensemble of data realizations produces the true covariance, and we further assume it may be written as the sum of the desired cosmological signal $\textbf{S}$ and other terms $\textbf{U}$.
-
-We are interested in estimating the three-dimensional power spectrum of the EoR.  
-Visibilities are measurements of the Fourier transform of the sky along two spatial dimensions (using the flat-sky approximation), and since we are interested in three-dimensional Fourier modes we only need to take one Fourier transform of our visibilities along the line-of-sight dimension.
-We consider band powers $P^\alpha$ of the power spectrum of $\textbf{x}$ over some range in cosmological $\mathbf{k}$, where $\alpha$ indexes a waveband in $k_{\parallel}$ (a cosmological wavenumber $k_{\parallel}$ is the Fourier dual to frequency under the delay approximation (\citealt{parsons_et_al2012b}), which is a good approximation for the short baselines that PAPER analyzes).
-The fundamental dependence of the covariance on the power spectrum band powers $P^\alpha$ is encoded as
-% JEA - Should distinguish slightly more clearly between Q and dC/dp_alpha
-\begin{equation}
-\textbf{S} = \sum_\alpha P^\alpha \frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \sum_\alpha P^\alpha \textbf{Q}^\alpha
-%\textbf{S} = p_{\alpha} \frac{\partial\textbf{C}}{\partial p_{\alpha}}
-%\frac{\partial\textbf{C}}{\partial p_{\alpha}} \equiv \textbf{Q}^{\alpha}
-\end{equation}
-where we define $\frac{\partial\textbf{C}}{\partial P^\alpha} \equiv \textbf{Q}^{\alpha}$.
-In other words, $\textbf{Q}$ describes the response of the covariance to a change in the power spectrum, relating a quadratic statistic of the data (the covariance) to a quadratic statistic in Fourier-space (the power spectrum).
-% JEA - ah, the dimensions again
-% which has dimensions ($N_{f}$,$N_{f}$).
-
-The optimal quadratic estimator prescription is then to compute
-\begin{equation}
-\label{eq:OQE}
-\widehat{P}^{\alpha}  = \sum_\beta ({\F^{-1}})^{\alpha\beta} (\widehat{q}^{\beta} - \widehat{b}^{\beta} )
-\end{equation}
-where $\F$ is the Fisher matrix (which determines errors on the power spectrum estimate)
-\begin{equation}
-F^{\alpha \beta} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \textbf{Q}^{\alpha} \C^{-1} \textbf{Q}^{\beta} \right),
-\end{equation}
-$\widehat{q}$ is the un-normalized power spectrum estimate
-\begin{equation}
-\label{eq:OQEQuadratic}
-\widehat{q}^\alpha =  \half \textbf{x}^\dagger \invC \textbf{Q}^{\alpha}  \invC \textbf{x},
-\end{equation}
-and $\widehat{b}$ is the additive bias
-\begin{equation}
-\label{eq:OQELinear}
-\widehat{b}^{\alpha} = \half \Tr\left( \mathbf{U} \invC \textbf{Q}^{\alpha} \invC \right).
-\end{equation}
-The power spectrum estimator in Equation \eqref{eq:OQE} is the minimum variance (smallest error bar) estimate of the power spectrum subject to the constraint that it is also unbiased; that is, the ensemble average of the estimator is equal to its true value
-\begin{equation}
-\label{eq:super_unbiased}
-\langle \widehat{P}^{\alpha} \rangle = P^\alpha
-\end{equation}
-\citep{tegmark_et_al1997a,bond_et_al1998}.
-
-Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminants in order to obtain an unbiased estimate of the power spectrum.
-By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
-However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
-
-More specifically, the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
-Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-If the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
-Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
-Moreover, because the linear bias is always positive and there is no multiplicative bias, the quadratic-only term will always produce an estimate which is {\it high} relative to the true value, and which can conservatively be interpreted as an upper limit.
-These considerations, and the difficulty of obtaining an estimate for $\mathbf{U}$, motivate the neglect of the linear bias in the rest of this analysis.
-
-%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
-Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator
-%which may still produce an unbiased estimate, 
-where Equation \eqref{eq:OQEQuadratic} is replaced by
-\begin{equation}
-\label{eq:qhat}
-\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
-\end{equation}
-where $\textbf{R}$ is a weighting matrix chosen by the data analyst.
-For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
-%with dimensions ($N_{f}$,$N_{f}$) --- as
-
-%%% COME BACK HERE
-% Need to still explain the motivation for this
-With an appropriate normalization matrix $\textbf{M}$, the quantity
-%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
-\begin{equation}
-\label{eq:phat}
-\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
-\end{equation}
-is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.
-
-To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
-\begin{eqnarray}
-\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
-&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
-\end{eqnarray}
-where $W^{\alpha \beta}$ are elements of a window function matrix.
-Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
-However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
-In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized.
-Beyond this, the data analyst has a choice for $
-\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal.
-In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
-If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
-% JEA - is one really free to choose M and R independently?
-
-% JEA - I don't think it's attractive at all
-%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
-Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
-Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}.
-In previous PAPER analyses, one time-averages the data to obtain:
-\begin{equation}
-\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
-\end{equation}
-assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
-amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
-\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.
-
-In the next three sections, we use toy models to investigate the effects of weighting matrices on signal loss by experimenting with different matrices $\textbf{R}$ and examining their impact on the resulting power spectrum estimates $\widehat{\textbf{P}}$.
-Our goal in experimenting with weighting is to suppress foregrounds and investigate EoR losses associated with it.
-We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:CaseStudy}.
-
-%\item While the correct covariance will remove this contamination, there is no particular harm in having these modes be strongly correlated with the data, since we desire their projection in any case.
-
-As a brief preview, we summarize our findings in the following sections here:
-
-\begin{itemize}
-
-\item If the covariance matrix is estimated from the data, a strong correlation between the estimated modes and the data will in general produce an estimate of the signal power spectrum which is strongly biased {\it low} relative to the true value.
-In this context, this is what we call ``signal loss''  (Section \ref{sec:toymodel}).
-
-\item The effect of the bias is worsened when the number of independent samples used to estimate the covariance matrix is reduced (Section \ref{sec:toymodel_frf}).
-
-\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum.
-In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).
-
-%\item The convergence of the modes of the empirical covariance matrix to the true matrix depends on the size of the eigenvalues, with the modes with the largest eigenvalues converging more quickly (in norm) to the true eigenvector than those with smaller eigenvalues.
-Thus, in estimating the covariance matrix empirically, larger eigenvalue modes are likely to be more reliable (Section \ref{sec:toymodel_frf}).
-
-\item Knowing these things, there are some simple ways of altering the empirical covariance matrix to decouple it from the data and produce unbiased power spectrum estimates (Section \ref{sec:otherweight}).
-
-% JEA - I really struggle with whether this is intuitively obvious ...
-it's hard to get a sense of what "noise" is averaging down slower.
-All modes have the same number of samples going into the estimate.
-Should I think of the size of he eigenvalue is an estimate of its "signal/noise" in the given data realization?
-% Also, have we shown this sufficiently rigorously?
-Is the toy model sufficiently general?
-(Probably.)  But, for any dataset you kind of have to make a decision about where you think "reliable" is, i.e., where in eigenvalue would you make a cut?
-Is Figure 20 basically trying to argue for the real data that this is ~a few modes?
-
-\end{itemize}
-
-\subsection{Empirical Inverse Covariance Weighting}
-\label{sec:toymodel}
-
-% JEA  - This material was moved up
-%One choice for the weighting matrix $\textbf{R}$ used in power spectrum analysis is an inverse covariance matrix.
-This type of weighting is attractive for power spectrum analyses because it yields the smallest possible error bars on a measurement.
-Said differently, it gives the minimum variance estimate of the power spectrum (\citealt{tegmark_et_al1997a}; \citealt{bond_et_al1998}).
-In \citet{liu_tegmark2011}, it was shown that inverse covariance weighting also serves as a way to down-weight some portion of foregrounds (namely, those which do not share the same covariance structure as the cosmological signal), motivating our use of the weighting for previous PAPER analyses.
-%
-%One important feature of weighting data by its true inverse covariance is that, while it can suppress some foregrounds, it cannot suppress the EoR signal (nor foreground modes that masquerade as signal-like modes).
-By construction, inverse covariance weighting in the quadratic estimator does not lead to signal loss.
-Therefore, in an ideal world with perfect foreground,
-%instrumental, and EoR models, we could form $\textbf{C}$ in a way that accurately describes our measured data and use inverse covariance weighting to produce minimum variance power spectrum estimates without destroying the signal.
-In other words, the optimal quadratic estimator is by construction an unbiased estimator of the power spectrum.
-
-%In practice, we do not have perfect models for $\textbf{C}$, and it is the use of an estimated covariance $\widehat{\textbf{C}}$ instead of the true covariance $\textbf{C}$ that can lead to loss. 
-Using a toy model, we will now build intuition into how weighting by the inverse of the empirically estimated covariance, $\widehat{\textbf{C}}^{-1}$, can give rise to signal loss.
-We construct a simple dataset that contains visibility data with $100$ time integrations and $20$ frequency channels.
-This model represents realistic dimensions of about an hour of PAPER data which might be used for a power spectrum analysis.
-For PAPER-64 (both the \citetalias{ali_et_al2015} analysis and our new analysis) we use $\sim8$ hours of data (with channel widths of $0.5$ MHz and integration times of $43$ seconds), but here we scale it down with no loss of generality.
-
-We create mock visibilities, $\textbf{x}$, and assume a non-tracking, drift-scan observation.
-Hence, flat spectrum sources (away from zenith) lead to measured visibilities which oscillate in time and frequency.
-We therefore form a mock visibility measurement of a bright foreground signal, $\textbf{x}_{\rm FG}$, as a complex sinusoid that varies smoothly in time and frequency, a simplistic but realistic representation of a single bright source.
-We also create a mock visibility measurement of an EoR signal $\textbf{x}_{\rm EoR}$ as a complex, Gaussian random signal.
-A more realistic EoR signal would have a sloped power spectrum in $p(k)$ (instead of flat, as in the case of white noise), which could be simulated by introducing frequency correlations into the mock EoR signal.
-However, here we treat all $k$'s separately, so a simplistic white noise approximation can be used.
-Our combined data vector is then $\textbf{x} =
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$, to which we apply different weighting schemes throughout Section \ref{sec:SiglossOverview}. The three data components are shown in Figure 
-\ref{fig:toy_sigloss1}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss1.pdf}
-	\caption{Our toy model dataset to which we apply different weighting schemes to in order to investigate signal loss.
-We model a mock foreground-only visibility with a sinusoid signal that varies smoothly in
-time and frequency. We model a mock visibility of an EoR signal as a random Gaussian signal. We add the two together to form $\textbf{x} = 
-\textbf{x}_{\rm FG} + \textbf{x}_{\rm EoR}$. Real parts are shown here.}
-	\label{fig:toy_sigloss1}
-\end{figure}
-
-%First, 
-We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \eqref{eq:qhat} and \eqref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
-Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
-The foreground sinusoid is clearly visible in $\widehat{\textbf{C}}_{\rm FG}$.
-The power spectrum result is shown in green in the left plot of Figure \ref{fig:toy_sigloss3}.
-Also plotted in the figure are the uniform-weighted ($\textbf{R} \equiv \textbf{I}$) power spectrum of the individual components $\textbf{x}_{\rm FG}$ (blue) and $\textbf{x}_{\rm EoR}$ (red).
-As shown, our $\widehat{\textbf{C}}^{-1}$ weighted result successfully suppresses foregrounds,
-%For our toy model, the successful suppression of the foreground mode is 
-demonstrated in Figure \ref{fig:toy_sigloss3} by the missing foreground peak in the weighted power spectrum estimate (green).
-It is also evident that our result fails to recover the EoR signal --- it exhibits the correct shape, but the amplitude level is slightly low.
-It is this behavior which we describe as signal loss.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss12.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss13.pdf}
-	\caption{The estimated covariance matrices (top row) and inverse covariance-weighted data (bottom row) for FG only (left), EoR only 
-(middle), and FG + EoR (right). Real parts are shown here.}
-	\label{fig:toy_sigloss12}
-\end{figure}
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss3.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.33\textwidth]{plots/toy_sigloss4.pdf}
-	\caption{Resulting power spectrum estimates for the toy model simulation described in Section \ref{sec:toymodel} --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-The power spectrum of the foregrounds peaks at a $k$-mode based on the frequency of the sinusoid used to create the mock FG signal.
-In the two panels, we compare using empirically estimated inverse covariance weighting where $\textbf{C}$ is derived from the data (left), and projecting out the zeroth eigenmode only (right).
-In the former case, signal loss arises from the coupling of the eigenmodes of $\widehat{\textbf{C}}$ to the data.
-% JEA - redundant
-%For an empirically estimated $\widehat{\textbf{C}}$, 
-%its eigenvalues differ from those of the true covariance, where 
-%the coupling between EoR-dominated eigenmodes and the data can lead to loss.
-%Hence, 
-There is negligible signal loss when all eigenmodes besides the foreground one are no longer correlated with the data.
-%assigning identical weights to all eigenmodes except the first, 
-%constructing a covariance proportional to the identity and the outer product of the sinusoid eigenmode, since we are only down-weighting the FG-dominated mode in this case.
-}
-	\label{fig:toy_sigloss3}
-\end{figure*}
-
-As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain %the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in
-a nearly unbiased estimate of the power spectrum.
-The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
-
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection; whether or not it is strongly correlated with the the actual data vector is irrelevant.
-However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
-If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As described in Section \ref{sec:siglossmethod}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
-
-%For a toy model mathematical derivation of signal loss arising from a data-estimated covariance matrix, see Appendix \ref{sec:sigloss_appendix}.
-Here we will describe the origin of this signal loss intuitively.
-
-%% JEA - I don't think the eigenspectrum really helps, but at some point we probably want to show it ...
-%To begin to understand the lossy behavior of this result, we can closely study our estimated covariance eigenspectrum, shown in Figure \ref{fig:toy_sigloss2}.
-Since it is estimated from our data, its eigenspectrum differs from the eigenspectrum of the true covariance $\textbf{C}$, and this difference has important consequences on our result.
-%
-%An eigenspectrum ranks the eigenvalues of a matrix from highest to lowest and can be thought of as a spectrum of weights that are given to each spectral mode in the data.
-In other words, the eigenvalues encode the strength of different shapes in the dataset.
-The eigenspectrum of the identity matrix $\textbf{I}$ is flat (all $1$'s) because it gives equal weighting to all modes.
-In our application, covariance matrices tend to have sloped eigenspectra, meaning that modes are given different weights in QE power spectrum estimation.
-%% JEA - I think this is actually NOT true - see the toy model as an example.
-The size of the eigenvalues isn't what determines that the undesired mode is downweighted and the others left alone.
-I haven't computed the eigenvalues explicitly, but down-weighting of m occurs regardless of the relative size of s and u.
-%The modes with the highest eigenvalues are down-weighted the most.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss2.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ (blue), $\widehat{\textbf{C}}_{\rm EoR}$ (red), and $\widehat{\textbf{C}}_{\rm FG+EoR}$ 
-%(green).
-The eigenspectrum of $\widehat{\textbf{C}}_{\rm FG}$ peaks at the zeroth eigenmode, due to the presence of only one sinusoid.
-These empirically estimated covariance matrices have eigenspectra that are different from that of the true $\textbf{C}$.
-Specifically, these eigenmodes have the risk of being down-weighted more significantly than they should be because they are coupled to the data in a way that produces loss.}
-%	\label{fig:toy_sigloss2}
-%\end{figure}
-
-%We show the {\it eigenspectrum} (the eigenvalues of the matrix in descending order) of this toy model in Figure \ref{fig:toy_sigloss2}.  In this case,
-%For example, 
-%the largest-valued eigenmode of $\widehat{\textbf{C}}$ (highest eigenvalue) describes the sinusoid foreground mode in the toy model (the peak in Figure \ref{fig:toy_sigloss3}). 
-%
-
-%In general, the highest-valued eigenmodes of $\widehat{\textbf{C}}$ typically (but not always) describe bright foregrounds --- the most prominent shapes in a dataset.
-For these FG-dominated modes, where foregrounds outshine the EoR signal, down-weighting is beneficial.
-In some sense, we desire signal loss in this regime, if by `signal' we mean `foregrounds.' In this case it is beneficial for these eigenmodes to be coupled to the data in a way that produces loss.
-
-%If the true covariance matrix $\textbf{C}$ of our data was known, then every single eigenvalue and eigenvector of $\textbf{C}$ would be 
-%representative of real fluctuations in the data. However, when using an estimated $\widehat{\textbf{C}}$ that is derived from one 
-%particular data realization, its eigenvalues and eigenvectors may differ from the truth.
-Said differently, shapes that may not exist (or exist rarely) in a true covariance may appear stronger in the estimated covariance.
-Hence, they will be down-weighted
-%more than they should be.
-
-The danger of an empirically estimated covariance matrix comes mostly from not being able to describe the EoR-dominated eigenmodes of $\textbf{C}$ accurately, for which the EoR signal is brighter than foregrounds.
-In such a case, the coupling between these modes to the data realization leads to the overfitting and subtraction of the EoR signal.
-More specifically, the coupling between the estimated covariance and the data is anti-correlated in nature (which is explained in more detail in Section \ref{sec:siglossmethod}), which leads to loss.
-Mis-estimating $\textbf{C}$ for EoR-dominated eigenmodes is therefore more harmful than for FG-dominated modes, and since the lowest-valued eigenmodes of an eigenspectrum are typically EoR-dominated, using this part of the spectrum for weighting is most dangerous.
-
-Armed with this information,
-%Using what we've learned about the eigenspectrum, 
-we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
-% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
-%is a sinusoid, so it 
-can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
-project out the zeroth eigenmode and 
-%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
-then take the remaining covariance to be the identity matrix.  
-This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
-In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
-% down-weight them 
-foregrounds with negligible signal loss.
-
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization.
-There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
-\ref{sec:otherweight}.
-
-\subsection{Fringe-Rate Filtering}
-\label{sec:toymodel_frf}
-
-We have shown how signal loss can arise due to the coupling of EoR-dominated eigenmodes to the data.
-We will next show how this effect is exacerbated by reducing the total number of independent samples in a dataset.
-
-A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.
-
-Because fringe-rate filtering is analogous to averaging in time, it comes at the cost of reducing the total number of independent samples in the data.
-With fewer independent modes, it becomes more difficult for the empirical covariance to estimate the true covariance matrix of the fringe-rate filtered data.
-We can quantify this effect by evaluating a convergence metric $\varepsilon(\Chat)$ for the empirical covariance, which we define as
-
-% JEA - Death to eigenspectra!
-%The resulting eigenspectrum as compared to the green curve (FG + EoR) in Figure \ref{fig:toy_sigloss2} is shown in Figure \ref{fig:toy_sigloss15}.
-
-\begin{equation}
-\label{eq:converge}
-\varepsilon (\Chat) \equiv \sqrt{\frac{\sum_{ij} (\widehat{C}_{ij} - {C}_{ij})^2}{\sum_{ij} {C}_{ij}^2}},
-\end{equation}
-where $\C$ is the true covariance matrix.
-To compute this metric, we draw different numbers of realizations (different draws of Gaussian noise) of our toy model EoR measurement, $\textbf{x}_{\rm EoR}$, and take their ensemble average.
-We then compare this to the ``true" covariance, which in our simulation is set to be the empirical covariance after a large number ($500$) of realizations.
-As shown in Figure \ref{fig:toy_sigloss16}, we perform this computation for a range of total independent ensemble realizations (horizontal axis) and number of independent samples in the data following time-averaging, or ``fringe-rate filtering" (different colors).
-With more independent time samples (i.e., more realizations) in the data, one converges to the true fringe-rate filtered covariance more quickly.
-
-The situation here with using a finite number of time samples to estimate our covariance is analogous to a problem faced in galaxy surveys, where the non-linear covariance 
-of the matter power spectrum is estimated using a large --- but finite --- number of expensive simulations. There, the limited 
-number of independent simulations results in inaccuracies in estimated covariance matrices 
-\citep{dodelson_schneider2013,taylor_joachimi_etal2014}, which in turn result in biases in the final parameter constraints 
-\citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
-\emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
-galaxy survey literature for estimating accurate covariance matrices can be successfully adapted for $21\,\textrm{cm}$ 
-cosmology. These techniques include the imposition of sparsity priors \citep{padmanabhan_et_al2016}, the fitting of 
-theoretically motivated parametric forms \citep{pearson_samushia2016}, covariance tapering \citep{paz_sanchez2015}, 
-marginalization over the true covariance \citep{sellentin_heavens2016}, and shrinkage methods 
-\citep{pope_szapudi2008,joachimi_2017}.
-
-%Just as important as the eigenvalues are the eigenvectors of our empirical covariances. 
-The overall convergence of the covariance is important, but also noteworthy is the fact that different eigenvectors converge to their true forms at different rates.
-This is illustrated by Figure \ref{fig:toy_sigloss17}, which shows the convergence of eigenvectors in an empirical estimate of a covariance matrix.
-For this particular toy model, we construct a covariance whose true form combines the same mock foreground from the previous toy models with an EoR component that is modeled as a diagonal matrix with eigenvalues spanning one order of magnitude (more specifically, we construct the EoR covariance as a diagonal matrix in the Fourier domain, where the signal is expected to be uncorrelated; its Fourier transform is then the true covariance of the EoR in the frequency domain, or $\textbf{C}_{\rm EoR}$).
-For different numbers of realizations, we draw random EoR signals that are consistent with $\textbf{C}_{\rm EoR}$, add them to the mock foreground data, and compute the combined empirical covariance by averaging over the realizations.
-The eigenvectors of this empirical covariance are then compared to the true eigenvectors $\widehat{\textbf{v}}$, where we use as a convergence metric $\varepsilon(\widehat{\textbf{v}})$, defined as:
-\begin{equation}
-\label{eq:converge_eig}
-\varepsilon (\widehat{\textbf{v}}) \equiv \sqrt{\sum_{i}^{N_{f}}|\textbf{v}-\widehat{\textbf{v}}|_{i}^2},
-\end{equation}
-where $N_{f}$ is the number of frequencies ($20$) in the mock data.
-The eigenmode convergence curves in Figure \ref{fig:toy_sigloss17} are ranked ordered by eigenvalue, such that ``Eigenmode \#0" illustrates the convergence of the eigenvector with the largest eigenvalue, ``Eigenmode \#1" for the second largest eigenvalue, and so on.
-We see that the zeroth eigenmode --- the mode describing the foreground signal --- is quickest to converge.
-
-Our numerical test reveals that the convergence rates of empirical eigenvectors is related to the sample variance in our empirical estimate.
-In general, computing an empirical covariance from a finite ensemble average means that the empirical eigenmodes have sample variances.
-Consider first a limiting case where all eigenvalues are equal.
-In such a scenario, any linear combination of eigenvectors is also an eigenvector, and thus there is no sensible way to define the convergence of eigenvectors.
-In our current test, aside from the zeroth mode, the eigenvalues have similar values but are not precisely equal.
-Hence, there is a well-defined set of eigenvectors to converge to.
-However, due to the sample variance of our empirical covariance estimate, there may be accidental degeneracies between modes, where some modes are mixing and swapping with others.
-Therefore, the steeper an eigenspectrum, the easier it is for the eigenmodes to decouple from each other and approach their true forms.
-A particularly drastic example of this can be seen in the behavior of mode $0$ (the foreground mode), whose eigenvalue differs enough from the others that it is able to converge reasonably quickly despite substantial sample variance in our empirical covariance estimate.
-To break degeneracies in the remaining modes, however, requires many more realizations.
-
-While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
-The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss.
-However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
-
-In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
-Even for the case of real PAPER data (Section \ref{sec:CaseStudy}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
-However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
-
-%One sees that the highest-valued eigenmodes converge to their true eigenvectors more quickly.
-With only a small number of realizations, these empirically estimated modes already retain little correlation with the specific realizations of data that were used to form the empirical covariance.
-As we will see in the next section, using only these eigenmodes, which are less coupled to data realizations, minimizes signal loss.
-In contrast, the lower-valued eigenmodes retain more memory of the data realizations, which leads to correlations that induce signal loss.
-% JEA - this is redundant
-%Said differently, a steep covariance eigenspectrum can be especially dangerous because the eigenmodes that converge the slowest are typically also EoR-dominated and are therefore susceptible to the most loss.
-%\acl{Think about whether we need to do the Fourier space version as well.}
-
-% JEA - death to eigenspectra!
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.31\textwidth]{plots/toy_sigloss15.pdf}
-%	\caption{Eigenspectrum of $\widehat{\textbf{C}}_{\rm FG+EoR}$, in the case of no fringe-rate filtering (solid green) and with fringe-rate filtering (dashed green).
-The dashed, steep eigenspectrum has a greater risk of signal loss because its lowest-valued eigenmodes are both more strongly coupled to the data (than those of the solid eigenspectrum) and, in this example, are also EoR-dominated.}
-%	\label{fig:toy_sigloss15}
-%\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss16.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples (100 of them).
-Subsequent colors show time-averaged signals.
-As the number of realizations increases, we see that the empirical covariances approach the true covariances.
-With more independent samples, the quicker an empirical covariance converges (i.e., the quicker it decouples from the data), and the less signal loss we would expect to result.}
-	\label{fig:toy_sigloss16}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss17.pdf}
-	\caption{The convergence level, as defined by Equation \eqref{eq:converge_eig}, of empirically estimated eigenvectors for different numbers of mock data realizations.
-The colors span from the 0th eigenmode (has the highest eigenvalue) to the 19th eigenmode (has the lowest eigenvalue), where they are ordered by eigenvalue in descending order.
-This figure shows that the zeroth eigenmode converges the quickest, implying that eigenvectors with eigenvalues that are substantially different than the rest (the FG-dominated mode has a much higher eigenvalue than the EoR modes) are able to converge to the true eigenvectors the quickest.
-On the other hand, eigenmodes $1$-$19$ have similar eigenvalues and are slower to converge because of degeneracies between them.}
-	\label{fig:toy_sigloss17}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/toy_sigloss5.pdf}
-	\caption{Our ``fringe-rate filtered" (time-averaged) toy model dataset. We average every four samples together, 
-yielding $25$ independent samples in time. Real parts are shown here.}
-	\label{fig:toy_sigloss5}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss7.pdf}
-	\caption{Resulting power spectrum estimate for the ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
-EoR only (red), and the weighted FG + EoR dataset (green). We use empirically estimated inverse covariance weighting where $\textbf{C}$ is 
-computed from the data.
-There is a larger amount of signal loss than for the non-averaged data, a consequence of weighting by eigenmodes that are more strongly coupled to the data due to there being fewer independent modes in the data.}
-	\label{fig:toy_sigloss7}
-\end{figure}
-
-With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal.
-We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank.
-We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
-%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}
-
-The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
-expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance.
-In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter.
-This is evident by noticing that the
-green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
-%It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
-This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
-
-Using our toy model, we have seen that a sensitivity-driven analysis technique like fringe-rate filtering has trade-offs of signal 
-loss and noisier estimates when using data-estimated covariance matrices. Longer integrations increase sensitivity but reduce 
-the number of independent samples, resulting in 
-eigenmodes correlated with the data
-% JEA - it's not that they are wrong, but that they are correlated
-%poorly characterized, steep eigenspectra 
-that can overfit signal greatly. We 
-note that a fringe-rate filter does have a range of benefits, many described in \citet{parsons_et_al2016}, so it can still be 
-advantageous to use one despite the trade-offs.
-
-\subsection{Other Weighting Options}
-\label{sec:otherweight}
-
-In Section \ref{sec:toymodel} we showed one example of how altering $\widehat{\textbf{C}}$ can 
-make the difference between nearly zero and some signal loss. We will now use our toy model to describe several other ways to tailor $\widehat{\textbf{C}}$ 
-in order to minimize signal loss. We choose four independent regularization methods to highlight in this section, which have 
-been chosen due to their simplicity in implementation and straightforward interpretations. We illustrate the resulting power 
-spectra for the different cases in Figure \ref{fig:toy_sigloss8}.
-% and \ref{fig:toy_sigloss14}. 
-These examples are not meant to be taken as suggested analysis methods but rather as illustrative cases.
-
-As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
-avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
-variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
-_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
-\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
-left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
-%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
-In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.
-
-\begin{figure*}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss10.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss8.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss9.pdf}
-	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each minimize signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\widehat{\textbf{C}}$ (lower right).
-The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
-	\label{fig:toy_sigloss8}
-\end{figure*}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,width=\columnwidth]{plots/toy_sigloss14.pdf}
-%	\caption{We compare the eigenspectrum of an empirically calculated $\widehat{\textbf{C}}$ (green) to that of four alternate 
-%weighting options, including modeling the covariance matrix of EoR (red), regularizing $\widehat{\textbf{C}}$ by adding an identity 
-%matrix to it (blue), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (yellow), and multiplying an identity matrix with $
-%\widehat{\textbf{C}}$ (magenta). All eigenspectra (except the green) are relatively flat and don't exhibit signal loss. All were 
-%computed for the `fringe-rate filtered' (time-averaged) toy model case presented in Section \ref{sec:toymodel_frf}.}
-%	\label{fig:toy_sigloss14}
-%\end{figure}
-%
-The second panel (top right) in Figure \ref{fig:toy_sigloss8} uses a regularization method of setting $\widehat{\textbf{C}}_{\rm reg} \equiv 
-\widehat{\textbf{C}} + \gamma\textbf{I}$, where $\gamma = 5$ (an arbitrary strength 
-of $\textbf{I}$ for the purpose of this toy model). By adding the identity matrix, element-wise, we are weighting the diagonal 
-elements of the estimated covariance matrix more heavily than those off-diagonal.
-Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data and there is no loss.
-%Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
-
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss by only using the first three eigenmodes of the estimated covariance.
-Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this
-method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights).
-Again, avoiding the overfitting of EoR-dominated modes which are coupled to the data results in negligible signal loss.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are foreground or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
-We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
-
-The last regularization scheme we are highlighting here is setting $\widehat{\textbf{C}}_{\rm reg} \equiv \widehat{\textbf{C}} \circ \textbf{I}$ (element-wise multiplication), or inverse variance weighting (i.e., keeping only the diagonal elements of $\widehat{\textbf{C}}$).
-In the bottom right
-panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
-To understand this, we recall that our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by
-the identity matrix, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
-suppressing the foreground.
-But because we decoupled the whole eigenspectrum from the data, we also avoid signal loss.
-Although this method did not successfully recover the EoR signal for this particular simulation, it is important that we show that there
-are many options for estimating a covariance matrix, and some may down-weight certain eigenmodes more effectively than others based on the spectral nature 
-of the components in a dataset. 
-%One may imagine a situation where a particular systematic is contained to an isolated 
-%frequency (such as radio frequency interference or crosstalk). In such a case, preserving only the diagonal elements of $
-%\widehat{\textbf{C}}$ would be an effective way of removing this contamination.
-
-In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are coupled to data and not converged to their true forms.
-We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
-
-% SECTION 3 CASE STUDY ---------------------------------------------------------------------------------
-
-\section{Signal Loss in PAPER-64}
-\label{sec:CaseStudy}
-
-We now turn to a detailed signal loss investigation using a subset of the PAPER-64 dataset from \citetalias{ali_et_al2015}.
-In the previous section we showed how signal loss arises when weighting data with empirically estimated covariances; in this section we highlight how the amount of this loss was underestimated in the previous analysis.
-Additionally, we illustrate how we have revised our analysis pipeline in light of our growing understandings.
-
-As a brief review, PAPER is a dedicated 21\,cm experiment located in the Karoo Desert in South Africa. The PAPER-64 
-configuration consists of 64 dual-polarization drift-scan elements that are arranged in a grid layout. For our case study, we 
-focus solely on Stokes I estimated data \citep{moore_et_al2013} from PAPER's $30$ m East/West baselines (Figure 
-\ref{fig:ant_layout}).
-All data is compressed, calibrated (using self-calibration and redundant calibration), delay-filtered (to remove foregrounds inside the wedge), LST-binned, and fringe-rate filtered.
-For detailed information about the backend system of PAPER-64, its observations, and data reduction pipeline, we
-refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015}.
-We note that all data processing steps are identical to those in \citetalias{ali_et_al2015} until after the LST-binning step in Figure 3 of \citetalias{ali_et_al2015}.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
-	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
-paper (i.e., a subset of the shortest horizontal spacings).}
-	\label{fig:ant_layout}
-\end{figure}
-
-The previously best published 21\,cm upper limit result from \citetalias{ali_et_al2015} placed a $2\sigma$ upper limit 
-on $\Delta^{2}(k)$, defined as
-
-\begin{equation}
-\Delta^{\textbf{2}}(k) = \frac{k^{3}}{2\pi^{2}}\,\hat{P}(k),
-\end{equation}
-
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$. The need to revise this limit stems mostly from previously underestimated signal loss, which we 
-address in this section.
-
-For the analysis in this paper, we use $8.1$ hours of LST, namely an RA range of $0.5$-$8.6$ hours (\citetalias{ali_et_al2015} uses a slightly longer RA 
-range of $0$-$8.6$ hours; we found that some early LSTs were more severely foreground contaminated).
-We also use only $10$ baselines, a subset of the $51$ total East/West baselines used in \citetalias{ali_et_al2015}, in order to illustrate our revised methods.
-All power spectrum results are produced for a center frequency of 151\,MHz using a width of 10\,MHz ($20$ channels), identical to the analysis in \citetalias{ali_et_al2015}.
-In the case study in this paper, we only use one baseline type instead of the three as in
-\citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues that will be made clear later on).
-
-The most significant changes from \citetalias{ali_et_al2015} occur in our revised power spectrum analysis, which is explained in the rest of this paper, but we also note that the applied fringe-rate filter is also slightly different.
-In \citetalias{ali_et_al2015}, the
-applied filter was not equivalent to the optimal fringe-rate filter (which is designed to maximize power spectrum sensitivity).
-Instead, the optimal filter was degraded slightly by widening it in fringe-rate space.
-This was chosen in order to increase the number of independent
-modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still underestimated. With the development of a new, 
-robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
-computed for a fiducial 30\,m baseline at 150\,MHz, the center frequency in our band. The filter in both the fringe-rate 
-domain and time domain is shown in Figure \ref{fig:frp}.
-
-Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
-As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
-Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/frp.pdf}
-	\caption{Top: the normalized optimal power-spectrum sensitivity weighting in fringe-rate space for our fiducial baseline and 
-Stokes I polarization beam. Bottom: the time domain convolution kernel corresponding to the top panel. Real and imaginary 
-components are illustrated in cyan and magenta, respectively, with the absolute amplitude in black. The fringe-rate filter acts as 
-an integration in time, increasing sensitivity but reducing the number of independent samples in the dataset.}
-	\label{fig:frp}
-\end{figure}
-
-We present our PAPER-64 signal loss investigation in three parts.
-We first give an overview of our signal injection framework which is used to estimate loss.
-In this framework (and as in \citetalias{ali_et_al2015}), we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
-As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
-Next, we describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
-Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}.
-
-% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
-
-\subsection{Signal Loss Methodology} 
-\label{sec:siglossmethod}
-In short, our method for estimating signal loss consists of adding an EoR-like signal into visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
-To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
-Here we use the same method as in \citetalias{ali_et_al2015}, where mock Gaussian noise visibilities (mock EoR signals)
-are filtered in time using an optimal fringe-rate filter to retain only ``sky-like" modes.
-Since the optimal filter has a shape that matches the rate of the sidereal motion of the sky, this transforms the Gaussian noise into a measurement that PAPER could make.
-This signal is then added to the visibility data.\footnote{One
-specific change from \citetalias{ali_et_al2015} is that we add this simulated signal - which has been fringe-rate filtered once already in order to transform it into a ``sky-like" signal - into the analysis pipeline before a fringe-rate filter is
-applied to the data (i.e., prior to the analysis step of fringe-rate filtering). Previously, the addition was done after the fringe-rate filter analysis step.  This change results in an increased 
-estimate of signal loss, %(by a factor of $\sim$$10$), 
-likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was underestimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
-
-Mathematically, suppose that $\textbf{e}$ is the mock injected EoR signal (at some amplitude level).
-We do not know the true EoR signal contained within our visibility data, $\textbf{x}$, so $\textbf{e}$ takes on the role of the true EoR signal (for which we measure its loss).
-Furthermore, one can make the assumption that the true EoR signal is small within our measured data, so the data vector $\textbf{x}$ itself is representative of mostly contaminants.
-Using this assumption, the sum of $\textbf{x}$ and $\textbf{e}$, defined as $\textbf{r}$:
-
-\begin{equation}
-\label{eq:rxe}
-\textbf{r} = \textbf{x} + \textbf{e},
-\end{equation}
-can be thought of as the sum of contaminants plus EoR.
-The quantity $\textbf{r}$ then becomes the dataset for which we are measuring how much loss of $\textbf{e}$ there is due to our power spectrum pipeline.
-
-We are interested in quantifying how much variance in $\textbf{e}$ is lost after weighting $\textbf{r}$ and estimating the power 
-spectrum according to QE formalism. We investigate this by comparing two quantities we call the input power spectrum and 
-output power spectrum: $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$, estimated using QE as
-
-\begin{equation}
-\label{eq:Pin}
-\widehat{P}_{\rm in}^{\alpha} \equiv \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}
-\end{equation}
-
-\noindent and
-
-\begin{eqnarray}
-\label{eq:sigloss}
-\widehat{P}_{\rm out}^{\alpha} &\equiv& \widehat{\textbf{P}}_{r}^{\alpha} \nonumber\\%-\widehat{\textbf{P}}_{x,\alpha} \nonumber \\
-&=& \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{r},% - \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x},
-\end{eqnarray}
-where, for illustrative purposes and notational simplicity, we have written these equations with scalar normalizations M, even though for our numerical results we choose a diagonal matrix normalization using $\mathbf{M}$ as in Equation \eqref{eq:phat}.
-
-The quantity $\widehat{P}_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$.
-It can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations.
-The role of $\widehat{P}_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics.
-The input power spectrum is then to be compared to $\widehat{P}_{\rm out}$, which approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-
-%In the limit where no significant cross-correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e., the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure).
-In other words, we make the anzatz that
-
-%\begin{equation}
-%\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x} \label{eqn:anzatz},
-%\end{equation}
-%and folding in our definition from Equation \eqref{eq:sigloss}, this ansatz implies that we are seeking the injected 
-%signal amplitude which causes a power doubling ($\phat_r = 2 \phat_x$). \cc{I am unsure of this power doubling thing}
-
-Under this injection framework, we can begin to see explicitly why there can be large signal loss. Expanding out Equation \eqref{eq:sigloss}, $\widehat{P}_{\rm out}$ becomes:
-
-%
-%In short, we can approximate a signal loss estimate as the ratio of $\widehat{P}_{\rm out}/P_{\rm in}$, evaluated at the data level $\widehat{\textbf{P}}_{x}$.
-We motivate the fact that we can evaluate the output-to-input power spectrum ratio at $\widehat{\textbf{P}}_{x}$ by the following reasoning (and then detail our signal loss estimation in practice in the sections that follow).
-%
-%In the limit of no instrumental noise, the data that we measure, $\x$, is comprised of two signals, such that
-%\begin{equation}
-%\x \equiv \f + \s,
-%\end{equation}
-%where $\mathbf{f}$ represents the foregrounds and $\mathbf{s}$ represents the cosmological signal.
-In general, suppose that our power spectrum algorithm passes the data through some function $g$, yielding a lossy estimate of the power spectrum $\phat_{x}$.
-This can be parametrized as
-%\begin{equation}
-%\label{eq:LinearPspecSum}
-%\langle \phat_{x} \rangle  = \langle g(\x) \rangle = \ell_{\rm fg} \p_{\rm fg} + \ell_{\rm eor} \p_{\rm eor},
-%\end{equation}
-%where $\ell_{\rm eor}$ and $\ell_{\rm fg}$ are multiplicative factors accounting for the signal loss in the true EoR 
-%power spectrum $\p_{\rm eor}$ and true foreground power spectrum $\p_{\rm fg}$, respectively. It is not 
-%\emph{a priori} obvious why this parameterization is suitable; we thus provide a toy model in Appendix 
-%\ref{sec:sigloss_appendix} to motivate this, although it should be noted that the derivation is an approximation 
-%which assumes that the covariance used in the QE analysis is close to the true covariance with effects due to 
-%small sample size limited to first order perturbations and thus neglects cross-correlation between $x$ and $e$.  
-%In actual fact the sample size is similar to the number of independent modes, a case were one expects cross 
-%terms to be remain significant.   
-%
-%Given this form, a suitable estimate for $\p_{\rm eor}$ would be $\phat_{x} / \ell_{\rm eor}$, or the uncorrected power spectrum of data divided by the signal loss estimate.
-Although such an estimate leaves an additive bias from foregrounds (see Section \ref{sec:BiasTypes}) that must be mitigated by other methods (as is the case for any attempt to measure the $21\,\textrm{cm}$ power spectrum), it normalizes $\p_{\rm eor}$ back to its correct level such that there is no multiplicative bias.
-The most conceptually straightforward way to compute $\ell_{\rm eor}$ is to model the foregrounds and EoR signal via simulations, and then to form the quantity
-%\begin{equation}
-%\label{eq:Deriv1}
-%\widehat{\ell}_{\rm eor} = \frac{g(\f + \s) - g(\f)}{\p_{\rm eor}}.
-%\end{equation}
-%However, this approach assumes that we have sufficiently good knowledge of our foreground and signal models, which is certainly not the case --- if it were, it would be simpler to construct our covariance matrices from our models, avoiding signal loss altogether!
-Instead, we can use the data itself as our model of the foregrounds, injecting a new EoR signal $\e$ (with power spectrum $P_{in}$), computing instead
-%\begin{equation}
-%\label{eq:Deriv2}
-%\widehat{\ell}_{\rm eor} = \frac{g(\x+ \e) - g(\x)}{P_{in}},
-%\end{equation}
-%which reduces to the same result because of the linearity of Equation \eqref{eq:LinearPspecSum}.
-Essentially, one is computing the slope of $\langle \phat_{x} \rangle$ with respect to $\p_{\rm eor}$ (note that both Equations \eqref{eq:Deriv1} and \eqref{eq:Deriv2} take the form of finite difference derivatives).
-Under the approximation that the relation between the two quantities is linear, it does not matter whether this slope is evaluated about $\x$ or $\f$.
-In reality, one expects some deviations from linearity, but Equation \eqref{eq:Deriv2} remains a good approximation of Equation \eqref{eq:Deriv1} as long as $\x$ is dominated by $\f$.
-%
-%Using this motivation, the numerator of Equation \eqref{eq:Deriv2} is precisely our expression for $\widehat{P}_{\rm out}$ (Equation \eqref{eq:sigloss}), and the denominator is $P_{\rm in}$ (Equation \eqref{eq:Pin}), where the function $g$ is our QE power spectrum pipeline.
-\dcj{Here is the post-hoc justification for this signal loss method.
-Except goes back to assumption of equation for g which just \emph{assumes} that there are no cross-terms in the estimation of a power spectrum.
-So we're just kicking the can down the road.} \acl{Ok, in my defense, Equation \eqref{eq:LinearPspecSum} is a little better than an \emph{assumption}.
-Appendix \eqref{sec:sigloss_appendix} does in fact illustrate this with an example.
-The crucial question is whether we're allowed to motivate our method based on a relationship that is only true in expectation.
-Note that this expectation includes allowances for signal loss due to the cross-correlation between signal and foregrounds, with an example of this being Appendix \ref{sec:sigloss_appendix}.}
-%\jp{I'm fine with leaving the text as is and calling this note closed with the addition of the appendix, but will wait for sign off from DCJ.}
-%\dcj{ Assuming that expansion to "leading order in $\eta$" means $\eta<<1$ then the approximation is that the 
-%covariance is nearly perfectly calculated from the data with only small effects due to finite samples. Thus 
-%correlations don't make it into the expression and foregrounds remain uncorrelated with eor or injected signals.  
-%I added words explaining this but it still looks strange for us to be saying that loss is linear in one section and 
-%then explaining in the next section exactly how cross-terms were what messed us up in the first go round.} 
-%\acl{Ok, I'm open to suggestions as to how to phrase this, because lots of people seem to be thinking that the appendix was meant to justify everything.
-It's not.
-It's meant as a motivational example.
-I just wanted something where I could follow through analytically to the end to show that it's ok to think about signal loss as a multiplicative factor.
-At least in expectation.
-And then how one deals with not correcting for the signal loss in expectation is described in Section \ref{sec:Practice}.}
-%
-%Effectively, this means that the relationship between the input and output power spectra, $P_{\rm in}$ and $\widehat{P}_{\rm out}$, can be thought of as a transfer function 
-%which, for a sampling of $P_{\rm in}$ and $\widehat{P}_{\rm out}$ provides a mapping from an input power spectrum distribution into an output 
-%distribution. By viewing data through this signal loss lens, we may then ask the question ``what input power spectrum 
-%distribution could this (signal-loss affected) data come from?" 
-%
-%In Section \ref{sec:Illustration}, we provide some intuition for how the transfer function is able to capture signal loss.
-Section \ref{sec:Practice} then details the numerical computations used to translate our power spectrum result into one viewed through a
-%signal loss lens.
-We note that interpretation of the signal injection results can be framed in multiple ways which yield similar but not identical answers.
-One alternative to the method described in Section \ref{sec:Practice} is described in Appendix \ref{sec:Pr_appendix}.
-%%We showcase two methods... \cc{fill in with some broad statement of why we're showing 2 methods but also state that they yield similar results...}
-
-%\subsubsection{Signal Loss Illustration}
-%\label{sec:Illustration}
-%To explore how our expression for $\widehat{P}_{\rm out}$ encapsulates signal loss, we expand out Equation \eqref{eq:sigloss}:
-
-\begin{eqnarray}
-\label{eq:crossterm_full}
-\widehat{P}_{\rm out}^{\alpha} &=& \text{M}^{\alpha}_{r}(\textbf{x}+\textbf{e})^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}(\textbf{x}+\textbf{e}) \nonumber \\%- 
-%\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x} \nonumber \\
-&=& \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} + \text{M}^{\alpha}_{d}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x}.
-%\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-Assuming \textbf{R}$_{r}$ is symmetric, the two cross-terms (terms with one copy of $\textbf{e}$ and one copy of $\textbf{x}$) can be summed together as:
-
-\begin{eqnarray}
-\label{eq:crossterm}
-\widehat{P}_{\rm out}^{\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
-^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
-&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}. %\nonumber \\
-%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
-\end{eqnarray}
-One of the key takeaways of this section is that the \citetalias{ali_et_al2015} analysis estimated signal loss by comparing \textit{only} the signal-only term (second term in Equation \eqref{eq:crossterm}) with $\widehat{P}_{\rm in}$, whereas in fact the cross-term (third term in Equation \eqref{eq:crossterm}) can substantially lower $\widehat{P}_{\rm out}$.
-In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirically estimated inverse covariance weighting ($\textbf{R}_{r} \equiv \widehat{\textbf{C}}_{r}^{-1}$) and uniform weighting ($\textbf{R}_{r} \equiv \textbf{I}$).
-We will now go into further detail and examine the behavior of this equation in three different regimes of the injected signal - very weak (left ends of the $P_{\rm in}$ axes in Figure \ref{fig:sigloss_terms}), very strong (right ends), and in between (middle portions).
-
-{\bf Small injection:}
-%In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$.
-They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected.
-%This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. 
-In this regime, the cross-terms (red) behave as noise averaged over a finite number of samples.
-Output values are Gaussian distributed around zero, spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{R}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-In fact, for the uniformly weighted case, the cross-term  $\text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e}$ is well modeled as a symmetric distribution with zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-We also note that in this regime, $\widehat{\textbf{P}}_{r}$ (black) approaches the data-only power spectrum value (gray) as expected.
-%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term.
-However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $\widehat{P}_{\rm out}$.
-It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $\widehat{P}_{\rm out}$ (black).
-We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level.
-This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).
-
-{\bf Large injection:}
-When the injected signal is much larger than the measured power spectrum, the data-only components can 
-be neglected as they are many orders of magnitude smaller.
-We include a description of this regime for completeness in our discussion, but note that the upper limits that we compute are typically not determined by simulations in this regime (i.e., in using an empirical weighting scheme we've assumed the data to be dominated by foregrounds rather than the cosmological signal).
-However, it is useful as a check of our system in a relatively simple case.
-As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are small in comparison to the signal-only term (green).
-Here only does the signal-only term used in \citetalias{ali_et_al2015} dominate the total power output.
-We again see that, in the empirical inverse covariance weighted case, the cross-terms behave as noise (positive and negative fluctuations around zero mean).
-This is for the same reason as at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$.
-The cross-correlation can again be modeled as a symmetric distribution of zero mean and width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-
-{\bf In between:}
-When the injected signal is of a similar amplitude to the data by itself, the situation becomes less straightforward. We see that 
-the weighted injected power spectrum component mirrors the input power indicating little loss (i.e., the green curve follows the dotted black line), eventually 
-departing from unity when the injected amplitude is well above the level of the data power spectrum. However, 
-in this regime the cross-term (red) has nearly the same amplitude, but with a negative sign.
-As explained below, this negativity is the result of cross-correlating inverse covariance weighted terms.
-This negative component drives down the $\widehat{P}_{\rm out}$ estimator (black).
-Again, we emphasize that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for underestimating power spectrum limits in \citetalias{ali_et_al2015}.
-
-%A brief description of Figure \ref{fig:sigloss_terms} is as follows.
-The gray curve represents the data level, which is constant as the level of $P_{\rm in}$, the input EoR signal, is changed.
-The blue curve is the power spectrum of the data only, weighted by an empirical covariance estimated from the data plus the EoR signal ($\widehat{\textbf{C}}_{r}^{-1}$).
-It approaches the gray at low injection level, as expected, since in that case $\widehat{\textbf{C}}_{r}^{-1} \rightarrow \widehat{\textbf{C}}_{x}^{-1}$.
-The green curve is the power spectrum of the EoR signal, weighted by $\widehat{\textbf{C}}_{r}^{-1}$.
-This is the exact term that was compared to $P_{\rm in}$ in the \citetalias{ali_et_al2015} signal loss analysis, and in doing so this would imply there is negligible loss (where the green crosses the gray).
-It is primarily due to the cross-terms (red), that the black curve exhibits $\sim$$3$ orders of magnitude of loss at the data level, for the inverse covariance weighted case.
-We see that the cross-terms can produce a large, negative signal which serves to reduce $\widehat{P}_{\rm out}$ and drive the bulk of our loss.
-In the unweighted case, however (right plot), the cross-terms primarily drive a tail of `excess' $\widehat{P}_{\rm out}$ at low injects, though at larger injects we see unity transfer as expected (the solid black curve lies on the dotted black line, which represents unity transfer).
-
-%\dcj{This section isn't held up by figure 17. Is that because the "illustriative" figure is off? Or is it that cross-terms don't matter when injected signal is very large.}
-%We now turn to building intuition behind the negative power that arises from the cross-terms in Equation \eqref{eq:crossterm}.
-For illustrative purposes in this subsection only, we consider a scenario where $\textbf{e}$ dominates compared to $\textbf{x}$.
-It is in this limit where we expect signal loss to be greatest, and $\widehat{P}_{\rm out}$ becomes:
-%
-%\begin{eqnarray}
-%\label{eq:pout_expand}
-%P_{\rm out, \alpha} &\approx&  M^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} +
-% 2M^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e}.
-%\end{eqnarray}
-%The first term of $\widehat{P}_{\rm out}$ is simply the weighted power spectrum of $\textbf{e}$ alone.
-Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
-However, without taking into account the cross-terms (the second term), we can substantially underestimate loss.
-In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
-Including these cross-terms in our new analysis represents the bulk change of our revised analysis compared to \citetalias{ali_et_al2015}.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_terms.pdf}
-	\caption{Illustration of the power spectrum amplitude of five different power spectrum terms, each a function of visibility data ($\textbf{x}$), simulated injected EoR signal ($\textbf{e}$), or both ($\textbf{r}$).
-This figure shows how these quantities behave as the power level of the injected EoR signal increases (along the x-axis).
-The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we sample a larger $P_{\rm in}$ range and fit smooth polynomials to our data points to make an illustrative example.
-We emphasize that the output power spectrum in black ($\widehat{P}_{\rm out}=\widehat{\textbf{P}}_r$) approximates the (lossy) power spectrum estimate that is output by our analysis pipeline prior to any signal loss adjustments.
-Roughly speaking, it can be compared to the input signal level ($P_{\rm in}$) to estimate the amount of signal loss.
-Left: Empirical inverse covariance weighting is used in power spectrum estimation, as done in \citetalias{ali_et_al2015}.
-The dotted diagonal black line indicates perfect 1:1 input-to-output mapping (no signal loss).
-The gray horizontal line is the power spectrum value of data alone, $\widehat{\textbf{P}}_{x}$ (it does not depend on injected power).
-The green signal-signal component is the term used in \citetalias{ali_et_al2015} to estimate signal loss.
-It is significantly higher than $\widehat{\textbf{P}}_{r}$ (black) when the cross-terms (red) are large and negative (black $=$ green $+$ red $+$ blue).
-In the regime where cross-correlations between signal and data are not dominant (small and large $P_{\rm in}$), the cross-terms have a noise-like term with width $\sqrt{\widehat{\textbf{P}}_e}\sqrt{\widehat{\textbf{P}}_x}$.
-However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative estimates due to couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$.
-This causes the difference between the green curve (which exhibits negligible loss at the data-only power spectrum value) and the black curve (which exhibits $\sim4$ orders of magnitude of loss).
-Right: The same power spectrum terms illustrated for the uniform weighted case.}
-\label{fig:sigloss_terms}
-\end{figure*}
-
-The source of the strong negative cross-term is not immediately obvious, however it is an explainable effect. 
-When $\textbf{R}_{r}$
-is taken to be $\widehat{\textbf{C}}_{r}^{-1}$, the third term of Equation \eqref{eq:crossterm} is a cross-correlation between $\widehat{\textbf{C}}_{r}^{-1}\textbf{x}$ and
-$\widehat{\textbf{C}}_{r}^{-1}\textbf{e}$. As shown in \citet{switzer_et_al2015}, this cross-correlation term is non-zero, and in fact negative in expectation. 
-This negative cross-term power arises from a coupling between the inverse of 
-$\widehat{\textbf{C}}_{r}$ and $\mathbf{x}$. 
-Intuitively, we can see this by expanding the empirical covariance of $\textbf{r}=\textbf{x}+\textbf{e}$:
-
-\begin{eqnarray}
-\widehat{\textbf{C}}_{r} &=& \langle \textbf{rr}^{\dagger} \rangle_{t} \nonumber \\ 
-&=& \langle \textbf{xx}^{\dagger} \rangle_{t} + \langle \textbf{xe}^{\dagger} \rangle_{t} + \langle \textbf{ex}^{\dagger} \rangle_{t} + \langle 
-\textbf{ee}^{\dagger} \rangle_{t},
-\end{eqnarray}
-
-\noindent where we can neglect the first term because $\textbf{x}$ is small (i.e., the large negative cross-term power in the left panel of Figure \ref{fig:sigloss_terms} occurs when the injected amplitude surpasses the level of the data-only power spectrum).
-Without loss of generality, we will assume
-an eigenbasis of $\textbf{e}$, so that $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$ is diagonal. The middle 
-two terms, however, can have power in their off-diagonal terms due to the fact that, when averaging over a finite
-ensemble, $\langle\textbf{xe}^\dagger\rangle_t$ is not zero.
-As shown in Appendix C of \citet{parsons_et_al2014}%\footnote{This same appendix also gives a now-prescient warning about signal loss and the dangers of noise and sample variance in inverse covariance.}
-, to leading order the inversion of a diagonal-dominant matrix like $\widehat{\textbf{C}}_{r}$ (from $\langle 
-\textbf{ee}^{\dagger} \rangle_{t}$) with smaller
-off-diagonal terms results in a new diagonal-dominant matrix with negative off-diagonal terms. These off-diagonal
-terms depend on both $\textbf{x}$ and $\textbf{e}$. Then, when $\widehat{\textbf{C}}^{-1}_{r}$ is multiplied into $\textbf{x}$,
-the result is a vector that is similar to $\textbf{x}$ but
-contains a residual correlation to $\textbf{e}$ from the off-diagonal components of $\widehat{\textbf{C}}^{-1}_{r}$. The
-correlation is negative because the product $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ effectively squares the $\textbf{x}$-dependence
-of the off-diagonal terms in $\widehat{\textbf{C}}^{-1}_{r}$ while retaining the negative sign that arose from the inversion
-of a diagonal-dominant matrix.
-% XXX [ARP: we may want to write this all out explicitly in an appendix]
-
-%The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
-%simulation, which would yield greater values for $\widehat{P}_{\rm out}$ and thereby underestimate signal loss.
-This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data.
-Therefore, in our revised
-%signal loss computation we use the full quantity for $\widehat{P}_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
-%weighted power spectrum of the data from the weighted power spectrum of data plus EoR.
-
-%\dcj{This paragraph has me confused.}
-%The conclusion is that signal loss generically arises because of couplings between $\widehat{\textbf{C}}^{-1}_{r}$ and $\mathbf{x}$.
-In principle, using $\widehat{\textbf{C}}^{-1}_{r}$ in place of the true inverse covariance $\textbf{C}^{-1}$ provides yet another source of multiplicative bias, which results in a modification to the treatment shown here.
-Such a modification is accounted for in the demonstration of Appendix \ref{sec:sigloss_appendix}, where we additionally discard the assumption that $|\textbf{x}|\ll|\textbf{e}|$.
-However, despite the loosening of these approximations, one sees that the qualitative message (of anti-correlations resulting in signal loss) remains intact.
-
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
-Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
-However, the normalization matrix $\mathbf{M}$ is derived assuming that the unnormalized estimator is quadratic in the data.
-The power spectrum estimate will therefore be incorrectly normalized, which manifests as signal loss.
-We leave a full analytic solution for $\mathbf{M}$ for future work, since our simulations already capture the full phenomenology of signal loss and have the added benefit of being more easily generalizable in the face of non-Gaussian systematics.
-
-\subsection{Signal Loss in Practice}
-\label{sec:Practice}
-
-We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
-outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
-($\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which leads to substantial loss. %With this weighting, our 
-%expressions for $\widehat{P}_{\rm in}$ and $\widehat{P}_{\rm out}$ become:
-
-%\begin{eqnarray}
-%\widehat{P}_{\rm in}^{\alpha} &=&  \text{M}^{\alpha}_{\rm in}\textbf{e}^{\dagger}\textbf{I}\textbf{Q}^{\alpha}\textbf{I}\textbf{e} \\
-%\widehat{P}_{\rm out}^{\alpha} &=&  \text{M}^{\alpha}_{r}\textbf{r}^{\dagger}\widehat{\textbf{C}}_{r}^{-1}\textbf{Q}^{\alpha}%\widehat{\textbf{C}}_{r}^{-1}\textbf{r}.% \nonumber \\
-%\end{eqnarray}
-
-%The treatment we outlined in the previous section implicitly assumed that signal loss corrections could be treated in expectation.
-In practice, however, the signal loss itself is a random variable --- some realizations of the cosmological signal may be more correlated with foreground modes than others, leading to more signal loss.
-This leads to two issues.
-The first is that Equation \eqref{eq:LinearPspecSum} may not hold.
-In particular, a third term that is a quadratic combination of $\f$ and $\s$ (e.g., $\f^\dagger \C^{-1} \s$) may appear.
-However, we can circumvent this issue by decomposing $\f$ into a sum of two vectors, one that is proportional to $\s$ and one that is orthogonal to $\s$.
-The former can be absorbed into the EoR term (part of the signal loss estimate), while the latter can be absorbed into the foreground term.
-In other words, suppose that we have
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 + \ell_{\rm eor} |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f} \cdot \mathbf{e}.
-%\end{equation}
-%in place of Equation \eqref{eq:LinearPspecSum}.
-Now, split $\mathbf{f}$ into $\mathbf{ f}_\parallel +\mathbf{ f}_\perp$, which are the components of the foregrounds that couple to the EoR versus those that do not.
-Further parameterize $\mathbf{ f}_\parallel \equiv \rho \mathbf{e}$, where $\rho$ is some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR.
-This then gives
-%\begin{equation}
-%\label{eq:fperpfpara}
-%\phat_x \approx \ell_{\rm fg} |\mathbf{f}|^2 +( \ell_{\rm eor} + \rho  \ell_{\rm fe} ) |\mathbf{e}|^2 + \ell_{\rm fe} \mathbf{f}\cdot \mathbf{f}_\perp.
-%\end{equation}
-%Since $|\mathbf{e}|^2$ would be a lossless estimate of the true EoR power spectrum, this expression recovers the linear relation between the true EoR power spectrum and the lossy estimate.
-%\dcj{Wait what?
-I think you are saying essentially that some x can remain in Pout which is what we are seeing.
-Or is this some extra bit of method which has been added to the analysis...} \acl{I'm not sure that's what I'm saying.
-(And by ``I'm not sure" I don't mean it in the colloquial sense of ``you're not right and I'm just trying to be polite about it", but rather the literal sense of the phrase ``I'm not sure").
-What I was trying to say was that if I wrote Equation \eqref{eq:LinearPspecSum} without the ensemble average, I could say
-%\begin{equation}
-%\phat_x \approx \ell_{\rm fg} f^2 + \ell_{\rm eor} e^2 + \ell_{\rm fe} fe.
-%\end{equation}
-%(Note that even this is an approximation. In principle there is an infinite series containing all possible powers of 
-%$e$ and $f$). Now, we split $f$ into $ f_\parallel + f_\perp$, which are the components of the foregrounds that 
-%couple to the EoR versus those that do not. Further parameterize $f_\parallel \equiv \rho e$, where $\rho$ is 
-%some correlation coefficient that quantifies the degree of correlation between the foregrounds and the EoR. 
-%Under this parameterization, one can write the $fe$ term in terms of $e^2$ (which gets absorbed into the other 
-%EoR term, plus residual foregrounds that we don't care about).}\acl{Just promoted this last part to something in 
-%the main text.}\dcj{I will admit to being a little lost here.  Doesn't changing the basis just convert the unknown f 
-%dot s term into other unknown terms. Isn't the whole point of Eq 24 supposed to be that we can subtract off the 
-%$g(x)$ to estimate $\hat{\ell}_{\rm eor}$?  How do we subtract off $f\dot f_\perp$? Don't we want to know $
-%\ell_{\rm eor}$ not $(\ell_{\rm eor} + \rho\ell_{\rm fe})$? }
-%\acl{I think what we are trying to say here is that actually the thing we want \emph{is} $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.
-Essentially, the potential coupling between the injected EoR and the foregrounds means that we lose the nice form of Equation \eqref{eq:LinearPspecSum}, which justified what is basically a multiplicative correction to signal loss.
-What we are suggesting here is that even when there is a coupling, the estimator can be parameterized as $\alpha  |\mathbf{e}|^2 + \beta$.
-So essentially we are defining an effective $
-%\ell_{\rm eor}$, which is given by $(\ell_{\rm eor} + \rho\ell_{\rm fe})$.}
-
-One issue to address is how one incorporates the randomness of $\widehat{P}_{\rm out}$ into our signal loss corrections.
-A different realization of the mock EoR signal is injected with each bootstrap run, causing the output to vary in three ways ---  there is noise variation from the bootstraps, there is cosmic variation from generating multiple realizations of the mock EoR signal, and there is a variation caused by whether the injected signal looks more or less ``like'' the data (i.e., how much coupling there is, which affects how much loss results).
-
-For each injection level, the true $P_{\rm in}$ is simply the average of our bootstrapped estimates $\widehat{P}_{\rm in}$, since $\widehat{P}_{\rm in, \alpha}$ is by construction an unbiased estimator.
-Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} |
-\widehat{P}_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $\widehat{P}_{\rm out}$.
-Bayes' rule relates the posterior, which we don't know, to the likelihood, which we can forward model.
-In other words,
-
-\begin{equation}
-\label{eq:Bayes}
-p(P_{\rm in} | \widehat{P}_{\rm out}) \propto {\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})}\,p(P_{\rm in}) ,
-\end{equation}
-
-\noindent where $\mathcal{L} $ is the likelihood function defined 
-as the distribution of data plus signal injection ($\widehat{P}_{\rm out}$) given the injection $P_{\rm in}$.  We construct this distribution  
-by fixing $P_{\rm in}$ and simulating our analysis pipeline for many realizations of the injected EoR signal 
-consistent with this power spectrum. The resulting distribution is normalized such that the sum over $\widehat{P}_{\rm out}$ is unity, and the 
-whole process is then repeated for a different value of $P_{\rm in}$.
-
-%\subsubsection{Signal Loss Implementation Details}
-%\label{sec:Implementation}
-
-The implementation details of the injection process require some more detailed explanation.
-In our code, we add a new realization of EoR to each independent bootstrap of data (see Section \ref{sec:Boot} for a description of PAPER's bootstrapping routine) with the goal of simultaneously capturing cosmic variance, noise variance, and signal loss.
-To limit computing time we perform $20$ realizations of each $P_{\rm in}$ level.
-We also run $50$ total EoR injection levels, yielding $P_{\rm in}$ values that range from $\sim$$10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, resulting in a total of $1000$ data points on our $P_{\rm in}$ vs.
-$\widehat{P}_{\rm out}$ grid.
-
-Going forward, we treat every $k$-value separately in order to determine an upper limit on the EoR signal per $k$.
-We bin our simulation outputs along the $P_{\rm in}$ axis (one bin per injection level) and, since they are well-approximated by a Gaussian distribution in our numerical results, we smooth the distribution of $\widehat{P}_{\rm out}$ values by fitting Gaussians for each bin based on its mean and variance (and normalize them).
-Stitching all of them together results in a 2-dimensional transfer function --- the likelihood function in Bayes' rule, namely $\mathcal{L} (  \widehat{P}_{\rm out} | P_{\rm in})$.
-We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
-%For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
-
-Finally, our transfer functions are shown in Figure \ref{fig:sigloss_transfercurve} for both the weighted (left) and unweighted (right) cases.
-Our bootstrapped power spectrum outputs are shown as black points and the colored heat-map overlaid on top is the likelihood function modified by our prior.
-Although we only show figures for one $k$-value, we note that
-the shape of the transfer curve is similar for all $k$'s.
-We then invoke Bayes' interpretation and re-interpret it as the posterior $p(P_{\rm in}|\widehat{P}_{\rm out})$ where we recall that $\widehat{P}_{\rm out}$ represents a (lossy) power spectrum.
-To do this we make a horizontal cut across at the data value $\widehat{\textbf{P}}_{x}$ (setting $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{x}$), shown by the gray solid line, to yield a posterior distribution for the signal.
-We normalize this final distribution and compute the $95\%$ confidence interval (an upper limit on EoR).
-
-%We note that the distribution of $\phat_{x}$ has a variance determined from the bootstrapping process and is peaked around the power spectrum value computed from the no-bootstrapping case.
-We smooth its distribution using 1D kernel density estimators (and normalize to unity) before multiplying it with the transfer function.
-Performing a summation and normalization for the entire distribution of $\phat_{x}$ yields a final $P_{\rm in}$ distribution --- the distribution of our data as seen through the signal loss lens.
-We compute power spectrum points from the peak of the histograms, and power spectrum errors from $95\%$ confidence intervals.
-
-By-eye inspection of the transfer function in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
-\widehat{\textbf{P}}_{x}$ is marked by the solid gray horizontal lines.
-From the left plot (empirically estimated inverse covariance weighting), one can eyeball that a data value of $10^{5} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, for example, would map approximately to an upper limit of $\sim10^{9} \,$mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, implying a signal loss factor of $\sim10^{4}$.
-
-%As a final complication to our procedure, we note that there will be some scatter in our likelihood due to our having only a finite number of simulations.
-Ideally, running many simulations would lead to convergence; however, our desire to be able to quickly and easily estimate signal loss for a variety of weighting schemes and datasets means having a finite sample in practice.
-\dcj{This dependence on injection count was checked with a run having 10x the usual number of integrations.} To separate the intrinsic stochasticity of signal loss from that which arises due to simulation sample variance, we repeat our analysis for a power spectrum estimator without signal loss ($\textbf{R} = \textbf{I}$), shown as the right plot in Figure \ref{fig:sigloss_transfercurve}.
-Here the scatter, evident as deviations from unity-transfer, is entirely due to finite sample variance.
-To remove this effect we measure the width of this lossless case and then de-convolve that extra width from the likelihood for the lossy scenario.
-Specifically, we de-convolve Gaussian distributions of $\widehat{P}_{\rm out}$ in the uniform-weighted case from those of the weighted case (vertical cuts through the plots in Figure \ref{fig:sigloss_transfercurve}), for every $P_{\rm in}$.
-By doing this, we are left with only the intrinsic scatter in signal loss, or scatter that stems from how much the random EoR signal $\textbf{e}$ happens to
-%look like the data $\textbf{x}$, a quantity we do not know offhand but one that we would like to correct for.
-As an extreme example, if we are very unlucky, one realization of $\textbf{e}$ would have the same shapes, or eigenvectors, as $\textbf{x}$.
-An empirically-derived covariance would then down-weight these shapes, destroying the entire EoR signal.
-On the other hand, the less that $\textbf{e}$ looks like $\textbf{x}$, the less signal loss that would result.
-The intrinsic scatter we can get is not a dominant factor in this case but it is important to correct for the fact that a particular $\widehat{P}_{\rm out}$ value could arise from a range of $P_{\rm in}$ values.
-
-%The solid black diagonal line in Figure \ref{fig:sigloss_transfercurve} shows unity-transfer, which we expect to occur for the 
-%nweighted case ($\textbf{R} = \textbf{I}$). Therefore, it is worth thinking about the spread, or scatter, around this black line that 
-%we see in the right plot (the colored `heat-map'). One might imagine that there should be one true $\widehat{P}_{\rm out}$ value for every 
-%$P_{\rm in}$, implying one well-determined signal loss factor for every data value. Focusing on the unweighted case alone, the 
-%scatter observed arises from the fact that the values of the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation 
-%\eqref{eq:pout_expand} change for different mock EoR signals, $\textbf{e}$. Since we draw different random $\textbf{e}$'s for 
-%every bootstrap (for reasons made clear in the next paragraph), there is a range of $\widehat{P}_{\rm out}$ values that results from the same 
-%$P_{\rm in}$. This randomness causes the spread seen in the right plot of Figure \ref{fig:sigloss_transfercurve}, as well as most of 
-%the spread in the weighted case (left plot).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.pdf}
-	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{P}_{\rm out}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}.
-Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level.
-Since our $\widehat{P}_{\rm out}$ values are well-approximated by a Gaussian distribution, we fit Gaussians to each injection level based on the mean and variance of the simulation outputs.
-This entire likelihood function is then multiplied by a Jeffreys prior for $p(P_{\rm in}$), with the final result shown as the colored
-heat-maps on top of the points. Two cases are displayed: empirically estimated inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
-diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{P}}_{x}$, from which a posterior distribution for the signal is extracted.
-From these plots, it is clear that the weighted case results in $\sim4$ orders of magnitude of signal loss at the data-only power spectrum value, whereas the uniform-weighted case does
-not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
-	\label{fig:sigloss_transfercurve}
-\end{figure*}
-
-%One peculiar aspect of Figure \ref{fig:sigloss_transfercurve} is the fact that at low $P_{\rm in}$ values it appears that we can have signal gain ($\widehat{P}_{\rm out} > P_{in}$).
-\cc{This is a log-plotting effect and is under-construction!}.
-%This is unphysical in nature but caused due to the dominating cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand} once $\textbf{e}$ becomes small. 
-%
-%The shape of our signal loss transfer function can be described as follows.
-At low injection levels, for small $\textbf{e}$, we are dominated by the cross-terms involving $\textbf{e}$ and $\textbf{x}$ in Equation \eqref{eq:pout_expand}.
-As $\textbf{e}$ increases, we move
-%into a regime where $\widehat{P}_{\rm out} \sim P_{in}$, and then eventually into a regime where $\widehat{P}_{\rm out} < P_{in}$ when $\textbf{e}$ is 
-%large enough to be destroyed if weighting the data using itself. Although we only show figures for one $k$ value, we note that 
-%the shape of the transfer curve is nearly identical for all $k$'s (though we treat each $k$ separately).
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[trim={1cm 0cm 1cm 1cm},width=1\textwidth]{plots/sigloss_datadist_inversecovariance.png}
-%	\caption{Normalized histograms of the power spectra that result from using inverse covariance weighting on %PAPER-64 data after signal loss correction.
-Power spectrum points are computed from the peak of the distributions.
-Errors are computed using $95\%$ confidence intervals.}
-%	\label{fig:sigloss_datadist_inversecovariance}
-%\end{figure*}
-
-The loss-corrected power spectrum limit for empirically estimated inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (solid red), which we can compare to the original lossy result (dashed red).
-%There are a few important checks to examine.
-First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels.
-This is an important check, as we expect no signal loss for this case.
-Any difference here would indicate an error in the pipeline or discrepancy in the range of data included.
-Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction.
-Post-signal loss estimation, the power spectrum limits are higher than both the theoretical noise level (green) and uniform-weighted power spectrum (which is shown three ways: black and gray points are positive and negative power spectrum values, respectively, with $2\sigma$ error bars from bootstrapping, the solid blue is the upper limit on the EoR signal using the full signal injection framework, and the shaded gray is the power spectrum values with thermal noise errors).
-We elaborate on this point in the next section, as well as investigate alternate
-weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of the EoR signal.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of empirical inverse covariance weighting.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using empirical inverse covariance weighting.
-Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:Error}.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-In this example, we see that the lossy power spectrum limit is $\sim 4$ orders of magnitude too low when using empirical inverse covariance weighting.}
-\label{fig:ps2_data}
-\end{figure*}
-
-\subsection{Minimizing Signal Loss}
-\label{sec:Weight}
-
-With a signal loss formalism established, we now have the capability of experimenting 
-with different weighting options for $\textbf{R}$. Our goal here is to choose a weighting method that successfully down-weights 
-foregrounds and systematics in our data without generating large amounts of signal loss as we have seen with the inverse covariance estimator. We have found that the balance 
-between the two is a delicate one and requires a careful understanding and altering of empirical covariances.
-
-We saw in Section \ref{sec:otherweight} how limiting the number of down-weighted eigenmodes (i.e., flattening out part of the 
-eigenspectrum and effectively decoupling the lowest-valued eigenmodes, which are typically EoR-dominated, from the data) can help minimize signal loss.
-We experiment with this idea on PAPER-64 data, dialing the number of modes
-that are down-weighted from zero (which is equivalent to identity-weighting, or the uniform-weighted case) to $21$ (which is the full inverse 
-covariance estimator). The power spectrum results for one $k$-value, both before and after signal loss 
-estimation, are shown in the top panel in Figure \ref{fig:sigloss_modeloop}. We see that the amount of signal loss increases as weighting 
-becomes more aggressive (dashed red). In other words, more EoR-dominated fluctuations are being overfit and 
-subtracted as more modes are down-weighted. We also find that the power spectrum upper limit, post-signal loss estimation, 
-increases with the number of down-weighted modes (solid red).
-The more modes we use in down-weighting, the stronger the coupling between the weighting and the data, and the greater the error we have in estimating the power spectrum.
-\citet{switzer_et_al2013} took a similar approach in determining the optimal number of modes to down-weight in GBT data, finding similar trends and noting that removing too few modes is limited by residual foregrounds and removing too many modes is limited by large error bars and signal loss.
-
-Optimistically, we expect there to be a ``sweet spot" as we dial our regularization knob; a level of regularization where weighting 
-is beneficial compared to uniform weighting (blue).
-In other words, we would like a weighting scheme that down-weights eigenmodes that predominantly describe foreground modes, but not EoR modes.
-We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
-only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting).
-For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
-
-We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss.
-We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}.
-The dashed red and solid red lines represent power spectrum limits pre and post-signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as a percentage of Tr($\widehat{\textbf{C}})\textbf{I}$ added to $\widehat{\textbf{C}}$.
-We parameterize this ``regularization strength" parameter as $\gamma$, namely $\widehat{\textbf{C}} \equiv \widehat{\textbf{C}} + \gamma$Tr$(\widehat{\textbf{C}})\textbf{I}$.
-From this plot we see that only a small percentage of Tr($\widehat{\textbf{C}})$ is needed to significantly reduce loss.
-We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the red curves will approach the uniform-weighted case.
-We also notice that the post-signal loss limit hovers around the uniform-weighted limit for a large range of regularization strengths and while an overall trend from high-to-low signal loss is seen as the strength increases, there does not appear to be a clear ``minimum" that produces the least loss.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.pdf}
-	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$\,$h$ Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
-are shown before (dashed red) and after (solid red) signal loss estimation via our signal injection framework as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
-are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e., unweighted) to $21$ modes on the right (i.e., the full inverse 
-covariance estimator).
-$\sim4$ orders of magnitude of signal loss results when using empirically estimated inverse covariance weighting.
-Bottom: Power spectrum upper limits before (dashed red) and after (solid red) signal loss estimation as a function of identity added to the empirical covariance.
-This regularization knob is tuned from $\gamma = 10^{-4}$ on the right (i.e., very little regularization) to $\gamma = 1$ on the left (see main text for the definition of $\gamma$).
-Also
-plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (blue) and inverse variance 
-weighted case (black); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
-as green.
-In the PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}}_{\rm eff} \equiv 0.09 \, $Tr($\widehat{\textbf{C}})\textbf{I} + \widehat{\textbf{C}}$ ($\gamma = 0.09$) as a simple example of regularization that minimizes loss, and note that the power spectrum limits using this type of regularization are roughly constant across a large range of values of $\gamma$.}
-	\label{fig:sigloss_modeloop}
-\end{figure*}
-
-In addition to our thermal noise prediction (green) and uniform-weighted power spectrum limit (blue), one additional horizontal line is shown in Figure \ref{fig:sigloss_modeloop} 
-in both panels and represents a third regularization technique.
-This line (black) denotes the power spectrum value, post-signal loss estimation, for inverse variance weighting (multiplying an identity
-matrix element-wise to $\widehat{\textbf{C}}$).
-This result is single-valued and not a function of the horizontal axis.
-We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
-However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
-We choose this weighting scheme merely as a simple example of regularizing PAPER-64 covariances, noting that the power spectrum upper limit remains roughly constant for a broad range of values of $\gamma$.
-
-It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
-Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations.
-Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
-(\textit{in prep.}) use uniform weightings in order to produce more trustworthy, straightforward power spectrum limits that do not suffer from loss.
-
-The power spectrum result for our subset of PAPER-64 data (using only one baseline separation type, $10$ baselines, and $\widehat{\textbf{C}}_{\rm eff}$) using the analysis presented in this paper is shown in Figure
-\ref{fig:ps1_data}.
-Again, the solid red curve represents our upper limit on the EoR signal using the full signal injection framework.
-The uniform weighted case is shown as the black and gray points, which correspond to positive and negative power spectrum values respectively (with
-$2\sigma$ errors bars from bootstrapping).
-It is also shown as an upper limit using the signal injection framework (solid blue), which is interestingly larger than the errors computed from bootstrapping, likely because the full injection framework takes into account additional sample variance whereas the bootstrapped errors do not.
-Finally, the gray shaded regions combine the measured uniform weighted power spectrum values with thermal noise errors.
-We show this power spectrum result as one example of how a simple regularization of an empirical covariance matrix can minimize signal loss, though we also note that this weighting does not produce more stringent limits than the uniform weighted case, thus further motivating uniform-weighting for Kolopanis et al.
-(\textit{in prep.}).
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_data_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_data_add.pdf}
-	\caption{A power spectrum of a subset of PAPER-64 data illustrating the use of $\widehat{\textbf{C}}_{\rm eff}$ to minimize signal loss.
-The solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-This power spectrum result does not use the full dataset's sensitivity as in \citetalias{ali_et_al2015} and Kolopanis et al.
-(\textit{in prep.}), though we include all analysis changes which have mostly stemmed from revisions regarding signal
-loss, bootstrapping, and the theoretical error computation. We see that the regularization scheme used here produces limits similar to the unweighted limits.}
-	\label{fig:ps1_data}
-\end{figure*}
-
-In this section we have shown three simple ways of regularizing $\widehat{\textbf{C}}$ to minimize signal loss using PAPER-64 
-data. There are many other weighting schemes that we leave for consideration in future work. For example, one could estimate 
-$\widehat{\textbf{C}}$ using information from different subsets of baselines. For redundant arrays this might mean calculating $
-\widehat{\textbf{C}}$ from a different but similar baseline type, such as the $\sim30$\,m diagonal PAPER baselines (instead of the 
-horizontal E/W ones). Alternatively, covariances could be estimated from all baselines except the two being cross-multiplied 
-when forming a power spectrum estimate. This method was used in \citet{parsons_et_al2014} (a similar method was also used in \citet{dillon_et_al2015}) in order to avoid suppressing the 
-21\,cm signal, and it is worth noting that the PAPER-32 results are likely less impacted from the issue of signal loss underestimation 
-because of this very reason (however, they are affected by the error estimation issues described in Section \ref{sec:Error}, so 
-we also regard those results as suspect and superseded by those of Kolopanis et al. (\textit{in prep.})).
-
-Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
-calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to
-down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time.
-Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from
-data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
-
-In Section \ref{sec:CaseStudy}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
-We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
-In the remainder of this paper, we will transition to other aspects of our analysis that have been revised since \citetalias{ali_et_al2015}.
-
-% SECTION 4 OTHER ERRORS ---------------------------------------------------------------------------------
-
-\section{Additional PAPER-64 Revisions}
-\label{sec:OtherErrors}
-
-Underestimated signal loss is the main reason for the revision of the power spectrum limits from \citetalias{ali_et_al2015}.
-It is interesting to note that --- had all the other aspects of the original analysis been correct --- the underestimated limits may have been more easily caught.
-Unfortunately, two related power spectrum components, namely the error bars on the power spectrum data points and the theoretical noise prediction, were also calculated incorrectly.
-
-In this section, we summarize multiple inconsistencies and errors that have been found since the previous analysis in terms of error estimation.
-We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
-We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified through simulations.
-
-\subsection{Bootstrapping}
-\label{sec:Boot}
-
-Broadly speaking, we desire robust methods for determining accurate 
-confidence intervals for our measurements. For PAPER's analysis, we choose a data-driven method of error estimation, computing error bars that have been derived from the inherent 
-variance of our measurements. A common technique used to do this is bootstrapping, which we first define below and then discuss its application to PAPER.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, bootstrap measurements (of power spectra, for example) can be made from different random samples of data.
-Each of these bootstraps is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-%Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements).
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
-Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap).
-Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
-The error (on the mean) is then computed as the standard deviation across all bootstraps.
-
-%We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
-$N_{\rm boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
-Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
-However, we will see that $N$ depends on sample independence, and it is this dependence that led to the underestimation of errors in \citetalias{ali_et_al2015}.
-
-%Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
-This could represent $1000$ power spectrum measurements, for which we are interested in its error.
-We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-%We next form $500$ bootstraps ($N_{\rm boot} = 500$).
-To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
-The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
-This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
-values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
-and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
-itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, underestimates 
-errors.
-
-%As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of independent data samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$).
-This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both underestimate the error by drawing too many or overestimate it by drawing too few.
-However, since we know that we have $100$ independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-%	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-%sampling with replacement.
-The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
-The estimated errors match up with the theoretical prediction only at $N=100$.}
-%	\label{fig:toy_error1}
-%\end{figure}
-
-This is the precisely how errors were underestimated in PAPER-64.
-Because of fringe-rate filtering, which averages data in time to increase sensitivity, PAPER-64 data is correlated along the time axis.
-Hence, there are fewer independent samples after filtering, thus decreasing the variance of the bootstraps.
-
-More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time.
-In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis, and a total of $400$ bootstraps were created in this step, each comprised of randomly selected values sampled with replacement (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Means were then taken of the values in each bootstrap. Finally, power 
-spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap greatly 
-exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds of these random 
-samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
-\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-
-In addition to learning how sample independence affects bootstrapped errors, we have made three additional changes to our bootstrapping procedure since \citetalias{ali_et_al2015}, summarized here:
-
-\begin{itemize}
-
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
-
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into five independent groups, where no baselines were repeated in each group.
-Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
-This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
-Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
-
-\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
-
-\end{itemize}
-
-In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
-Bootstrapping can be an effective and straightforward way to estimate errors of a dataset, however, bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
-We have thus avoided this issue by removing one of our bootstrap axes, as well as updated several other details of our procedure to ensure accurate re-sampling and error estimation.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
-This underestimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
-We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
-	\label{fig:data_errors}
-\end{figure}
-
-\subsection{Theoretical Error Estimation}
-\label{sec:Error}
-
-One useful way of cross-checking measured power spectrum values and errors is to compute a theoretical estimation of thermal noise based on observational parameters.
-Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-Upon re-analysis of PAPER-64, we have discovered that this estimate was also underestimated in previous analyses.
-
-To compute our theoretical noise estimate, we use an analytic sensitivity calculation.
-Through detailed studies using several independently generated noise simulations, what we found was that our simulations all agreed but were discrepant with the previous calculations.
-The analytic
-calculation is only an approximation and attempts to combine a large number of pieces of information in an approximate way; however, when re-considering some of the approximations, the differences were large enough (factors of $10$ in some cases) to warrant a
-careful investigation. What follows here is an 
-accounting of the differences which have been discovered.
-We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots in this paper, is computed with these changes accounted for.
-
-The noise prediction $n(k)$ (\citealt{parsons_et_al2012a}; \citealt{pober_et_al2013}) for a power spectral analysis of 
-interferometric 21\,cm data, in temperature-units, is:
-
-\begin{equation}
-\label{eq:sense}
-N(k) = \frac{X^{2}Y \Omega_{\rm eff} T_{\rm sys}^{2}}{\sqrt{2N_{\rm lst}N_{\rm seps}}\,t_{\rm int}N_{\rm days}N_{\rm bls}N_{\rm pols}}.
-\end{equation}
-We will now explain each factor in Equation \eqref{eq:sense} and highlight key differences from the numbers used in \citetalias{ali_et_al2015}.
-
-\begin{itemize}
-\item $X^{2}Y$: Conversion factors from observing coordinates (angles on the sky and frequency) to cosmological coordinates (co-moving 
-distances). For $z=8.4$, $X^{2}Y = 5 \times 10^{11} \, h^{-3}$ Mpc$^{3}$ str$^{-1}$ GHz$^{-1}$.
-\item $\Omega_{\rm eff}$: The effective primary beam area in steradians (\citealt{parsons_et_al2010}; \citealt{pober_et_al2012}). 
-The effective beam area changes with the application of a fringe-rate filter, since different parts of the beam are up-weighted and down-weighted.
-Using numbers from Table 1 in \citet{parsons_et_al2016}, $\Omega_{\rm eff} = 0.74^{2}/0.24$ for an optimal fringe-rate
-filter and the PAPER primary beam. 
-\item $T_{\rm sys}$: The system temperature is set by:
-
-\begin{equation}
-\label{eq:sys}
-T_{\rm sys} = 180\Big(\frac{\nu}{0.18}\Big)^{-2.55} + T_{\rm rcvr},
-\end{equation}
-
-where $\nu$ are frequencies in GHz (\citealt{thompson_et_al2001}). We use a receiver temperature of $144$\,K, yielding $T_{\rm sys} = 431$\,K at $150$\,MHz. 
-This is lower than the $T_{\rm sys}$ of $500$\,K used in \citetalias{ali_et_al2015} because of several small miscalculation errors that were 
-identified\footnote{For example, there was a missing a square root in going from a variance to a standard deviation.}.
-\item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying two independent visibility measurements. In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
-\item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
-because we integrate incoherently over time. For PAPER-64, $N_{\rm lst} = 8$.
-\item $N_{\rm seps}$: The number of baseline separation types (where baselines of a unique separation type have the same orientation and length) averaged incoherently in a final power spectrum estimate.
-For the
-analysis in this paper, we only use one type of baseline (PAPER's 30\,m East/West baselines).
-However, both the updated limits in Kolopanis et al.
-(\textit{in prep.}) and the sensitivity prediction in Figure \ref{fig:sense_check} use three separation types ($N_{\rm seps}=3$) to match \citetalias{ali_et_al2015}.
-\item $t_{\rm int}$: Length of an independent integration of the data. It is crucial to adapt this number if filtering is applied along the time axis (i.e., a 
-fringe-rate filter). We compute the effective integration time of our fringe-rate filtered data by scaling the original integration time $t_{i}$
-using the following:
-\begin{equation}
-t_{\rm int} = t_{i} \frac{\int1 \, df}{\int w^{2}(f) \,df},
-\end{equation}
-where $t_{i}=43$ seconds, $t_{\rm int}$ is the fringe-rate filtered integration time, $w$ is the fringe-rate profile, and the integral is 
-taken over all fringe-rates. For PAPER-64, this number is $t_{\rm int} = 3857$\,s. 
-\item $N_{\rm days}$: The total number of days of data analyzed. In \citetalias{ali_et_al2015}, this number was set to $135$. However, because we 
-divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even" in order to avoid noise biases).
-Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
-$N_{\rm days}$. Our expression therefore becomes:
-\begin{equation}
-N_{\rm days} = \sqrt{\langle N_{i}^{2}\rangle} \sqrt{(N_{\rm datasets}^{2}-N_{\rm datasets})}
- %\frac{1}{N_{\rm days}} = \sqrt{\Big\langle\frac{1}{N_{i}^{2}} \Big\rangle_{i}},
- \end{equation}
-\noindent where $i$ indexes LST and frequency channel over all datasets (\citealt{jacobs_et_al2015}). For PAPER-64, our revised estimate of $N_{\rm days}$ is $\sim47$ 
-days.
-\item $N_{\rm bls}$: The number of baselines contributing to the sensitivity of a power spectrum estimate. In \citetalias{ali_et_al2015}, this number was 
-the total number of $30$\,m East/West baselines used in the analysis. However, using the total number of baselines ($N_{\rm bls\_total} = 51$) neglects 
-the fact that the \citetalias{ali_et_al2015} analysis averages baselines into groups for computational speed-up when cross-multiplying data. Our revised estimate for the parameter is:
-\begin{equation}
-N_{\rm bls} = \frac{N_{\rm bls\_total}}{N_{\rm gps}}\sqrt{\frac{N_{\rm gps}^{2}-N_{\rm gps}}{2}},
-\end{equation}
-\noindent where, in the \citetalias{ali_et_al2015} analysis, $N_{\rm gps} = 5$. Each baseline group averages down linearly as the number of baselines 
-entering the group ($N_{\rm bls\_total}/N_{\rm gps}$) and then as the square root of the number of cross-multiplied pairs \Big($\sqrt{\frac{N_{\rm gps}^{2} - 
-N_{\rm gps}}{2}}$\Big).
-A revised \citetalias{ali_et_al2015} analysis should therefore use $N_{\rm bls} \sim 32$ instead of $51$, and this change is taken into account in Figure \ref{fig:sense_check}.
-However, the analysis in this paper and in Kolopanis et al.
-(\textit{in prep.}) no longer averages baselines into groups ($N_{\rm gps} = 1$).
-For the subset of data presented in this paper, $N_{\rm bls} = 10$.
-\item $N_{\rm pols}$: The number of polarizations averaged together. For the case of Stokes I, $N_{\rm pols}=2$.
-\end{itemize}
-
-An additional factor of $\sqrt{2}$ is gained in sensitivity when folding together positive and negative $k$'s to form $\Delta^{2}(k)$.
-
-Our revised sensitivity estimate for the \citetalias{ali_et_al2015} analysis of PAPER-64 is shown in Figure \ref{fig:sense_check}. 
-Together, the revised parameters yield a decrease in sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\columnwidth]{plots/sense_check.pdf}
-	\caption{An updated prediction for the thermal noise level of PAPER-64 data (black) is shown in comparison to previously 
-published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
-\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:Error}, which when combined decreases our 
-sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
-	\label{fig:sense_check}
-\end{figure}
-
-To verify our thermal noise prediction, we form power spectra estimates using a pure noise simulation. We create Gaussian 
-random noise assuming a constant $T_{\rm rcvr}$ (translated into $T_{\rm sys}$ via Equation \eqref{eq:sys}) but accounting for the true $N_{\rm days}$ as determined 
-by LST sampling counts for each time and frequency in the LST-binned data. We convert $T_{\rm sys}$ into a root-mean-square variance statistic 
-using:
-
-\begin{equation}
-\label{eq:noise}
-T_{\rm rms} = \frac{T_{\rm sys}}{\sqrt{\Delta\nu \Delta t N_{\rm days} N_{\rm pols}}},
-\end{equation}
-
-\noindent where $\Delta\nu$ is the channel spacing, $\Delta t$ is the integration time, $N_{\rm days}$ is the number of daily counts for a 
-particular time and frequency that went into our LST-binned set, and $N_{\rm pols}$ is the number of polarizations ($2$ for Stokes 
-I). This temperature sets the variance of the Gaussian random noise.
-
-Power spectrum results for the noise simulation, which uses our full power spectrum pipeline, are shown in Figure 
-\ref{fig:ps_noise}.
-We highlight that the bootstrapped data (black and gray points, with $2\sigma$ error bars) and thermal noise prediction (solid green) show good agreement, as bootstrapping provides an accurate estimate of the noise variance.
-However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
-While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
-Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations.
-Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.4\textwidth]{plots/ps1_noise_add.pdf}
-	\includegraphics[width=0.4\textwidth]{plots/ps2_noise_add.pdf}
-	\caption{The power spectrum for a noise simulation that mimics the noise level of a subset of PAPER-64 data, where the solid red curve is the $2\sigma$ upper limit on the EoR signal estimated from our signal injection framework using $\widehat{\textbf{C}}_{\rm eff}$.
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters (calculated by Equation \eqref{eq:sense}) is in green.
-Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
-The vertical dashed black lines signify the horizon limit for this analysis using $30$\,m baselines.
-We highlight that the bootstrapped data points and thermal noise prediction show good agreement, while the limits from the full injection framework (red and blue) are inflated due to the additional inclusion of sample variance that comes from the injection simulations.}
-	\label{fig:ps_noise}
-\end{figure*}
-
-% CONCLUSION ---------------------------------------------------------------------------------
-
-\section{Conclusion}
-\label{sec:Con}
-
-Although current 21\,cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, 
-ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like 
-HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
-that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline and be able to accurately 
-and robustly calculate both power spectrum and theoretical errors.
-
-In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
-signal loss and error estimation, which can be summarized as follows:
-
-\begin{itemize}
-\item Substantial signal loss can result when weighting data using empirically estimated covariances due to couplings with the data realizations (Section 
-\ref{sec:SiglossOverview}). Loss of the 21\,cm signal is especially significant the fewer number of independent modes that
-exist in the data. Hence, there exists a trade-off between sensitivity driven 
-time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:siglossmethod}). However, a 
-signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for correlations between the data and signal which can be large and negative.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:Boot}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
-simple and accurate way of estimating errors.
-\end{itemize}
-
-As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, and accurately estimating thermal noise.
-Our revised PAPER-64 limits are presented in Kolopanis et al.
-(\textit{in prep.}), which supersede all previously published PAPER limits.
-Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
-(\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
-However, the main reasons for a previously underestimated limit (\citealt{ali_et_al2018}) and
-ways in which our new analysis differs can still be summarized by the following:
-
-\begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was underestimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
-covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
-\ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-Underestimated signal loss therefore represents the bulk of our revision.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
-Several other errors were also found regarding error estimation, though with smaller effects.
-\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:Error}). We note that our sensitivity prediction is revised by a factor less than our overall
-power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
-points.
-\end{itemize}
-
-The future of 21\,cm cosmology is exciting, as new experiments have sensitivities that expect to reach and surpass EoR levels, improved 
-foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
-instruments.
-On the power spectrum analysis side, robust signal loss simulations and precise error calculations will play critical roles in accurate 21\,cm results.
-With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
-
-% ACKNOWLEDGEMENTS ---------------------------------------------------------------------------------
-
-\section{Acknowledgements}
-CC would like to acknowledge the UC Berkeley Chancellor's Fellowship and National Science Foundation Graduate Research 
-Fellowship (Division of Graduate Education award 1106400). She would also like to thank Phil Bull, Bryna Hazelton, Miguel Morales, and Eric Switzer for helpful discussions. PAPER and HERA 
-are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would 
-also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively).
-AL acknowledges support for this work by NASA through Hubble Fellowship grant \#HST-HF2-51363.001-A awarded by the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., for NASA, under contract NAS5-26555.
-SAK is supported by the University of Pennsylvania School of Arts and Sciences Dissertation Completion Fellowship.
-JSD acknowledges NSF AAPF
-award 1701536.
-GB acknowledges support from the Royal Society and the Newton Fund under grant NA150184.
-This work is based on research supported in part by the National Research Foundation of South Africa (award 103424).
-We graciously thank SKA-SA for site infrastructure and observing support.
-\label{sec:Ack}
-
-% APPENDIX ---------------------------------------------------------------------------------
-
-%\color{blue}
-
-\begin{comment}
-
-\appendix
-\section{A toy model for inverse covariance weighting}
-\label{sec:icw_appendix}
-
-%AAAXXX
-
-In this Appendix, we focus on the optimal quadratic estimator, Equation \eqref{eq:OQE}, and mathematically illustrate its role in estimating the power spectrum of EoR.
-While there exists detailed literature about quadratic estimators in general (e.g., \citealt{liu_tegmark2011}; \citealt{trott_et_al2012}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}), here we focus on two simple cases in order to outline one situation where the estimator successfully suppresses contamination and one where it does not.
-By describing these two cases, we hope to clarify and motivate the desire to use OQE while also understanding its limitations.
-
-We specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
-We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
-\begin{equation}
-\Delta_i = \sigma_i + \upsilon_i
-\end{equation}
-with 
-\begin{equation}
-\langle \sigma_i \rangle = 0; \; \langle \sigma^2_i \rangle = s; \; {\rm and}~\langle \bm{\sigma \sigma}^T \rangle = s \mathbf{I}_{N \times N} \equiv \mathbf{S},
-\end{equation}
-where we wish to estimate $s$.  The contaminant in this first case has a similar structure (as the EoR) for its covariance, and is assumed uncorrelated with the signal
-\begin{equation}
-\label{eq:IdealToyModelCovariance}
-\langle \upsilon_i \rangle = 0; \; 
-\langle \upsilon^2_i \rangle = u; \; 
-\langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{I}_{N \times N} \equiv \mathbf{U}; {\rm and}~ 
-\langle \sigma_i \upsilon_j \rangle = 0.
-\end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \eqref{eq:OQE} is
-\begin{equation}
-\label{eq:IdealToyModelEstimator}
-\hat{s} = \frac{ \bm{\Delta^T \Delta}}{N} 
-\end{equation}
-and its expectation is
-\begin{equation}
-\langle \hat{s} \rangle = s + u.
-\end{equation}
-Thus, {\it when the covariance structure of the contaminant is identical to the signal} ($\PDeriv{\mathbf{S}}{s} = \PDeriv{\mathbf{U}}{u} =  \PDeriv{\C}{s}$), the information available to the quadratic portion of the estimator to distinguish between the two is degenerate, and knowledge only of $\C$ and $\PDeriv{\C}{s}$ is inadequate.
-In order to obtain an unbiased estimate of $s$, one must also use knowledge of $\mathbf{U}$.
-Indeed, computing the linear bias from Equation \eqref{eq:OQELinear}, one finds $b = u$.
-
-Now consider a case, chosen to be very similar to the toy model in \ref{sec:toymodel},  in which the data again have an additive contaminant, now given by
-\begin{equation}
-\Delta_i = \sigma_i + \upsilon m_i
-\end{equation}
-where the properties of $\sigma_i$ are as before, but now $\upsilon$ is a random variable and $m_i$ is a fixed function of $i$ with
-\begin{equation}
-\langle \upsilon \rangle = 0; \;
-\langle \upsilon^2 \rangle = u; \; 
- \langle \bm{\upsilon \upsilon}^T \rangle = u \mathbf{m m}^T \equiv \mathbf{U}; \;
- \mathbf{m}^T \mathbf{m} = 1; \; {\rm and}~ 
-\langle \sigma_i \upsilon \rangle = 0.
-\end{equation}
-Here $\mathbf{m}$ represents a mode which is correlated across many data points (i.e., we are assuming $\mathbf{U}$ need {\it not} be diagonal), with amplitude given by  $\upsilon$.
-The normalization of $\mathbf{m}$ is a matter of convention, and can be absorbed in the variance $u$; the choice above will be convenient for understanding the limiting case $u \gg s$.
-
-We can calculate the quadratic portion of the estimator explicitly by using the Sherman-Morrison identity to invert the covariance matrix.  Defining
-\begin{equation}
-\xi \equiv \frac{u/s}{1+u/s},
-\end{equation} 
-we have
-\begin{equation}
-\invC  =   \frac{1}{s} \left(\I - \xi \mathbf{m m}^T \right)
-\end{equation}
-and
-\begin{equation}
-\hat{s} = 
-%\half {\F}^{-1} \left(\bm \Delta^T \invC \PDeriv{\C}{s}  \invC \bm \Delta \right) = 
-\frac{ \bm \Delta^T  (\I +  (\xi^2 - 2 \xi)  \mathbf{m m}^T)  \bm \Delta}{N + \xi^2 - 2 \xi} 
-\end{equation}
-with expectation
-\begin{equation}
-\langle \hat{s} \rangle = 
-s + \frac{1 - 2 \xi + \xi^2}{N + - 2 \xi + \xi^2} u. 
-\end{equation}
-It is worth observing immediately that there is no multiplicative bias on $s$, and that the additive bias is strictly $< u/N$.
-
-An instructive limit is $u \gg s$, $\xi \to 1$, in which case the virtue of weighting by $\invC$ becomes clearer, as it becomes
-\begin{equation}
-\invC  = \frac{1}{s} \left(\I - \mathbf{m m}^T \right)
-\end{equation}
-where $\I - \mathbf{m m}^T$ is the projection operator, projecting out $\mathbf{m}$ from any vector it acts on, and further, the linear bias tends to 0 as $\xi \to 1$ (i.e., the projection is ``perfect'' and not ``undone'' by the Fisher matrix normalization).
-
-This is the ideal case for the inverse covariance weighting performed in the PAPER analysis, where removal of contamination with a known covariance can be suppressed by a kind of projection of the offending modes.
-But even in this case, it is worth pointing out that the estimator still has a linear bias for finite $u$.
-We have also assumed that the contaminating mode $\mathbf{m}$ is known perfectly; the next appendix takes up the case where the modes are estimated from the data.
-
-\color{black}
-
-%\appendix
-\section{A toy model for signal loss}
-\label{sec:sigloss_appendix}
-
-In this Appendix, we examine a toy model for signal loss.
-Our goal is to derive an analytic formula for power spectrum signal loss.
-While this model does not apply generally to all the scenarios presented in this paper, it provides some analytic intuition for how the coupling between data and an empirical covariance can result in signal loss.
-
-The minimum-variance quadratic estimator $\widehat{P}^\alpha$ for the $\alpha$th bandpower of the power spectrum is given by 
-\begin{equation}
-\widehat{P}^\alpha = \frac{1} {2 \F^{\alpha \alpha} }\x^t \C^{-1} \Q^{\alpha} \C^{-1} \x,
-\end{equation}
-where
-\begin{equation}
-F^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \right)
-\end{equation}
-is the $\alpha$th diagonal element of the Fisher matrix.
-For this section only, with no loss of generality, we assume that the data $\textbf{x}$ are real.
-We also assume for simplicity that $\mathbf{x}$ is the data from a single instant in time, so that it is of length $N_f$, where $N_f$ is the number of frequency channels.
-
-In our case, we do not have \emph{a priori} knowledge of the covariance matrix.
-Thus, we deviate from the true minimum-variance quadratic estimator and replace $\C$ with $\Chat$, its data-derived approximation.
-Our estimator then becomes
-\begin{equation}
-\label{eq:phatloss}
-\widehat{P}^\alpha_\textrm{loss} = \frac{1} {2 \widehat{\F}^{\alpha \alpha} }\x^t \Chat^{-1} \Q^{\alpha} \Chat^{-1} \x,
-\end{equation}
-where
-\begin{equation}
-\widehat{F}^{\alpha \alpha} \equiv \frac{1}{2} \textrm{tr} \left( \Chat^{-1} \Q^\alpha \Chat^{-1} \Q^\alpha \right),
-\end{equation}
-with the label ``loss" to foreshadow the fact that this will be an estimator with signal loss (i.e., a multiplicative bias of less than unity).
-We will now provide an explicit demonstration of this by modeling the estimated covariance as
-\begin{equation}
-\label{eq:ChatDef}
-\Chat = (1-\eta) \C + \eta \x \x^t,
-\end{equation}
-where $\eta$ is a parameter quantifying our success at estimating the true covariance matrix.
-If $\eta = 0$, our covariance estimate has perfectly modeled the true covariance and $\Chat = \C$.
-On the other hand, if $\eta =1$, then our covariance estimate is based purely on the one realization of the covariance that is our actual data, and we would expect a high level of overfitting and signal loss.
-
-Our strategy for computing the signal loss will be to insert Equation \eqref{eq:ChatDef} into Equation \eqref{eq:phatloss} and to express the resulting estimator $\widehat{P}^\alpha_\textrm{loss}$ in terms of $\widehat{P}^\alpha$.
-We begin by expressing $\Chat^{-1}$ in terms of $\C^{-1}$ using the Woodbury identity so that
-\begin{equation}
-\Chat^{-1} = \frac{\C^{-1}}{1-\eta} \left[ \I - \frac{\eta \x \x^t \C^{-1}}{1+ \eta (g-1)}\right],
-\end{equation}
-where we have defined $g \equiv \x^t \C^{-1} \x$. Inserting this into our Fisher estimate we have
-\begin{equation}
-\widehat{F}^{\alpha \alpha} = \frac{F^{\alpha \alpha}}{(1-\eta)^2} \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^{\alpha})^2}{F^{\alpha \alpha}}\right],
-\end{equation}
-where $h^\alpha \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \x $ and $h^{\alpha \alpha} \equiv \x^t \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1}\x $.
-Note that $g$, $h^\alpha$, and $h^{\alpha \alpha}$ are all random variables, since they depend on $\x$.
-Inserting these expressions into our estimator gives
-\begin{equation}
-\label{eq:phatlossexpanded}
-\widehat{P}^\alpha_\textrm{loss} = \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \frac{\eta g}{1+ \eta (g-1)}\right]^2  \left[ 1 -\frac{\eta }{1+ \eta (g-1)} \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}} + \frac{1}{2} \left( \frac{\eta }{1+ \eta (g-1)} \right)^2 \frac{(h^\alpha)^2}{F^{\alpha \alpha}}\right]^{-1}.
-\end{equation}
-Both for the purposes of analytical tractability and to provide intuition, we expand this expression to leading 
-order in $\eta$. This approximates the limiting case where the covariance $\Chat$ is close to the ideal and the 
-lossy covariance is a small perturbation.  The result is
-\begin{equation}
-\widehat{P}^\alpha_\textrm{loss} \approx \frac{1}{2} \frac{h^\alpha}{F^{\alpha \alpha}} \left[ 1 - \eta \left( g - \frac{h^{\alpha \alpha}}{F^{\alpha \alpha}}\right)\right].
-\end{equation}
-Taking the ensemble average of both sides and noting that the true power spectrum $P^\alpha$ is equal to $\langle h^\alpha \rangle / 2 F^{\alpha \alpha}$, we obtain
-\begin{equation}
-\langle \widehat{P}^\alpha_\textrm{loss} \rangle \approx (1- \eta N_f) P^\alpha + 4 \eta \frac{\rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha \C^{-1} \Q^\alpha )}{\left[ \rm{tr} (\C^{-1} \Q^\alpha \C^{-1} \Q^\alpha  ) \right]^2} \approx (1- \eta N_f) P^\alpha,
-\end{equation}
-where recall that $N_f$ is the length of $\x$, or the number of frequency channels.
-In the last step we dropped the final term, since it scales as $\eta P^\alpha$ (without the factor of $N$) and is therefore typically small compared to the terms that have been retained.
-
-Recalling that $P^\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss.
-This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations.
-This violates the assumptions implicit in the derivation of $F^{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{liu_tegmark2011}.
-The result is an improperly normalized---and thus lossy---power spectrum estimate.
-
-\section{Derivation of the Jeffreys Prior}
-\label{sec:jeffreys}
+\title{Derivation and Application of the Jeffreys Prior \\for Estimating Signal Loss in PAPER} 
+\author{Carina Cheng and the PAPER Collaboration}
+\maketitle
+\vspace{1cm}
 
 The Jeffreys prior is an objective, non-informative prior distribution for a parameter space using Bayesian probability (\citealt{jaynes1968}).
-For the signal injection framework outlined in Section \ref{sec:Practice}, we wish to compute the prior $p(P_{\rm in})$, or the probability density of the power spectrum of the EoR signal.
+For the signal injection framework outlined in Cheng et al.
+(\textit{submitted}), we wish to compute the prior $p(P_{\rm in})$, or the probability density of the power spectrum of the EoR signal.
 
@@
 \noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Combining Equations \eqref{eq:jeffreys}, \eqref{eq:logprob}, and \eqref{eq:prob} the Jeffreys prior simplifies to become:
+Using Equations \eqref{eq:prob} and \eqref{eq:logprob}, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} becomes:
 
-%\begin{eqnarray}
-%\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
-%&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
-%\end{eqnarray}
+%\begin{equation}
+%\label{eq:logprob_full}
+%\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
+%\end{equation}
 
-%Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
+%Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of %Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
+
+\begin{eqnarray}
+\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
+&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
+\end{eqnarray}
+
+Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
 Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
@@
 
-When we simulate our full injection framework as in Section \ref{sec:Practice}, we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
+When we simulate our full injection framework as in Cheng et al.
+(\textit{submitted}), we sample 50 $P_{\rm in}$ values that range from $\sim$ $10^{5}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$ to $\sim$ 10$^{11}$\,mK$^{2}$ ($h^{-1}$ Mpc)$^{3}$, and we note that the prior is set to zero outside those regions.
 For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-%An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
+An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
 
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
-%	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
+	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
 Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
 The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
-%	\label{fig:jeffreys1}
-%\end{figure}
+	\label{fig:jeffreys1}
+\end{figure}
 
-We show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
+We also show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
 Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.
@@
 
-\end{comment}
-
 \bibliographystyle{apj}

### 2018-10-09 PAPER.tex
small syntax edit in abstract

@@
 \begin{abstract}
-The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
+The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the birth of the first stars and 
 galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 

### 2018-11-01 PAPER_longversion.tex
updated references in accordance with ApJ style and compiled

--- 2018-10-08 PAPER.tex
@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
-\shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
+\shorttitle{Characterizing Signal Loss, Error, and Bias in the 21\,cm Reionization Power Spectrum}
 \shortauthors{Cheng et al.}
@@
 \begin{document}
-\title{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64}
+\title{Characterizing Signal Loss, Error, and Bias in the 21\,cm Reionization \\Power Spectrum: A Revised Study of PAPER-64}
 
@@
 galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
-EoR by tracing the 21\,cm line of neutral hydrogen.
-Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data.
-It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates.
-Specifically, with a statistical power spectrum detection in HERA's foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal.
-In this paper, we focus on signal loss associated with power spectrum estimation.
-We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C.
-Backer Precision Array for Probing the Epoch of Reionization (PAPER).
-In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
-Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for.
-We focus on a subset of PAPER-64 data in this paper; revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
-(\textit{in prep.}) and supersede results from previously published PAPER analyses.
+EoR by tracing the 21\,cm line of neutral hydrogen, a signal which is very faint and difficult to isolate. With a new generation 
+of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to 
+develop techniques that help maximize sensitivity while validating results. Additionally, it is imperative to understand the trade-offs 
+between different analysis methods and their effects on power spectrum estimates. In this paper, we focus on three major 
+themes --- signal loss, power spectrum error estimation, and bias in measurements. We describe techniques that affect 
+these themes using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array 
+for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of these themes have 
+led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64.
+While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al.
+(\textit{in prep.}) and supersede results from
+previously published PAPER analyses.
 \end{abstract}
@@
 
-In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
+In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using
 the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
@@
 instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}.
-A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results.
-More specifically, it is imperative to develop techniques that ensure
-the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method.
-In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation.
-This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis.
-We first approach this topic from a broad perspective, and then perform a detailed
+A clean measurement therefore requires an intimate understanding of the instrument and a rigorous study of data analysis choices.
+With continual progress being made
+in the field and HERA on the horizon, it is becoming increasingly important to understand how the methods we choose interact 
+with each other to affect power spectrum results. More specifically, it is imperative to develop techniques and tests that ensure 
+the accuracy and reliability of a potential EoR detection. In this paper, we discuss three topics (signal loss, error estimation, and bias) that are essential to investigate 
+for a robust 21\,cm power spectrum analysis. We also highlight four power spectrum techniques (fringe-rate filtering, weighting, bootstrapping, jackknife testing) and their trade-offs, potential 
+pitfalls, and connections to the themes. We first approach the themes from a broad perspective, and then perform a detailed 
 case study using data from the 64-element configuration of PAPER.
-In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al.
+In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a companion paper, Kolopanis et al.
 (\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.
 
-Finally, we also highlight several additional errors made in previous PAPER analyses, including those related to bootstrapping and error estimation.
-This paper accompanies the erratum of \citet{ali_et_al2018} and adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
+Finally, this paper adds to the growing foundations of lessons which have been documented, for example, in \citet{Paciga2013}, \citet{Patil2016}, and \citet{Jacobs2016}, by the GMRT, LOFAR, and MWA projects respectively.
 These lessons are imperative as the community as a whole moves towards higher sensitivities and potential EoR detections.
 
-This paper is organized into three main sections.
-In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
-In Section \ref{sec:CaseStudy}, we present a case study using data from the PAPER-64 array, highlighting key changes from the signal loss methods used in the published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which previously underestimated loss.
-In Section \ref{sec:OtherErrors}, we summarize additional lessons learned since \citetalias{ali_et_al2015} that have shaped our revised analysis.
-Finally, we conclude in Section \ref{sec:Con}.
-
-% SECTION 2 SIGLOSS TOY MODEL ---------------------------------------------------------------------------------
-%\color{blue}
-
-\section{Signal Loss Toy Models}
-\label{sec:SiglossOverview}
-% JEA - We never totally nail down what ``signal loss'' is ...
-
-Signal loss refers to attenuation of the target cosmological signal 
+This paper is organized into two main halves. In Section \ref{sec:Themes} we introduce the three themes of our focus, using 
+toy models to develop intuition for each one. In Section \ref{sec:CaseStudy} we present a case study into each theme using data 
+from the PAPER-64 array, highlighting key changes from the methods used in the previously published result in \citet{ali_et_al2015}, henceforth known as \citetalias{ali_et_al2015}, which have led to a
+revised PAPER-64 power spectrum result (Kolopanis et al. (\textit{in prep.})). We conclude in Section \ref{sec:Con}.
+
+% SECTION 2 INTRO ---------------------------------------------------------------------------------
+
+\section{Power Spectrum Themes and Techniques}
+\label{sec:Themes}
+
+There are many choices a 21\,cm data analyst must consider.
+%For PAPER, its grid configuration allows the use of many signal processing tricks to down-weight foregrounds without reference to a sky model.
+However, even with the advantage of being agnostic about the sky, many questions still remain.
+%, though the space is significantly constrained by 
+%the type of instrument being used.  The PAPER instrument in its grid configuration focuses most sensitivity on 
+%only a few baselines but imaging performance is poor. In this space, signal processing tricks which filter or 
+%down-weight foreground modes without reference to a sky model have the advantage of being agnostic about 
+%the sky. However, even within this problem sub-space, questions remain.
+How can time-ordered measurements be combined? How can the 
+variance of the data be estimated? In what way(s) can the data be weighted to suppress contaminated modes while not 
+destroying an EoR signal? How can a statistically significant detection of a signal be properly identified? Many common techniques, such as 
+averaging data, weighting, bootstrapping, and jackknife testing, address these issues but harbor additional trade-offs. For 
+example, an aggressive filtering method may succeed in eliminating interfering systematics but comes at the cost of losing 
+some EoR signal. A chosen weighting scheme may theoretically maximize sensitivity but fail to suppress foregrounds in practice.
+
+Though there are many data analysis choices, measuring the statistical 21\,cm power spectrum ultimately requires robust 
+methods for determining accurate confidence intervals and rigorous techniques to identify and control systematics.  In this 
+paper, we focus on three 21\,cm power spectrum themes that encapsulate this goal and discuss four techniques that interplay 
+with each other and impact the themes. We will give brief definitions now, and build intuition for each theme in the sections to 
+follow.
+
+%\begin{center}
+%Power Spectrum Themes
+%\end{center}
+
+%A deep understanding of the following three themes is essential for the accuracy and interpretation of a 21\,cm power spectrum result.
+Stemming from a re-analysis of PAPER-64 data, we believe these themes serve as an important checklist for a rigorous power spectrum analysis.
+\begin{itemize}
+\item \textbf{Signal Loss} (Section \ref{sec:SiglossOverview}): Signal loss refers to attenuation of the target \textit{cosmological} signal 
 in a power spectrum estimate.
@@
 Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.
-
-One type of signal loss can occur when weighting data by itself.
-Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others.
-For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
+\item \textbf{Error Estimation} (Section \ref{sec:ErrorOverview}): Confidence intervals on a 21\,cm power spectrum result 
+determine the difference between a detection and a null result, which have two very different implications.
+Additionally, accurate error estimation is crucial for the comparison of results to theoretical models.
+Errors can be
+estimated in a variety of ways, and we will discuss a few of them.
+\item \textbf{Bias} (Section \ref{sec:BiasOverview}): There are several possible sources of power offset in a visibility 
+measurement that can show up as a detection in a power spectrum, such as bias from noise and foregrounds. In particular, a 
+successful EoR detection would also imitate a bias. Proving that a bias is an EoR detection may be the most difficult challenge for future 21\,cm 
+analyses, as it is crucial to be able to distinguish a detection of foreground leakage, for example, from that of EoR. In this paper 
+we will highlight some sources of bias, discuss ways to mitigate their effects, and describe example tests that a true EoR detection must 
+pass.
+\end{itemize}
+
+%\begin{center}
+%Power Spectrum Techniques
+%\end{center}
+
+The following techniques each have advantages when it comes to maximizing sensitivity and understanding systematics in 
+data. However, some have limitations, and we will discuss circumstances in which there are trade-offs. We choose to focus on 
+these four techniques because they represent major steps in PAPER's power spectrum pipeline, with several of them also 
+being standard steps in general 21\,cm analyses.
+\begin{itemize}
+\item \textbf{Fringe-rate filtering:} Fringe-rate filtering is an averaging scheme for time-ordered data 
+(\citealt{parsons_et_al2016}). Broadly, a fringe-rate filter averages visibilities in time to produce a smaller number of more sensitive 
+independent samples. However, such a filter also affects the presence 
+of foregrounds and systematics. We explain the trade-offs of filtering in more detail in Section \ref{sec:toymodel_frf}.
+\item \textbf{Weighting:} A dataset can be weighted to emphasize certain features and minimize others. One particular flavor of 
+weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance 
+weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}).
 Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes.
 However, a challenge of inverse covariance
-weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss.
-In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
+weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two can have large impacts on signal loss.
+We investigate the impact of different types of weighting on signal loss in Section \ref{sec:SiglossOverview}.
+\item \textbf{Bootstrapping:} In addition to using theoretical models for covariance matrices and theoretical error estimation 
+methods, bootstrapping is one way to estimate errors. Namely, bootstrapping is a useful method for estimating errors of a dataset from 
+itself (\citealt{andrae2010}). By randomly drawing many subsamples of the data, we obtain a sense of its inherent variance, though there are subtleties to 
+consider such as the independence of values in a dataset. We explore this potential pitfall of bootstrapping in Section \ref{sec:ErrorOverview}.
+\item \textbf{Jackknife testing:} A resampling technique useful for estimating bias, jackknives can be taken along different 
+dimensions of a dataset to cross-validate results. In particular, null tests can be used to verify whether results are free of 
+systematics, as done with CO power spectra (\citealt{keating_et_al2016}) and CMB measurements (see e.g.
+\citealt{ade_et_al2008}; \citealt{chiang_et_al2010}; \citealt{bischoff_et_al2011}; \citealt{das_et_al2011b}; \citealt{araujo_et_al2012}; \citealt{crites_et_al2015}; \citealt{ade_et_al2016}; \citealt{ade_et_al2017}; \citealt{sherwin_et_al2017}).
+An EoR detection must pass both jackknife and null tests, which we highlight in Section \ref{sec:JackknifeOverview}.
+\end{itemize}
+
+In the next three subsections, we study each theme in depth, focusing on how power spectrum technique trade-offs affect each. 
+We use toy data models to develop intuition into why certain analysis choices may be appealing and discuss ways in which 
+they are limited. We highlight problems that can arise regarding each theme and offer suggestions to mitigate the issues. 
+Ultimately, we show that rigorous investigations into signal loss, error estimation, and bias must be performed for robust 21\,cm results.
+
+% SECTION 2 SIGLOSS ---------------------------------------------------------------------------------
+%\color{blue}
+
+\subsection{Signal Loss}
+\label{sec:SiglossOverview}
+% JEA - We never totally nail down what ``signal loss'' is ...
+
+Signal loss can arise in a variety of ways in an analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay domain filter, or deriving weights from data and applying them to itself.
+Here we focus on signal loss associated with
+% JEA - we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
+the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
 This loss was significantly 
 %applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
-underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.
+under-estimated in the \citetalias{ali_et_al2015} analysis.
 
@@
 
-\subsection{The Quadratic Estimator Method}
+\subsubsection{The Quadratic Estimator Method}
 \label{sec:QE}
@@
 
-We begin with an overview of the quadratic estimator (QE) formalism used for power spectrum estimation.
 The goal of power spectrum analysis is to produce an unbiased estimator of the EoR power spectrum in the presence of both noise and foreground emission.
@@
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
+We provide a brief summary of the optimal quadratic estimator and explain its advantages below.
 
@@
 %We begin with our 
-Suppose that the measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
+The measured visibilities for a single baseline in Jy are arranged as a data vector, $\textbf{x}$. It has length $N_{t} N_{f}$,
 % JEA - not sure this helps
@@
 
-Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminants in order to obtain an unbiased estimate of the power spectrum.
+Intuitively, the estimator must be capable of ``suppressing" or ``removing" the effects of contaminates in order to obtain an unbiased estimate of the power spectrum.
 By construction, the subtraction of the residual foreground and noise bias accomplishes this, removing any additive bias.
 However, the $\mathbf{C}^{-1}$ piece of Equation \eqref{eq:OQEQuadratic} also has the effect of suppressing residual foregrounds and noise, in both the additive bias and any contributions the residuals may have to the variance.
-
-More specifically, the effect of the weighting in Equation \eqref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \eqref{eq:OQELinear} is to subtract out the remaining bias.
+The way in which the optimal estimator accomplishes this is illustrated with a toy model in Appendix \ref{sec:icw_appendix}.
+In this appendix, we show that the effect of the weighting in Equation \ref{eq:OQEQuadratic} is to project out the modes of $\textbf{U}$ with a different covariance structure than $\mathbf{S}$ in the power spectrum estimate, and the effect of Equation \ref{eq:OQELinear} is to subtract out the remaining bias.
 Similar effects for a realistic model of the EoR and foregrounds are shown in \citet{liu_tegmark2011}.
-If the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
+
+The toy model in Appendix \ref{sec:icw_appendix} also illustrates that if the covariance structure of the contaminants is sufficiently different from the desired power spectrum, then the linear bias term may be expected to be quite small, and it is only necessary to know $\C$ and $\textbf{Q}^{\alpha}$, but not $\mathbf{U}$.
 Since the foregrounds are expected to be strongly correlated between frequencies whereas the EoR is not, we expect different covariance structures and therefore a small linear bias.
@@
 For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
-Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
+The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial P^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
 %with dimensions ($N_{f}$,$N_{f}$) --- as
@@
 \end{equation}
-is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.
-
+is a sensible estimate of the true power spectrum $\textbf{P}$.
 To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
@@
 where $W^{\alpha \beta}$ are elements of a window function matrix.
-Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
+Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit).
+If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias.
 However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate.
@@
 Beyond this, the data analyst has a choice for $
-\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal.
+\textbf{M}$. For simplicity throughout this paper we choose $\textbf{M}$ to be diagonal, although we discuss other cases for the analysis 
+of PAPER-64 data as explained in Section \ref{sec:Bias}.
 In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated.
@@
 \end{equation}
-assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
+assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
 amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
@@
 We note that we purposely take a thorough and pedagogical approach to describing the toy model examples given in the next few sections.
-The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:CaseStudy}.
+The specifics of how signal loss appears in PAPER's analysis is later described in Section \ref{sec:Sigloss}.
 
@@
 
-\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum.
-In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).
+\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness (the degeneracy) of the empirical eigenspectrum.
+In general, larger sample variances and flatter eigenspectra (more degeneracies) lead to more loss (Section \ref{sec:toymodel_frf}).
 
@@
 
-\subsection{Empirical Inverse Covariance Weighting}
+\subsubsection{Toy Model: Inverse Covariance Weighting}
 \label{sec:toymodel}
@@
 %First, 
-We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \eqref{eq:qhat} and \eqref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
+We compute the power spectrum of our toy model dataset $\textbf{x}$ using Equations \ref{eq:qhat} and \ref{eq:phat}, with $\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$.
 Figure \ref{fig:toy_sigloss12} shows the estimated covariances of our toy model datasets along with the $\widehat{\textbf{C}}^{-1}$ weighted data.
@@
 As discussed in Section \ref{sec:QE}, this behavior is {\it not} expected in the case that we were to use a true $\textbf{C}^{-1}$ weighting.
-Rather, we would obtain %the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in
-a nearly unbiased estimate of the power spectrum.
+Rather, we would obtain the behavior shown in the toy model in Appendix \ref{sec:icw_appendix}\footnote{Note that there the true covariance matrix is also the sum of a diagonal portion describing the signal, and a single mode describing the contaminant (similar to Figure \ref{fig:toy_sigloss12}).}, with suppression of the foreground mode resulting in a nearly unbiased estimate of the power spectrum.
 The key difference is that since $\widehat{\textbf{C}}$ is estimated from the data, its eigenvectors and eigenvalues are strongly coupled to the particular data realization that was used to compute it, and this coupling leads to loss.
 
-For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection; whether or not it is strongly correlated with the the actual data vector is irrelevant.
+For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.
 However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data.
 If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}.
-As described in Section \ref{sec:siglossmethod}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
-In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
+As shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.
+In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}
 
@@
 %then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes.
-Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
+Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e., only allowing over-fitting to occur for the first mode).
 then take the remaining covariance to be the identity matrix.  
@@
 
-Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization.
+Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization.
 There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section
@@
 
-\subsection{Fringe-Rate Filtering}
+\subsubsection{Toy Model: Fringe-Rate Filtering}
 \label{sec:toymodel_frf}
@@
 A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}).
-Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.
+Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes which are noise-like.
 
@@
 \citep{hartlap_et_al2007}. In our case, the empirically estimated covariances are used for estimating the power spectrum, and 
-as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
+as we discussed in the previous section (and will argue more thoroughly in Section \ref{sec:siglossmethod} and Appendix \ref{sec:sigloss_appendix}), couplings between these covariances and the data can lead to power spectrum estimates that are biased
 \emph{low}---which is precisely signal loss. In future work, it will be fruitful to investigate whether advanced techniques from the 
@@
 
-While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
-The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss.
+While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss.
+The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged, there will not be any signal loss.
 However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.
@@
 In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode.
-Even for the case of real PAPER data (Section \ref{sec:CaseStudy}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
+Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds.
 However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between modes that determines how quickly they converge, and hence how much signal loss can result.
@@
 	\caption{The convergence level, as defined by Equation \eqref{eq:converge}, of empirically estimated covariances of mock EoR signals with different numbers of independent samples.
-In red, the mock EoR signal is comprised entirely of independent samples (100 of them).
+In red, the mock EoR signal is comprised entirely of independent samples.
 Subsequent colors show time-averaged signals.
@@
 We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}).
-We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank.
+We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank.
 We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
@@
 green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum (red).
-%It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
+It is worth noting that a hybrid method, where the empirical covariance is calculated using the original dataset (not fringe-rate filtered) but applied to the filtered dataset, results in less loss than what is exhibited in Figure \ref{fig:toy_sigloss7} (though still lossy).
 This approach is worth exploring in future work; however in this paper we focus solely on ways to calculate and minimize loss associated with weighting a dataset based on itself (rather than weights associated with a dataset produced by a separate analysis).
@@
 
-\subsection{Other Weighting Options}
+\subsubsection{Toy Model: Other Weighting Options}
 \label{sec:otherweight}
@@
 left), we see that there is negligible signal loss.
-This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
+This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations).
 %This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
@@
 	\includegraphics[trim={0cm 0cm 0cm 0cm},clip,height=0.3\textwidth]{plots/toy_sigloss11.pdf}
-	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), EoR only (red), and the weighted FG + EoR dataset (green).
-We show four alternate weighting options that each minimize signal loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of $\widehat{\textbf{C}}$ (lower right).
-The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
+	\caption{Resulting power spectra estimates for our ``fringe-rate filtered" (time-averaged) toy model simulation --- foregrounds only (blue), 
+EoR only (red), and the weighted FG + EoR dataset (green). We show four alternate weighting options that each minimize signal 
+loss, including modeling the covariance matrix of EoR (upper left), regularizing $\widehat{\textbf{C}}$ by adding an identity matrix to 
+it (upper right), using only the first three eigenmodes of $\widehat{\textbf{C}}$ (lower left), and keeping only the diagonal elements of 
+$\widehat{\textbf{C}}$ (lower right). The first case (upper left) is not feasible in practice since we do not know $\textbf{C}_{\rm FG}$ and $\textbf{C}_{\rm EoR}$ like we do in the toy model.}
 	\label{fig:toy_sigloss8}
@@
 elements of the estimated covariance matrix more heavily than those off-diagonal.
-Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data and there is no loss.
+Since the identity component does not know anything about the data realization, it alters the covariance to be less coupled to the data.
 %Although there is negligible signal loss using this regularization, the small green peak at the fourth $k$-mode represents residual foregrounds that still exist since the shapes encoded in the off-diagonal frequency correlations of the covariance matrix were deemed not as prominent as the diagonal elements using this weighting scheme.
 
-The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss by only using the first three eigenmodes of the estimated covariance.
-Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this
+The third panel (bottom left) in Figure \ref{fig:toy_sigloss8} minimizes signal loss a different way --- 
+by only using the first three eigenmodes of the estimated covariance. Recalling that our toy model foregrounds can be described entirely by the zeroth eigenmode, this 
 method intentionally projects out the highest-valued modes only by replacing all but the three highest weights in the 
-eigenspectrum with $1$'s (equal weights).
-Again, avoiding the overfitting of EoR-dominated modes which are coupled to the data results in negligible signal loss.
-While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are foreground or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
+eigenspectrum with $1$'s (equal weights). Again, avoiding the over-fitting of EoR-dominated modes which are coupled to the data results in negligible signal loss. However, we do 
+not perfectly recover the shape of the EoR power spectrum because we lost information when ignoring the relative weights of most of the modes.
+While this case is illuminating for the toy model, in practice it is not obvious which eigenmodes are FG or EoR dominated (and they could be mixed as well), so determining which subset of modes to down-weight is not trivial.
 We experiment with this idea using PAPER data in Section \ref{sec:Weight}.
@@
 panel of Figure \ref{fig:toy_sigloss8}, we see that this method does not down-weight the foregrounds at all --- this regularization altered $\widehat{\textbf{C}}$ in a way where it is no longer coupled to \textit{any} of the empirically estimated eigenmodes, including the FG-dominated one.
-To understand this, we recall that our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations.
-Multiplying by
-the identity matrix, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
+For this toy model,
+our foregrounds are spread out in frequency and therefore have non-negligible frequency-frequency correlations. Multiplying by 
+the identity, element-wise, results in a diagonal matrix, meaning we do not have any correlation information. Because of this, we do a poor job 
 suppressing the foreground.
@@
 
-In summary, we have shown how signal loss is caused by weighting a dataset by itself, and in particular how estimated covariances can overfit EoR modes when they are coupled to data and not converged to their true forms.
-We have also seen that there are trade-offs between a chosen weighting method, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
-
-% SECTION 3 CASE STUDY ---------------------------------------------------------------------------------
-
-\section{Signal Loss in PAPER-64}
+In summary, we have a choice of how to weight 21\,cm data. Ideally, we want to down-weight bright foregrounds without 
+removing the underlying cosmological signal. However, there are trade-offs between the weighting method 
+used, its foreground-removal effectiveness, the number of independent samples in a dataset, and the amount of resulting signal loss.
+
+\color{black}
+
+% SECTION 2 ERROR ESTIMATION ---------------------------------------------------------------------------------
+
+\subsection{Error Estimation}
+\label{sec:ErrorOverview}
+
+Our second major 21\,cm power spectrum theme is error estimation, as we desire robust methods for determining accurate 
+confidence intervals for our measurements. Two popular ways of calculating errors on a power spectrum 
+measurement are calculating the variance of power spectrum results, and computing a theoretical error estimate based on an instrument's 
+system temperature and observational parameters. In a perfect world, both methods would match up. However, in practice the 
+two do not always agree due to a number of factors, including possible non-Gaussianities in the noise properties of our instruments and possible systematics in the data.
+
+A third option which acts as a middle ground between purely theoretical and purely empirical errors is using Gaussian error.
+This involves the assumption of Gaussianity, but allows the variance of the power spectrum estimator to be written as a function of the two-point estimator, or covariance.
+One could empirically calculate the covariance and then propagate it into an analytic expression to compute the errors, making this method fall somewhere between being fully empirical and fully modeled (see \citet{das_et_al2011a} for an example of its implementation).
+
+For PAPER's analysis, we choose a data-driven method of error estimation that does not rely on assumptions of Gaussianity. Namely, we compute error bars that have been derived from the inherent 
+variance of our measurements. A common technique used to do this is bootstrapping. For pedagogical purposes, we first define the technique of 
+bootstrapping and then illustrate one of its pitfalls through a toy model.
+
+Bootstrapping uses sampling with replacement to estimate a posterior distribution. For example, measurements (like power 
+spectra) can be made from different samples of data.
+Each of these measurements is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common
+between them. Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for 
+our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
+
+Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements). 
+Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection 
+of the $N$ measurements. Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn 
+from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap). Next we take 
+the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic 
+here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one). The error (on 
+the mean) is then computed as the standard deviation across all bootstraps.
+
+We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or 
+values, that comprise a bootstrap. In the toy models presented in this section, $N_{\rm boot}$ is typically large, and the standard 
+deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
+Typically $N$ is a straightforward value to set that just depends on the experiment.
+However, we will illustrate one case in which it is not simply the number of samples along the axis that is being re-sampled.
+More specifically, we will see that $N$ depends on sample independence and may not always be straightforward to approximate.
+
+For our toy model, suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean). 
+This could represent $1000$ power spectrum measurements, for which we are interested in its error. We predict that the error 
+on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
+
+We next form $500$ bootstraps ($N_{\rm boot} = 500$). To create each bootstrap, we draw $N$ samples, with replacement, of the 
+original data, and take the mean over the $N$ samples. The standard deviation over the $500$ bootstraps gives an error 
+estimate for our dataset. This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical 
+prediction (green).
+
+One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
+values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
+and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
+itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, under-estimates 
+errors. The use of a fringe-rate filter, which averages data in time to increase sensitivity, is one example which leads to a 
+reduction in the number of independent samples, creating a situation in which errors can be under-estimated. We will now show 
+this effect using our toy model.
+
+Going back to our toy model, we apply a sliding boxcar average to $10$ samples at a time, thus reducing the number of 
+independent data samples to $N/10 = 100$. Bootstrapping this time-averaged noise, using the same method as described 
+earlier (drawing $N=1000$ elements per bootstrap sample), under-estimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$). This occurs 
+because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times 
+in all bootstraps, leading to less variation between the bootstraps. In fact, the error derived from bootstrapping is a strong 
+function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both 
+under-estimate the error by drawing too many or over-estimate it by drawing too few. However, since we know that we have $100$ 
+independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction 
+as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
+
+This example highlights the importance of understanding how analysis techniques (such as fringe-rate filtering) can affect a 
+common statistical procedure like bootstrapping. Bootstrapping as a means of estimating power spectrum errors from real 
+fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task. For 
+example, computing the effective number of independent samples of fringe-rate filtered data is not as simple as counting the 
+number of averages performed.
+Down-sampling a time-averaged signal is straightforward using a boxcar average, but non-trivial with a more complicated convolution function that has long tails.
+Hence, we do not recommend bootstrapping unless the
+number of independent samples along the axis that is being re-sampled is well-determined.
+In Section \ref{sec:Boot}, we explain how we under-estimated errors in the \citetalias{ali_et_al2015} analysis of PAPER and how our bootstrapping procedure has now changed to avoid the over-sampling of correlated data.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
+	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
+sampling with replacement. The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ 
+elements (with replacement) from a length $1000$ array of a Gaussian random signal.
+The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
+They illustrate how errors can be under-estimated if
+drawing more elements than there are independent samples in the data. The estimated errors match up with the theoretical 
+prediction only at $N=100$.}
+	\label{fig:toy_error1}
+\end{figure}
+
+In summary, bootstrapping can be an effective and straightforward way to estimate errors of a dataset. However, we have 
+illustrated a situation in which bootstrapping can lead to under-estimated errors and therefore under-estimated power spectrum limits. We have shown that 
+bootstrapped error depends strongly on the number of elements drawn in a bootstrap sample. Estimated errors can drop to 
+arbitrarily small values when the number of elements drawn exceeds the effective number of independent elements. 
+%We have also shown a situation in which a bootstrapping method does not provide the most sensitive measurement possible. 
+While bootstrapping is convenient because it provides a way to estimate errors from the data itself, one must assess whether certain 
+analysis choices have compromised the method and whether a variation or an avoidance of traditional re-sampling could be preferred instead.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error2.png}
+%	\caption{The fraction of independent elements in one bootstrap sample as a function of the total number of elements in a 
+%dataset (i.e., if $4$ out of $5$ elements are independent, this would yield a fraction of $0.8$). A fraction of $1.0$ means that all 
+%elements in the bootstrap sample are independent, and therefore sensitivity is maximized (alternately, this axis can be thought 
+%of as power spectrum sensitivity, where sensitivity increases moving upwards along the y-axis).
+Two bootstrapping methods are shown here --- sampling all elements with replacement (gray) and sampling only the last element with replacement (black).
+The former fails to maximize sensitivity since some elements end up being repeated due to random sampling.}
+%The `outlier' points lying at a fraction of $1.0$ at the far left of the plot occur in the off-chance that the last spot in the sample happens to be the one missing element instead of a repeated element --- this is more likely to happen with a small total number of elements but also results in a more dramatically different fraction as compared to the case of a repeated element in the last spot, hence why these points appear like outliers.}
+%	\label{fig:toy_error2}
+%\end{figure}
+
+% SECTION 2 BIAS ---------------------------------------------------------------------------------
+
+\subsection{Bias}
+\label{sec:BiasOverview}
+
+In a 21\,cm power spectrum, detections could be the EoR signal, but they could also 
+%(and unfortunately more likely) 
+be attributed to other sources of bias. Connecting a detection to EoR as opposed to noise or foreground bias is a key challenge of 
+future 21\,cm data analyses \citep[e.g.][]{petrovic_and_oh2011}. In this section we will discuss possible sources of bias in a measurement, as well as techniques 
+that can help mitigate their effects. We will also present a series of tests in a pedagogical fashion which we suggest be used to 
+help evaluate deep limits and/or detections.
+
+\subsubsection{Foreground and Noise Bias}
+\label{sec:BiasTypes}
+
+In Section \ref{sec:SiglossOverview}, we discussed signal loss as a form of multiplicative bias to estimates of the signal.
+Foregrounds are another type of bias, but an additive instead of a multiplicative one.
+Foreground bias is perhaps one of the main factors limiting 21\,cm results, as foreground signals lie $\sim4$-$5$ orders of
+magnitude above the cosmological signal.
+Though there are many techniques proposed for removing foregrounds (see e.g.
+\citealt{vedantham_et_al2012}; \citealt{chapman_et_al2012}; \citealt{parsons_et_al2012a}; \citealt{parsons_et_al2012b}; \citealt{dillon_et_al2013a}; \citealt{wang_et_al2013}; \citealt{parsons_et_al2014}; \citealt{liu_et_al2014a}; \citealt{wolz_et_al2014}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2015}; \citealt{pober_et_al2016a}; \citealt{trott_et_al2016}), most
+experiments currently remain limited by residuals rather than noise, especially at low $k$.
+
+One common method to isolate and filter foregrounds is to exploit their behavior in $k$-space. For a particular 
+baseline length, there is a maximum delay imposed on sources attached to the sky, which corresponds to the light-crossing time between two 
+antennas in a baseline. For longer baselines, this value increases, producing what is known as ``the 
+wedge"
+\citep{datta_et_al2010, parsons_et_al2012b, vedantham_et_al2012, pober_et_al2013, thyagarajan_et_al2013, liu_et_al2014a, liu_et_al2014b, patil_et_al2017}. 
+The wedge describes a region in $k$-space contaminated by smooth spectrum foregrounds, bounded by baseline length (which is proportional to $k_{\perp}$) and delay (which is 
+proportional to $k_{\parallel}$). Properties of the wedge can be used to isolate and 
+%remove 
+avoid foregrounds, as done by \citetalias{ali_et_al2015}, 
+\citet{parsons_et_al2014}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{jacobs_et_al2015}, \citet{beardsley_et_al2016}, and \citet{trott_et_al2016}.
+
+Although smooth-spectrum foregrounds preferentially show up at low delay, or low $k$-modes, their isolation within the wedge is not perfect.
+In deep measurements, power spectrum measurements at $k_{\parallel}$ values beyond
+the delay associated with the length of a baseline are often still contaminated at a low level. This leakage, particularly at low $k$'s, can be attributed to 
+convolution kernels associated with Fourier-transforming visibilities into delay-space. In other words, smooth-spectrum 
+foregrounds appear as $\delta$-functions in delay-space, convolved by the Fourier transform of the source spectrum, the signal chain, and the 
+antenna response, all of which could smear out the foregrounds and cause leakage outside the wedge \citep[e.g.][]{ewall-wice_et_al2017, kerrigan_et_al2018}.
+
+There are analysis techniques to mitigate the effects of foreground leakage and prevent information from low $k's$ from 
+spreading to high $k$ values. For example, narrow window functions in delay-space can be used to minimize the leakage from a particular 
+$k$ value into other ones (\citealt{liu_et_al2014b}). In other words, one can construct an estimator using QE that forces a 
+window function to have a minimum response to low $k$ values. The window function used in \citetalias{ali_et_al2015} is constructed in such a way, 
+specifically to prevent foregrounds that live at low $k's$ from contaminating higher $k$-modes (see Section \ref{sec:Bias}).
+
+Determining the source of positive non-EoR detections at higher $k$'s is more difficult.
+In previous power spectrum results, these detections have been explained as instrumental systematics, particularly time-variable cross talk, RFI, cable reflections, and calibration errors (\citetalias{ali_et_al2015}; \citealt{parsons_et_al2014}; \citealt{dillon_et_al2014}; \citealt{beardsley_et_al2016}; \citealt{patil_et_al2017}).
+In the next section, we will present some tests that can help distinguish these excesses from that of EoR.
+
+In addition to foreground bias, noise can also be responsible for positive power spectrum detections if thermal noise is 
+multiplied by itself. Every 21\,cm visibility measurement contains thermal noise that is comprised of receiver and sky noise. 
+We expect this noise to be independent between antennas and thus we can beat it down (increase sensitivity) by integrating 
+longer, using more baselines, etc. However, the squaring of noise can occur when cross-multiplying visibilities, which is shown by 
+the two copies of $\textbf{x}$ in Equation \eqref{eq:qhat}. If both copies of $\textbf{x}$ come from the same baseline and time, it 
+can result in power spectrum measurements that are higher than those predicted by the thermal noise of the instrument. One 
+way to avoid this type of noise bias is to avoid cross-multiplying data from the same baselines or days. This ensures that the 
+two quantities that go into a measurement have separate noises that don't correlate with each other.
+We also note that if the noise level is known, this type of bias can be subtracted off, though this procedure is argued to be dangerous (\citealt{dillon_et_al2014}; \citealt{parsons_et_al2014}).
+
+Another type of noise bias can stem from the spurious cross-coupling of signals between antennas. This excess is known as 
+instrumental crosstalk and is an inadvertent correlation between two independent measurements via a coupled signal path. 
+Crosstalk varies on a time-scale much slower than the typical fringe-rates of 
+sources. Because it is slow-varying, crosstalk can be suppressed using time-averages or fringe-rate filters. However, there 
+remains a possibility that power spectrum detections that aren't the cosmological signal are caused by residual, low-level crosstalk which survived any 
+suppression techniques.
+
+\subsubsection{Jackknife Tests}
+\label{sec:JackknifeOverview}
+
+We now approach the difficult task of tracing excesses to foreground, noise, and EoR biases through a discussion of useful 
+jackknife tests. Again, we first approach this topic pedagogically as an introduction to the related PAPER discussion in Section 
+\ref{sec:Bias}.
+
+The jackknife is a resampling technique in which a statistic (i.e., power spectrum) is computed in subsets of the data (\citealt{quenouille1949}; \citealt{tukey1958}). These 
+subsets are then compared to reveal systematics. In this section we define two main tests --- the null test and the traditional 
+jackknife --- and explain how a power spectrum detection must pass each. We then highlight how these tests can be used to 
+help distinguish between different sources of bias.
+
+\begin{itemize}
+\item \textbf{Null Test}: A null test is a type of jackknife test that removes the astronomical signal from data in order to 
+investigate underlying systematics (see \citet{keating_et_al2016} for examples from intensity mapping that are closely related to our current application). For example, one can 
+divide data into two subsets by separating odd and even Julian dates, or the first half of the observing season from the second. 
+Subtracting the two removes signal that is common to both subsets, including foregrounds and the EoR signal. The resulting power 
+spectrum should be consistent with thermal noise estimates; if it is not, it suggests the presence of a systematic that differs 
+from one of the data subsets to the other (i.e., doesn't get subtracted perfectly). 
+\item \textbf{Traditional Jackknife}: In a broader sense, it is important to perform many jackknife tests in order to instill 
+confidence in a final result. A stable result must be steadfast throughout all jackknives no matter how the data is sliced. 
+Jackknives can be taken along several different axes --- for example, one could start with a full dataset, and compute a new 
+power spectrum every time as a day of data is removed, or a baseline is removed. This type of jackknife would reveal bias 
+present only at certain LSTs (such as a foreground source), for example, or misbehaving baselines.
+\end{itemize}
+
+While the null test hunts for deviations from thermal noise and the jackknife tests for deviations in subsamples, they are both 
+closely related. We can highlight the connection between the two using a toy model dataset.
+
+Suppose we have four independent measurements made along two different axes.
+As an example, we construct $\textbf{x}_{1a}$, $\textbf{x}_{1b}$, $\textbf{x}_{2a}$, and $\textbf{x}_{2b}$, where the numbers symbolize two different days of data and the letters represent two different baselines.
+Each of the
+measurements have dimensions of $100$ time integrations and $20$ frequency channels. They each have separate thermal 
+noises constructed as a Gaussian random signal for each, and identical EoR signals.
+
+To mimic the presence of a systematic, we add a toy sinusoid foreground, similar to the one used in 
+Section \ref{sec:toymodel}, to only $\textbf{x}_{2a}$ and $\textbf{x}_{2b}$. This represents a foreground signal 
+present in only the second day of data, but not the first. Mathematically, if  $\textbf{n}$ 
+is noise, $\textbf{e}$ is the EoR signal, and $\textbf{f}$ is the foreground signal, the four measurements can be written as:
+
+\begin{eqnarray}
+\label{eq:bias1}
+\textbf{x}_{1a} &=& \textbf{n}_{1a} + \textbf{e}  \\ 
+\textbf{x}_{1b} &=& \textbf{n}_{1b} + \textbf{e}  \\ 
+\textbf{x}_{2a} &=& \textbf{n}_{2a} + \textbf{e} + \textbf{f} \\ 
+\textbf{x}_{2b} &=& \textbf{n}_{2b} + \textbf{e} + \textbf{f}.
+\end{eqnarray}
+
+\noindent We now take a jackknife along the day-axis, forming separate power spectrum estimates for each day:
+
+\begin{eqnarray}
+\widehat{\textbf{P}}_{1} &\propto& \textbf{x}_{1a}\textbf{x}_{1b}^{\dagger} \\
+\widehat{\textbf{P}}_{2} &\propto& \textbf{x}_{2a}\textbf{x}_{2b}^{\dagger}.
+\end{eqnarray}
+
+We do not perform a time-average or apply a fringe-rate filter to this toy model, since we are interested only in what jackknife 
+tests can tell us about biases. For the same reason, we use a weighting matrix of $\textbf{I}$ for power spectrum estimation to 
+avoid signal loss.
+
+To construct a null test, we difference the two power spectra, with the result shown in Figure \ref{fig:toy_bias1} (black) along with the power spectrum of noise only (green).
+Subtracting the two estimates removes sky signal that should ideally be present in both jackknives.
+However, we see a clear difference between the null test and the power spectrum of
+noise. This signifies a non-EoR bias that is only present in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$, but not both.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias1.pdf}
+	\caption{A null jackknife test shown as the power spectrum difference between two measurements (black), compared to the power spectrum of noise alone (green).
+Because the null test is not consistent with noise, it suggests the
+presence of a systematic in either $\textbf{x}_{1}$ or $\textbf{x}_{2}$. Null tests of clean measurements should be consistent 
+with thermal noise.}
+	\label{fig:toy_bias1}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_bias2.pdf}
+	\caption{Power spectrum estimates for $\textbf{x}_{1}$ and $\textbf{x}_{2}$, two jackknives of the toy model. They suggest 
+the presence of a systematic in $\textbf{x}_{2}$ only, illustrating how jackknives can be used to tease out excesses. Clean 
+measurements should remain consistent despite the jackknife taken.}
+	\label{fig:toy_bias2}
+\end{figure}
+
+While the null test is useful for testing noise properties and the uniformity of a dataset, jackknives are useful in pinpointing 
+which data subsets are contaminated by biases and which are not; in our toy model we see that the bias exists only in $
+\textbf{x}_{2}$ (Figure \ref{fig:toy_bias2}). If foreground or noise biases exist in a dataset, jackknives can tease them out and 
+provide insight into possible sources. For example, if jackknives along the time-axis reveal a bias present at a certain LST, a 
+likely explanation would be excess foreground emission from a radio source in the sky at that time. A jackknife test involving 
+data before and after the application of a fringe-rate filter can reveal whether crosstalk noise bias is successfully suppressed 
+with the filter, or if similar-shaped detections in both power spectra suggest otherwise. There are many other jackknife axes of 
+which we will not go into detail here, including baseline, frequency, and polarization. Ultimately, an EoR detection should persist 
+through them all and a clean measurement should exhibit noise-like null spectra.
+
+In this section we have highlighted how null tests and jackknife tests are key for determining the nature of a power spectrum 
+detection. In Section \ref{sec:Bias} we perform some examples of these tests on PAPER-64 data in order to show that our 
+excesses are not EoR and to identify their likely cause.
+
+% SECTION 3  ---------------------------------------------------------------------------------
+
+\section{Demonstration in PAPER-64 Data}
 \label{sec:CaseStudy}
 
-We now turn to a detailed signal loss investigation using a subset of the PAPER-64 dataset from \citetalias{ali_et_al2015}.
-In the previous section we showed how signal loss arises when weighting data with empirically estimated covariances; in this section we highlight how the amount of this loss was underestimated in the previous analysis.
-Additionally, we illustrate how we have revised our analysis pipeline in light of our growing understandings.
+In the previous sections we have discussed three overarching 21\,cm power spectrum themes --- signal loss, error estimation, 
+and bias. Understanding the subtleties and trade-offs involved in each is necessary for an accurate and robust understanding of 
+a power spectrum result.
+
+We now apply these lessons to data from the PAPER experiment, using a subset of the PAPER-64 dataset from
+\citetalias{ali_et_al2015} in order to illustrate our revised analysis pipeline.
 
@@
 	\centering
-	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
+	\includegraphics[trim={0cm 3cm 0cm 3cm},width=\columnwidth]{plots/ant_layout_aspect.pdf}
 	\caption{The PAPER-64 antenna layout. We use only $10$ of the $30$ m East/West baselines for the analysis in this 
@@
 
-\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$. The need to revise this limit stems mostly from previously underestimated signal loss, which we 
-address in this section.
+\noindent of $(22.4$ mK$)^{2}$ in the range $0.15 < k < 0.5$\,$h$ Mpc$^{-1}$ at $z = 8.4$.
+The need to revise this limit stems mostly from previously under-estimated signal loss and under-estimated error bars, both of which we
+address in the following sections.
 
@@
 \citetalias{ali_et_al2015}, but Kolopanis et al.
-(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues that will be made clear later on).
+(\textit{in prep.}) uses the full dataset presented in \citetalias{ali_et_al2015} to revise the result and place limits on the EoR at multiple redshifts (using a straightforward and not lossy approach to avoid many of the issues presented in this paper).
 
@@
 This was chosen in order to increase the number of independent
-modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still underestimated. With the development of a new, 
+modes and reduce signal loss associated with the quadratic estimator, though as we will explain in the next section, this signal loss was still under-estimated. With the development of a new, 
 robust method for assessing signal loss, we choose to use the optimal filter in order to maximize sensitivity. This filter is 
@@
 Finally, we emphasize that the discussion that follows is solely focused on signal loss associated with empirical covariance weighting.
-As mentioned in Section \ref{sec:SiglossOverview}, there are a number of steps in our analysis pipeline which could lead to loss, including gain calibration, delay filtering, and fringe-rate filtering, which have been investigated at various levels of detail in \citet{parsons_et_al2014} and \citetalias{ali_et_al2015} but are clearly the subject of future work.
-Here we only focus on the most significant source of loss we have identified and note that other sources of loss may still be present (though at much smaller levels).
+As mentioned in Section \ref{sec:SiglossOverview}, there are several other ways the PAPER analysis pipeline can lead to loss, including through calibration and delay-filtering.
+We refer the reader to \citet{parsons_et_al2010} and \citetalias{ali_et_al2015} for discussions about these other types of signal loss, noting here that they are much less significant than the loss focused on in this paper.
 
@@
 
-We present our PAPER-64 signal loss investigation in three parts.
-We first give an overview of our signal injection framework which is used to estimate loss.
-In this framework (and as in \citetalias{ali_et_al2015}), we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
+% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
+
+\subsection{PAPER-64: Signal Loss}
+\label{sec:Sigloss}
+
+In Section \ref{sec:SiglossOverview}, we showed how signal loss arises when weighting data using information from the data itself.
+Here we describe a methodology for estimating the amount of signal loss caused by a particular power spectrum estimator when applied to a particular dataset.
+In this work, as in \citetalias{ali_et_al2015}, we inject simulated cosmological signals into our data and test the recovery of those signals (an approach also taken by \citet{masui_et_al2013}).
 As we will see, correlations between the injected signals and the data are significant complicating factors which were previously not taken into account.
-Next, we describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
-Finally, we build off of the previous section by experimenting with different regularization schemes on PAPER data in order to minimize loss.
-Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}.
-
-% SECTION 3 SIGNAL LOSS ---------------------------------------------------------------------------------
-
-\subsection{Signal Loss Methodology} 
+
+We present our PAPER-64 signal loss investigation in three parts: we first give an overview of our injection framework and illustrate how different power spectrum components affect loss.
+We next describe our methodology in practice and detail how we map our simulations into a posterior for the EoR signal.
+Finally, we build off of Section \ref{sec:SiglossOverview} by experimenting with different regularization schemes on PAPER data in order to minimize loss.
+Throughout each section, we also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously under-estimated losses.
+
+%The results of such an injection scheme can be interpreted in multiple ways.
+In this paper we describe two --- this section describes one and in Appendix \ref{sec:Pr_appendix} we present an alternate interpretation.
+These two methods yield very similar results, but fundamentally are answering subtly distinct questions.
+We also highlight major differences from the signal loss computation used in \citetalias{ali_et_al2015}, which previously underestimated losses.
+
+\subsubsection{Signal Loss Methodology} 
 \label{sec:siglossmethod}
-In short, our method for estimating signal loss consists of adding an EoR-like signal into visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
+In short, our method consists of adding an EoR-like signal into the visibility data and then measuring how much of this injected signal would be detectable given any attenuation of this signal by the (lossy) data analysis pipeline.
 To capture the full statistical likelihood of signal loss, one requires a quick way to generate many realizations of simulated 21\,cm signal visibilities.
@@
 likely due to the use of the fringe-rate filter as a simulator.
-However, this pipeline difference, while significant, is not the dominant reason why signal loss was underestimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
+However, this pipeline difference, while significant, is not the dominant reason why signal loss was under-estimated in \citetalias{ali_et_al2015} (the dominant reason is explained in the main text in Section \ref{sec:siglossmethod}).}
 
@@
 Again, we emphasize that in \citetalias{ali_et_al2015}, signal loss was computed by only looking at the second term in Equation \eqref{eq:crossterm} (green), which incorrectly implies no loss at the data-only power spectrum level.
-Ignoring the effect of the negative power from the cross-terms is the main reason for underestimating power spectrum limits in \citetalias{ali_et_al2015}.
+Ignoring the effect of the negative power from the cross-terms is the main reason for under-estimating power spectrum limits in \citetalias{ali_et_al2015}.
 
@@
 Again, it is this quantity that was used in \citetalias{ali_et_al2015} to calculate signal loss.
-However, without taking into account the cross-terms (the second term), we can substantially underestimate loss.
+However, without taking into account the cross-terms (the second term), we can substantially under-estimate loss.
 In short, this is because correlations between the data and injected EoR signal emerge as statistical noise that is added to the power spectrum estimate, decreasing the value of $\widehat{P}_{\rm out}$.
@@
 
-{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator is that it is not properly normalized.
+{\bf In general:} Another way to phrase the shortcoming of the empirical inverse covariance estimator (which is also discussed in Appendix \ref{sec:sigloss_appendix}) is that it is not properly normalized.
 Signal loss due to couplings between the data and its weightings arise because our unnormalized quadratic estimator from Equation \eqref{eq:qhat} ceases to be a quadratic quantity, and instead contains higher order powers of the data.
@@
 
-\subsection{Signal Loss in Practice}
+\subsubsection{Signal Loss in Practice}
 \label{sec:Practice}
@@
 We then have a choice for our prior, $p(P_{\rm in})$, and we choose to invoke a Jeffreys prior (\citealt{jaynes1968}) because it is a true uninformative prior.
-%For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
+For a derivation and more details about the Jeffreys prior used in our analysis, see Appendix \ref{sec:jeffreys}.
 
@@
 Shown for comparison is the lossy limit prior to signal loss estimation (dashed red).
-The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:Error}.
+The theoretical $2\sigma$ thermal noise level prediction based on observational parameters is in green, whose calculation is detailed in Section \ref{sec:PSSense}.
 Additionally, the power spectrum result for the uniform weighted case is shown in three different ways: power spectrum values (black and gray points as positive and negative values, respectively, with $2\sigma$ error bars from bootstrapping), the $2\sigma$ upper limit on the EoR signal using our full signal injection framework (solid blue), and the measured power spectrum values with $2\sigma$ thermal noise errors (gray shaded regions).
@@
 
-\subsection{Minimizing Signal Loss}
+\subsubsection{Minimizing Signal Loss}
 \label{sec:Weight}
@@
 We see in Figure \ref{fig:sigloss_modeloop} that this occurs roughly when
-only the $\sim3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting only slightly outperforms uniform weighting).
+only the $\sim2$-$3$ highest-valued eigenmodes are down-weighted and the rest are given equal weights (though for the case shown, weighting does not actually outperform uniform weighting).
 For a similar discussion on projecting out modes (zeroing out eigenmodes, rather than just ignoring their relative weightings as we do in this study), see \citet{switzer_et_al2013}.
@@
 We see that all three regularization schemes shown (solid red top panel, solid red bottom panel, black) perform similarly at
-their best (i.e., when $\sim3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
+their best (i.e., when $\sim2$-$3$ eigenmodes are down-weighted in the case of the top panel's solid red curve).
 However, for the remainder of this paper, we choose to use the weighting option of $\widehat{\textbf{C}} + 0.09 \,$Tr($\widehat{\textbf{C}})\textbf{I}$, or $\gamma = 0.09$, which we will denote as $\widehat{\textbf{C}}_{\rm eff}$.
@@
 It is important to note that our signal injection methodology for assessing loss makes the assumption that we know the true signal's strength and structure.
-Realistically, these details about the EoR signal are unknown and our signal loss framework is limited by our simulations.
+Realistically, these details about the EoR signal are unknown, and therefore our signal loss framework is subject to bias.
 Therefore, while this paper employs this methodology as an example of one way of estimating loss, Kolopanis et al.
@@
 data that is similar but not exactly the same as the data that is being down-weighted.
-Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
-
-In Section \ref{sec:CaseStudy}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
+Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.
+
+In Section \ref{sec:Sigloss}, we have detailed several aspects of signal loss in PAPER-64: how the loss arises, how it can be estimated from an injection framework, and ways it can be minimized.
 We again emphasize that these lessons learned about signal loss are largely responsible for shaping our revised analysis of PAPER data.
-In the remainder of this paper, we will transition to other aspects of our analysis that have been revised since \citetalias{ali_et_al2015}.
-
-% SECTION 4 OTHER ERRORS ---------------------------------------------------------------------------------
-
-\section{Additional PAPER-64 Revisions}
-\label{sec:OtherErrors}
-
-Underestimated signal loss is the main reason for the revision of the power spectrum limits from \citetalias{ali_et_al2015}.
-It is interesting to note that --- had all the other aspects of the original analysis been correct --- the underestimated limits may have been more easily caught.
-Unfortunately, two related power spectrum components, namely the error bars on the power spectrum data points and the theoretical noise prediction, were also calculated incorrectly.
-
-In this section, we summarize multiple inconsistencies and errors that have been found since the previous analysis in terms of error estimation.
-We first describe updated methods regarding bootstrapping, which determines the error bars on our limits.
-We then highlight an updated calculation for the theoretical noise sensitivity of PAPER-64 and illustrate how our revised calculation has been verified through simulations.
-
-\subsection{Bootstrapping}
-\label{sec:Boot}
-
-Broadly speaking, we desire robust methods for determining accurate 
-confidence intervals for our measurements. For PAPER's analysis, we choose a data-driven method of error estimation, computing error bars that have been derived from the inherent 
-variance of our measurements. A common technique used to do this is bootstrapping, which we first define below and then discuss its application to PAPER.
-
-Bootstrapping uses sampling with replacement to estimate a posterior distribution.
-For example, bootstrap measurements (of power spectra, for example) can be made from different random samples of data.
-Each of these bootstraps is a different realization drawn from some underlying distribution, and realizations are correlated with each other to a degree set by the fraction of sampled points that are held in common between them.
-Through the process of re-sampling and averaging along different axes of a dataset, such as along baselines or times, we can estimate error bars for our results which represent the underlying distribution of values that are allowed by our measurements (\citealt{efron_tibshirani1994}; \citealt{andrae2010}).
-
-%Suppose we have $N$ different measurements targeting the same quantity (for example, $N$ power spectrum measurements).
-Bootstrapping means that we form $N_{\rm boot}$ (often a large number) bootstraps, where each bootstrap is a random selection of the $N$ measurements.
-Bootstraps each have dimensions of $N$, and the values populated into each bootstrap are drawn from the original set of measurements with replacement (i.e., every $n^{th}$ slot in $N$ is filled randomly for each bootstrap).
-Next we take the mean of each bootstrap to collapse it from an array of length $N$ to a single number (we are interested in the mean statistic here, but any function of interest can be applied to each bootstrap as long as it's the same function for each one).
-The error (on the mean) is then computed as the standard deviation across all bootstraps.
-
-%We must be careful in distinguishing $N_{\rm boot}$, the number of bootstraps, from $N$, the number of samples, or elements, or values, that comprise a bootstrap.
-$N_{\rm boot}$ is typically large, and the standard deviation across bootstraps (the error we are computing) converges for large $N_{\rm boot}$.
-Typically $N$ is a straightforward value to set that just depends on the experiment (i.e., it is simply the number of samples along the axis that is being re-sampled).
-However, we will see that $N$ depends on sample independence, and it is this dependence that led to the underestimation of errors in \citetalias{ali_et_al2015}.
-
-%Let us first suppose we have a Gaussian random signal dataset of length $N=1000$ and unity variance (zero mean).
-This could represent $1000$ power spectrum measurements, for which we are interested in its error.
-We predict that the error on the mean should obey $1/\sqrt{N}$, where $N$ is the number of samples.
-
-%We next form $500$ bootstraps ($N_{\rm boot} = 500$).
-To create each bootstrap, we draw $N$ samples, with replacement, of the original data, and take the mean over the $N$ samples.
-The standard deviation over the $500$ bootstraps gives an error estimate for our dataset.
-This error is indicated by the gray star in Figure \ref{fig:toy_error1} and matches our theoretical prediction (green).
-
-One major caveat of bootstrapping arises when working with correlated data. If, for example, a dataset has many repeated 
-values inside it, this would be reflected in each bootstrap. The same value would be present multiple times within a bootstrap 
-and also be present between bootstraps, purely because it has a more likely chance of being drawn if there are repeats of 
-itself. Therefore, bootstrapping correlated data results in a smaller variation between bootstraps, and hence, underestimates 
-errors.
-
-%As a demonstration, we apply a sliding boxcar average to $10$ samples of our toy model at a time, thus reducing the number of independent data samples to $N/10 = 100$.
-Bootstrapping this time-averaged noise, using the same method as described earlier (drawing $N=1000$ elements per bootstrap sample), underestimates the error by a factor of $\sim3$ (black points in Figure \ref{fig:toy_error1}, at $N=1000$).
-This occurs because we are drawing more samples than independent ones available, and thus some samples are repeated multiple times in all bootstraps, leading to less variation between the bootstraps.
-In fact, the error derived from bootstrapping is a strong function of the number of elements that are drawn per bootstrap (Figure \ref{fig:toy_error1}, black points), and we can both underestimate the error by drawing too many or overestimate it by drawing too few.
-However, since we know that we have $100$ independent samples in this toy model, the error associated with drawing $N=100$ samples with replacement does match the theoretical prediction as expected (the black points cross the green line at $N=100$ in Figure \ref{fig:toy_error1}).
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[trim={0cm 0cm 0cm 0cm},width=\columnwidth]{plots/toy_error1.pdf}
-%	\caption{Error estimation from bootstrapping as a function of the number of elements drawn per bootstrap when 
-%sampling with replacement.
-The star represents the standard deviation of $N_{\rm boot}=500$ bootstraps, each created by drawing $1000$ elements (with replacement) from a length $1000$ array of a Gaussian random signal.
-The black points correspond to time-averaged data (correlated data) which has $100$ independent samples.
-They illustrate how errors can be underestimated if drawing more elements than there are independent samples in the data.
-The estimated errors match up with the theoretical prediction only at $N=100$.}
-%	\label{fig:toy_error1}
-%\end{figure}
-
-This is the precisely how errors were underestimated in PAPER-64.
-Because of fringe-rate filtering, which averages data in time to increase sensitivity, PAPER-64 data is correlated along the time axis.
-Hence, there are fewer independent samples after filtering, thus decreasing the variance of the bootstraps.
-
-More specifically, the PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
-spectrum that is a function of $k$ and time.
-In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis, and a total of $400$ bootstraps were created in this step, each comprised of randomly selected values sampled with replacement (i.e., each of these bootstraps contained the same number of values as the number of time integrations, which, at $\sim$
-$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
-Means were then taken of the values in each bootstrap. Finally, power 
-spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
-this previous analysis, the number of elements sampled per bootstrap greatly 
-exceeded the number of independent LST samples, underestimating errors. A random draw of $700$ 
-measurements from this dataset has many repeated values, and the variance between hundreds of these random 
-samples is smaller than the true underlying variance of the data.
-
-Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
-bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
-Power spectrum $2\sigma$ errors (computed from bootstrap variances) with and without this bootstrapping change for a fringe-rate filtered noise simulation are shown in Figure
-\ref{fig:data_errors} in black and gray, respectively. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
-shown in the figure, when more elements are drawn for each bootstrap than the number of 
-independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
-Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
-While Figure \ref{fig:data_errors} implies that errors, computed prior to our bootstrapping change (gray), are underestimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation (whose creation details are outlined in the next section), in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
-
-In addition to learning how sample independence affects bootstrapped errors, we have made three additional changes to our bootstrapping procedure since \citetalias{ali_et_al2015}, summarized here:
-
-\begin{itemize}
-
-\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
-In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
-On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
-This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
-
-\item{In \citetalias{ali_et_al2015}, individual baselines were divided into five independent groups, where no baselines were repeated in each group.
-Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
-This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
-Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
-
-\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
-More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
-The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
-
-\end{itemize}
-
-In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
-Bootstrapping can be an effective and straightforward way to estimate errors of a dataset, however, bootstrapping as a means of estimating power spectrum errors from real fringe-rate filtered data requires knowledge of the number of independent samples, which is not always a trivial task.
-We have thus avoided this issue by removing one of our bootstrap axes, as well as updated several other details of our procedure to ensure accurate re-sampling and error estimation.
-
-\begin{figure}
-	\centering
-	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
-	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
-methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
-effects of bootstrapping from signal loss.
-The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
-This underestimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
-We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
-We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
-	\label{fig:data_errors}
-\end{figure}
-
-\subsection{Theoretical Error Estimation}
+In the remainder of this paper, we will transition to other new aspects of our analysis, framed within the context of error estimation and (non-EoR) bias in PAPER-64.
+
+% SECTION 3 ERROR ESTIMATION ---------------------------------------------------------------------------------
+
+\subsection{PAPER-64: Error Estimation}
 \label{sec:Error}
 
-One useful way of cross-checking measured power spectrum values and errors is to compute a theoretical estimation of thermal noise based on observational parameters.
-Although a theoretical model often differs from true errors, it is helpful to understand the ideal case and the factors that affect its sensitivity.
-Upon re-analysis of PAPER-64, we have discovered that this estimate was also underestimated in previous analyses.
-
-To compute our theoretical noise estimate, we use an analytic sensitivity calculation.
-Through detailed studies using several independently generated noise simulations, what we found was that our simulations all agreed but were discrepant with the previous calculations.
-The analytic
-calculation is only an approximation and attempts to combine a large number of pieces of information in an approximate way; however, when re-considering some of the approximations, the differences were large enough (factors of $10$ in some cases) to warrant a
-careful investigation. What follows here is an 
+In this section we discuss the ways in which we estimate errors for PAPER-64 power spectra.
+We first walk through an expression for a theoretical error estimation (of thermal noise) based on observational parameters.
+Although a theoretical model often
+differs from true errors, it is helpful to understand the ideal case and the factors 
+that affect its sensitivity. Additionally, we build on the lessons learned about bootstrapping in Section \ref{sec:ErrorOverview} to 
+revise our bootstrapping method as applied to PAPER-64 data in order to compute accurate errors from the data itself.
+
+In particular, we highlight major changes in both our sensitivity calculation and bootstrapping method that differ from the \citetalias{ali_et_al2015} 
+analysis of PAPER-64. While we do not discuss the changes within the context of PAPER-32, it is worth noting that the power 
+spectrum results in \citet{parsons_et_al2014} are affected by the same issues.
+
+\subsubsection{Theoretical Error Estimation}
+\label{sec:PSSense}
+
+Re-analysis of the PAPER-64 data included a detailed study using several independently generated noise simulations. What we 
+found was that these simulations all agreed but were discrepant with the previous analytic sensitivity calculations. The analytic 
+calculation is only an approximation; however, the differences were large enough (factors of $10$ in some cases) to warrant a 
+careful investigation. The analytic calculation attempts to combine a large number of pieces of information in an approximate 
+way, and when re-considering some of the approximations, we have found there to be large effects. What follows here is an 
 accounting of the differences which have been discovered.
-We note that our theoretical error estimate, which is plotted as the solid green curve in many of the previous power spectrum plots in this paper, is computed with these changes accounted for.
+Our revised theoretical error estimation, which is plotted as the solid green curve in many of the previous power spectrum plots, is computed with these changes accounted for.
 
@@
 \item $\sqrt{2}$: This factor in the denominator of the sensitivity equation comes from taking the real part of the power spectrum 
-estimates after cross-multiplying two independent visibility measurements. In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
+estimates after cross-multiplying independent ``even" and ``odd" visibility measurements (this cross-multiplication is done principally to avoid a noise bias).
+In \citetalias{ali_et_al2015}, a factor of $2$ was mistakenly used.
 \item $N_{\rm lst}$: The number of independent LST bins that go into a power spectrum estimation. The sensitivity scales as the square root 
@@
 divide our data in half (to form ``even" and ``odd" datasets, or $N_{\rm datasets} = 2$), this number should reflect the number of days in each individual dataset instead of the total.
-Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even" in order to avoid noise biases).
+Additionally, this number should be adjusted to reflect the actual number of cross-multiplications that occur between datasets (``even" with ``odd" and ``odd" with ``even", but not ``odd" with ``odd" or ``even" with ``even", for reasons explained in Section \ref{sec:MitBias}).
 Finally, because our LST coverage is not $100\%$ complete (it doesn't overlap for every single day), we incorporate a root-mean-square statistic in computing a realistic value of
@@
 published sensitivity limits (gray), both computed for the parameters and methods used in \citetalias{ali_et_al2015}. Major factors that contribute to the discrepancy are $
-\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:Error}, which when combined decreases our 
+\Omega_{\rm eff}$, $N_{\rm days}$ and $N_{\rm bls}$, as in Equation \eqref{eq:sense} and described in Section \ref{sec:PSSense}, which when combined decreases our 
 sensitivity (higher noise floor) by a factor of $\sim7$ in mK$^{2}$.}
@@
 However, the limits from the full signal loss framework (weighted and unweighted in red and blue, respectively) are inflated, likely due to the additional inclusion of sample variance that comes from the EoR simulations.
-While the noise simulation provides an important indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
-Additionally, we recommend that future work investigate possible error correlations between baseline pairs and any interaction effects between signal and noise that may effect error calculations.
-Because of these reasons, we therefore interpret our noise prediction as the sensitivity floor for our measurements.
+While the noise simulation provides an indicator about the accuracy of our theoretical noise calculation, we note that the calculation did not take into account additional sources of error associated with earlier analysis steps (for example, \citet{trott_wayth_2017} show how calibration specifically can add errors to visibilities).
+We therefore interpret our noise prediction as the sensitivity floor for our measurements.
 
@@
 
+\subsubsection{Bootstrapping}
+\label{sec:Boot}
+
+We bootstrap PAPER-64 power spectra in order to determine confidence intervals for our results. In this section, we highlight 
+four specific changes in the way we estimate errors since \citetalias{ali_et_al2015}, the first of which builds off of the lesson we have learned previously about bootstrapping independent samples.
+
+\begin{itemize}
+
+\item{As discussed in Section \ref{sec:ErrorOverview}, bootstrapping is only a valid way of estimating errors if a dataset is comprised 
+of independent samples, or the number of independent samples is well known. The PAPER-64 pipeline outputs $20$ bootstraps (over baselines), each a $2$-dimensional power 
+spectrum that is a function of $k$ and time.
+
+In \citetalias{ali_et_al2015}, a second round of bootstrapping occurred over the time axis. A total of $400$ bootstraps were created in this step 
+($N_{\rm boot} = 400$), each comprised of randomly selected values sampled with replacement along the time axis. More 
+specifically, each of these bootstraps contained the same number of values as the number of time integrations (which, at $\sim$
+$700$, greatly exceeds the approximate number of independent samples after fringe-rate filtering).
+Means were then taken of the values in each bootstrap. Finally, power 
+spectrum limits were computed by taking the mean and standard deviation over all the bootstraps. We emphasize again that in 
+this previous analysis, the number of elements sampled per bootstrap greatly 
+exceeded the number of independent LST samples, under-estimating errors. A random draw of $700$ 
+measurements from this dataset has many repeated values, and the variance between hundreds ($N_{\rm boot}$) of these random 
+samples is smaller than the true underlying variance of the data.
+
+Given our new understanding of the sensitivity of bootstraps to the number of elements sampled, we have removed the second 
+bootstrapping step along time entirely and now simply bootstrap over the baseline axis.
+Power spectrum $2\sigma$ errors (computed from bootstrap variances) with this bootstrapping change for fringe-rate filtered noise are shown in Figure
+\ref{fig:data_errors}. The estimates are uniformly weighted in order to disentangle the effects of bootstrapping from signal loss. As 
+shown in the figure, when more elements are drawn for each bootstrap than the number of 
+independent samples (by over-sampling elements along the time axis), repeated values begin to crop up and the apparent variation between bootstraps drops, resulting in limits (gray) below the predicted noise level (green).
+Using the revised bootstrapping method, where bootstrapping only occurs over the baseline axis, the limits (black) are shown to agree with the analytic prediction for noise.
+While Figure \ref{fig:data_errors} implies that errors are under-estimated by a factor of $\sim$ $5$ in mK$^{2}$ for the noise simulation, in practice this factor is lower for the case of real data (a factor of $\sim$ $3$ in mK$^{2}$ instead), possibly due to the data being less correlated in time than the fringe-rate filtered noise in the simulation.
+}%Figure \ref{fig:data_errors} implies that power spectrum upper limits were originally under-estimated by a factor of $\sim$ $5$ in mK$^{2}$.
+
+\item{A second change to our bootstrapping procedure is that we now bootstrap over baseline cross-products, instead of the baselines themselves.
+In the previous analysis, baselines were bootstrapped prior to forming cross power spectra, and using this particular ordering of operations (bootstrapping, then cross-multiplication) yields variances that have been found to disagree with predicted errors from bootstrapping using simulations.
+On the contrary, bootstrapping over cross power spectra ensures that we are estimating the variance of our quantity of interest (i.e., the power spectrum).
+This change, while fundamental in retaining the integrity of the bootstrapping method in general, alters the resulting power spectrum errors by factors of $<2$ in practice.}
+
+\item{In \citetalias{ali_et_al2015}, individual baselines were divided into $5$ independent groups, where no baselines were repeated in each group.
+Then, baselines within each group were averaged together, and the groups were cross-multiplied to form power spectra.
+This grouping method was used to reduce computational time, however upon closer examination it has been found that the initial grouping introduces an element of randomness into the final measurements --- more specifically, the power spectrum value fluctuates depending on how baselines are assigned into their initial groups.
+Our new approach removes this element of randomness at the cost of computational expense, as we now perform all baseline cross-products.}
+
+\item{Finally, the last change from the \citetalias{ali_et_al2015} method is that our power spectrum points (previously computed as the mean of all bootstraps), are now computed as the power spectrum estimate resulting from not bootstrapping at all.
+More specifically, we compute one estimate without sampling, and this estimate is propagated through our signal loss computation (this estimate is $\widehat{\textbf{P}}_{x}$).
+The difference between taking the mean of the bootstrapped values and using the estimate from the no-bootstrapping case is small, but doing the latter ensures that we are forming results that reflect the estimate preferred by all our data.}
+
+\end{itemize}
+
+In summary, we have learned several lessons regarding bootstrapping and have revised our analysis procedure in order to determine error bars that correctly reflect the variance in our power spectrum estimates.
+Additionally, we have carried out substantial testing with these changes in place to verify that the computed errors for our noise simulations are accurate and agree with thermal noise predictions.
+
+\begin{figure}
+	\centering
+	\includegraphics[trim={0.3cm 0cm 0.3cm 0.3cm},width=\columnwidth]{plots/noise_errors.pdf}
+	\caption{$2\sigma$ power spectrum errors (from bootstrap variances) for a noise simulation (computed via Equation \eqref{eq:noise} using PAPER-64 observing parameters) using two different bootstrapping
+methods. The noise is fringe-rate filtered and a weighting matrix of $\textbf{I}$ (uniform-weighted) is used in order to disentangle the 
+effects of bootstrapping from signal loss.
+The bootstrapping method used in \citetalias{ali_et_al2015} is shown in gray, where bootstrapping occurs along both the baseline and time axes.
+This under-estimates errors by sampling more values than independent ones in the dataset (fringe-rate filtering reduces the number of independent samples along time).
+We use the method illustrated by the black curve in our updated analysis, where bootstrapping only occurs along the baseline axis.
+We find that these revised limits agree with the $2\sigma$ analytic prediction for noise (green).}
+	\label{fig:data_errors}
+\end{figure}
+
+% SECTION 3 BIAS ---------------------------------------------------------------------------------
+
+\subsection{PAPER-64: Bias}
+\label{sec:Bias}
+
+In Section \ref{sec:BiasOverview} we highlighted some common sources of bias that can show up as power spectrum 
+detections and imitate an EoR signal. We discussed the importance of using jackknife and null tests for instilling confidence in an EoR 
+detection, as well as for identifying other sources of biases. Here we demonstrate methods used by PAPER-64 to mitigate 
+foreground and noise bias and we perform null tests in order to characterize the stability and implications of our results.
+
+\subsubsection{Mitigating Bias}
+\label{sec:MitBias}
+
+We briefly discuss one way we mitigate foreground leakage in a power spectrum estimate, and two ways we 
+suppress noise biases. These methods are not novel to this analysis but here we frame them in the context of minimizing false 
+(non-EoR) detections.
+
+Tailoring window functions is one way to suppress foreground biases (similar discussions to the following one are in \citet{liu_et_al2014b} and \citetalias{ali_et_al2015}).
+As alluded to in Section \ref{sec:SiglossOverview}, we
+have a choice for the normalization matrix $\textbf{M}$ in Equation \eqref{eq:phat}. For the analysis of PAPER-64 data, we 
+compute $\textbf{M}$ using the matrix $\textbf{G}$ (which would be the Fisher matrix if $\textbf{R} \equiv \textbf{C}^{-1}$), defined as:
+
+\begin{equation}
+\textbf{G}^{\alpha\beta} = \frac{1}{2} \text{tr} [\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{Q}^{\beta} ]
+\end{equation}
+
+\noindent where $\textbf{R}$ is the data-weighting matrix and $\alpha$ and $\beta$ are wavebands in $k_{\parallel}$. We take 
+the Cholesky decomposition of $\textbf{G}$, decomposing it into two lower triangular matrices (which is possible since $\textbf{G}$ is Hermitian):
+
+\begin{equation}
+\textbf{G} = \textbf{LL}^{\dagger}.
+\end{equation}
+
+\noindent Next, we construct $\textbf{M}$:
+
+\begin{equation}
+\textbf{M} = \textbf{DL}^{-1}
+\end{equation}
+
+\noindent where $\textbf{D}$ is a diagonal matrix. In doing so, our window function, defined as $\textbf{W} = \textbf{MG}$ (see Equation \eqref{eq:Wpplusbias}), 
+becomes
+
+\begin{equation}
+\textbf{W} = \textbf{DL}^{\dagger}.
+\end{equation}
+
+\noindent Because of the nature of the lower triangular matrix, this window function has the property of preventing the leakage 
+of foreground power from low-$k$ to high-$k$ modes. Specifically, we order the elements in $\textbf{G}$ in such a way so that 
+power can leak from high-$k$ modes to low-$k$ modes, but not vice versa.
+Since most foreground power shows up at low-$k$'s, this method ensures a window function that retains clean, noise-dominated measurements while minimizing the
+contamination of foreground bias. This tailored window function was used in the \citetalias{ali_et_al2015} analysis, however throughout this paper, we use a diagonal $\textbf{M}$ for simplicity.
+
+In addition to mitigating foreground bias at high-$k$'s, two other sources of bias that we actively suppress in the PAPER-64 
+analysis are noise bias associated with the squaring of thermal noise and noise bias from crosstalk. In order to avoid the 
+former, we filter out certain cross-multiplications when forming $\widehat{q}$ in Equation \eqref{eq:qhat}. Namely, the PAPER-64 
+dataset is divided into two halves: even Julian dates and odd Julian dates. Our data vectors are then $\textbf{x}_{even, 1}$ for 
+the ``even" dataset and baseline $1$, $\textbf{x}_{odd, 1}$ for the ``odd" dataset and baseline $1$, etc. We only form 
+$\widehat{q}$ when the two copies of $\textbf{x}$ come from different groups and baselines, never multiplying ``baseline 1" with ``baseline 1", for 
+example, in order to prevent the squaring of the same thermal noise.
+
+To mitigate crosstalk bias, which appears as a static bias in time, we apply a fringe-rate filter that suppresses fringe-rates of 
+zero. Figure \ref{fig:frp} shows that the filter response is zero for such static signals. The effect of filtering out zero fringe-rates 
+on power spectrum results is shown in \citetalias{ali_et_al2015}. Most notably, even without accounting for signal loss, the crosstalk bias at all $k$'s is very strong compared to the removed case.
+
+\subsubsection{Jackknife/Null Tests}
+
+As shown in Figure \ref{fig:ps1_data}, our illustrative PAPER-64 power spectrum shows biases above the predicted noise level, particularly at low-$k$ values.
+As discussed in Section \ref{sec:BiasTypes}, this bias is
+most likely attributable to foreground leakage. %The cause for biases at higher $k$-values is more difficult to pinpoint.
+
+Here we perform three null tests on PAPER-64 data that aim to isolate systematics in the data and verify 
+that our biases are not attributable to EoR.
+Similar to in Section \ref{sec:JackknifeOverview}, we take jackknives along different axes of the dataset to produce multiple power spectra.
+We then difference them (i.e., the null test) to tease out excess variances.
+
+The three results are shown in Figure \ref{fig:null}.
+Each test displays the differenced power spectrum between two halves of a jackknife, where the plotted points are the differenced power spectrum values, and the plotted errors are the bootstrapped errors of the two dataset halves added in quadrature.
+The expected thermal noise level (gray shaded regions) is the thermal noise of each dataset added in quadrature as well.
+Constructing the tests as such ensures that we are probing whether the variances of each dataset differ by an amount consistent with the thermal noise.
+We use uniform weightings for all tests.
+
+We take jackknives along three different axes:
+
+\begin{itemize}
+%\item Original Data (black): This is identical to the unweighted, revised PAPER-64 power spectrum in Figure \ref{fig:ps1_data} (one baseline type only) with weighting matrix $\textbf{I}$.
+There are clear detections at low $k$'s.
+\item Baselines: We split our dataset into two halves, where each contains half of the total baselines used in the 
+analysis. No baselines are repeated between the two datasets.
+\item Sidereal Hour: We split our dataset into two halves based on LST, namely the first half (LSTs 0.5-4.5 hours) and second half (LSTs 
+4.5-8.6 hours).
+\item Day: We split our dataset into even and odd Julian dates.
+We form power spectra for each separately, allowing the cross-multiplication of ``even" with ``even", for example, for this null test only.
+If the same sky signal is in both the ``even" and ``odd" datasets, we expect it to cancel out.
+%However, allowing these cross-multiplications can in practice introduce a low level noise bias...
+\end{itemize}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.47\textwidth]{plots/null_bls.pdf}
+	\includegraphics[width=0.47\textwidth]{plots/null_lsts.pdf}
+	\includegraphics[width=0.47\textwidth]{plots/null_eo.pdf}
+	\caption{Differenced power spectrum results (with $2\sigma$ bootstrapped errors) for three null tests, where a jackknife is taken along the baseline axis (top left), LST axis (top right), and even/odd Julian date axis (bottom).
+The results shown are unweighted (no signal loss), where the power spectrum values plotted are computed from the difference between two power spectra produced on either side of the jackknife axis.
+The gray shaded region in each plot is the estimated $2\sigma$ theoretical noise limit given the parameters of each test.
+We find that there are no significant systematics for $k > \pm 0.2$\,$h$ Mpc$^{-1}$ for all three tests.
+However, we find that all tests exhibit an extra variance at $k$-values near the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$), likely due to foreground-noise coupling terms when foregrounds are brightest.
+Additionally, we find that the LST null test is not fully consistent with zero, implying a bias that is LST dependent and likely caused by varying foregrounds.}
+	\label{fig:null}
+\end{figure*}
+
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=1\textwidth]{plots/null_zoom.png}
+%	\caption{Power spectrum results for three null tests using $\widehat{\textbf{C}}_{\rm eff}$, compared to the analytically estimated 
+%$2\sigma$ error (gray shaded region). For each of the tests, we take a jackknife along a different axis of the dataset - along Julian days (separating 
+%even and odd days; blue), along baselines (green), and along LST (magenta). We expect the sky signal to disappear for a `passing' null test.
+%We find that the baselines (green) and even/odd (blue) tests are consistent with noise, and that the dominant source of the biases in our power spectrum are likely caused by variation of foregrounds in LST (due to the magenta result being the most inconsistent with noise)}
+%	\label{fig:null}
+%\end{figure*}
+
+In investigating Figure \ref{fig:null}, we focus on three main possibilities --- whether the data points and error bars are consistent with thermal noise (``passing"), whether the error bars are consistent with zero but not consistent with thermal noise (``passing but has an additional variance"), or whether the error bars are not consistent with zero at all (``failing").
+We examine each case in the context of our results below.
+
+Firstly, all three null tests display data points that lie within the thermal noise gray band for $k > \pm 0.25$\,$h$ Mpc$^{-1}$.
+In addition, all three null tests show error bars consistent with the thermal noise level for those same $k$'s.
+This implies that the two jackknife halves do not differ by an amount greater than the thermal noise (i.e., the baselines making up the two jackknives either do not contain bias, or contain similar amounts of bias; we suspect it is the former though more thorough jackknives along this axis are needed to make this conclusion).
+We deem these as ``passing" null tests for the specific jackknives taken (again, dividing up the data in a different way along the same axes may not yield the same results, so more thorough testing is needed to be sure).
+
+The second null test possibility (error bars consistent with zero but not with thermal noise) is displayed by the $k$-values just outside the horizon ($k\sim\pm 0.1$\,$h$ Mpc$^{-1}$) for all three tests.
+This indicates an additive noise component that is increasing our errors.
+More specifically, although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
+This is because cross-multiplications produce four additive terms --- a signal-squared term (where ``signal" includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+When differencing two power spectra (each with their own four terms), we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
+While the cross-terms have a mathematical expectation value of zero, in practice we are limited by our number of samples ($90$ cross-products for this analysis times $\sim$ $8$ independent LST samples).
+Combined with the fact that the foregrounds are so bright, the finite ensemble of the couplings can introduce extra variance that varies with foreground strength.
+It is therefore not surprising that this effect is largest at $k$-values just outside the horizon, where we expect foregrounds to be brightest post-delay filtering.
+
+Lastly, a third null test result is an error bar not consistent with zero.
+This is the case for the LST null test at $k\sim-0.1$\,$h$ Mpc$^{-1}$ and $k\sim0.15$\,$h$ Mpc$^{-1}$, as well as the even/odd test at $k\sim0.2$\,$h$ Mpc$^{-1}$ and $k\sim0.25$\,$h$ Mpc$^{-1}$.
+In such a case, the two jackknife halves differ by an amount greater than the thermal noise (i.e., the data point is not in the thermal noise band), yet they are each constrained tightly by individual error bars that when combined, are not consistent with zero.
+This result implies that there exists a low level bias that is LST-dependent and Julian date-dependent.
+The former is likely caused by residual foregrounds that vary in LST, and it is not surprising that this type of bias occurs near the horizon limit.
+The latter requires further investigation that we leave to future work.
+
+%Most importantly, a clean detection of EoR would have passed all three tests, which is clearly not what we see.
+
+%We also note that all three tests, whether biased or unbiased, result in power spectrum errors that are slightly larger than the estimated thermal noise (gray band) at high-$k$.
+This indicates an additive noise component that is increasing our errors (while not affecting whether they pass through zero or not).
+
+%There are a couple possible explanations for this.
+Although we expect each cross-multiplication that is used in power spectrum estimation to have independent noise, there is still the possibility of a noise-foreground coupling term that can introduce power.
+This is because cross-multiplications produce four additive terms --- a signal-squared term (where signal includes both foregrounds and EoR), two cross-terms between the signal and noise, and one noise-only term.
+When differencing two power spectra, we expect the signal-only term to subtract out for a ``passing" null test, and we expect the noise-only terms to be consistent with thermal noise.
+The cross-terms, however, can introduce extra variance that would vary with foreground strength, therefore being consistent with the shape of our results.
+One additional explanation, specifically for the slightly large error bars seen at high $k$'s, could simply be that our estimate of the thermal noise is too low, as all three tests seem to imply a larger, but consistent, estimate in this high-$k$ regime.
+Regardless of a potentially larger thermal noise prediction, however, the large error bars near the horizon limit still signify the presence of excess variance in our data.
+
+In this section we have presented the first jackknife and null tests from the PAPER experiment.
+Unsurprisingly, they imply that our measurements are biased by foregrounds, and not the EoR signal (a clean detection of EoR would have passed all three tests).
+While simple, these tests outline a framework that can be used by future measurements.
+The 21\,cm community is beginning to recognize the importance of these types of tests (\citealt{pober_et_al2016b}) in characterizing power spectra at the EoR level, and it is clear that future results will require more substantial and thorough investigations of this nature.
+
+%, and that the even/odd test is consistent with noise given the $2\sigma$ expectations (nearly $95\%$ of the error bars are passing through zero).
+We additionally note that the error bars for the baselines test (green) are especially small --- this is because the signal is effectively cancelled out prior to cross-multiplication (when forming baseline groups).
+
+%The null test in LST is much more illuminating.
+Because of the large variable error bars, many of which do not include zero, this suggests that the primary systematic driving our power spectrum points and errors to be outside the
+%estimated error region is LST-dependent, and therefore likely to be residual foregrounds.
+In other words, the fact that several magenta power spectrum points, as well as their error bars, are outside the estimated error region implies that $t_{1}$ and
+%$t_{2}$ differ by an amount greater than thermal noise and they do not effectively cancel out the sky signal during cross-multiplication.
+We also note that the LST null test is biased high, consistent with the interpretation that our positive power spectrum detections in Figure \ref{fig:ps1_data} are those of foregrounds.
+
+%We do not investigate the detailed nature of the residual foregrounds in this paper, though one could imagine performing many 
+%similar null tests with a sliding window of $t_{1}$'s and $t_{2}$'s. This would illuminate the particular LST range that introduces 
+%the foreground bias (or whether the bias is constant in LST), and could potentially be traced to an individual bright radio source. 
+%This type of detailed analysis will be critical at EoR sensitivities; however, for our current analysis we are not surprised that the main source of
+%bias we see comes from foregrounds. % in regions where we expect leakage.
+
 % CONCLUSION ---------------------------------------------------------------------------------
@@
 HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown 
-that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline and be able to accurately 
-and robustly calculate both power spectrum and theoretical errors.
+that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately 
+and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife 
+and null tests.
 
 In particular, in this paper we have investigated the subtleties and tradeoffs of common 21\,cm power spectrum techniques on 
-signal loss and error estimation, which can be summarized as follows:
+signal loss, error estimation, and bias, which can be summarized as follows:
 
@@
 time-averaging techniques such as fringe-rate filtering and signal loss when using empirically estimated covariances. 
-\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:siglossmethod}). However, a 
-signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can underestimate loss by 
-failing to account for correlations between the data and signal which can be large and negative.
-\item Errors that are estimated via bootstrapping can be underestimated if samples in the dataset are significantly correlated 
-(Section \ref{sec:Boot}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
+\item Signal injection and recovery simulations can be used to quantify signal loss (Section \ref{sec:Sigloss}). However, a 
+signal-only simulation (i.e., comparing a uniformly weighted vs. weighted power spectrum of EoR only) can under-estimate loss by 
+failing to account for correlations between the data and signal which can be large and negative (Section \ref{sec:siglossmethod}).
+\item Errors that are estimated via bootstrapping can be under-estimated if samples in the dataset are significantly correlated 
+(Section \ref{sec:ErrorOverview}). However, if the number of independent samples in a dataset is well-determined, bootstrapping is a 
 simple and accurate way of estimating errors.
+\item Meaningful null tests are vital to validate an EoR detection (Section \ref{sec:JackknifeOverview}). Similarly, performing 
+jackknife tests along multiple axes of a dataset is necessary for confidence in an EoR detection and can also be used to tease 
+out systematics.
 \end{itemize}
@@
 As a consequence of our investigations, we have also used a subset of PAPER-64 data to make a new power spectrum analysis.
-This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, and accurately estimating thermal noise.
+This serves as an illustrative example of using a signal injection framework, correctly computing errors via bootstrapping, accurately estimating thermal noise, and implementing jackknife tests.
 Our revised PAPER-64 limits are presented in Kolopanis et al.
@@
 Because of the many challenges associated with signal loss and its estimation as described in this paper, Kolopanis et al.
-(\textit{in prep.}) use a straightforward power spectrum estimation approach that is not lossy.
-However, the main reasons for a previously underestimated limit (\citealt{ali_et_al2018}) and
+(\textit{in prep.}) uses a straightforward power spectrum estimation approach that is not lossy.
+However, the main reasons for a previously under-estimated limit and
 ways in which our new analysis differs can still be summarized by the following:
@@
 \begin{itemize}
-\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was underestimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
+\item Signal loss, previously found to be $<2\%$ in \citetalias{ali_et_al2015}, was under-estimated by a factor of $>$$1000$ for the case of empirically estimated inverse 
 covariance weighting. Using a regularized covariance weighting method can minimize loss (Section 
 \ref{sec:Weight}), however, because a regularized weighting method is not as aggressive as the former, it produces limits that are still higher than the lossy empirical inverse covariance limits.
-Underestimated signal loss therefore represents the bulk of our revision.
-\item Power spectrum errors, originally computed by bootstrapping, were underestimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
+Under-estimated signal loss therefore represents the bulk of our revision.
+\item Power spectrum errors, originally computed by bootstrapping, were under-estimated for the data by a factor of $\sim2$ in mK due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering (Section \ref{sec:Boot}).
 Several other errors were also found regarding error estimation, though with smaller effects.
 \item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a 
-decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:Error}). We note that our sensitivity prediction is revised by a factor less than our overall
+decrease in predicted sensitivity level by a factor of $\sim3$ in mK (Section \ref{sec:PSSense}). We note that our sensitivity prediction is revised by a factor less than our overall
 power spectrum result, implying that if taken at face value, the theoretical prediction for noise in \citetalias{ali_et_al2015} was too high for its data 
@@
 foreground mitigation and removal strategies are being developed, and simulations are being designed to better understand 
-instruments.
-On the power spectrum analysis side, robust signal loss simulations and precise error calculations will play critical roles in accurate 21\,cm results.
+instruments. On the power spectrum analysis side, robust signal loss simulations, precise error calculations, and 
+comprehensive jackknife tests will play critical roles in accurate 21\,cm results.
 With strong foundations being established now, it is safe to say that we can expect to learn much about reionization and our early Universe in the coming years.
@@
 
-\begin{comment}
-
 \appendix
@@
 
-We specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
+In our toy model, we specifically choose toy models where the data covariance is diagonal, as indeed we expect the EoR signal to be.
 We assume we have $N$ data points $\Delta_i$ which are the sum of a desired signal $\sigma_i$ and an undesired contaminant $\upsilon_i$
@@
 \end{equation}
-With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \eqref{eq:OQE} is
+With the covariance matrix given by $\C = \mathbf{S} + \mathbf{U}$, the estimator for $s$ using only the quadratic part of Equation \ref{eq:OQE} is
 \begin{equation}
@@
 \noindent where $\sigma$ is the standard deviation of $\widehat{P}_{\rm out}$ and $\bar y$ is the mean of $\widehat{P}_{\rm out}$, and they are both functions of $P_{\rm in}$.
-Combining Equations \eqref{eq:jeffreys}, \eqref{eq:logprob}, and \eqref{eq:prob} the Jeffreys prior simplifies to become:
-
-%\begin{eqnarray}
-%\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
-%&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
-%\end{eqnarray}
-
-%Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
+Using Equations \eqref{eq:prob} and \eqref{eq:logprob}, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} becomes:
+
+%\begin{equation}
+%\label{eq:logprob_full}
+%\mathcal{L} = -\, log \, \sqrt{2\pi} - log\, \sigma - \frac{1}{2}\Big(\frac{y-\bar y}{\sigma}\Big)^{2}. 
+%\end{equation}
+
+%Next, the quantity inside the expectation value of Equation \eqref{eq:jeffreys} can be computed by taking the derivative of %Equation \eqref{eq:logprob_full} with respect to $P_{\rm in}$, or $x$:
+
+\begin{eqnarray}
+\Big(\frac{\partial \mathcal{L}}{\partial x} \Big)^{2} &=& \frac{1}{\sigma^{2}}\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} -  \Big(\frac{2(y-\bar y)}{\sigma^{3}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} - \Big(\frac{2(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2} \nonumber \\
+&+& \Big(\frac{(y-\bar y)^{2}}{\sigma^{4}}\Big)\Big(\frac{\partial \bar y}{\partial x}\Big)^{2} + \Big(\frac{2(y-\bar y)^{3}}{\sigma^{5}}\Big)\frac{\partial \sigma}{\partial x}\frac{\partial \bar y}{\partial x} + \Big(\frac{(y-\bar y)^{4}}{\sigma^{6}}\Big)\Big(\frac{\partial \sigma}{\partial x}\Big)^{2}.
+\end{eqnarray}
+
+Taking the expectation value then removes all terms with odd powers of $(y - \bar y)$ because those Gaussian moments evaluate to zero.
 Additionally, the second moment can be simplified since $\langle (y - \bar y)^{2} \rangle = \sigma^{2}$ and the fourth moment can be simplified since $\langle (y - \bar y)^{4} \rangle = 3\sigma^{4}$.
@@
 For the injections that we do sample, we can simply fit analytic functions to the mean and standard deviations of $\widehat{P}_{\rm out}$ ($\bar y$ and $\sigma$) as functions of $P_{\rm in}$.
-%An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
-%	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
+An example of the typical shape of these functions for the PAPER-64 analysis is shown in Figure \ref{fig:jeffreys1}, though in practice we fit solutions for every $k$-value and simulation independently.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\columnwidth]{plots/jeffrey_fits.pdf}
+	\caption{An illustrative example (for the PAPER-64 analysis using uniform weighting and $k=0.393$\,$h$ Mpc$^{-1}$) of how the mean of $P_{\rm out}$ (left) and standard deviation of $P_{\rm out}$ (right) behave as a function of $P_{\rm in}$.
 Polynomials are fit to each (red) to describe how $\bar y$ and $\sigma$ evolve with $x$ (injection level), respectively, for the computation of the Jeffreys prior as defined in Equation \eqref{eq:jeffreys_final}.
 The polynomial fits for this example are $y = (-5.1 \times 10^{-15})x^{2} + x + (1.5 \times 10^{7})$ and $y = (5.0 \times 10^{-13})x^{2} + 0.2 x + 10^{7}$ for $\bar y$ and $\sigma$, respectively.}
-%	\label{fig:jeffreys1}
-%\end{figure}
-
-We show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
+	\label{fig:jeffreys1}
+\end{figure}
+
+We also show the typical shape of the Jeffreys prior used in our analysis in Figure \ref{fig:jeffreys2}, as computed by Equation \eqref{eq:jeffreys_final}.
 Most noticeably, it is not constant with $P_{\rm in}$, meaning a uniform prior, which is often used for simplicity, is informative in our application.
@@
 
+%------------------------------- commented below---------------------------------------
+\begin{comment}
+\section{Simplified Loss Correction}
+\label{sec:Pr_appendix}
+One of the main difficulties in defining a signal loss procedure is in the interpretation of the injection procedure `output'.
+The method described in Section \ref{sec:Sigloss} relies on several assumptions which required justification including the assumption that the number of samples is large enough to treat sample variance as a first order purturbation on the ideal covariance matrix instead of the dominant effect we know it is.
+\acl{I'm not sure the previous sentence was fair.
+Again, the appendix is a motivating example.
+Carina's numerical computations do not rely on the derivation.} However it is possible to ask a slightly different question and with less math still get roughly the same answer.
+
+In the main text we made an estimate of the signal loss effecting only the injected EoR by supposing that the lossy injected signal was the difference between the injected and not injected cases: $\widehat{P}_{\rm out} = \widehat{\textbf{P}}_{r} - \widehat{\textbf{P}}_{x}$.
+Suppose that we rephrase the question we are asking to: ``At what point would an injected signal be detectable at significant levels?".
+\acl{Can we justify better why this is the right question?
+In particular, why is the detection of an injected signal the right thing to look at?
+After all, the universe doesn't do any signal injections.
+I think to justify that signal injections are the right thing to consider in the first place, one requires some sort of correspondence between equations analogous to Equation \eqref{eq:Deriv1} and \eqref{eq:Deriv2}.} Instead of disentangling the part of the output power spectrum dominated by the injected signal we can simply use $\widehat{\textbf{P}}_{r}$, the weighted power spectrum of the data plus injected signal.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
+\caption{The distribution of $\widehat{\textbf{P}}_{r}$ values for a 
+given injection level P$_{\rm in}$.
+The $\widehat{\textbf{P}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal.
+It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}).
+We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right).
+The dotted black
+diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{P}}_{x}$, the data distribution.
+At low injection, $\widehat{\textbf{P}}_{r}$ converges to the data level.
+}
+\label{fig:Pr_vs_Pin}
+\end{figure}
+
+This question is phrased visually in Figure \ref{fig:Pr_vs_Pin}.
+In the 2D space relating total $\widehat{\textbf{P}}_r$ to injected $P_{\rm in}$, very small injected levels begin at the level equivalent of no injection (i.e., data only) and very large levels are dominated by the injected signal.
+It is the transition zone, where the injected signal amplitude is similar to the data level (and thus subject to cross-correlations in both the covariance and in the power spectrum calculation) that we search for the point at which an injected signal would be clearly detected.
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=.5\textwidth]{plots/method2_prob_vs_pinj.png}
+\caption{The probability that an injected signal of level P$_{\rm inj}$
+is observable at a 2$\sigma$ level above the value of $\widehat{\textbf{P}}_{x}$ (data).
+The different colors represent different $k$ values. We choose a probability of $95\%$ for our signal loss estimated power spectrum.}
+\label{fig:Prob_vs_Pin}
+\end{figure}
+
+One difference in this method from the one in the main text is that we are exclusively asking about signals detectable \emph{above} the level of the observed data.
+Thus it is explicitly limited to placing an upper limit, even if in some $k$-modes one has actual detections above the noise.
+This might be seen as more conservative, however, a similar assumption has already been made when choosing to down-weight the data using itself.
+In such a down-weighting step, one has assumed that significant excess power is associated with a foreground residual.
+We note that a high SNR detection will require a different method.
+
+Formally we can express our test as: ``What is the $P_{\rm in}$ such that the power spectrum of ``data + 
+injected eor" ($\widehat{P}_{e+x}$) is detectable above the power spectrum of the data itself ($\widehat{P}_x$. 
+In other words, what is $e$ such that,
+\begin{equation}
+\widehat{\textbf{P}}_{e+x} > \widehat{\textbf{P}}_{x},
+\end{equation}  
+?''  Of course, both sides of this equation are actually a distribution of values associated with data variance and injected model variance.
+One way to interpret this test for the two distributions is to compute the probability that the two distributions are not (i.e., the null test) the same.
+ \acl{I'm confused a little by this equation. I would've thought that the right thing to do would be to first compute $x_0$, given implicitly by
+ \begin{equation}
+ \int_{-\infty}^{x_0}\Prob(\widehat{\textbf{P}}_x) dx = \Lambda,
+ \end{equation}
+ where $\Lambda$ is the appropriate number for $2\sigma$.
+That tells us what $x$ would be needed for us to thing that it was an outlier result without there being an extra $e$ in the data.
+Then we ask how often we get such an outlier result by computing
+  \begin{equation}
+ \int_{x_0}^\infty \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) dx.
+\end{equation}
+Is what you've written equivalent to this? Sorry if this is remedial...
+ }
+ \begin{equation}
+\Prob(P_{e})  =  1 -  \int \Prob(\widehat{\textbf{P}}_x) \Prob(\widehat{\textbf{P}}_{e+x}|P_{e}) x
+ \end{equation}
+ where $\Prob(\widehat{\textbf{P}}_x)$ is the probability of obtaining the power spectrum $\widehat{\textbf{P}}_x$ found via bootstrapping (power spectrum of data only) and $\Prob(\widehat{\textbf{P}}_{e+x}|P_{e})$ is the probability of obtaining the summed power spectrum $\widehat{\textbf{P}}_{x+e}$ given a range of input power levels, as sampled in Figure \ref{fig:Pr_vs_Pin}.
+
+Probability vs.
+injection level is shown in Figure \ref{fig:Prob_vs_Pin}.
+At low injection levels the variation between $\textbf{x}$ and $\textbf{(e+x)}$ is such that the null test is ruled out to within $20$\%.
+This is the level expected from two distributions with $\sim$10 effective samples.
+As the injected signal approaches the level of the data, the probability of null rejection rises steeply.
+
+Lastly, this method requires that we choose the probability at which we choose to reject the null hypothesis.
+As can be seen in Figure \ref{fig:Prob_vs_Pin}, the difference between $80$\% and $90$\% can mean a difference of almost an order of magnitude in the power spectrum level that is ruled out.
+We can also see that, due to the small number of samples, the probability does not perfectly converge at high injected power levels.
+Rather than insist on a rejection at the $99$th percent level, we compromise at $95$\%.
+
+The resulting limits for inverse covariance weighted PAPER-64 data (the same data used in Section \ref{sec:Sigloss}, no regularization), using this second signal loss method, are shown in Figure \ref{fig:sigloss_compare} compared with the method used in the main text.
+Overall the limits show good agreement, with k modes differing by factors of $\sim$$2$ for $k > 0.1$ $h$Mpc$^{-1}$ .
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.4\textwidth]{plots/sigloss_method_comparison_95.png}
+\caption{A comparison of the signal loss method described in Section \ref{sec:Sigloss}
+with the method in this appendix at $95$\% confidence (red curve).
+Also shown are the upper limits of the uniform-weighted power spectrum
+(blue dashed) and theoretical noise model (green).} 
+\label{fig:sigloss_compare} 
+\end{figure}
+
 \end{comment}

### 2018-11-01 PAPER.tex
small syntax edit

@@
 %\documentclass[twocolumn,numberedappendix]{emulateapj}
+%\documentclass[preprint2]{emulateapj}
 \shorttitle{Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum}
@@
 \citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
-Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
+Radio Telescope (GMRT; \citealt{Paciga2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
 the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
@@
 
-This paper is organized into three main sections.
+This paper is organized into four main sections.
 In Section \ref{sec:SiglossOverview} we use toy models to develop intuition about signal loss, its origin, and its subtleties.
@@
 This weighting is applied to data, which is then propagated into a final estimator using the power spectrum estimation technique of quadratic estimators (QE) as done in
-\citet{liu_tegmark2011}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{trott_et_al2012}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
+\citet{liu_tegmark2011}, \citet{trott_et_al2012}, \citet{dillon_et_al2013a}, \citet{liu_et_al2014a}, \citet{liu_et_al2014b}, \citet{dillon_et_al2014}, \citet{dillon_et_al2015}, \citet{switzer_et_al2015}, and \citet{trott_et_al2016}.
 %Before showing how signal loss can arise when using different weighting matrices, we first summarize QE as performed in the PAPER analysis.
@@
 
-\bibliographystyle{apj}
+%\bibliographystyle{apj}
 \bibliography{refs}
